### 2019-05-24 latex/afm-cs-main.tex
Initial commit of merging the old paper and stuff from my thesis.

\documentclass[twocolumn,twoside]{IEEEtran/IEEEtran}
% \documentclass[defaultstyle,11pt]{IEEETran}
% Lucy says to look at:
% float_page_fraction
% tex_page_fraction
% https://tex.stackexchange.com/questions/35125/how-to-use-the-placement-options-t-h-with-figures#35130
% \renewcommand\floatpagefraction{0.5} %% default: 0.5
% \renewcommand\topfraction{0.7} % default: 0.7
% \renewcommand*\textfraction{.05}
\usepackage{amssymb}		% to get all AMS symbols
\usepackage{amsthm}
\usepackage{mathtools}
\usepackage{graphicx}		% to insert figures
\usepackage{hyperref}		% PDF hyperreferences??
\usepackage{multirow}
\usepackage{mathtools}
\usepackage{cite}
\usepackage{listings}
\usepackage{booktabs}
% \usepackage{amsthm}
\usepackage[percent]{overpic}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{xspace}
\usepackage{enumitem}
\usepackage{catchfilebetweentags} % for data input
\usepackage[inkscapelatex=false, inkscapepath=svgsubpath]{svg}
\usepackage{url}
\usepackage{mdframed}
\usepackage{amsmath, dsfont, bbold}
% \usepackage{algpseudocode,algorithm,algorithmicx}
\usepackage[linesnumberedhidden,ruled]{algorithm2e}
\usepackage{placeins}
\usepackage{todonotes}

% Indent paragraphs inside enumerate
\usepackage{enumitem}
\setlist{  
  listparindent=\parindent,
  parsep=0pt,
}
\newcommand{\xyc}{\ensuremath{XY}\xspace}
\newcommand{\xc}{\ensuremath{X}\xspace}
\newcommand{\yc}{\ensuremath{Y}\xspace}
\newcommand{\zc}{\ensuremath{Z}\xspace}

\usepackage{layouts}
%textwidth: \printinunitsof{in}\prntlen{\textwidth}
%linewidth: \printinunitsof{in}\prntlen{\linewidth}
% textwidth: \printinunitsof{in}\prntlen{\textheight}

% this reveals that textwidth and linewidth are 6.5 inches,
% and textheight is 9.1 inches.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%       BEGIN DOCUMENT...         %%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\title{High-speed atomic force microscopy through $\mu$-path sampling}

\author{Roger A. Braker and Yufan Luo and Lucy Y. Pao and Sean B. Andersson
  \thanks{The authors are with the Dept. of Electrical, Computer, and Energy
    Engineering at the University of Colorado, 425 UCB, Boulder, CO 80309,
    United States. Phone: +1 (303) 492-2360. Fax: +1 (303) 492-2758. R. A.
    Braker (corresponding author roger.braker@colorado.edu) is a graduate
    student and L.Y. Pao (pao@colorado.edu) is the Richard \& Joy Dorf
    Professor.} \thanks{This work was supported in part by the US National
    Science Foundation (NSF Grant CMMI-1234980) and Agilent Technologies, Inc.}
}

\maketitle
\begin{abstract}
  Undersampling-based approaches in Atomic Force Microscopy (AFM) aim to reduce
  the time to acquire an image by reducing the number of measurements needed
  while still maintaining image quality. In this paper, we describe a hardware
  implementation and demonstration of one such approach based on the use of
  collections of short scans known as $\mu$--paths. Using a commercial AFM, we
  acquire data on two different grating samples using two different sampling
  approaches: randomly-placed $\mu-$paths and $\mu-$paths designed to minimize
  the reconstruction error based on partial prior information about the spatial
  frequency content in the sample image. Reconstructions are made from these
  data using three approaches: (1) inpainting, an interpolation technique that
  diffuses information from sampled locations into unsampled regions, (2)
  basis-pursuit, a compressive sensing-based algorithm that seeks to minimize a
  measure of sparsity in the underlying image, and (3) a new variant of basis
  pursuit, Basis Pursuit Vertical Variation (BPVV), that is designed to reduce
  artifacts arising from the sampling pattern. The quality of the resulting
  images is compared to images from standard raster scans of the same regions at
  comparable imaging rates using both the peak signal-to-noise ratio and the
  structured similarity index metric. These experiments demonstrate that at slow
  scan rates, the $\mu-$path scheme produces similar image quality with
  significantly less sampling (and thus less tip-sample interaction) and that at
  high rates, the undersampling scheme produces higher quality images than
  raster scanning.
\end{abstract}

\section{Introduction}\label{sec:introduction}
The Atomic Force Microscope (AFM) is a powerful instrument capable of imaging
sample surface topography, material characteristics, and other surface
properties, at the nanometer scale. AFMs acquire information about the sample
through a variety of imaging modes, all of which rely on the deflection of the
cantilever caused by the tip-sample interaction force. While the details of each
of the modes are quite different, in general, feedback control is used to hold
the deflection signal constant and information about the property of interest is
inferred from the applied control or the measured dynamics of the cantilever
\cite{Abramovitch:2007gt}. Because of its versatility, spatial resolution, and
ability to image in vacuum, air, and liquid, AFM is widely used in a variety of
disciplines, including physics, biology and materials science
\cite{Dufrene:2017gm,Yang:2017im,Payton:2016hj,Altman:2015ic,Haase:2015eh}

In addition to imaging static samples, AFM is increasingly being applied to
study dynamics in systems with nanometer-scale features
\cite{Yang:2017im,Shibata:2017da,Shibata:2015jd,Ando:2014ja}. The image
acquisition time of conventional AFMs, however, is typically on the order of
seconds to minutes, severely limiting the time-scales that can be explored.
Driven by the need for faster imaging, there continue to be many active research
efforts to overcome this challenge. Since an AFM is fundamentally a mechanical
microscope, many of the approaches to high-speed AFM (HS-AFM) have focused on
modifications to the physical components. These have included the use of small,
fast cantilevers \cite{viani1999fast, braunsmann2010high,Adams:2016hg}, the
development of faster actuators \cite{Maroufi:2015gt,Yong:2012kd,Kenton:2012cm},
as well as the application of advanced controllers
\cite{Rana:2018es,Yong:2015gr,butterworth2010adaptive,salapaka2002high}. By
combining different techniques, there are current generation, high-end
instruments that can image at rates on the order of 1-10 frames/sec
\cite{Ando:2014ja}. However, the fastest rates are achieved only over small scan
ranges and there remain many systems of interest whose dynamics are faster even
than these instruments can achieve. In addition, there is a large installed base
of much slower AFMs that can benefit from alternative approaches to improving
imaging rate.

A complimentary class of HS-AFM approaches considers modifications to the
sampling scheme rather than the system mechanics. Alternative scan trajectories
like spirals, cycloids, and Lissajous figures, have been used in place of the
standard raster scan. These trajectories are easier for the actuators to follow,
allowing the tip to be moved more quickly and leading to faster image
acquisition on an otherwise unmodified instrument
\cite{Bazaei:2017dm,Wu:2015dt,Rana:2014bj,Tuma:2012hv,Yong:2010gm}. Such
approaches are ultimately limited by the vertical bandwidth of the instrument
for regulating the deflection signal \cite{Teo:2016ev}. Related to these are
local scanning methods that use the measurements in real-time to steer the tip
to focus the scan on features of interest, reducing imaging time by reducing the
amount of sampling needed
\cite{Hartman:2018ja,Wen:2018fl,Zhang:2015cf,Huang:2014dw}. While these have
been shown to yield an order of magnitude or better improvement in imaging rate,
they are limited in the class of samples that can be imaged.

An alternative group of non-raster scanning schemes, introduced in
\cite{song2011video,andersson2012non}, is based on the idea of undersampling. As
with local scanning, data acquisition time is reduced by reducing the amount of
measurements acquired. Unlike local scanning methods, this approach still
presents the full image. Taking advantage of the redundancy in many natural
signals of interest, the final surface image can be recovered from the limited
number of measured pixels using a variety of different reconstruction methods
such as inpainting or schemes based on the theory of compressive sensing (CS)
\cite{chen2013enhancement,luo2015comparison}. In addition to the reduced imaging
time, undersampling schemes also reduce tip-sample interactions, thereby
reducing the likelihood of tip wear or sample damage.

One simple way to create undersampling schemes is by modifying existing full
scan patterns including raster, spiral, and Lissajous scanning. For example,
subline sampling is generated by randomly skipping some of the horizontal lines
in raster scanning \cite{han2018reconstruction,chen2013enhancement}. For spiral
and Lissajous patterns, the scan parameters (frequency and amplitude) can be
selected to ensure the trajectory only passes through a desired fraction of the
pixels in the final image. The scanning time for these smooth undersampling
patterns can be estimated based on the proportion of the pixels in the
trajectory. However, results in the literature of CS make clear that
\textit{randomness} in the sampling pattern is essential for creating good
reconstructions in the general case. The smooth nature of these patterns reduces
their randomness and thus leads to less accurate reconstructions than a
completely random sampling of the pixels for the same sampling fraction.

In AFM, implementing a truly random pattern requires that the tip be engaged
with the surface to collect a measurement, lifted and moved to the new location,
and engaged again. Because the re-engagement process is typically slow, this can
lead to excessively long image acquisition times and negate the gains from
undersampling \cite{andersson2012non}. One discrete undersampling scheme, called
a $\mu$-path pattern, was proposed in \cite{maxwell2014compressed} to improve
sampling efficiency. The $\mu$-path pattern consists of randomly placed short,
horizontal scans (see Fig.~\ref{fig:mu_mask} for one such pattern) and is
designed to balance the randomness needed to ensure good reconstruction with
continuous scanning to reduce the number of tip
engagements. %Though the pattern is motivated from CS, it also works well in practice for inpainting reconstruction \cite{luo2015comparison}.

Our previous work on the $\mu$-path pattern using theoretical calculations,
simulations, and a preliminary implementation, demonstrates that the approach
can achieve significant scanning time reduction while maintaining faithful image
reconstruction \cite{maxwell2014compressed,Luo:2015tu,Braker:2018gi}. This paper
builds upon that earlier work in several significant ways. First, we demonstrate
performance using both randomly-placed $\mu-$paths and designed $\mu-$paths that
are optimized to minimize the expected reconstruction error given some initial
estimate of the frequency structure of the sample. These schemes are described
in Sec. \ref{sec:samplingScheme}. We also introduce a new reconstruction
algorithm which is designed to minimize the artifacts arising from the structure
of the $\mu$-path scanning pattern. This algorithm is described and compared to
existing reconstruction methods through simulations in Sec.
\ref{sec:reconstructionMethods}. We then demonstrate the entire scheme from
sampling through reconstruction using experiments on a commercial AFM (Agilent
5500). The experimental setup and implementation details are described in Secs.
\ref{sec:experimentalSetup} and \ref{sec:implementation}\footnote{The software
  portion of the implementation and image reconstruction described in this paper
  can be found at \url{https://github.com/yufan88/}}. Experimental results with
two different grating samples are provided in Sec.
\ref{sec:experimentalResults}. Finally, we provide a few concluding remarks in
Sec. \ref{sec:conclusions}.

% =========================================================================
\subsection{Reconstruction methods}
\label{sec:reconstructionMethods}

In this work, we use three reconstruction algorithms to generate the final
surface image. The first one comes from the field of compressive sensing (CS).
CS is a signal processing technique which aims at signal reconstruction from a
relatively small (sub-Nyquist limit) number of measurements
\cite{carmi2014compressive}. It takes advantage of the approximate sparsity of
real-world signals, that is, of the fact that many coefficients of such signals
are close to zero when represented in an appropriate basis. CS methods seek the
true image signal $x\in\mathbb{R}^n$ from the following observation equation,
\begin{equation}\label{op:observation}
  y = \Phi x = \Phi\Psi\eta,
\end{equation}
\noindent where $y\in\mathbb{R}^m$ is the observation vector, $\Phi$ is an
$m\times n$ matrix defining the measurements, $\Psi$ is an $n\times n$ sparsity
basis and $\eta$ is the sparse representation of $x$ in the domain of $\Psi$. In
general, $m\ll n$. In an imaging application, where the underlying signal is a
matrix $X\in\mathbb{R}^{h\times s}$, we take $x=\text{vec}(X)$, where the
$\text{vec}(\cdot)$ operator stacks the columns of a matrix. Note that the
symbols $x$ and $y$ are also used to indicate coordinate directions in the AFM.
They are reused here as they are standard notation in the CS literature; their
specific meaning throughout the paper should be clear from context.

In the AFM application, the probe can only measure a single pixel at a time.
This implies that $\Phi$ is a sparse matrix with each row having only one
nonzero entry and that $y$ is a subset of $x$. Ideally, the sparsity basis and
the measurement matrix $\Phi$ will have a low \textit{mutual coherence}, a
measure that describes how each of the rows of $\Phi$ (the measurements)
``spreads out'' in the domain of $\Psi$ \cite{candes2007sparsity}. In practice,
the Discrete Cosine Transform (DCT) keeps a good balance between achieving a low
mutual coherence between the basis and the required structure of the AFM sensing
matrices and providing a high sparsity of typical AFM sample images. Therefore,
for concreteness, in this work we use the DCT as the sparsity basis $\Psi$.

One common realization of the CS-based reconstruction problem, known as basis
pursuit with denoising (BPDN), is given by the following optimization problem,
\begin{equation}\label{op:bp}
  \begin{aligned}
	\min_{x} \left \| \Psi^{-1}x \right \|_1\quad \text{subject to}\quad \|\Phi
    x - y\|_2 < \sigma,
  \end{aligned}
\end{equation}
where $\| \cdot \|_1$ and $\| \cdot \|_2$ denote $l_1$ and $l_2$ norms,
respectively, and $\sigma$ represents some measure of the signal noise such as
its variance. This problem essentially searches for the sparsest signal from all
the candidates that match the measurements. While BPDN is a computationally
demanding algorithm, particularly for large images, it in general provides
accurate reconstructions. In this work, we use the package
$l_1$-magic~\cite{l1magic} to solve the BPDN problem. More efficient greedy
algorithms have also been developed. One of these, Simplified Matching Pursuit
(SMP), was created by two of the authors and was designed specifically for the
sampling matrices in the AFM setting \cite{Luo:2015tu}.

Although BPDN is effective in the general setting, using it for reconstruction
from horizontal $\mu$-path samples often yields artifacts in the vertical
direction (that is, the direction orthogonal to the $\mu$-path scans) leading to
strong discontinuities in the image. These artifacts grow more prominent as the
length of the $\mu$-paths is increased \cite{maxwell2014compressed} as these
longer paths lead to increased mutual coherence between the measurement matrix
$\Phi$ and the sparsity basis $\Psi$. However, longer $\mu$-paths means fewer
tip re-engagements and thus shorter scan times. As a result, the second
algorithm we consider is a new variant of BPDN that we term basis pursuit with
vertical variation (BPVV). In order to mitigate the vertical artifacts, BPVV
adds a vertical total variation penalty in the spatial domain to the
optimization objective. That is, \eqref{op:bp} is modified to
\begin{equation}\label{op:bp_tv}
  \begin{aligned}
	\min_{x} \left \| \Psi^{-1}x \right \|_1 + \epsilon \left \| \nabla_v x
    \right \|_1 \, \text{subject to} \, \| \Phi x - y \|_2 < \sigma,
  \end{aligned}
\end{equation}
where ${\nabla_v x=\text{vec}(\nabla_v X)}$ is the discrete gradient in the
vertical ($y$) direction and
% \textcolor{red}{
\begin{equation}
  (\nabla_v X)_{i,j} = 
  \begin{cases}
    X_{i+1,j} - X_{i,j}, & 1\leq i<h,~ 1\leq j\leq s,\\
    0, & \phantom{:}i=h,~\phantom{:::::} 1\leq j\leq s.
  \end{cases}
\end{equation}

\begin{algorithm}
  \SetKwInOut{Initialize}{Initialize} \SetKwInOut{Output}{Output}

  \Initialize{$x = d_y = w = b_y = b_w = k = 0$, $y_0=y$ sampled pixels}
  \While{$\left \|\Phi x^k - y^k \right \|_2 \ge \sigma$} {
    % $x^{k+1} = x^{k}$\\
    \For{$i= 1$ \KwTo $N$} {
      $p\leftarrow\mu\Phi^Ty^k+\lambda\nabla_v^T\left(d_y-b_y\right)+\gamma\Psi\left(w-b_w\right)$\\
      $x^{k+1}\leftarrow \left(\mu\Phi^{T}\Phi+\lambda\nabla_v^T\nabla_v+\gamma I\right)^{-1}p$\\
      $d_y\leftarrow \text{shrink}(\nabla_vx^{k+1}+b_y,1/\lambda)$\\
      $w\leftarrow \text{shrink}\left(\Psi^{-1}x^{k+1}+b_w,1/\gamma\right)$\\
      $b_y\leftarrow b_y+\left(\nabla_vx^{k+1}-d_y\right)$\\
      $b_w\leftarrow b_w+\left(\Psi^{-1}x^{k+1}-w\right)$\\
    }
    $y^{k+1} = y^k + y - \Phi x^{k+1}$\\
    $k \leftarrow k + 1$\\
  } \Output{Reconstruction $x^k$}
  \caption{Split Bregman BPVV}
  \label{ag:BPTV}
\end{algorithm}
\todo{Modify this for NESTA}

In \eqref{op:bp_tv}, $\left \| \nabla_v x \right \|_1$ is the total variation of
the signal in the vertical direction and $\epsilon$ is a weighting parameter
which in this work is taken to be unity. The description of BPVV in
\eqref{op:bp_tv} can be viewed as the combination of CS and inpainting
(described below), in which the first term seeks a sparse solution while the
second term tries to diffuse pixel information. To solve the optimization
problem in \eqref{op:bp_tv} we use the split Bregman method
\cite{goldstein2009split}. The resulting algorithm is described in
Algorithm~\ref{ag:BPTV} where $\mu, \lambda, \gamma$ are scalar penalty
parameters that influence the convergence of the algorithm (though not the
solution found) and
\begin{equation}\label{df:shrink}
  \text{shrink}(x,\gamma) = \frac{x}{|x|}\max\left(|x|-\gamma,0\right),
\end{equation}
where all operations are element-wise.

\noindent 
\begingroup \setlength{\tabcolsep}{1pt}
\begin{figure*}[htbp]
  \centering
  \begin{tabular}{cccccc}
    \textit{\small original image} & \textit{\small BPDN} & \textit{\small BPVV} & \textit{\small detail of original} & \textit{\small detail of BPDN} & \textit{\small detail of BPVV} \\
    \includegraphics[width=0.16\textwidth]{figures-SBA/circulargrating_gt_framed}
                                   & \includegraphics[width=0.16\textwidth]{figures-SBA/circulargrating_40mu}		
                                                          & \includegraphics[width=0.16\textwidth]{figures-SBA/circulargrating_bptv_40mu}
                                                                                 & \includegraphics[width=0.16\textwidth]{figures-SBA/circulargrating_gt_zoomin}
                                                                                                                      & \includegraphics[width=0.16\textwidth]{figures-SBA/circulargrating_mu40_zoomin}
                                                                                                                                                       & \includegraphics[width=0.16\textwidth]{figures-SBA/circulargrating_bptv_40mu_zoomin}\\	
    \includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_gt_framed}
                                   & \includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_40mu}		
                                                          & \includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_bptv_40mu}	
                                                                                 & \includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_gt_zoomin}	
                                                                                                                      & \includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_40mu_zoomin}
                                                                                                                                                       & \includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_bptv_40mu_zoomin}	\\
    \includegraphics[width=0.16\textwidth]{figures-SBA/dnaforbptv_gt_framed}
                                   & \includegraphics[width=0.16\textwidth]{figures-SBA/dnaforbptv_40mu}		
                                                          & \includegraphics[width=0.16\textwidth]{figures-SBA/dnaforbptv_bptv_40mu}	
                                                                                 & \includegraphics[width=0.16\textwidth]{figures-SBA/dnaforbptv_gt_zoomin}	
                                                                                                                      & \includegraphics[width=0.16\textwidth]{figures-SBA/dnaforbptv_40mu_zoomin}
                                                                                                                                                       & \includegraphics[width=0.16\textwidth]{figures-SBA/dnaforbptv_bptv_40mu_zoomin}		
  \end{tabular}
  \caption{Reconstruction comparison between BPDN and BPVV. (first column)
    Original raster-scanned image. (second column) BPDN reconstruction from
    random, 40 pixel long $\mu$-paths with 25\% sampling. (third column) BPVV
    reconstruction from the same sub-sampled data. (remaining columns)
    Corresponding details from the red boxes indicated in the raster image. The
    results show that BPVV reduces the artifacts arising from the horizontal
    scans of the $\mu$-path pattern that appear in BPDN reconstructions.}
  \label{fig:BPTV_demonstration}
\end{figure*}
\endgroup

A comparison between BPDN and BPVV is shown in
Fig.~\ref{fig:BPTV_demonstration}. Images of three different samples (a circular
grating, a square grating and a DNA image) were acquired using an Agilent 5500
AFM with a standard raster scan (first and fourth columns in the figure). These
images were then resampled using a random $\mu$-path pattern of size 40 pixels
with 25\% of the pixels sampled. Images were reconstructed using BPDN (second
and fifth columns) and BPVV (third and sixth columns). The reconstruction
results show the artifacts apparent in the BPDN reconstruction are largely
mitigated using BPVV.

% =========================================================================
\section{Experimental setup} \label{sec:experimentalSetup}
% =========================================================================
Our experimental setup, illustrated in Fig.~\ref{fig:exp_setup_anderssonLab},
consists of an Agilent 5500 AFM, a cRIO-9082 embedded controller (National
Instruments), and a standard desktop computer. Through a breakout box, the
Agilent 5500 provides access to the $x$, $y$, and $z$-axis measurements as well
as the deflection signal (denoted in the following as $l$). When the Agilent
default software (PicoView) is set to open-loop mode, a $\pm 10$ V input on the
control box allows control of the $x$, $y$, and $z$-axis piezos. The N9524A
piezoelectric scanner in the Agilent 5500 provides a maximum scan area of
$90~\mu$m $\times$ 90~$\mu$m in the $xy$ (horizontal) direction and a range of
$20~\mu$m in the $z$ (vertical) direction. Initial engagement of the tip to the
sample is performed using the PicoView software before control is handed over to
the custom controllers.

TKTKT add stuff about nPoint stage and C300.

All control logic is programmed using LabVIEW 2017 and compiled to a Xilinx
Spartan-6 LX150 Field Programmable Gate Array (FPGA) inside the cRIO-9082. The
cRIO includes a 16-Bit, 100 kHz NI-9215 analog-to-digital input module and a
16-Bit, 100 kHz NI-9263 digital-to-analog output module. All control loops are
implemented using a 25 kHz sampling rate.

% =========================================================================
\section{Control}\label{sec:control}
The control structure for each axis is different. For the $X$-axis, we use a
state space controller. It is described fully in \cite{braker_afmmpc_2019} and
achieves a bandwidth of about 110 Hz, which is approximately 1/3 of the $X$-axis
resonance at 350 Hz.

The control law used for the $Y$-axis is a simple integral controllers of the
form
\begin{equation}
  \frac{U(z)}{E_Y(z)}=D(z) = \frac{K_Iz}{z-1},
  \label{eqn:dzI}
\end{equation}
where, the error signal $E_Y(z) = Y(z)-R_Y$.

\todo{Should I implement something better for $Y$-axis, e.g., cancel complex
  pole-zeros at 350 hz and add notch filter???}

The $Z$-axis control is slightly more complicated than the simple $Y$-axis
integral controller and is described in the following subsection.
\subsection{Z-axis Control Design}\label{sec:zaxis_cs_control}
% In Section~\ref{sec:zaxis-dist}, we eliminated or reduced many of the
% disturbances impinging on the $Z$-axis. This puts us in a position to
% increase the bandwidth without introducing building dynamics into our
% images.
The main challenge to increasing the $Z$-axis bandwidth is the bending mode
resonance at 215 Hz, which can be seen in the FRF from $u_Z$ to $Z_{d}$ in
Fig.~\ref{fig:z_control} (blue curve). We address this by inverting the complex
pole-zero pair at 215 Hz. There are multiple advantages to this method: first,
an inverse compensator still makes sense as a feedforward, open-loop compensator
if the feedback path is broken. This, situation can and does occur during parts
of the CS cycle. Second, as we discuss further below, the inverse compensator
requires no tuning as it is defined only by a fit to the measured FRF and this
can be almost completely automated.

\begin{figure}[t!]
  \centering
  \includesvg[width=1\columnwidth]{plots-afm-cs-final/figures/z_control_design.svg}
  \caption{}
  \label{fig:z_control}
\end{figure}
The entire $Z$-axis controller consists of a PI controller, $D_I(z)$ cascaded
with the resonance inversion, $D^{-1}(z)$. The inclusion of $D^{-1}$ allows us
to substantially increase the PI gain and achieve a closed-loop bandwidth of
about 480 Hz. This is the black curve in Fig.~\ref{fig:z_control}. For
comparison, the red curve in Fig.~\ref{fig:z_control} shows the closed-loop FRF
without the inverse compensator, which experiments indicate is unstable.

One challenge to this approach is the system gain and resonance at 215~Hz
changes not only day-to-day but also (and especially) when changing cantilevers.
This is illustrated in Fig.~\ref{fig:z_evolution}, which shows the FRF near the
mode for two three different cantilevers. Two are of the same make and model.

One cause for such different gains is variation in the length of the cantilever
(and possibly how the laser was adjusted). This is illustrated in
Fig.~\ref{fig:z_axis_gain}. Here, we consider a cantilever with length $h$ that
rests on the surface of some specimen with a nominal angle of $\theta$. In this
drawing, the laser is perpendicular to the sample surface. Given a vertical
perturbation $\Delta z$, we have that
\begin{equation}
  \Delta \alpha \approx \frac{d}{h} \Delta z,
\end{equation}
where $d$ is the distance from the cantilever to the detector and
$\Delta \alpha$ is the change in position of the incident laser spot on the
detector. Thus, given the same change in the vertical position, we will see a
larger change in the deflection signal for a shorter cantilever. In other words,
a short cantilever will exhibit a larger DC-gain in the $G_{u_Z,Z_d}$ transfer
function.
\begin{figure}
  \begin{minipage}[t]{.46\textwidth}
    % L B R T
    \includesvg[width=1\textwidth]{plots-afm-cs-final/figures/z_cant_evolution.svg}
    \caption{FRFs of three different cantilevers, showing substantial
      differences in the DC-gain and smaller, but still significant differences
      the frequency of the modes.}
    \label{fig:z_evolution}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{.46\textwidth}
    % L B R T
    \includegraphics[width=1\textwidth]{plots-afm-cs-final/figures/z_axis_gain_schematic-crop.pdf}
    \caption{Schematic drawing of how the length of the cantilever affects the
      $z$-axis gain.}
    \label{fig:z_axis_gain}
  \end{minipage}
\end{figure}

Fig.~\ref{fig:z_evolution} shows the frequency response of $G_{u_Z,Z_d}$ near
the bending mode for three different cantilevers. Cantilevers (A) and (B) are
both AppNano SICON cantilevers and have a nominal length of 450 microns.
Cantilever (C) is an NCLR and has a nominal length of 225 microns.
Interestingly, the SICON cantilevers show substantial variation. Unfortunately,
the manufacture does not provide a tolerance on the nominal length, so it is
difficult to tease out whether that variation is due to manufacturing
variability or other factors not explained by this analysis.

Notably, the frequency of the pole and zero do appear to shift and our inversion
scheme is not robust to this. To deal with this, I have built a (mostly)
automated system ID routine into the imaging software. This routine is a
specialized version of the techniques described previously in
Chapter~\ref{chap:modeling}. First, it obtains an FRF of the bending mode over a
frequency range spanning 180~Hz to 240~Hz (the same set of points as in
Fig.~\ref{fig:z_evolution}). The input and output sinusoids are demodulated in
quasi-realtime as they come off the FPGA. Once this is complete, a 2-pole,
2-zero transfer function model of the form
\begin{equation*}
  \hat{D}(z) = k \frac{z^2 + b_1z + b_o}{z^2 + a_1z + a_o}
\end{equation*}
is fit to the FRF, using the same optimization scheme as \eqref{eqn:logfit}.
This is done inside the LabView VI by calling a custom DLL, which leverages
CMPFIT~\cite{cmpfit,markwardt_mpfit_2009}, a
Levenberg-Marquardt~\cite{more_levenberg_1978} routine written in C. To promote
a stable fit, the optimization enforces the necessary conditions that
\begin{align*}
  |a_1| &< 2, \quad  |a_o| < 1\\
  |b_1| &< 2, \quad  |b_o| < 1.
\end{align*}
The routine then checks that both the poles and zeros are indeed stabile, saves
the data to a JSON file and passes the transfer function parameters into the
imaging portion of the application which finally uploads the parameters into the
FPGA imaging bitfile. Optionally, one can by-pass this step and simply load the
previously saved JSON file.

One of the benefits of this approach is that the DC-gain of the transfer
function $G_{u_Z,Z_d}$ becomes (approximately) normalized to unity, which makes
re-tuning the control system after changing tips far easier to non-existent. The
benefit to automating the process is that it drastically reduces the friction
required to obtain an up-to-date compensator, which means that an up-to-date
compensator is more likely to be used~\cite{abramovitch_25years_2015}.

Fig.~\ref{fig:afm_bd_dinv} shows a block diagram if the $Z$-axis control loop.
We point out a small change from Chapter~\ref{chap:cs_init}: the addition of
$D^{-1}(z)$ changes the correct signal to use to represent the sample surface.
If we take the output of the entire compensator, $u_Z=D_ID^{-1}e_z$, then we
will get a lot of wiggles in the resulting signal. Rather, we need to take only
the output of the integrator to represent the surface.
% \begin{figure}
%   \centering
%   \includegraphics[width=1\columnwidth]{plots-afm-cs-final/figures/AFM_loop_Dinv-crop.pdf}
%   \caption{Block diagram of the $Z$-axis control loop with the inverse
%   compensator. }
%   \label{fig:afm_bd_dinv}
% \end{figure}
\begin{figure*}[t]
  \centering
  \includegraphics[width=0.75\textwidth]{plots-afm-cs-final/figures/AFM_loop_Dinv_antiwup-crop.pdf}
  \caption{Block diagram of the $Z$-axis control loop. The anti-windup is active
    for decision index $i\in\{0,1,5\}$, which correspond to states such that
    $r_Z=r_{Z,\textrm{up}}$.}
  \label{fig:afm_bd_dinv_final}
\end{figure*}

It should be noted that this control is sufficient to eliminate the limit-cycle
behavior described in Section~\ref{sec:aproachspeed}:

% \begin{figure}[tbhp!]
%   \centering\includegraphics[width=3.0in]{figures-SBA/uz_multiplexer_KI_anderssonLab2}
%   \caption{The $z$-piezo movement is driven by switching between feedback from
%   the $z$-axis position signal and from the deflection signal. The shaded area
%   represents the digital control system, while the non-shaded region is the
%   physical system.}
%   \label{fig:zMultiplex_anderssonLab}
% \end{figure}

As illustrated in Fig.~\ref{fig:zMultiplex_anderssonLab}, the voltage applied to
the $z$-piezo is adjusted by switching the feedback signal between the $z$-axis
position sensor (when the tip is off the surface) and the deflection signal
(when the tip is engaged). The difference equation associated with
\eqref{eqn:dzI} for the $z$-axis is
\begin{equation}
  u_z(k) = K_Ie(k) + u_z(k-1).
  \label{eqn:intdiff}
\end{equation}

In the $z$-axis position control mode, the $z$-axis position is controlled to a
fixed value $z_{ref}$ which, in general, is slightly above the sample surface.
The difference between the measured $z$-axis position and $z_{ref}$,
${e(k) = z_{ref} - z(k)}$, is used as the error signal. In the deflection
control mode, when the tip is in contact with the sample, the deflection signal
is controlled to a fixed value $l_{ref}$ to ensure a constant tip-sample force.
The sample surface acts as a disturbance to the control loop. Therefore, the
$z$-axis position measurements can be taken to represent the surface topography
of the sample. In this case, the difference between the measured deflection and
$l_{ref}$ is the error, $e(k) = l_{ref} - l(k)$.

We note that the $z$-axis control described here operates the AFM in constant
force mode during imaging. It is straightforward to perform scanning under
different AFM modes, such as tapping mode, simply by adjusting the signals and
control involved in the vertical loop.

% =========================================================================
\section{Implementation}\label{sec:implementation}
% =========================================================================

% =========================================================================
\subsection{State machine}
Implementing the $\mu$-path scheme involves operating the AFM in several
distinct stages. In the $xy$-direction, the system must transition from tracking
a step command (in the transition to a new measurement location) to tracking a
scan pattern. For our simple integral controller, this only involves changing
the reference signals $x_{ref}$ and $y_{ref}$. In the $z$-direction, the system
must transition between tip descent, surface scanning, tip retraction, and
maintaining a $z$-axis position. In addition, the $z$-piezo has to switch
between position control and deflection control with two fixed reference values,
$z_{ref}$ for position control and $l_{ref}$ for deflection control.

Transition between, and operation in, these different stages is implemented as a
simple state machine. The $x$, $y$, and $z$-axis control loops are operating in
parallel and independently. The state machine consists of the following states.

\begin{enumerate}
\item \textbf{Initialization:} In this state, the user uses the PicoView
  software to bring the tip to the sample with the stepper motor. Once the tip
  is engaged in the surface, the user switches the control from PicoView to the
  custom software in LabView. The system writes parameters including the
  locations of $\mu$-paths from a desktop file to a host-to-FPGA FIFO (first in,
  first out) buffer. Next, the closed-loop control of all the axes through the
  FPGA is enabled and the system performs the following operations.
  \begin{itemize}
  \item \textbf{Read} the starting location of the first $\mu$-path from the
    host-to-FPGA FIFO.
  \item \textbf{Set} the $z$-axis loop to position control mode.
  \item \textbf{Wait until} $|e_z(k)|$ reaches a settling criterion, then go to
    state 2.
  \end{itemize}
\item \textbf{$xy$-axis move:} The system moves the tip to the next target
  location.
  \begin{itemize}
  \item \textbf{Set} $x_{ref}$ and $y_{ref}$ to the beginning of the $\mu$-path.
  \item \textbf{Wait until} $|e_x(k)|$ and $|e_y(k)|$ reach a settling
    criterion, then go to state 3.
  \end{itemize}
\item \textbf{Tip engage:} The system drives the tip towards the sample surface.
  Here, we use a smaller $K_I$ for the $z$-piezo, which results in a slow
  descent and less windup while the tip is out of contact.
  \begin{itemize}
  \item \textbf{Set} the $z$-axis loop to deflection control mode.
  \item \textbf{Wait until} $|e_z(k)|$ reaches a settling criterion, then
    transition to state 4. \todo{Update this}
  \end{itemize}
\item \textbf{Scan:} In this state, the system moves the tip following the
  trajectory of the current $\mu$-path.
  \begin{itemize}
  \item \textbf{Update} $x_{ref}$, and $y_{ref}$ iteratively to follow the
    trajectory of the current $\mu$-path to the end. At the same time, write the
    $x,y,z,$ and deflection measurements to an FPGA-to-host FIFO.
  \item \textbf{Wait until} $|e_x(k)|$ and $|e_y(k)|$ reach the end of the
    $\mu$-path,
    % a settling criterion,
    then go to state 5.
  \end{itemize}
  % \item \textbf{Transition decision:} The tip is at the end of the $\mu$-path
  %   at this time. The location of the next $\mu$-path is read from the FIFO.
  %   In
  %   order to accelerate the scanning process, the decision to lift the tip or
  %   not is made in this state. The time $t_{xy\_scan}$ it takes to scan to the
  %   beginning of the next $\mu$-path is compared to
  %   $t_{\textit{z}up}+t_{xy}+t_{\textit{z}down}$. If the former is larger,
  %   then
  %   go to state 6; otherwise, go to state 2.
\item \textbf{Tip withdraw:} In this state, the system withdraws the tip in the
  $z$-direction. A large $K_I$ is used for the $z$-piezo here in order to save
  time.
  \begin{itemize}
  \item \textbf{Set} the $z$-axis loop to position control mode.
  \item \textbf{Set} the $z$ setpoint at a specified distance off the surface.
  \item \textbf{Wait until} $|e_z(k)|$ reaches a settling criterion, then go to
    state 2.
  \end{itemize}
\end{enumerate}

Two cycles of this sequential process are illustrated by the time series in
Fig.~\ref{fig:mupathsignaltrajectory}. The following subsections describe in
more detail several features of the CS scanning process.

% \begin{figure}[htbp!]
%   \centering
%     %   \includegraphics[width=3.0in]{figures-SBA/mupathsignaltrajectory}
%   \includegraphics[width=3.0in]{figures-SBA/mupathsignaltrajectory-swapped}
%   \caption{Two cycles of the $\mu$-path scanning process. The top two plots
%   are the lateral motion of the stage, the third is the $z$-sensor signal, and
%   the bottom is the deflection signal. Each stage of the state machine is
%   indicated by color.}
%   \label{fig:mupathsignaltrajectory}
% \end{figure}

% The first section discusses several modifications (i.e., differences to
% Chapter~\ref{chap:cs_init}) to the CS-scanning cycle. Section
% \ref{sec:post_process} discusses the post-processing techniques used. Section
% \ref{sec:rdi} develops a new metric to compare the relative damage done by
% different scans and Section~\ref{sec:psnr_ssim_limits} takes a closer look at
% the SSIM and PSNR metrics in an effort to understand what ''reasonable''
% numbers look like for AFM images taken with our AFM. Similarly,
% Section~\ref{sec:cs_sim} looks at some CS simulations (based on real raster
% scans) to help us understand what, ideally, we should see from the experiments
% performed in Section~\ref{sec:results:final}.

% Several cycles of the CS-scheme are shown in
% Fig.~\ref{fig:mupathsignaltrajectory}. Each of these differences is discussed
% more fully in the following three subsections.
\begin{figure*}[ht!]
  \centering \includesvg[scale=0.85]{plots-afm-cs-final/figures/cs_cycle.svg}
  \caption{Several CS cycles. Each state is indicated by color.}
  \label{fig:mupathsignaltrajectory}
\end{figure*}

% \begin{figure*}
%   \centering
%   \includesvg[width=.9\textwidth]{plots-afm-cs-final/figures/state-machine-final.svg}
%   \caption{Diagram of the state-machine implemented in the final design.}
%   \label{fig:sm_final}
% \end{figure*}

\subsection{Cantilever does not need to fully disengage.}
In the initial implementation, we insisted that the during tip-retraction
(state-5), the cantilever tip should fully break contact with the surface. Here,
we impose no such requirement. Rather, we change the $Z$-setpoint during
tip-retraction to only pull away far enough that the deflection signal stays low
(i.e., below the scanning setpoint), even while we run across the surface.

\textbf{Motivation} The motivation for this is two-fold. First, there is the
obvious advantage that, by not pulling the tip so away, there is less distance
to recover during the re-engagement. The original idea was to pull away from the
surface far enough to disengage, then step back down towards the surface by some
fraction of the step up. This proved impractical for several reasons. First, it
requires the control system to be able to detect when disengagement has
occurred. While preliminary experiments indicate it may be possible to achieve
this by detecting a change in the derivative of the deflection signal, the
actual value of the control signal which achieved dis-engagement proved to be
highly variable (ranging from about 0.6 v to over 3 volts (210 nanometers to
over a micron)) and sometimes saturating the control signal without
disengagement. Experiments indicate that the dis-engagement point depends on (at
least) the tip condition and the cantilever spring constant \footnote{The
  numbers cited used a cantilever with $k\approx .1$~N/m. Experiments using a
  cantilever with $k\approx 50$ N/m yielded much more consistent and much
  smaller needed dis-engagement control signals. However, cantilevers with such
  large spring constants are tapping-mode cantilevers, a mode which our AFM is
  incapable of. Scanning in contact mode with such a cantilever implies that a
  very large force is being applied to the sample.}.

Such large pull-away distances are problematic, especially for our AFM, which
lacks a $Z$-position sensor. The difficulty is that when the tip is re-engaged
with the sample from far away, this incites a large drift transient. This is
shown in Fig.~\ref{fig:z_drift} under the panels labeled ``big lift''. By
starting the re-engagement closer to the sample, this transient is much smaller.
Without a $Z$-position sensor, we have to let this drift die out or it will
corrupt the image. Thus, even if the step-up-down scheme could be made to work,
the overall time would still be limited by this drift. I made some effort to fit
an LTI model to the drift mode, so this affect could be removed in
post-processing. Unfortunately, as we saw in
Section~\ref{sec:modeling_remaining}, an LTI drift model does not adequately
describe the drift transient, because the drift rate seems to depend on the
control history.

A third advantage is that, given the \emph{same} absolute starting height above
the specimen, re-engagement is faster when the tip has not snapped free. The
reason for this is that when the cantilever snaps away from the specimen
surface, the deflection signal is essentially saturated. This gives the control
loop an artificially small error signal, which leads to a very sluggish descent.

\textbf{Justification} Ultimately the concern is damage to the sample and tip,
which is caused by the force imparted by the cantilever probe
\cite{clayton_review_2009}. The deflection signal, though un-calibrated (meaning
it does not directly lead to a value in $kN$), is proportional to that force,
because it is proportional to how much the cantilever is bent. I.e., a large
(towards $+\infty$) deflection implies the spring force of the cantilever is
pushing hard into the sample, thereby inducing damage. In a typical imaging
scenario, we choose a deflection setpoint, (say $0.15$~[v], as in
Fig.~\ref{fig:z_drift}), and have in some way decided that this is sufficient,
all else being equal, to not damage things too much.

Thus, rather than completely dis-engaging the tip from the surface, I propose to
simply move the setpoint towards $-\infty$ during the $XY$-move. If this new
setpoint is sufficiently far away, the deflection signal will stay below the
scanning setpoint, which we had decided was a ''safe'' value. The change in
setpoints is achieved via the multiplexer in Fig.~\ref{fig:afm_bd_dinv_final}
which selects either the scanning setpoint $r_{Z,s}$ or the retraction setpoint
$r_{Z,\textrm{up}}$ based the current state.

\begin{figure}[ht!]
  \begin{subfigure}{.48\textwidth}
    \includesvg[width=1\textwidth]{plots-afm-cs-final/figures/justify_small_lift.svg}
    \caption{ }
    % \label{fig: }
  \end{subfigure}
  \begin{subfigure}{.48\textwidth}
    \includesvg[width=01\textwidth]{plots-afm-cs-final/figures/justify_small_lift_zoom.svg}
    \caption{ }
    % \label{fig: }
  \end{subfigure}
  \caption{One CS-cycle with different dis-engagement heights. (a) Full view.
    (b) Zoomed-in view. Note the drift transient in the left panel of (b). }
  \label{fig:z_drift}
\end{figure}

This new scheme does not imply that the cantilever \emph{never} fully
disengages. Occasionally, the new setpoint is far enough away that the probe
does still snap away from the sample surface. When this happens, the integrator,
$D_I(z)$, will windup. This happens because typically, the desired setpoint
$r_{Z,\textrm{up}}$ is more negative than the free (disengaged) value of the
deflection. Thus, the sensor signal is essentially saturated and no matter how
far the $Z$-actuator tries to move, no change will result in the deflection,
leading to windup and a control signal that exceeds the actuator bounds. To deal
with this, we implement an anti-windup scheme for all states where
$r_Z=r_{Z,\textrm{up}}$, i.e., states (0), (1) and (5). This is illustrated in
the block diagram in Fig.~\ref{sec:modfied_cs_cycle}. During these states, the
output of the accumulator is saturated before its own internal feedback.

\subsection{The pre-scan}
\begin{figure*}
  \begin{subfigure}{.33\textwidth}
    \includesvg[width=1\textwidth]{plots-afm-cs-final/figures/zbounce_uz_example.svg}
    \caption{ }
    \label{fig: }
  \end{subfigure}
  \begin{subfigure}{.33\textwidth}
    \includesvg[width=1\textwidth]{plots-afm-cs-final/figures/prescan_uz_example.svg}
    \caption{ }
    \label{fig:uz_prescan}
  \end{subfigure}
  \begin{subfigure}{.33\textwidth}
    \includesvg[width=1\textwidth]{plots-afm-cs-final/figures/prescan_zbounce_PSD.svg}
    \caption{ }
    \label{fig: }
  \end{subfigure}
  \caption{(a) A ``$Z$-bounce'' experiment where the $XY$-stage is motionless
    and the cantilever is repeatedly engaged and disengaged. (b) One cycle of a
    tightly packed set of CS-cycles where the movement between each measurement
    location is 0. (c) PSDs from the portions of the trajectories which are
    colored blue and turquoise, averaged over many such cycles, demonstrating
    that the scan process itself reduces vibration in the $Z$-axis.}
  \label{fig:prescan_difference}
\end{figure*}
After the tip-descent, we begin scanning in a ``pre-scan'' phase (state (3)). To
motivate, this consider Fig.~\ref{fig:prescan_difference}. The left panel
represents what we call a ``$Z$''-bounce experiment, where the $XY$-stage stays
motionless, but we repeatedly retract and re-engage the tip with specimen,
exactly as we would in a CS scan. The right panel represents a single cycle from
specialized CS pattern, where the $\mu$-paths are still 500 nm long, but the
paths are separated by 0 pixels. In this case, the specimen is freshly cleaved
mica. The goal here is to eliminate (i) any oscillations which arise from the
$XY$-move (which, as we will show in Section ~\ref{sec:need_mimo}, can be
significant) and (ii) to have a perfectly flat surface to scan over so that
there are as few disturbances as possible entering the control loop. Finally,
the middle panel of Fig.~\ref{fig:prescan_difference} shows the PSDs of the left
and right panels (but averaged over many similar cycles). Note that the PSD is
only computed from the combination of the blue and turquoise signals.

What we see then, is that, for some unknown (to me) reason, scanning reduces the
amount of energy that shows up near 215 Hz. The idea behind the pre-scan is to
take advantage of this. The pre-scan phase is relatively long (150 samples),
especially for the faster scan rates. However, the pre-scan also allows us to
eliminate the over-scan at the end of the $\mu$-path, because by the time we are
ready to start taking data, the $X$-axis is already in quasi-steady-state. For
the current control design, the required over-scan is about 90 samples (which
can be computed from the steady-state error of the closed-loop system to a
ramp), which means the pre-scan incurs an effective overhead of about 60 samples
per $\mu$-path.

The tip settling (pre-scan) period could likely be much shorter if we a had a
$Z$-axis position sensor. Part of the reason it is so long is that, despite not
pulling the cantilever completely away from the sample, there is still a small
drift transient, as can be seen Fig.~\ref{fig:uz_prescan}. We would like to at
least give the major part of that drift transient time to die out. With a
position sensor, we would not care about the drift transient: the control signal
drifts to keep the $Z$-position constant.

\section{Post-processing}\label{sec:post_process}
Here, we discuss how we post-process the raster and CS images.

\subsection{Aligning images via cross-correlation}\label{sec:align}
To get metrics that are meaningful in any sense, we need the master image and
the comparee to be aligned. We take two steps to help ensure this. First, during
each batch of images, the nPoint stage remains under closed loop control.
Between images, the FPGA control loop idles in state-0, as discussed above in
Section~\ref{sec:idle_0}. This was not necessary duing the initial
implementation because then, the nPoint stage was controlled by the nPoint PI
controller. While this helps things substantially, there is still an alignment
issue between subsequent images, which I believe stems from the original Agilent
piezo tube, which is a three axis tube. The $XY$-axes of the tube are
uncontrolled during imaging, and in fact, after a firmware ``upgrade'', the
option to close the $XY$-loop has been grayed out in the PicoView software.

To help deal with this, we compare sub-slices of the master image and the
comparee. The results in this chapter use a sub-image obtained by removing a
border of 25 pixels from each edge. Thus, for the purposes of comparison, the
original 512$\times$512 pixel image becomes a 462$\times$462 pixel image. Let
$X$ represent the original, master image and ${\tilde X=X_{25:-25, 25:-25}}$,
using Python notation. To find the correct subslice of the comparee, we use a
two dimensional cross-correlation, which is defined as
\begin{equation}
  Z_{k,\ell} = \sum_{m=0}^{M-1}\sum_{n=0}^{N-1} \tilde{X}_{m-k, n-\ell}Y_{m-k, n-\ell}.
\end{equation}
where $Y$ is the comparee.

The index of the maximum value of the matrix $Z$
\begin{equation}
  (i^*,j^*) = \textrm{arg~} \max_{i,j}Z_{i,j}
\end{equation}
corresponds to the lower left corner of the correct subslice. Thus, the
comparisons will computed against $\tilde{Y} = Y_{i^*:i^*+487, j^*:j^*+487}$.
For an example of this in action, see the Fig.~\ref{fig:baseline_errors} in the
next section.

Unfortunately, the mis-alignment is not simply constant offset, but rather
drifts over time. This can be seen, e.g., in Fig.~\ref{fig:rast_aligned_0p5}.
Thus, while the technique described here mitigates the issue, it does not fully
eliminate the problem.

% \subsection{Dynamic de-trending}
% Because our AFM is not equipped with a $Z$-axis sensor, it is important to
% remove as much drift as possible from the $u_Z$ control signal, otherwise,
% this slow dynamic will corrupt the final image. This can partly be achieved by
% doing an image after the AFM has been on for a long time, e.g., 20 minutes,
% and especially after taking several slow raster scans. We can also remove some
% of the drift by fitting a curve
% \begin{equation}
%   d_k = \alpha + \beta t_k + \gamma \log\left(\frac{t_k}{0.1}\right)
% \end{equation}
% where $t_k$ is the time at the $k$-th sampling period and $\alpha$, $\beta$,
% and $\gamma$ are the parameters to be fit. This is a combination of a
% time-domain drift model \cite{Jung_open_loop_2000} and a linear fit which
% accounts for sample tilt. This line is fit to the entire set of $u_Z$ control
% data and subtracted.

\subsection{CS-reconstruction}\label{sec:tv_denoise}
Some of the noise in an image reconstructed via BPDN can be reduced by solving a
Total Variation (TV) de-noising optimization problem
\begin{equation}
  \min_{U} ||\nabla_xU||_1 + ||\nabla_yU||_1 + \mu||F - U||_2 \label{eqn:breg1}
\end{equation}
where $F$ is the image produced by the BPDN optimization and $U$ is the
de-noised image. This idea was heavily inspired by Yufan Luo's approach
\cite{luo_mupath_2019}. The difference is that (i) I do this for both $\nabla_x$
and $\nabla_y$, where he only does it for $\nabla_y$ and (ii) that he does it in
a single optimization which combines \eqref{eqn:breg1} with BPDN while I do it
in two separate optimizations. The optimization is solved using the Split
Bregman technique described in \cite{goldstein_splitbregman_2009} and my
implementation is publicly available \cite{L1c}.

\section{A New Metric}\label{sec:rdi}
\begin{figure}[t!]
  \centering
  \includesvg[width=1\columnwidth]{plots-afm-cs-final/figures/damage_illustration.svg}
  \caption{The RDI metric defined in \eqref{eqn:RDI} penalizes everything in the
    red shaded region and does not penalize anything in the un-shaded region.}
  \label{fig:damage_illustrate}
\end{figure}
In Chapter~\ref{chap:cs_init} that we employed two metrics, the SSIM and PSNR,
to compare different raster and CS scans to a master image. We took the master
image as a raster scan taken at a slow rate. These metrics only assess the
similarity of two images. However, in AFM imaging, pure image quality is not the
only concern, particularly for delicate samples. What is needed is a figure of
merit for how much damage was done to specimen during the imaging process. While
this is not really a concern while imaging a hard calibration grating, it plays
a prominent role biological samples~\cite{ando_highspeed_2008}. In general,
damage occurs while scanning into an uphill region, which results in a positive
deflection signal. The actual damage done by a given $Z_d$ will depend on the
spring constant of the cantilever and the softness of the specimen. Nonetheless,
we can use the positive deviations of $Z_d$ as a relative measure of damage
between different scan speeds or scanning methods, for a given cantiliver and
specimen. This motivates a metric we term the relative damage index (RDI), which
we define as
\begin{align}
  \text{RDI} &= \frac{1}{T_s}\sum_{k\in I} \frac{1}{k} \left(Z_{d,k} - r_{Z,s}\right)^2 \label{eqn:RDI}\\
  I &= \{k: k\in[0,~N-1],~ Z_{d,k}-r_{Z,s} > 0 \} \nonumber
\end{align}
where $N$ is the total number of samples in a given scan, $Z_{d,k}$ is the
deflection signal at sample $k$ and $r_{Z,\textrm{s}}$ is the scanning setpoint.
The RDI is basically the power in positive deflection. By excluding negative
values of the deflection, we do not penalize the CS algorithm while it is
re-engaging with the specimen \emph{unless} it overshoots the scanning setpoint,
which we do want to penalize. This is illustrated in
Fig.~\ref{fig:damage_illustrate}, which shows several CS cycles with a poorly
tuned controller. Only deflection signals in the red-shaded region will be
penalized by the RDI.

% Define the master image as $X$ and a reconstruction as $Y$, with each having
% $p\times p=n$ pixels. Stack the columns of each into the vectors
% $x, y\in\mathbb{R}^{n^2}$. Let $L$ be the dynamic range of the master image
% $x$. Then the PSNR is given by
% \begin{equation*}
%   \text{PSNR}(x,y) = 10\log_{10}\frac{L^2}
%   {\sqrt{\frac{1}{p^2} \sum_{i=1}^{n}( x_{i} - y_{i})^2}}.
% \end{equation*}
% The goal of the SSIM is to compare two image's structure, luminescence, and
% contrast and is built up from the means ($\mu_x$ and $\mu_y$), standard
% deviations ($\sigma_x$ and $\sigma_y$), and covariance ($\sigma_{xy}$) of the
% image vectors $x$ and $y$. The variation of the SSIM used in this thesis is
% defined as
% \begin{equation*}
%   \text{SSIM}(x,y) = \frac{(2\mu_x\mu_y + C_1)(2\sigma_{xy}+C_2)}
%   {(\mu_x^2 + \mu_y^2 + C_1)(\sigma_x^2 + \sigma_y^2 + C_2)}
% \end{equation*}
% where the constants $C_1$ and $C_2$ are regularizing constants to prevent
% singularity if, e.g., $\mu_x=\mu_y=0$. We use the default values suggested in
% \cite{wang_image_2004} of $C_1=(0.01L)^2$ and ${C_2=(0.03L)^2}$, where again,
% $L$ is the dynamic range. Both metrics have been used before to compare
% \emph{simulations} of CS reconstruction in the context of AFM
% \cite{oxvig_structure_2017, Luo_nano_2015}. We believe, however, that the
% numbers presented here in Table~\ref{tab:metrics} should be interpreted with
% some caution as it remains somewhat of an open question of how to best compare
% \emph{experimental} images from AFM.
\section{Limitations of SSIM and PSNR}\label{sec:psnr_ssim_limits}
What kind of numbers are reasonable to expect from the SSIM and PSNR metrics? We
mentioned in Chapter~\ref{chap:cs_init} that comparison of experimental images
was difficult (particularly for our experimental setup) because, e.g., Agilent
piezo tube drifts which gives a varying offset between images. However, we did
not try to tease apart to what extent the poor SSIM and PSNR numbers we reported
were due to simply the difference in scanning speeds vs things like image
mis-alignment.

In this section, we explore this subject by comparing images obtained under the
most ideal experimental conditions. Specifically, we look at the variation that
exists when comparing multiple raster scans taken at the same rate. Second, we
look at CS simulations where we sub-sample a raster image and reconstruct it.
The goal is to provide context to the numbers in
Section~\ref{sec:results:final}.

Recall that two images which are identical will yield an infinite PSNR and an
SSIM of 1.

\begin{figure}[t!]
  % ------------ 1.0 Hz ---------------------
  \begin{subfigure}{.48\textwidth}
    \includesvg[width=1\textwidth]{plots-afm-cs-final/figures/baseline_errors_noalign_1Hz.svg}
    \caption{1.0~Hz, no alignment.}
    \label{fig:rast_unaligned_1}
  \end{subfigure}
  \hfill
  \begin{subfigure}{.48\textwidth}
    \includesvg[width=1\textwidth]{plots-afm-cs-final/figures/baseline_errors_aligned_1Hz.svg}
    \caption{1.0~Hz, with alignment.}
    \label{fig:rast_aligned_1}
  \end{subfigure}
% 
  \caption{Errors between a ''master'' and 6 different raster scans, all taken
    sequentially and at a scan rate of 0.5 Hz. (a) Errors without alignment (b)
    The same data as above in (a) but aligned via cross correlation.}
  \label{fig:baseline_errors}
\end{figure}

In the first experiment, (Figs \ref{fig:rast_unaligned_0p5} and
\ref{fig:rast_aligned_0p5}) we took 6 raster scans of the same 5 by 5 micron
square of the CS-20NG sample grating. These scans were taken sequentially and
the NPXY100A remained in closed-loop throughout the process. Taking the first
scan as the master, we compute (without any alignment) the PSNR and SSIM
metrics. Fig.~\ref{fig:rast_unaligned_0p5} shows the error between the master
image and the remaining 6 images. Note that the best PSNR here is 12.13 and the
worst is 7.87. The best SSIM is 0.40 and the worst is 0.14.

Next, using the cross-correlation alignment technique discussed in
Section~\ref{sec:align}, we aligned the master image with a sub-slice of each of
the remaining 6 (the sub-slice removes 25 pixels from each side). Again, we
computed the PSNR and SSIM. These results are shown in
Fig.~\ref{fig:rast_aligned_0p5}, which again shows the errors between the
aligned master and the remaining 6 images. Although the situation is improved
compared to the un-aligned images, there is still noticable stretching,
particularly in the $Y$-direction. Notably, the with the alignment technique,
PSNR now ranges from SSIM 21.68 to 15.56 and the SSIM ranges from 0.67 to 0.50.

We repeat this experiment but this time use a 1~Hz scan.
Fig.~\ref{fig:rast_unaligned_1} shows the unaligned error images and
Fig.\ref{fig:rast_aligned_1} shows the aligned error images. Temporally, the
images are order left-to-right and top-to-bottom. Thus we can see, both visually
and via the metrics, that in Fig.~\ref{fig:rast_unaligned_1} the mis-alignment
grows over time (In the 0.5~Hz scans, it appears that after the third from, the
misalignment is so bad, the situation can't get any worse). In the aligned 1~Hz
images, our metrics are not only higher but also more consistent: and the SSIM
lies between 0.7 and 0.73 and the PSNR ranges from 22.51 to 24.99.

Due to this unfortunate drift, in Section~\ref{sec:results:final}, we will use a
1~Hz scan as the baseline image. Hopefully, this will give a decent trade-off
between having an image with minimal drift and scanning slowly enough that it
accurately represents the sample grating. Due to the improved $Z$-axis
bandwidth, a 1~Hz scan should still have better (or at least comparable) quality
than the 0.25~Hz scan taken in Chapter~\ref{chap:cs_init}. Additionally,
Fig.\ref{fig:rast_aligned_1} provides us with an (approximate) upper bound for
our expectations when looking at the experimental results in
Section~\ref{sec:results:final}.

\section{Experimental Results}\label{sec:results:final}
We took scans of the CS-20NG sample grating over an area with holes on a 500 nm
pitch. The holes are 20 nm deep. This is the same area imaged in
Chapter~\ref{chap:cs_init}. We scanned 5 micron by 5 micron images with 512
lines each, yielding 512 by 512 pixel images. As before, the $\mu$-path scans
are 500 nm long, as this allows us to work around the lack of a $Z$-axis sensor.
This yields a $\mu$-path size of 52 pixels.

The free value of the deflections signal was approximately -0.6 volts and we set
the scanning reference to $r_{Z,s}=-0.3$~volts and the withdraw reference to
$r_{Z,\textrm{up}}=-0.8$ volts. We set the $XY$-settle boundary to $\pm 0.05$
microns and required 20 samples within this boundary before moving to the
$Z$-engage state. The pre-scan length was 150 time steps. The control for the
$Z$-direction was as described in Chapter~\ref{chap:zaxis-improv}, and the
$X$-direction control used the SLF state-space (CZ) design of
Chapter~\ref{chap:mpc_slf} with one difference: the hysteresis model was
re-tuned for a $\pm$ 7 micron area. The $Y$-axis used a simple integral
controller, whose closed-loop FRF was shown in Fig.~\ref{fig:mimo_cl_frf}.

For the raster scans, we took scans at 1.0~Hz, 4.0~Hz, 5.0~Hz, 8.0~Hz and
10~Hz\footnote{For a 25~kHz sampling frequency, a 10~Hz raster scan at 512
  pixels is close to the upper limit because each pixel will only have
  approximately $ \frac{25000}{2\cdot 10 \cdot 512}\approx 2.4$ samples.}. The
CS scans we taken with scan velocities equivalent to raster scans of 1.0~Hz,
2.0~Hz, 4.0~Hz, 5.0~Hz and 8.0~Hz with sampling densities of 10~\% and 15~\%. As
in Chapter~\ref{chap:cs_init}, the cantilever was an AppNano SICON, with a
length of 450 microns and spring constant $k\in[0.02,~0.8]$~N/m.

The CS scans were reconstructed with BPDN (see \eqref{eqn:bpdn}) using the
log-barrier Newton method available in \texttt{L1c}\cite{L1c}. We set
$\epsilon = 0.1$ and the data remained scaled in terms of volts. We then
filtered the resulting image with the TV-denoising optimization described in
Section~\ref{sec:tv_denoise} with $\mu=100$.

For the raster scans, we discard data from the re-trace and divided the
remaining data into 512$\times$512 bins based on the \xc and \yc sensor
measurements. We then average the data in each bin to obtain the value of one
pixel. To remove the affects of piezo creep and sample tilt, we then de-trend
each individual line. De-trending each line introduces the artifacts we noted in
Section~\ref{sec:comp_raster}. To remove this effect, we select a column of
pixels on the left and right side of each image that does not cross any holes
(i.e., a vertical line through the flat area), register each scan line to a
common height along these columns. This step eases comparison with the CS scans
and was inspired by a feature in \texttt{SPIW} \cite{spiw}.

As a final step, we subtract the mean from each CS and raster image, so that
they can all be mapped to the same color intensity in the images. The color maps
represent a range of $\pm$20 nm.

The resulting images are shown in Fig.~\ref{fig:resultsF1_images}. The rows of
pixels indicated by the red lines are shown Fig.~\ref{fig:pixel_rows}. Due to
the improved $Z$-axis bandwidth and the image alignment issues described in
Section~\ref{sec:psnr_ssim_limits}, we use the 1.0~Hz raster scan as the master
image. Fig.~\ref{fig:resultsF1_errs} shows the error between aligned sub-slices
of the 1.0~Hz image and the remaining scans. The sub-slice removed a 30 pixel
boundary from each edge. Despite this alignment, the middle pixels tend to show
a smaller error than those towards the top and bottom, which is similar to the
affect observed before in Fig.~\ref{fig:baseline_errors}.

For each raster scan and each CS scan, we computed the SSIM, PSNR (both with
default parameters) using the 1~Hz scan as the master and also computed the RDI
metric. These are collected in table ~\ref{tab:rast_vs_cs_v1}.

\begin{figure*}
  \includesvg[scale=1]{plots-afm-cs-final/figures/cs_raster_images_4-26-2019}
  \caption{Raster and compressed sensing images of a 5 micron square area of the
    CS-20NG grating. All images are 512$\times$512 pixels. The rows of pixels
    indicated by the red line are shown in \ref{fig:pixel_rows}.}
  \label{fig:resultsF1_images}
\end{figure*}

% \begin{figure*}
%   \includesvg[scale=1]{plots-afm-cs-final/figures/cs_raster_images_err_4-26-2019}
%   \caption{Errors between aligned sub-slices of the 1.0~Hz raster image and
%   the remaining scans. The original scans are shown in
%   Fig.~\ref{fig:resultsF1_images}.}
%   \label{fig:resultsF1_errs}
% \end{figure*}

\begin{table}[t!]
  \centering
  \caption{Performance metrics for the scans taken on 4-26-2019. All CS images
    filtered with TV denoising, $\mu$=100.}
  \begin{tabular}{cccccc}
    \input{plots-afm-cs-final/tables/cs_raster_table_4-26-2019_muInf_dct2.tex}
  \end{tabular}
  \label{tab:rast_vs_cs_v1}
\end{table}

\begin{table}[t!]
  \centering
  \caption{Breakdown of state times for the CS scans listed in
    Table~\ref{tab:rast_vs_cs_v1}. All times are in seconds.}
  \label{tab:final_state_times}
  \begin{tabular}{ccccccc}
    \input{plots-afm-cs-final/tables/cs_state_times_table_4-26-2019_muInf_dct2.tex}
  \end{tabular}
\end{table}

\begin{figure*}[t!]
  \includesvg[width=1\textwidth]{plots-afm-cs-final/figures/cs_raster_pixel_rows_3-20-2019.svg}
  \caption{Rows of pixels, as indicated by the red lines in
    Fig.~\ref{fig:resultsF1_images}. For clarity, not all images are included.}
  \label{fig:pixel_rows}
\end{figure*}

Unfortunately, the SSIM and PSNR metrics are not particularly illuminating. It
is easiest to see this by plotting PSNR and SSIM against total acquisition time,
which is shown in Fig.~\ref{fig:time_ssim_psnr}. There are several
inconsistencies. First, the 4~Hz raster scan has the lowest PSNR of all the
raster scans, while the 8~Hz scan has the highest. Second, all of the 15\% CS
scans except the 8~Hz version have as good or better SSIM numbers than the
raster scans. It makes no sense for a CS scan at a 5~Hz rate to have better
quality than a raster scan at a 5~Hz rate. It is interesting to also compare
these numbers to the batch of 1~Hz raster scans we compared in
Section~\ref{sec:psnr_ssim_limits}. The blue shaded bands of
Figs~\ref{fig:time_ssim_psnr} indicate the mean of the SSIM and PSNR metrics
from Section \ref{sec:psnr_ssim_limits} plus or minus one standard deviation.
This seems to be further evidence that, at least for our experimental setup,
these numbers are not especially meaningful.

\begin{figure*}[t!]
  \begin{subfigure}{1\textwidth}
    \includesvg[scale=1]{plots-afm-cs-final/figures/cs_rast_time_vs_ssim_psnr.svg}
    \caption{(left) SSIM as a function of total acquisition time. (right) PSNR
      as a function of total acquisition time.}
    \label{fig:time_ssim_psnr}
  \end{subfigure}

  \begin{subfigure}{1\textwidth}
    \includesvg[scale=1]{plots-afm-cs-final/figures/cs_rast_damage.svg}
    \caption{(left) RDI as a function of scan rate for raster scans and CS scans
      at 10\% and 15\% sampling. (right) RDI as a function of total imaging
      time.}
    \label{fig:time_damage}
  \end{subfigure}

  \label{fig:time_vs_metrics}
\end{figure*}

Where CS seems to really shine is if we look at the RDI for a given time or scan
rate. This is plotted in Fig.~\ref{fig:time_damage}. For example, the 10~Hz
raster scan, which takes about 51 seconds, gives an RDI of 23.7. All of the CS
scans, except for the 15\% scan at 1~Hz (which is only 0.9 seconds longer) are
faster than the 10~Hz raster scan, yet have much lower RDI values, ranging from
1.21 to 13.13. Unsurprisingly, the relationship between scan speed and RDI is
quite linear. For the raster scans, the left panel of Fig.~\ref{fig:time_damage}
just plots the inverse relationship of the right panel, since scan time is
inversely proportional to raster frequency. This is not quite the case for the
CS scans due to the sub-sampling and the fixed overhead which does not scale
with scan rate (e.g., the amount of time for the $XY$-move etc remains
essentially constant for a given scan density).

What is surprising is that for the same scan rate, the CS scans have a lower RDI
than a raster scan at the same rate. One possibility is that the probability
that a given $\mu$-path will start on the flat portion of the grating, scan
\textit{into} a hole and then the tip withdraws before exiting the hole is
higher than the probability that a scan starts in a hole and exits the hole.
This would result in a lower RDI, because scanning \textit{out} of hole is what
the RDI penalizes.

From the left panel of Fig.~\ref{fig:time_damage}, we see that for a fixed RDI,
CS has a faster imaging acquisition rate. The amount of improvement is best if
we need a very low RDI: for example, if we want to hold the RDI below 2, then we
have to take the 1~Hz raster scan (512 seconds) while we can achieve the same
RDI via CS in about 52 seconds with the 15\% sampling, which is a speed
improvement of nearly 10. The higher of an RDI we are willing to tolerate, the
advantage of CS over raster narrows. For example, the 4~Hz raster scan and 5~Hz,
15\% CS scan have comparable RDI, but now CS is only about 6 times faster. This
is a result of the constant overhead imposed by the engage/disengage and
$XY$-move states in CS.

\section{Conclusions}
The main conclusion of this chapter is that with CS, it seems that we can
acquire images faster yet (putatively) with less specimen damage than is
possible with raster scanning, which we showed by introducing a new metric, the
RDI. Of course, a natural criticism is that we did not validate the RDI against
delicate specimens. We leave this as an area for future work.

A more minor takeaway is that comparing experimental AFM images is difficult,
especially for systems like ours which cannot control the $XY$-axes of the piezo
tube.

One final point that should be mentioned is that, by using an $X$-axis
controller designed for tracking step inputs, we have unfairly disadvantaged
raster scanning. Due the faster harmonic decay of a triangle wave compared to a
series of step inputs, in principle a higher bandwidth $X$-axis controller could
be used for raster scanning because the cross-coupling concerns discussed in
Section~\ref{sec:cz_cr_cs} would play a smaller role. While this will be
discussed a bit further in the next chapter, for now we note that the most
prominent way the lower bandwidth $X$-axis controller has limited raster
scanning is by chopping off the left and right edges of the images, which can be
seen in Fig.~\ref{fig:resultsF1_images} and \ref{fig:pixel_rows}. However, the
metrics are computed on a subslice that is large enough to eliminate this
region. Additionally, the RDI is mostly affected by the $Z$-direction bandwidth.

%%%%%%%%% then the Bibliography, if any %%%%%%%%%
% \bibliographystyle{plain} % or "siam", or "alpha", etc.
\bibliographystyle{IEEEtran} % or "siam", or "alpha", etc.
% \nocite{*} % list all refs in database, cited or not
\bibliography{/home/arnold/bib_pdf/main_bibliography,Andersson_bibs,Yufans_bibs} % Bib database in "refs.bib"

%%%%%%%%% then the Appendices, if any %%%%%%%%%
\end{document}

### 2019-05-24 latex/afm-cs-main.tex
This should build.

@@
   \centering
-  \includesvg[width=1\columnwidth]{plots-afm-cs-final/figures/z_control_design.svg}
+  \includesvg[width=1\columnwidth]{figures/z_control_design.svg}
   \caption{}
@@
     % L B R T
-    \includesvg[width=1\textwidth]{plots-afm-cs-final/figures/z_cant_evolution.svg}
+    \includesvg[width=1\textwidth]{figures/z_cant_evolution.svg}
     \caption{FRFs of three different cantilevers, showing substantial
@@
     % L B R T
-    \includegraphics[width=1\textwidth]{plots-afm-cs-final/figures/z_axis_gain_schematic-crop.pdf}
+    \includegraphics[width=1\textwidth]{figures/z_axis_gain_schematic-crop.pdf}
     \caption{Schematic drawing of how the length of the cantilever affects the
@@
 %   \centering
-%   \includegraphics[width=1\columnwidth]{plots-afm-cs-final/figures/AFM_loop_Dinv-crop.pdf}
+%   \includegraphics[width=1\columnwidth]{figures/AFM_loop_Dinv-crop.pdf}
 %   \caption{Block diagram of the $Z$-axis control loop with the inverse
@@
   \centering
-  \includegraphics[width=0.75\textwidth]{plots-afm-cs-final/figures/AFM_loop_Dinv_antiwup-crop.pdf}
+  \includegraphics[width=0.75\textwidth]{figures/AFM_loop_Dinv_antiwup-crop.pdf}
   \caption{Block diagram of the $Z$-axis control loop. The anti-windup is active
@@
 \begin{figure*}[ht!]
-  \centering \includesvg[scale=0.85]{plots-afm-cs-final/figures/cs_cycle.svg}
+  \centering \includesvg[scale=0.85]{figures/cs_cycle.svg}
   \caption{Several CS cycles. Each state is indicated by color.}
@@
 %   \centering
-%   \includesvg[width=.9\textwidth]{plots-afm-cs-final/figures/state-machine-final.svg}
+%   \includesvg[width=.9\textwidth]{figures/state-machine-final.svg}
 %   \caption{Diagram of the state-machine implemented in the final design.}
@@
   \begin{subfigure}{.48\textwidth}
-    \includesvg[width=1\textwidth]{plots-afm-cs-final/figures/justify_small_lift.svg}
+    \includesvg[width=1\textwidth]{figures/justify_small_lift.svg}
     \caption{ }
@@
   \begin{subfigure}{.48\textwidth}
-    \includesvg[width=01\textwidth]{plots-afm-cs-final/figures/justify_small_lift_zoom.svg}
+    \includesvg[width=01\textwidth]{figures/justify_small_lift_zoom.svg}
     \caption{ }
@@
   \begin{subfigure}{.33\textwidth}
-    \includesvg[width=1\textwidth]{plots-afm-cs-final/figures/zbounce_uz_example.svg}
+    \includesvg[width=1\textwidth]{figures/zbounce_uz_example.svg}
     \caption{ }
@@
   \begin{subfigure}{.33\textwidth}
-    \includesvg[width=1\textwidth]{plots-afm-cs-final/figures/prescan_uz_example.svg}
+    \includesvg[width=1\textwidth]{figures/prescan_uz_example.svg}
     \caption{ }
@@
   \begin{subfigure}{.33\textwidth}
-    \includesvg[width=1\textwidth]{plots-afm-cs-final/figures/prescan_zbounce_PSD.svg}
+    \includesvg[width=1\textwidth]{figures/prescan_zbounce_PSD.svg}
     \caption{ }
@@
   \centering
-  \includesvg[width=1\columnwidth]{plots-afm-cs-final/figures/damage_illustration.svg}
+  \includesvg[width=1\columnwidth]{figures/damage_illustration.svg}
   \caption{The RDI metric defined in \eqref{eqn:RDI} penalizes everything in the
@@
   \begin{subfigure}{.48\textwidth}
-    \includesvg[width=1\textwidth]{plots-afm-cs-final/figures/baseline_errors_noalign_1Hz.svg}
+    \includesvg[width=1\textwidth]{figures/baseline_errors_noalign_1Hz.svg}
     \caption{1.0~Hz, no alignment.}
@@
   \begin{subfigure}{.48\textwidth}
-    \includesvg[width=1\textwidth]{plots-afm-cs-final/figures/baseline_errors_aligned_1Hz.svg}
+    \includesvg[width=1\textwidth]{figures/baseline_errors_aligned_1Hz.svg}
     \caption{1.0~Hz, with alignment.}
@@
 \begin{figure*}
-  \includesvg[scale=1]{plots-afm-cs-final/figures/cs_raster_images_4-26-2019}
+  \includesvg[scale=1]{figures/cs_raster_images_4-26-2019}
   \caption{Raster and compressed sensing images of a 5 micron square area of the
@@
 % \begin{figure*}
-%   \includesvg[scale=1]{plots-afm-cs-final/figures/cs_raster_images_err_4-26-2019}
+%   \includesvg[scale=1]{figures/cs_raster_images_err_4-26-2019}
 %   \caption{Errors between aligned sub-slices of the 1.0~Hz raster image and
@@
   \begin{tabular}{cccccc}
-    \input{plots-afm-cs-final/tables/cs_raster_table_4-26-2019_muInf_dct2.tex}
+    \input{tables/cs_raster_table_4-26-2019_muInf_dct2.tex}
   \end{tabular}
@@
   \begin{tabular}{ccccccc}
-    \input{plots-afm-cs-final/tables/cs_state_times_table_4-26-2019_muInf_dct2.tex}
+    \input{tables/cs_state_times_table_4-26-2019_muInf_dct2.tex}
   \end{tabular}
@@
 \begin{figure*}[t!]
-  \includesvg[width=1\textwidth]{plots-afm-cs-final/figures/cs_raster_pixel_rows_3-20-2019.svg}
+  \includesvg[width=1\textwidth]{figures/cs_raster_pixel_rows_3-20-2019.svg}
   \caption{Rows of pixels, as indicated by the red lines in
@@
   \begin{subfigure}{1\textwidth}
-    \includesvg[scale=1]{plots-afm-cs-final/figures/cs_rast_time_vs_ssim_psnr.svg}
+    \includesvg[scale=1]{figures/cs_rast_time_vs_ssim_psnr.svg}
     \caption{(left) SSIM as a function of total acquisition time. (right) PSNR
@@
   \begin{subfigure}{1\textwidth}
-    \includesvg[scale=1]{plots-afm-cs-final/figures/cs_rast_damage.svg}
+    \includesvg[scale=1]{figures/cs_rast_damage.svg}
     \caption{(left) RDI as a function of scan rate for raster scans and CS scans

### 2019-05-24 compare_loops_thesis.m

@@ -1,0 +1,193 @@
+
+clear
+clc
+Ts = 40e-6;
+
+LPF = zpk([], [0.7, 0.7], 1, Ts);
+LPF = LPF/dcgain(LPF);
+models = load(fullfile(PATHS.sysid, 'x-axis_sines_infoFourierCoef_10-21-2018-03.mat'));
+G = -models.modelFit.G_zdir;
+Ki_s = [0.005, 0.01, 0.05];
+
+
+root = '/media/labserver/afm-cs/z-scope';
+
+fnames = {'data-out_KI_p005.csv',...
+  'data-out_KI_p05.csv'};
+
+idx = Inf;
+
+
+% F1 = mkfig(1, 5, 2.5, true); clf
+% % ax1 = gca();
+% ax1 =axes('Position', [0.13 0.15 0.775 0.815]);
+% ax1.Color = fig_color;
+% hold on, grid on,
+% 
+% % figure(2); clf
+% F2 = mkfig(2, 5, 2.5, true); clf
+% % ax2 = gca();
+% ax2 =axes('Position', [0.13 0.15 0.775 0.815]);
+% ax2.Color = fig_color;
+% hold on, grid on,
+% 
+% h_ze = gobjects(length(fnames),1);
+% h_uz = gobjects(length(fnames),1);
+% clrs = {'b', 'r', 'k'};
+
+% KI_s = [0.005, 0.05]; % for legend.
+% for k=1:length(fnames)
+%   Dz = zpk([0], [1], Ki_s(k), Ts);
+%   
+%   H_ud = minreal((1 + G*Dz)/Dz)*LPF;
+%   
+%   dat_k = csvread(fullfile(root, fnames{k}));
+%   
+%   ze_k = dat_k(:,1);
+%   uz_k = dat_k(:,2);
+%   
+%   idx = min(idx, length(ze_k));
+%     
+%   t_k = (0:length(ze_k)-1)'*Ts;
+% 
+%   idx1 = 480;
+%   idx2 = 56532;
+%   h_ze_k = plot(ax1, t_k(idx1: idx2), ze_k(idx1:idx2), 'Color', clrs{k});
+%   h_ze_k.DisplayName = sprintf('$K_I=%.3f$', KI_s(k));
+%   uu = detrend(uz_k);
+%   h_uz_k = plot(ax2, t_k(idx1:idx2), uu(idx1:idx2), 'Color', clrs{k});
[…]

### 2019-05-24 functions/PATHS.m

@@ -1,0 +1,82 @@
+classdef PATHS
+  %PATHS Summary of this class goes here
+  %   Detailed explanation goes here
+  
+  properties
+  end
+  
+  methods (Static)
+    function [ PATH ] = exp()
+      % PATH constant to where all experimental data is stored for the
+      % MPC journal paper.
+      if ispc
+        PATH = 'Z:\afm-cs';
+      else
+        PATH = '/media/labserver/afm-cs';
+      end
+    end
+    
+    
+    function PATH = cs_image_data(size, date_dir)
+      PATH = fullfile(PATHS.exp(), 'imaging', 'cs-imaging', size, date_dir);
+    end
+    
+    function PATH = raster_image_data(size, date_dir)
+      PATH = fullfile(PATHS.exp(), 'imaging', 'raster', size, date_dir);
+    end
+    
+    function [ PATH ] = CS_root()
+    % PATH constant to where all experimental data is stored for the
+    % MPC journal paper.
+      if ~ispc()
+        PATH = fullfile(getMatPath, 'afm-cs');
+      else
+        PATH = 'C:\Users\arnold\Documents\afm-cs';
+      end
+    end
+    
+    function [ PATH ] = labview()
+    % PATH constant to where all experimental data is stored for the
+    % MPC journal paper.
+      
+      PATH = fullfile(PATHS.CS_root, 'labview');
+    end
+    
+    function path = reconstruction_BP()
+      path = fullfile(PATHS.CS_root, 'reconstruction', 'BP');
+    end
+    function path = reconstruction_SMP1D()
+      path = fullfile(PATHS.CS_root, 'reconstruction', 'SMP_1D');
+    end
+    
+    function [ PATH ] = sysid()
+      % PATH constant to where the system ID data is stored
+      
+      PATH = fullfile(PATHS.exp, 'sysID');
+    end
+    
+    function PATH = tuesday_fig_path(date_folder, fname)
+    % PATH = tuesday_fig_path(date_folder, fname)
+    % Constructs a figure path to the tuesday figs subfolder, date_folder,
+    % for figure file fname.
+    % If date_folder does not exist, creates it.
+      folder_path = fullfile(PATHS.CS_root, 'matlab-code', 'tuesday-figs',...
+        date_folder);
+      if ~exist(folder_path, 'dir')
+        mkdir(folder_path);
+      end
+      PATH = fullfile(folder_path, fname);
+    end
+    
[…]

### 2019-05-25 latex/afm-cs-main.tex
Add the mimo FRF figure.

@@
 % \usepackage{algpseudocode,algorithm,algorithmicx}
-\usepackage[linesnumberedhidden,ruled]{algorithm2e}
+\usepackage[ruled,linesnumbered]{algorithm2e}
 \usepackage{placeins}
@@
 \begin{document}
-\title{High-speed atomic force microscopy through $\mu$-path sampling}
-
-\author{Roger A. Braker and Yufan Luo and Lucy Y. Pao and Sean B. Andersson
+\title{Improving the Image Acquisition Rate of an Atomic Force Microscope Through Compressive Sampling}
+
+\author{Roger A. Braker, Yufan Luo, Lucy Y. Pao and Sean B. Andersson
   \thanks{The authors are with the Dept. of Electrical, Computer, and Energy
@@
 \begin{equation}\label{op:observation}
-  y = \Phi x = \Phi\Psi\eta,
+  y = R x = RU\eta,
 \end{equation}
-\noindent where $y\in\mathbb{R}^m$ is the observation vector, $\Phi$ is an
-$m\times n$ matrix defining the measurements, $\Psi$ is an $n\times n$ sparsity
-basis and $\eta$ is the sparse representation of $x$ in the domain of $\Psi$. In
+\noindent where $y\in\mathbb{R}^m$ is the observation vector, $R$ is an
+$m\times n$ matrix defining the measurements, $U$ is an $n\times n$ sparsity
+basis and $\eta$ is the sparse representation of $x$ in the domain of $U$. In
 general, $m\ll n$. In an imaging application, where the underlying signal is a
 matrix $X\in\mathbb{R}^{h\times s}$, we take $x=\text{vec}(X)$, where the
-$\text{vec}(\cdot)$ operator stacks the columns of a matrix. Note that the
-symbols $x$ and $y$ are also used to indicate coordinate directions in the AFM.
+$\text{vec}(\cdot)$ operator stacks the columns of a matrix.
+
+The symbols $x$ and $y$ are also used to indicate coordinate directions in the AFM.
 They are reused here as they are standard notation in the CS literature; their
@@
 In the AFM application, the probe can only measure a single pixel at a time.
-This implies that $\Phi$ is a sparse matrix with each row having only one
+This implies that $R$ is a sparse matrix with each row having only one
 nonzero entry and that $y$ is a subset of $x$. Ideally, the sparsity basis and
-the measurement matrix $\Phi$ will have a low \textit{mutual coherence}, a
-measure that describes how each of the rows of $\Phi$ (the measurements)
-``spreads out'' in the domain of $\Psi$ \cite{candes2007sparsity}. In practice,
+the measurement matrix $U$ will have a low \textit{mutual coherence}, a
+measure that describes how each of the rows of $R$ (the measurements)
+``spreads out'' in the domain of $U$ \cite{candes2007sparsity}. In practice,
 the Discrete Cosine Transform (DCT) keeps a good balance between achieving a low
 mutual coherence between the basis and the required structure of the AFM sensing
-matrices and providing a high sparsity of typical AFM sample images. Therefore,
-for concreteness, in this work we use the DCT as the sparsity basis $\Psi$.
+matrices and providing a high sparsity of typical AFM sample images. In the following,
+we assume that $U^TU=I$, though in the simulation and experimental results, we take
+$U$ as the DCT basis.
 
@@
 pursuit with denoising (BPDN), is given by the following optimization problem,
-\begin{equation}\label{op:bp}
-  \begin{aligned}
-	\min_{x} \left \| \Psi^{-1}x \right \|_1\quad \text{subject to}\quad \|\Phi
-    x - y\|_2 < \sigma,
-  \end{aligned}
+\begin{equation}
+  \min_{x} \left \| U^Tx \right \|_1 \quad
+  \text{s.t.}\quad x\in Q_p = \{x:~\|Rx - y\|_2 < \sigma\} \label{op:bp}
 \end{equation}
@@
 demanding algorithm, particularly for large images, it in general provides
-accurate reconstructions. In this work, we use the package
-$l_1$-magic~\cite{l1magic} to solve the BPDN problem. More efficient greedy
-algorithms have also been developed. One of these, Simplified Matching Pursuit
-(SMP), was created by two of the authors and was designed specifically for the
-sampling matrices in the AFM setting \cite{Luo:2015tu}.
+accurate reconstructions.
 
@@
 longer paths lead to increased mutual coherence between the measurement matrix
-$\Phi$ and the sparsity basis $\Psi$. However, longer $\mu$-paths means fewer
-tip re-engagements and thus shorter scan times. As a result, the second
+$R$ and the sparsity basis $U$. However, longer $\mu$-paths means fewer
+tip re-engagements and thus shorter scan times.
+As a result, the second
 algorithm we consider is a new variant of BPDN that we term basis pursuit with
@@
 optimization objective. That is, \eqref{op:bp} is modified to
-\begin{equation}\label{op:bp_tv}
-  \begin{aligned}
-	\min_{x} \left \| \Psi^{-1}x \right \|_1 + \epsilon \left \| \nabla_v x
-    \right \|_1 \, \text{subject to} \, \| \Phi x - y \|_2 < \sigma,
-  \end{aligned}
-\end{equation}
-where ${\nabla_v x=\text{vec}(\nabla_v X)}$ is the discrete gradient in the
-vertical ($y$) direction and
-% \textcolor{red}{
-\begin{equation}
+
+\begin{align}
+  \min_{x\in Q_p}~f(x) &= \min_{x\in Q_p} |U^Tx|_1 + \alpha_v|D_vx|_1 + \alpha_h|D_hx|_1  \label{op:bp_tv}
+  % \text{subject to} &\, \| R x - y \|_2 < \sigma,
+\end{align}
+where ${D_v x=\text{vec}(\nabla_v X)}$ (resp., ${D_v x=\text{vec}(\nabla_v X)}$) is the
+discrete gradient in the vertical (resp., horizontal) direction and
+\begin{align*}
   (\nabla_v X)_{i,j} = 
@@
     0, & \phantom{:}i=h,~\phantom{:::::} 1\leq j\leq s.
+  \end{cases}\\
+  (\nabla_h X)_{i,j} = 
+  \begin{cases}
+    X_{i,j+1} - X_{i,j}, & 1\leq i\leq h,~1\leq j<s \\
+    0, & \phantom{}1\leq i\leq,~\phantom{:::} j=s
   \end{cases}
+\end{align*}
+In \eqref{op:bp_tv}, $\left \| D_v x \right \|_1$ (resp., $\left \| D_h x \right \|_1$) is the total variation (TV) of the signal in the vertical (resp., horizontal) direction.
+The parameters $\alpha_v$ and $\alpha_h$ are weighting parameters.
+The description of BPVV in \eqref{op:bp_tv} can be viewed as the combination of CS
+and inpainting (described below), in which the first term seeks a sparse solution while the
+last two terms try to diffuse pixel information.
+To solve the optimization problem in \eqref{op:bp_tv} we use a (slight) extension to NESTA~\cite{becker_nesta_2011}. To that end, we re-write the cost $f(x)$ in \eqref{op:bp_tv} as
+\begin{equation*}
+  f(x) = \max_{u\in Q_d} \left\langle u, Wx \right\rangle,\quad Q_d = \{u:~||u||_{\infty} \leq 1\}
+\end{equation*}
+where 
+\begin{equation*}
+W = \begin{bmatrix}U&\alpha_hD^T_h&\alpha_vD^T_v \end{bmatrix}^T.
+%   W = \begin{bmatrix}U^T\\\alpha_hD_h\\\alpha_vD_v \end{bmatrix}.
+\end{equation*}
+One of the core features of the NESTA algorithm is to replace the non-smooth functional $f(x)$ with a smoothed approximation
+\begin{equation}
+  f_{\mu} = \max_{u\in Q_d} \left\langle u,
+    W x \right\rangle - \frac{\mu}{2}||u||_2^2. \label{eqn:fcn_prox}
 \end{equation}
+The gradient of \eqref{eqn:fcn_prox} is given by
+\begin{equation*}
+  \nabla f_{\mu}(x)[i] = W^Tu_{\mu}(x)
+\end{equation*}
+where
+\begin{equation*}
+  (u_{\mu}(x))[i] = 
+\begin{cases}
+    \mu^{-1}(Wx)[i], & |W x[i]| < \mu,\\
+    \text{sgn}(W x[i]), & \text{else}.
+  \end{cases}
+\end{equation*}
 
@@
 
-  \Initialize{$x = d_y = w = b_y = b_w = k = 0$, $y_0=y$ sampled pixels}
-  \While{$\left \|\Phi x^k - y^k \right \|_2 \ge \sigma$} {
+  \Initialize{$x \in Q_p, \mu=0.9||W x_0||_{\infty}$, $L_{\mu} = \frac{1}{\mu}||W||^2_2$}
     % $x^{k+1} = x^{k}$\\
-    \For{$i= 1$ \KwTo $N$} {
-      $p\leftarrow\mu\Phi^Ty^k+\lambda\nabla_v^T\left(d_y-b_y\right)+\gamma\Psi\left(w-b_w\right)$\\
-      $x^{k+1}\leftarrow \left(\mu\Phi^{T}\Phi+\lambda\nabla_v^T\nabla_v+\gamma I\right)^{-1}p$\\
-      $d_y\leftarrow \text{shrink}(\nabla_vx^{k+1}+b_y,1/\lambda)$\\
-      $w\leftarrow \text{shrink}\left(\Psi^{-1}x^{k+1}+b_w,1/\gamma\right)$\\
-      $b_y\leftarrow b_y+\left(\nabla_vx^{k+1}-d_y\right)$\\
-      $b_w\leftarrow b_w+\left(\Psi^{-1}x^{k+1}-w\right)$\\
+  \While{$\mu < \mu_{\textrm{final}}$ } {
+    $k=0$\\
+      \While{$\Delta f_{\mu} > \delta$} {
+        $\alpha_k = \frac{1}{2}(k+1)$ \\
+        $\tau_k = \frac{2}{k+3}$ \\
+        $\displaystyle y_k = \text{arg } \min_{x\in Q_p}
+          \frac{L_{\mu}}{2}||x - x_k||_2^2 + \langle \nabla f(x_k),~ x\rangle$\\
+        $\displaystyle {z_k = \text{arg } \min_{x\in Q_p} \frac{L_{\mu}}{2}||x-x_0||_2^2 +
+        \langle \sum_{i=0}^k \alpha_i \nabla f(x_i), ~x \rangle}$\\
+        $x_{k+1} = \tau_kz_k + (1-\tau_k)y_k$\\
+        $k \leftarrow k + 1$\\
       }
-    $y^{k+1} = y^k + y - \Phi x^{k+1}$\\
-    $k \leftarrow k + 1$\\
-  } \Output{Reconstruction $x^k$}
-  \caption{Split Bregman BPVV}
+      $x_0 = x_k$\\
+      $\mu = \gamma \mu$\\
+      $L_{\mu} = (1/\mu)||W||^2_2$
+    }
+  \Output{Reconstruction $x_k$}
+  \caption{NESTA algorithm}
   \label{ag:BPTV}
 \end{algorithm}
-\todo{Modify this for NESTA}
-
-In \eqref{op:bp_tv}, $\left \| \nabla_v x \right \|_1$ is the total variation of
-the signal in the vertical direction and $\epsilon$ is a weighting parameter
-which in this work is taken to be unity. The description of BPVV in
-\eqref{op:bp_tv} can be viewed as the combination of CS and inpainting
-(described below), in which the first term seeks a sparse solution while the
-second term tries to diffuse pixel information. To solve the optimization
-problem in \eqref{op:bp_tv} we use the split Bregman method
-\cite{goldstein2009split}. The resulting algorithm is described in
-Algorithm~\ref{ag:BPTV} where $\mu, \lambda, \gamma$ are scalar penalty
-parameters that influence the convergence of the algorithm (though not the
-solution found) and
-\begin{equation}\label{df:shrink}
-  \text{shrink}(x,\gamma) = \frac{x}{|x|}\max\left(|x|-\gamma,0\right),
+In the termination condition for the inner loop, $\Delta f_{\mu} = |f_{\mu}(x_k) - \bar{f}_{\mu}(x_k)|/\bar{f}_{\mu}(x_k)$ where
+\begin{equation}
+\bar{f}_{\mu}(x_k) = \frac{1}{\min\{10, k\}} \sum_{\ell=1}^{\min\{10,k\}} f_{\mu}(x_{k-\ell})
 \end{equation}
-where all operations are element-wise.
+The sub-problems in lines 6 and 7 have the form
+\begin{equation}
+  p = \textrm{arg } \min_{x\in Q_p} \frac{L}{2}||x - r|| + \langle g,~x - r\rangle
+\end{equation}
+for some vectors $g$ and $r$ and, as shown in~\cite{becker_nesta_2011}, have a closed-form solution given by
+\begin{align}
+  \lambda & = \textrm{max}(0, \sigma^{-1}\left| b - Rq\right| - L\\
+  q &= r - L^{-1}g\\
+  p &= \left(I - \frac{\lambda}{\lambda + L} R^TR\right)\left( \frac{\lambda}{L}R^Tb + q\right).
+\end{align}
 
@@
 
-One cause for such different gains is variation in the length of the cantilever
-(and possibly how the laser was adjusted). This is illustrated in
-Fig.~\ref{fig:z_axis_gain}. Here, we consider a cantilever with length $h$ that
-rests on the surface of some specimen with a nominal angle of $\theta$. In this
-drawing, the laser is perpendicular to the sample surface. Given a vertical
-perturbation $\Delta z$, we have that
-\begin{equation}
-  \Delta \alpha \approx \frac{d}{h} \Delta z,
-\end{equation}
-where $d$ is the distance from the cantilever to the detector and
-$\Delta \alpha$ is the change in position of the incident laser spot on the
-detector. Thus, given the same change in the vertical position, we will see a
-larger change in the deflection signal for a shorter cantilever. In other words,
-a short cantilever will exhibit a larger DC-gain in the $G_{u_Z,Z_d}$ transfer
-function.
-\begin{figure}
-  \begin{minipage}[t]{.46\textwidth}
-    % L B R T
-    \includesvg[width=1\textwidth]{figures/z_cant_evolution.svg}
-    \caption{FRFs of three different cantilevers, showing substantial
-      differences in the DC-gain and smaller, but still significant differences
-      the frequency of the modes.}
-    \label{fig:z_evolution}
-  \end{minipage}
-  \hfill
-  \begin{minipage}[t]{.46\textwidth}
-    % L B R T
-    \includegraphics[width=1\textwidth]{figures/z_axis_gain_schematic-crop.pdf}
-    \caption{Schematic drawing of how the length of the cantilever affects the
-      $z$-axis gain.}
-    \label{fig:z_axis_gain}
-  \end{minipage}
-\end{figure}
-
-Fig.~\ref{fig:z_evolution} shows the frequency response of $G_{u_Z,Z_d}$ near
-the bending mode for three different cantilevers. Cantilevers (A) and (B) are
-both AppNano SICON cantilevers and have a nominal length of 450 microns.
-Cantilever (C) is an NCLR and has a nominal length of 225 microns.
-Interestingly, the SICON cantilevers show substantial variation. Unfortunately,
-the manufacture does not provide a tolerance on the nominal length, so it is
-difficult to tease out whether that variation is due to manufacturing
-variability or other factors not explained by this analysis.
-
-Notably, the frequency of the pole and zero do appear to shift and our inversion
-scheme is not robust to this. To deal with this, I have built a (mostly)
-automated system ID routine into the imaging software. This routine is a
-specialized version of the techniques described previously in
-Chapter~\ref{chap:modeling}. First, it obtains an FRF of the bending mode over a
-frequency range spanning 180~Hz to 240~Hz (the same set of points as in
-Fig.~\ref{fig:z_evolution}). The input and output sinusoids are demodulated in
-quasi-realtime as they come off the FPGA. Once this is complete, a 2-pole,
-2-zero transfer function model of the form
-\begin{equation*}
-  \hat{D}(z) = k \frac{z^2 + b_1z + b_o}{z^2 + a_1z + a_o}
-\end{equation*}
-is fit to the FRF, using the same optimization scheme as \eqref{eqn:logfit}.
-This is done inside the LabView VI by calling a custom DLL, which leverages
-CMPFIT~\cite{cmpfit,markwardt_mpfit_2009}, a
-Levenberg-Marquardt~\cite{more_levenberg_1978} routine written in C. To promote
-a stable fit, the optimization enforces the necessary conditions that
-\begin{align*}
-  |a_1| &< 2, \quad  |a_o| < 1\\
-  |b_1| &< 2, \quad  |b_o| < 1.
-\end{align*}
-The routine then checks that both the poles and zeros are indeed stabile, saves
-the data to a JSON file and passes the transfer function parameters into the
-imaging portion of the application which finally uploads the parameters into the
-FPGA imaging bitfile. Optionally, one can by-pass this step and simply load the
-previously saved JSON file.
-
-One of the benefits of this approach is that the DC-gain of the transfer
-function $G_{u_Z,Z_d}$ becomes (approximately) normalized to unity, which makes
-re-tuning the control system after changing tips far easier to non-existent. The
-benefit to automating the process is that it drastically reduces the friction
-required to obtain an up-to-date compensator, which means that an up-to-date
-compensator is more likely to be used~\cite{abramovitch_25years_2015}.
-
-Fig.~\ref{fig:afm_bd_dinv} shows a block diagram if the $Z$-axis control loop.
-We point out a small change from Chapter~\ref{chap:cs_init}: the addition of
-$D^{-1}(z)$ changes the correct signal to use to represent the sample surface.
-If we take the output of the entire compensator, $u_Z=D_ID^{-1}e_z$, then we
-will get a lot of wiggles in the resulting signal. Rather, we need to take only
-the output of the integrator to represent the surface.
+\begin{figure*}
+  \centering
+  \includesvg[width=1\textwidth]{figures/MIMO_CL_uxuy.svg}
+  \caption{MIMO closed and open loop FRFs, showing the dramatic affect on $G_{Z,u_X}$ and $G_{Z,u_Y}$ when the feedforward compensators are used for the $X$ and $Y$ axes.}
+  \label{fig:mimo_frf_uxuy}
+\end{figure*}
+
+% One cause for such different gains is variation in the length of the cantilever
+% (and possibly how the laser was adjusted). This is illustrated in
+% Fig.~\ref{fig:z_axis_gain}. Here, we consider a cantilever with length $h$ that
+% rests on the surface of some specimen with a nominal angle of $\theta$. In this
+% drawing, the laser is perpendicular to the sample surface. Given a vertical
+% perturbation $\Delta z$, we have that
+% \begin{equation}
+%   \Delta \alpha \approx \frac{d}{h} \Delta z,
+% \end{equation}
+% where $d$ is the distance from the cantilever to the detector and
+% $\Delta \alpha$ is the change in position of the incident laser spot on the
+% detector. Thus, given the same change in the vertical position, we will see a
+% larger change in the deflection signal for a shorter cantilever. In other words,
+% a short cantilever will exhibit a larger DC-gain in the $G_{u_Z,Z_d}$ transfer
+% function.
 % \begin{figure}
+%   \begin{minipage}[t]{.46\textwidth}
+%     % L B R T
+%     \includesvg[width=1\textwidth]{figures/z_cant_evolution.svg}
+%     \caption{FRFs of three different cantilevers, showing substantial
+%       differences in the DC-gain and smaller, but still significant differences
+%       the frequency of the modes.}
+%     \label{fig:z_evolution}
+%   \end{minipage}
+%   \hfill
+%   \begin{minipage}[t]{.46\textwidth}
+%     % L B R T
+%     \includegraphics[width=1\textwidth]{figures/z_axis_gain_schematic-crop.pdf}
+%     \caption{Schematic drawing of how the length of the cantilever affects the
+%       $z$-axis gain.}
+%     \label{fig:z_axis_gain}
+%   \end{minipage}
+% \end{figure}
+
+% Fig.~\ref{fig:z_evolution} shows the frequency response of $G_{u_Z,Z_d}$ near
+% the bending mode for three different cantilevers. Cantilevers (A) and (B) are
+% both AppNano SICON cantilevers and have a nominal length of 450 microns.
+% Cantilever (C) is an NCLR and has a nominal length of 225 microns.
+% Interestingly, the SICON cantilevers show substantial variation. Unfortunately,
+% the manufacture does not provide a tolerance on the nominal length, so it is
+% difficult to tease out whether that variation is due to manufacturing
+% variability or other factors not explained by this analysis.
+
+% Notably, the frequency of the pole and zero do appear to shift and our inversion
+% scheme is not robust to this. To deal with this, I have built a (mostly)
+% automated system ID routine into the imaging software. This routine is a
+% specialized version of the techniques described previously in
+% Chapter~\ref{chap:modeling}. First, it obtains an FRF of the bending mode over a
+% frequency range spanning 180~Hz to 240~Hz (the same set of points as in
+% Fig.~\ref{fig:z_evolution}). The input and output sinusoids are demodulated in
+% quasi-realtime as they come off the FPGA. Once this is complete, a 2-pole,
+% 2-zero transfer function model of the form
+% \begin{equation*}
+%   \hat{D}(z) = k \frac{z^2 + b_1z + b_o}{z^2 + a_1z + a_o}
+% \end{equation*}
+% is fit to the FRF, using the same optimization scheme as \eqref{eqn:logfit}.
+% This is done inside the LabView VI by calling a custom DLL, which leverages
+% CMPFIT~\cite{cmpfit,markwardt_mpfit_2009}, a
+% Levenberg-Marquardt~\cite{more_levenberg_1978} routine written in C. To promote
+% a stable fit, the optimization enforces the necessary conditions that
+% \begin{align*}
+%   |a_1| &< 2, \quad  |a_o| < 1\\
+%   |b_1| &< 2, \quad  |b_o| < 1.
+% \end{align*}
+% The routine then checks that both the poles and zeros are indeed stabile, saves
+% the data to a JSON file and passes the transfer function parameters into the
+% imaging portion of the application which finally uploads the parameters into the
+% FPGA imaging bitfile. Optionally, one can by-pass this step and simply load the
+% previously saved JSON file.
+
+% One of the benefits of this approach is that the DC-gain of the transfer
+% function $G_{u_Z,Z_d}$ becomes (approximately) normalized to unity, which makes
+% re-tuning the control system after changing tips far easier to non-existent. The
+% benefit to automating the process is that it drastically reduces the friction
+% required to obtain an up-to-date compensator, which means that an up-to-date
+% compensator is more likely to be used~\cite{abramovitch_25years_2015}.
+
+% Fig.~\ref{fig:afm_bd_dinv} shows a block diagram if the $Z$-axis control loop.
+% We point out a small change from Chapter~\ref{chap:cs_init}: the addition of
+% $D^{-1}(z)$ changes the correct signal to use to represent the sample surface.
+% If we take the output of the entire compensator, $u_Z=D_ID^{-1}e_z$, then we
+% will get a lot of wiggles in the resulting signal. Rather, we need to take only
+% the output of the integrator to represent the surface.
+% % \begin{figure}
+% %   \centering
+% %   \includegraphics[width=1\columnwidth]{figures/AFM_loop_Dinv-crop.pdf}
+% %   \caption{Block diagram of the $Z$-axis control loop with the inverse
+% %   compensator. }
+% %   \label{fig:afm_bd_dinv}
+% % \end{figure}
+% \begin{figure*}[t]
 %   \centering
-%   \includegraphics[width=1\columnwidth]{figures/AFM_loop_Dinv-crop.pdf}
-%   \caption{Block diagram of the $Z$-axis control loop with the inverse
-%   compensator. }
-%   \label{fig:afm_bd_dinv}
-% \end{figure}
-\begin{figure*}[t]
-  \centering
-  \includegraphics[width=0.75\textwidth]{figures/AFM_loop_Dinv_antiwup-crop.pdf}
-  \caption{Block diagram of the $Z$-axis control loop. The anti-windup is active
-    for decision index $i\in\{0,1,5\}$, which correspond to states such that
-    $r_Z=r_{Z,\textrm{up}}$.}
-  \label{fig:afm_bd_dinv_final}
-\end{figure*}
-
-It should be noted that this control is sufficient to eliminate the limit-cycle
-behavior described in Section~\ref{sec:aproachspeed}:
-
-% \begin{figure}[tbhp!]
-%   \centering\includegraphics[width=3.0in]{figures-SBA/uz_multiplexer_KI_anderssonLab2}
-%   \caption{The $z$-piezo movement is driven by switching between feedback from
-%   the $z$-axis position signal and from the deflection signal. The shaded area
-%   represents the digital control system, while the non-shaded region is the
-%   physical system.}
-%   \label{fig:zMultiplex_anderssonLab}
-% \end{figure}
-
-As illustrated in Fig.~\ref{fig:zMultiplex_anderssonLab}, the voltage applied to
-the $z$-piezo is adjusted by switching the feedback signal between the $z$-axis
-position sensor (when the tip is off the surface) and the deflection signal
-(when the tip is engaged). The difference equation associated with
-\eqref{eqn:dzI} for the $z$-axis is
-\begin{equation}
-  u_z(k) = K_Ie(k) + u_z(k-1).
-  \label{eqn:intdiff}
-\end{equation}
-
-In the $z$-axis position control mode, the $z$-axis position is controlled to a
-fixed value $z_{ref}$ which, in general, is slightly above the sample surface.
-The difference between the measured $z$-axis position and $z_{ref}$,
-${e(k) = z_{ref} - z(k)}$, is used as the error signal. In the deflection
-control mode, when the tip is in contact with the sample, the deflection signal
-is controlled to a fixed value $l_{ref}$ to ensure a constant tip-sample force.
-The sample surface acts as a disturbance to the control loop. Therefore, the
-$z$-axis position measurements can be taken to represent the surface topography
-of the sample. In this case, the difference between the measured deflection and
-$l_{ref}$ is the error, $e(k) = l_{ref} - l(k)$.
-
-We note that the $z$-axis control described here operates the AFM in constant
-force mode during imaging. It is straightforward to perform scanning under
-different AFM modes, such as tapping mode, simply by adjusting the signals and
-control involved in the vertical loop.
+%   \includegraphics[width=0.75\textwidth]{figures/AFM_loop_Dinv_antiwup-crop.pdf}
+%   \caption{Block diagram of the $Z$-axis control loop. The anti-windup is active
+%     for decision index $i\in\{0,1,5\}$, which correspond to states such that
+%     $r_Z=r_{Z,\textrm{up}}$.}
+%   \label{fig:afm_bd_dinv_final}
+% \end{figure*}
+
+% It should be noted that this control is sufficient to eliminate the limit-cycle
+% behavior described in Section~\ref{sec:aproachspeed}:
+
+% % \begin{figure}[tbhp!]
+% %   \centering\includegraphics[width=3.0in]{figures-SBA/uz_multiplexer_KI_anderssonLab2}
+% %   \caption{The $z$-piezo movement is driven by switching between feedback from
+% %   the $z$-axis position signal and from the deflection signal. The shaded area
+% %   represents the digital control system, while the non-shaded region is the
+% %   physical system.}
+% %   \label{fig:zMultiplex_anderssonLab}
+% % \end{figure}
+
+% As illustrated in Fig.~\ref{fig:zMultiplex_anderssonLab}, the voltage applied to
+% the $z$-piezo is adjusted by switching the feedback signal between the $z$-axis
+% position sensor (when the tip is off the surface) and the deflection signal
+% (when the tip is engaged). The difference equation associated with
+% \eqref{eqn:dzI} for the $z$-axis is
+% \begin{equation}
+%   u_z(k) = K_Ie(k) + u_z(k-1).
+%   \label{eqn:intdiff}
+% \end{equation}
+
+% In the $z$-axis position control mode, the $z$-axis position is controlled to a
+% fixed value $z_{ref}$ which, in general, is slightly above the sample surface.
+% The difference between the measured $z$-axis position and $z_{ref}$,
+% ${e(k) = z_{ref} - z(k)}$, is used as the error signal. In the deflection
+% control mode, when the tip is in contact with the sample, the deflection signal
+% is controlled to a fixed value $l_{ref}$ to ensure a constant tip-sample force.
+% The sample surface acts as a disturbance to the control loop. Therefore, the
+% $z$-axis position measurements can be taken to represent the surface topography
+% of the sample. In this case, the difference between the measured deflection and
+% $l_{ref}$ is the error, $e(k) = l_{ref} - l(k)$.
+
+% We note that the $z$-axis control described here operates the AFM in constant
+% force mode during imaging. It is straightforward to perform scanning under
+% different AFM modes, such as tapping mode, simply by adjusting the signals and
+% control involved in the vertical loop.
 

### 2019-05-25 latex/afm-cs-main.tex
Add todos, comment stuff out.

@@
 \end{equation}
-\noindent where $y\in\mathbb{R}^m$ is the observation vector, $R$ is an
-$m\times n$ matrix defining the measurements, $U$ is an $n\times n$ sparsity
+\noindent where $y\in\mathbb{R}^n$ is the observation vector, $R$ is an
+$n\times m$ matrix defining the measurements, $U$ is an $m\times m$ sparsity
 basis and $\eta$ is the sparse representation of $x$ in the domain of $U$. In
-general, $m\ll n$. In an imaging application, where the underlying signal is a
+general, $n\ll m$. In an imaging application, where the underlying signal is a
 matrix $X\in\mathbb{R}^{h\times s}$, we take $x=\text{vec}(X)$, where the
@@
 
-The symbols $x$ and $y$ are also used to indicate coordinate directions in the AFM.
-They are reused here as they are standard notation in the CS literature; their
-specific meaning throughout the paper should be clear from context.
-
 In the AFM application, the probe can only measure a single pixel at a time.
-This implies that $R$ is a sparse matrix with each row having only one
-nonzero entry and that $y$ is a subset of $x$. Ideally, the sparsity basis and
-the measurement matrix $U$ will have a low \textit{mutual coherence}, a
+Thus the rows of $R$ are a subset of the rows of an $m$ by $m$ identity matrix.
+Ideally, the sparsity basis and
+the measurement matrix $R$ will have a low \textit{mutual coherence}, a
 measure that describes how each of the rows of $R$ (the measurements)
@@
 
-One common realization of the CS-based reconstruction problem, known as basis
-pursuit with denoising (BPDN), is given by the following optimization problem,
+Basis pursuit with denoising (BPDN) is one common realization of the CS-based
+reconstruction problem, and is given by the optimization
 \begin{equation}
@@
 \end{equation}
-  where $\| \cdot \|_1$ and $\| \cdot \|_2$ denote $l_1$ and $l_2$ norms,
-respectively, and $\sigma$ represents some measure of the signal noise such as
-its variance. This problem essentially searches for the sparsest signal from all
-the candidates that match the measurements. While BPDN is a computationally
-demanding algorithm, particularly for large images, it in general provides
-accurate reconstructions.
+where $\sigma$ represents uncertainty in the measurements. BPDN
+essentially searches for the sparsest signal from all
+the candidates that match the measurements.
 
@@
 \end{align*}
+\todo{This is way too long}
 In \eqref{op:bp_tv}, $\left \| D_v x \right \|_1$ (resp., $\left \| D_h x \right \|_1$) is the total variation (TV) of the signal in the vertical (resp., horizontal) direction.
@@
     \textit{\small original image} & \textit{\small BPDN} & \textit{\small BPVV} & \textit{\small detail of original} & \textit{\small detail of BPDN} & \textit{\small detail of BPVV} \\
-    \includegraphics[width=0.16\textwidth]{figures-SBA/circulargrating_gt_framed}
-                                   & \includegraphics[width=0.16\textwidth]{figures-SBA/circulargrating_40mu}		
-                                                          & \includegraphics[width=0.16\textwidth]{figures-SBA/circulargrating_bptv_40mu}
-                                                                                 & \includegraphics[width=0.16\textwidth]{figures-SBA/circulargrating_gt_zoomin}
-                                                                                                                      & \includegraphics[width=0.16\textwidth]{figures-SBA/circulargrating_mu40_zoomin}
-                                                                                                                                                       & \includegraphics[width=0.16\textwidth]{figures-SBA/circulargrating_bptv_40mu_zoomin}\\
+    % \includegraphics[width=0.16\textwidth]{figures-SBA/circulargrating_gt_framed}
+    %                                & \includegraphics[width=0.16\textwidth]{figures-SBA/circulargrating_40mu}		
+    %                                                       & \includegraphics[width=0.16\textwidth]{figures-SBA/circulargrating_bptv_40mu}
+    %                                                                              & \includegraphics[width=0.16\textwidth]{figures-SBA/circulargrating_gt_zoomin}
+    %                                                                                                                   & \includegraphics[width=0.16\textwidth]{figures-SBA/circulargrating_mu40_zoomin}
+    %                                                                                                                                                    & \includegraphics[width=0.16\textwidth]{figures-SBA/circulargrating_bptv_40mu_zoomin}\\
     \includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_gt_framed}
@@
 \end{figure*}
+\todo{Re-do this figure???}
 \endgroup
@@
 Our experimental setup, illustrated in Fig.~\ref{fig:exp_setup_anderssonLab},
-consists of an Agilent 5500 AFM, a cRIO-9082 embedded controller (National
+consists of an Agilent 5400 AFM, a cRIO-9082 embedded controller (National
 Instruments), and a standard desktop computer. Through a breakout box, the
@@
 control box allows control of the $x$, $y$, and $z$-axis piezos. The N9524A
-piezoelectric scanner in the Agilent 5500 provides a maximum scan area of
+piezoelectric scanner in the Agilent 5400 provides a maximum scan area of
 $90~\mu$m $\times$ 90~$\mu$m in the $xy$ (horizontal) direction and a range of
@@
 
-TKTKT add stuff about nPoint stage and C300.
+\todo{ add stuff about nPoint stage and C300.}
 
@@
   FPGA is enabled and the system performs the following operations.
+    \todo{Shorten this. Sean, what was your trick to not indent enumerate?}
   \begin{itemize}
@@
 
-% \begin{figure}[htbp!]
-%   \centering
-%     %   \includegraphics[width=3.0in]{figures-SBA/mupathsignaltrajectory}
-%   \includegraphics[width=3.0in]{figures-SBA/mupathsignaltrajectory-swapped}
-%   \caption{Two cycles of the $\mu$-path scanning process. The top two plots
-%   are the lateral motion of the stage, the third is the $z$-sensor signal, and
-%   the bottom is the deflection signal. Each stage of the state machine is
-%   indicated by color.}
-%   \label{fig:mupathsignaltrajectory}
-% \end{figure}
-
-% The first section discusses several modifications (i.e., differences to
-% Chapter~\ref{chap:cs_init}) to the CS-scanning cycle. Section
-% \ref{sec:post_process} discusses the post-processing techniques used. Section
-% \ref{sec:rdi} develops a new metric to compare the relative damage done by
-% different scans and Section~\ref{sec:psnr_ssim_limits} takes a closer look at
-% the SSIM and PSNR metrics in an effort to understand what ''reasonable''
-% numbers look like for AFM images taken with our AFM. Similarly,
-% Section~\ref{sec:cs_sim} looks at some CS simulations (based on real raster
-% scans) to help us understand what, ideally, we should see from the experiments
-% performed in Section~\ref{sec:results:final}.
-
 % Several cycles of the CS-scheme are shown in
@@
 % more fully in the following three subsections.
+
 \begin{figure*}[ht!]
@@
 \end{figure*}
-
-% \begin{figure*}
-%   \centering
-%   \includesvg[width=.9\textwidth]{figures/state-machine-final.svg}
-%   \caption{Diagram of the state-machine implemented in the final design.}
-%   \label{fig:sm_final}
-% \end{figure*}
+\todo{Make fig \ref{fig:mupathsignaltrajectory}  smaller}
 
 \subsection{Cantilever does not need to fully disengage.}
+\todo{Dramatically truncate this section}
 In the initial implementation, we insisted that the during tip-retraction
@@
 
-\begin{figure}[ht!]
-  \begin{subfigure}{.48\textwidth}
-    \includesvg[width=1\textwidth]{figures/justify_small_lift.svg}
-    \caption{ }
-    % \label{fig: }
-  \end{subfigure}
-  \begin{subfigure}{.48\textwidth}
-    \includesvg[width=01\textwidth]{figures/justify_small_lift_zoom.svg}
-    \caption{ }
-    % \label{fig: }
-  \end{subfigure}
-  \caption{One CS-cycle with different dis-engagement heights. (a) Full view.
-    (b) Zoomed-in view. Note the drift transient in the left panel of (b). }
-  \label{fig:z_drift}
-\end{figure}
+% \begin{figure}[ht!]
+%   \begin{subfigure}{.48\textwidth}
+%     \includesvg[width=1\textwidth]{figures/justify_small_lift.svg}
+%     \caption{ }
+%     % \label{fig: }
+%   \end{subfigure}
+%   \begin{subfigure}{.48\textwidth}
+%     \includesvg[width=01\textwidth]{figures/justify_small_lift_zoom.svg}
+%     \caption{ }
+%     % \label{fig: }
+%   \end{subfigure}
+%   \caption{One CS-cycle with different dis-engagement heights. (a) Full view.
+%     (b) Zoomed-in view. Note the drift transient in the left panel of (b). }
+%   \label{fig:z_drift}
+% \end{figure}
 
@@
 
-% \subsection{Dynamic de-trending}
-% Because our AFM is not equipped with a $Z$-axis sensor, it is important to
-% remove as much drift as possible from the $u_Z$ control signal, otherwise,
-% this slow dynamic will corrupt the final image. This can partly be achieved by
-% doing an image after the AFM has been on for a long time, e.g., 20 minutes,
-% and especially after taking several slow raster scans. We can also remove some
-% of the drift by fitting a curve
-% \begin{equation}
-%   d_k = \alpha + \beta t_k + \gamma \log\left(\frac{t_k}{0.1}\right)
-% \end{equation}
-% where $t_k$ is the time at the $k$-th sampling period and $\alpha$, $\beta$,
-% and $\gamma$ are the parameters to be fit. This is a combination of a
-% time-domain drift model \cite{Jung_open_loop_2000} and a linear fit which
-% accounts for sample tilt. This line is fit to the entire set of $u_Z$ control
-% data and subtracted.
-
-\subsection{CS-reconstruction}\label{sec:tv_denoise}
-Some of the noise in an image reconstructed via BPDN can be reduced by solving a
-Total Variation (TV) de-noising optimization problem
-\begin{equation}
-  \min_{U} ||\nabla_xU||_1 + ||\nabla_yU||_1 + \mu||F - U||_2 \label{eqn:breg1}
-\end{equation}
-where $F$ is the image produced by the BPDN optimization and $U$ is the
-de-noised image. This idea was heavily inspired by Yufan Luo's approach
-\cite{luo_mupath_2019}. The difference is that (i) I do this for both $\nabla_x$
-and $\nabla_y$, where he only does it for $\nabla_y$ and (ii) that he does it in
-a single optimization which combines \eqref{eqn:breg1} with BPDN while I do it
-in two separate optimizations. The optimization is solved using the Split
-Bregman technique described in \cite{goldstein_splitbregman_2009} and my
-implementation is publicly available \cite{L1c}.
-
 \section{A New Metric}\label{sec:rdi}
@@
     CS-20NG grating. All images are 512$\times$512 pixels. The rows of pixels
-    indicated by the red line are shown in \ref{fig:pixel_rows}.}
+    indicated by the red line are shown in Fig.~\ref{fig:pixel_rows}.}
   \label{fig:resultsF1_images}

### 2019-05-28 latex/afm-cs-main.tex
Streamline latex. svg-inkscape should not be part of repo.

@@
-\documentclass[twocolumn,twoside]{IEEEtran/IEEEtran}
+\documentclass[twocolumn,oneside]{IEEEtran/IEEEtran}
 % \documentclass[defaultstyle,11pt]{IEEETran}
@@
 % \renewcommand*\textfraction{.05}
+\usepackage{showframe}
 \usepackage{amssymb}		% to get all AMS symbols
@@
 
+\newcommand{\rzup}{\ensuremath{r_{z,\textrm{up}}}\xspace}
+\newcommand{\rzs}{\ensuremath{r_{z,\textrm{s}}}\xspace}
+
+% *******************************************************************************
+% This artificially increases the papersize and margins, so todo notes are legible.
+% ***************** WARNING: comment this out for final version. ****************
+\usepackage[paperwidth=734.295pt, textwidth=516pt,
+            marginparsep=5pt, hoffset=10pt, marginparwidth=90pt,
+            textheight=696pt]{geometry}
+% Use layouts to display the original dimensions, so we can get as close to that as possible with
+% our fake page size.
 \usepackage{layouts}
@@
 
-% this reveals that textwidth and linewidth are 6.5 inches,
-% and textheight is 9.1 inches.
+% *******************************************************************************
 
@@
   collections of short scans known as $\mu$--paths. Using a commercial AFM, we
-  acquire data on two different grating samples using two different sampling
-  approaches: randomly-placed $\mu-$paths and $\mu-$paths designed to minimize
-  the reconstruction error based on partial prior information about the spatial
-  frequency content in the sample image. Reconstructions are made from these
-  data using three approaches: (1) inpainting, an interpolation technique that
-  diffuses information from sampled locations into unsampled regions, (2)
-  basis-pursuit, a compressive sensing-based algorithm that seeks to minimize a
-  measure of sparsity in the underlying image, and (3) a new variant of basis
-  pursuit, Basis Pursuit Vertical Variation (BPVV), that is designed to reduce
+  acquire data on a grating sample.
+  %using two different sampling
+  %approaches: randomly-placed $\mu-$paths and $\mu-$paths designed to minimize
+  %the reconstruction error based on partial prior information about the spatial
+  %frequency content in the sample image.
+  Reconstructions are made from these data using
+  %three approaches: (1) inpainting, an interpolation technique that
+  %diffuses information from sampled locations into unsampled regions, (2)
+  %basis-pursuit, a compressive sensing-based algorithm that seeks to minimize a
+  %measure of sparsity in the underlying image, and (3)
+  a new variant of basis
+  pursuit, Basis Pursuit with Vertical Variation (BPVV), that is designed to reduce
   artifacts arising from the sampling pattern. The quality of the resulting
@@
   comparable imaging rates using both the peak signal-to-noise ratio and the
-  structured similarity index metric. These experiments demonstrate that at slow
+  structured similarity index metric
+  and a new metric we call the relative damage index.
+  \todo{Will this conclusion still hold?}
+  These experiments demonstrate that at slow
   scan rates, the $\mu-$path scheme produces similar image quality with
@@
 \section{Introduction}\label{sec:introduction}
+% textwidth: \printinunitsof{pt}\prntlen{\textwidth}
+
+% linewidth: \printinunitsof{pt}\prntlen{\linewidth}
+
+% paperwidth: \printinunitsof{pt}\prntlen{\paperwidth}
+
+% marginparwidth: \printinunitsof{pt}\prntlen{\marginparwidth}
+
+% marginsep: \printinunitsof{pt}\prntlen{\marginparsep}
+
+% textheight: \printinunitsof{pt}\prntlen{\textheight}
+
 The Atomic Force Microscope (AFM) is a powerful instrument capable of imaging
@@
 engagements. %Though the pattern is motivated from CS, it also works well in practice for inpainting reconstruction \cite{luo2015comparison}.
+\todo{Would be beneficial to shrink intro, if possible}
 
@@
 can achieve significant scanning time reduction while maintaining faithful image
-reconstruction \cite{maxwell2014compressed,Luo:2015tu,Braker:2018gi}. This paper
-builds upon that earlier work in several significant ways. First, we demonstrate
-performance using both randomly-placed $\mu-$paths and designed $\mu-$paths that
-are optimized to minimize the expected reconstruction error given some initial
-estimate of the frequency structure of the sample. These schemes are described
-in Sec. \ref{sec:samplingScheme}. We also introduce a new reconstruction
+reconstruction \cite{maxwell2014compressed,Luo:2015tu, braker_hardware_2018}. This paper
+builds upon that earlier work in several significant ways.
+% % ------------------ TKTKTKT ------------------
+% \todo{Strike this?}
+% First, we demonstrate
+% performance using both randomly-placed $\mu-$paths and designed $\mu-$paths that
+% are optimized to minimize the expected reconstruction error given some initial
+% estimate of the frequency structure of the sample. These schemes are described
+% in Sec. \ref{sec:samplingScheme}.
+% % --------------------------
+We also introduce a new reconstruction
 algorithm which is designed to minimize the artifacts arising from the structure
@@
 existing reconstruction methods through simulations in Sec.
-\ref{sec:reconstructionMethods}. We then demonstrate the entire scheme from
+\ref{sec:reconstructionMethods}.
+Section \ref{sec:control} describes improvements to the control algorithms compared to our preliminary implementation in ~\cite{braker_hardware_2018}.
+We then demonstrate the entire scheme from
 sampling through reconstruction using experiments on a commercial AFM (Agilent
@@
   portion of the implementation and image reconstruction described in this paper
-  can be found at \url{https://github.com/yufan88/}}. Experimental results with
-two different grating samples are provided in Sec.
-\ref{sec:experimentalResults}. Finally, we provide a few concluding remarks in
+  can be found at \url{https://github.com/rabraker/AFM_CS}}. Experimental results are provided in Sec.
+\ref{sec:results}. Finally, we provide a few concluding remarks in
 Sec. \ref{sec:conclusions}.
 
+\begin{figure}
+  \centering
+  \includegraphics[width=0.7\columnwidth]{figures-SBA/random_mask.pdf}
+  \caption{An example of the horizontal $\mu$-path sampling pattern for a 256$\times$256 pixel image with 35 pixels in each short scan and a total of 20\% pixels scanned.}
+  \label{fig:mu_mask}
+\end{figure}
 % =========================================================================
@@
 \label{sec:reconstructionMethods}
-
-In this work, we use three reconstruction algorithms to generate the final
-surface image. The first one comes from the field of compressive sensing (CS).
-CS is a signal processing technique which aims at signal reconstruction from a
+Compressive sensing (CS) is a signal processing technique which aims at signal reconstruction from a
 relatively small (sub-Nyquist limit) number of measurements
 \cite{carmi2014compressive}. It takes advantage of the approximate sparsity of
-real-world signals, that is, of the fact that many coefficients of such signals
+real-world signals, that is, that many coefficients of such signals
 are close to zero when represented in an appropriate basis. CS methods seek the
-true image signal $x\in\mathbb{R}^n$ from the following observation equation,
+true image signal $x\in\mathbb{R}^n$ from the observation equation,
 \begin{equation}\label{op:observation}
@@
 measure that describes how each of the rows of $R$ (the measurements)
-``spreads out'' in the domain of $U$ \cite{candes2007sparsity}. In practice,
-the Discrete Cosine Transform (DCT) keeps a good balance between achieving a low
-mutual coherence between the basis and the required structure of the AFM sensing
-matrices and providing a high sparsity of typical AFM sample images. In the following,
-we assume that $U^TU=I$, though in the simulation and experimental results, we take
-$U$ as the DCT basis.
+``spreads out'' in the domain of $U$ \cite{candes2007sparsity}.
+In the following, we assume that $U^TU=I$, though in the simulation and
+experimental results, we take $U$ as the Discrete Cosine Transform (DCT) basis.
+The DCT basis generally keeps a good balance between achieving a low
+mutual coherence between $U$ and the required structure of the AFM sensing
+matrices $R$ and providing a high sparsity of typical AFM sample images.
 
@@
 tip re-engagements and thus shorter scan times.
-As a result, the second
-algorithm we consider is a new variant of BPDN that we term basis pursuit with
-vertical variation (BPVV). In order to mitigate the vertical artifacts, BPVV
-adds a vertical total variation penalty in the spatial domain to the
+
+\todo{This development is way too long!}
+To mitigate these affects, we propose a new variant of BPDN that we term basis pursuit with
+vertical variation (BPVV). BPVV adds a vertical total variation penalty in the spatial domain to the
 optimization objective. That is, \eqref{op:bp} is modified to
-
+\todo{It has been my observation that some benefit is gained by including $D_h$, but weighting it less than $D_v$. Not sure if we should leave it in. If so, BPVV should be BPTV or something.}
 \begin{align}
-  \min_{x\in Q_p}~f(x) &= \min_{x\in Q_p} |U^Tx|_1 + \alpha_v|D_vx|_1 + \alpha_h|D_hx|_1  \label{op:bp_tv}
+  \min_{x\in Q_p}~f(x) &= \min_{x\in Q_p} \left\|U^Tx\right\|_1 + \alpha_v\left\|D_vx\right\|_1
+                         + \alpha_h\left\|D_hx\right\|_1  \label{op:bp_tv}
   % \text{subject to} &\, \| R x - y \|_2 < \sigma,
@@
 where ${D_v x=\text{vec}(\nabla_v X)}$ (resp., ${D_v x=\text{vec}(\nabla_v X)}$) is the
-discrete gradient in the vertical (resp., horizontal) direction and
-\begin{align*}
-  (\nabla_v X)_{i,j} = 
-  \begin{cases}
-    X_{i+1,j} - X_{i,j}, & 1\leq i<h,~ 1\leq j\leq s,\\
-    0, & \phantom{:}i=h,~\phantom{:::::} 1\leq j\leq s.
-  \end{cases}\\
-  (\nabla_h X)_{i,j} = 
-  \begin{cases}
-    X_{i,j+1} - X_{i,j}, & 1\leq i\leq h,~1\leq j<s \\
-    0, & \phantom{}1\leq i\leq,~\phantom{:::} j=s
-  \end{cases}
-\end{align*}
-\todo{This is way too long}
-In \eqref{op:bp_tv}, $\left \| D_v x \right \|_1$ (resp., $\left \| D_h x \right \|_1$) is the total variation (TV) of the signal in the vertical (resp., horizontal) direction.
+discrete gradient in the vertical (resp., horizontal) direction (see, e.g., \cite[Section 6.1,]{becker_nesta_2011}). 
+% and
+% \begin{align*}
+%   (\nabla_v X)_{i,j} = 
+%   \begin{cases}
+%     X_{i+1,j} - X_{i,j}, & 1\leq i<h,~ 1\leq j\leq s,\\
+%     0, & \phantom{:}i=h,~\phantom{:::::} 1\leq j\leq s.
+%   \end{cases}\\
+%   (\nabla_h X)_{i,j} = 
+%   \begin{cases}
+%     X_{i,j+1} - X_{i,j}, & 1\leq i\leq h,~1\leq j<s \\
+%     0, & \phantom{}1\leq i\leq,~\phantom{:::} j=s
+%   \end{cases}
+% \end{align*}
+Thus, in \eqref{op:bp_tv}, $\left \| D_v x \right \|_1$ (resp., $\left \| D_h x \right \|_1$) is the total variation (TV) of the signal in the vertical (resp., horizontal) direction.
 The parameters $\alpha_v$ and $\alpha_h$ are weighting parameters.
+
 The description of BPVV in \eqref{op:bp_tv} can be viewed as the combination of CS
-and inpainting (described below), in which the first term seeks a sparse solution while the
+and inpainting, in which the first term seeks a sparse solution while the
 last two terms try to diffuse pixel information.
+\todo{When written this way, it seems that BP+VV/TV can could also be interpreted in the frameowrk of overcomplete dictionaries?\cite{candes_redundant_2011}. }
 To solve the optimization problem in \eqref{op:bp_tv} we use a (slight) extension to NESTA~\cite{becker_nesta_2011}. To that end, we re-write the cost $f(x)$ in \eqref{op:bp_tv} as
@@
 \end{equation*}
-
+The optimization \eqref{op:bp_tv} may now be solved using Algorithm~\ref{ag:NESTA}.
+\todo{seems like a waste of space to reprint the algo, since its really no different than the reference}
 \begin{algorithm}
@@
   \caption{NESTA algorithm}
-  \label{ag:BPTV}
+  \label{ag:NESTA}
 \end{algorithm}
+
 In the termination condition for the inner loop, $\Delta f_{\mu} = |f_{\mu}(x_k) - \bar{f}_{\mu}(x_k)|/\bar{f}_{\mu}(x_k)$ where
@@
 \end{equation}
-The sub-problems in lines 6 and 7 have the form
-\begin{equation}
-  p = \textrm{arg } \min_{x\in Q_p} \frac{L}{2}||x - r|| + \langle g,~x - r\rangle
-\end{equation}
-for some vectors $g$ and $r$ and, as shown in~\cite{becker_nesta_2011}, have a closed-form solution given by
-\begin{align}
-  \lambda & = \textrm{max}(0, \sigma^{-1}\left| b - Rq\right| - L\\
-  q &= r - L^{-1}g\\
-  p &= \left(I - \frac{\lambda}{\lambda + L} R^TR\right)\left( \frac{\lambda}{L}R^Tb + q\right).
-\end{align}
+When $RR^T=I$, the sub-problems in lines 6 and 7 have a closed-form solution. Details can be found in~\cite{becker_nesta_2011}.
+
+% The sub-problems in lines 6 and 7 have the form
+% \begin{equation}
+%   p = \textrm{arg } \min_{x\in Q_p} \frac{L}{2}||x - r|| + \langle g,~x - r\rangle
+% \end{equation}
+% for some vectors $g$ and $r$ and, as shown in~\cite{becker_nesta_2011}, have a closed-form solution given by
+% \begin{align}
+%   \lambda & = \textrm{max}(0, \sigma^{-1}\left| b - Rq\right| - L\\
+%   q &= r - L^{-1}g\\
+%   p &= \left(I - \frac{\lambda}{\lambda + L} R^TR\right)\left( \frac{\lambda}{L}R^Tb + q\right).
+% \end{align}
 
@@
 A comparison between BPDN and BPVV is shown in
-Fig.~\ref{fig:BPTV_demonstration}. Images of three different samples (a circular
-grating, a square grating and a DNA image) were acquired using an Agilent 5500
+Fig.~\ref{fig:BPTV_demonstration}. Images of two different samples
+(a square grating and a DNA image) were acquired using an Agilent 5500
 AFM with a standard raster scan (first and fourth columns in the figure). These
@@
 results show the artifacts apparent in the BPDN reconstruction are largely
-mitigated using BPVV.
+mitigated using BPVV. Thus, in the remainder of the paper, we focus exclusively on BPVV.
 
@@
 Our experimental setup, illustrated in Fig.~\ref{fig:exp_setup_anderssonLab},
-consists of an Agilent 5400 AFM, a cRIO-9082 embedded controller (National
-Instruments), and a standard desktop computer. Through a breakout box, the
-Agilent 5500 provides access to the $x$, $y$, and $z$-axis measurements as well
-as the deflection signal (denoted in the following as $l$). When the Agilent
-default software (PicoView) is set to open-loop mode, a $\pm 10$ V input on the
-control box allows control of the $x$, $y$, and $z$-axis piezos. The N9524A
-piezoelectric scanner in the Agilent 5400 provides a maximum scan area of
-$90~\mu$m $\times$ 90~$\mu$m in the $xy$ (horizontal) direction and a range of
-$20~\mu$m in the $z$ (vertical) direction. Initial engagement of the tip to the
+consists of an Agilent 5400 AFM  retrofitted with an nPoint NPXY100A
+piezoelectric stage, a cRIO-9082 embedded controller (National
+Instruments), and a standard desktop computer.
+
+Through a breakout box, the Agilent 5400 provides access to the $z$-axis deflection signal.
+When the Agilent software is set to open-loop mode, a $\pm10$~volt input on the standard control box allows control of the $z$-axis of the N9524a piezo scanner, which has a total range of 7 $\mu$m.
+Initial (course) engagement of the tip to the
 sample is performed using the PicoView software before control is handed over to
@@
 
-\todo{ add stuff about nPoint stage and C300.}
-
-All control logic is programmed using LabVIEW 2017 and compiled to a Xilinx
+All control logic is programmed using LabVIEW 2019 and compiled to a Xilinx
 Spartan-6 LX150 Field Programmable Gate Array (FPGA) inside the cRIO-9082. The
@@
 state space controller. It is described fully in \cite{braker_afmmpc_2019} and
-achieves a bandwidth of about 110 Hz, which is approximately 1/3 of the $X$-axis
+achieves a bandwidth of about 150 Hz, which is over 1/3 of the first $X$-axis
 resonance at 350 Hz.
 
-The control law used for the $Y$-axis is a simple integral controllers of the
+The control law used for the $Y$-axis is a simple PI controller of the
 form
@@
 \subsection{Z-axis Control Design}\label{sec:zaxis_cs_control}
-% In Section~\ref{sec:zaxis-dist}, we eliminated or reduced many of the
-% disturbances impinging on the $Z$-axis. This puts us in a position to
-% increase the bandwidth without introducing building dynamics into our
-% images.
 The main challenge to increasing the $Z$-axis bandwidth is the bending mode
@@
 Fig.~\ref{fig:z_control} (blue curve). We address this by inverting the complex
-pole-zero pair at 215 Hz. There are multiple advantages to this method: first,
+pole-zero pair at 215 Hz. Thus, the entire $Z$-axis controller consists of a PI
+controller, $D_I(z)$ cascaded with the resonance inversion, $D^{-1}(z)$, as shown in Fig.~\ref{fig:afm_bd_dinv}. The DC-gain
+of $D$ is (approximately) the same as the DC-gain of the plant.
+The inclusion of $D^{-1}$ allows us to substantially increase the PI gain and
+achieve a closed-loop bandwidth of about 480 Hz. This is the black curve in Fig.~\ref{fig:z_control}.
+
+There are multiple advantages to this method: first,
 an inverse compensator still makes sense as a feedforward, open-loop compensator
-if the feedback path is broken. This, situation can and does occur during parts
-of the CS cycle. Second, as we discuss further below, the inverse compensator
-requires no tuning as it is defined only by a fit to the measured FRF and this
-can be almost completely automated.
+if the feedback path is broken. This situation can and does occur during parts
+of the CS cycle. Second, the inverse compensator
+requires no tuning as it is defined only by a fit to the measured FRF.
+
+One challenge to the inversion approach is both the system gain and resonance at 215~Hz
+changes not only day-to-day but also (and especially) when changing cantilevers and our inversion is not robust to this.
+However, because $D^{-1}$ is defined purely by a second order fit to a small band of the FRF, updating the compensator can be automated.
+\todo{What else to say here?}
 
@@
   \includesvg[width=1\columnwidth]{figures/z_control_design.svg}
-  \caption{}
+  \caption{FRFs of the $Z$-axis. The blue curve is the open loop response from $u_Z$ to deflection. By inverting the bending mode at 215~Hz, we achieve the black curve in closed-loop.}
   \label{fig:z_control}
 \end{figure}
-The entire $Z$-axis controller consists of a PI controller, $D_I(z)$ cascaded
-with the resonance inversion, $D^{-1}(z)$. The inclusion of $D^{-1}$ allows us
-to substantially increase the PI gain and achieve a closed-loop bandwidth of
-about 480 Hz. This is the black curve in Fig.~\ref{fig:z_control}. For
-comparison, the red curve in Fig.~\ref{fig:z_control} shows the closed-loop FRF
-without the inverse compensator, which experiments indicate is unstable.
-
-One challenge to this approach is the system gain and resonance at 215~Hz
-changes not only day-to-day but also (and especially) when changing cantilevers.
-This is illustrated in Fig.~\ref{fig:z_evolution}, which shows the FRF near the
-mode for two three different cantilevers. Two are of the same make and model.
 
@@
   \label{fig:mimo_frf_uxuy}
+\end{figure*}
+
+\begin{figure*}[t]
+  \centering
+  \includegraphics[width=0.75\textwidth]{figures/AFM_loop_Dinv_antiwup-crop.pdf}
+  \caption{Block diagram of the $Z$-axis control loop. The anti-windup is active
+    for decision index $i\in\{0,1,5\}$, which correspond to states such that
+    $r_Z=\rzup$.}
+  \label{fig:afm_bd_dinv}
 \end{figure*}
@@
 
+\subsection{Feedforward Control}\label{sec:ff_control}
+In our AFM, there is a strong coupling between the horizontal axes and vertical deflection.
+Fig.~\ref{fig:mimo_frf_uxuy} shows a MIMO FRF for $u_X$ and $u_Y$ to the outputs in each axis.
+The dotted black curves are the open loop responses and the dashed red curves are the nominal closed-loop responses.
+Though the $Z$-direction inputs are not shown, the closed loop responses include the $Z$-axis controller.
+Note that, especially for $H_{z,u_X}$, the closed-loop response is barely improved over the open loop response and in particular, there is a sharp resonance at 215~Hz and 505~Hz.
+To deal with this, we employ two different strategies for CS and raster scanning.
+
+For raster scanning, we use a truncated Fourier series, where each Fourier coefficient is scaled by the inverse of the closed-loop FRF at the corresponding frequency.
+We truncate this series such that the highest frequency is smaller than 200 Hz.
+See, e.g., \cite{clayton_review_2009} for more details on this strategy.
+
+For CS scanning, we insert a feed-forward filter with two notches, one at 215~Hz and the other at 505~Hz.
+We design a similar feed-forward filter for the $Y$-axis.
+Both filters are shown in Fig.~\ref{fig:mimo_frf_uxuy} as the solid pink curves and the resulting overall FRF is shown as the solid blue curves.
+Particularly for $H_{z,u_X}$, these filters result in a dramatic reduction in the cross coupling.
+A similar affect could be achieve by using a simple low-pass filter.
+However, to achieve the same 40~dB of attenuation of the mode at 215 Hz, would require, e.g., that a two-pole LPF have its cut-off frequency at about 20~Hz.
+
 % =========================================================================
@@
 scan pattern. For our simple integral controller, this only involves changing
-the reference signals $x_{ref}$ and $y_{ref}$. In the $z$-direction, the system
+the reference signals $x_{ref}$ and $y_{ref}$.
+In the $z$-direction, the system
 must transition between tip descent, surface scanning, tip retraction, and
-maintaining a $z$-axis position. In addition, the $z$-piezo has to switch
-between position control and deflection control with two fixed reference values,
-$z_{ref}$ for position control and $l_{ref}$ for deflection control.
+maintaining a $z$-axis position.
 
 Transition between, and operation in, these different stages is implemented as a
-simple state machine. The $x$, $y$, and $z$-axis control loops are operating in
-parallel and independently. The state machine consists of the following states.
-
-\begin{enumerate}
-\item \textbf{Initialization:} In this state, the user uses the PicoView
-  software to bring the tip to the sample with the stepper motor. Once the tip
-  is engaged in the surface, the user switches the control from PicoView to the
-  custom software in LabView. The system writes parameters including the
-  locations of $\mu$-paths from a desktop file to a host-to-FPGA FIFO (first in,
-  first out) buffer. Next, the closed-loop control of all the axes through the
-  FPGA is enabled and the system performs the following operations.
-    \todo{Shorten this. Sean, what was your trick to not indent enumerate?}
-  \begin{itemize}
-  \item \textbf{Read} the starting location of the first $\mu$-path from the
-    host-to-FPGA FIFO.
-  \item \textbf{Set} the $z$-axis loop to position control mode.
-  \item \textbf{Wait until} $|e_z(k)|$ reaches a settling criterion, then go to
-    state 2.
-  \end{itemize}
-\item \textbf{$xy$-axis move:} The system moves the tip to the next target
-  location.
-  \begin{itemize}
-  \item \textbf{Set} $x_{ref}$ and $y_{ref}$ to the beginning of the $\mu$-path.
-  \item \textbf{Wait until} $|e_x(k)|$ and $|e_y(k)|$ reach a settling
-    criterion, then go to state 3.
-  \end{itemize}
-\item \textbf{Tip engage:} The system drives the tip towards the sample surface.
-  Here, we use a smaller $K_I$ for the $z$-piezo, which results in a slow
-  descent and less windup while the tip is out of contact.
-  \begin{itemize}
-  \item \textbf{Set} the $z$-axis loop to deflection control mode.
-  \item \textbf{Wait until} $|e_z(k)|$ reaches a settling criterion, then
-    transition to state 4. \todo{Update this}
-  \end{itemize}
-\item \textbf{Scan:} In this state, the system moves the tip following the
-  trajectory of the current $\mu$-path.
-  \begin{itemize}
-  \item \textbf{Update} $x_{ref}$, and $y_{ref}$ iteratively to follow the
-    trajectory of the current $\mu$-path to the end. At the same time, write the
-    $x,y,z,$ and deflection measurements to an FPGA-to-host FIFO.
-  \item \textbf{Wait until} $|e_x(k)|$ and $|e_y(k)|$ reach the end of the
-    $\mu$-path,
-    % a settling criterion,
-    then go to state 5.
-  \end{itemize}
-  % \item \textbf{Transition decision:} The tip is at the end of the $\mu$-path
-  %   at this time. The location of the next $\mu$-path is read from the FIFO.
-  %   In
-  %   order to accelerate the scanning process, the decision to lift the tip or
-  %   not is made in this state. The time $t_{xy\_scan}$ it takes to scan to the
-  %   beginning of the next $\mu$-path is compared to
-  %   $t_{\textit{z}up}+t_{xy}+t_{\textit{z}down}$. If the former is larger,
-  %   then
-  %   go to state 6; otherwise, go to state 2.
-\item \textbf{Tip withdraw:} In this state, the system withdraws the tip in the
-  $z$-direction. A large $K_I$ is used for the $z$-piezo here in order to save
-  time.
-  \begin{itemize}
-  \item \textbf{Set} the $z$-axis loop to position control mode.
-  \item \textbf{Set} the $z$ setpoint at a specified distance off the surface.
-  \item \textbf{Wait until} $|e_z(k)|$ reaches a settling criterion, then go to
-    state 2.
-  \end{itemize}
-\end{enumerate}
-
+simple state machine, summarized in Table~\ref{tab:cs_tasks}. 
+In the following, $r_X$ and $r_Y$ refer to the references for the $X$ and $Y$ axes while $r_{Z,s}$ and $\rzup$ refer to the $Z$-axis setpoints during scanning and retraction, respectively.
+
+\begin{table}\label{tab:cs_tasks}
+  \centering
+  \caption{Summary of the tasks for $\mu$-path scanning.}
+  \begin{tabular}{lccc}
+    state & $X$,$Y$ & $Z$ & next-state\\
+    \toprule
+    (1) $XY$-move & setpoint & $r_Z = \rzup$ & (2)\\
+    (2) tip-engage & setpoint & $r_Z = \rzs$ & (3)\\
+    (3) pre-scan & ramp & $r_Z = \rzs$ & (4)\\
+    (4) $\mu$-path scan & ramp & $r_Z = \rzs$ & (5)\\
+    (5) tip up & setpoint & $r_Z = \rzup$ & (1)\\
+  \end{tabular}
+\end{table}
 Two cycles of this sequential process are illustrated by the time series in
@@
 
-% Several cycles of the CS-scheme are shown in
-% Fig.~\ref{fig:mupathsignaltrajectory}. Each of these differences is discussed
-% more fully in the following three subsections.
-
-\begin{figure*}[ht!]
-  \centering \includesvg[scale=0.85]{figures/cs_cycle.svg}
+\begin{figure}[t!]
+  \centering
+  \includesvg[width=1\columnwidth]{figures/cs_cycle.svg}
   \caption{Several CS cycles. Each state is indicated by color.}
   \label{fig:mupathsignaltrajectory}
-\end{figure*}
-\todo{Make fig \ref{fig:mupathsignaltrajectory}  smaller}
+\end{figure}
 
@@
 \todo{Dramatically truncate this section}
-In the initial implementation, we insisted that the during tip-retraction
+In our initial implementation \cite{braker_hardware_2018}, we insisted that the during tip-retraction
 (state-5), the cantilever tip should fully break contact with the surface. Here,
@@
 (i.e., below the scanning setpoint), even while we run across the surface.
-
-\textbf{Motivation} The motivation for this is two-fold. First, there is the
-obvious advantage that, by not pulling the tip so away, there is less distance
-to recover during the re-engagement. The original idea was to pull away from the
-surface far enough to disengage, then step back down towards the surface by some
-fraction of the step up. This proved impractical for several reasons. First, it
-requires the control system to be able to detect when disengagement has
-occurred. While preliminary experiments indicate it may be possible to achieve
-this by detecting a change in the derivative of the deflection signal, the
-actual value of the control signal which achieved dis-engagement proved to be
-highly variable (ranging from about 0.6 v to over 3 volts (210 nanometers to
-over a micron)) and sometimes saturating the control signal without
-disengagement. Experiments indicate that the dis-engagement point depends on (at
-least) the tip condition and the cantilever spring constant \footnote{The
-  numbers cited used a cantilever with $k\approx .1$~N/m. Experiments using a
-  cantilever with $k\approx 50$ N/m yielded much more consistent and much
-  smaller needed dis-engagement control signals. However, cantilevers with such
-  large spring constants are tapping-mode cantilevers, a mode which our AFM is
-  incapable of. Scanning in contact mode with such a cantilever implies that a
-  very large force is being applied to the sample.}.
-
-Such large pull-away distances are problematic, especially for our AFM, which
-lacks a $Z$-position sensor. The difficulty is that when the tip is re-engaged
-with the sample from far away, this incites a large drift transient. This is
-shown in Fig.~\ref{fig:z_drift} under the panels labeled ``big lift''. By
-starting the re-engagement closer to the sample, this transient is much smaller.
-Without a $Z$-position sensor, we have to let this drift die out or it will
-corrupt the image. Thus, even if the step-up-down scheme could be made to work,
-the overall time would still be limited by this drift. I made some effort to fit
-an LTI model to the drift mode, so this affect could be removed in
-post-processing. Unfortunately, as we saw in
-Section~\ref{sec:modeling_remaining}, an LTI drift model does not adequately
-describe the drift transient, because the drift rate seems to depend on the
-control history.
-
-A third advantage is that, given the \emph{same} absolute starting height above
-the specimen, re-engagement is faster when the tip has not snapped free. The
-reason for this is that when the cantilever snaps away from the specimen
-surface, the deflection signal is essentially saturated. This gives the control
-loop an artificially small error signal, which leads to a very sluggish descent.
-
-\textbf{Justification} Ultimately the concern is damage to the sample and tip,
-which is caused by the force imparted by the cantilever probe
-\cite{clayton_review_2009}. The deflection signal, though un-calibrated (meaning
-it does not directly lead to a value in $kN$), is proportional to that force,
-because it is proportional to how much the cantilever is bent. I.e., a large
-(towards $+\infty$) deflection implies the spring force of the cantilever is
-pushing hard into the sample, thereby inducing damage. In a typical imaging
-scenario, we choose a deflection setpoint, (say $0.15$~[v], as in
-Fig.~\ref{fig:z_drift}), and have in some way decided that this is sufficient,
-all else being equal, to not damage things too much.
-
-Thus, rather than completely dis-engaging the tip from the surface, I propose to
-simply move the setpoint towards $-\infty$ during the $XY$-move. If this new
-setpoint is sufficiently far away, the deflection signal will stay below the
-scanning setpoint, which we had decided was a ''safe'' value. The change in
-setpoints is achieved via the multiplexer in Fig.~\ref{fig:afm_bd_dinv_final}
+We choose \rzup so that the interaction between the tip and sample becomes purely adhesive.
+In general, stable imaging in is not possible at \rzup and complete dis-engagement occasionally occurs.
+
+\todo{Not clear to me that friction is useful if I scan parallel to cantilever.
+Also not clear to me that the normal force and shear force are orthogonal concepts.
+Maybe the macroscopic analogy breaks down, but thinking of a knife pushed into a surface and then dragged...}
+
+The change in setpoints is achieved via the multiplexer in Fig.~\ref{fig:afm_bd_dinv}
 which selects either the scanning setpoint $r_{Z,s}$ or the retraction setpoint
 $r_{Z,\textrm{up}}$ based the current state.
-
-% \begin{figure}[ht!]
-%   \begin{subfigure}{.48\textwidth}
-%     \includesvg[width=1\textwidth]{figures/justify_small_lift.svg}
-%     \caption{ }
-%     % \label{fig: }
-%   \end{subfigure}
-%   \begin{subfigure}{.48\textwidth}
-%     \includesvg[width=01\textwidth]{figures/justify_small_lift_zoom.svg}
-%     \caption{ }
-%     % \label{fig: }
-%   \end{subfigure}
-%   \caption{One CS-cycle with different dis-engagement heights. (a) Full view.
-%     (b) Zoomed-in view. Note the drift transient in the left panel of (b). }
-%   \label{fig:z_drift}
-% \end{figure}
-
-This new scheme does not imply that the cantilever \emph{never} fully
-disengages. Occasionally, the new setpoint is far enough away that the probe
-does still snap away from the sample surface. When this happens, the integrator,
-$D_I(z)$, will windup. This happens because typically, the desired setpoint
-$r_{Z,\textrm{up}}$ is more negative than the free (disengaged) value of the
-deflection. Thus, the sensor signal is essentially saturated and no matter how
-far the $Z$-actuator tries to move, no change will result in the deflection,
-leading to windup and a control signal that exceeds the actuator bounds. To deal
-with this, we implement an anti-windup scheme for all states where
-$r_Z=r_{Z,\textrm{up}}$, i.e., states (0), (1) and (5). This is illustrated in
-the block diagram in Fig.~\ref{sec:modfied_cs_cycle}. During these states, the
-output of the accumulator is saturated before its own internal feedback.
+When dis-engagement does occur, the $Z$-axis control loop implements an anti-windup scheme.
+
+% Ultimately the concern is damage to the sample and tip,
+% which is caused by the force imparted by the cantilever probe
+% \cite{clayton_review_2009}. The deflection signal, though un-calibrated (meaning
+% it does not directly lead to a value in $kN$), is proportional to that force,
+% because it is proportional to how much the cantilever is bent. I.e., a large
+% (towards $+\infty$) deflection implies the spring force of the cantilever is
+% pushing hard into the sample, thereby inducing damage. In a typical imaging
+% scenario, we choose a deflection setpoint, (say $0.15$~[v], as in
+% Fig.~\ref{fig:z_drift}), and have in some way decided that this is sufficient,
+% all else being equal, to not damage things too much.
 
@@
 \end{figure*}
-After the tip-descent, we begin scanning in a ``pre-scan'' phase (state (3)). To
+After the tip-descent, we begin scanning in a ``pre-scan'' phase (state (3)).
+During this phase,
+
+To
 motivate, this consider Fig.~\ref{fig:prescan_difference}. The left panel
@@
 specialized CS pattern, where the $\mu$-paths are still 500 nm long, but the
-paths are separated by 0 pixels. In this case, the specimen is freshly cleaved
-mica. The goal here is to eliminate (i) any oscillations which arise from the
+paths are separated by 0 pixels.
+In this case, the specimen is freshly cleaved
+mica.
+The goal here is to eliminate (i) any oscillations which arise from the
 $XY$-move (which, as we will show in Section ~\ref{sec:need_mimo}, can be
@@
 there are as few disturbances as possible entering the control loop. Finally,
-the middle panel of Fig.~\ref{fig:prescan_difference} shows the PSDs of the left
+the left panel of Fig.~\ref{fig:prescan_difference} shows the PSDs of the left
 and right panels (but averaged over many similar cycles). Note that the PSD is
@@
 
-The tip settling (pre-scan) period could likely be much shorter if we a had a
-$Z$-axis position sensor. Part of the reason it is so long is that, despite not
-pulling the cantilever completely away from the sample, there is still a small
-drift transient, as can be seen Fig.~\ref{fig:uz_prescan}. We would like to at
-least give the major part of that drift transient time to die out. With a
-position sensor, we would not care about the drift transient: the control signal
-drifts to keep the $Z$-position constant.
-
-\section{Post-processing}\label{sec:post_process}
-Here, we discuss how we post-process the raster and CS images.
-
-\subsection{Aligning images via cross-correlation}\label{sec:align}
-To get metrics that are meaningful in any sense, we need the master image and
-the comparee to be aligned. We take two steps to help ensure this. First, during
-each batch of images, the nPoint stage remains under closed loop control.
-Between images, the FPGA control loop idles in state-0, as discussed above in
-Section~\ref{sec:idle_0}. This was not necessary duing the initial
-implementation because then, the nPoint stage was controlled by the nPoint PI
-controller. While this helps things substantially, there is still an alignment
-issue between subsequent images, which I believe stems from the original Agilent
-piezo tube, which is a three axis tube. The $XY$-axes of the tube are
-uncontrolled during imaging, and in fact, after a firmware ``upgrade'', the
-option to close the $XY$-loop has been grayed out in the PicoView software.
-
-To help deal with this, we compare sub-slices of the master image and the
-comparee. The results in this chapter use a sub-image obtained by removing a
-border of 25 pixels from each edge. Thus, for the purposes of comparison, the
-original 512$\times$512 pixel image becomes a 462$\times$462 pixel image. Let
-$X$ represent the original, master image and ${\tilde X=X_{25:-25, 25:-25}}$,
-using Python notation. To find the correct subslice of the comparee, we use a
-two dimensional cross-correlation, which is defined as
-\begin{equation}
-  Z_{k,\ell} = \sum_{m=0}^{M-1}\sum_{n=0}^{N-1} \tilde{X}_{m-k, n-\ell}Y_{m-k, n-\ell}.
-\end{equation}
-where $Y$ is the comparee.
-
-The index of the maximum value of the matrix $Z$
-\begin{equation}
-  (i^*,j^*) = \textrm{arg~} \max_{i,j}Z_{i,j}
-\end{equation}
-corresponds to the lower left corner of the correct subslice. Thus, the
-comparisons will computed against $\tilde{Y} = Y_{i^*:i^*+487, j^*:j^*+487}$.
-For an example of this in action, see the Fig.~\ref{fig:baseline_errors} in the
-next section.
-
-Unfortunately, the mis-alignment is not simply constant offset, but rather
-drifts over time. This can be seen, e.g., in Fig.~\ref{fig:rast_aligned_0p5}.
-Thus, while the technique described here mitigates the issue, it does not fully
-eliminate the problem.
-
-\section{A New Metric}\label{sec:rdi}
+% The tip settling (pre-scan) period could likely be much shorter if we a had a
+% $Z$-axis position sensor. Part of the reason it is so long is that, despite not
+% pulling the cantilever completely away from the sample, there is still a small
+% drift transient, as can be seen Fig.~\ref{fig:uz_prescan}. We would like to at
+% least give the major part of that drift transient time to die out. With a
+% position sensor, we would not care about the drift transient: the control signal
+% drifts to keep the $Z$-position constant.
+
+% \section{Post-processing}\label{sec:post_process}
+% Here, we discuss how we post-process the raster and CS images.
+
+% \subsection{Aligning images via cross-correlation}\label{sec:align}
+% To get metrics that are meaningful in any sense, we need the master image and
+% the comparee to be aligned. We take two steps to help ensure this. First, during
+% each batch of images, the nPoint stage remains under closed loop control.
+% Between images, the FPGA control loop idles in state-0, as discussed above in
+% Section~\ref{sec:idle_0}. This was not necessary duing the initial
+% implementation because then, the nPoint stage was controlled by the nPoint PI
+% controller. While this helps things substantially, there is still an alignment
+% issue between subsequent images, which I believe stems from the original Agilent
+% piezo tube, which is a three axis tube. The $XY$-axes of the tube are
+% uncontrolled during imaging, and in fact, after a firmware ``upgrade'', the
+% option to close the $XY$-loop has been grayed out in the PicoView software.
+
+% To help deal with this, we compare sub-slices of the master image and the
+% comparee. The results in this chapter use a sub-image obtained by removing a
+% border of 25 pixels from each edge. Thus, for the purposes of comparison, the
+% original 512$\times$512 pixel image becomes a 462$\times$462 pixel image. Let
+% $X$ represent the original, master image and ${\tilde X=X_{25:-25, 25:-25}}$,
+% using Python notation. To find the correct subslice of the comparee, we use a
+% two dimensional cross-correlation, which is defined as
+% \begin{equation}
+%   Z_{k,\ell} = \sum_{m=0}^{M-1}\sum_{n=0}^{N-1} \tilde{X}_{m-k, n-\ell}Y_{m-k, n-\ell}.
+% \end{equation}
+% where $Y$ is the comparee.
+
+% The index of the maximum value of the matrix $Z$
+% \begin{equation}
+%   (i^*,j^*) = \textrm{arg~} \max_{i,j}Z_{i,j}
+% \end{equation}
+% corresponds to the lower left corner of the correct subslice. Thus, the
+% comparisons will computed against $\tilde{Y} = Y_{i^*:i^*+487, j^*:j^*+487}$.
+% For an example of this in action, see the Fig.~\ref{fig:baseline_errors} in the
+% next section.
+
+% Unfortunately, the mis-alignment is not simply constant offset, but rather
+% drifts over time. This can be seen, e.g., in Fig.~\ref{fig:rast_aligned_0p5}.
+% Thus, while the technique described here mitigates the issue, it does not fully
+% eliminate the problem.
+
+\section{Metrics}\label{sec:rdi}
+In section~\ref{sec:results} we use three metrics to asses our results. The first two seek to quantify image quality of two images. 
+Define a master image as $X$ and a reconstruction or corrupted version as $Y$, with each having $s\times h=m$ pixels.
+Let $x=\textrm{vec}(X)$ and $y=\textrm{vec}(Y)$.
+Let $L$ be the dynamic range of the master image $x$.
+Then the peak signal to noise ratio (PSNR) is given by
+\begin{equation*}
+  \text{PSNR}(x,y) = 10\log_{10}\frac{L^2}
+  {\sqrt{\frac{1}{p^2} \sum_{i=1}^{m}( x_{i} - y_{i})^2 }}.
+\end{equation*}
+
+The goal of the SSIM is to compare two image's structure, luminescence, and contrast and is built up from the means ($\mu_x$ and $\mu_y$), standard deviations ($\sigma_x$ and $\sigma_y$), and covariance ($\sigma_{xy}$) of the image vectors $x$ and $y$.
+The variation of the SSIM used in this paper is defined as
+\begin{equation*}
+  \text{SSIM}(x,y) = \frac{(2\mu_x\mu_y + C_1)(2\sigma_{xy}+C_2)}
+  {(\mu_x^2 + \mu_y^2 + C_1)(\sigma_x^2 + \sigma_y^2 + C_2)}
+\end{equation*}
+where the constants $C_1$ and $C_2$ are regularizing constants to prevent singularity if, e.g., $\mu_x=\mu_y=0$.
+We use the default values suggested in \cite{wang_image_2004} of $C_1=(0.01L)^2$ and ${C_2=(0.03L)^2}$, where again, $L$ is the dynamic range.
+
+In general two images which are identical will yield an infinite PSNR and an SSIM of 1.
+
+\todo{Should probably remove this entire section?}
+
+What kind of numbers are reasonable to expect from the SSIM and PSNR metrics? We
+mentioned in Chapter~\ref{chap:cs_init} that comparison of experimental images
+was difficult (particularly for our experimental setup) because, e.g., Agilent
+piezo tube drifts which gives a varying offset between images. However, we did
+not try to tease apart to what extent the poor SSIM and PSNR numbers we reported
+were due to simply the difference in scanning speeds vs things like image
+mis-alignment.
+
+\begin{figure}[t!]
+  % ------------ 1.0 Hz ---------------------
+  \begin{subfigure}{.48\textwidth}
+    \includesvg[width=1\textwidth]{figures/baseline_errors_noalign_1Hz.svg}
+    \caption{1.0~Hz, no alignment.}
+    \label{fig:rast_unaligned_1}
+  \end{subfigure}
+  \hfill
+  \begin{subfigure}{.48\textwidth}
+    \includesvg[width=1\textwidth]{figures/baseline_errors_aligned_1Hz.svg}
+    \caption{1.0~Hz, with alignment.}
+    \label{fig:rast_aligned_1}
+  \end{subfigure}
+% 
+  \caption{Errors between a ''master'' and 6 different raster scans, all taken
+    sequentially and at a scan rate of 0.5 Hz. (a) Errors without alignment (b)
+    The same data as above in (a) but aligned via cross correlation.}
+  \label{fig:baseline_errors}
+\end{figure}
+
+In the first experiment, (Figs \ref{fig:rast_unaligned_0p5} and
+\ref{fig:rast_aligned_0p5}) we took 6 raster scans of the same 5 by 5 micron
+square of the CS-20NG sample grating. These scans were taken sequentially and
+the NPXY100A remained in closed-loop throughout the process. Taking the first
+scan as the master, we compute (without any alignment) the PSNR and SSIM
+metrics. Fig.~\ref{fig:rast_unaligned_0p5} shows the error between the master
+image and the remaining 6 images. Note that the best PSNR here is 12.13 and the
+worst is 7.87. The best SSIM is 0.40 and the worst is 0.14.
+
+Next, using the cross-correlation alignment technique discussed in
+Section~\ref{sec:align}, we aligned the master image with a sub-slice of each of
+the remaining 6 (the sub-slice removes 25 pixels from each side). Again, we
+computed the PSNR and SSIM. These results are shown in
+Fig.~\ref{fig:rast_aligned_0p5}, which again shows the errors between the
+aligned master and the remaining 6 images. Although the situation is improved
+compared to the un-aligned images, there is still noticable stretching,
+particularly in the $Y$-direction. Notably, the with the alignment technique,
+PSNR now ranges from SSIM 21.68 to 15.56 and the SSIM ranges from 0.67 to 0.50.
+
+We repeat this experiment but this time use a 1~Hz scan.
+Fig.~\ref{fig:rast_unaligned_1} shows the unaligned error images and
+Fig.\ref{fig:rast_aligned_1} shows the aligned error images. Temporally, the
+images are order left-to-right and top-to-bottom. Thus we can see, both visually
+and via the metrics, that in Fig.~\ref{fig:rast_unaligned_1} the mis-alignment
+grows over time (In the 0.5~Hz scans, it appears that after the third from, the
+misalignment is so bad, the situation can't get any worse). In the aligned 1~Hz
+images, our metrics are not only higher but also more consistent: and the SSIM
+lies between 0.7 and 0.73 and the PSNR ranges from 22.51 to 24.99.
+
+% Due to this unfortunate drift, in Section~\ref{sec:results:final}, we will use a
+% 1~Hz scan as the baseline image. Hopefully, this will give a decent trade-off
+% between having an image with minimal drift and scanning slowly enough that it
+% accurately represents the sample grating. Due to the improved $Z$-axis
+% bandwidth, a 1~Hz scan should still have better (or at least comparable) quality
+% than the 0.25~Hz scan taken in Chapter~\ref{chap:cs_init}. Additionally,
+% Fig.\ref{fig:rast_aligned_1} provides us with an (approximate) upper bound for
+% our expectations when looking at the experimental results in
+% Section~\ref{sec:results:final}.
+
+\subsection{A new metric}
 \begin{figure}[t!]
@@
 \end{figure}
-In Chapter~\ref{chap:cs_init} that we employed two metrics, the SSIM and PSNR,
-to compare different raster and CS scans to a master image. We took the master
-image as a raster scan taken at a slow rate. These metrics only assess the
-similarity of two images. However, in AFM imaging, pure image quality is not the
+
+Th PSNR and SSIM metrics only assess the similarity of two images.
+However, in AFM imaging, pure image quality is not the
 only concern, particularly for delicate samples. What is needed is a figure of
@@
 
-% Define the master image as $X$ and a reconstruction as $Y$, with each having
-% $p\times p=n$ pixels. Stack the columns of each into the vectors
-% $x, y\in\mathbb{R}^{n^2}$. Let $L$ be the dynamic range of the master image
-% $x$. Then the PSNR is given by
-% \begin{equation*}
-%   \text{PSNR}(x,y) = 10\log_{10}\frac{L^2}
-%   {\sqrt{\frac{1}{p^2} \sum_{i=1}^{n}( x_{i} - y_{i})^2}}.
-% \end{equation*}
-% The goal of the SSIM is to compare two image's structure, luminescence, and
-% contrast and is built up from the means ($\mu_x$ and $\mu_y$), standard
-% deviations ($\sigma_x$ and $\sigma_y$), and covariance ($\sigma_{xy}$) of the
-% image vectors $x$ and $y$. The variation of the SSIM used in this thesis is
-% defined as
-% \begin{equation*}
-%   \text{SSIM}(x,y) = \frac{(2\mu_x\mu_y + C_1)(2\sigma_{xy}+C_2)}
-%   {(\mu_x^2 + \mu_y^2 + C_1)(\sigma_x^2 + \sigma_y^2 + C_2)}
-% \end{equation*}
-% where the constants $C_1$ and $C_2$ are regularizing constants to prevent
-% singularity if, e.g., $\mu_x=\mu_y=0$. We use the default values suggested in
-% \cite{wang_image_2004} of $C_1=(0.01L)^2$ and ${C_2=(0.03L)^2}$, where again,
-% $L$ is the dynamic range. Both metrics have been used before to compare
-% \emph{simulations} of CS reconstruction in the context of AFM
-% \cite{oxvig_structure_2017, Luo_nano_2015}. We believe, however, that the
-% numbers presented here in Table~\ref{tab:metrics} should be interpreted with
-% some caution as it remains somewhat of an open question of how to best compare
-% \emph{experimental} images from AFM.
-\section{Limitations of SSIM and PSNR}\label{sec:psnr_ssim_limits}
-What kind of numbers are reasonable to expect from the SSIM and PSNR metrics? We
-mentioned in Chapter~\ref{chap:cs_init} that comparison of experimental images
-was difficult (particularly for our experimental setup) because, e.g., Agilent
-piezo tube drifts which gives a varying offset between images. However, we did
-not try to tease apart to what extent the poor SSIM and PSNR numbers we reported
-were due to simply the difference in scanning speeds vs things like image
-mis-alignment.
-
-In this section, we explore this subject by comparing images obtained under the
-most ideal experimental conditions. Specifically, we look at the variation that
-exists when comparing multiple raster scans taken at the same rate. Second, we
-look at CS simulations where we sub-sample a raster image and reconstruct it.
-The goal is to provide context to the numbers in
-Section~\ref{sec:results:final}.
-
-Recall that two images which are identical will yield an infinite PSNR and an
-SSIM of 1.
-
-\begin{figure}[t!]
-  % ------------ 1.0 Hz ---------------------
-  \begin{subfigure}{.48\textwidth}
-    \includesvg[width=1\textwidth]{figures/baseline_errors_noalign_1Hz.svg}
-    \caption{1.0~Hz, no alignment.}
-    \label{fig:rast_unaligned_1}
-  \end{subfigure}
-  \hfill
-  \begin{subfigure}{.48\textwidth}
-    \includesvg[width=1\textwidth]{figures/baseline_errors_aligned_1Hz.svg}
-    \caption{1.0~Hz, with alignment.}
-    \label{fig:rast_aligned_1}
-  \end{subfigure}
-% 
-  \caption{Errors between a ''master'' and 6 different raster scans, all taken
-    sequentially and at a scan rate of 0.5 Hz. (a) Errors without alignment (b)
-    The same data as above in (a) but aligned via cross correlation.}
-  \label{fig:baseline_errors}
-\end{figure}
-
-In the first experiment, (Figs \ref{fig:rast_unaligned_0p5} and
-\ref{fig:rast_aligned_0p5}) we took 6 raster scans of the same 5 by 5 micron
-square of the CS-20NG sample grating. These scans were taken sequentially and
-the NPXY100A remained in closed-loop throughout the process. Taking the first
-scan as the master, we compute (without any alignment) the PSNR and SSIM
-metrics. Fig.~\ref{fig:rast_unaligned_0p5} shows the error between the master
-image and the remaining 6 images. Note that the best PSNR here is 12.13 and the
-worst is 7.87. The best SSIM is 0.40 and the worst is 0.14.
-
-Next, using the cross-correlation alignment technique discussed in
-Section~\ref{sec:align}, we aligned the master image with a sub-slice of each of
-the remaining 6 (the sub-slice removes 25 pixels from each side). Again, we
-computed the PSNR and SSIM. These results are shown in
-Fig.~\ref{fig:rast_aligned_0p5}, which again shows the errors between the
-aligned master and the remaining 6 images. Although the situation is improved
-compared to the un-aligned images, there is still noticable stretching,
-particularly in the $Y$-direction. Notably, the with the alignment technique,
-PSNR now ranges from SSIM 21.68 to 15.56 and the SSIM ranges from 0.67 to 0.50.
-
-We repeat this experiment but this time use a 1~Hz scan.
-Fig.~\ref{fig:rast_unaligned_1} shows the unaligned error images and
-Fig.\ref{fig:rast_aligned_1} shows the aligned error images. Temporally, the
-images are order left-to-right and top-to-bottom. Thus we can see, both visually
-and via the metrics, that in Fig.~\ref{fig:rast_unaligned_1} the mis-alignment
-grows over time (In the 0.5~Hz scans, it appears that after the third from, the
-misalignment is so bad, the situation can't get any worse). In the aligned 1~Hz
-images, our metrics are not only higher but also more consistent: and the SSIM
-lies between 0.7 and 0.73 and the PSNR ranges from 22.51 to 24.99.
-
-Due to this unfortunate drift, in Section~\ref{sec:results:final}, we will use a
-1~Hz scan as the baseline image. Hopefully, this will give a decent trade-off
-between having an image with minimal drift and scanning slowly enough that it
-accurately represents the sample grating. Due to the improved $Z$-axis
-bandwidth, a 1~Hz scan should still have better (or at least comparable) quality
-than the 0.25~Hz scan taken in Chapter~\ref{chap:cs_init}. Additionally,
-Fig.\ref{fig:rast_aligned_1} provides us with an (approximate) upper bound for
-our expectations when looking at the experimental results in
-Section~\ref{sec:results:final}.
-
-\section{Experimental Results}\label{sec:results:final}
+\section{Experimental Results}\label{sec:results}
 We took scans of the CS-20NG sample grating over an area with holes on a 500 nm
-pitch. The holes are 20 nm deep. This is the same area imaged in
-Chapter~\ref{chap:cs_init}. We scanned 5 micron by 5 micron images with 512
+pitch. The holes are 20 nm deep.
+We scanned 5 micron by 5 micron images with 512
 lines each, yielding 512 by 512 pixel images. As before, the $\mu$-path scans
@@
 The free value of the deflections signal was approximately -0.6 volts and we set
-the scanning reference to $r_{Z,s}=-0.3$~volts and the withdraw reference to
-$r_{Z,\textrm{up}}=-0.8$ volts. We set the $XY$-settle boundary to $\pm 0.05$
+the scanning reference to ${\rzs=-0.3}$~volts and the withdraw reference to
+${\rzup=-0.8}$ volts. We set the $XY$-settle boundary to $\pm 0.05$
 microns and required 20 samples within this boundary before moving to the
-$Z$-engage state. The pre-scan length was 150 time steps. The control for the
-$Z$-direction was as described in Chapter~\ref{chap:zaxis-improv}, and the
-$X$-direction control used the SLF state-space (CZ) design of
-Chapter~\ref{chap:mpc_slf} with one difference: the hysteresis model was
-re-tuned for a $\pm$ 7 micron area. The $Y$-axis used a simple integral
-controller, whose closed-loop FRF was shown in Fig.~\ref{fig:mimo_cl_frf}.
+$Z$-engage state. The pre-scan length was 150 time steps.
+
+\todo{Should I scan even faster??}
 
 For the raster scans, we took scans at 1.0~Hz, 4.0~Hz, 5.0~Hz, 8.0~Hz and
-10~Hz\footnote{For a 25~kHz sampling frequency, a 10~Hz raster scan at 512
-  pixels is close to the upper limit because each pixel will only have
-  approximately $ \frac{25000}{2\cdot 10 \cdot 512}\approx 2.4$ samples.}. The
-CS scans we taken with scan velocities equivalent to raster scans of 1.0~Hz,
-2.0~Hz, 4.0~Hz, 5.0~Hz and 8.0~Hz with sampling densities of 10~\% and 15~\%. As
-in Chapter~\ref{chap:cs_init}, the cantilever was an AppNano SICON, with a
+10~Hz.  The CS scans we taken with scan velocities equivalent to raster scans of 1.0~Hz,
+2.0~Hz, 4.0~Hz, 5.0~Hz and 8.0~Hz with sampling densities of 10~\% and 15~\%.
+The cantilever was an AppNano SICON, with a
 length of 450 microns and spring constant $k\in[0.02,~0.8]$~N/m.
 
-The CS scans were reconstructed with BPDN (see \eqref{eqn:bpdn}) using the
-log-barrier Newton method available in \texttt{L1c}\cite{L1c}. We set
-$\epsilon = 0.1$ and the data remained scaled in terms of volts. We then
-filtered the resulting image with the TV-denoising optimization described in
-Section~\ref{sec:tv_denoise} with $\mu=100$.
+The CS scans were reconstructed with BPVV. We set
+$\sigma = 0.1$, $\mu_f=$TKT, $\alpha_v=$TKT and $\alpha_h=$TKTKT. The data remained scaled in terms of volts.
 
@@
 The resulting images are shown in Fig.~\ref{fig:resultsF1_images}. The rows of
-pixels indicated by the red lines are shown Fig.~\ref{fig:pixel_rows}. Due to
-the improved $Z$-axis bandwidth and the image alignment issues described in
-Section~\ref{sec:psnr_ssim_limits}, we use the 1.0~Hz raster scan as the master
-image. Fig.~\ref{fig:resultsF1_errs} shows the error between aligned sub-slices
-of the 1.0~Hz image and the remaining scans. The sub-slice removed a 30 pixel
-boundary from each edge. Despite this alignment, the middle pixels tend to show
-a smaller error than those towards the top and bottom, which is similar to the
-affect observed before in Fig.~\ref{fig:baseline_errors}.
+pixels indicated by the red lines are shown Fig.~\ref{fig:pixel_rows}.
+
+% The sub-slice removed a 30 pixel
+% boundary from each edge. Despite this alignment, the middle pixels tend to show
+% a smaller error than those towards the top and bottom, which is similar to the
+% affect observed before in Fig.~\ref{fig:baseline_errors}.
 
@@
 
-\begin{figure*}
-  \includesvg[scale=1]{figures/cs_raster_images_4-26-2019}
+\begin{figure}
+  \includesvg[width=1\columnwidth]{figures/cs_raster_images_4-26-2019}
   \caption{Raster and compressed sensing images of a 5 micron square area of the
@@
   \label{fig:resultsF1_images}
-\end{figure*}
-
-% \begin{figure*}
-%   \includesvg[scale=1]{figures/cs_raster_images_err_4-26-2019}
-%   \caption{Errors between aligned sub-slices of the 1.0~Hz raster image and
-%   the remaining scans. The original scans are shown in
-%   Fig.~\ref{fig:resultsF1_images}.}
-%   \label{fig:resultsF1_errs}
-% \end{figure*}
+\end{figure}
 
@@
 
-\begin{figure*}[t!]
-  \begin{subfigure}{1\textwidth}
-    \includesvg[scale=1]{figures/cs_rast_time_vs_ssim_psnr.svg}
-    \caption{(left) SSIM as a function of total acquisition time. (right) PSNR
-      as a function of total acquisition time.}
-    \label{fig:time_ssim_psnr}
-  \end{subfigure}
-
-  \begin{subfigure}{1\textwidth}
+\begin{figure*}[h!]
+  % \begin{subfigure}{1\textwidth}
+  %   \includesvg[scale=1]{figures/cs_rast_time_vs_ssim_psnr.svg}
+  %   \caption{(left) SSIM as a function of total acquisition time. (right) PSNR
+  %     as a function of total acquisition time.}
+  %   \label{fig:time_ssim_psnr}
+  % \end{subfigure}
+
+  % \begin{subfigure}{1\textwidth}
     \includesvg[scale=1]{figures/cs_rast_damage.svg}
+    % \caption{(left) RDI as a function of scan rate for raster scans and CS scans
+      % at 10\% and 15\% sampling. (right) RDI as a function of total imaging
+      % time.}
+  % \end{subfigure}
 \caption{(left) RDI as a function of scan rate for raster scans and CS scans
@@
     \label{fig:time_damage}
-  \end{subfigure}
-
-  \label{fig:time_vs_metrics}
+  % \label{fig:time_vs_metrics}
 \end{figure*}
@@
 
-\section{Conclusions}
+\section{Conclusions}\label{sec:conclusions}
 The main conclusion of this chapter is that with CS, it seems that we can
@@
 delicate specimens. We leave this as an area for future work.
-
-A more minor takeaway is that comparing experimental AFM images is difficult,
-especially for systems like ours which cannot control the $XY$-axes of the piezo
-tube.
 

### 2019-05-28 latex/snippets.tex
Symlink my bib file into repo.

\begin{enumerate}
\item \textbf{Initialization:} In this state, the user uses the PicoView
  software to bring the tip to the sample with the stepper motor. Once the tip
  is engaged in the surface, the user switches the control from PicoView to the
  custom software in LabView. The system writes parameters including the
  locations of $\mu$-paths from a desktop file to a host-to-FPGA FIFO (first in,
  first out) buffer. Next, the closed-loop control of all the axes through the
  FPGA is enabled and the system performs the following operations.
    \todo{Shorten this. Sean, what was your trick to not indent enumerate?}
  \begin{itemize}
  \item \textbf{Read} the starting location of the first $\mu$-path from the
    host-to-FPGA FIFO.
  \item \textbf{Set} the $z$-axis loop to position control mode.
  \item \textbf{Wait until} $|e_z(k)|$ reaches a settling criterion, then go to
    state 2.
  \end{itemize}
\item \textbf{$xy$-axis move:} The system moves the tip to the next target
  location by holding $r_X$ and $r_Y$ to the beginning of the next $\mu$-path.
\item \textbf{Tip engage:} We set the $Z$ setpoint to $r_{Z,s}$ so that the
  tip is driven towards the sample surface. 
  \begin{itemize}
  \item \textbf{Set} the $z$-axis loop to deflection control mode.
  \item \textbf{Wait until} $|e_z(k)|$ reaches a settling criterion, then
    transition to state 4. \todo{Update this}
  \end{itemize}
\item \textbf{Scan:} In this state, the system moves the tip following the
  trajectory of the current $\mu$-path.
  \begin{itemize}
  \item \textbf{Update} $x_{ref}$, and $y_{ref}$ iteratively to follow the
    trajectory of the current $\mu$-path to the end. At the same time, write the
    $x,y,z,$ and deflection measurements to an FPGA-to-host FIFO.
  \item \textbf{Wait until} $|e_x(k)|$ and $|e_y(k)|$ reach the end of the
    $\mu$-path,
    % a settling criterion,
    then go to state 5.
  \end{itemize}
  % \item \textbf{Transition decision:} The tip is at the end of the $\mu$-path
  %   at this time. The location of the next $\mu$-path is read from the FIFO.
  %   In
  %   order to accelerate the scanning process, the decision to lift the tip or
  %   not is made in this state. The time $t_{xy\_scan}$ it takes to scan to the
  %   beginning of the next $\mu$-path is compared to
  %   $t_{\textit{z}up}+t_{xy}+t_{\textit{z}down}$. If the former is larger,
  %   then
  %   go to state 6; otherwise, go to state 2.
\item \textbf{Tip withdraw:} In this state, the system withdraws the tip in the
  $z$-direction. A large $K_I$ is used for the $z$-piezo here in order to save
  time.
  \begin{itemize}
  \item \textbf{Set} the $z$-axis loop to position control mode.
  \item \textbf{Set} the $z$ setpoint at a specified distance off the surface.
  \item \textbf{Wait until} $|e_z(k)|$ reaches a settling criterion, then go to
    state 2.
  \end{itemize}
\end{enumerate}

### 2019-05-28 latex/afm-cs-main.tex
Symlink my bib file into repo.
Symlink doesnt work.
Makefile for block-diagrams.

@@
 \usepackage{graphicx}		% to insert figures
-\usepackage{hyperref}		% PDF hyperreferences??
+% \usepackage{hyperref}		% PDF hyperreferences??
 \usepackage{multirow}
@@
 % =========================================================================
-Our experimental setup, illustrated in Fig.~\ref{fig:exp_setup_anderssonLab},
+Our experimental setup, illustrated in Fig.~\ref{fig:exp_setup},
 consists of an Agilent 5400 AFM  retrofitted with an nPoint NPXY100A
@@
 implemented using a 25 kHz sampling rate.
-
+\begin{figure}
+  \includegraphics[width=1\columnwidth]{figures/exp_setup.pdf}
+  \caption{Schematic diagram of the expermental AFM setup.}
+  \label{fig:exp_setup}
+\end{figure}
 % =========================================================================
@@
   \centering
-  \includegraphics[width=0.75\textwidth]{figures/AFM_loop_Dinv_antiwup-crop.pdf}
+  \includegraphics[width=0.75\textwidth]{figures/AFM_loop_z.pdf}
   \caption{Block diagram of the $Z$-axis control loop. The anti-windup is active
@@
 
-\begin{table}\label{tab:cs_tasks}
+\begin{table}
   \centering
@@
   \end{tabular}
+  \label{tab:cs_tasks}
 \end{table}
@@
     \caption{ }
-    \label{fig: }
+    % \label{fig: }
   \end{subfigure}
@@
 
-To
-motivate, this consider Fig.~\ref{fig:prescan_difference}. The left panel
+To motivate, this consider Fig.~\ref{fig:prescan_difference}. The left panel
 represents what we call a ``$Z$''-bounce experiment, where the $XY$-stage stays
@@
 The goal here is to eliminate (i) any oscillations which arise from the
-$XY$-move (which, as we will show in Section ~\ref{sec:need_mimo}, can be
-significant) and (ii) to have a perfectly flat surface to scan over so that
+$XY$-move and (ii) to have a perfectly flat surface to scan over so that
 there are as few disturbances as possible entering the control loop. Finally,
@@
 
+\subsection{Limitations of SSIM and PSNR}\label{sec:limits}
 \todo{Should probably remove this entire section?}
 
-What kind of numbers are reasonable to expect from the SSIM and PSNR metrics? We
-mentioned in Chapter~\ref{chap:cs_init} that comparison of experimental images
-was difficult (particularly for our experimental setup) because, e.g., Agilent
-piezo tube drifts which gives a varying offset between images. However, we did
-not try to tease apart to what extent the poor SSIM and PSNR numbers we reported
-were due to simply the difference in scanning speeds vs things like image
-mis-alignment.
+What kind of numbers are reasonable to expect from the SSIM and PSNR metrics?
+To answer this question, we compare a sequence of 1~Hz raster scans.
+In this experiment, (Fig. \ref{fig:rast_unaligned_1}) we took 6 raster scans of the same 5 by 5 micron
+square of the CS-20NG sample grating. These scans were taken sequentially and
+the NPXY100A remained in closed-loop throughout the process.
+Fig.~\ref{fig:rast_unaligned_1} shows the error between the master
+image and the remaining 6 images.
+Temporally, the images are order left-to-right and top-to-bottom.
+Thus we can see, both visually and via the metrics, that in Fig.~\ref{fig:rast_unaligned_1} the mis-alignment
+grows over time.
+
+Taking the first scan as the master, we compute the PSNR and SSIM
+metrics. The best PSNR here is 16.57 and the worst is 9.02.
+The best SSIM is 0.54 and the worst is 0.28.
 
@@
 
-In the first experiment, (Figs \ref{fig:rast_unaligned_0p5} and
-\ref{fig:rast_aligned_0p5}) we took 6 raster scans of the same 5 by 5 micron
-square of the CS-20NG sample grating. These scans were taken sequentially and
-the NPXY100A remained in closed-loop throughout the process. Taking the first
-scan as the master, we compute (without any alignment) the PSNR and SSIM
-metrics. Fig.~\ref{fig:rast_unaligned_0p5} shows the error between the master
-image and the remaining 6 images. Note that the best PSNR here is 12.13 and the
-worst is 7.87. The best SSIM is 0.40 and the worst is 0.14.
-
-Next, using the cross-correlation alignment technique discussed in
-Section~\ref{sec:align}, we aligned the master image with a sub-slice of each of
+Next, using a cross-correlation alignment technique
+% discussed in Section~\ref{sec:align},
+we aligned the master image with a sub-slice of each of
 the remaining 6 (the sub-slice removes 25 pixels from each side). Again, we
 computed the PSNR and SSIM. These results are shown in
-Fig.~\ref{fig:rast_aligned_0p5}, which again shows the errors between the
+Fig.~\ref{fig:rast_aligned_1}, which again shows the errors between the
 aligned master and the remaining 6 images. Although the situation is improved
 compared to the un-aligned images, there is still noticable stretching,
-particularly in the $Y$-direction. Notably, the with the alignment technique,
-PSNR now ranges from SSIM 21.68 to 15.56 and the SSIM ranges from 0.67 to 0.50.
-
-We repeat this experiment but this time use a 1~Hz scan.
-Fig.~\ref{fig:rast_unaligned_1} shows the unaligned error images and
-Fig.\ref{fig:rast_aligned_1} shows the aligned error images. Temporally, the
-images are order left-to-right and top-to-bottom. Thus we can see, both visually
-and via the metrics, that in Fig.~\ref{fig:rast_unaligned_1} the mis-alignment
-grows over time (In the 0.5~Hz scans, it appears that after the third from, the
-misalignment is so bad, the situation can't get any worse). In the aligned 1~Hz
-images, our metrics are not only higher but also more consistent: and the SSIM
-lies between 0.7 and 0.73 and the PSNR ranges from 22.51 to 24.99.
+particularly in the $Y$-direction. Notably, with the alignment technique,
+the SSIM lies between 0.7 and 0.73 and the PSNR ranges from 22.51 to 24.99 and appears more stable in time.
 
@@
 pixel. To remove the affects of piezo creep and sample tilt, we then de-trend
-each individual line. De-trending each line introduces the artifacts we noted in
-Section~\ref{sec:comp_raster}. To remove this effect, we select a column of
+each individual line.
+De-trending each line causes the flat portion between the holes in the horizontal direction to appear at a different height than the flat portion between holes in the vertical direction.
+To remove this effect, we select a column of
 pixels on the left and right side of each image that does not cross any holes
@@
 % \nocite{*} % list all refs in database, cited or not
-\bibliography{/home/arnold/bib_pdf/main_bibliography,Andersson_bibs,Yufans_bibs} % Bib database in "refs.bib"
+\bibliography{braker_bibs,Andersson_bibs,Yufans_bibs} % Bib database in "refs.bib"
 

### 2019-05-29 latex/afm-cs-main.tex
Split the metrics figures into three individuals.

@@
 tip re-engagements and thus shorter scan times.
+\noindent 
+\begingroup \setlength{\tabcolsep}{1pt}
+\begin{figure*}[h!]
+  \centering
+  \begin{tabular}{cccccc}
+    \textit{\small original image} & \textit{\small BPDN} & \textit{\small BPVV}
+    & \textit{\small detail of original} & \textit{\small detail of BPDN} & \textit{\small detail of BPVV} \\
+    % 
+    \includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_gt_framed}
+    %
+    & \includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_40mu}
+     % 
+    & \includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_bptv_40mu}
+     % 
+    & \includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_gt_zoomin}
+     % 
+    &\includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_40mu_zoomin}
+    %
+    &\includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_bptv_40mu_zoomin}\\
+    % 
+    % ------------------------------ Row  2 --------------------------------------------
+    \includegraphics[width=0.16\textwidth]{figures-SBA/dnaforbptv_gt_framed}
+    %
+    & \includegraphics[width=0.16\textwidth]{figures-SBA/dnaforbptv_40mu}
+    %
+    & \includegraphics[width=0.16\textwidth]{figures-SBA/dnaforbptv_bptv_40mu}
+    %
+    & \includegraphics[width=0.16\textwidth]{figures-SBA/dnaforbptv_gt_zoomin}
+    %
+    & \includegraphics[width=0.16\textwidth]{figures-SBA/dnaforbptv_40mu_zoomin}
+    %
+    & \includegraphics[width=0.16\textwidth]{figures-SBA/dnaforbptv_bptv_40mu_zoomin}
+  \end{tabular}
+  \caption{Reconstruction comparison between BPDN and BPVV. (first column)
+    Original raster-scanned image. (second column) BPDN reconstruction from
+    random, 40 pixel long $\mu$-paths with 25\% sampling. (third column) BPVV
+    reconstruction from the same sub-sampled data. (remaining columns)
+    Corresponding details from the red boxes indicated in the raster image. The
+    results show that BPVV reduces the artifacts arising from the horizontal
+    scans of the $\mu$-path pattern that appear in BPDN reconstructions.}
+  \label{fig:BPTV_demonstration}
+\end{figure*}
+\todo{Re-do this figure???}
+\endgroup
 
@@
 \end{equation*}
+
 One of the core features of the NESTA algorithm is to replace the non-smooth functional $f(x)$ with a smoothed approximation
@@
 The optimization \eqref{op:bp_tv} may now be solved using Algorithm~\ref{ag:NESTA}.
+
 \todo{seems like a waste of space to reprint the algo, since its really no different than the reference}
@@
 
-\noindent 
-\begingroup \setlength{\tabcolsep}{1pt}
-\begin{figure*}[htbp]
-  \centering
-  \begin{tabular}{cccccc}
-    \textit{\small original image} & \textit{\small BPDN} & \textit{\small BPVV} & \textit{\small detail of original} & \textit{\small detail of BPDN} & \textit{\small detail of BPVV} \\
-    % \includegraphics[width=0.16\textwidth]{figures-SBA/circulargrating_gt_framed}
-    %                                & \includegraphics[width=0.16\textwidth]{figures-SBA/circulargrating_40mu}		
-    %                                                       & \includegraphics[width=0.16\textwidth]{figures-SBA/circulargrating_bptv_40mu}
-    %                                                                              & \includegraphics[width=0.16\textwidth]{figures-SBA/circulargrating_gt_zoomin}
-    %                                                                                                                   & \includegraphics[width=0.16\textwidth]{figures-SBA/circulargrating_mu40_zoomin}
-    %                                                                                                                                                    & \includegraphics[width=0.16\textwidth]{figures-SBA/circulargrating_bptv_40mu_zoomin}\\
-    \includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_gt_framed}
-                                   & \includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_40mu}		
-                                                          & \includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_bptv_40mu}	
-                                                                                 & \includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_gt_zoomin}	
-                                                                                                                      & \includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_40mu_zoomin}
-                                                                                                                                                       & \includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_bptv_40mu_zoomin}	\\
-    \includegraphics[width=0.16\textwidth]{figures-SBA/dnaforbptv_gt_framed}
-                                   & \includegraphics[width=0.16\textwidth]{figures-SBA/dnaforbptv_40mu}		
-                                                          & \includegraphics[width=0.16\textwidth]{figures-SBA/dnaforbptv_bptv_40mu}	
-                                                                                 & \includegraphics[width=0.16\textwidth]{figures-SBA/dnaforbptv_gt_zoomin}	
-                                                                                                                      & \includegraphics[width=0.16\textwidth]{figures-SBA/dnaforbptv_40mu_zoomin}
-                                                                                                                                                       & \includegraphics[width=0.16\textwidth]{figures-SBA/dnaforbptv_bptv_40mu_zoomin}
-  \end{tabular}
-  \caption{Reconstruction comparison between BPDN and BPVV. (first column)
-    Original raster-scanned image. (second column) BPDN reconstruction from
-    random, 40 pixel long $\mu$-paths with 25\% sampling. (third column) BPVV
-    reconstruction from the same sub-sampled data. (remaining columns)
-    Corresponding details from the red boxes indicated in the raster image. The
-    results show that BPVV reduces the artifacts arising from the horizontal
-    scans of the $\mu$-path pattern that appear in BPDN reconstructions.}
-  \label{fig:BPTV_demonstration}
-\end{figure*}
-\todo{Re-do this figure???}
-\endgroup
-
 A comparison between BPDN and BPVV is shown in
@@
 
+\begin{figure}[ht!]
+  \includegraphics[width=1\columnwidth]{figures/exp_setup.pdf}
+  \caption{Schematic diagram of the expermental AFM setup.}
+  \label{fig:exp_setup}
+\end{figure}
+
 % =========================================================================
@@
 implemented using a 25 kHz sampling rate.
-\begin{figure}
-  \includegraphics[width=1\columnwidth]{figures/exp_setup.pdf}
-  \caption{Schematic diagram of the expermental AFM setup.}
-  \label{fig:exp_setup}
-\end{figure}
+
 % =========================================================================
@@
 
-For raster scanning, we use a truncated Fourier series, where each Fourier coefficient is scaled by the inverse of the closed-loop FRF at the corresponding frequency.
-We truncate this series such that the highest frequency is smaller than 200 Hz.
-See, e.g., \cite{clayton_review_2009} for more details on this strategy.
-
 For CS scanning, we insert a feed-forward filter with two notches, one at 215~Hz and the other at 505~Hz.
@@
 However, to achieve the same 40~dB of attenuation of the mode at 215 Hz, would require, e.g., that a two-pole LPF have its cut-off frequency at about 20~Hz.
+
+For raster scanning, we use a truncated Fourier series, where each Fourier coefficient is scaled by the inverse of the closed-loop FRF at the corresponding frequency.
+We truncate this series such that the highest frequency is smaller than 200 Hz.
+See, e.g., \cite{clayton_review_2009} for more details on this strategy.
+Note that these scheme implies that the effective bandwidth of the $X$-axis controller is higher while raster scanning than while CS-scanning.
+On the other hand, it also implies that the for faster scan rates, fewer Fourier coefficients are used, and so the approximation to a triangle wave is worse.
 
@@
 is easiest to see this by plotting PSNR and SSIM against total acquisition time,
-which is shown in Fig.~\ref{fig:time_ssim_psnr}. There are several
+which is shown in Fig.~\ref{fig:time_ssim} and ~\ref{fig:time_psnr}. There are several
 inconsistencies. First, the 4~Hz raster scan has the lowest PSNR of all the
@@
 raster scans. It makes no sense for a CS scan at a 5~Hz rate to have better
-quality than a raster scan at a 5~Hz rate. It is interesting to also compare
-these numbers to the batch of 1~Hz raster scans we compared in
-Section~\ref{sec:psnr_ssim_limits}. The blue shaded bands of
-Figs~\ref{fig:time_ssim_psnr} indicate the mean of the SSIM and PSNR metrics
-from Section \ref{sec:psnr_ssim_limits} plus or minus one standard deviation.
-This seems to be further evidence that, at least for our experimental setup,
-these numbers are not especially meaningful.
+quality than a raster scan at a 5~Hz rate.
+
+% It is interesting to also compare
+% these numbers to the batch of 1~Hz raster scans we compared in
+% Section~\ref{sec:limits}.
+% The blue shaded bands of
+% Figs~\ref{fig:time_ssim_psnr} indicate the mean of the SSIM and PSNR metrics
+% from Section \ref{sec:psnr_ssim_limits} plus or minus one standard deviation.
+% This seems to be further evidence that, at least for our experimental setup,
+% these numbers are not especially meaningful.
 
 \begin{figure*}[h!]
-  % \begin{subfigure}{1\textwidth}
-  %   \includesvg[scale=1]{figures/cs_rast_time_vs_ssim_psnr.svg}
-  %   \caption{(left) SSIM as a function of total acquisition time. (right) PSNR
-  %     as a function of total acquisition time.}
-  %   \label{fig:time_ssim_psnr}
-  % \end{subfigure}
-
-  % \begin{subfigure}{1\textwidth}
-    \includesvg[scale=1]{figures/cs_rast_damage.svg}
-    % \caption{(left) RDI as a function of scan rate for raster scans and CS scans
-      % at 10\% and 15\% sampling. (right) RDI as a function of total imaging
-      % time.}
-  % \end{subfigure}
-\caption{(left) RDI as a function of scan rate for raster scans and CS scans
-      at 10\% and 15\% sampling. (right) RDI as a function of total imaging
-      time.}
+  \begin{subfigure}{0.33\textwidth}
+    \includesvg[width=\textwidth]{figures/cs_rast_time_vs_ssim.svg}
+    \caption{}
+    \label{fig:time_ssim}
+  \end{subfigure}
+  \begin{subfigure}{0.33\textwidth}
+    \includesvg[width=1\textwidth]{figures/cs_rast_time_vs_psnr.svg}
+    \caption{}
+    \label{fig:time_psnr}
+  \end{subfigure}
+  \begin{subfigure}{0.33\textwidth}
+    \includesvg[width=\textwidth]{figures/cs_rast_damage.svg}
+    \caption{}
     \label{fig:time_damage}
+  \end{subfigure}
+\caption{Metrics for raster scan and $\mu$-path scans at 10\% and 15\% sampling.
+(a) SSIM as a function of total acquisition time.
+(b) PSNR  as a function of total acquisition time.
+(c) RDI as a function of total acquisition time.}
+
   % \label{fig:time_vs_metrics}
@@
 
-One final point that should be mentioned is that, by using an $X$-axis
-controller designed for tracking step inputs, we have unfairly disadvantaged
-raster scanning. Due the faster harmonic decay of a triangle wave compared to a
-series of step inputs, in principle a higher bandwidth $X$-axis controller could
-be used for raster scanning because the cross-coupling concerns discussed in
-Section~\ref{sec:cz_cr_cs} would play a smaller role. While this will be
-discussed a bit further in the next chapter, for now we note that the most
-prominent way the lower bandwidth $X$-axis controller has limited raster
-scanning is by chopping off the left and right edges of the images, which can be
-seen in Fig.~\ref{fig:resultsF1_images} and \ref{fig:pixel_rows}. However, the
-metrics are computed on a subslice that is large enough to eliminate this
-region. Additionally, the RDI is mostly affected by the $Z$-direction bandwidth.
-
 %%%%%%%%% then the Bibliography, if any %%%%%%%%%

### 2019-05-29 latex/afm-cs-main.tex
Minor edits

@@
 
-\todo{seems like a waste of space to reprint the algo, since its really no different than the reference}
 \begin{algorithm}
@@
 \end{algorithm}
+  \todo{seems like a waste of space to reprint the algo, since its really no different than the reference}
 
@@
 resonance at 350 Hz.
+\todo{Not sure how to give a deeper summary without getting to much into the weeds.}
 
@@
 \subsection{Cantilever does not need to fully disengage.}
-\todo{Dramatically truncate this section}
+\todo{Not clear to me yet that friction is useful if I scan parallel to cantilever.
+  Also not clear to me that the normal force and shear force are orthogonal concepts.
+  Maybe the macroscopic analogy breaks down, but thinking of a knife pushed into a surface and then dragged...}
 In our initial implementation \cite{braker_hardware_2018}, we insisted that the during tip-retraction
@@
 In general, stable imaging in is not possible at \rzup and complete dis-engagement occasionally occurs.
-
-\todo{Not clear to me that friction is useful if I scan parallel to cantilever.
-Also not clear to me that the normal force and shear force are orthogonal concepts.
-Maybe the macroscopic analogy breaks down, but thinking of a knife pushed into a surface and then dragged...}
 
@@
 \section{Metrics}\label{sec:rdi}
-In section~\ref{sec:results} we use three metrics to asses our results. The first two seek to quantify image quality of two images. 
+In section~\ref{sec:results} we use three metrics to asses our results.
+The first two seek to quantify image quality of two images. 
 Define a master image as $X$ and a reconstruction or corrupted version as $Y$, with each having $s\times h=m$ pixels.
-Let $x=\textrm{vec}(X)$ and $y=\textrm{vec}(Y)$.
-Let $L$ be the dynamic range of the master image $x$.
+Let $x=\textrm{vec}(X)$ and $y=\textrm{vec}(Y)$. Let $L$ be the dynamic range of the master image $x$.
 Then the peak signal to noise ratio (PSNR) is given by
@@
 We use the default values suggested in \cite{wang_image_2004} of $C_1=(0.01L)^2$ and ${C_2=(0.03L)^2}$, where again, $L$ is the dynamic range.
-
 In general two images which are identical will yield an infinite PSNR and an SSIM of 1.
@@
 \subsection{Limitations of SSIM and PSNR}\label{sec:limits}
-\todo{Should probably remove this entire section?}
-
 What kind of numbers are reasonable to expect from the SSIM and PSNR metrics?
@@
 grows over time. 
+\todo{Should probably remove this entire section?}
 

### 2019-05-29 latex/afm-cs-main.tex
Rework nesta part.

@@
 \begin{align}
-  \min_{x\in Q_p}~f(x) &= \min_{x\in Q_p} \left\|U^Tx\right\|_1 + \alpha_v\left\|D_vx\right\|_1
-                         + \alpha_h\left\|D_hx\right\|_1  \label{op:bp_tv}
-  % \text{subject to} &\, \| R x - y \|_2 < \sigma,
+  \min_{x\in Q_p}~f(x) &= \min_{x\in Q_p} \left\|U^Tx\right\|_1
+                         + \alpha\left\|D_vx\right\|_1
+                         + \beta\left\|D_hx\right\|_1 \label{op:bp_tv}\\
+                       &=\min_{x\in Q_p} \left\|Wx\right\|_1 \label{op:bp_tvW}
+                         % \quad W = \begin{bmatrix}U&\alpha_hD^T_h&\alpha_vD^T_v \end{bmatrix}^T \nonumber
 \end{align}
-where ${D_v x=\text{vec}(\nabla_v X)}$ (resp., ${D_v x=\text{vec}(\nabla_v X)}$) is the
-discrete gradient in the vertical (resp., horizontal) direction (see, e.g., \cite[Section 6.1,]{becker_nesta_2011}). 
+where
+\begin{equation*}
+W = \begin{bmatrix}U&\alpha_hD^T_h&\alpha_vD^T_v \end{bmatrix}^T
+\end{equation*}
+with ${D_v x=\text{vec}(\nabla_v X)}$ (resp., ${D_v x=\text{vec}(\nabla_v X)}$) representing a 
+discrete gradient of a matrix in the vertical (resp., horizontal) direction (see, e.g., \cite[Section 6.1,]{becker_nesta_2011}). 
 % and
@@
 Thus, in \eqref{op:bp_tv}, $\left \| D_v x \right \|_1$ (resp., $\left \| D_h x \right \|_1$) is the total variation (TV) of the signal in the vertical (resp., horizontal) direction.
-The parameters $\alpha_v$ and $\alpha_h$ are weighting parameters.
-
-The description of BPVV in \eqref{op:bp_tv} can be viewed as the combination of CS
-and inpainting, in which the first term seeks a sparse solution while the
-last two terms try to diffuse pixel information.
-\todo{When written this way, it seems that BP+VV/TV can could also be interpreted in the frameowrk of overcomplete dictionaries?\cite{candes_redundant_2011}. }
-To solve the optimization problem in \eqref{op:bp_tv} we use a (slight) extension to NESTA~\cite{becker_nesta_2011}. To that end, we re-write the cost $f(x)$ in \eqref{op:bp_tv} as
+The parameters $\alpha$ and $\beta$ are weighting parameters.
+The description of BPVV in \eqref{op:bp_tvW} can be interpreted as changing our assumption of sparsity in the DCT basis to assuming sparsity in an overcomplete dictionary \cite{candes_redundant_2011}.
+\todo{I believe this is correct: Sean/Yufan can you confirm or reject?}
+
+Moreover, when written as \eqref{op:bp_tvW}, the problem is in a form that may be solved with to NESTA~\cite{becker_nesta_2011}. For completeness, we give an overview here.
+To that end, we re-write the cost $f(x)$ in \eqref{op:bp_tvW} as
 \begin{equation*}
-  f(x) = \max_{u\in Q_d} \left\langle u, Wx \right\rangle,\quad Q_d = \{u:~||u||_{\infty} \leq 1\}
-\end{equation*}
-where
-\begin{equation*}
-W = \begin{bmatrix}U&\alpha_hD^T_h&\alpha_vD^T_v \end{bmatrix}^T.
-%   W = \begin{bmatrix}U^T\\\alpha_hD_h\\\alpha_vD_v \end{bmatrix}.
+  f(x) = \max_{u\in Q_d} \left\langle u, Wx \right\rangle,\quad Q_d = \{u:~||u||_{\infty} \leq 1\}.
 \end{equation*}

### 2019-05-29 latex/afm-cs-main.tex
Rework nesta part.
Updates from Overleaf

@@
 
-Moreover, when written as \eqref{op:bp_tvW}, the problem is in a form that may be solved with to NESTA~\cite{becker_nesta_2011}. For completeness, we give an overview here.
+Moreover, when written as \eqref{op:bp_tvW}, the problem is in a form that may be solved with NESTA~\cite{becker_nesta_2011}. For completeness, we give an overview here.
 To that end, we re-write the cost $f(x)$ in \eqref{op:bp_tvW} as
@@
 aligned master and the remaining 6 images. Although the situation is improved
-compared to the un-aligned images, there is still noticable stretching,
+compared to the un-aligned images, there is still noticeable stretching,
 particularly in the $Y$-direction. Notably, with the alignment technique,
@@
 we can use the positive deviations of $Z_d$ as a relative measure of damage
-between different scan speeds or scanning methods, for a given cantiliver and
+between different scan speeds or scanning methods, for a given cantilever and
 specimen. This motivates a metric we term the relative damage index (RDI), which

### 2019-05-29 latex/afm-cs-main.tex
Update on Overleaf.

@@
     % ------------------------------ Row  2 --------------------------------------------
-    \includegraphics[width=0.16\textwidth]{figures-SBA/dnaforbptv_gt_framed}
-    %
-    & \includegraphics[width=0.16\textwidth]{figures-SBA/dnaforbptv_40mu}
-    %
-    & \includegraphics[width=0.16\textwidth]{figures-SBA/dnaforbptv_bptv_40mu}
-    %
-    & \includegraphics[width=0.16\textwidth]{figures-SBA/dnaforbptv_gt_zoomin}
-    %
-    & \includegraphics[width=0.16\textwidth]{figures-SBA/dnaforbptv_40mu_zoomin}
-    %
-    & \includegraphics[width=0.16\textwidth]{figures-SBA/dnaforbptv_bptv_40mu_zoomin}
+    \includesvg[width=0.16\textwidth]{figures/dna_og.svg}
+    %
+    & \includesvg[width=0.16\textwidth]{figures/dna_bp.svg}
+    %
+    & \includesvg[width=0.16\textwidth]{figures/dna_bptv.svg}
+    %
+    & \includesvg[width=0.16\textwidth]{figures/dna_og_zoom.svg}
+    %
+    & \includesvg[width=0.16\textwidth]{figures/dna_bp_zoom.svg}
+    %
+    & \includesvg[width=0.16\textwidth]{figures/dna_bptv_zoom.svg}
   \end{tabular}

### 2019-05-29 latex/chapter-afm-cs-final.tex
Update on Overleaf.

\section{Final Implementation}\label{chap:afm-cs-final}

This chapter is a story of rising tides and all ships being lifted. I wish to give raster scanning a fair shake\footnote{It would not be hard to argue that I have failed in that endevour. Because the $X$-axis control scheme is designed for tracking step-inputs, it has more damping and lower bandwidth than what one could probably achieve if only raster scanning.}. Therefore, where appropriate, the improvements made to CS scanning are also applied to raster scanning. This means that both raster and CS scanning use the state space compensator designed in Chapter~\ref{chap:mpc_slf} and the $Z$-axis controller designed in Chapter~\ref{chap:zaxis-improv}.
This improves the results for both methods, compared to Chapter~\ref{chap:cs_init}.

 The first section discusses several modifications (i.e., differences to Chapter~\ref{chap:cs_init}) to the CS-scanning cycle. Section \ref{sec:post_process} discusses the post-processing techniques used. Section \ref{sec:rdi} develops a new metric to compare the relative damage done by different scans and Section~\ref{sec:psnr_ssim_limits} takes a closer look at the SSIM and PSNR metrics in an effort to understand what ''reasonable'' numbers look like for AFM images taken with our AFM. Similarly, Section~\ref{sec:cs_sim} looks at some CS simulations (based on real raster scans) to help us understand what, ideally, we should see from the experiments performed in Section~\ref{sec:results:final}.

\section{The Modified CS-Cycle}\label{sec:modfied_cs_cycle}
The final implementation is similar to the initial implementation originally described in Chapter~\ref{chap:cs_init}. However, there are some differences. These are summarized in
Table~\ref{tab:cs_cycle_diff}
\begin{table}
  \centering
  \caption{Summary of the differences between the initial CS implementation and the final version.}
  \label{tab:cs_cycle_diff}
  \begin{tabular}{c|p{1.75in}|p{1.75in}}
    state &  initial implementation & current implementation \\
    \hline
    $XY$-move & control: PI     & control: LQG           \\
    \hline
    tip-settle & $XY$ does not move & $XY$ starts scanning  (pre-scan)\\
    \hline
    $\mu$-path scan & finish with post-scan & no post scan \\
    \hline
    tip-up & $Z$-axis feedback off. Set ${u_k=u_{\textrm{up}}}$. & $Z$-axis feedback on. Set ${r_Z=r_{Z,\textrm{up}}}$. Implement anti-windup. \\
  \end{tabular}
\end{table}
The new state machine is diagramed in Fig.~\ref{fig:sm_final}. 
The primary modifications are (i) a pre-scan during $Z$-axis settling period, (ii) not intentionally disengaging during tip-retraction; (iii) at the end of a scan, return to state-0, so that everything remains in closed-loop.

Several cycles of the modified scheme are shown in Fig.~\ref{fig:cs_cycle_final}. Each of these differences is discussed more fully in the following three subsections.
\begin{figure}[ht!]
  \centering
  \includesvg[scale=0.85]{plots-afm-cs-final/figures/cs_cycle.svg}
  \caption{Several CS cycles. Each state is indicated by color.}
  \label{fig:cs_cycle_final}
\end{figure}

\begin{figure}
  \centering
    \includesvg[width=.9\textwidth]{plots-afm-cs-final/figures/state-machine-final.svg}
    \caption{Diagram of the state-machine implemented in the final design.}
    \label{fig:sm_final}
\end{figure}

\subsection{Cantilever does not need to fully disengage.}
In the initial implementation, we insisted that the during tip-retraction (state-5), the cantilever tip should fully break contact with the surface. Here, we impose no such requirement. Rather, we change the $Z$-setpoint during tip-retraction to only pull away far enough that the deflection signal stays low (i.e., below the scanning setpoint), even while we run across the surface.

\textbf{Motivation} The motivation for this is two-fold. First, there is the obvious advantage that, by not pulling the tip so away, there is less distance to recover during the re-engagement. The original idea was to pull away from the surface far enough to disengage, then step back down towards the surface by some fraction of the step up. This proved impractical for several reasons. First, it requires the control system to be able to detect when disengagement has occurred. While preliminary experiments indicate it may be possible to achieve this by detecting a change in the derivative of the deflection signal, the actual value of the control signal which achieved dis-engagement proved to be highly variable (ranging from about 0.6 v to over 3 volts (210 nanometers to over a micron)) and sometimes saturating the control signal without disengagement. Experiments indicate that the dis-engagement point depends on (at least) the tip condition and the cantilever spring constant \footnote{The numbers cited used a cantilever with $k\approx .1$~N/m. Experiments using a cantilever with $k\approx 50$ N/m yielded much more consistent and much smaller needed dis-engagement control signals. However, cantilevers with such large spring constants are tapping-mode cantilevers, a mode which our AFM is incapable of. Scanning in contact mode with such a cantilever implies that a very large force is being applied to the sample.}.

Such large pull-away distances are problematic, especially for our AFM, which lacks a $Z$-position sensor. The difficulty is that when the tip is re-engaged with the sample from far away, this incites a large drift transient.
This is shown in Fig.~\ref{fig:z_drift} under the panels labeled ``big lift''.
By starting the re-engagement closer to the sample, this transient is much smaller. Without a $Z$-position sensor, we have to let this drift die out or it will corrupt the image. Thus, even if the step-up-down scheme could be made to work, the overall time would still be limited by this drift. I made some effort to fit an LTI model to the drift mode, so this affect could be removed in post-processing. Unfortunately, as we saw in Section~\ref{sec:modeling_remaining}, an LTI drift model does not adequately describe the drift transient, because the drift rate seems to depend on the control history.

A third advantage is that, given the \emph{same} absolute starting height above the specimen, re-engagement is faster when the tip has not snapped free. The reason for this is that when the cantilever snaps away from the specimen surface, the deflection signal is essentially saturated. This gives the control loop an artificially small error signal, which leads to a very sluggish descent.

\textbf{Justification} Ultimately the concern is damage to the sample and tip, which is caused by the force imparted by the cantilever probe \cite{clayton_review_2009}. The deflection signal, though un-calibrated (meaning it does not directly lead to a value in $kN$), is proportional to that force, because it is proportional to how much the cantilever is bent. I.e., a large (towards $+\infty$) deflection implies the spring force of the cantilever is pushing hard into the sample, thereby inducing damage. In a typical imaging scenario, we choose a deflection setpoint, (say $0.15$~[v], as in Fig.~\ref{fig:z_drift}), and have in some way decided that this is sufficient, all else being equal, to not damage things too much.

Thus, rather than completely dis-engaging the tip from the surface, I propose to simply move the setpoint towards $-\infty$ during the $XY$-move. If this new setpoint is sufficiently far away, the deflection signal will stay below the scanning setpoint, which we had decided was a ''safe'' value. The change in setpoints is achieved via the multiplexer in Fig.~\ref{fig:afm_bd_dinv_final} which selects either the scanning setpoint $r_{Z,s}$ or the retraction setpoint $r_{Z,\textrm{up}}$ based the current state.
\begin{figure}[t]
  \centering
  \includegraphics[width=0.75\textwidth]{plots-afm-cs-final/figures/AFM_loop_Dinv_antiwup-crop.pdf}
  \caption{Block diagram of the $Z$-axis control loop. The anti-windup is active for decision index $i\in\{0,1,5\}$, which correspond to states such that $r_Z=r_{Z,\textrm{up}}$.}
  \label{fig:afm_bd_dinv_final}
\end{figure}

\begin{figure}[ht!]
  \begin{subfigure}{.48\textwidth}
    \includesvg[width=1\textwidth]{plots-afm-cs-final/figures/justify_small_lift.svg}
    \caption{ }
    % \label{fig: }
  \end{subfigure}
  \begin{subfigure}{.48\textwidth}
    \includesvg[width=01\textwidth]{plots-afm-cs-final/figures/justify_small_lift_zoom.svg}
    \caption{ }
    % \label{fig: }
  \end{subfigure}
  \caption{One CS-cycle with different dis-engagement heights. (a) Full view. (b) Zoomed-in view. Note the  drift transient in the left panel of (b). }
  \label{fig:z_drift}
\end{figure}

This new scheme does not imply that the cantilever \emph{never} fully disengages. Occasionally, the new setpoint is far enough away that the probe does still snap away from the sample surface. 
When this happens, the integrator, $D_I(z)$, will windup. This happens because typically, the desired setpoint $r_{Z,\textrm{up}}$ is more negative than the free (disengaged) value of the deflection. Thus, the sensor signal is essentially saturated and no matter how far the $Z$-actuator tries to move, no change will result in the deflection, leading to windup and a control signal that exceeds the actuator bounds. To deal with this, we implement an anti-windup scheme for all states where $r_Z=r_{Z,\textrm{up}}$, i.e., states (0), (1) and (5). This is illustrated in the block diagram in Fig.~\ref{sec:modfied_cs_cycle}. During these states, the output of the accumulator is saturated before its own internal feedback.

\subsection{The pre-scan}
\begin{figure}
  \begin{subfigure}{.33\textwidth}
    \includesvg[width=1\textwidth]{plots-afm-cs-final/figures/zbounce_uz_example.svg}
    \caption{ }
    \label{fig: }
  \end{subfigure}
  \begin{subfigure}{.33\textwidth}
     \includesvg[width=1\textwidth]{plots-afm-cs-final/figures/prescan_uz_example.svg}
    \caption{ }
    \label{fig:uz_prescan}
  \end{subfigure}
  \begin{subfigure}{.33\textwidth}
     \includesvg[width=1\textwidth]{plots-afm-cs-final/figures/prescan_zbounce_PSD.svg}
    \caption{ }
    \label{fig: }
  \end{subfigure}
  \caption{(a) A ``$Z$-bounce'' experiment where the $XY$-stage is motionless and the cantilever is repeatedly engaged and disengaged. (b) One cycle of a tightly packed set of CS-cycles where the movement between each measurement location is 0. (c) PSDs from the portions of the trajectories which are colored blue and turquoise, averaged over many such cycles, demonstrating that the scan process itself reduces vibration in the $Z$-axis.}
  \label{fig:prescan_difference}
\end{figure}
After the tip-descent, we begin scanning in a ``pre-scan'' phase (state (3)). To motivate, this consider Fig.~\ref{fig:prescan_difference}. The left panel represents what we call a ``$Z$''-bounce experiment, where the $XY$-stage stays motionless, but we repeatedly retract and re-engage the tip with specimen, exactly as we would in a CS scan. The right panel represents a single cycle from specialized CS pattern, where the $\mu$-paths are still 500 nm long, but the paths are separated by 0 pixels. In this case, the specimen is freshly cleaved mica. The goal here is to eliminate (i) any oscillations which arise from the $XY$-move (which, as we will show in Section ~\ref{sec:need_mimo}, can be significant) and (ii) to have a perfectly flat surface to scan over so that there are as few disturbances as possible entering the control loop. Finally, the middle panel of Fig.~\ref{fig:prescan_difference} shows the PSDs of the left and right panels (but averaged over many similar cycles). Note that the PSD is only computed from the combination of the blue and turquoise signals.

What we see then, is that, for some unknown (to me) reason, scanning reduces the amount of energy that shows up near 215 Hz. The idea behind the pre-scan is to take advantage of this.
The pre-scan phase is relatively long (150 samples), especially for the faster scan rates.
However, the pre-scan also allows us to eliminate the over-scan at the end of the $\mu$-path, because by the time we are ready to start taking data, the $X$-axis is already in quasi-steady-state. For the current control design, the required over-scan is about 90 samples (which can be computed from the steady-state error of the closed-loop system to a ramp), which means the pre-scan incurs an effective overhead of about 60 samples per $\mu$-path.

The tip settling (pre-scan) period could likely be much shorter if we a had a $Z$-axis position sensor. Part of the reason it is so long is that, despite not pulling the cantilever completely away from the sample, there is still a small drift transient, as can be seen Fig.~\ref{fig:uz_prescan}. We would like to at least give the major part of that drift transient time to die out.
With a position sensor, we would not care about the drift transient: the control signal drifts to keep the $Z$-position constant.

\subsection{Return to state-0}\label{sec:idle_0}
In the initial implementation, once a CS scan had finished, the FPGA software exited. Here, once the scan finishes, the state machine returns to state-0 where it idles, waiting for the Host to either command a shutdown or load a new scan file. Moreover, the software generalizes both raster and CS scans, so that a scan file may define either one. This allows us to perform multiple, back-to-back raster and CS scans while the system stays under closed-loop control, which helps to mitigate the image alignment issues discussed in the next section.

\section{Improved post-processing}\label{sec:post_process}
There are a few differences from Chapter~\ref{sec:comp_raster} in how we post-process the data into images. We discuss those here. 
\subsection{Aligning images via cross-correlation}\label{sec:align}
To get metrics that are meaningful in any sense, we need the master image and the comparee to be aligned.
We take two steps to help ensure this.
First, during each batch of images, the nPoint stage remains under closed loop control.
Between images, the FPGA control loop idles in state-0, as discussed above in Section~\ref{sec:idle_0}.
This was not necessary duing the initial implementation because then, the nPoint stage was controlled by the nPoint PI controller.
While this helps things substantially, there is still an alignment issue between subsequent images, which I believe stems from the original Agilent piezo tube, which is a three axis tube.
The $XY$-axes of the tube are uncontrolled during imaging, and in fact, after a firmware ``upgrade'', the option to close the $XY$-loop has been grayed out in the PicoView software.

To help deal with this, we compare sub-slices of the master image and the comparee. The results in this chapter use a sub-image obtained by removing a border of 25 pixels from each edge. Thus, for the purposes of comparison, the original 512$\times$512 pixel image becomes a 462$\times$462 pixel image. Let $X$ represent the original, master image and
${\tilde X=X_{25:-25, 25:-25}}$, using Python notation. To find the correct subslice of the comparee, we use a two dimensional cross-correlation, which is defined as
\begin{equation}
  Z_{k,\ell} = \sum_{m=0}^{M-1}\sum_{n=0}^{N-1} \tilde{X}_{m-k, n-\ell}Y_{m-k, n-\ell}.
\end{equation}
where $Y$ is the comparee.

The index of the maximum value of the matrix $Z$
\begin{equation}
(i^*,j^*) = \textrm{arg~} \max_{i,j}Z_{i,j}
\end{equation}
corresponds to the lower left corner of the correct subslice. Thus, the comparisons will computed against
$\tilde{Y} = Y_{i^*:i^*+487, j^*:j^*+487}$. For an example of this in action, see the Fig.~\ref{fig:baseline_errors} in the next section.

Unfortunately, the mis-alignment is not simply constant offset, but rather drifts over time. This can be seen, e.g., in Fig.~\ref{fig:rast_aligned_0p5}. Thus, while the technique described here mitigates the issue, it does not fully eliminate the problem.

% \subsection{Dynamic de-trending}
% Because our AFM is not equipped with a $Z$-axis sensor, it is important to remove as much drift as possible from the $u_Z$ control signal, otherwise, this slow dynamic will corrupt the final image. This can  partly be achieved by doing an image after the AFM has been on for a long time, e.g., 20 minutes, and especially after taking several slow raster scans. We can also remove some of the drift by fitting a curve
% \begin{equation}
%   d_k = \alpha + \beta t_k + \gamma \log\left(\frac{t_k}{0.1}\right)
% \end{equation}
% where $t_k$ is the time at the $k$-th sampling period and $\alpha$, $\beta$, and $\gamma$ are the parameters to be fit. This is a combination of a time-domain drift model \cite{Jung_open_loop_2000} and a linear fit which accounts for sample tilt. This line is fit to the entire set of $u_Z$ control data and subtracted.

\subsection{ TV-denoising}\label{sec:tv_denoise}
Some of the noise in an image reconstructed via BPDN can be reduced by solving a Total Variation (TV) de-noising optimization problem
\begin{equation}
  \min_{U} ||\nabla_xU||_1 + ||\nabla_yU||_1 + \mu||F - U||_2 \label{eqn:breg1}
\end{equation}
where $F$ is the image produced by the BPDN optimization and $U$ is the de-noised image. 
This idea was  heavily inspired by Yufan Luo's approach \cite{luo_mupath_2019}.
The difference is that (i) I do this for both $\nabla_x$ and $\nabla_y$, where he only does it for $\nabla_y$ and (ii) that he does it in a single optimization which combines \eqref{eqn:breg1} with BPDN while I do it in two separate optimizations. The optimization is solved using the Split Bregman technique described in \cite{goldstein_splitbregman_2009} and my implementation is publicly available \cite{L1c}.

\section{A New Metric}\label{sec:rdi}
\begin{figure}[t!]
  \centering
  \includesvg[scale=1]{plots-afm-cs-final/figures/damage_illustration.svg}
  \caption{The RDI metric defined in \eqref{eqn:RDI} penalizes everything in the red shaded region and does not penalize anything in the un-shaded region.}
  \label{fig:damage_illustrate}
\end{figure}
In Chapter~\ref{chap:cs_init} that we employed two metrics, the SSIM and PSNR, to compare different raster and CS scans to a master image. We took the master image as a raster scan taken at a slow rate. These metrics only assess the similarity of two images.
However, in AFM imaging, pure image quality is not the only concern, particularly for delicate samples. What is needed is a figure of merit for how much damage was done to specimen during the imaging process. While this is not really a concern while imaging a hard calibration grating, it plays a prominent role biological samples~\cite{ando_highspeed_2008}.
In general, damage occurs while scanning into an uphill region, which results in a positive deflection signal. The actual damage done by a given $Z_d$ will depend on the spring constant of the cantilever and the softness of the specimen.
Nonetheless, we can use the positive deviations of $Z_d$ as a relative measure of damage between different scan speeds or scanning methods, for a given cantiliver and specimen. This motivates a metric we term the relative damage index (RDI), which we define as
\begin{align}
  \text{RDI} &= \frac{1}{T_s}\sum_{k\in I} \frac{1}{k} \left(Z_{d,k} - r_{Z,s}\right)^2 \label{eqn:RDI}\\
  I &= \{k: k\in[0,~N-1],~ Z_{d,k}-r_{Z,s} > 0 \} \nonumber
\end{align}
where $N$ is the total number of samples in a given scan, $Z_{d,k}$ is the deflection signal at sample $k$ and $r_{Z,\textrm{s}}$ is the scanning setpoint. 
The RDI is basically the power in positive deflection.
By excluding negative values of the deflection, we do not penalize the CS algorithm while it is re-engaging with the specimen \emph{unless} it overshoots the scanning setpoint, which we do want to penalize. This is illustrated in Fig.~\ref{fig:damage_illustrate}, which shows several CS cycles with a poorly tuned controller.
Only deflection signals in the red-shaded region will be penalized by the RDI.

% Define the master image as $X$ and a reconstruction as $Y$, with each having $p\times p=n$ pixels. Stack the columns of each into the vectors $x, y\in\mathbb{R}^{n^2}$. Let $L$ be the dynamic range of the master image $x$. Then the PSNR is given by
% \begin{equation*}
%   \text{PSNR}(x,y) = 10\log_{10}\frac{L^2}
%   {\sqrt{\frac{1}{p^2} \sum_{i=1}^{n}( x_{i} - y_{i})^2}}.
% \end{equation*}
% The goal of the SSIM is to compare two image's structure, luminescence, and contrast and is built up from the means ($\mu_x$ and $\mu_y$), standard deviations ($\sigma_x$ and $\sigma_y$), and covariance ($\sigma_{xy}$) of the image vectors $x$ and $y$.  
% The variation of the SSIM used in this thesis is defined as
% \begin{equation*}
%   \text{SSIM}(x,y) = \frac{(2\mu_x\mu_y + C_1)(2\sigma_{xy}+C_2)}
%   {(\mu_x^2 + \mu_y^2 + C_1)(\sigma_x^2 + \sigma_y^2 + C_2)}
% \end{equation*}
% where the constants $C_1$ and $C_2$ are regularizing constants to prevent singularity if, e.g., $\mu_x=\mu_y=0$. We use the default values suggested in \cite{wang_image_2004} of $C_1=(0.01L)^2$ and ${C_2=(0.03L)^2}$, where again, $L$ is the dynamic range.
% Both metrics have been used before to compare \emph{simulations} of CS reconstruction in the context of AFM \cite{oxvig_structure_2017, Luo_nano_2015}. We believe, however, that the numbers presented here in Table~\ref{tab:metrics} should be interpreted with some caution as it remains somewhat of an open question of how to best compare \emph{experimental} images from AFM.
\section{Limitations of SSIM and PSNR}\label{sec:psnr_ssim_limits}
What kind of numbers are reasonable to expect from the SSIM and PSNR metrics?
We mentioned in Chapter~\ref{chap:cs_init} that comparison of experimental images was difficult (particularly for our experimental setup) because, e.g., Agilent piezo tube drifts which gives a varying offset between images. However, we did not try to tease apart to what extent the poor SSIM and PSNR numbers we reported were due to simply the difference in scanning speeds vs things like image mis-alignment.

In this section, we explore this subject by comparing images obtained under the most ideal experimental conditions. Specifically, we look at the variation that exists when comparing multiple raster scans taken at the same rate. Second, we look at CS simulations where we sub-sample a raster image and reconstruct it. The goal is to provide context to the numbers in Section~\ref{sec:results:final}.

Recall that two images which are identical will yield an infinite PSNR and an SSIM of 1.

\begin{figure}[t!]
  % ------------ 0.5 Hz ---------------------
  \begin{subfigure}{.48\textwidth}
    \includesvg[width=1\textwidth]{plots-afm-cs-final/figures/baseline_errors_noalign.svg}
    \caption{0.5~Hz, no alignment.}
    \label{fig:rast_unaligned_0p5}
  \end{subfigure}
  \hfill
  \begin{subfigure}{.48\textwidth}
    \includesvg[width=1\textwidth]{plots-afm-cs-final/figures/baseline_errors_aligned.svg}
      \caption{0.5~Hz, with alignment.}
    \label{fig:rast_aligned_0p5}
  \end{subfigure}
% ------------ 1.0 Hz ---------------------
    \begin{subfigure}{.48\textwidth}
    \includesvg[width=1\textwidth]{plots-afm-cs-final/figures/baseline_errors_noalign_1Hz.svg}
    \caption{1.0~Hz, no alignment.}
    \label{fig:rast_unaligned_1}
  \end{subfigure}
  \hfill
  \begin{subfigure}{.48\textwidth}
    \includesvg[width=1\textwidth]{plots-afm-cs-final/figures/baseline_errors_aligned_1Hz.svg}
      \caption{1.0~Hz, with alignment.}
    \label{fig:rast_aligned_1}
  \end{subfigure}
% 
  \caption{Errors between a ''master'' and 6 different raster scans, all taken sequentially and at a scan rate of 0.5 Hz. (a) Errors without alignment (b) The same data as above in (a) but aligned via cross correlation.}
  \label{fig:baseline_errors}
\end{figure}

In the first experiment, (Figs \ref{fig:rast_unaligned_0p5} and \ref{fig:rast_aligned_0p5})
we took 6 raster scans of the same 5 by 5 micron square of the CS-20NG sample grating.
These scans were taken sequentially and the NPXY100A remained in closed-loop throughout the process.
Taking the first scan as the master, we compute (without any alignment) the PSNR and SSIM metrics.
Fig.~\ref{fig:rast_unaligned_0p5} shows the error between the master image and the remaining 6 images.
Note that the best PSNR here is 12.13 and the worst is 7.87. The best SSIM is 0.40 and the worst is 0.14.

Next, using the cross-correlation alignment technique discussed in Section~\ref{sec:align},
we aligned the master image with a sub-slice of each of the remaining 6 (the sub-slice removes 25 pixels from each side). Again, we computed the PSNR and SSIM. These results are shown in Fig.~\ref{fig:rast_aligned_0p5}, which again shows the errors between the aligned master and the remaining 6 images. 
Although the situation is improved compared to the un-aligned images, there is still noticable stretching, particularly in the $Y$-direction. Notably, the with the alignment technique, PSNR now ranges from SSIM 21.68 to 15.56 and the SSIM ranges from 0.67 to 0.50.

We repeat this experiment but this time use a 1~Hz scan. Fig.~\ref{fig:rast_unaligned_1} shows the unaligned error images and Fig.\ref{fig:rast_aligned_1} shows the aligned error images. Temporally, the images are order left-to-right and top-to-bottom. Thus we can see, both visually and via the metrics, that in  Fig.~\ref{fig:rast_unaligned_1} the mis-alignment grows over time (In the 0.5~Hz scans, it appears that after the third from, the misalignment is so bad, the situation can't get any worse).
In the aligned 1~Hz images, our metrics are not only higher but also more consistent: and the SSIM lies between 0.7 and 0.73 and the PSNR ranges from 22.51 to 24.99.

Due to this unfortunate drift, in Section~\ref{sec:results:final}, we will use a 1~Hz scan as the baseline image. Hopefully, this will give a decent trade-off between having an image with minimal drift and scanning slowly enough that it accurately represents the sample grating. Due to the improved $Z$-axis bandwidth, a 1~Hz scan should still have better (or at least comparable) quality than the 0.25~Hz scan taken in Chapter~\ref{chap:cs_init}. Additionally, Fig.\ref{fig:rast_aligned_1} provides us with an (approximate) upper bound for our expectations when looking at the experimental results in Section~\ref{sec:results:final}.

\subsection{CS Simulations}\label{sec:cs_sim}
The goal of this section is learn what kind of quality might be expected from CS and to help us understand how much of the degradation in image quality is due to the nature of CS and how much is due to limitations in our experimental setup, e.g., transients from the tip descent or inconsistency stemming from lack of a $Z$-position sensor or the alignment issues discussed in the previous section.
\begin{figure}[ht!]
  \centering
  \begin{subfigure}{1\textwidth}
    \centering
      \includesvg[width=.8\textwidth]{plots-afm-cs-final/figures/cs_sim_1Hz_raster.svg}
  \caption{}
  \label{fig:cs_sim_1Hz}
  \end{subfigure}
  \begin{subfigure}{1\textwidth}
    \centering
    \includesvg[width=.8\textwidth]{plots-afm-cs-final/figures/cs_sim_1Hz_raster_from1Hz.svg}
    \caption{}
    \label{fig:cs_sim_raster_1p0_1p0}
  \end{subfigure}
  \caption{CS simulations. (a) The top left panel is a 1.0 Hz raster scan. The rest of the panels were sub-sampled with a $\mu$-path mask with the indicated sampling fraction and reconstructed with BPDN. (b) subsampled images taken from a separate 1~Hz raster scan and compared to the same original 1~Hz scan.}
  \label{fig:cs_sim_against_raster}
\end{figure}

\begin{table}[t!]
  \centering
  \caption{Metrics from the CS simulations shown in
    Fig.~\ref{fig:cs_sim_against_raster}.}
  \begin{tabular}{ccccc}
    \input{plots-afm-cs-final/tables/cs_sims_table.tex}
  \end{tabular}
  \label{tab:cs_sim}
\end{table}

To help tease apart these issues, we take two raster images of a 5 micron square at 1.0~Hz. Call them image \textbf{A} and image \textbf{B}. Comparing these two raster scans \textbf{A} to \textbf{B} yields a PSNR of 23.08 and an SSIM of 0.75.

First, we simulate CS reconstructions by sub-sampling image \textbf{A} with several $\mu$-path masks ranging from 7\% to 25\%, reconstruct the image with BPDN, and then filter the result with TV denosing ($\mu=300$). Call the resulting image $\hat{\mathbf{A}}$. These results are shown in Fig.~\ref{fig:cs_sim_1Hz}. The metrics labeling each reconstruction were computed against master image \textbf{A}.

Second, using the same sampling masks, we sub-sample image \textbf{B} and run the result through the same reconstruction pipeline. Call the resulting image $\hat{\mathbf{B}}$. These reconstructions are shown in Fig.~\ref{fig:cs_sim_raster_1p0_1p0}. Again the metrics are computed against image \textbf{A} (not \textbf{B}). For both scenarios, we compute the SSIM and PSNR metrics which are tabulated in Table~\ref{tab:cs_sim}.

It is first of all notable that the halos noted in Chapter~\ref{chap:cs_init} still show up these simulations.
Second, the metrics when comparing \textbf{A} vs $\mathbf{\hat{A}}$ are high: in fact they are the best metrics in this entire thesis, \textit{including the comparison between 1~Hz raster scans in Fig.~\ref{fig:rast_aligned_1}}. Second, the metrics when comparing \textbf{A} vs $\mathbf{\hat{B}}$ drop substantially. This should not be surprising and is evidently due the drop from CS combined with the drop due to mis-alignment.

% \FloatBarrier
\section{Experimental Results}\label{sec:results:final}
We took scans of the CS-20NG sample grating over an area with holes on a 500 nm pitch. The holes are 20 nm deep. This is the same area imaged in Chapter~\ref{chap:cs_init}. Again, we take a 5 micron by 5 micron images with 512 lines each, yielding 512 by 512 pixel images. As before, the $\mu$-path scans are 500 nm long, as this allows us to work around the lack of a $Z$-axis sensor. This yields a $\mu$-path size of 52 pixels.

The free value of the deflections signal was approximately -0.6 volts and we set the scanning reference to $r_{Z,s}=-0.3$~volts and the withdraw reference to $r_{Z,\textrm{up}}=-0.8$ volts. We set the $XY$-settle boundary to $\pm 0.05$ microns and required 20 samples within this boundary before moving to the $Z$-engage state. The pre-scan length was 150 time steps. The control for the $Z$-direction was as described in Chapter~\ref{chap:zaxis-improv}, and the $X$-direction control used the SLF state-space (CZ) design of Chapter~\ref{chap:mpc_slf} with one difference: the hysteresis model was re-tuned for a $\pm$ 7 micron area. The $Y$-axis used a simple integral controller, whose closed-loop FRF was shown in Fig.~\ref{fig:mimo_cl_frf}.

For the raster scans, we took scans at 1.0~Hz, 4.0~Hz, 5.0~Hz, 8.0~Hz and 10~Hz\footnote{For a 25~kHz sampling frequency, a 10~Hz raster scan at 512 pixels is close to the upper limit because each pixel will only have approximately $ \frac{25000}{2\cdot 10 \cdot 512}\approx 2.4$ samples.}. The CS scans we taken with scan velocities equivalent to raster scans of 1.0~Hz, 2.0~Hz, 4.0~Hz, 5.0~Hz and 8.0~Hz with sampling densities of 10~\% and 15~\%. As in Chapter~\ref{chap:cs_init}, the cantilever was an AppNano SICON, with a length of 450 microns and spring constant $k\in[0.02,~0.8]$~N/m.

The CS scans were reconstructed with BPDN (see \eqref{eqn:bpdn}) using the log-barrier Newton method available in \texttt{L1c}\cite{L1c}. We set $\epsilon = 0.1$ and the data remained scaled in terms of volts. We then filtered the resulting image with the TV-denoising optimization described in Section~\ref{sec:tv_denoise} with $\mu=100$.

For the raster scans, we discard data from the re-trace and divided the remaining data into 512$\times$512 bins based on the \xc and \yc sensor measurements. We then average the data in each bin to obtain the value of one pixel. To remove the affects of piezo creep and sample tilt, we then de-trend each individual line. De-trending each line introduces the artifacts we noted in Section~\ref{sec:comp_raster}. To remove this effect, we select a column of pixels on the left and right side of each image that does not cross any holes (i.e., a vertical line through the flat area), register each scan line to a common height along these columns. This step eases comparison with the CS scans and was inspired by a feature in \texttt{SPIW} \cite{spiw}.

As a final step, we subtract the mean from each CS and raster image, so that they can all be mapped to the same color intensity in the images. The color maps represent a range of $\pm$20 nm.

The resulting images are shown in Fig.~\ref{fig:resultsF1_images}. The rows of pixels indicated by the red lines are shown Fig.~\ref{fig:pixel_rows}. Due to the improved $Z$-axis bandwidth and the image alignment issues described in Section~\ref{sec:psnr_ssim_limits}, we use the 1.0~Hz raster scan as the master image.
Fig.~\ref{fig:resultsF1_errs} shows the error between aligned sub-slices of the 1.0~Hz image and the remaining scans. The sub-slice removed a 30 pixel boundary from each edge. Despite this alignment, the middle pixels tend to show a smaller error than those towards the top and bottom, which is similar to the affect observed before in  Fig.~\ref{fig:baseline_errors}.

For each raster scan and each CS scan, we computed the SSIM, PSNR (both with default parameters) using the 1~Hz scan as the master and also computed the RDI metric. These are collected in table ~\ref{tab:rast_vs_cs_v1}.

\begin{figure}
    \includesvg[scale=1]{plots-afm-cs-final/figures/cs_raster_images_4-26-2019}
    \caption{Raster and compressed sensing images of a 5 micron square area of the CS-20NG grating. All images are 512$\times$512 pixels. The rows of pixels indicated by the red line are shown in \ref{fig:pixel_rows}.}
    \label{fig:resultsF1_images}
\end{figure}

\begin{figure}
    \includesvg[scale=1]{plots-afm-cs-final/figures/cs_raster_images_err_4-26-2019}
    \caption{Errors between aligned sub-slices of the 1.0~Hz raster image and the remaining scans. The original scans are shown in Fig.~\ref{fig:resultsF1_images}.}  
    \label{fig:resultsF1_errs}
\end{figure}

\begin{table}[t!]
  \centering
  \caption{Performance metrics for the scans taken on 4-26-2019.  All CS images filtered with TV denoising, $\mu$=100.}
      \begin{tabular}{cccccc}
        \input{plots-afm-cs-final/tables/cs_raster_table_4-26-2019_muInf_dct2.tex}
      \end{tabular}
      \label{tab:rast_vs_cs_v1}
\end{table}

\begin{table}[t!]
  \centering
  \caption{Breakdown of state times for the CS scans listed in Table~\ref{tab:rast_vs_cs_v1}. All times are in seconds.}
  \label{tab:final_state_times}
  \begin{tabular}{ccccccc}
    \input{plots-afm-cs-final/tables/cs_state_times_table_4-26-2019_muInf_dct2.tex}
  \end{tabular}
\end{table}

\begin{figure}[t!]
    \includesvg[width=1\textwidth]{plots-afm-cs-final/figures/cs_raster_pixel_rows_3-20-2019.svg}
    \caption{Rows of pixels, as indicated by the red lines in Fig.~\ref{fig:resultsF1_images}. For clarity, not all images are included.}  
    \label{fig:pixel_rows}
\end{figure}

Unfortunately, the SSIM and PSNR metrics are not particularly illuminating. It is easiest to see this by plotting PSNR and SSIM against total acquisition time, which is shown in Fig.~\ref{fig:time_ssim_psnr}.
There are several inconsistencies. First, the 4~Hz raster scan has the lowest PSNR of all the raster scans, while the 8~Hz scan has the highest. Second, all of the 15\% CS scans except the 8~Hz version have as good or better SSIM numbers than the raster scans. It makes no sense for a CS scan at a 5~Hz rate to have better quality than a raster scan at a 5~Hz rate. It is interesting to also compare these numbers to the batch of 1~Hz raster scans we compared in Section~\ref{sec:psnr_ssim_limits}. The blue shaded bands of Figs~\ref{fig:time_ssim_psnr} indicate the mean of the SSIM and PSNR metrics from Section \ref{sec:psnr_ssim_limits} plus or minus one standard deviation. This seems to be further evidence that, at least for our experimental setup, these numbers are not especially meaningful.

\begin{figure}[t!]
    \begin{subfigure}{1\textwidth}
    \includesvg[scale=1]{plots-afm-cs-final/figures/cs_rast_time_vs_ssim_psnr.svg}
    \caption{(left) SSIM as a function of total acquisition time. (right) PSNR as a function of total acquisition time.}
    \label{fig:time_ssim_psnr}
  \end{subfigure}

  \begin{subfigure}{1\textwidth}
    \includesvg[scale=1]{plots-afm-cs-final/figures/cs_rast_damage.svg}
   \caption{(left) RDI as a function of scan rate for raster scans and CS scans at 10\% and 15\% sampling. (right) RDI as a function of total imaging time.}
    \label{fig:time_damage}
  \end{subfigure}

  \label{fig:time_vs_metrics}
\end{figure}

Where CS seems to really shine is if we look at the RDI for a given time or scan rate. This is plotted in Fig.~\ref{fig:time_damage}. For example, the 10~Hz raster scan, which takes about 51 seconds, gives an RDI of 23.7. All of the CS scans, except for the 15\% scan at 1~Hz (which is only 0.9 seconds longer) are faster than the 10~Hz raster scan, yet have much lower RDI values, ranging from 1.21 to 13.13.
Unsurprisingly, the relationship between scan speed and RDI is quite linear. For the raster scans, the left panel of Fig.~\ref{fig:time_damage} just plots the inverse relationship of the right panel, since scan time is inversely proportional to raster frequency. This is not quite the case for the CS scans due to the sub-sampling and the fixed overhead which does not scale with scan rate (e.g., the amount of time for the $XY$-move etc remains essentially constant for a given scan density).

What is surprising is that for the same scan rate, the CS scans have a lower RDI than a raster scan at the same rate. One possibility is that the probability that a given $\mu$-path will start on the flat portion of the grating, scan \textit{into} a hole and then the tip withdraws before exiting the hole is higher than the probability that a scan starts in a hole and exits the hole. This would result in a lower RDI, because scanning \textit{out} of hole is what the RDI penalizes.

From the left panel of Fig.~\ref{fig:time_damage}, we see that for a fixed RDI, CS has a faster imaging acquisition rate. The amount of improvement is best if we need a very low RDI: for example, if we want to hold the RDI below 2, then we have to take the 1~Hz raster scan (512 seconds) while we can achieve the same RDI via CS in about 52 seconds with the 15\% sampling, which is a speed improvement of nearly 10. The higher of an RDI we are willing to tolerate, the advantage of CS over raster narrows. For example, the 4~Hz raster scan and 5~Hz, 15\% CS scan have comparable RDI, but now CS is only about 6 times faster. This is a result of the constant overhead imposed by the engage/disengage and $XY$-move states in CS.

\section{Conclusions}
The main conclusion of this chapter is that with CS, it seems that we can acquire images faster yet (putatively) with less specimen damage than is possible with raster scanning, which we showed by introducing a new metric, the RDI. Of course, a natural criticism is that we did not validate the RDI against delicate specimens. We leave this as an area for future work.

A more minor takeaway is that comparing experimental AFM images is difficult, especially for systems like ours which cannot control the $XY$-axes of the piezo tube.

One final point that should be mentioned is that, by using an $X$-axis controller designed for tracking step inputs, we have unfairly disadvantaged raster scanning. Due the faster harmonic decay of a triangle wave compared to a series of step inputs, in principle a higher bandwidth $X$-axis controller could be used for raster scanning because the cross-coupling concerns discussed in Section~\ref{sec:cz_cr_cs} would play a smaller role. While this will be discussed a bit further in the next chapter, for now we note that the most prominent way the lower bandwidth $X$-axis controller has limited raster scanning is by chopping off the left and right edges of the images, which can be seen in Fig.~\ref{fig:resultsF1_images} and \ref{fig:pixel_rows}. However, the metrics are computed on a subslice that is large enough to eliminate this region. Additionally, the RDI is mostly affected by the $Z$-direction bandwidth.

% \bibliographystyle{IEEEtran}
% \bibliography{/home/arnold/bib_pdf/main_bibliography}
% \end{document}

%%% Local Variables:
%%% mode: latex
%%% End:

### 2019-05-29 latex/chapter_z_axis_improvements.tex
Update on Overleaf.

% In Figures~\ref{fig:impl0:20miccross} and \ref{fig:impl0:5miccross}, we saw that, at very low scan speeds, the control signal shows lots of oscillation. These are caused by building vibration electrical noise and are amplified by the $z$-axis control loop.
\section{Improving the $Z$-axis}\label{chap:zaxis-improv}

In this chapter, we improve the $Z$-axis control. The chapter is broken into two main sections. First, we study unwanted external disturbances imposing themselves on the $Z$-axis dynamics, their implications for control, and methods to mitigate them. In the second section, we design a relatively simple control scheme. The twist is that we enable automated identification and design.

\section{$Z$-axis disturbances}\label{sec:zaxis-dist}
First, we study how external disturbances enter the $Z$-axis control loop. We then show that, given a set of disturbances within some frequency band, we must limit the control bandwidth, and consequently the imaging speed, or resign ourselves to having the disturbances show up in our images. We then study the specific disturbances present in our experimental setup. Finally, we identify the source of two specific disturbances and show how they can be mitigated inexpensively.

\subsection{General Implications of Disturbances}

Figure \ref{fig:zimprv:z_axis_bd} shows a block diagram of the $z$-axis control loop.
The two relevant transfer functions are
\begin{align}
  H_{ed} &= \frac{-1}{1 + GD}\\
  H_{ud} &= \frac{-D}{1 + GD}, \label{eqn:hud}
\end{align}
which are the transfer function from the disturbance to the error and from the disturbance to the control. Here, $d=s+d_{\text{ext}}$, where $s(t)$ is the sample surface and $d_{\text{ext}}(t)$ is an external disturbance. Typically, the cantilever dynamics are much faster than the rest of the control loop. For example, the SICON-50 cantilever used in this thesis has a resonant frequency between 5 and 25~kHz, while the $Z$-piezo dynamics begin to roll off at about 1~kHz (see Fig.~\ref{fig:Guz2stage_frf}). Thus, the cantilever is often approximated as a constant gain, as shown in Fig.~\ref{fig:zimprv:z_axis_bd}. While scanning, our sensor is the $Z$-axis deflection signal, $Z_{d}$, which is a measure of how much the cantilever has been bent from its rest position. The task given to the $Z$-axis control loop is to maintain the deflection signal at a specified reference $R_Z$. While scanning, $R_Z$ is a constant. Thus, this is a disturbance rejection problem, where the sample surface is the disturbance. In the ideal situation, $d_{\text{ext}}=0$, so that $d(t) = s(t)$.
\begin{figure}[t!]
  \centering
  \includegraphics[width=0.7\textwidth]{plots_z_axis_improv/figures/AFM_loop.pdf}
  \caption{Block diagram of the $Z$-axis control loop, showing how disturbances from the sample surface and unwanted, external disturbances enter the control loop.}.
  \label{fig:zimprv:z_axis_bd}
\end{figure}

In general, the faster we scan, the larger bandwidth is needed in the $Z$-axis control loop. To see this, 
consider a (fictional) sample where the spatial frequency content is band-limited by frequency $f_{B_s}$ (i.e., the Fourier series describing the current scan line has a finite number of terms).
% Then the smallest wavelength in the current scan line is $\lambda_{B_s}=1/f_{B_s}$.
If we scan with speed $v$ then to the AFM probe, the surface, $s(t)$ appears in the time domain also band limited signal whose highest frequency component is
\begin{equation}
  f_{\textrm{surf}} = \frac{v}{\lambda}.
\end{equation}
Thus, as we scan faster, the surface presents as a higher frequency signal to the $Z$-axis control loop \cite{ando_highspeed_2008}.

We now show why we can take $u_Z$ to represent the sample surface. In general, $D(z)$ contains an integrator and $H_{ud}$ will be flat up to its roll off frequency $f_B$. Thus, if the frequency content of the surface $s$ is less than $f_B$, then from \eqref{eqn:hud}, $u \approx H_{ud}(1)s$. The upshot is that for any given control loop bandwidth, we can always\footnote{Assuming a sufficiently well behaved surface.} scan slowly enough so that most of the frequency content of the sample surface is less than $f_B$. If we wish to scan faster, we must increase $f_B$, or else the image will be distorted by the low-pass filtering nature of the control loop.

Now consider the situation when $d_{\text{ext}}\neq 0$. As illustrated in Fig.~\ref{fig:zimprv:z_axis_bd}, unwanted external disturbances enter the control loop at the same point as the sample surface.
This is because, e.g., from the perspective of the cantilever, the specimen vibrating vertically due a disturbance is indistinguishable from variations in the surface topology.
Thus, if the external disturbances are concentrated above some frequency $f_d$, then the $H_{ud}$ should roll-off before $f_d$ if we do not want those disturbances to corrupt the final image. This implies that we must artificially lower the scan speed to keep the specimen frequency content within the $H_{ud}$ bandwidth. Said another way, we must modulate the scan speed to induce a frequency separation between the external disturbances and the specimen. Thus, if we want to scan faster, we must extirpate as many external disturbances as possible.

% \begin{figure}[ht!]
%   \begin{subfigure}{.48\textwidth}
%     %                     L B R T  
%     \includegraphics[trim=0 0 0 0, clip,width=1\textwidth]{plots_z_axis_improv/figures/Hde.pdf}
%     \includegraphics[trim=0 0 0 0, clip,width=1\textwidth]{plots_z_axis_improv/figures/ze_noise_example_Kis.pdf}
% \caption{Stuff }
% \label{fig:Hde}
% \end{subfigure}
% \hfill
%   \begin{subfigure}{.48\textwidth}
%     %                     L B R T  
%   \includegraphics[trim=0 0 0 0, clip,width=1\textwidth]{plots_z_axis_improv/figures/Hdu.pdf}
%   \includegraphics[trim=0 0 0 0, clip,width=1\textwidth]{plots_z_axis_improv/figures/uz_noise_example_Kis.pdf}
%   \caption{ }
%   \label{fig: Hdu}
% \end{subfigure}
% \caption{Control Loops.}
% \label{fig:z_improv:bode_loops}
% \end{figure}
% Figure~\ref{fig:z_improv:bode_loops} shows Bode diagrams for these two transfer functions for several values of $K_I$. On the one hand, we would like the bandwidth of $H_{ud}$ to be as high as possible because this will improve image quality. On the other hand, if we increase the bandwidth too much, we amplify the external noise sources, which are concentrated in the shaded green band. This means that we must keep the bandwidth artificially low to avoid corrupting our images with that noise. In turn, this means that the upper limit on the scan rate is set by the external disturbances, rather than limitations of the instrument mechanics.

% The bottom row of plots in Fig.~\ref{fig:z_improv:bode_loops} shows the error and control signal in the time domain for two values of $K_I$. As one would expect, we do a better job rejecting disturbances with larger $K_I$. Unfortunately, we pay for this in the control signal. One might reasonably ask if this problem could be dealt with by leveraging the internal model principle to design a controller to specifically reject a sinusoid at 29 Hz. However, this will insert complex zeros on the imaginary axis which will ultimately produce artifacts in the image.

\section{Vibration Disturbances}
In this section, we characterize the external disturbances present in our experimental setup. 
To do this, we engage the cantilever with the sample surface, turn off all control loops, and measure the deflection signal. We then compute the power spectral density (PSD) of the deflection signal. This is shown in Fig.~\ref{fig:psd_xy_off} as the blue curve. This PSD is computed via Bartlett's method with 50 segments, each containing 32768 samples.

The $XY$ stage is off in this experiment. Note the significant amount of energy present in the band stretching from about  7~Hz to 80~Hz, which is shaded in green. The bottom plot in Fig~\ref{fig:psd_xy_off} shows a portion of the time series used to compute the PSD. There the low frequency oscillations are clearly evident as well. Recall from Fig.~\ref{fig:G_mat_frf} that there are no oscillatory modes in the system dynamics between 7 to 80~Hz. Thus, we expect that energy to come largely from an external disturbance, as opposed to being due to white noise (say from the $Z$-axis power amplifier) becoming colored through one of $Z$-piezo modes. From the discussion in the previous section, if we don't want this energy in our images, we must severely de-rate the $Z$-axis control loop so that it rolls-off well before 10~Hz. 
\begin{figure}[t!]
  \includesvg[width=1\textwidth]{plots_z_axis_improv/figures/initial_dfl_psd_xyoff}
  \includesvg[width=1\textwidth]{plots_z_axis_improv/figures/initial_dfl_time_xyoff}
  \caption{The blue and red curves (left axis) are the PSD of the deflection signal with $XY$-stage off. The black curve is the FRF $H_{Z_d,u_Z}$.}
  \label{fig:psd_xy_off}
\end{figure}
Thus, we would like to eliminate these disturbances. The most likely culprit is building vibration, which may stem from, e.g., foot-traffic, the HVAC system, or other parts of the buildings mechanics. Of course, we are not alone in this problem and commercial solutions exist. Typical solutions range from purely passive systems \cite{keysight_vibration}, active vibration cancellation \cite{herzan}, and a combination of active cancellation and tuned mass-dampers \cite{newport}. These products are expensive. The simplest design is the purely passive system \cite{keysight_vibration}, which insert a mechanical low pass filter between the building and the AFM by suspending the AFM from bungee cords.

The design is simple enough that it is straightforward construct a home-built alternative (shown in Fig.~\ref{fig:custom_isolator}) for about 70 USD. The idea is shown schematically in Fig.~\ref{fig:isolation_lpf}. The building's motion is represented as $p$ which is transfered to the AFM support (the mass $m$ through the spring and damper. The transfer function is given by
\begin{equation}
  x(s) = \frac{s\frac{\gamma}{m} + \frac{k}{m}}{s^2 + s\frac{\gamma}{m} + \frac{k}{m}}p(s).
  \label{eqn:vib_lpf}
\end{equation}

\begin{figure}[t!]
  \begin{minipage}[t]{.46\textwidth}
    \centering
    % L B R T
    \includegraphics[trim=0 0 0 0,
    clip,width=0.7\textwidth]{plots_z_axis_improv/figures/my_isolator}
    \caption{Photograph of the home-build passive vibration isolator.}
    \label{fig:custom_isolator}
  \end{minipage}
\hfill
\begin{minipage}[t]{.46\textwidth}
  \centering
  % L B R T
  \includegraphics[trim=0 0 0 0,
  clip,width=0.5\textwidth]{plots_z_axis_improv/figures/mass-spring-damper.pdf}
  \caption{Schematic drawing of the bungee cord-based passive vibration
    isolation system.}
  \label{fig:isolation_lpf}
\end{minipage}
\end{figure}
To be effective, we need the cutoff frequency of this filter to be as small as possible, which means we need either $k$ small or $m$ large. It is difficult to control $k$, so we focus on making $m$ large, which is why there is a concrete block and books weighting the platform in Fig.~\ref{fig:custom_isolator}. The PSD which results after implementing this vibration mitigation scheme are shown in the top panel of Fig.~\ref{fig:psd_xy_off} as the red curve, which shows that the energy in the band from 10 to 80 Hz has been drastically attenuated. The reduction in low frequency vibration can also be seen in the red time series in bottom panel Fig.~\ref{fig:psd_xy_off}.

\section{Disturbances from Electrical Noise}
As noted, the above experiments were conducted in idealized circumstances: the $XY$-stage was powered off. We now move beyond that and conduct another similar set of experiments, this time with the $XY$-stage turned on. In the experiments to follow, the AFM is now always on the bungee system. The resulting PSD is shown as the blue curve in Fig.~\ref{fig:psd_xy_on_int}. In addition, the PSDs of $X$ and $Y$ axes are shown. 
Also plotted (against the right axis) in Fig.~\ref{fig:psd_xy_on_int} are FRFs of $G_{x,u_x}$ and $G_{y,u_y}$.

\begin{figure}[ht!]
  \begin{minipage}[t]{1\textwidth}
    \includesvg[width=1\textwidth]{plots_z_axis_improv/figures/initial_dfl_psd_xyon_intfan.svg}
    \caption{(left axis) PSDs of the $X$, $Y$, and $Z_d$ signals when the fan is powered by the C300. (right axis) FRFs of $G_{x,u_x}$ and $G_{y,u_y}$.}
    \label{fig:psd_xy_on_int}
  \end{minipage}
  \begin{minipage}[t]{1\textwidth}
    \includesvg[width=1\textwidth]{plots_z_axis_improv/figures/initial_dfl_psd_xyon_extfan.svg}
    \caption{PSDs of the $X$, $Y$, and $Z_d$ signals when the fan is powered by an external source.}
    \label{fig:psd_xy_on_ext}
  \end{minipage}
  \begin{minipage}[t]{1\textwidth}
    \includesvg[width=1\textwidth]{plots_z_axis_improv/figures/initial_dfl_time_xyon.svg}
    \caption{Time series of $Z_d$ when (blue) the fan is powered by the C300 and (orange) powered by an external source.}
    \label{fig:psd_xy_on_time}
  \end{minipage}
  % \caption{The blue and red curves (left axis) are the PSD of the deflection signal with $XY$-stage off. The black curve is the FRF $H_{Z,u_Z}$.}
  % \label{fig:psd_xy_on}
\end{figure}

There are two things to observe here. First, the resonances in the $XY$ stage now show up quite clearly in the $Z$-axis PSD. This is because the power amplifier output is not free of noise and thus, the $XY$-stage is now being driven, albeit, by a very small amount. This motion is coupled into the deflection signal. This can occur through both the sample tilt phenomenon discussed in Section~\ref{sec:non_param_frf} or through actual out-of-plane motion of the $XY$-stage. In either case, this is one reason low noise power amplifiers are desirable. 
Second, we have picked up a large spike in all three PSDs at 380~Hz and 760 Hz (the second harmonic of 380 Hz). Although there are sharp spike above in Fig.~\ref{fig:psd_xy_off}, those correspond to harmonics of 60~Hz. The spikes here at 380~Hz and 760~Hz are new features and not harmonics of 60~Hz.

\begin{figure}
  \begin{subfigure}{.48\textwidth}
    \centering
    \includegraphics[width=0.8\textwidth]{plots_z_axis_improv/figures/c300_fan.jpg}
    \caption{ }
    \label{fig:c300_fan_pic}
  \end{subfigure}
  \begin{subfigure}{.48\textwidth}
    \centering
    \includesvg[width=1\textwidth]{plots_z_axis_improv/figures/fan_voltage.svg}
    \caption{ }
    \label{fig:c300_fan_voltage}
  \end{subfigure}
  \caption{(a) Photgraph of the C300 cooling fan. (b) Time-series of the fan voltage when the fan is plugged into the C300 circuit board (blue) and un-plugged (orange). In (b), the $x$-axis grids are spaced (1/380) seconds apart.}
  \label{fig: }
\end{figure}

Observe that the 380~Hz spike also occurs in the $X$ and $Y$ axis PSDs. We can trace this spike (mostly through luck) to the cooling fan inside the C300. If we unplug the fan from the circuit board (see Fig.~\ref{fig:c300_fan_pic}) and run it from an external power source, we get the orange curves in Fig.~\ref{fig:psd_xy_on_ext}: the spikes at 380~Hz and 760~Hz are now completely gone from all three PSDs. Fig.~\ref{fig:psd_xy_on_time} compares $Z_d$ time-series data for two scenarios, which shows a significant reduction in the overall amplitude.

The time-series in Fig.~\ref{fig:c300_fan_voltage} shows the fan voltage supply when the fan is plugged in (blue) and un-plugged (red). The period of oscillation in the blue curve is approximately 380~Hz. Evidently, the power source driving the fan inside the C300 is insufficiently decoupled from the voltage driving piezo stage. Thus, the XY stage oscillates at 380~Hz and this is coupled into the deflection via sample tilt.

\subsubsection{Results}\label{sec:bungee_results}
\begin{figure}[t!]
  \begin{subfigure}{.48\textwidth}
    %                     L B R T  
    \includesvg[width=1\textwidth]{plots_z_axis_improv/figures/raster_nobungee.svg}
    \caption{}
    \label{fig:raster_no_bung}
  \end{subfigure}
  \begin{subfigure}{.48\textwidth}
    %                     L B R T  
    \includesvg[width=1\textwidth]{plots_z_axis_improv/figures/raster_bungee.svg}
    \caption{ }
    \label{fig:raster_with_bung}
  \end{subfigure}
  \caption{Raster scan results over a 5 micron square area of the CS20-NG sample grating. The two bottom panels show a cross section of the rows of pixels indicated by color in the top two panels. (left) Before disturbance mitigation and (right) with both vibration isolation and isolating the C300 fan's electrical supply.}
  \label{fig:raster_dist_results}
\end{figure}
Fig.~\ref{fig:raster_dist_results} shows two raster scans of the CS20-NG sample grating. The scans were taken over a 5 micron square area at a scan rate of 1~Hz. The scan shown in Fig.~\ref{fig:raster_no_bung} was taken with the standard setup: i.e., the AFM is positioned on a table and the C300 fan is driven from the internal power supply. The scan shown in Fig.~\ref{fig:raster_with_bung} was taken with both mitigations, that is, using the bungee-based vibration isolator and with an external power source driving the C300 fan. Both scans were taken back to back with the same tip and the scan in \ref{fig:raster_no_bung} was taken first.

The bottom two panels show a cross section of the pixels indicated by the red and blue lines in the images. Of particular note are the red curves, which show the performance over the flat areas of the grating. The improvement seen in the right panel is drastic compared to the native instrument.

\subsubsection{Disadvantages}
The bungee cord vibration isolation method is not without disadvantages. The most notable problem is we cannot control the damping. From \eqref{eqn:vib_lpf}, the system damping $\zeta$ is given by
\begin{equation}
  \zeta = \frac{\gamma}{\sqrt{km}}.
\end{equation}
Thus, by increasing $m$, we decrease the damping, which means that near the natural frequency of our low pass filter, we have introduced a resonance with little damping. This will amplify vibrations whose frequency is near $\sqrt{k/m}$. However, these will be very low frequency oscillations, and if we follow the common practice of de-trending each scan line, do not seem to present significant difficulties.

% In Fig.~\ref{fig:raster_dist_results}, we de-trended each scan line. While this is a common post-processing technique in AFM, it introduces some artifacts and hides others. For example, in Fig.~\ref{fig:raster_dist_results}, it would appear that the area between the holes (in the $X$-directions) is higher than the flat areas between the holes in the $Y$-direction. We do not expect this to be the case from the specification of the CS20-NG. We may alternatively, de-trend the entire plane. An example of this is shown in Fig.~\ref{fig:undulation}.

% \begin{figure}[t!]
%   \includesvg[width=0.5\textwidth]{plots_z_axis_improv/figures/raster_no_bungee_mesh}
%   \includesvg[width=0.5\textwidth]{plots_z_axis_improv/figures/raster_bungee_mesh}
%   \caption{}
%   \label{fig:undulation}
% \end{figure}

% What we see is that, indeed, the bungee has system has eliminated most of the local noise (i.e., along the $X$-direction). Arguably, the oscillations in the $Y$-direction, which would correspond to frequency content of less than a tenth of a Hz (the scans takes approximately 5 minutes), have become worse.

\section{Z-axis Control Design}\label{sec:zaxis_cs_control}
In Section~\ref{sec:zaxis-dist}, we eliminated or reduced many of the disturbances impinging on the $Z$-axis. 
This puts us in a position to increase the bandwidth without introducing building dynamics into our images.
The main challenge to increasing the $Z$-axis bandwidth is the bending mode resonance at 215 Hz, which can be seen in the FRF from $u_Z$ to $Z_{d}$ in Fig.~\ref{fig:z_control} (blue curve). We address this by inverting the complex pole-zero pair at 215 Hz. There are multiple advantages to this method: first, an inverse compensator still makes sense as a feedforward, open-loop compensator if the feedback path is broken. This,  situation can and does occur during parts of the CS cycle. Second, as we discuss further below, the inverse compensator requires no tuning as it is defined only by a fit to the measured FRF and this can be almost completely automated.

\begin{figure}[b!]
  \centering
  \includesvg[scale=0.9]{plots-afm-cs-final/figures/z_control_design.svg}
  \caption{}
  \label{fig:z_control}
\end{figure}
The entire $Z$-axis controller consists of a PI controller, $D_I(z)$ cascaded with the resonance inversion, $D^{-1}(z)$. The inclusion of $D^{-1}$ allows us to substantially increase the PI gain and achieve a closed-loop bandwidth of about 480 Hz. This is the black curve in Fig.~\ref{fig:z_control}.
For comparison, the red curve in Fig.~\ref{fig:z_control} shows the closed-loop FRF without the inverse compensator, which experiments indicate is unstable.

One challenge to this approach is the system gain and resonance at 215~Hz changes not only day-to-day but also (and especially) when changing cantilevers. This is illustrated in Fig.~\ref{fig:z_evolution}, which shows the FRF near the mode for two three different cantilevers. Two are of the same make and model.

One cause for such different gains is variation in the length of the cantilever (and possibly how the laser was adjusted). This is illustrated in Fig.~\ref{fig:z_axis_gain}. Here, we consider a cantilever with length $h$ that rests on the surface of some specimen with a nominal angle of $\theta$. In this drawing, the laser is perpendicular to the sample surface. Given a vertical perturbation $\Delta z$, we have that
\begin{equation}
  \Delta \alpha \approx \frac{d}{h} \Delta z,
\end{equation}
where $d$ is the distance from the cantilever to the detector and $\Delta \alpha$ is the change in position of the incident laser spot on the detector. Thus, given the same change in the vertical position, we will see a larger change in the deflection signal for a shorter cantilever. In other words, a short cantilever will exhibit a larger DC-gain in the $G_{u_Z,Z_d}$ transfer function. 
\begin{figure}
    \begin{minipage}[t]{.46\textwidth}
    %                     L B R T  
    \includesvg[width=1\textwidth]{plots-afm-cs-final/figures/z_cant_evolution.svg}
    \caption{FRFs of three different cantilevers, showing substantial differences in the DC-gain and smaller, but still significant differences the frequency of the modes.}
  \label{fig:z_evolution}
\end{minipage}
\hfill
  \begin{minipage}[t]{.46\textwidth}
    % L B R T  
  \includegraphics[width=1\textwidth]{plots-afm-cs-final/figures/z_axis_gain_schematic-crop.pdf}
    \caption{Schematic drawing of how the length of the cantilever affects the $z$-axis gain.}
    \label{fig:z_axis_gain}
  \end{minipage}
\end{figure}

Fig.~\ref{fig:z_evolution} shows the frequency response of $G_{u_Z,Z_d}$ near the bending mode for three different cantilevers. Cantilevers (A) and (B) are both AppNano SICON cantilevers and have a nominal length of 450 microns. Cantilever (C) is an NCLR and has a nominal length of 225 microns. Interestingly, the SICON cantilevers show substantial variation. Unfortunately, the manufacture does not provide a tolerance on the nominal length, so it is difficult to tease out whether that variation is due to manufacturing variability or other factors not explained by this analysis.

Notably, the frequency of the pole and zero do appear to shift and our inversion scheme is not robust to this.
To deal with this, I have built a (mostly) automated system ID routine into the imaging software. This routine is a specialized version of the techniques described previously in Chapter~\ref{chap:modeling}. First, it obtains an FRF of the bending mode over a frequency range spanning 180~Hz to 240~Hz (the same set of points as in Fig.~\ref{fig:z_evolution}). The input and output sinusoids are demodulated in quasi-realtime as they come off the FPGA. Once this is complete, a 2-pole, 2-zero transfer function model of the form
\begin{equation*}
  \hat{D}(z) = k \frac{z^2 + b_1z + b_o}{z^2 + a_1z + a_o}
\end{equation*}
is fit to the FRF, using the same optimization scheme as \eqref{eqn:logfit}.
This is done inside the LabView VI by calling a custom DLL, which leverages CMPFIT~\cite{cmpfit,markwardt_mpfit_2009}, a Levenberg-Marquardt~\cite{more_levenberg_1978} routine written in C.
To promote a stable fit, the optimization enforces the necessary conditions that
\begin{align*}
  |a_1| &< 2, \quad  |a_o| < 1\\
  |b_1| &< 2, \quad  |b_o| < 1.
\end{align*}
The routine then checks that both the poles and zeros are indeed stabile, saves the data to a JSON file and passes the transfer function parameters into the imaging portion of the application which finally uploads the parameters into the FPGA imaging bitfile. Optionally, one can by-pass this step and simply load the previously saved JSON file.

One of the benefits of this approach is that the DC-gain of the transfer function $G_{u_Z,Z_d}$  becomes (approximately) normalized to unity, which makes re-tuning the control system after changing tips far easier to non-existent. The benefit to automating the process is that it drastically reduces the friction required to obtain an up-to-date compensator, which means that an up-to-date compensator is more likely to be used~\cite{abramovitch_25years_2015}.

Fig.~\ref{fig:afm_bd_dinv} shows a block diagram if the $Z$-axis control loop. We point out a small change from Chapter~\ref{chap:cs_init}: the addition of $D^{-1}(z)$ changes the correct signal to use to represent the sample surface. If we take the output of the entire compensator, $u_Z=D_ID^{-1}e_z$, then we will get a lot of wiggles in the resulting signal. Rather, we need to take only the output of the integrator to represent the surface. 
\begin{figure}
  \centering
  \includegraphics[scale=0.5]{plots-afm-cs-final/figures/AFM_loop_Dinv-crop.pdf}
  \caption{Block diagram of the $Z$-axis control loop with the inverse compensator. }
  \label{fig:afm_bd_dinv}
\end{figure}

It should be noted that this control is sufficient to eliminate the limit-cycle behavior described in Section~\ref{sec:aproachspeed}: we have done many CS scans across many variations of the CS-state machine using this control scheme and the limit cycle has not appeared. The resulting bandwidth of about 480~Hz is substantially higher than what we had in Chapter~\ref{chap:cs_init}. Unfortunately, although I recorded the Integral gain used in the initial implementation described in Chapter~\ref{chap:cs_init}, I do not know what the system gain was for that specific cantilever, so it is not possible to make that comparison quantitatively. Based on the improved scan rates achieved in the next chapter,  (see e.g., Fig.~\ref{fig:pixel_rows}), I would estimate the improvement to be between 5 and 10 times.

% \subsubsection{Caveats to Inversion}
% \textbf{ACTUALLY: maybe this is really just larger oscillations from a larger move size??}

% It seems that inversion favors raster scanning over CS.

% The issue, I believe and need to demonstrate more fully, is that the nature of the resonance can shift depending on the setpoint and especially the input magnitude (for sinusoidal inputs). During CS, we ask the system to operate over a wider range, and thus these non-linearties play a larger role. This is evident in Fig.~\ref{fig:dinv_CS_decay}, where we have connected multiple $\mu$-paths together. What we see is oscillations after the engagement and in the first scan, but which decay after the first hole. Thus, the inversion is more than capable when operating in the limited range around which it was identified, but performance degrades during the approach, which is away from the point at which it was identified.

% \begin{figure}
%   \centering
%   \includesvg[scale=0.8]{plots-afm-cs-final/figures/dinv_CS_cycle_decay.svg}
%   \caption{}
%   \label{fig:dinv_CS_decay}
% \end{figure}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "thesis_main"
%%% End:

### 2019-05-29 functions/@CsTools/bregman_split.m

@@ -1,0 +1,106 @@
+function [Ir] = bregman_split(I,E, mu, gam,maxiter,tol)
+% [Ir] = bregman_split(I,E, mu, gam,maxiter,tol)
+% Solve the CS Anylsis problem
+% 
+% min |\Psi x|_1  s.t. ||\Phi x - y||_2 < \sigma
+%
+% through Bregman Splitting.
+% 
+% Arguments
+% ---------
+%   I - sampled image with size n*m
+%   E - sample matrix with size n*m, 1 if sampled, 0 otherwise
+%   mu,gam - tuning vaiables - they are turned out to be very
+%   maxiter - max # of iteration
+%   tol - allowed error
+% 
+% Outputs
+% ------
+%   Ir - reconstrcuted image
+% 
+
+
+  
+  [n, m] = size(I);
+  
+  I_vec = CsTools.pixmat2vec(I);
+  E_vec = CsTools.pixmat2vec(E);
+  pix_idx = find(E_vec==1);
+  I = speye(n^2);
+  E_mat = I(pix_idx, :);
+  
+  u = I_vec.*E_vec;
+
+  y_full_sparse = zeros(n^2, 1);
+  w = zeros(n^2,1);
+  b_w = zeros(n^2,1);
+
+  y = I_vec(E_vec>0.5);
+  
+  
+  % Build the matrix
+  % A = mu *Phi^T*Phi + lambda * Del^T*Del + gamma*I.
+
+   A = mu*(E_mat'*E_mat) +  gam * I;
+
+  yk = y;
+  
+  max_outer_iter = 1000;
+
+  j = 1;
+  %fprintf('| outer-iter |    || Phi*x-y||_2     |\n');
+  fprintf(' | out-iter  | Residual |\n')
+  fprintf('----------------------------\n')
+  for outer_iter = 1:max_outer_iter
+    
+    %fprintf('loop time   | Lin Solver time |   dct time |   remainder    |\n')
+    for i = 1:maxiter
+      Ety = y_full_sparse;
+      Ety(pix_idx) = yk;
+      
+      rhs = mu*Ety + .1*gam*idct(w-b_w);
+
+      %uk_1 = A\rhs; % Inv(A)*rhs
+      % use conjugate gradient with pre-conditioner instead. WAY faster.
+      [uk_1, ~, ~] = pcg(A, rhs, 1e-8, 100); %, L1, L1T);
+     
+      dct_uk1 = 10*dct(uk_1);
+
[…]

### 2019-05-29 functions/@CsTools/l1qc_logbarrier.m

@@ -1,0 +1,116 @@
+% l1qc_logbarrier.m
+%
+% Solve quadratically constrained l1 minimization:
+% min ||x||_1   s.t.  ||Ax - b||_2 <= \epsilon
+%
+% Reformulate as the second-order cone program
+% min_{x,u}  sum(u)   s.t.    x - u <= 0,
+%                            -x - u <= 0,
+%      1/2(||Ax-b||^2 - \epsilon^2) <= 0
+% and use a log barrier algorithm.
+%
+% Usage:  xp = l1qc_logbarrier(x0, A, At, b, opts)
+%
+% x0 - Nx1 vector, initial point.
+%
+% A - Either a handle to a function that takes a N vector and returns a K 
+%     vector , or a KxN matrix.  If A is a function handle, the algorithm
+%     operates in "largescale" mode, solving the Newton systems via the
+%     Conjugate Gradients algorithm.
+%
+% At - Handle to a function that takes a K vector and returns an N vector.
+%      If A is a KxN matrix, At is ignored.
+%
+% b - Kx1 vector of observations.
+%
+%   opts: a struct (create with CsTools.l1qc_opts) with the following fields: 
+%         .epsilon : denoising tolerance (as in (1) above). 
+%         .mu :      log-barrier weight is multiplied by mu each LB iteration
+%                    (try 10).
+%         .cgtol:    tolerance for the conjugate gradient (CG) solver (try 1e-8).
+%         .cgmaxiter: maximum iterations for the CG solver (try 200).
+%         .lbtol :   Determines the total number of log-barrier iterations
+%                    (try  1e-3).
+%         .newton_tol : newton iterations terminate when the 
+%                       newton decrement < newton_tol (try newton_tol = lbtol).
+%         .newton_max_iter : Maximum number of newton iterations (try 50).
+%         .verbose : How much to print. Silent if verbose =0, prints info each
+%         log-barrier iteration if verbose =1, and also each newton iteration
+%         if verbose = 2.
+%
+
+% Written by: Justin Romberg, Caltech
+% Email: jrom@acm.caltech.edu
+% Created: October 2005
+%
+
[…]

### 2019-05-29 functions/@CsTools/l1qc_newton.m

@@ -1,0 +1,171 @@
+% l1qc_newton.m
+%
+% Newton algorithm for log-barrier subproblems for l1 minimization
+% with quadratic constraints.
+%
+% Usage: 
+% [xp,up,niter] = l1qc_newton(x0, u0, A, At, b, epsilon, tau, 
+%                             newtontol, newtonmaxiter, cgtol, cgmaxiter)
+%
+% x0,u0 - starting points
+%
+% A - Either a handle to a function that takes a N vector and returns a K 
+%     vector , or a KxN matrix.  If A is a function handle, the algorithm
+%     operates in "largescale" mode, solving the Newton systems via the
+%     Conjugate Gradients algorithm.
+%
+% At - Handle to a function that takes a K vector and returns an N vector.
+%      If A is a KxN matrix, At is ignored.
+%
+% b - Kx1 vector of observations.
+%
+% epsilon - scalar, constraint relaxation parameter
+%
+% tau - Log barrier parameter.
+%
+% newtontol - Terminate when the Newton decrement is <= newtontol.
+%         Default = 1e-3.
+%
+% newtonmaxiter - Maximum number of iterations.
+%         Default = 50.
+%
+% cgtol - Tolerance for Conjugate Gradients; ignored if A is a matrix.
+%     Default = 1e-8.
+%
+% cgmaxiter - Maximum number of iterations for Conjugate Gradients; ignored
+%     if A is a matrix.
+%     Default = 200.
+%
+% Written by: Justin Romberg, Caltech
+% Email: jrom@acm.caltech.edu
+% Created: October 2005
+%
+
+
+function [xp, up, niter, cgit_tot] = l1qc_newton(x0, u0, A, At, b, epsilon, tau, newtontol,...
+    newtonmaxiter, cgtol, cgmaxiter, Tii, verbose) 
+
+
+  % line search parameters
+  alpha = 0.01;
+  beta = 0.5;
+  
+  
+  % initial point
+  x = x0;
+  u = u0;
+  [r, fu1, fu2, fe, f] =  f_eval(A, x, u, b, epsilon, tau);
+  
+  
+  if verbose
+    fprintf('Newton-iter | Functional | Newton decrement |  Stepsize  |  cg-res | cg-iter | backiter |    s     |\n');
+  end
+  
[…]

### 2019-05-29 functions/@CsTools/mu_path_mask.m

@@ -1,0 +1,50 @@
+% [pix_mask_mat, pix_idx] = mu_path_mask(mupath_len, n, m, samplingRatio, repeat_sampling)
+%
+% Return Mu path sampling mask
+%
+% Arguments
+% ----------
+%   mupath_len : size (in pixels) of mu path pattern
+%   n,m : image size
+%   samplingRatio : (Percentage) - total pixels to sample = samplingRatio*n*m
+%   repeat_sampling : (true|false) If true, repeat sampling allowed. 
+%                     If false: repeat sampling not allowed.
+% Returns
+% --------
+%   pix_idx : a vector of sampled pixel indeces.
+%   pix_mask_mat : an n by m mu path pattern mask, which contains 1's in the
+%                  mu-path areas, and zeros elsewhere.
+
+
+function [pix_mask, pix_idx] = mu_path_mask(mupath_len, n, m, samplingRatio, repeat_sampling)
+   
+    if nargin < 5
+        repeat_sampling = false;
+    end
+
+    pix_mask = zeros(n,m);
+
+    while (sum(sum(pix_mask))<samplingRatio*n*m)
+        
+        if repeat_sampling
+            
+            rand_i = randi(n);
+            rand_j = randi([2-mupath_len m]);            
+            pix_mask(rand_i,max(rand_j,1):min(rand_j+mupath_len-1,n)) = 1;            
+            
+        else            
+            rand_i = randi(n);
+            rand_j = randi(m-mupath_len+1);
+            if sum(pix_mask(rand_i,rand_j:rand_j+mupath_len-1)) < 0.5
+                pix_mask(rand_i,rand_j:rand_j+mupath_len-1) = 1;
+            end            
+        end
+    end
+    
+    pix_idx = find(CsTools.pixmat2vec(pix_mask)>0.5);
+   
+end
+
+
+
+

### 2019-05-29 functions/@CsTools/pixvec2mat.m

@@ -1,0 +1,24 @@
+function Mpix = pixvec2mat(vpix, nrows, ncol)
+  % Mpix = pixvec2mat(vpix, nrows, ncol)
+  %
+  % Converts the (forced to be) column vector vpix into a matrix such that
+  % The rows of Mpix are taken as contiguous chunks of vpix. I.e.,
+  %
+  % Mpix = [ vpix(1:ncol)';
+  %          vpix(ncol+1:2*ncol)'
+  %              :              ]
+  % where ncol = length(vpix)/nrows;
+  %
+  % See Also: PixelVectorToMatrix, which is a less efficient implementation of
+  % the same operation.
+
+  % assure vpix is a column vector to start
+  vpix = vpix(:);
+  
+  if nargin == 2
+    Mpix = reshape(vpix, [], nrows)';
+  else
+    Mpix = reshape(vpix', nrows, ncol)';
+  end
+  
+end

### 2019-05-29 functions/Core_Nesterov_mine.m

@@ -1,0 +1,263 @@
+function [xk,niter] = Core_Nesterov_mine(...
+            A,At,b,mu,delta,opts)
+% [xk,niter,residuals,outputData,opts] =Core_Nesterov(A,At,b,mu,delta,opts)
+%
+% Solves a L1 minimization problem under a quadratic constraint using the
+% Nesterov algorithm, without continuation:
+%
+%     min_x || U x ||_1 s.t. ||y - Ax||_2 <= delta
+% 
+% If continuation is desired, see the function NESTA.m
+%
+% The primal prox-function is also adapted by accounting for a first guess
+% xplug that also tends towards x_muf 
+%
+% The observation matrix A is a projector
+%
+% Inputs:   A and At - measurement matrix and adjoint (either a matrix, in which
+%               case At is unused, or function handles).  m x n dimensions.
+%           b   - Observed data, a m x 1 array
+%           muf - The desired value of mu at the last continuation step.
+%               A smaller mu leads to higher accuracy.
+%           delta - l2 error bound.  This enforces how close the variable
+%               must fit the observations b, i.e. || y - Ax ||_2 <= delta
+%               If delta = 0, enforces y = Ax
+%               Common heuristic: delta = sqrt(m + 2*sqrt(2*m))*sigma;
+%               where sigma=std(noise).
+%           opts - see NESTA_opts.
+%  Outputs:
+%           xk  - estimate of the solution x
+%           niter - number of iterations
+%           residuals - first column is the residual at every step,
+%               second column is the value of f_mu at every step
+%           opts - the structure containing the options that were used      
+%
+% Written by: Jerome Bobin, Caltech
+% Email: bobin@acm.caltech.edu
+% Created: February 2009
+% Modified: May 2009, Jerome Bobin and Stephen Becker, Caltech
[…]

### 2019-05-29 functions/NESTA_opts.m

@@ -1,0 +1,63 @@
+%               This is a structure that contains additional options,
+%               some of which are optional.
+%               The fieldnames are case insensitive.  Below
+%               are the possible fieldnames:
+%               
+%               opts.U and opts.Ut - Analysis/Synthesis operators as function
+%               handles.
+%               opts.normU - if opts.U is provided, this should be norm(U)
+% 
+%               opts.alpha_v - weight for vertical TV (default 0)
+%               opts.alpha_h - weight for horizontal TV (default 0)
+% 
+%               opts.MaxIntIter - number of continuation steps.
+%                 default is 5
+%               opts.maxiter - max number of iterations in an inner loop.
+%                 default is 10,000
+% 
+%               opts.TolVar - tolerance for the stopping criteria, i.e.,
+%                             when the relative change in the objective 
+%                             function is less than TolVar.
+%               opts.Verbose - if this is 0 or false, then very
+%                   little output is displayed.  If this is 1 or true,
+%                   then output every iteration is displayed.
+%                   If this is a number p greater than 1, then
+%                   output is displayed every pth iteration.
+%               opts.errFcn - if this is a function handle,
+%                   then the program will evaluate opts.errFcn(xk)
+%                   at every iteration and display the result.
+%                   ex.  opts.errFcn = @(x) norm( x - x_true )
+
+function opts = NESTA_opts(varargin)
+    
+   p = inputParser();
+   U_default_fun = @(x) x;
+   p.addParameter('Verbose', true);
+  
+  
+   p.addParameter('MaxIntIter',5);
+   p.addParameter('TypeMin','L1');
+   p.addParameter('TolVar',1e-5);
+   
+   p.addParameter('xplug',[]);
+   p.addParameter('normU',[]);  % so we can tell if it's been set
+   
+   p.addParameter('errFcn',[]);
+
+   p.addParameter('U', U_default_fun);
+   p.addParameter('Ut', U_default_fun);
+   
+   p.addParameter('alpha_v', 0);
+   p.addParameter('alpha_h', 0);
+   
+   p.parse(varargin{:});
+   
+   opts = p.Results;
+   
+   if ~isequal(opts.U, U_default_fun)
+       opts.U_userSet = true;
+   else
+       opts.U_userSet = false;
+       opts.normU = 1;
+   end
+end

### 2019-05-29 functions/PATHS.m

@@ -1,0 +1,108 @@
+classdef PATHS
+  %PATHS Summary of this class goes here
+  %   Detailed explanation goes here
+  
+  properties
+  end
+  
+  methods (Static)
+    function [ PATH ] = exp()
+      % PATH constant to where all experimental data is stored for the
+      if ispc
+        PATH = 'Z:\afm-cs';
+      else
+        PATH = '/media/labserver/afm-cs';
+      end
+    end
+    function path = tmech_fig()
+       path = '/home/arnold/gradschool/publications/afm-cs-tmech/latex/figures/'; 
+    end
+    function path = tmech_table()
+      path = '/home/arnold/gradschool/publications/afm-cs-tmech/latex/tables';
+    end
+    
+    function path = cs_final_fig()
+      path = '/home/arnold/gradschool/thesis/plots-afm-cs-final/figures';
+    end
+    function path = cs_final_table()
+      path = '/home/arnold/gradschool/thesis/plots-afm-cs-final/tables';
+    end
+    function path = thesis_root()
+      path = '/home/arnold/gradschool/thesis';
+    end
+    function path = defense_fig()
+      path = '/home/arnold/gradschool/thesis/defense/presentation/figures';
+    end
+    function [ PATH ] = step_exp()
+      % PATH constant to where all experimental data for step experiments 
+      % (for the x-y plane) is stored for the.
+        PATH = fullfile(PATHS.exp(), 'step-exps');
+    end
+    
+    function PATH = cs_image_data(size, date_dir)
+      PATH = fullfile(PATHS.exp(), 'imaging', 'cs-imaging', size, date_dir);
+    end
+    
+    function PATH = raster_image_data(size, date_dir)
+      PATH = fullfile(PATHS.exp(), 'imaging', 'raster', size, date_dir);
+    end
+    
+    function [ PATH ] = CS_root()
+    % PATH constant to where all experimental data is stored for the
+    % MPC journal paper.
+      if ~ispc()
+        PATH = fullfile(getMatPath, 'afm-cs');
+      else
+        PATH = 'C:\Users\arnold\Documents\afm-cs';
+      end
+    end
+    
+    function [ PATH ] = labview()
+    % PATH constant to where all experimental data is stored for the
+    % MPC journal paper.
+      
+      PATH = fullfile(PATHS.CS_root, 'labview');
+    end
+    
+    function path = reconstruction_BP()
[…]

### 2019-05-29 functions/mkfig.m

@@ -1,0 +1,36 @@
+%  F = mkfig(num, width, height)
+%
+function F = mkfig(num, width, height, presentation)
+if nargin <4
+  presentation = false;
+end
+F = figure(num); clf
+axes('FontName','Times New Roman') % Set axis font style
+box('on'); % Define box around whole figure
+hold on;
+
+% First, set units to inches. Then get the (x0,y0) position, and only reset the
+% width and height. Because it is annoying to always have the figure start at
+% (0,0).
+set(F, 'Units', 'inches');
+pos = get(F, 'Position');
+
+lft = pos(1);
+bt = pos(2);
+
+% experimental: keep top the same
+ ht_diff = height - pos(4);
+ wd_diff = width - pos(3);
+set(F, 'Units', 'Inches', 'Position', [lft-wd_diff, bt-ht_diff, width, height],...
+    'PaperUnits', 'Inches', 'PaperSize', [width, height],...
+    'InvertHardcopy', 'off');
+
+if presentation
+set(F, 'Color', fig_color);
+else
+  set(F, 'Color', 'w');
+end
+
+
+
+end

### 2019-05-29 functions/remove_ticks.m

@@ -1,0 +1,7 @@
+function remove_ticks(ax)
+   % Remove the x and y axis ticks labels.
+   for k=1:length(ax)
+       set(ax(k), 'XTickLabel', [])
+       set(ax(k), 'yTickLabel', [])
+   end
+end

### 2019-05-29 functions/save_fig.m

@@ -1,0 +1,62 @@
+
+
+function save_fig(fig, fpath_no_ext, for_presentation)
+% save a figure as either pdf (for_presentation=true) or svg
+% (for_presentation=false). In both cases, the background color will be set to
+% the color defined in the function fig_color_presentation() and fig_color()
+% respectively. 
+%
+% for_presentation is optional, default is false.
+
+  if nargin <3
+    for_presentation = false;
+  end
+
+  if for_presentation
+    ext = '.pdf';
+    bg = fig_color_presentation();
+  else
+    ext = '.svg';
+    bg = [1, 1, 1]; %fig_color();
+  end
+
+  % Check to see if fpath has a file extension:
+  % Cant see how to match a period. Docs say \x{N} will match character with 
+  % hexedecimal of value N. A period is 2E in Hex...
+  expr = '\x{2E}[A-Za-z]{4,4}$';
+  idx = regexp(fpath_no_ext, expr);
+  if ~isempty(idx)
+    ext_old = fpath_no_ext(idx:end);
+    fpath = [fpath_no_ext(1:idx-1), ext];
+    warning('File extension detected. Replacing %s with %s\n', ext_old, ext)
+  else
+    fpath = [fpath_no_ext, ext];
+  end
+
+  
+  
+  % set the figure to have the right background and not be insane.  
+  set(fig, 'InvertHardcopy', 'off', 'Color', bg);
+
+  % set the axes to have the right background. Not sure if the figure can have
+  % children besides axes...
+  childs = get(fig, 'Children');
+  for k=1:length(childs)
+    if isa(childs(k), 'matlab.graphics.axis.Axes') || isa(childs(k), 'matlab.graphics.illustration.Legend')
+      set(childs(k), 'Color', bg);
+    else
+      fprintf('Dont know what to do with child of type %s\n', class(childs(k)));
+    end
+  end
+
+  if strcmp(ext, '.pdf')
+    print(fig, '-dpdf', fpath)
+  elseif strcmp(ext, '.svg')
+    saveas(fig, fpath)
+  else
+    warning('Something went wrong. Dont know what to do with extenstion %s\n', ext)
+  end
+
+
+
+end

### 2019-05-29 functions/tight_subplot.m

@@ -1,0 +1,64 @@
+function [ha, pos] = tight_subplot(Nh, Nw, gap, marg_h, marg_w, no_ticks)
+% tight_subplot creates "subplot" axes with adjustable gaps and margins
+%
+% [ha, pos] = tight_subplot(Nh, Nw, gap, marg_h, marg_w, no_ticks)
+%
+%   in:  Nh      number of axes in hight (vertical direction)
+%        Nw      number of axes in width (horizontaldirection)
+%        gap     gaps between the axes in normalized units (0...1)
+%                   or [gap_h gap_w] for different gaps in height and width 
+%        marg_h  margins in height in normalized units (0...1)
+%                   or [lower upper] for different lower and upper margins 
+%        marg_w  margins in width in normalized units (0...1)
+%                   or [left right] for different left and right margins 
+%        no_ticks: (boolean) if true, remove ticks
+%  out:  ha     array of handles of the axes objects
+%                   starting from upper left corner, going row-wise as in
+%                   subplot
+%        pos    positions of the axes objects
+%
+%  Example: ha = tight_subplot(3,2,[.01 .03],[.1 .01],[.01 .01])
+%           for ii = 1:6; axes(ha(ii)); plot(randn(10,ii)); end
+%           set(ha(1:4),'XTickLabel',''); set(ha,'YTickLabel','')
+% Pekka Kumpulainen 21.5.2012   @tut.fi
+% Tampere University of Technology / Automation Science and Engineering
+
+  if nargin<3; gap = .02; end
+  if nargin<4 || isempty(marg_h); marg_h = .05; end
+  if nargin<5; marg_w = .05; end
+  if nargin<6; no_ticks = true; end
+  if numel(gap) == 1
+    gap = [gap gap];
+  end
+  if numel(marg_w) == 1
+    marg_w = [marg_w marg_w];
+  end
+  if numel(marg_h) == 1
+    marg_h = [marg_h marg_h];
+  end
+  axh = (1-sum(marg_h)-(Nh-1)*gap(1))/Nh;
+  axw = (1-sum(marg_w)-(Nw-1)*gap(2))/Nw;
+  py = 1-marg_h(2)-axh;
+  % ha = zeros(Nh*Nw,1);
+  ii = 0;
+  ha = gobjects(Nh*Nw,1);
+  for ih = 1:Nh
+    px = marg_w(1);
+    
+    for ix = 1:Nw
+      ii = ii+1;
[…]

### 2019-05-29 matlab_wrapper.py

@@ -1,0 +1,13 @@
+#!/usr/bin/python
+
+import matlab.engine as me
+import sys
+
+script = sys.argv[1]
+
+eng = me.connect_matlab()
+
+eng.run(script, nargout=0)
+
+# close all the leftover figures.
+eng.close('all')

### 2019-05-29 plot_bptv_vs_bp.m

@@ -1,0 +1,99 @@
+clear
+addpath('functions/')
+clc
+
+
+im_og = double(rgb2gray(imread('dnn_dna_gt.png')));
+im_og = im_og / max(im_og(:));
+n = 256;
+im_og = im_og(1:n, 1:n);
+
+mu_len = 25;
+samp_frac = 0.25;
+
+[mask, pix_idx] = CsTools.mu_path_mask(mu_len, n, n, samp_frac);
+
+U_fun = @(x) idct(x);
+Ut_fun = @(x) dct(x);
+
+E_fun = @(x) CsTools.E_fun1(x, pix_idx);
+Et_fun = @(x) CsTools.Et_fun1(x, pix_idx, n, n);
+
+
+opts = NESTA_opts('U', U_fun, 'Ut', Ut_fun, 'alpha_v', 0.25, 'alpha_h', 1,...
+    'verbose', 5, 'TolVar', 1e-5);
+
+b = CsTools.pixmat2vec(im_og);
+b = b(pix_idx);
+
+mu = 1e-3;
+delta = .001
+
+x_bptv = NESTA_mine(E_fun, Et_fun, b, mu, delta, opts);
+X_bptv = CsTools.pixvec2mat(x_bptv, n);
+
+
+opts = NESTA_opts('U', U_fun, 'Ut', Ut_fun, 'alpha_v', 0, 'alpha_h', 0,...
+    'verbose', 5, 'TolVar', 1e-5);
+
+
+x_bp = NESTA_mine(E_fun, Et_fun, b, mu, delta, opts);
+X_bp = CsTools.pixvec2mat(x_bp, n);
+
+
+[Fig_dna_og, ax_dna_og] = imshow_local(im_og, 1);
+[Fig_dna_bp, ax_dna_bp] = imshow_local(X_bp, 2);
+[Fig_dna_bptv, ax_dna_bptv] = imshow_local(X_bptv, 3);
+
+% bottom, left corner of box
+x0 = 55;
+y0 = 66;
+
+y1 = 24;
+x1 = 96;
+
+slice_x = x0:x1;
+slice_y = y1:y0;
+
+size(slice_x)
+size(slice_y)
+
+plot_box(ax_dna_og, x0, y0, x1, y1);
+
+[Fig_dna_og_zoom, ax_dna_og_zoom] = imshow_local(im_og(slice_y, slice_x), 4);
[…]

### 2019-05-30 latex/afm-cs-main.tex
Update to latest results, with xy-feedforward.

@@
 
-\begin{figure}
-  \includesvg[width=1\columnwidth]{figures/cs_raster_images_4-26-2019}
+\begin{figure*}
+  \includesvg[width=1\textwidth]{figures/cs_raster_images_4-26-2019}
   \caption{Raster and compressed sensing images of a 5 micron square area of the
@@
   \label{fig:resultsF1_images}
-\end{figure}
+\end{figure*}
 
@@
   \centering
-  \caption{Performance metrics for the scans taken on 4-26-2019. All CS images
-    filtered with TV denoising, $\mu$=100.}
+  \caption{Performance metrics for raster and CS scans.}
   \begin{tabular}{cccccc}
@@
 \begin{figure*}[t!]
-  \includesvg[width=1\textwidth]{figures/cs_raster_pixel_rows_3-20-2019.svg}
+  \includesvg[width=1\textwidth]{figures/cs_raster_pixel_rows_4-26-2019.svg}
   \caption{Rows of pixels, as indicated by the red lines in
@@
 
+\subsection{Comparison to sub-line sampling}
+Compressed sensing so far does not look good if we compare to subline sampling.
+The left panel of Fig.~\ref{fig:subline} shows a 5~Hz raster scan taken with 128 lines which takes approximately 25 seconds.
+We use that data to produce a 128 by 512 pixel image, and then use basic linear interpolation to fill produce a 512 by 512 pixel image.
+The CS image with the nearest acquisition time (15\% at 4~Hz) is shown in the right panel.
+The raster scan looks better and has basically the same RDI, and better SSIM and PSNR numbers.
+We conclude there is no reason to use CS.
+\begin{figure}
+  \includesvg[width=1\columnwidth]{figures/subline_vs_cs.svg}
+  \caption{(left) A 128 line raster scan interpolated onto 512 lines. (left) the CS scan with the nearest time.}
+  \label{fig:subline}
+\end{figure}
+
 \section{Conclusions}\label{sec:conclusions}

### 2019-05-30 latex/afm-cs-main.tex
Update simulations to cs20ng grating.

@@
 sample surface topography, material characteristics, and other surface
-properties, at the nanometer scale. AFMs acquire information about the sample
-through a variety of imaging modes, all of which rely on the deflection of the
-cantilever caused by the tip-sample interaction force. While the details of each
-of the modes are quite different, in general, feedback control is used to hold
+properties, with nanometer scale precision. AFMs acquire information about the sample by monitoring the deflection of the cantilever caused by the tip-sample interaction force. In general, 
+%AFMs acquire information about the sample
+%through a variety of imaging modes, all of which rely on the deflection of the
+%cantilever caused by the tip-sample interaction force. While the details of each
+%of the modes are quite different, in general, 
+feedback control is used to hold
 the deflection signal constant and information about the property of interest is
@@
 
-In addition to imaging static samples, AFM is increasingly being applied to
+In addition to imaging static samples, AFM is used to
 study dynamics in systems with nanometer-scale features
@@
     & \textit{\small detail of original} & \textit{\small detail of BPDN} & \textit{\small detail of BPVV} \\
+    \includesvg[width=0.16\textwidth]{figures/cs20ng_og.svg}
     %
-    \includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_gt_framed}
+    & \includesvg[width=0.16\textwidth]{figures/cs20ng_bp.svg}
     %
-    & \includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_40mu}
+    & \includesvg[width=0.16\textwidth]{figures/cs20ng_bptv.svg}
     %
-    & \includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_bptv_40mu}
+    & \includesvg[width=0.16\textwidth]{figures/cs20ng_og_zoom.svg}
     %
-    & \includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_gt_zoomin}
+    & \includesvg[width=0.16\textwidth]{figures/cs20ng_bp_zoom.svg}
     %
-    &\includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_40mu_zoomin}
-    %
-    &\includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_bptv_40mu_zoomin}\\
+    & \includesvg[width=0.16\textwidth]{figures/cs20ng_bptv_zoom.svg}\\
     % 

### 2019-05-30 plot_bptv_vs_bp.m

@@ -2,76 +2,98 @@ clear
 addpath('functions/')
 clc
 
+% ------------ Row 1, CS20NG -------------------------
+im_og = double(imread('cs20ng.png'));
+mu_len = 50;
+samp_frac = 0.15;
+n = size(im_og, 1);
 
+[mask, pix_idx] = CsTools.mu_path_mask(mu_len, n, n, samp_frac);
+
+figbase = 1;
+cp_bptv_bp(im_og, pix_idx, 'cs20ng', figbase)
+
+
+% ------------ Row 2, DNA -------------------------
 im_og = double(rgb2gray(imread('dnn_dna_gt.png')));
-im_og = im_og / max(im_og(:));
+
 n = 256;
 im_og = im_og(1:n, 1:n);
 
 mu_len = 25;
 samp_frac = 0.25;
+figbase = 100;
 
-[mask, pix_idx] = CsTools.mu_path_mask(mu_len, n, n, samp_frac);
+[mask, pix_idx] = CsTools.mu_path_mask(mu_len, n, n, samp_frac, figbase);
 
-U_fun = @(x) idct(x);
-Ut_fun = @(x) dct(x);
-
-E_fun = @(x) CsTools.E_fun1(x, pix_idx);
-Et_fun = @(x) CsTools.Et_fun1(x, pix_idx, n, n);
+cp_bptv_bp(im_og, pix_idx, 'dna')
 
 
-opts = NESTA_opts('U', U_fun, 'Ut', Ut_fun, 'alpha_v', 0.25, 'alpha_h', 1,...
-    'verbose', 5, 'TolVar', 1e-5);
+function cp_bptv_bp(im_og, pix_idx, prefix, figbase)
+    
+    im_og = im_og / max(im_og(:));
+    n = size(im_og, 1);
+    
+    U_fun = @(x) idct(x);
+    Ut_fun = @(x) dct(x);
+    
+    E_fun = @(x) CsTools.E_fun1(x, pix_idx);
+    Et_fun = @(x) CsTools.Et_fun1(x, pix_idx, n, n);
+    
+    
+    opts = NESTA_opts('U', U_fun, 'Ut', Ut_fun, 'alpha_v', 0.25, 'alpha_h', 1,...
+        'verbose', 5, 'TolVar', 1e-5);
+    
+    b = CsTools.pixmat2vec(im_og);
+    b = b(pix_idx);
+    
[…]

### 2019-06-04 latex/afm-cs-main.tex
Update on Overleaf.

@@
     & \textit{\small detail of original} & \textit{\small detail of BPDN} & \textit{\small detail of BPVV} \\
-    \includesvg[width=0.16\textwidth]{figures/cs20ng_og.svg}
-    %
-    & \includesvg[width=0.16\textwidth]{figures/cs20ng_bp.svg}
-    %
-    & \includesvg[width=0.16\textwidth]{figures/cs20ng_bptv.svg}
-    %
-    & \includesvg[width=0.16\textwidth]{figures/cs20ng_og_zoom.svg}
-    %
-    & \includesvg[width=0.16\textwidth]{figures/cs20ng_bp_zoom.svg}
-    %
-    & \includesvg[width=0.16\textwidth]{figures/cs20ng_bptv_zoom.svg}\\
+    % 
+    \includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_gt_framed}
+    %
+    & \includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_40mu}
+     % 
+    & \includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_bptv_40mu}
+     % 
+    & \includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_gt_zoomin}
+     % 
+    &\includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_40mu_zoomin}
+    %
+    &\includegraphics[width=0.16\textwidth]{figures-SBA/anothergrating_bptv_40mu_zoomin}\\
     % 

### 2019-06-06 latex/afm-cs-main.tex
Update bp/bptv simulation plots.

--- 2019-05-30 latex/afm-cs-main.tex
@@
 A comparison between BPDN and BPVV is shown in
-Fig.~\ref{fig:BPTV_demonstration}. Images of two different samples
-(a square grating and a DNA image) were acquired using an Agilent 5500
-AFM with a standard raster scan (first and fourth columns in the figure). These
-images were then resampled using a random $\mu$-path pattern of size 40 pixels
-with 25\% of the pixels sampled. Images were reconstructed using BPDN (second
-and fifth columns) and BPVV (third and sixth columns). The reconstruction
-results show the artifacts apparent in the BPDN reconstruction are largely
-mitigated using BPVV. Thus, in the remainder of the paper, we focus exclusively on BPVV.
-
+Fig.~\ref{fig:BPTV_demonstration}.
+The first column two raster scans: the top is 512 by 512 pixel image of a CS20NG grating acquired with an Agilent 5400 AFM and the bottom is a 256 by 256 pixel image of DNA acquired with an Agilent 5500 AFM.
+For the CS20NG grating, we sampled 15\% of the pixels with 50 pixel $\mu$-paths.
+We sampled 25\% of the DNA image with 25 pixel long $\mu$-paths.
+The second columns shows the full frame reconstructions using BPDN and the third columns shows the result using BPVV.
+The fourth column zooms in on the region indicated by the red box in column one.
+Similarly, the fifth and six columns show the detail of the reconstructions.
+The reconstruction results show the artifacts apparent in the BPDN reconstruction are largely
+mitigated using BPVV.
+Thus, in the remainder of the paper, we focus exclusively on BPVV.
+As for reconstruction time, it took about 1.5 seconds to reconstruct the DNA image and about 7 seconds for the CS20NG.
+
+% =========================================================================
+\section{Experimental setup} \label{sec:experimentalSetup}
+% =========================================================================
 \begin{figure}[ht!]
@@
 
-% =========================================================================
-\section{Experimental setup} \label{sec:experimentalSetup}
-% =========================================================================
 Our experimental setup, illustrated in Fig.~\ref{fig:exp_setup},
@@
 
+\begin{figure*}
+  \includesvg[width=1\linewidth]{figures/cs_raster_images_6-4-2019.svg}
+  \caption{}
+  \label{fig:many}
+\end{figure*}
+
 \subsection{Comparison to sub-line sampling}
@@
   \includesvg[width=1\columnwidth]{figures/subline_vs_cs.svg}
-  \caption{(left) A 128 line raster scan interpolated onto 512 lines. (left) the CS scan with the nearest time.}
+  \caption{(left) A 128 line raster scan interpolated onto 512 lines. (right) The CS scan with the nearest time.}
   \label{fig:subline}

### 2019-06-06 plot_bptv_vs_bp.m

@@ -4,15 +4,42 @@ clc
 
 % ------------ Row 1, CS20NG -------------------------
 im_og = double(imread('cs20ng.png'));
-mu_len = 50;
+% im_og = im_og(1:2:512, 1:2:512);
+mu_len = 20;
 samp_frac = 0.15;
 n = size(im_og, 1);
 
 [mask, pix_idx] = CsTools.mu_path_mask(mu_len, n, n, samp_frac);
 
 figbase = 1;
-cp_bptv_bp(im_og, pix_idx, 'cs20ng', figbase)
+t_recon_cs20ng = cp_bptv_bp(im_og, pix_idx, 'cs20ng', figbase)
 
+    U_fun = @(x) idct(x);
+    Ut_fun = @(x) dct(x);
+    
+    E_fun = @(x) CsTools.E_fun1(x, pix_idx);
+    Et_fun = @(x) CsTools.Et_fun1(x, pix_idx, n, n);
+%%        
+clc
+im_og = im_og / max(im_og(:));
+b = CsTools.pixmat2vec(im_og);
+b = b(pix_idx);
+alpv = .01;
+alph = .91;
+opts = NESTA_opts('U', U_fun, 'Ut', Ut_fun, 'verbose', 0, 'TolVar', 1e-5);
+
+% [ssm, X] = fun(im_og, b, E_fun, Et_fun, opts, alpv, alph);
+% ssm
+alps_0 = [alpv; alph];
+%%
+
+
+f = @(alps) fun(im_og, b, E_fun, Et_fun, opts, alps(1), alps(2));
+
+fmopts = optimoptions('fmincon', 'MaxIterations', 10, 'Disp', 'iter');
+alps = fmincon(f, alps_0, [], [], [], [], [0;0], [], [], fmopts)
+
+%%
 
 % ------------ Row 2, DNA -------------------------
 im_og = double(rgb2gray(imread('dnn_dna_gt.png')));
@@ -26,10 +53,45 @@ figbase = 100;
 
 [mask, pix_idx] = CsTools.mu_path_mask(mu_len, n, n, samp_frac, figbase);
 
-cp_bptv_bp(im_og, pix_idx, 'dna')
+t_recon_dna = cp_bptv_bp(im_og, pix_idx, 'dna', figbase)
+
+fprintf('CS20NG reconstruction time: %.2f\n', t_recon_cs20ng);
+fprintf('DNA reconstruction time: %.2f\n', t_recon_dna);
 
 
[…]

### 2019-06-06 latex/afm-cs-main.tex
Update figures to latest.

@@
 
+% \begin{figure*}
+%   \includesvg[width=1\textwidth]{figures/cs_raster_images_4-26-2019}
+%   \caption{Raster and compressed sensing images of a 5 micron square area of the
+%     CS-20NG grating. All images are 512$\times$512 pixels. The rows of pixels
+%     indicated by the red line are shown in Fig.~\ref{fig:pixel_rows}.}
+%   \label{fig:resultsF1_images}
+% \end{figure*}
+
 \begin{figure*}
-  \includesvg[width=1\textwidth]{figures/cs_raster_images_4-26-2019}
+  \includesvg[width=1\linewidth]{figures/cs_raster_images_6-5-2019.svg}
   \caption{Raster and compressed sensing images of a 5 micron square area of the
-    CS-20NG grating. All images are 512$\times$512 pixels. The rows of pixels
+     CS-20NG grating. All images are 512$\times$512 pixels: the raster images marked as 64 and 128 lines have been interpolated. The rows of pixels
      indicated by the red line are shown in Fig.~\ref{fig:pixel_rows}.}
@@
 \begin{figure*}[t!]
-  \includesvg[width=1\textwidth]{figures/cs_raster_pixel_rows_4-26-2019.svg}
+  \includesvg[width=1\textwidth]{figures/cs_raster_pixel_rows_6-5-2019.svg}
   \caption{Rows of pixels, as indicated by the red lines in
@@
 
-\begin{figure*}
-  \includesvg[width=1\linewidth]{figures/cs_raster_images_6-4-2019.svg}
-  \caption{}
-  \label{fig:many}
-\end{figure*}
-
 \subsection{Comparison to sub-line sampling}

### 2019-06-06 latex/afm-cs-main.tex
Update writing of control section.

@@
 \section{Control}\label{sec:control}
-The control structure for each axis is different. For the $X$-axis, we use a
-state space controller. It is described fully in \cite{braker_afmmpc_2019} and
-achieves a bandwidth of about 150 Hz, which is over 1/3 of the first $X$-axis
-resonance at 350 Hz.
-\todo{Not sure how to give a deeper summary without getting to much into the weeds.}
-
-The control law used for the $Y$-axis is a simple PI controller of the
-form
-\begin{equation}
-  \frac{U(z)}{E_Y(z)}=D(z) = \frac{K_Iz}{z-1},
-  \label{eqn:dzI}
-\end{equation}
-where, the error signal $E_Y(z) = Y(z)-R_Y$.
-
-\todo{Should I implement something better for $Y$-axis, e.g., cancel complex
-  pole-zeros at 350 hz and add notch filter???}
-
-The $Z$-axis control is slightly more complicated than the simple $Y$-axis
-integral controller and is described in the following subsection.
-\subsection{Z-axis Control Design}\label{sec:zaxis_cs_control}
-The main challenge to increasing the $Z$-axis bandwidth is the bending mode
-resonance at 215 Hz, which can be seen in the FRF from $u_Z$ to $Z_{d}$ in
-Fig.~\ref{fig:z_control} (blue curve). We address this by inverting the complex
-pole-zero pair at 215 Hz. Thus, the entire $Z$-axis controller consists of a PI
-controller, $D_I(z)$ cascaded with the resonance inversion, $D^{-1}(z)$, as shown in Fig.~\ref{fig:afm_bd_dinv}. The DC-gain
-of $D$ is (approximately) the same as the DC-gain of the plant.
-The inclusion of $D^{-1}$ allows us to substantially increase the PI gain and
-achieve a closed-loop bandwidth of about 480 Hz. This is the black curve in Fig.~\ref{fig:z_control}.
-
-There are multiple advantages to this method: first,
-an inverse compensator still makes sense as a feedforward, open-loop compensator
-if the feedback path is broken. This situation can and does occur during parts
-of the CS cycle. Second, the inverse compensator
-requires no tuning as it is defined only by a fit to the measured FRF.
-
-One challenge to the inversion approach is both the system gain and resonance at 215~Hz
-changes not only day-to-day but also (and especially) when changing cantilevers and our inversion is not robust to this.
+The control structure for each axis is similar and essentially consists of a set of filters in series with a PI controller.
+The open-loop frequency response for the $Z$-axis is shown in Fig.~\ref{fig:z_control} (red curve) and in Fig.~\ref{fig:mimo_frf_uxuy} for the $X$ and $Y$ axes (black curves).
+The first resonance of each axis is the bending mode.
+For the $Z$ axis, this resonance is at 215~Hz and at approximately 350~Hz for the $X$ and $Y$ axes.
+
+The filter for the $Z$-axis controller inverts the complex-conjugate pole-zero pair at 215~Hz.
+This allows the gain of the PI controller to be increased substantially.
+The closed-loop achieves a bandwidth of about 450~Hz, as shown by the black curve in Fig.~\ref{fig:z_control}.
+
+We take a similar approach to the $X$ and $Y$ axes.
+The filter inverts the bending modes at 350~Hz and adds a notch filter for the main resonant peak at 650~Hz.
+The resulting closed-loops are shown in the (1,1) and (2,2) positions of Fig.~\ref{fig:mimo_frf_uxuy}.
+In general, the $X$-axis positioning requirements are more stringent for both CS and raster scanning
+
+Unfortunately, as Fig.~\ref{fig:mimo_frf_uxuy} makes clear, there is a strong cross-coupling between the axes.
+The coupling from the horizontal plane to the $Z$ axis is particularly problematic and our SISO control scheme does little to attenuate the resonances of $G_{Z,u_X}$ and $G_{Z,u_Y}$.
+In particular, there are modes in both these transfer functions at 215 and 505 Hz that do not appear in a SISO model of $G_{X,u_x}$ or $G_{y,u_Y}$.
+
+For raster scans, the frequency content of the $X$-axis reference (which is a triangle wave) decays like $1/n^2$ with a gain proportional to the raster frequency.
+In contrast, the $X$-axis reference for a $\mu$-path scan is composed of a sequence of steps and ramps.
+The inclusion of the (discontinuous) steps means we should expect the $\mu$-path $X$ reference to decay like $1/n$.
+Thus,  while the cross-coupling can induce $Z$-axis vibrations for faster raster scans, it is especially problematic for $\mu$-path scanning.
+In principle, one could mitigate these issues with a full MIMO control design.
+In this work, we opt for a much simpler feedforward scheme described in the next subsection.
+
+% The control law used for the $Y$-axis is a simple PI controller of the
+% form
+% \begin{equation}
+%   \frac{U(z)}{E_Y(z)}=D(z) = \frac{K_Iz}{z-1},
+%   \label{eqn:dzI}
+% \end{equation}
+% where, the error signal $E_Y(z) = Y(z)-R_Y$.
+% 
+% \todo{Should I implement something better for $Y$-axis, e.g., cancel complex
+%   pole-zeros at 350 hz and add notch filter???}
+
+% The $Z$-axis control is slightly more complicated than the simple $Y$-axis
+% integral controller and is described in the following subsection.
+% \subsection{Z-axis Control Design}\label{sec:zaxis_cs_control}
+% The main challenge to increasing the $Z$-axis bandwidth is the bending mode
+% resonance at 215 Hz, which can be seen in the FRF from $u_Z$ to $Z_{d}$ in
+% Fig.~\ref{fig:z_control} (blue curve). We address this by inverting the complex
+% pole-zero pair at 215 Hz. Thus, the entire $Z$-axis controller consists of a PI
+% controller, $D_I(z)$ cascaded with the resonance inversion, $D^{-1}(z)$, as shown in Fig.~\ref{fig:afm_bd_dinv}. The DC-gain
+% of $D$ is (approximately) the same as the DC-gain of the plant.
+% The inclusion of $D^{-1}$ allows us to substantially increase the PI gain and
+% achieve a closed-loop bandwidth of about 480 Hz. This is the black curve in Fig.~\ref{fig:z_control}.
+
+% There are multiple advantages to this method: first,
+% an inverse compensator still makes sense as a feedforward, open-loop compensator
+% if the feedback path is broken. This situation can and does occur during parts
+% of the CS cycle. Second, the inverse compensator
+% requires no tuning as it is defined only by a fit to the measured FRF.
+
+% One challenge to the inversion approach is both the system gain and resonance at 215~Hz
+% changes not only day-to-day but also (and especially) when changing cantilevers and our inversion is not robust to this.
 However, because $D^{-1}$ is defined purely by a second order fit to a small band of the FRF, updating the compensator can be automated.
-\todo{What else to say here?}
+% \todo{What else to say here?}
 
@@
 \subsection{Feedforward Control}\label{sec:ff_control}
-In our AFM, there is a strong coupling between the horizontal axes and vertical deflection.
+% In our AFM, there is a strong coupling between the horizontal axes and vertical deflection.
 Fig.~\ref{fig:mimo_frf_uxuy} shows a MIMO FRF for $u_X$ and $u_Y$ to the outputs in each axis.
@@
 
-For CS scanning, we insert a feed-forward filter with two notches, one at 215~Hz and the other at 505~Hz.
+For CS scanning, we insert a feed-forward filter with three notches, one at 215~Hz, one at 350~Hz and one at 505~Hz.
 We design a similar feed-forward filter for the $Y$-axis.
-Both filters are shown in Fig.~\ref{fig:mimo_frf_uxuy} as the solid pink curves and the resulting overall FRF is shown as the solid blue curves.
-Particularly for $H_{z,u_X}$, these filters result in a dramatic reduction in the cross coupling.
+Both filters are shown in Fig.~\ref{fig:mimo_frf_uxuy} as the solid pink curves and the resulting overall FRF is shown as the solid blue curves, which show a dramatic reduction in the cross coupling.
 A similar affect could be achieve by using a simple low-pass filter.
@@
 See, e.g., \cite{clayton_review_2009} for more details on this strategy.
-Note that these scheme implies that the effective bandwidth of the $X$-axis controller is higher while raster scanning than while CS-scanning.
+Note that this scheme implies that the effective bandwidth of the $X$-axis controller is higher while raster scanning than while CS-scanning.
 On the other hand, it also implies that the for faster scan rates, fewer Fourier coefficients are used, and so the approximation to a triangle wave is worse.

### 2019-06-06 plot_z_axis_control_design.m
Script to plot z-axis control

@@ -1,0 +1,60 @@
+addpath functions
+clear
+% close all
+root = fullfile(PATHS.sysid, 'z_axis_evolution', 'batch-1');
+file = 'first_res_fit-3-17-2019-1.json';
+
+dat = loadjson(fullfile(root, file));
+
+gz_k = dat.SOS_frf_data.resp_real + dat.SOS_frf_data.resp_imag*1i;
+
+ss_fname = fullfile(root, 'ALL-axis_sines_info_intsamps_quickFourierCoef_3-17-2019-01.json');
+ss_data = SweptSinesOnline(ss_fname);
+
+G_frf = frd(ss_data.FC_s(:,2)./ss_data.FC_s(:,1), ss_data.freq_s, AFM.Ts, 'FrequencyUnit', 'Hz');
+
+
+KI = -0.06;
+D_inv = dat.K*frd(tf(dat.Dinv_Num, dat.Dinv_den, AFM.Ts),  ss_data.freq_s,  'FrequencyUnit', 'Hz');
+
+KI_norm = KI;
+
+D_ki = zpk([], [1], KI, AFM.Ts);
+D_ki_old = zpk([], [1], 0.005, AFM.Ts);
+
+DD = D_ki * D_inv;
+
+Loop = DD * G_frf;
+Loop_noinv = D_ki * G_frf;
+
+Huz_d = feedback(D_ki, D_inv*G_frf);
+H2 = D_ki/(1+Loop);
+
+Hyr = feedback(D_ki*D_inv*G_frf, 1);
+Hyr_old = feedback(D_ki_old*G_frf, 1);
+Hyr_noinv = feedback(D_ki*dat.K*G_frf, 1);
+
+
+F2 = mkfig(2, 3.48, 2); clf
+[ha, pos] = tight_subplot(1, 1, [.02, .01 ], [.165, 0.03], [.12, .02]);
+
+
+h1 = frf_bode_mag(Loop, ss_data.freq_s, ha, 'Hz', 'Color', [0.35, 0.75, 0.93], 'LineWidth', 1.2);
+h2 = frf_bode_mag(G_frf, ss_data.freq_s, ha, 'Hz', 'r', 'LineWidth', 1.2);
+h4 = frf_bode_mag(Hyr, ss_data.freq_s, ha, 'Hz', '-k', 'LineWidth', 1.2);
+
+ylim(ha(1), [-40, 20]);
+
+h1.DisplayName = 'Loop gain';
[…]

### 2019-06-06 latex/afm-cs-main.tex
Make z-axis o.l. and c.l colors consistent with xy.

@@
 The control structure for each axis is similar and essentially consists of a set of filters in series with a PI controller.
-The open-loop frequency response for the $Z$-axis is shown in Fig.~\ref{fig:z_control} (red curve) and in Fig.~\ref{fig:mimo_frf_uxuy} for the $X$ and $Y$ axes (black curves).
+The open-loop frequency response for the $Z$-axis is shown in Fig.~\ref{fig:z_control} (black curve) and in Fig.~\ref{fig:mimo_frf_uxuy} for the $X$ and $Y$ axes (red curves).
 The first resonance of each axis is the bending mode.

### 2019-06-06 plot_z_axis_control_design.m

@@ -40,8 +40,8 @@ F2 = mkfig(2, 3.48, 2); clf
 
 
 h1 = frf_bode_mag(Loop, ss_data.freq_s, ha, 'Hz', 'Color', [0.35, 0.75, 0.93], 'LineWidth', 1.2);
-h2 = frf_bode_mag(G_frf, ss_data.freq_s, ha, 'Hz', 'r', 'LineWidth', 1.2);
-h4 = frf_bode_mag(Hyr, ss_data.freq_s, ha, 'Hz', '-k', 'LineWidth', 1.2);
+h2 = frf_bode_mag(G_frf, ss_data.freq_s, ha, 'Hz', '-k', 'LineWidth', 1.2);
+h4 = frf_bode_mag(Hyr, ss_data.freq_s, ha, 'Hz', '-r', 'LineWidth', 1.2);
 
 ylim(ha(1), [-40, 20]);
 

### 2019-06-06 latex/afm-cs-main.tex
Update the metrics figs to include a custom colorbar legend.

@@
 \begin{figure*}[h!]
-  \begin{subfigure}{0.33\textwidth}
-    \includesvg[width=\textwidth]{figures/cs_rast_time_vs_ssim.svg}
+  \centering
+  \begin{subfigure}{1\textwidth}
+    \centering
+    \includesvg[width=0.8\textwidth]{figures/cs_rast_time_vs_ssim.svg}
     \caption{}
@@
   \end{subfigure}
-  \begin{subfigure}{0.33\textwidth}
-    \includesvg[width=1\textwidth]{figures/cs_rast_time_vs_psnr.svg}
+  \begin{subfigure}{1\textwidth}
+    \centering
+    \includesvg[width=0.8\textwidth]{figures/cs_rast_time_vs_psnr.svg}
     \caption{}
@@
   \end{subfigure}
-  \begin{subfigure}{0.33\textwidth}
-    \includesvg[width=\textwidth]{figures/cs_rast_damage.svg}
+  \begin{subfigure}{1\textwidth}
+    \centering
+    \includesvg[width=0.8\textwidth]{figures/cs_rast_damage.svg}
     \caption{}
@@
 (b) PSNR  as a function of total acquisition time.
-(c) RDI as a function of total acquisition time.}
+(c) RDI as a function of total acquisition time.
+The scan rate is indicated by color while the scan style is indicated by marker style.}
 

### 2019-06-06 process_data_6_5_2019.m

@@ -31,7 +31,7 @@ cs_files = strsplit(fls);
 cs_files = flipud(cs_files(1:end-1)')
 
 
-%%
+
 rast_exps = cell(length(raster_files), 1);
 for k=1:length(raster_files)
     [dat_root, dat_name, ext] = fileparts(raster_files{k});
@@ -44,7 +44,7 @@ for k=1:length(raster_files)
 end
 fprintf('finished loading raster data\n')
 
-%%
+if 0
 target_pix = 512;
 use_ze = false;
 % last image is 128 pixels
@@ -99,6 +99,7 @@ end
 for k=1:length(rast_exps)
     rast_exps{k}.save(true)
 end
+end
 %%
 
 cs_exps = cell(length(cs_files), 1);
@@ -121,46 +122,46 @@ use_dct2 = false;
 thresh = (20/7)*(1/1000)*20;
 
 use_ze=false;
-%%
-register_uzk = true;
-% fprintf('  Hz  |  actual perc  |  nom. perc  |  mu-path overhead |\n')
-% fprintf('---------------------------------------------------------\n')
-for k=1:length(cs_exps)
-    cs_exps{k}.process_cs_data(use_ze, register_uzk);
-    cs_exps{k}.process_cs_data(true, false);
-    %     fprintf('finished processing raw CS data..\n');
-    fprintf('  Hz  |  actual perc  |  nom. perc  |  mu-path overhead |\n')
-    fprintf('---------------------------------------------------------\n')
-    fprintf('  %.1f     %.3f          %.2f            %.4f\n',...
-        cs_exps{k}.equiv_raster_rate,...
-        cs_exps{k}.sub_sample_frac()*100,...
-        cs_exps{k}.meta_in.actual_sub_samble_perc,...
-        cs_exps{k}.get_mean_mu_overhead());
-
-    ht = cs_exps{k}.feature_height;
-    if 1
-        U_fun = @(x) idct(x);
-        Ut_fun = @(x) dct(x);
+if 0
+    register_uzk = true;
+    % fprintf('  Hz  |  actual perc  |  nom. perc  |  mu-path overhead |\n')
[…]

### 2019-06-08 latex/afm-cs-main.tex
Update on Overleaf.
Remove some package imports
Plot imaging speed as factor improvement.

@@
 % \documentclass[defaultstyle,11pt]{IEEETran}
-% Lucy says to look at:
-% float_page_fraction
-% tex_page_fraction
-% https://tex.stackexchange.com/questions/35125/how-to-use-the-placement-options-t-h-with-figures#35130
-% \renewcommand\floatpagefraction{0.5} %% default: 0.5
-% \renewcommand\topfraction{0.7} % default: 0.7
-% \renewcommand*\textfraction{.05}
+
 \usepackage{showframe}
@@
 \usepackage{graphicx}		% to insert figures
-% \usepackage{hyperref}		% PDF hyperreferences??
 \usepackage{multirow}
-\usepackage{mathtools}
 \usepackage{cite}
@@
 \usepackage{booktabs}
-% \usepackage{amsthm}
 \usepackage[percent]{overpic}
-\usepackage{caption}
 \usepackage{subcaption}
@@
 \usepackage{enumitem}
-\usepackage{catchfilebetweentags} % for data input
 \usepackage[inkscapelatex=false, inkscapepath=svgsubpath]{svg}
 \usepackage{url}
-\usepackage{mdframed}
-\usepackage{amsmath, dsfont, bbold}
-% \usepackage{algpseudocode,algorithm,algorithmicx}
 \usepackage[ruled,linesnumbered]{algorithm2e}
@@
 \begingroup \setlength{\tabcolsep}{1pt}
-\begin{figure*}[h!]
+\begin{figure*}[ht!]
   \centering
@@
 pitch. The holes are 20 nm deep.
-We scanned 5 micron by 5 micron images with 512
-lines each, yielding 512 by 512 pixel images. As before, the $\mu$-path scans
-are 500 nm long, as this allows us to work around the lack of a $Z$-axis sensor.
-This yields a $\mu$-path size of 52 pixels.
+We scanned 5 micron by 5 micron images using standard raster scans with 512, 128 and 64 lines.
+The raster scans with 128 and 64 lines were binned horizontally to first produce 128 by 512 and 64 by 512 images.
+We then interpolated these images vertically to produce 512 by 512 pixel images.
+
+We also took $\mu$-path scans with densities at 12.5\%, 15\% and 25\% and reconstructed 512 by 512 pixel images.
+For all CS scans, the $\mu$-paths are 500 nm long, as this allows us to work around the lack of a $Z$-axis sensor. This yields a $\mu$-path size of 52 pixels.
 
@@
 $Z$-engage state. The pre-scan length was 150 time steps.
-
-\todo{Should I scan even faster??}
-
-For the raster scans, we took scans at 1.0~Hz, 4.0~Hz, 5.0~Hz, 8.0~Hz and
-10~Hz.  The CS scans we taken with scan velocities equivalent to raster scans of 1.0~Hz,
-2.0~Hz, 4.0~Hz, 5.0~Hz and 8.0~Hz with sampling densities of 10~\% and 15~\%.
 The cantilever was an AppNano SICON, with a
@@
 
+% \todo{Should I scan even faster??}
+
+For the raster scans, we took scans at 1.0~Hz, 2.5~Hz, 5.0~Hz, 8.0~Hz and
+10~Hz.  The CS scans we taken with scan velocities equivalent to raster scans of 1.0~Hz,
+2.0~Hz, 5.0~Hz and 8.0~Hz with sampling densities of 10~\% and 15~\%.
+
 The CS scans were reconstructed with BPVV. We set
-$\sigma = 0.1$, $\mu_f=$TKT, $\alpha_v=$TKT and $\alpha_h=$TKTKT. The data remained scaled in terms of volts.
+$\sigma = 0.1$, $\mu_f=1e-5$, $\alpha_v=0.75$ and $\alpha_h=0.0$. The data remained scaled in terms of volts.
 
 For the raster scans, we discard data from the re-trace and divided the
-remaining data into 512$\times$512 bins based on the \xc and \yc sensor
+remaining data for each scan line 512 bins based on the \xc sensor
 measurements. We then average the data in each bin to obtain the value of one
@@
 
-% \begin{figure*}
-%   \includesvg[width=1\textwidth]{figures/cs_raster_images_4-26-2019}
-%   \caption{Raster and compressed sensing images of a 5 micron square area of the
-%     CS-20NG grating. All images are 512$\times$512 pixels. The rows of pixels
-%     indicated by the red line are shown in Fig.~\ref{fig:pixel_rows}.}
-%   \label{fig:resultsF1_images}
-% \end{figure*}
-
 \begin{figure*}
-  \includesvg[width=1\linewidth]{figures/cs_raster_images_6-5-2019.svg}
+  \includesvg[width=0.95\linewidth]{figures/cs_raster_images_6-5-2019.svg}
   \caption{Raster and compressed sensing images of a 5 micron square area of the
@@
 
-\begin{table}[t!]
-  \centering
-  \caption{Performance metrics for raster and CS scans.}
-  \begin{tabular}{cccccc}
-    \input{tables/cs_raster_table_4-26-2019_muInf_dct2.tex}
-  \end{tabular}
-  \label{tab:rast_vs_cs_v1}
-\end{table}
+% \begin{table}[t!]
+%   \centering
+%   \caption{Performance metrics for raster and CS scans.}
+%   \begin{tabular}{cccccc}
+%     \input{tables/cs_raster_table_4-26-2019_muInf_dct2.tex}
+%   \end{tabular}
+%   \label{tab:rast_vs_cs_v1}
+% \end{table}
 
@@
 
-\begin{figure*}[h!]
+Fig.~\ref{fig:improve_512} shows amount of improvement of the different sub-sampling techniques over full raster scans with 512 lines as a function of scan rate.
+As far as pure speed goes, the CS scan at 12.5\% is the fastest for a rate of 1~Hz, though the 64 line raster scan is close.
+At the same time, the image quality of the 1~Hz, 12.5\% CS scan is better than the the 1~Hz 64 line raster scan.
+However, this advantage quickly evaporates for faster scan rates.
+Indeed, for rates beyond about 5~Hz, the raster scan with 128 lines is not only faster than the 12.5\% CS scan, it also has (arguably) better image quality.
+
+Thus, we conclude that $\mu$-path based sub-sampling is only beneficial when there is an exigent reason to scan slowly.
+This may be the case for delicate specimens.
+We can roughly quantify this by computing TKTKTK
+
+SEGUE TO SOMETHING LIKE RDI HERE.
+
+\begin{figure}
+  \includesvg[width=1\columnwidth]{figures/improvements.svg}
+  \caption{Fraction of improvement in total scan time over a scan with 512 lines vs scan rate for the three sets of CS scans (at 25\%, 15\% and 12.5\%) and courser raster scans at 128 and 64 lines.}
+  \label{fig:improve_512}
+\end{figure}
+
+\begin{figure*}[ht!]
   \centering
@@
 
-\subsection{Comparison to sub-line sampling}
-Compressed sensing so far does not look good if we compare to subline sampling.
-The left panel of Fig.~\ref{fig:subline} shows a 5~Hz raster scan taken with 128 lines which takes approximately 25 seconds.
-We use that data to produce a 128 by 512 pixel image, and then use basic linear interpolation to fill produce a 512 by 512 pixel image.
-The CS image with the nearest acquisition time (15\% at 4~Hz) is shown in the right panel.
-The raster scan looks better and has basically the same RDI, and better SSIM and PSNR numbers.
-We conclude there is no reason to use CS.
-\begin{figure}
-  \includesvg[width=1\columnwidth]{figures/subline_vs_cs.svg}
-  \caption{(left) A 128 line raster scan interpolated onto 512 lines. (right) The CS scan with the nearest time.}
-  \label{fig:subline}
-\end{figure}
+% \begin{figure}
+%   \includesvg[width=1\columnwidth]{figures/subline_vs_cs.svg}
+%   \caption{(left) A 128 line raster scan interpolated onto 512 lines. (right) The CS scan with the nearest time.}
+%   \label{fig:subline}
+% \end{figure}
 

### 2019-06-08 process_data_6_5_2019.m

@@ -126,7 +126,7 @@ if 0
     register_uzk = true;
     % fprintf('  Hz  |  actual perc  |  nom. perc  |  mu-path overhead |\n')
     % fprintf('---------------------------------------------------------\n')
-    for k=1:length(cs_exps)
+    for k=1:1 %length(cs_exps)
         cs_exps{k}.process_cs_data(use_ze, register_uzk);
         cs_exps{k}.process_cs_data(true, false);
         %     fprintf('finished processing raw CS data..\n');
@@ -169,12 +169,12 @@ if 0
         cs_exps{k}.pix_mat_uz = cs_exps{k}.pix_mat_uz - bar_bp;
         cs_exps{k}.pix_mat_raw_uz = cs_exps{k}.pix_mat_raw_uz - bar_bp;
         
-        im_tmp = cs_exps{k}.pix_mat_ze;
+        im_tmp = cs_exps{k}.pix_mat_uz;
         
         %         im_tmp = detrend_plane(im_tmp);
         im_tmp = im_tmp - mean(im_tmp(:));
         %     im_tmp = SplitBregmanROF(im_tmp, 100, 0.001);
-        ImshowDataView.imshow(im_tmp, [-thresh, thresh], ax4, ax4_2, cb_exp)
+        ImshowDataView.imshow(im_tmp, [-thresh, .25*thresh], ax4, ax4_2, cb_exp)
         title(ax4, stit)
         hold(ax4, 'on')
         drawnow();
@@ -182,7 +182,7 @@ if 0
         %plot(ax4, [idx_left, idx_left], [1, 512], 'r')
         %plot(ax4, [idx_right, idx_right], [1, 512], 'r')
     end
-    
+    %%
     
     for k=1:length(cs_exps)
         cs_exps{k}.save()
@@ -227,6 +227,8 @@ rastm_512 = ScanMetrics();
 rastm_128 = ScanMetrics();
 rastm_64 = ScanMetrics();
 rast_imk_fit = {};
+
+dct_ = @(x) dct(x);
 for k=1:length(rast_exps)
     if k== master_rast_idx
         continue
@@ -504,7 +506,7 @@ fac = (xs(1) + wo)/xs(1);
 
 for k=1:5
[…]

### 2019-06-10 latex/afm-cs-main.tex
Move rdi to results.

@@
 
-% Due to this unfortunate drift, in Section~\ref{sec:results:final}, we will use a
-% 1~Hz scan as the baseline image. Hopefully, this will give a decent trade-off
-% between having an image with minimal drift and scanning slowly enough that it
-% accurately represents the sample grating. Due to the improved $Z$-axis
-% bandwidth, a 1~Hz scan should still have better (or at least comparable) quality
-% than the 0.25~Hz scan taken in Chapter~\ref{chap:cs_init}. Additionally,
-% Fig.\ref{fig:rast_aligned_1} provides us with an (approximate) upper bound for
-% our expectations when looking at the experimental results in
-% Section~\ref{sec:results:final}.
-
-\subsection{A new metric}
-\begin{figure}[t!]
-  \centering
-  \includesvg[width=1\columnwidth]{figures/damage_illustration.svg}
-  \caption{The RDI metric defined in \eqref{eqn:RDI} penalizes everything in the
-    red shaded region and does not penalize anything in the un-shaded region.}
-  \label{fig:damage_illustrate}
-\end{figure}
-
-Th PSNR and SSIM metrics only assess the similarity of two images.
-However, in AFM imaging, pure image quality is not the
-only concern, particularly for delicate samples. What is needed is a figure of
-merit for how much damage was done to specimen during the imaging process. While
-this is not really a concern while imaging a hard calibration grating, it plays
-a prominent role biological samples~\cite{ando_highspeed_2008}. In general,
-damage occurs while scanning into an uphill region, which results in a positive
-deflection signal. The actual damage done by a given $Z_d$ will depend on the
-spring constant of the cantilever and the softness of the specimen. Nonetheless,
-we can use the positive deviations of $Z_d$ as a relative measure of damage
-between different scan speeds or scanning methods, for a given cantilever and
-specimen. This motivates a metric we term the relative damage index (RDI), which
-we define as
-\begin{align}
-  \text{RDI} &= \frac{1}{T_s}\sum_{k\in I} \frac{1}{k} \left(Z_{d,k} - r_{Z,s}\right)^2 \label{eqn:RDI}\\
-  I &= \{k: k\in[0,~N-1],~ Z_{d,k}-r_{Z,s} > 0 \} \nonumber
-\end{align}
-where $N$ is the total number of samples in a given scan, $Z_{d,k}$ is the
-deflection signal at sample $k$ and $r_{Z,\textrm{s}}$ is the scanning setpoint.
-The RDI is basically the power in positive deflection. By excluding negative
-values of the deflection, we do not penalize the CS algorithm while it is
-re-engaging with the specimen \emph{unless} it overshoots the scanning setpoint,
-which we do want to penalize. This is illustrated in
-Fig.~\ref{fig:damage_illustrate}, which shows several CS cycles with a poorly
-tuned controller. Only deflection signals in the red-shaded region will be
-penalized by the RDI.
+% \subsection{A new metric}
+% \begin{figure}[t!]
+%   \centering
+%   \includesvg[width=1\columnwidth]{figures/damage_illustration.svg}
+%   \caption{The RDI metric defined in \eqref{eqn:RDI} penalizes everything in the
+%     red shaded region and does not penalize anything in the un-shaded region.}
+%   \label{fig:damage_illustrate}
+% \end{figure}
+
+% Th PSNR and SSIM metrics only assess the similarity of two images.
+% However, in AFM imaging, pure image quality is not the
+% only concern, particularly for delicate samples. What is needed is a figure of
+% merit for how much damage was done to specimen during the imaging process. While
+% this is not really a concern while imaging a hard calibration grating, it plays
+% a prominent role biological samples~\cite{ando_highspeed_2008}. In general,
+% damage occurs while scanning into an uphill region, which results in a positive
+% deflection signal. The actual damage done by a given $Z_d$ will depend on the
+% spring constant of the cantilever and the softness of the specimen. Nonetheless,
+% we can use the positive deviations of $Z_d$ as a relative measure of damage
+% between different scan speeds or scanning methods, for a given cantilever and
+% specimen. This motivates a metric we term the relative damage index (RDI), which
+% we define as
+% \begin{align}
+%   \text{RDI} &= \frac{1}{T_s}\sum_{k\in I} \frac{1}{k} \left(Z_{d,k} - r_{Z,s}\right)^2 \label{eqn:RDI}\\
+%   I &= \{k: k\in[0,~N-1],~ Z_{d,k}-r_{Z,s} > 0 \} \nonumber
+% \end{align}
+% where $N$ is the total number of samples in a given scan, $Z_{d,k}$ is the
+% deflection signal at sample $k$ and $r_{Z,\textrm{s}}$ is the scanning setpoint.
+% The RDI is basically the power in positive deflection. By excluding negative
+% values of the deflection, we do not penalize the CS algorithm while it is
+% re-engaging with the specimen \emph{unless} it overshoots the scanning setpoint,
+% which we do want to penalize. This is illustrated in
+% Fig.~\ref{fig:damage_illustrate}, which shows several CS cycles with a poorly
+% tuned controller. Only deflection signals in the red-shaded region will be
+% penalized by the RDI.
 
@@
 
-% The sub-slice removed a 30 pixel
-% boundary from each edge. Despite this alignment, the middle pixels tend to show
-% a smaller error than those towards the top and bottom, which is similar to the
-% affect observed before in Fig.~\ref{fig:baseline_errors}.
-
 For each raster scan and each CS scan, we computed the SSIM, PSNR (both with
@@
 
-% It is interesting to also compare
-% these numbers to the batch of 1~Hz raster scans we compared in
-% Section~\ref{sec:limits}.
-% The blue shaded bands of
-% Figs~\ref{fig:time_ssim_psnr} indicate the mean of the SSIM and PSNR metrics
-% from Section \ref{sec:psnr_ssim_limits} plus or minus one standard deviation.
-% This seems to be further evidence that, at least for our experimental setup,
-% these numbers are not especially meaningful.
-
 Fig.~\ref{fig:improve_512} shows amount of improvement of the different sub-sampling techniques over full raster scans with 512 lines as a function of scan rate.
@@
 This may be the case for delicate specimens.
-We can roughly quantify this by computing TKTKTK
-
-SEGUE TO SOMETHING LIKE RDI HERE.
+We can roughly quantify this by computing the power in the deflection signal during scanning
+\begin{align}
+  \text{RDI} &= \frac{1}{T_s}\sum_{k=0}^N \frac{1}{k} \left(Z_{d,k} - r_{Z,s}\right)^2 \label{eqn:RDI}\\
+\end{align}
+The idea behind the idea is that increased scan rates lead to larger deflection signals (and thereby increased force into the specimen) at each surface feature, which the RDI accumulates.
+
+The values of the RDI for each of the $\mu$-path and raster scans are shown in Fig.~\ref{fig:time_damage} as a function of total imaging time.
+As one would expect, as imaging time decreases, the RDI for each scan type increases.
+
+% More importantly though,
 

### 2019-06-10 plot_bptv_vs_bp.m
indenting.

@@ -14,11 +14,11 @@ n = size(im_og, 1);
 figbase = 1;
 t_recon_cs20ng = cp_bptv_bp(im_og, pix_idx, 'cs20ng', figbase)
 
-    U_fun = @(x) idct(x);
-    Ut_fun = @(x) dct(x);
+U_fun = @(x) idct(x);
+Ut_fun = @(x) dct(x);
     
-    E_fun = @(x) CsTools.E_fun1(x, pix_idx);
-    Et_fun = @(x) CsTools.Et_fun1(x, pix_idx, n, n);
+E_fun = @(x) CsTools.E_fun1(x, pix_idx);
+Et_fun = @(x) CsTools.Et_fun1(x, pix_idx, n, n);
 %%        
 clc
 im_og = im_og / max(im_og(:));

### 2019-06-10 q_vs_density.m
Parameter sweep of q and frac.

@@ -1,0 +1,108 @@
+% ------------ Row 1, CS20NG -------------------------
+
+
+im_og = double(imread('cs20ng.png'));
+% im_og = double(imread('cameraman.tif'));
+im_og = im_og - min(im_og(:));
+im_og = (im_og / max(im_og(:)))*256;
+% im_og = im_og(1:2:512, 1:2:512);
+
+samp_frac = 0.15;
+npix = size(im_og, 1);
+
+mx = max(im_og(:)) - min(im_og(:))
+skip = 4;
+h = skip:skip:npix;
+im_128_sub = im_og(h, :);
+
+im_128 = interp_y(im_128_sub, npix);
+
+ssm_128 = ssim(im_128, im_og, 'DynamicRange', mx);
+psn_128 = psnr(im_128, im_og, mx);
+
+U_fun = @(x) idct(x);
+Ut_fun = @(x) dct(x);
+
+
+%%
+fprintf('128: ssm: %.3f, psn: %.3f\n', ssm_128, psn_128);
+fprintf('===============================================\n');
+figure(11); clf
+subplot(1,2,1),
+imagesc(im_128), colormap('gray')
+drawnow()
+
+mu = 1e-7;
+delta = 0.01;
+% alpv = 0.01;
+alph = 0.75;
+opts = NESTA_opts('U', U_fun, 'Ut', Ut_fun, 'verbose', 0, 'TolVar', 1e-5,...
+    'alpha_v', alpv, 'alpha_h', alph);
+
+
+qs = (5:3:50);
+fracs = (5:2:50)/100;
+% fracs = 50/100;
+dat = zeros(length(qs), 6);
+map = zeros(length(qs), length(fracs));
+gam = npix/50;
+for j = 1:length(qs)
+    store = true;
+    opts.alpha_v = 0.5;
+    opts.alpha_h = 2*(gam*qs(j))/npix;
+    for k=1:length(fracs)
+        mu_len = qs(j);
+        samp_frac = fracs(k);
+        [mask, pix_idx] = CsTools.mu_path_mask(mu_len, npix, npix, samp_frac);
+        E_fun = @(x) CsTools.E_fun1(x, pix_idx);
+        Et_fun = @(x) CsTools.Et_fun1(x, pix_idx, npix, npix);
+        
+        b = CsTools.pixmat2vec(im_og);
+        b = b(pix_idx);
+        x_bptv = NESTA_mine(E_fun, Et_fun, b, mu, delta, opts);
+        
[…]

### 2019-06-12 latex/afm-cs-main.tex
Update on Overleaf.
Update figures.

@@
   and a new metric we call the relative damage index.
-  \todo{Will this conclusion still hold?}
+  \todo{Re-write abstract, especially conclusions}
   These experiments demonstrate that at slow
@@
 builds upon that earlier work in several significant ways.
+
 % % ------------------ TKTKTKT ------------------
@@
 The DCT basis generally keeps a good balance between achieving a low
-mutual coherence between $U$ and the required structure of the AFM sensing
-matrices $R$ and providing a high sparsity of typical AFM sample images.
+mutual coherence between $U$ and the $\mu$-path sensing
+matrices $R$ and providing a high sparsity for typical AFM sample images.
 
@@
                          + \beta\left\|D_hx\right\|_1 \label{op:bp_tv}\\
-                       &=\min_{x\in Q_p} \left\|Wx\right\|_1 \label{op:bp_tvW}
+                       &=\min_{x\in Q_p} \left\|W^Tx\right\|_1 \label{op:bp_tvW}
                          % \quad W = \begin{bmatrix}U&\alpha_hD^T_h&\alpha_vD^T_v \end{bmatrix}^T \nonumber
@@
 \begin{equation*}
-W = \begin{bmatrix}U&\alpha_hD^T_h&\alpha_vD^T_v \end{bmatrix}^T
+W = \begin{bmatrix}U^T&\alpha D_h&\beta D_v \end{bmatrix}
 \end{equation*}
@@
 
-Moreover, when written as \eqref{op:bp_tvW}, the problem is in a form that may be solved with NESTA~\cite{becker_nesta_2011}. For completeness, we give an overview here.
-To that end, we re-write the cost $f(x)$ in \eqref{op:bp_tvW} as
-\begin{equation*}
-  f(x) = \max_{u\in Q_d} \left\langle u, Wx \right\rangle,\quad Q_d = \{u:~||u||_{\infty} \leq 1\}.
-\end{equation*}
-
-One of the core features of the NESTA algorithm is to replace the non-smooth functional $f(x)$ with a smoothed approximation
-\begin{equation}
-  f_{\mu} = \max_{u\in Q_d} \left\langle u,
-    W x \right\rangle - \frac{\mu}{2}||u||_2^2. \label{eqn:fcn_prox}
-\end{equation}
-The gradient of \eqref{eqn:fcn_prox} is given by
-\begin{equation*}
-  \nabla f_{\mu}(x)[i] = W^Tu_{\mu}(x)
-\end{equation*}
-where
-\begin{equation*}
-  (u_{\mu}(x))[i] = 
-\begin{cases}
-    \mu^{-1}(Wx)[i], & |W x[i]| < \mu,\\
-    \text{sgn}(W x[i]), & \text{else}.
-  \end{cases}
-\end{equation*}
-The optimization \eqref{op:bp_tv} may now be solved using Algorithm~\ref{ag:NESTA}.
-
-\begin{algorithm}
-  \SetKwInOut{Initialize}{Initialize} \SetKwInOut{Output}{Output}
-
-  \Initialize{$x \in Q_p, \mu=0.9||W x_0||_{\infty}$, $L_{\mu} = \frac{1}{\mu}||W||^2_2$}
-    % $x^{k+1} = x^{k}$\\
-  \While{$\mu < \mu_{\textrm{final}}$ } {
-    $k=0$\\
-      \While{$\Delta f_{\mu} > \delta$} {
-        $\alpha_k = \frac{1}{2}(k+1)$ \\
-        $\tau_k = \frac{2}{k+3}$ \\
-        $\displaystyle y_k = \text{arg } \min_{x\in Q_p}
-          \frac{L_{\mu}}{2}||x - x_k||_2^2 + \langle \nabla f(x_k),~ x\rangle$\\
-        $\displaystyle {z_k = \text{arg } \min_{x\in Q_p} \frac{L_{\mu}}{2}||x-x_0||_2^2 +
-        \langle \sum_{i=0}^k \alpha_i \nabla f(x_i), ~x \rangle}$\\
-        $x_{k+1} = \tau_kz_k + (1-\tau_k)y_k$\\
-        $k \leftarrow k + 1$\\
-      }
-      $x_0 = x_k$\\
-      $\mu = \gamma \mu$\\
-      $L_{\mu} = (1/\mu)||W||^2_2$
-    }
-  \Output{Reconstruction $x_k$}
-  \caption{NESTA algorithm}
-  \label{ag:NESTA}
-\end{algorithm}
-  \todo{seems like a waste of space to reprint the algo, since its really no different than the reference}
-
-In the termination condition for the inner loop, $\Delta f_{\mu} = |f_{\mu}(x_k) - \bar{f}_{\mu}(x_k)|/\bar{f}_{\mu}(x_k)$ where
-\begin{equation}
-\bar{f}_{\mu}(x_k) = \frac{1}{\min\{10, k\}} \sum_{\ell=1}^{\min\{10,k\}} f_{\mu}(x_{k-\ell})
-\end{equation}
-When $RR^T=I$, the sub-problems in lines 6 and 7 have a closed-form solution. Details can be found in~\cite{becker_nesta_2011}.
-
-% The sub-problems in lines 6 and 7 have the form
+Moreover, when written as \eqref{op:bp_tvW}, the problem is in a form that may be solved with NESTA~\cite{becker_nesta_2011}.
+
+% For completeness, we give an overview here.
+% To that end, we re-write the cost $f(x)$ in \eqref{op:bp_tvW} as
+% \begin{equation*}
+%   f(x) = \max_{u\in Q_d} \left\langle u, W^Tx \right\rangle,\quad Q_d = \{u:~||u||_{\infty} \leq 1\}.
+% \end{equation*}
+
+% One of the core features of the NESTA algorithm is to replace the non-smooth functional $f(x)$ with a smoothed approximation
 % \begin{equation}
-%   p = \textrm{arg } \min_{x\in Q_p} \frac{L}{2}||x - r|| + \langle g,~x - r\rangle
+%   f_{\mu} = \max_{u\in Q_d} \left\langle u,
+%     W^T x \right\rangle - \frac{\mu}{2}||u||_2^2. \label{eqn:fcn_prox}
 % \end{equation}
-% for some vectors $g$ and $r$ and, as shown in~\cite{becker_nesta_2011}, have a closed-form solution given by
-% \begin{align}
-%   \lambda & = \textrm{max}(0, \sigma^{-1}\left| b - Rq\right| - L\\
-%   q &= r - L^{-1}g\\
-%   p &= \left(I - \frac{\lambda}{\lambda + L} R^TR\right)\left( \frac{\lambda}{L}R^Tb + q\right).
-% \end{align}
+% The gradient of \eqref{eqn:fcn_prox} is given by
+% \begin{equation*}
+%   \nabla f_{\mu}(x)[i] = Wu_{\mu}(x)
+% \end{equation*}
+% where
+% \begin{equation*}
+%   (u_{\mu}(x))[i] = 
+% \begin{cases}
+%     \mu^{-1}(W^Tx)[i], & |W^T x[i]| < \mu,\\
+%     \text{sgn}(W^T x[i]), & \text{else}.
+%   \end{cases}
+% \end{equation*}
+% The optimization \eqref{op:bp_tv} may now be solved using Algorithm~\ref{ag:NESTA}.
+
+% \begin{algorithm}
+%   \SetKwInOut{Initialize}{Initialize} \SetKwInOut{Output}{Output}
+
+%   \Initialize{$x \in Q_p, \mu=0.9||W^T x_0||_{\infty}$, $L_{\mu} = \frac{1}{\mu}||W||^2_2$}
+%     % $x^{k+1} = x^{k}$\\
+%   \While{$\mu < \mu_{\textrm{final}}$ } {
+%     $k=0$\\
+%       \While{$\Delta f_{\mu} > \delta$} {
+%         $\alpha_k = \frac{1}{2}(k+1)$ \\
+%         $\tau_k = \frac{2}{k+3}$ \\
+%         $\displaystyle y_k = \text{arg } \min_{x\in Q_p}
+%           \frac{L_{\mu}}{2}||x - x_k||_2^2 + \langle \nabla f(x_k),~ x\rangle$\\
+%         $\displaystyle {z_k = \text{arg } \min_{x\in Q_p} \frac{L_{\mu}}{2}||x-x_0||_2^2 +
+%         \langle \sum_{i=0}^k \alpha_i \nabla f(x_i), ~x \rangle}$\\
+%         $x_{k+1} = \tau_kz_k + (1-\tau_k)y_k$\\
+%         $k \leftarrow k + 1$\\
+%       }
+%       $x_0 = x_k$\\
+%       $\mu = \gamma \mu$\\
+%       $L_{\mu} = (1/\mu)||W||^2_2$
+%     }
+%   \Output{Reconstruction $x_k$}
+%   \caption{NESTA algorithm}
+%   \label{ag:NESTA}
+% \end{algorithm}
+%   \todo{seems like a waste of space to reprint the algo, since its really no different than the reference}
+
+% In the termination condition for the inner loop, $\Delta f_{\mu} = |f_{\mu}(x_k) - \bar{f}_{\mu}(x_k)|/\bar{f}_{\mu}(x_k)$ where
+% \begin{equation}
+% \bar{f}_{\mu}(x_k) = \frac{1}{\min\{10, k\}} \sum_{\ell=1}^{\min\{10,k\}} f_{\mu}(x_{k-\ell})
+% \end{equation}
+% When $RR^T=I$, the sub-problems in lines 6 and 7 have a closed-form solution. Details can be found in~\cite{becker_nesta_2011}.
+
+% % The sub-problems in lines 6 and 7 have the form
+% % \begin{equation}
+% %   p = \textrm{arg } \min_{x\in Q_p} \frac{L}{2}||x - r|| + \langle g,~x - r\rangle
+% % \end{equation}
+% % for some vectors $g$ and $r$ and, as shown in~\cite{becker_nesta_2011}, have a closed-form solution given by
+% % \begin{align}
+% %   \lambda & = \textrm{max}(0, \sigma^{-1}\left| b - Rq\right| - L\\
+% %   q &= r - L^{-1}g\\
+% %   p &= \left(I - \frac{\lambda}{\lambda + L} R^TR\right)\left( \frac{\lambda}{L}R^Tb + q\right).
+% % \end{align}
 
@@
 % =========================================================================
-\section{Control}\label{sec:control}
-The control structure for each axis is similar and essentially consists of a set of filters in series with a PI controller.
-The open-loop frequency response for the $Z$-axis is shown in Fig.~\ref{fig:z_control} (black curve) and in Fig.~\ref{fig:mimo_frf_uxuy} for the $X$ and $Y$ axes (red curves).
-The first resonance of each axis is the bending mode.
-For the $Z$ axis, this resonance is at 215~Hz and at approximately 350~Hz for the $X$ and $Y$ axes.
-
-The filter for the $Z$-axis controller inverts the complex-conjugate pole-zero pair at 215~Hz.
-This allows the gain of the PI controller to be increased substantially.
-The closed-loop achieves a bandwidth of about 450~Hz, as shown by the black curve in Fig.~\ref{fig:z_control}.
-
-We take a similar approach to the $X$ and $Y$ axes.
-The filter inverts the bending modes at 350~Hz and adds a notch filter for the main resonant peak at 650~Hz.
-The resulting closed-loops are shown in the (1,1) and (2,2) positions of Fig.~\ref{fig:mimo_frf_uxuy}.
-In general, the $X$-axis positioning requirements are more stringent for both CS and raster scanning
-
-Unfortunately, as Fig.~\ref{fig:mimo_frf_uxuy} makes clear, there is a strong cross-coupling between the axes.
-The coupling from the horizontal plane to the $Z$ axis is particularly problematic and our SISO control scheme does little to attenuate the resonances of $G_{Z,u_X}$ and $G_{Z,u_Y}$.
-In particular, there are modes in both these transfer functions at 215 and 505 Hz that do not appear in a SISO model of $G_{X,u_x}$ or $G_{y,u_Y}$.
-
-For raster scans, the frequency content of the $X$-axis reference (which is a triangle wave) decays like $1/n^2$ with a gain proportional to the raster frequency.
-In contrast, the $X$-axis reference for a $\mu$-path scan is composed of a sequence of steps and ramps.
-The inclusion of the (discontinuous) steps means we should expect the $\mu$-path $X$ reference to decay like $1/n$.
-Thus,  while the cross-coupling can induce $Z$-axis vibrations for faster raster scans, it is especially problematic for $\mu$-path scanning.
-In principle, one could mitigate these issues with a full MIMO control design.
-In this work, we opt for a much simpler feedforward scheme described in the next subsection.
-
-% The control law used for the $Y$-axis is a simple PI controller of the
-% form
-% \begin{equation}
-%   \frac{U(z)}{E_Y(z)}=D(z) = \frac{K_Iz}{z-1},
-%   \label{eqn:dzI}
-% \end{equation}
-% where, the error signal $E_Y(z) = Y(z)-R_Y$.
-% 
-% \todo{Should I implement something better for $Y$-axis, e.g., cancel complex
-%   pole-zeros at 350 hz and add notch filter???}
-
-% The $Z$-axis control is slightly more complicated than the simple $Y$-axis
-% integral controller and is described in the following subsection.
-% \subsection{Z-axis Control Design}\label{sec:zaxis_cs_control}
-% The main challenge to increasing the $Z$-axis bandwidth is the bending mode
-% resonance at 215 Hz, which can be seen in the FRF from $u_Z$ to $Z_{d}$ in
-% Fig.~\ref{fig:z_control} (blue curve). We address this by inverting the complex
-% pole-zero pair at 215 Hz. Thus, the entire $Z$-axis controller consists of a PI
-% controller, $D_I(z)$ cascaded with the resonance inversion, $D^{-1}(z)$, as shown in Fig.~\ref{fig:afm_bd_dinv}. The DC-gain
-% of $D$ is (approximately) the same as the DC-gain of the plant.
-% The inclusion of $D^{-1}$ allows us to substantially increase the PI gain and
-% achieve a closed-loop bandwidth of about 480 Hz. This is the black curve in Fig.~\ref{fig:z_control}.
-
-% There are multiple advantages to this method: first,
-% an inverse compensator still makes sense as a feedforward, open-loop compensator
-% if the feedback path is broken. This situation can and does occur during parts
-% of the CS cycle. Second, the inverse compensator
-% requires no tuning as it is defined only by a fit to the measured FRF.
-
-% One challenge to the inversion approach is both the system gain and resonance at 215~Hz
-% changes not only day-to-day but also (and especially) when changing cantilevers and our inversion is not robust to this.
-However, because $D^{-1}$ is defined purely by a second order fit to a small band of the FRF, updating the compensator can be automated.
-% \todo{What else to say here?}
-
-\begin{figure}[t!]
-  \centering
-  \includesvg[width=1\columnwidth]{figures/z_control_design.svg}
-  \caption{FRFs of the $Z$-axis. The blue curve is the open loop response from $u_Z$ to deflection. By inverting the bending mode at 215~Hz, we achieve the black curve in closed-loop.}
-  \label{fig:z_control}
-\end{figure}
-
-\begin{figure*}
-  \centering
-  \includesvg[width=1\textwidth]{figures/MIMO_CL_uxuy.svg}
-  \caption{MIMO closed and open loop FRFs, showing the dramatic affect on $G_{Z,u_X}$ and $G_{Z,u_Y}$ when the feedforward compensators are used for the $X$ and $Y$ axes.}
-  \label{fig:mimo_frf_uxuy}
-\end{figure*}
-
-\begin{figure*}[t]
-  \centering
-  \includegraphics[width=0.75\textwidth]{figures/AFM_loop_z.pdf}
-  \caption{Block diagram of the $Z$-axis control loop. The anti-windup is active
-    for decision index $i\in\{0,1,5\}$, which correspond to states such that
-    $r_Z=\rzup$.}
-  \label{fig:afm_bd_dinv}
-\end{figure*}
-
-% One cause for such different gains is variation in the length of the cantilever
-% (and possibly how the laser was adjusted). This is illustrated in
-% Fig.~\ref{fig:z_axis_gain}. Here, we consider a cantilever with length $h$ that
-% rests on the surface of some specimen with a nominal angle of $\theta$. In this
-% drawing, the laser is perpendicular to the sample surface. Given a vertical
-% perturbation $\Delta z$, we have that
-% \begin{equation}
-%   \Delta \alpha \approx \frac{d}{h} \Delta z,
-% \end{equation}
-% where $d$ is the distance from the cantilever to the detector and
-% $\Delta \alpha$ is the change in position of the incident laser spot on the
-% detector. Thus, given the same change in the vertical position, we will see a
-% larger change in the deflection signal for a shorter cantilever. In other words,
-% a short cantilever will exhibit a larger DC-gain in the $G_{u_Z,Z_d}$ transfer
-% function.
-% \begin{figure}
-%   \begin{minipage}[t]{.46\textwidth}
-%     % L B R T
-%     \includesvg[width=1\textwidth]{figures/z_cant_evolution.svg}
-%     \caption{FRFs of three different cantilevers, showing substantial
-%       differences in the DC-gain and smaller, but still significant differences
-%       the frequency of the modes.}
-%     \label{fig:z_evolution}
-%   \end{minipage}
-%   \hfill
-%   \begin{minipage}[t]{.46\textwidth}
-%     % L B R T
-%     \includegraphics[width=1\textwidth]{figures/z_axis_gain_schematic-crop.pdf}
-%     \caption{Schematic drawing of how the length of the cantilever affects the
-%       $z$-axis gain.}
-%     \label{fig:z_axis_gain}
-%   \end{minipage}
-% \end{figure}
-
-% Fig.~\ref{fig:z_evolution} shows the frequency response of $G_{u_Z,Z_d}$ near
-% the bending mode for three different cantilevers. Cantilevers (A) and (B) are
-% both AppNano SICON cantilevers and have a nominal length of 450 microns.
-% Cantilever (C) is an NCLR and has a nominal length of 225 microns.
-% Interestingly, the SICON cantilevers show substantial variation. Unfortunately,
-% the manufacture does not provide a tolerance on the nominal length, so it is
-% difficult to tease out whether that variation is due to manufacturing
-% variability or other factors not explained by this analysis.
-
-% Notably, the frequency of the pole and zero do appear to shift and our inversion
-% scheme is not robust to this. To deal with this, I have built a (mostly)
-% automated system ID routine into the imaging software. This routine is a
-% specialized version of the techniques described previously in
-% Chapter~\ref{chap:modeling}. First, it obtains an FRF of the bending mode over a
-% frequency range spanning 180~Hz to 240~Hz (the same set of points as in
-% Fig.~\ref{fig:z_evolution}). The input and output sinusoids are demodulated in
-% quasi-realtime as they come off the FPGA. Once this is complete, a 2-pole,
-% 2-zero transfer function model of the form
-% \begin{equation*}
-%   \hat{D}(z) = k \frac{z^2 + b_1z + b_o}{z^2 + a_1z + a_o}
-% \end{equation*}
-% is fit to the FRF, using the same optimization scheme as \eqref{eqn:logfit}.
-% This is done inside the LabView VI by calling a custom DLL, which leverages
-% CMPFIT~\cite{cmpfit,markwardt_mpfit_2009}, a
-% Levenberg-Marquardt~\cite{more_levenberg_1978} routine written in C. To promote
-% a stable fit, the optimization enforces the necessary conditions that
-% \begin{align*}
-%   |a_1| &< 2, \quad  |a_o| < 1\\
-%   |b_1| &< 2, \quad  |b_o| < 1.
-% \end{align*}
-% The routine then checks that both the poles and zeros are indeed stabile, saves
-% the data to a JSON file and passes the transfer function parameters into the
-% imaging portion of the application which finally uploads the parameters into the
-% FPGA imaging bitfile. Optionally, one can by-pass this step and simply load the
-% previously saved JSON file.
-
-% One of the benefits of this approach is that the DC-gain of the transfer
-% function $G_{u_Z,Z_d}$ becomes (approximately) normalized to unity, which makes
-% re-tuning the control system after changing tips far easier to non-existent. The
-% benefit to automating the process is that it drastically reduces the friction
-% required to obtain an up-to-date compensator, which means that an up-to-date
-% compensator is more likely to be used~\cite{abramovitch_25years_2015}.
-
-% Fig.~\ref{fig:afm_bd_dinv} shows a block diagram if the $Z$-axis control loop.
-% We point out a small change from Chapter~\ref{chap:cs_init}: the addition of
-% $D^{-1}(z)$ changes the correct signal to use to represent the sample surface.
-% If we take the output of the entire compensator, $u_Z=D_ID^{-1}e_z$, then we
-% will get a lot of wiggles in the resulting signal. Rather, we need to take only
-% the output of the integrator to represent the surface.
-% % \begin{figure}
-% %   \centering
-% %   \includegraphics[width=1\columnwidth]{figures/AFM_loop_Dinv-crop.pdf}
-% %   \caption{Block diagram of the $Z$-axis control loop with the inverse
-% %   compensator. }
-% %   \label{fig:afm_bd_dinv}
-% % \end{figure}
-% \begin{figure*}[t]
-%   \centering
-%   \includegraphics[width=0.75\textwidth]{figures/AFM_loop_Dinv_antiwup-crop.pdf}
-%   \caption{Block diagram of the $Z$-axis control loop. The anti-windup is active
-%     for decision index $i\in\{0,1,5\}$, which correspond to states such that
-%     $r_Z=r_{Z,\textrm{up}}$.}
-%   \label{fig:afm_bd_dinv_final}
-% \end{figure*}
-
-% It should be noted that this control is sufficient to eliminate the limit-cycle
-% behavior described in Section~\ref{sec:aproachspeed}:
-
-% % \begin{figure}[tbhp!]
-% %   \centering\includegraphics[width=3.0in]{figures-SBA/uz_multiplexer_KI_anderssonLab2}
-% %   \caption{The $z$-piezo movement is driven by switching between feedback from
-% %   the $z$-axis position signal and from the deflection signal. The shaded area
-% %   represents the digital control system, while the non-shaded region is the
-% %   physical system.}
-% %   \label{fig:zMultiplex_anderssonLab}
-% % \end{figure}
-
-% As illustrated in Fig.~\ref{fig:zMultiplex_anderssonLab}, the voltage applied to
-% the $z$-piezo is adjusted by switching the feedback signal between the $z$-axis
-% position sensor (when the tip is off the surface) and the deflection signal
-% (when the tip is engaged). The difference equation associated with
-% \eqref{eqn:dzI} for the $z$-axis is
-% \begin{equation}
-%   u_z(k) = K_Ie(k) + u_z(k-1).
-%   \label{eqn:intdiff}
-% \end{equation}
-
-% In the $z$-axis position control mode, the $z$-axis position is controlled to a
-% fixed value $z_{ref}$ which, in general, is slightly above the sample surface.
-% The difference between the measured $z$-axis position and $z_{ref}$,
-% ${e(k) = z_{ref} - z(k)}$, is used as the error signal. In the deflection
-% control mode, when the tip is in contact with the sample, the deflection signal
-% is controlled to a fixed value $l_{ref}$ to ensure a constant tip-sample force.
-% The sample surface acts as a disturbance to the control loop. Therefore, the
-% $z$-axis position measurements can be taken to represent the surface topography
-% of the sample. In this case, the difference between the measured deflection and
-% $l_{ref}$ is the error, $e(k) = l_{ref} - l(k)$.
-
-% We note that the $z$-axis control described here operates the AFM in constant
-% force mode during imaging. It is straightforward to perform scanning under
-% different AFM modes, such as tapping mode, simply by adjusting the signals and
-% control involved in the vertical loop.
-
-\subsection{Feedforward Control}\label{sec:ff_control}
-% In our AFM, there is a strong coupling between the horizontal axes and vertical deflection.
-Fig.~\ref{fig:mimo_frf_uxuy} shows a MIMO FRF for $u_X$ and $u_Y$ to the outputs in each axis.
-The dotted black curves are the open loop responses and the dashed red curves are the nominal closed-loop responses.
-Though the $Z$-direction inputs are not shown, the closed loop responses include the $Z$-axis controller.
-Note that, especially for $H_{z,u_X}$, the closed-loop response is barely improved over the open loop response and in particular, there is a sharp resonance at 215~Hz and 505~Hz.
-To deal with this, we employ two different strategies for CS and raster scanning.
-
-For CS scanning, we insert a feed-forward filter with three notches, one at 215~Hz, one at 350~Hz and one at 505~Hz.
-We design a similar feed-forward filter for the $Y$-axis.
-Both filters are shown in Fig.~\ref{fig:mimo_frf_uxuy} as the solid pink curves and the resulting overall FRF is shown as the solid blue curves, which show a dramatic reduction in the cross coupling.
-A similar affect could be achieve by using a simple low-pass filter.
-However, to achieve the same 40~dB of attenuation of the mode at 215 Hz, would require, e.g., that a two-pole LPF have its cut-off frequency at about 20~Hz.
-
-For raster scanning, we use a truncated Fourier series, where each Fourier coefficient is scaled by the inverse of the closed-loop FRF at the corresponding frequency.
-We truncate this series such that the highest frequency is smaller than 200 Hz.
-See, e.g., \cite{clayton_review_2009} for more details on this strategy.
-Note that this scheme implies that the effective bandwidth of the $X$-axis controller is higher while raster scanning than while CS-scanning.
-On the other hand, it also implies that the for faster scan rates, fewer Fourier coefficients are used, and so the approximation to a triangle wave is worse.
-
-% =========================================================================
 \section{Implementation}\label{sec:implementation}
@@
 
-% =========================================================================
-\subsection{State machine}
 Implementing the $\mu$-path scheme involves operating the AFM in several
@@
 
+\begin{figure*}[ht!]
+  \centering
+  \includegraphics[width=1\textwidth]{figures/AFM_loop_xyz.pdf}
+  \caption{Block diagram of the $Z$-axis control loop. The anti-windup is active
+    for decision index $i\in\{0,1,5\}$, which correspond to states such that
+    $r_Z=\rzup$.}
+  \label{fig:afm_bd_dinv}
+\end{figure*}
 \subsection{The pre-scan}
-\begin{figure*}
-  \begin{subfigure}{.33\textwidth}
-    \includesvg[width=1\textwidth]{figures/zbounce_uz_example.svg}
-    \caption{ }
-    % \label{fig: }
-  \end{subfigure}
-  \begin{subfigure}{.33\textwidth}
-    \includesvg[width=1\textwidth]{figures/prescan_uz_example.svg}
-    \caption{ }
-    \label{fig:uz_prescan}
-  \end{subfigure}
-  \begin{subfigure}{.33\textwidth}
-    \includesvg[width=1\textwidth]{figures/prescan_zbounce_PSD.svg}
-    \caption{ }
-    % \label{fig: }
-  \end{subfigure}
-  \caption{(a) A ``$Z$-bounce'' experiment where the $XY$-stage is motionless
-    and the cantilever is repeatedly engaged and disengaged. (b) One cycle of a
-    tightly packed set of CS-cycles where the movement between each measurement
-    location is 0. (c) PSDs from the portions of the trajectories which are
-    colored blue and turquoise, averaged over many such cycles, demonstrating
-    that the scan process itself reduces vibration in the $Z$-axis.}
-  \label{fig:prescan_difference}
-\end{figure*}
+% \begin{figure*}
+%   \begin{subfigure}{.33\textwidth}
+%     \includesvg[width=1\textwidth]{figures/zbounce_uz_example.svg}
+%     \caption{ }
+%     % \label{fig: }
+%   \end{subfigure}
+%   \begin{subfigure}{.33\textwidth}
+%     \includesvg[width=1\textwidth]{figures/prescan_uz_example.svg}
+%     \caption{ }
+%     \label{fig:uz_prescan}
+%   \end{subfigure}
+%   \begin{subfigure}{.33\textwidth}
+%     \includesvg[width=1\textwidth]{figures/prescan_zbounce_PSD.svg}
+%     \caption{ }
+%     % \label{fig: }
+%   \end{subfigure}
+%   \caption{(a) A ``$Z$-bounce'' experiment where the $XY$-stage is motionless
+%     and the cantilever is repeatedly engaged and disengaged. (b) One cycle of a
+%     tightly packed set of CS-cycles where the movement between each measurement
+%     location is 0. (c) PSDs from the portions of the trajectories which are
+%     colored blue and turquoise, averaged over many such cycles, demonstrating
+%     that the scan process itself reduces vibration in the $Z$-axis.}
+%   \label{fig:prescan_difference}
+% \end{figure*}
 After the tip-descent, we begin scanning in a ``pre-scan'' phase (state (3)).
@@
 
+\subsection{Control}\label{sec:control}
+\begin{figure}
+  \centering
+  \includesvg[width=1\columnwidth]{figures/z_control_design.svg}
+  \caption{FRFs of the $Z$-axis. The blue curve is the open loop response from $u_Z$ to deflection. By inverting the bending mode at 215~Hz, we achieve the black curve in closed-loop.}
+  \label{fig:z_control}
+\end{figure}
+
+The control structure for each axis is similar and essentially consists of a set of filters in series with a PI controller.
+The open-loop frequency response for the $Z$-axis is shown in Fig.~\ref{fig:z_control} (black curve) and in Fig.~\ref{fig:mimo_frf_uxuy} for the $X$ and $Y$ axes (red curves).
+The first resonance of each axis is the bending mode.
+For the $Z$ axis, this resonance is at 215~Hz and at approximately 350~Hz for the $X$ and $Y$ axes.
+
+The filter for the $Z$-axis controller inverts the complex-conjugate pole-zero pair at 215~Hz.
+This allows the gain of the PI controller to be increased substantially.
+The closed-loop achieves a bandwidth of about 450~Hz, as shown by the black curve in Fig.~\ref{fig:z_control}.
+
+We take a similar approach to the $X$ and $Y$ axes.
+The filter inverts the bending modes at 350~Hz and adds a notch filter for the main resonant peak at 650~Hz.
+The resulting closed-loops are shown in the (1,1) and (2,2) positions of Fig.~\ref{fig:mimo_frf_uxuy}.
+In general, the $X$-axis positioning requirements are more stringent for both CS and raster scanning
+
+Unfortunately, as Fig.~\ref{fig:mimo_frf_uxuy} makes clear, there is a strong cross-coupling between the axes.
+The coupling from the horizontal plane to the $Z$ axis is particularly problematic and our SISO control scheme does little to attenuate the resonances of $G_{Z,u_X}$ and $G_{Z,u_Y}$.
+In particular, there are modes in both these transfer functions at 215 and 505 Hz that do not appear in a SISO model of $G_{X,u_x}$ or $G_{y,u_Y}$.
+
+For raster scans, the frequency content of the $X$-axis reference (which is a triangle wave) decays like $1/n^2$ with a gain proportional to the raster frequency.
+In contrast, the $X$-axis reference for a $\mu$-path scan is composed of a sequence of steps and ramps.
+The inclusion of the (discontinuous) steps means we should expect the $\mu$-path $X$ reference to decay like $1/n$.
+Thus,  while the cross-coupling can induce $Z$-axis vibrations for faster raster scans, it is especially problematic for $\mu$-path scanning.
+In principle, one could mitigate these issues with a full MIMO control design.
+In this work, we opt for a much simpler feedforward scheme described in the next subsection.
+
+% The control law used for the $Y$-axis is a simple PI controller of the
+% form
+% \begin{equation}
+%   \frac{U(z)}{E_Y(z)}=D(z) = \frac{K_Iz}{z-1},
+%   \label{eqn:dzI}
+% \end{equation}
+% where, the error signal $E_Y(z) = Y(z)-R_Y$.
+% 
+% \todo{Should I implement something better for $Y$-axis, e.g., cancel complex
+%   pole-zeros at 350 hz and add notch filter???}
+
+% The $Z$-axis control is slightly more complicated than the simple $Y$-axis
+% integral controller and is described in the following subsection.
+% \subsection{Z-axis Control Design}\label{sec:zaxis_cs_control}
+% The main challenge to increasing the $Z$-axis bandwidth is the bending mode
+% resonance at 215 Hz, which can be seen in the FRF from $u_Z$ to $Z_{d}$ in
+% Fig.~\ref{fig:z_control} (blue curve). We address this by inverting the complex
+% pole-zero pair at 215 Hz. Thus, the entire $Z$-axis controller consists of a PI
+% controller, $D_I(z)$ cascaded with the resonance inversion, $D^{-1}(z)$, as shown in Fig.~\ref{fig:afm_bd_dinv}. The DC-gain
+% of $D$ is (approximately) the same as the DC-gain of the plant.
+% The inclusion of $D^{-1}$ allows us to substantially increase the PI gain and
+% achieve a closed-loop bandwidth of about 480 Hz. This is the black curve in Fig.~\ref{fig:z_control}.
+
+% There are multiple advantages to this method: first,
+% an inverse compensator still makes sense as a feedforward, open-loop compensator
+% if the feedback path is broken. This situation can and does occur during parts
+% of the CS cycle. Second, the inverse compensator
+% requires no tuning as it is defined only by a fit to the measured FRF.
+
+\begin{figure*}
+  \centering
+  \includesvg[width=1\textwidth]{figures/MIMO_CL_uxuy.svg}
+  \caption{MIMO closed and open loop FRFs, showing the dramatic affect on $G_{Z,u_X}$ and $G_{Z,u_Y}$ when the feedforward compensators are used for the $X$ and $Y$ axes.}
+  \label{fig:mimo_frf_uxuy}
+\end{figure*}
+
+% As illustrated in Fig.~\ref{fig:zMultiplex_anderssonLab}, the voltage applied to
+% the $z$-piezo is adjusted by switching the feedback signal between the $z$-axis
+% position sensor (when the tip is off the surface) and the deflection signal
+% (when the tip is engaged). The difference equation associated with
+% \eqref{eqn:dzI} for the $z$-axis is
+% \begin{equation}
+%   u_z(k) = K_Ie(k) + u_z(k-1).
+%   \label{eqn:intdiff}
+% \end{equation}
+
+% In the $z$-axis position control mode, the $z$-axis position is controlled to a
+% fixed value $z_{ref}$ which, in general, is slightly above the sample surface.
+% The difference between the measured $z$-axis position and $z_{ref}$,
+% ${e(k) = z_{ref} - z(k)}$, is used as the error signal. In the deflection
+% control mode, when the tip is in contact with the sample, the deflection signal
+% is controlled to a fixed value $l_{ref}$ to ensure a constant tip-sample force.
+% The sample surface acts as a disturbance to the control loop. Therefore, the
+% $z$-axis position measurements can be taken to represent the surface topography
+% of the sample. In this case, the difference between the measured deflection and
+% $l_{ref}$ is the error, $e(k) = l_{ref} - l(k)$.
+
+% We note that the $z$-axis control described here operates the AFM in constant
+% force mode during imaging. It is straightforward to perform scanning under
+% different AFM modes, such as tapping mode, simply by adjusting the signals and
+% control involved in the vertical loop.
+
+\subsection{Feedforward Control}\label{sec:ff_control}
+% In our AFM, there is a strong coupling between the horizontal axes and vertical deflection.
+Fig.~\ref{fig:mimo_frf_uxuy} shows a MIMO FRF for $u_X$ and $u_Y$ to the outputs in each axis.
+The dotted black curves are the open loop responses and the dashed red curves are the nominal closed-loop responses.
+Though the $Z$-direction inputs are not shown, the closed loop responses include the $Z$-axis controller.
+Note that, especially for $H_{z,u_X}$, the closed-loop response is barely improved over the open loop response and in particular, there is a sharp resonance at 215~Hz and 505~Hz.
+To deal with this, we employ two different strategies for CS and raster scanning.
+
+For CS scanning, we insert a feed-forward filter with three notches, one at 215~Hz, one at 350~Hz and one at 505~Hz.
+We design a similar feed-forward filter for the $Y$-axis.
+Both filters are shown in Fig.~\ref{fig:mimo_frf_uxuy} as the solid pink curves and the resulting overall FRF is shown as the solid blue curves, which show a dramatic reduction in the cross coupling.
+A similar affect could be achieve by using a simple low-pass filter.
+However, to achieve the same 40~dB of attenuation of the mode at 215 Hz, would require, e.g., that a two-pole LPF have its cut-off frequency at about 20~Hz.
+
+For raster scanning, we use a truncated Fourier series, where each Fourier coefficient is scaled by the inverse of the closed-loop FRF at the corresponding frequency.
+We truncate this series such that the highest frequency is smaller than 200 Hz.
+See, e.g., \cite{clayton_review_2009} for more details on this strategy.
+Note that this scheme implies that the effective bandwidth of the $X$-axis controller is higher while raster scanning than while CS-scanning.
+On the other hand, it also implies that the for faster scan rates, fewer Fourier coefficients are used, and so the approximation to a triangle wave is worse.
+\begin{figure}
+  \includesvg[width=1\columnwidth]{figures/with_wo_ff.svg}
+  \caption{Scans over mica. (left) Without feedforward. (right) with feedforward.}
+  \label{fig:with_ff}
+\end{figure}
+
+\section{Metrics}\label{sec:rdi}
+In section~\ref{sec:results} we use three metrics to asses our results.
+The first two seek to quantify image quality of two images. 
+Define a master image as $X$ and a reconstruction or corrupted version as $Y$, with each having $s\times h=m$ pixels.
+Let $x=\textrm{vec}(X)$ and $y=\textrm{vec}(Y)$. Let $L$ be the dynamic range of the master image $x$.
+Then the peak signal to noise ratio (PSNR) is given by
+\begin{equation*}
+  \text{PSNR}(x,y) = 10\log_{10}\frac{L^2}
+  {\sqrt{\frac{1}{p^2} \sum_{i=1}^{m}( x_{i} - y_{i})^2 }}.
+\end{equation*}
+
+The goal of the SSIM is to compare two image's structure, luminescence, and contrast and is built up from the means ($\mu_x$ and $\mu_y$), standard deviations ($\sigma_x$ and $\sigma_y$), and covariance ($\sigma_{xy}$) of the image vectors $x$ and $y$.
+The variation of the SSIM used in this paper is defined as
+\begin{equation*}
+  \text{SSIM}(x,y) = \frac{(2\mu_x\mu_y + C_1)(2\sigma_{xy}+C_2)}
+  {(\mu_x^2 + \mu_y^2 + C_1)(\sigma_x^2 + \sigma_y^2 + C_2)}
+\end{equation*}
+where the constants $C_1$ and $C_2$ are regularizing constants to prevent singularity if, e.g., $\mu_x=\mu_y=0$.
+We use the default values suggested in \cite{wang_image_2004} of $C_1=(0.01L)^2$ and ${C_2=(0.03L)^2}$, where again, $L$ is the dynamic range.
+In general two images which are identical will yield an infinite PSNR and an SSIM of 1.
+
+\subsection{Limitations of SSIM and PSNR}\label{sec:limits}
+What kind of numbers are reasonable to expect from the SSIM and PSNR metrics?
+To answer this question, we compare a sequence of 1~Hz raster scans.
+In this experiment, (Fig. \ref{fig:rast_unaligned_1}) we took 6 raster scans of the same 5 by 5 micron
+square of the CS-20NG sample grating. These scans were taken sequentially and
+the NPXY100A remained in closed-loop throughout the process.
+Fig.~\ref{fig:rast_unaligned_1} shows the error between the master
+image and the remaining 6 images.
+Temporally, the images are order left-to-right and top-to-bottom.
+Thus we can see, both visually and via the metrics, that in Fig.~\ref{fig:rast_unaligned_1} the mis-alignment
+grows over time. 
+\todo{Should probably remove this entire section?}
+
+Taking the first scan as the master, we compute the PSNR and SSIM
+metrics. The best PSNR here is 16.57 and the worst is 9.02.
+The best SSIM is 0.54 and the worst is 0.28.
+
+\begin{figure}[t!]
+  \includesvg[width=1\columnwidth]{figures/baseline_errors_aligned_1Hz.svg}
+  \caption{Errors between the first and second (left column) and first and sixth (right column) raster scans in a sequence of six 1.0~Hz raster scans. (top) Errors without alignment (bottom)
+    The same data but aligned via cross correlation.}
+  \label{fig:baseline_errors}
+\end{figure}
+
+Next, using a cross-correlation alignment technique
+% discussed in Section~\ref{sec:align},
+we aligned the master image with a sub-slice of each of
+the remaining 6 (the sub-slice removes 25 pixels from each side). Again, we
+computed the PSNR and SSIM. These results are shown in
+Fig.~\ref{fig:rast_aligned_1}, which again shows the errors between the
+aligned master and the remaining 6 images. Although the situation is improved
+compared to the un-aligned images, there is still noticeable stretching,
+particularly in the $Y$-direction. Notably, with the alignment technique,
+the SSIM lies between 0.7 and 0.73 and the PSNR ranges from 22.51 to 24.99 and appears more stable in time.
 % \section{Post-processing}\label{sec:post_process}
@@
 % eliminate the problem.
-
-\section{Metrics}\label{sec:rdi}
-In section~\ref{sec:results} we use three metrics to asses our results.
-The first two seek to quantify image quality of two images. 
-Define a master image as $X$ and a reconstruction or corrupted version as $Y$, with each having $s\times h=m$ pixels.
-Let $x=\textrm{vec}(X)$ and $y=\textrm{vec}(Y)$. Let $L$ be the dynamic range of the master image $x$.
-Then the peak signal to noise ratio (PSNR) is given by
-\begin{equation*}
-  \text{PSNR}(x,y) = 10\log_{10}\frac{L^2}
-  {\sqrt{\frac{1}{p^2} \sum_{i=1}^{m}( x_{i} - y_{i})^2 }}.
-\end{equation*}
-
-The goal of the SSIM is to compare two image's structure, luminescence, and contrast and is built up from the means ($\mu_x$ and $\mu_y$), standard deviations ($\sigma_x$ and $\sigma_y$), and covariance ($\sigma_{xy}$) of the image vectors $x$ and $y$.
-The variation of the SSIM used in this paper is defined as
-\begin{equation*}
-  \text{SSIM}(x,y) = \frac{(2\mu_x\mu_y + C_1)(2\sigma_{xy}+C_2)}
-  {(\mu_x^2 + \mu_y^2 + C_1)(\sigma_x^2 + \sigma_y^2 + C_2)}
-\end{equation*}
-where the constants $C_1$ and $C_2$ are regularizing constants to prevent singularity if, e.g., $\mu_x=\mu_y=0$.
-We use the default values suggested in \cite{wang_image_2004} of $C_1=(0.01L)^2$ and ${C_2=(0.03L)^2}$, where again, $L$ is the dynamic range.
-In general two images which are identical will yield an infinite PSNR and an SSIM of 1.
-
-\subsection{Limitations of SSIM and PSNR}\label{sec:limits}
-What kind of numbers are reasonable to expect from the SSIM and PSNR metrics?
-To answer this question, we compare a sequence of 1~Hz raster scans.
-In this experiment, (Fig. \ref{fig:rast_unaligned_1}) we took 6 raster scans of the same 5 by 5 micron
-square of the CS-20NG sample grating. These scans were taken sequentially and
-the NPXY100A remained in closed-loop throughout the process.
-Fig.~\ref{fig:rast_unaligned_1} shows the error between the master
-image and the remaining 6 images.
-Temporally, the images are order left-to-right and top-to-bottom.
-Thus we can see, both visually and via the metrics, that in Fig.~\ref{fig:rast_unaligned_1} the mis-alignment
-grows over time. 
-\todo{Should probably remove this entire section?}
-
-Taking the first scan as the master, we compute the PSNR and SSIM
-metrics. The best PSNR here is 16.57 and the worst is 9.02.
-The best SSIM is 0.54 and the worst is 0.28.
-
-\begin{figure}[t!]
-  % ------------ 1.0 Hz ---------------------
-  \begin{subfigure}{.48\textwidth}
-    \includesvg[width=1\textwidth]{figures/baseline_errors_noalign_1Hz.svg}
-    \caption{1.0~Hz, no alignment.}
-    \label{fig:rast_unaligned_1}
-  \end{subfigure}
-  \hfill
-  \begin{subfigure}{.48\textwidth}
-    \includesvg[width=1\textwidth]{figures/baseline_errors_aligned_1Hz.svg}
-    \caption{1.0~Hz, with alignment.}
-    \label{fig:rast_aligned_1}
-  \end{subfigure}
-% 
-  \caption{Errors between a ''master'' and 6 different raster scans, all taken
-    sequentially and at a scan rate of 0.5 Hz. (a) Errors without alignment (b)
-    The same data as above in (a) but aligned via cross correlation.}
-  \label{fig:baseline_errors}
-\end{figure}
-
-Next, using a cross-correlation alignment technique
-% discussed in Section~\ref{sec:align},
-we aligned the master image with a sub-slice of each of
-the remaining 6 (the sub-slice removes 25 pixels from each side). Again, we
-computed the PSNR and SSIM. These results are shown in
-Fig.~\ref{fig:rast_aligned_1}, which again shows the errors between the
-aligned master and the remaining 6 images. Although the situation is improved
-compared to the un-aligned images, there is still noticeable stretching,
-particularly in the $Y$-direction. Notably, with the alignment technique,
-the SSIM lies between 0.7 and 0.73 and the PSNR ranges from 22.51 to 24.99 and appears more stable in time.
+% =========================================================================
 
@@
 
-\begin{figure*}[t!]
-  \includesvg[width=1\textwidth]{figures/cs_raster_pixel_rows_6-5-2019.svg}
+\begin{figure}[t!]
+  \includesvg[width=1\columnwidth]{figures/cs_raster_pixel_rows_6-5-2019.svg}
   \caption{Rows of pixels, as indicated by the red lines in
@@
   \label{fig:pixel_rows}
-\end{figure*}
+\end{figure}
 
@@
 
-\begin{figure*}[ht!]
-  \centering
-  \begin{subfigure}{1\textwidth}
-    \centering
-    \includesvg[width=0.8\textwidth]{figures/cs_rast_time_vs_ssim.svg}
+\begin{figure}[ht!]
+  \centering
+  \begin{subfigure}{1\columnwidth}
+    \centering
+    \includesvg[width=1\columnwidth]{figures/cs_rast_time_vs_ssim.svg}
     \caption{}
@@
   \end{subfigure}
-  \begin{subfigure}{1\textwidth}
-    \centering
-    \includesvg[width=0.8\textwidth]{figures/cs_rast_time_vs_psnr.svg}
+  \begin{subfigure}{1\columnwidth}
+    \centering
+    \includesvg[width=1\columnwidth]{figures/cs_rast_time_vs_psnr.svg}
     \caption{}
@@
   \end{subfigure}
-  \begin{subfigure}{1\textwidth}
-    \centering
-    \includesvg[width=0.8\textwidth]{figures/cs_rast_damage.svg}
+  \begin{subfigure}{1\columnwidth}
+    \centering
+    \includesvg[width=1\columnwidth]{figures/cs_rast_damage.svg}
     \caption{}
@@
 The scan rate is indicated by color while the scan style is indicated by marker style.}
-
   % \label{fig:time_vs_metrics}
-\end{figure*}
+\end{figure}
 

### 2019-06-12 plot_with_without_FF_loop_cs20ngflat.m

@@ -1,0 +1,179 @@
+% 
+% This script plots the z-bounce like experiment over a flat portion of the
+% CS20ng grating. Both controllers are based on the loop-shaping transfer
+% function control. The -03 experiment has the feedforward filter, the 02 does
+% not.
+
+% close all
+clear PATHS
+addpath functions
+addpath ~/matlab/dependencies/l1c/
+addpath ~/matlab/dependencies/l1c/lib
+
+addpath ~/matlab/afm-cs/matlab-code/functions/
+% initialize paths.
+
+figbase = 20;
+
+
+size_dir = '5microns';
+hole_depth = (20);
+
+chan_map = ChannelMap([1:5]);
+% exp_date = '3-20-2019'
+% ----------------------- Load and Process CS-data -----------------------------
+
+
+data_root = '/media/labserver/afm-cs/z-bounce/6-12-2019/';
+% ----------------------- Load and Process raster-data -------------------------
+cs_files = {...
+'cs-traj-512pix-3perc-500nm-5mic-01Hz-150prescan-notconnect_out_6-12-2019-03.csv',...
+'cs-traj-512pix-3perc-500nm-5mic-01Hz-150prescan-notconnect_out_6-12-2019-02.csv',...
+};
+
+cs_exps = {};
+for k=1:length(cs_files)
+  cs_paths = get_cs_paths(data_root, cs_files{k});
+  gg = @(u, idx_state_s) log_creep_detrend(u, idx_state_s);
+  cs_exps{k} = CsExp(cs_paths, 'feature_height', hole_depth, 'gg', gg, 'load_full', true);
+  cs_exps{k}.print_state_times();
+end
+
+name_s = {'CR w/o notch', 'CR-w/notch', 'CZ w/o notch', 'CZ w/ notch'};
+for k=1:length(cs_exps)
+   cs_exps{k}.uz  = cs_exps{k}.uz*AFM.volts2nm_z;
+end
+
+%%
+if 0
+    [~, axs1] = make_cs_traj_figs(figbase+100, 3);
+    cs_exps{1}.plot_all_cycles(axs1{1:3}, [], [], 512);
+    
+    [~, axs2] = make_cs_traj_figs(figbase+200, 3);
+    cs_exps{2}.plot_all_cycles(axs2{1:3}, [], [], 512);
+    
[…]

### 2019-06-12 q_vs_density.m

@@ -1,6 +1,6 @@
 % ------------ Row 1, CS20NG -------------------------
 
-
+addpath functions
 im_og = double(imread('cs20ng.png'));
 % im_og = double(imread('cameraman.tif'));
 im_og = im_og - min(im_og(:));
@@ -14,46 +14,65 @@ mx = max(im_og(:)) - min(im_og(:))
 skip = 4;
 h = skip:skip:npix;
 im_128_sub = im_og(h, :);
-
 im_128 = interp_y(im_128_sub, npix);
-
 ssm_128 = ssim(im_128, im_og, 'DynamicRange', mx);
 psn_128 = psnr(im_128, im_og, mx);
+
+skip = 8;
+h = skip:skip:npix;
+im_64_sub = im_og(h, :);
+im_64 = interp_y(im_64_sub, npix);
+ssm_64 = ssim(im_64, im_og, 'DynamicRange', mx);
+psn_64 = psnr(im_64, im_og, mx);
+
 
 U_fun = @(x) idct(x);
 Ut_fun = @(x) dct(x);
 
-
-%%
-fprintf('128: ssm: %.3f, psn: %.3f\n', ssm_128, psn_128);
-fprintf('===============================================\n');
-figure(11); clf
-subplot(1,2,1),
-imagesc(im_128), colormap('gray')
-drawnow()
-
 mu = 1e-7;
 delta = 0.01;
-% alpv = 0.01;
+alpv = 0.01;
 alph = 0.75;
 opts = NESTA_opts('U', U_fun, 'Ut', Ut_fun, 'verbose', 0, 'TolVar', 1e-5,...
     'alpha_v', alpv, 'alpha_h', alph);
 
-
-qs = (5:3:50);
+%%
+qs = [(1:2:10), (15:5:50), (50:15:512)];
 fracs = (5:2:50)/100;
 % fracs = 50/100;
-dat = zeros(length(qs), 6);
-map = zeros(length(qs), length(fracs));
+dat128 = zeros(length(qs), 7);
+dat64 = zeros(length(qs), 7);
+map_ssm = zeros(length(qs), length(fracs));
+map_psn = zeros(length(qs), length(fracs));
+
+Y = map_ssm;
+X = map_ssm;
 gam = npix/50;
-for j = 1:length(qs)
-    store = true;
-    opts.alpha_v = 0.5;
-    opts.alpha_h = 2*(gam*qs(j))/npix;
-    for k=1:length(fracs)
[…]

### 2019-06-15 latex/afm-cs-main.tex
Update data automagically with catchfilebetween tags. Re-work some of the results section.

@@
 \usepackage{placeins}
-\usepackage{todonotes}
+\usepackage[disable]{todonotes}
 
@@
 
+\usepackage{catchfilebetweentags} % for data input
+\newcommand{\scanD}[1]{\ExecuteMetaData[cs_data.txt]{#1}}
+\newcommand{\baseline}[1]{\ExecuteMetaData[baseline_errors.txt]{#1}}
+
 % *******************************************************************************
@@
 % ***************** WARNING: comment this out for final version. ****************
-\usepackage[paperwidth=734.295pt, textwidth=516pt,
-            marginparsep=5pt, hoffset=10pt, marginparwidth=90pt,
-            textheight=696pt]{geometry}
+%\usepackage[paperwidth=734.295pt, textwidth=516pt,
+%            marginparsep=5pt, hoffset=10pt, marginparwidth=90pt,
+%           textheight=696pt]{geometry}
 % Use layouts to display the original dimensions, so we can get as close to that as possible with
 % our fake page size.
-\usepackage{layouts}
+%\usepackage{layouts}
 %textwidth: \printinunitsof{in}\prntlen{\textwidth}
@@
   acquire data on a grating sample.
-  %using two different sampling
-  %approaches: randomly-placed $\mu-$paths and $\mu-$paths designed to minimize
-  %the reconstruction error based on partial prior information about the spatial
-  %frequency content in the sample image.
   Reconstructions are made from these data using
@@
 builds upon that earlier work in several significant ways.
+
+\textbf{Contributions}
+Much of the prior work on undersampled AFM images is based purely on simulations \cite{han_optimal_2018, Luo_nano_2015, oxvig_structure_2017, jensen_reconstruction_2013, maxwell_acc_2014, Chen_2012jx}.
 
@@
 \end{equation}
-\noindent where $y\in\mathbb{R}^n$ is the observation vector, $R$ is an
+\noindent where $y\in\mathbb{R}^m$ is the observation vector, $R$ is an
 $n\times m$ matrix defining the measurements, $U$ is an $m\times m$ sparsity
@@
 In the following, we assume that $U^TU=I$, though in the simulation and
-experimental results, we take $U$ as the Discrete Cosine Transform (DCT) basis.
+experimental results, we take $U^T$ as the Discrete Cosine Transform (DCT).
 The DCT basis generally keeps a good balance between achieving a low
@@
 strong discontinuities in the image. These artifacts grow more prominent as the
-length of the $\mu$-paths is increased \cite{maxwell2014compressed} as these
+length of the $\mu$-paths is increased \cite{maxwell2014compressed}, because these
 longer paths lead to increased mutual coherence between the measurement matrix
 $R$ and the sparsity basis $U$. However, longer $\mu$-paths means fewer
-tip re-engagements and thus shorter scan times.
+$\mu$-paths and thus shorter scan times.
 \noindent 
@@
 \end{figure*}
-\todo{Re-do this figure???}
 \endgroup
 
-\todo{This development is way too long!}
 To mitigate these affects, we propose a new variant of BPDN that we term basis pursuit with
@@
 \todo{I believe this is correct: Sean/Yufan can you confirm or reject?}
-
-Moreover, when written as \eqref{op:bp_tvW}, the problem is in a form that may be solved with NESTA~\cite{becker_nesta_2011}.
+When written as \eqref{op:bp_tvW}, the problem is in a form that may be solved with NESTA~\cite{becker_nesta_2011}.
 
@@
 
-A comparison between BPDN and BPVV is shown in
+A simulation comparison between BPDN and BPVV is shown in
 Fig.~\ref{fig:BPTV_demonstration}.
-The first column two raster scans: the top is 512 by 512 pixel image of a CS20NG grating acquired with an Agilent 5400 AFM and the bottom is a 256 by 256 pixel image of DNA acquired with an Agilent 5500 AFM.
+The first column shows two raster scans: the top is 512 by 512 pixel image of a CS20NG grating acquired with an Agilent 5400 AFM and the bottom is a 256 by 256 pixel image of DNA acquired with an Agilent 5500 AFM.
 For the CS20NG grating, we sampled 15\% of the pixels with 50 pixel $\mu$-paths.
@@
 
-Through a breakout box, the Agilent 5400 provides access to the $z$-axis deflection signal.
-When the Agilent software is set to open-loop mode, a $\pm10$~volt input on the standard control box allows control of the $z$-axis of the N9524a piezo scanner, which has a total range of 7 $\mu$m.
+Through a breakout box, the Agilent 5400 provides access to the $Z$-axis deflection signal.
+When the Agilent software is set to open-loop mode, a $\pm10$~volt input on the standard control box allows control of the $Z$-axis of the N9524a piezo scanner, which has a total range of 7 $\mu$m.
 Initial (course) engagement of the tip to the
@@
 Implementing the $\mu$-path scheme involves operating the AFM in several
-distinct stages. In the $xy$-direction, the system must transition from tracking
+distinct stages. In the $XY$-direction, the system must transition from tracking
 a step command (in the transition to a new measurement location) to tracking a
 scan pattern. For our simple integral controller, this only involves changing
-the reference signals $x_{ref}$ and $y_{ref}$.
-In the $z$-direction, the system
+the reference signals $X_{ref}$ and $Y_{ref}$.
+In the $Z$-direction, the system
 must transition between tip descent, surface scanning, tip retraction, and
-maintaining a $z$-axis position.
+maintaining a $Z$-axis position.
 
@@
 \end{figure}
-
-The control structure for each axis is similar and essentially consists of a set of filters in series with a PI controller.
-The open-loop frequency response for the $Z$-axis is shown in Fig.~\ref{fig:z_control} (black curve) and in Fig.~\ref{fig:mimo_frf_uxuy} for the $X$ and $Y$ axes (red curves).
-The first resonance of each axis is the bending mode.
-For the $Z$ axis, this resonance is at 215~Hz and at approximately 350~Hz for the $X$ and $Y$ axes.
-
-The filter for the $Z$-axis controller inverts the complex-conjugate pole-zero pair at 215~Hz.
+The control structure for each axis, shown in the block diagram in Fig.~\ref{fig:afm_bd_dinv}, is similar and essentially consists of a set of filters in series with a PI controller.
+The open-loop frequency response for the $Z$-axis is shown in Fig.~\ref{fig:z_control} and in Fig.~\ref{fig:mimo_frf_uxuy} for the $X$ and $Y$ axes as the black curves.
+The first resonance of each axis is the bending mode, which appears at 215~Hz for the $Z$ axis and about 350~Hz for the $X$ and $Y$ axes.
+
+The filter portion of the $Z$-axis controller $D_Z$ is second-order and simply inverts the complex-conjugate pole-zero pair at 215~Hz.
 This allows the gain of the PI controller to be increased substantially.
 The closed-loop achieves a bandwidth of about 450~Hz, as shown by the black curve in Fig.~\ref{fig:z_control}.
-
-We take a similar approach to the $X$ and $Y$ axes.
-The filter inverts the bending modes at 350~Hz and adds a notch filter for the main resonant peak at 650~Hz.
-The resulting closed-loops are shown in the (1,1) and (2,2) positions of Fig.~\ref{fig:mimo_frf_uxuy}.
-In general, the $X$-axis positioning requirements are more stringent for both CS and raster scanning
-
-Unfortunately, as Fig.~\ref{fig:mimo_frf_uxuy} makes clear, there is a strong cross-coupling between the axes.
-The coupling from the horizontal plane to the $Z$ axis is particularly problematic and our SISO control scheme does little to attenuate the resonances of $G_{Z,u_X}$ and $G_{Z,u_Y}$.
-In particular, there are modes in both these transfer functions at 215 and 505 Hz that do not appear in a SISO model of $G_{X,u_x}$ or $G_{y,u_Y}$.
-
-For raster scans, the frequency content of the $X$-axis reference (which is a triangle wave) decays like $1/n^2$ with a gain proportional to the raster frequency.
-In contrast, the $X$-axis reference for a $\mu$-path scan is composed of a sequence of steps and ramps.
-The inclusion of the (discontinuous) steps means we should expect the $\mu$-path $X$ reference to decay like $1/n$.
-Thus,  while the cross-coupling can induce $Z$-axis vibrations for faster raster scans, it is especially problematic for $\mu$-path scanning.
-In principle, one could mitigate these issues with a full MIMO control design.
-In this work, we opt for a much simpler feedforward scheme described in the next subsection.
-
-% The control law used for the $Y$-axis is a simple PI controller of the
-% form
-% \begin{equation}
-%   \frac{U(z)}{E_Y(z)}=D(z) = \frac{K_Iz}{z-1},
-%   \label{eqn:dzI}
-% \end{equation}
-% where, the error signal $E_Y(z) = Y(z)-R_Y$.
-% 
-% \todo{Should I implement something better for $Y$-axis, e.g., cancel complex
-%   pole-zeros at 350 hz and add notch filter???}
-
-% The $Z$-axis control is slightly more complicated than the simple $Y$-axis
-% integral controller and is described in the following subsection.
-% \subsection{Z-axis Control Design}\label{sec:zaxis_cs_control}
-% The main challenge to increasing the $Z$-axis bandwidth is the bending mode
-% resonance at 215 Hz, which can be seen in the FRF from $u_Z$ to $Z_{d}$ in
-% Fig.~\ref{fig:z_control} (blue curve). We address this by inverting the complex
-% pole-zero pair at 215 Hz. Thus, the entire $Z$-axis controller consists of a PI
-% controller, $D_I(z)$ cascaded with the resonance inversion, $D^{-1}(z)$, as shown in Fig.~\ref{fig:afm_bd_dinv}. The DC-gain
-% of $D$ is (approximately) the same as the DC-gain of the plant.
-% The inclusion of $D^{-1}$ allows us to substantially increase the PI gain and
-% achieve a closed-loop bandwidth of about 480 Hz. This is the black curve in Fig.~\ref{fig:z_control}.
+Without this inversion, the bandwidth is limited to about 50~Hz.
+
+We take a similar approach for the $X$ and $Y$ axes.
+The filters $D_x$ and $D_y$ invert the bending modes at 350~Hz and add notch filters at the main resonant peaks near 650~Hz.
+The resulting closed-loop transfer functions are shown as the red curves in Fig.~\ref{fig:mimo_frf_uxuy}.
+
+In general, the $X$-axis positioning requirements are more stringent for both CS and raster scanning.
+BLA BLAH hysteresis and creep.
+Thus, the $X$-axis compensator also includes an inverse creep and hysteresis model.
+The hysteresis model is a modified Prandtl-Ishlinki type model and is based on the work of \cite{kuhnen_modeling_2003}, while the drift compensation models the piezo creep as a simple second order transfer function with real poles and zeros.
+In Fig.~\ref{fig:afm_bd_dinv}, the hysteresis inversion is indicated by $\mathcal{H}^{-1}[\cdot]$.
+We have found that the inclusion of these extra compensators limits the overshoot of the $X$-axis during larger moves between different $\mu$-paths.
+More details on fitting the creep and hysteresis models can be found in our other work \cite{braker_afmmpc_2019}.
 
@@
 To deal with this, we employ two different strategies for CS and raster scanning.
-
-For CS scanning, we insert a feed-forward filter with three notches, one at 215~Hz, one at 350~Hz and one at 505~Hz.
+Unfortunately, as the bottom panel of Fig.~\ref{fig:mimo_frf_uxuy} makes clear, there is a strong cross-coupling from the horizontal plane to the $Z$ axis (the coupling from $u_Z$ to the $X$ and $Y$ axes is very weak, and so is not shown).
+Our SISO control scheme does little to attenuate the resonances of $G_{Z,u_X}$ and $G_{Z,u_Y}$.
+In particular, there are modes in both these transfer functions at 215 and 505 Hz that do not appear in a SISO model of $G_{X,u_X}$ or $G_{Y,u_Y}$.
+
+For raster scans, the frequency content of the $X$-axis reference (which is a triangle wave) decays like $1/n^2$ with a gain proportional to the raster frequency.
+In contrast, the $X$-axis reference for a $\mu$-path scan is composed of a sequence of steps and ramps.
+The inclusion of the (discontinuous) steps means we should expect the $\mu$-path $X$ reference to decay like $1/n$.
+Thus,  while the cross-coupling can induce $Z$-axis vibrations for faster raster scans, it is especially problematic for $\mu$-path scanning.
+This is illustrated in the left column of Fig.~\ref{fig:with_ff}, which shows a CS cycle during which the $X$-axis makes a 5 micron move, which induces excessively large vibrations in the vertical control.
+
+In principle, one could mitigate these issues with a full MIMO control design. In this work, we opt for a much simpler feedforward scheme.
+For CS scanning, we insert feed-forward filters ($F_X$ and $F_Y$ in Fig.~\ref{fig:afm_bd_dinv}) with three notches: one at 215~Hz, one at 350~Hz and one at 505~Hz.
 We design a similar feed-forward filter for the $Y$-axis.
@@
 A similar affect could be achieve by using a simple low-pass filter.
-However, to achieve the same 40~dB of attenuation of the mode at 215 Hz, would require, e.g., that a two-pole LPF have its cut-off frequency at about 20~Hz.
-
-For raster scanning, we use a truncated Fourier series, where each Fourier coefficient is scaled by the inverse of the closed-loop FRF at the corresponding frequency.
-We truncate this series such that the highest frequency is smaller than 200 Hz.
+However, to achieve the same 40~dB of attenuation of the mode at 215 Hz, would require, e.g., that a two-pole low-pass filter have its cut-off frequency at about 20~Hz.
+Thus, while our feedforward scheme slows the $X$-axis down, we achieve better bandwidth than we would with a simple low-pass filter.
+
+For raster scanning, we set $F_X=F_Y=1$ and instead take advantage of the periodicity of the $X$-axis reference, which is a triangle wave.
+We modify the triangle wave to a truncated Fourier series, where each Fourier coefficient is scaled by the inverse of the closed-loop FRF at the corresponding frequency.
 See, e.g., \cite{clayton_review_2009} for more details on this strategy.
-Note that this scheme implies that the effective bandwidth of the $X$-axis controller is higher while raster scanning than while CS-scanning.
+We truncate this series such that the highest frequency is smaller than 200 Hz, which implies that we should never excite the problematic $G_{Z,u_X}$ modes.
+This scheme implies that the effective bandwidth of the $X$-axis controller is higher while raster scanning than while CS-scanning.
 On the other hand, it also implies that the for faster scan rates, fewer Fourier coefficients are used, and so the approximation to a triangle wave is worse.
@@
 \subsection{Limitations of SSIM and PSNR}\label{sec:limits}
-What kind of numbers are reasonable to expect from the SSIM and PSNR metrics?
-To answer this question, we compare a sequence of 1~Hz raster scans.
-In this experiment, (Fig. \ref{fig:rast_unaligned_1}) we took 6 raster scans of the same 5 by 5 micron
-square of the CS-20NG sample grating. These scans were taken sequentially and
-the NPXY100A remained in closed-loop throughout the process.
-Fig.~\ref{fig:rast_unaligned_1} shows the error between the master
-image and the remaining 6 images.
-Temporally, the images are order left-to-right and top-to-bottom.
-Thus we can see, both visually and via the metrics, that in Fig.~\ref{fig:rast_unaligned_1} the mis-alignment
-grows over time. 
-\todo{Should probably remove this entire section?}
-
-Taking the first scan as the master, we compute the PSNR and SSIM
-metrics. The best PSNR here is 16.57 and the worst is 9.02.
-The best SSIM is 0.54 and the worst is 0.28.
+The SSIM and PSNR have become reasonably popular in studies comparing simulated AFM image reconstructions \cite{oxvig_structure_2017, han_optimal_2018, Luo_nano_2015}.
+However, it remains somewhat of an open question how to best compare experimental AFM images.
+While we use the SSIM and PSNR in Section~\ref{sec:results}, we believe those numbers should be interpreted with some caution.
+In our experimental setup, actuation in the $XY$-plane happens via the nPoint piezo stage and the $XY$-direction of the original piezo scanner is uncontrolled.
+This leads to substantial drift between images.
+To illustrate this, we took a sequence of 6 raster scans of a sample grating, each at a 1~Hz scan rate over a 5 micron by 5 micron area.
+The top row of Fig.~\ref{fig:baseline_errors} shows the error between the first and second image and the first and 6th image.
+The PSNR and SSIM between images one and six are \baseline{one2twoNoAlgnPsnr} and \baseline{one2twoNoAlgnSsim}; between images one and six they are \baseline{one2sixNoAlgnPsnr} and \baseline{one2sixNoAlgnSsim}, respectively, even though on their own each image has good quality.
+
+To mitigate this affect, we use an image alignment technique based on the 2D cross-correlation between each image.
+Essentially, this takes a sub-slice of image 1 (here, a 25 pixel inset on each edge), and finds the offset in the other image that produces the smallest error.
+The result of this procedure are shown in the bottom row of Fig.~\ref{fig:baseline_errors}.
+% Taking the first scan as the master, we compute the PSNR and SSIM
+% metrics. The best PSNR here is 16.57 and the worst is 9.02.
+% The best SSIM is 0.54 and the worst is 0.28.
+Although the situation is improved compared to the un-aligned images, there is still noticeable stretching,
+particularly in the $Y$-direction.
+Notably, with the alignment technique,
+the SSIM is \baseline{one2twoAlgnSsim} for images one and two, and \baseline{one2sixAlgnSsim} for images one and six; the PSNR is \baseline{one2twoAlgnPsnr} and \baseline{one2sixAlgnPsnr} respectively.
 
@@
 
-Next, using a cross-correlation alignment technique
-% discussed in Section~\ref{sec:align},
-we aligned the master image with a sub-slice of each of
-the remaining 6 (the sub-slice removes 25 pixels from each side). Again, we
-computed the PSNR and SSIM. These results are shown in
-Fig.~\ref{fig:rast_aligned_1}, which again shows the errors between the
-aligned master and the remaining 6 images. Although the situation is improved
-compared to the un-aligned images, there is still noticeable stretching,
-particularly in the $Y$-direction. Notably, with the alignment technique,
-the SSIM lies between 0.7 and 0.73 and the PSNR ranges from 22.51 to 24.99 and appears more stable in time.
-% \section{Post-processing}\label{sec:post_process}
-% Here, we discuss how we post-process the raster and CS images.
-
-% \subsection{Aligning images via cross-correlation}\label{sec:align}
-% To get metrics that are meaningful in any sense, we need the master image and
-% the comparee to be aligned. We take two steps to help ensure this. First, during
-% each batch of images, the nPoint stage remains under closed loop control.
-% Between images, the FPGA control loop idles in state-0, as discussed above in
-% Section~\ref{sec:idle_0}. This was not necessary duing the initial
-% implementation because then, the nPoint stage was controlled by the nPoint PI
-% controller. While this helps things substantially, there is still an alignment
-% issue between subsequent images, which I believe stems from the original Agilent
-% piezo tube, which is a three axis tube. The $XY$-axes of the tube are
-% uncontrolled during imaging, and in fact, after a firmware ``upgrade'', the
-% option to close the $XY$-loop has been grayed out in the PicoView software.
-
-% To help deal with this, we compare sub-slices of the master image and the
-% comparee. The results in this chapter use a sub-image obtained by removing a
-% border of 25 pixels from each edge. Thus, for the purposes of comparison, the
-% original 512$\times$512 pixel image becomes a 462$\times$462 pixel image. Let
-% $X$ represent the original, master image and ${\tilde X=X_{25:-25, 25:-25}}$,
-% using Python notation. To find the correct subslice of the comparee, we use a
-% two dimensional cross-correlation, which is defined as
-% \begin{equation}
-%   Z_{k,\ell} = \sum_{m=0}^{M-1}\sum_{n=0}^{N-1} \tilde{X}_{m-k, n-\ell}Y_{m-k, n-\ell}.
-% \end{equation}
-% where $Y$ is the comparee.
-
-% The index of the maximum value of the matrix $Z$
-% \begin{equation}
-%   (i^*,j^*) = \textrm{arg~} \max_{i,j}Z_{i,j}
-% \end{equation}
-% corresponds to the lower left corner of the correct subslice. Thus, the
-% comparisons will computed against $\tilde{Y} = Y_{i^*:i^*+487, j^*:j^*+487}$.
-% For an example of this in action, see the Fig.~\ref{fig:baseline_errors} in the
-% next section.
-
-% Unfortunately, the mis-alignment is not simply constant offset, but rather
-% drifts over time. This can be seen, e.g., in Fig.~\ref{fig:rast_aligned_0p5}.
-% Thus, while the technique described here mitigates the issue, it does not fully
-% eliminate the problem.
-% =========================================================================
-
-% \subsection{A new metric}
+\subsection{A new metric}
 % \begin{figure}[t!]
@@
 \section{Experimental Results}\label{sec:results}
-We took scans of the CS-20NG sample grating over an area with holes on a 500 nm
-pitch. The holes are 20 nm deep.
-We scanned 5 micron by 5 micron images using standard raster scans with 512, 128 and 64 lines.
-The raster scans with 128 and 64 lines were binned horizontally to first produce 128 by 512 and 64 by 512 images.
-We then interpolated these images vertically to produce 512 by 512 pixel images.
-
+We compared $\mu$-path scanning to two scenarios. First, we compare it to full resolution raster scans at several scan rates. Second we compare to course raster scans.
+% For both comparisons, we use the same set of $\mu$-path scans.
+
+\subsection{Comparison to full raster}
+We took scans of a Ted Pella CS-20NG sample grating over an area with holes on a 500 nm
+pitch.
+The holes are 20 nm deep.
+We scanned 5 micron by 5 micron images using standard raster scans with 512 lines.
+For the raster scans, we took scans at 1.0~Hz, 2.5~Hz, 5.0~Hz, 8.0~Hz and 10~Hz.
 We also took $\mu$-path scans with densities at 12.5\%, 15\% and 25\% and reconstructed 512 by 512 pixel images. 
-For all CS scans, the $\mu$-paths are 500 nm long, as this allows us to work around the lack of a $Z$-axis sensor. This yields a $\mu$-path size of 52 pixels.
+The CS scans we taken with scan velocities equivalent to raster scan rates of 1.0~Hz,
+2.0~Hz, 5.0~Hz and 8.0~Hz. 
+For all CS scans, the $\mu$-paths are $\scanD{muLenNM}$ nm long, which translates to $\scanD{muLenPix}$ pixels.
 
 The free value of the deflections signal was approximately -0.6 volts and we set
-the scanning reference to ${\rzs=-0.3}$~volts and the withdraw reference to
-${\rzup=-0.8}$ volts. We set the $XY$-settle boundary to $\pm 0.05$
-microns and required 20 samples within this boundary before moving to the
-$Z$-engage state. The pre-scan length was 150 time steps.
-The cantilever was an AppNano SICON, with a
-length of 450 microns and spring constant $k\in[0.02,~0.8]$~N/m.
-
-% \todo{Should I scan even faster??}
-
-For the raster scans, we took scans at 1.0~Hz, 2.5~Hz, 5.0~Hz, 8.0~Hz and
-10~Hz.  The CS scans we taken with scan velocities equivalent to raster scans of 1.0~Hz,
-2.0~Hz, 5.0~Hz and 8.0~Hz with sampling densities of 10~\% and 15~\%.
-
+the scanning reference to ${\rzs=\scanD{spScan}}$~volts and the withdraw reference to
+${\rzup=\scanD{spMv}}$ volts. We set the $XY$-settle boundary to $\pm \scanD{xyBoundaryMic}$
+microns and required $\scanD{xySetSamps}$ samples within this boundary before moving to the
+$Z$-engage state. The pre-scan length was $\scanD{preScanSamples}$ time steps.
+The cantilever was an Budget Sensors ContAI-G, with a nominal
+length of 450 microns and spring constant of $k=0.2$~N/m.
+
+% \SSData{G2}$& $g_6 = \SSData{G6}
 The CS scans were reconstructed with BPVV. We set
-$\sigma = 0.1$, $\mu_f=1e-5$, $\alpha_v=0.75$ and $\alpha_h=0.0$. The data remained scaled in terms of volts.
+${\sigma = \scanD{sigma}}$, ${\mu_f=\scanD{muf}}$, ${\alpha_v=\scanD{alpv}}$ and ${\alpha_h=\scanD{alph}}$. The data remained scaled in terms of volts.
 
 For the raster scans, we discard data from the re-trace and divided the
-remaining data for each scan line 512 bins based on the \xc sensor
+remaining data for each scan line into 512 bins based on the \xc sensor
 measurements. We then average the data in each bin to obtain the value of one
@@
 The resulting images are shown in Fig.~\ref{fig:resultsF1_images}. The rows of
-pixels indicated by the red lines are shown Fig.~\ref{fig:pixel_rows}.
+pixels indicated by the red lines are shown as cross sections Fig.~\ref{fig:pixel_rows}.
 
@@
 \begin{figure*}
-  \includesvg[width=0.95\linewidth]{figures/cs_raster_images_6-5-2019.svg}
+  \centering
+  \includesvg[scale=.98]{figures/cs_raster_images_6-5-2019.svg}
   \caption{Raster and compressed sensing images of a 5 micron square area of the
@@
 % More importantly though, 
+\subsection{Comparison to Sub-line Sampling}
+Perhaps the simplest alternative to $\mu$-path sampling is to simply take a standard raster scan with fewer lines.
+This is the technique we consider in this subsection.
+Many of sub-line sampling papers assume that the lines to sample are selected randomly \cite{han_optimal_2018, Luo_nano_2015}.
+In contrast, we take an even simpler approach scan every 4th and every 8th line.
+This yields images with 128 and 64 lines respectively.
+For each of these scenarios, we first divide the data for each line into 512 bins.
+This gives an image that is 128 (resp., 64) pixels by 512 pixels.
+We then linearly interpolate along each column to produce a 512 by 512 pixel image.
+Again, we take these courser raster scans at 1.0, 5.0, 8.0 and 10.0 Hz.
+The resulting images are shown in Fig.
+XX.
 

### 2019-06-15 plot_baseline_raster_analysis_1Hz.m

@@ -41,7 +41,7 @@ raster_files = {...
 pixmaps = cell(length(raster_files), 1);
 for k=1:length(raster_files)
   raster_paths = get_raster_paths(dat_root, raster_files{k});
-  rast_exps{k} = RasterExp(raster_paths, 'reload_raw', true);
+  rast_exps{k} = RasterExp(raster_paths, 'reload_raw', false);
 end
 
 %%
@@ -70,7 +70,7 @@ for k=1:length(rast_exps)
 end
 
 for k=1:length(rast_exps)
-  %rast_exps{k}.save()
+  rast_exps{k}.save()
 end
 
 %%
@@ -86,18 +86,20 @@ modes = [false, true];
 F = mkfig(3000, 3.5, 3.5); clf
 [ha, pos] = tight_subplot(2, 2, [.02, .01 ], [.027, 0.055], .005);
 ha = reshape(ha', 2, [])';
-
+clc
+suffix = {'NoAlgn', 'Algn'}
+names = {'one2two', 'one2six'};
+ST = struct();
 for j=1:2
   mode = modes(j);
 
   thresh = (20/7)*(1/1000)*20;
   
-  fprintf('---------------------------------------------------\n');
-  titles = {'image 1 & 2', 'image 1 & 6'};
+  titles = {'image 1 \& 2', 'image 1 \& 6'};
   for k=1:2 
     imk = pixmats{k+1};
     imk = imk - mean(imk(:));
-    
+
     if mode == true
       imk_slice = imk(slice, slice);
       im1_ontok_fit = norm_align(imk_slice, im_master);
@@ -106,12 +108,18 @@ for j=1:2
       im1_ontok_fit = im_master;
     end
     [psn_1k, ssm_1k] = ssim_psnr_norm(im1_ontok_fit, imk_slice, 2*thresh);
+    name = [names{k}, suffix{j}]
+    psn_name = [name, 'Psnr'];
+    ssm_name = [name, 'Ssim'];
+    ST.(psn_name) = psn_1k;
+    ST.(ssm_name) = ssm_1k;
+    
     dmg = rast_exps{k+1}.damage_metric();
     mx = max(imk_slice(:));
     mn = min(imk_slice(:));
-    stit = titles{k}; %sprintf('PSNR=%.2f, SSIM=%.2f', psn_1k, ssm_1k);
+    stit = titles{k}; 
     
[…]

### 2019-06-17 latex/afm-cs-main.tex
Tweak figures. Tighten up prose.

@@
 \begin{document}
-\title{Improving the Image Acquisition Rate of an Atomic Force Microscope Through Compressive Sampling}
+\title{Improving the Image Acquisition Rate of an Atomic Force
+  Microscope Through Compressive Sampling}
 
 \author{Roger A. Braker, Yufan Luo, Lucy Y. Pao and Sean B. Andersson
-  \thanks{The authors are with the Dept. of Electrical, Computer, and Energy
-    Engineering at the University of Colorado, 425 UCB, Boulder, CO 80309,
-    United States. Phone: +1 (303) 492-2360. Fax: +1 (303) 492-2758. R. A.
-    Braker (corresponding author roger.braker@colorado.edu) is a graduate
-    student and L.Y. Pao (pao@colorado.edu) is the Richard \& Joy Dorf
-    Professor.} \thanks{This work was supported in part by the US National
-    Science Foundation (NSF Grant CMMI-1234980) and Agilent Technologies, Inc.}
-}
+  \thanks{The authors are with the Dept. of Electrical, Computer, and
+    Energy Engineering at the University of Colorado, 425 UCB,
+    Boulder, CO 80309, United States. Phone: +1 (303) 492-2360. Fax:
+    +1 (303) 492-2758. R. A. Braker (corresponding author
+    roger.braker@colorado.edu) is a graduate student and L.Y. Pao
+    (pao@colorado.edu) is the Richard \& Joy Dorf Professor.}
+  \thanks{This work was supported in part by the US National Science
+    Foundation (NSF Grant CMMI-1234980) and Agilent Technologies,
+    Inc.} }
 
@@
 \begin{abstract}
-  Undersampling-based approaches in Atomic Force Microscopy (AFM) aim to reduce
-  the time to acquire an image by reducing the number of measurements needed
-  while still maintaining image quality. In this paper, we describe a hardware
-  implementation and demonstration of one such approach based on the use of
-  collections of short scans known as $\mu$--paths. Using a commercial AFM, we
-  acquire data on a grating sample.
-  Reconstructions are made from these data using
-  %three approaches: (1) inpainting, an interpolation technique that
-  %diffuses information from sampled locations into unsampled regions, (2)
-  %basis-pursuit, a compressive sensing-based algorithm that seeks to minimize a
-  %measure of sparsity in the underlying image, and (3)
-  a new variant of basis
-  pursuit, Basis Pursuit with Vertical Variation (BPVV), that is designed to reduce
-  artifacts arising from the sampling pattern. The quality of the resulting
-  images is compared to images from standard raster scans of the same regions at
-  comparable imaging rates using both the peak signal-to-noise ratio and the
-  structured similarity index metric
-  and a new metric we call the relative damage index.
-  \todo{Re-write abstract, especially conclusions}
-  These experiments demonstrate that at slow
-  scan rates, the $\mu-$path scheme produces similar image quality with
-  significantly less sampling (and thus less tip-sample interaction) and that at
-  high rates, the undersampling scheme produces higher quality images than
-  raster scanning.
+  Undersampling-based approaches in Atomic Force Microscopy (AFM) aim
+  to reduce the time to acquire an image by reducing the number of
+  measurements needed while still maintaining image quality. In this
+  paper, we describe a hardware implementation and demonstration of
+  one such approach based on the use of collections of short scans
+  known as $\mu$--paths. Using a commercial AFM, we acquire data on a
+  grating sample. Reconstructions are made from these data using
+  % three approaches: (1) inpainting, an interpolation technique that
+  % diffuses information from sampled locations into unsampled
+  % regions, (2)
+  % basis-pursuit, a compressive sensing-based algorithm that seeks to
+  % minimize a
+  % measure of sparsity in the underlying image, and (3)
+  a new variant of basis pursuit, Basis Pursuit with Vertical
+  Variation (BPVV), that is designed to reduce artifacts arising from
+  the sampling pattern. The quality of the resulting images is
+  compared to images from standard raster scans of the same regions at
+  comparable imaging rates using both the peak signal-to-noise ratio
+  and the structured similarity index metric and a new metric we call
+  the relative damage index. \todo{Re-write abstract, especially
+    conclusions} These experiments demonstrate that at slow scan
+  rates, the $\mu-$path scheme produces similar image quality with
+  significantly less sampling (and thus less tip-sample interaction)
+  and that at high rates, the undersampling scheme produces higher
+  quality images than raster scanning.
 \end{abstract}
@@
 
-The Atomic Force Microscope (AFM) is a powerful instrument capable of imaging
-sample surface topography, material characteristics, and other surface
-properties, with nanometer scale precision. AFMs acquire information about the sample by monitoring the deflection of the cantilever caused by the tip-sample interaction force. In general, 
-%AFMs acquire information about the sample
-%through a variety of imaging modes, all of which rely on the deflection of the
-%cantilever caused by the tip-sample interaction force. While the details of each
-%of the modes are quite different, in general, 
-feedback control is used to hold
-the deflection signal constant and information about the property of interest is
-inferred from the applied control or the measured dynamics of the cantilever
-\cite{Abramovitch:2007gt}. Because of its versatility, spatial resolution, and
-ability to image in vacuum, air, and liquid, AFM is widely used in a variety of
-disciplines, including physics, biology and materials science
+The Atomic Force Microscope (AFM) is a powerful instrument capable of
+imaging sample surface topography, material characteristics, and other
+surface properties, with nanometer scale precision. AFMs acquire
+information about the sample by monitoring the deflection of the
+cantilever caused by the tip-sample interaction force. In general,
+% AFMs acquire information about the sample through a variety of
+% imaging modes, all of which rely on the deflection of the cantilever
+% caused by the tip-sample interaction force. While the details of
+% each of the modes are quite different, in general,
+feedback control is used to hold the deflection signal constant and
+information about the property of interest is inferred from the
+applied control or the measured dynamics of the cantilever
+\cite{Abramovitch:2007gt}. Because of its versatility, spatial
+resolution, and ability to image in vacuum, air, and liquid, AFM is
+widely used in a variety of disciplines, including physics, biology
+and materials science
 \cite{Dufrene:2017gm,Yang:2017im,Payton:2016hj,Altman:2015ic,Haase:2015eh}
 
-In addition to imaging static samples, AFM is used to
-study dynamics in systems with nanometer-scale features
-\cite{Yang:2017im,Shibata:2017da,Shibata:2015jd,Ando:2014ja}. The image
-acquisition time of conventional AFMs, however, is typically on the order of
-seconds to minutes, severely limiting the time-scales that can be explored.
-Driven by the need for faster imaging, there continue to be many active research
-efforts to overcome this challenge. Since an AFM is fundamentally a mechanical
-microscope, many of the approaches to high-speed AFM (HS-AFM) have focused on
-modifications to the physical components. These have included the use of small,
-fast cantilevers \cite{viani1999fast, braunsmann2010high,Adams:2016hg}, the
-development of faster actuators \cite{Maroufi:2015gt,Yong:2012kd,Kenton:2012cm},
-as well as the application of advanced controllers
-\cite{Rana:2018es,Yong:2015gr,butterworth2010adaptive,salapaka2002high}. By
-combining different techniques, there are current generation, high-end
-instruments that can image at rates on the order of 1-10 frames/sec
-\cite{Ando:2014ja}. However, the fastest rates are achieved only over small scan
-ranges and there remain many systems of interest whose dynamics are faster even
-than these instruments can achieve. In addition, there is a large installed base
-of much slower AFMs that can benefit from alternative approaches to improving
-imaging rate.
-
-A complimentary class of HS-AFM approaches considers modifications to the
-sampling scheme rather than the system mechanics. Alternative scan trajectories
-like spirals, cycloids, and Lissajous figures, have been used in place of the
-standard raster scan. These trajectories are easier for the actuators to follow,
-allowing the tip to be moved more quickly and leading to faster image
-acquisition on an otherwise unmodified instrument
-\cite{Bazaei:2017dm,Wu:2015dt,Rana:2014bj,Tuma:2012hv,Yong:2010gm}. Such
-approaches are ultimately limited by the vertical bandwidth of the instrument
-for regulating the deflection signal \cite{Teo:2016ev}. Related to these are
-local scanning methods that use the measurements in real-time to steer the tip
-to focus the scan on features of interest, reducing imaging time by reducing the
-amount of sampling needed
-\cite{Hartman:2018ja,Wen:2018fl,Zhang:2015cf,Huang:2014dw}. While these have
-been shown to yield an order of magnitude or better improvement in imaging rate,
-they are limited in the class of samples that can be imaged.
+In addition to imaging static samples, AFM is used to study dynamics
+in systems with nanometer-scale features
+\cite{Yang:2017im,Shibata:2017da,Shibata:2015jd,Ando:2014ja}. The
+image acquisition time of conventional AFMs, however, is typically on
+the order of seconds to minutes, severely limiting the time-scales
+that can be explored. Driven by the need for faster imaging, there
+continue to be many active research efforts to overcome this
+challenge. Since an AFM is fundamentally a mechanical microscope, many
+of the approaches to high-speed AFM (HS-AFM) have focused on
+modifications to the physical components. These have included the use
+of small, fast cantilevers \cite{viani1999fast,
+  braunsmann2010high,Adams:2016hg}, the development of faster
+actuators \cite{Maroufi:2015gt,Yong:2012kd,Kenton:2012cm}, as well as
+the application of advanced controllers
+\cite{Rana:2018es,Yong:2015gr,butterworth2010adaptive,salapaka2002high}.
+By combining different techniques, there are current generation,
+high-end instruments that can image at rates on the order of 1-10
+frames/sec \cite{Ando:2014ja}. However, the fastest rates are achieved
+only over small scan ranges and there remain many systems of interest
+whose dynamics are faster even than these instruments can achieve. In
+addition, there is a large installed base of much slower AFMs that can
+benefit from alternative approaches to improving imaging rate.
+
+A complimentary class of HS-AFM approaches considers modifications to
+the sampling scheme rather than the system mechanics. Alternative scan
+trajectories like spirals, cycloids, and Lissajous figures, have been
+used in place of the standard raster scan. These trajectories are
+easier for the actuators to follow, allowing the tip to be moved more
+quickly and leading to faster image acquisition on an otherwise
+unmodified instrument
+\cite{Bazaei:2017dm,Wu:2015dt,Rana:2014bj,Tuma:2012hv,Yong:2010gm}.
+Such approaches are ultimately limited by the vertical bandwidth of
+the instrument for regulating the deflection signal \cite{Teo:2016ev}.
+Related to these are local scanning methods that use the measurements
+in real-time to steer the tip to focus the scan on features of
+interest, reducing imaging time by reducing the amount of sampling
+needed \cite{Hartman:2018ja,Wen:2018fl,Zhang:2015cf,Huang:2014dw}.
+While these have been shown to yield an order of magnitude or better
+improvement in imaging rate, they are limited in the class of samples
+that can be imaged.
 
 An alternative group of non-raster scanning schemes, introduced in
-\cite{song2011video,andersson2012non}, is based on the idea of undersampling. As
-with local scanning, data acquisition time is reduced by reducing the amount of
-measurements acquired. Unlike local scanning methods, this approach still
-presents the full image. Taking advantage of the redundancy in many natural
-signals of interest, the final surface image can be recovered from the limited
-number of measured pixels using a variety of different reconstruction methods
-such as inpainting or schemes based on the theory of compressive sensing (CS)
-\cite{chen2013enhancement,luo2015comparison}. In addition to the reduced imaging
-time, undersampling schemes also reduce tip-sample interactions, thereby
-reducing the likelihood of tip wear or sample damage.
-
-One simple way to create undersampling schemes is by modifying existing full
-scan patterns including raster, spiral, and Lissajous scanning. For example,
-subline sampling is generated by randomly skipping some of the horizontal lines
-in raster scanning \cite{han2018reconstruction,chen2013enhancement}. For spiral
-and Lissajous patterns, the scan parameters (frequency and amplitude) can be
-selected to ensure the trajectory only passes through a desired fraction of the
-pixels in the final image. The scanning time for these smooth undersampling
-patterns can be estimated based on the proportion of the pixels in the
-trajectory. However, results in the literature of CS make clear that
-\textit{randomness} in the sampling pattern is essential for creating good
-reconstructions in the general case. The smooth nature of these patterns reduces
-their randomness and thus leads to less accurate reconstructions than a
-completely random sampling of the pixels for the same sampling fraction.
-
-In AFM, implementing a truly random pattern requires that the tip be engaged
-with the surface to collect a measurement, lifted and moved to the new location,
-and engaged again. Because the re-engagement process is typically slow, this can
-lead to excessively long image acquisition times and negate the gains from
-undersampling \cite{andersson2012non}. One discrete undersampling scheme, called
-a $\mu$-path pattern, was proposed in \cite{maxwell2014compressed} to improve
-sampling efficiency. The $\mu$-path pattern consists of randomly placed short,
-horizontal scans (see Fig.~\ref{fig:mu_mask} for one such pattern) and is
-designed to balance the randomness needed to ensure good reconstruction with
-continuous scanning to reduce the number of tip
+\cite{song2011video,andersson2012non}, is based on the idea of
+undersampling. As with local scanning, data acquisition time is
+reduced by reducing the amount of measurements acquired. Unlike local
+scanning methods, this approach still presents the full image. Taking
+advantage of the redundancy in many natural signals of interest, the
+final surface image can be recovered from the limited number of
+measured pixels using a variety of different reconstruction methods
+such as inpainting or schemes based on the theory of compressive
+sensing (CS) \cite{chen2013enhancement,luo2015comparison}. In addition
+to the reduced imaging time, undersampling schemes also reduce
+tip-sample interactions, thereby reducing the likelihood of tip wear
+or sample damage.
+
+One simple way to create undersampling schemes is by modifying
+existing full scan patterns including raster, spiral, and Lissajous
+scanning. For example, subline sampling is generated by randomly
+skipping some of the horizontal lines in raster scanning
+\cite{han2018reconstruction,chen2013enhancement}. For spiral and
+Lissajous patterns, the scan parameters (frequency and amplitude) can
+be selected to ensure the trajectory only passes through a desired
+fraction of the pixels in the final image. The scanning time for these
+smooth undersampling patterns can be estimated based on the proportion
+of the pixels in the trajectory. However, results in the literature of
+CS make clear that \textit{randomness} in the sampling pattern is
+essential for creating good reconstructions in the general case. The
+smooth nature of these patterns reduces their randomness and thus
+leads to less accurate reconstructions than a completely random
+sampling of the pixels for the same sampling fraction.
+
+In AFM, implementing a truly random pattern requires that the tip be
+engaged with the surface to collect a measurement, lifted and moved to
+the new location, and engaged again. Because the re-engagement process
+is typically slow, this can lead to excessively long image acquisition
+times and negate the gains from undersampling \cite{andersson2012non}.
+One discrete undersampling scheme, called a $\mu$-path pattern, was
+proposed in \cite{maxwell2014compressed} to improve sampling
+efficiency. The $\mu$-path pattern consists of randomly placed short,
+horizontal scans (see Fig.~\ref{fig:mu_mask} for one such pattern) and
+is designed to balance the randomness needed to ensure good
+reconstruction with continuous scanning to reduce the number of tip
 engagements. %Though the pattern is motivated from CS, it also works well in practice for inpainting reconstruction \cite{luo2015comparison}.
@@
 
-Our previous work on the $\mu$-path pattern using theoretical calculations,
-simulations, and a preliminary implementation, demonstrates that the approach
-can achieve significant scanning time reduction while maintaining faithful image
-reconstruction \cite{maxwell2014compressed,Luo:2015tu, braker_hardware_2018}. This paper
-builds upon that earlier work in several significant ways.
-
-\textbf{Contributions}
-Much of the prior work on undersampled AFM images is based purely on simulations \cite{han_optimal_2018, Luo_nano_2015, oxvig_structure_2017, jensen_reconstruction_2013, maxwell_acc_2014, Chen_2012jx}.
+Our previous work on the $\mu$-path pattern using theoretical
+calculations, simulations, and a preliminary implementation,
+demonstrates that the approach can achieve significant scanning time
+reduction while maintaining faithful image reconstruction
+\cite{maxwell2014compressed,Luo:2015tu, braker_hardware_2018}. This
+paper builds upon that earlier work in several significant ways.
+
+\textbf{Contributions} Much of the prior work on undersampled AFM
+images is based purely on simulations \cite{han_optimal_2018,
+  Luo_nano_2015, oxvig_structure_2017, jensen_reconstruction_2013,
+  maxwell_acc_2014, Chen_2012jx}.
 
 % % ------------------ TKTKTKT ------------------
-% \todo{Strike this?}
-% First, we demonstrate
-% performance using both randomly-placed $\mu-$paths and designed $\mu-$paths that
-% are optimized to minimize the expected reconstruction error given some initial
-% estimate of the frequency structure of the sample. These schemes are described
-% in Sec. \ref{sec:samplingScheme}.
+% \todo{Strike this?} First, we demonstrate performance using both
+% randomly-placed $\mu-$paths and designed $\mu-$paths that are
+% optimized to minimize the expected reconstruction error given some
+% initial estimate of the frequency structure of the sample. These
+% schemes are described in Sec. \ref{sec:samplingScheme}.
 % % --------------------------
-We also introduce a new reconstruction
-algorithm which is designed to minimize the artifacts arising from the structure
-of the $\mu$-path scanning pattern. This algorithm is described and compared to
-existing reconstruction methods through simulations in Sec.
-\ref{sec:reconstructionMethods}.
-Section \ref{sec:control} describes improvements to the control algorithms compared to our preliminary implementation in ~\cite{braker_hardware_2018}.
-We then demonstrate the entire scheme from
-sampling through reconstruction using experiments on a commercial AFM (Agilent
-5500). The experimental setup and implementation details are described in Secs.
-\ref{sec:experimentalSetup} and \ref{sec:implementation}\footnote{The software
-  portion of the implementation and image reconstruction described in this paper
-  can be found at \url{https://github.com/rabraker/AFM_CS}}. Experimental results are provided in Sec.
-\ref{sec:results}. Finally, we provide a few concluding remarks in
-Sec. \ref{sec:conclusions}.
+We also introduce a new reconstruction algorithm which is designed to
+minimize the artifacts arising from the structure of the $\mu$-path
+scanning pattern. This algorithm is described and compared to existing
+reconstruction methods through simulations in Sec.
+\ref{sec:reconstructionMethods}. Section \ref{sec:control} describes
+improvements to the control algorithms compared to our preliminary
+implementation in ~\cite{braker_hardware_2018}. We then demonstrate
+the entire scheme from sampling through reconstruction using
+experiments on a commercial AFM (Agilent 5500). The experimental setup
+and implementation details are described in Secs.
+\ref{sec:experimentalSetup} and \ref{sec:implementation}\footnote{The
+  software portion of the implementation and image reconstruction
+  described in this paper can be found at
+  \url{https://github.com/rabraker/AFM_CS}}. Experimental results are
+provided in Sec. \ref{sec:results}. Finally, we provide a few
+concluding remarks in Sec. \ref{sec:conclusions}.
 
@@
   \includegraphics[width=0.7\columnwidth]{figures-SBA/random_mask.pdf}
-  \caption{An example of the horizontal $\mu$-path sampling pattern for a 256$\times$256 pixel image with 35 pixels in each short scan and a total of 20\% pixels scanned.}
+  \caption{An example of the horizontal $\mu$-path sampling pattern
+    for a 256$\times$256 pixel image with 35 pixels in each short scan
+    and a total of 20\% pixels scanned.}
   \label{fig:mu_mask}
@@
 \label{sec:reconstructionMethods}
-Compressive sensing (CS) is a signal processing technique which aims at signal reconstruction from a
-relatively small (sub-Nyquist limit) number of measurements
-\cite{carmi2014compressive}. It takes advantage of the approximate sparsity of
-real-world signals, that is, that many coefficients of such signals
-are close to zero when represented in an appropriate basis. CS methods seek the
-true image signal $x\in\mathbb{R}^n$ from the observation equation,
+Compressive sensing (CS) is a signal processing technique which aims
+at signal reconstruction from a relatively small (sub-Nyquist limit)
+number of measurements \cite{carmi2014compressive}. It takes advantage
+of the approximate sparsity of real-world signals, that is, that many
+coefficients of such signals are close to zero when represented in an
+appropriate basis. CS methods seek the true image signal
+$x\in\mathbb{R}^n$ from the observation equation,
 \begin{equation}\label{op:observation}
@@
 \end{equation}
-\noindent where $y\in\mathbb{R}^m$ is the observation vector, $R$ is an
-$n\times m$ matrix defining the measurements, $U$ is an $m\times m$ sparsity
-basis and $\eta$ is the sparse representation of $x$ in the domain of $U$. In
-general, $n\ll m$. In an imaging application, where the underlying signal is a
-matrix $X\in\mathbb{R}^{h\times s}$, we take $x=\text{vec}(X)$, where the
-$\text{vec}(\cdot)$ operator stacks the columns of a matrix.
-
-In the AFM application, the probe can only measure a single pixel at a time.
-Thus the rows of $R$ are a subset of the rows of an $m$ by $m$ identity matrix.
-Ideally, the sparsity basis and
-the measurement matrix $R$ will have a low \textit{mutual coherence}, a
-measure that describes how each of the rows of $R$ (the measurements)
-``spreads out'' in the domain of $U$ \cite{candes2007sparsity}.
-In the following, we assume that $U^TU=I$, though in the simulation and
-experimental results, we take $U^T$ as the Discrete Cosine Transform (DCT).
-The DCT basis generally keeps a good balance between achieving a low
-mutual coherence between $U$ and the $\mu$-path sensing
-matrices $R$ and providing a high sparsity for typical AFM sample images.
-
-Basis pursuit with denoising (BPDN) is one common realization of the CS-based
-reconstruction problem, and is given by the optimization
+\noindent where $y\in\mathbb{R}^m$ is the observation vector, $R$ is
+an $n\times m$ matrix defining the measurements, $U$ is an $m\times m$
+sparsity basis and $\eta$ is the sparse representation of $x$ in the
+domain of $U$. In general, $n\ll m$. In an imaging application, where
+the underlying signal is a matrix $X\in\mathbb{R}^{h\times s}$, we
+take $x=\text{vec}(X)$, where the $\text{vec}(\cdot)$ operator stacks
+the columns of a matrix.
+
+In the AFM application, the probe can only measure a single pixel at a
+time. Thus the rows of $R$ are a subset of the rows of an $m$ by $m$
+identity matrix. Ideally, the sparsity basis and the measurement
+matrix $R$ will have a low \textit{mutual coherence}, a measure that
+describes how each of the rows of $R$ (the measurements) ``spreads
+out'' in the domain of $U$ \cite{candes2007sparsity}. In the
+following, we assume that $U^TU=I$, though in the simulation and
+experimental results, we take $U^T$ as the Discrete Cosine Transform
+(DCT). The DCT basis generally keeps a good balance between achieving
+a low mutual coherence between $U$ and the $\mu$-path sensing matrices
+$R$ and providing a high sparsity for typical AFM sample images.
+
+Basis pursuit with denoising (BPDN) is one common realization of the
+CS-based reconstruction problem, and is given by the optimization
 \begin{equation}
@@
 where $\sigma$ represents uncertainty in the measurements. BPDN
-essentially searches for the sparsest signal from all
-the candidates that match the measurements.
-
-Although BPDN is effective in the general setting, using it for reconstruction
-from horizontal $\mu$-path samples often yields artifacts in the vertical
-direction (that is, the direction orthogonal to the $\mu$-path scans) leading to
-strong discontinuities in the image. These artifacts grow more prominent as the
-length of the $\mu$-paths is increased \cite{maxwell2014compressed}, because these
-longer paths lead to increased mutual coherence between the measurement matrix
-$R$ and the sparsity basis $U$. However, longer $\mu$-paths means fewer
-$\mu$-paths and thus shorter scan times.
+essentially searches for the sparsest signal from all the candidates
+that match the measurements.
+
+Although BPDN is effective in the general setting, using it for
+reconstruction from horizontal $\mu$-path samples often yields
+artifacts in the vertical direction (that is, the direction orthogonal
+to the $\mu$-path scans) leading to strong discontinuities in the
+image. These artifacts grow more prominent as the length of the
+$\mu$-paths is increased \cite{maxwell2014compressed}, because these
+longer paths lead to increased mutual coherence between the
+measurement matrix $R$ and the sparsity basis $U$. However, longer
+$\mu$-paths means fewer $\mu$-paths and thus shorter scan times.
 \noindent
@@
     % 
-    % ------------------------------ Row  2 --------------------------------------------
+                                                                          % ------------------------------
+                                                                          % Row
+                                                                          % 2
+                                                                          % --------------------------------------------
     \includesvg[width=0.16\textwidth]{figures/dna_og.svg}
@@
   \end{tabular}
-  \caption{Reconstruction comparison between BPDN and BPVV. (first column)
-    Original raster-scanned image. (second column) BPDN reconstruction from
-    random, 40 pixel long $\mu$-paths with 25\% sampling. (third column) BPVV
-    reconstruction from the same sub-sampled data. (remaining columns)
-    Corresponding details from the red boxes indicated in the raster image. The
-    results show that BPVV reduces the artifacts arising from the horizontal
-    scans of the $\mu$-path pattern that appear in BPDN reconstructions.}
+  \caption{Reconstruction comparison between BPDN and BPVV. (first
+    column) Original raster-scanned image. (second column) BPDN
+    reconstruction from random, 40 pixel long $\mu$-paths with 25\%
+    sampling. (third column) BPVV reconstruction from the same
+    sub-sampled data. (remaining columns) Corresponding details from
+    the red boxes indicated in the raster image. The results show that
+    BPVV reduces the artifacts arising from the horizontal scans of
+    the $\mu$-path pattern that appear in BPDN reconstructions.}
   \label{fig:BPTV_demonstration}
@@
 
-To mitigate these affects, we propose a new variant of BPDN that we term basis pursuit with
-vertical variation (BPVV). BPVV adds a vertical total variation penalty in the spatial domain to the
-optimization objective. That is, \eqref{op:bp} is modified to
-\todo{It has been my observation that some benefit is gained by including $D_h$, but weighting it less than $D_v$. Not sure if we should leave it in. If so, BPVV should be BPTV or something.}
+To mitigate these affects, we propose a new variant of BPDN that we
+term basis pursuit with vertical variation (BPVV). BPVV adds a
+vertical total variation penalty in the spatial domain to the
+optimization objective. That is, \eqref{op:bp} is modified to \todo{It
+  has been my observation that some benefit is gained by including
+  $D_h$, but weighting it less than $D_v$. Not sure if we should leave
+  it in. If so, BPVV should be BPTV or something.}
 \begin{align}
@@
                        &=\min_{x\in Q_p} \left\|W^Tx\right\|_1 \label{op:bp_tvW}
-                         % \quad W = \begin{bmatrix}U&\alpha_hD^T_h&\alpha_vD^T_v \end{bmatrix}^T \nonumber
+                       % \quad W
+                       % = \begin{bmatrix}U&\alpha_hD^T_h&\alpha_vD^T_v \end{bmatrix}^T
+                       % \nonumber
 \end{align}
@@
 \end{equation*}
-with ${D_v x=\text{vec}(\nabla_v X)}$ (resp., ${D_v x=\text{vec}(\nabla_v X)}$) representing a 
-discrete gradient of a matrix in the vertical (resp., horizontal) direction (see, e.g., \cite[Section 6.1,]{becker_nesta_2011}). 
+with ${D_v x=\text{vec}(\nabla_v X)}$ (resp.,
+${D_v x=\text{vec}(\nabla_v X)}$) representing a discrete gradient of
+a matrix in the vertical (resp., horizontal) direction (see, e.g.,
+\cite[Section 6.1,]{becker_nesta_2011}).
 % and
@@
 % \end{align*}
-Thus, in \eqref{op:bp_tv}, $\left \| D_v x \right \|_1$ (resp., $\left \| D_h x \right \|_1$) is the total variation (TV) of the signal in the vertical (resp., horizontal) direction.
-The parameters $\alpha$ and $\beta$ are weighting parameters.
-The description of BPVV in \eqref{op:bp_tvW} can be interpreted as changing our assumption of sparsity in the DCT basis to assuming sparsity in an overcomplete dictionary \cite{candes_redundant_2011}.
-\todo{I believe this is correct: Sean/Yufan can you confirm or reject?}
-When written as \eqref{op:bp_tvW}, the problem is in a form that may be solved with NESTA~\cite{becker_nesta_2011}.
-
-% For completeness, we give an overview here.
-% To that end, we re-write the cost $f(x)$ in \eqref{op:bp_tvW} as
+Thus, in \eqref{op:bp_tv}, $\left \| D_v x \right \|_1$ (resp.,
+$\left \| D_h x \right \|_1$) is the total variation (TV) of the
+signal in the vertical (resp., horizontal) direction. The parameters
+$\alpha$ and $\beta$ are weighting parameters. The description of BPVV
+in \eqref{op:bp_tvW} can be interpreted as changing our assumption of
+sparsity in the DCT basis to assuming sparsity in an overcomplete
+dictionary \cite{candes_redundant_2011}. \todo{I believe this is
+  correct: Sean/Yufan can you confirm or reject?} When written as
+\eqref{op:bp_tvW}, the problem is in a form that may be solved with
+NESTA~\cite{becker_nesta_2011}.
+
+% For completeness, we give an overview here. To that end, we re-write
+% the cost $f(x)$ in \eqref{op:bp_tvW} as
 % \begin{equation*}
@@
 
-% One of the core features of the NESTA algorithm is to replace the non-smooth functional $f(x)$ with a smoothed approximation
+% One of the core features of the NESTA algorithm is to replace the
+% non-smooth functional $f(x)$ with a smoothed approximation
 % \begin{equation}
@@
 % \end{equation*}
-% The optimization \eqref{op:bp_tv} may now be solved using Algorithm~\ref{ag:NESTA}.
+% The optimization \eqref{op:bp_tv} may now be solved using
+% Algorithm~\ref{ag:NESTA}.
 
@@
 
-%   \Initialize{$x \in Q_p, \mu=0.9||W^T x_0||_{\infty}$, $L_{\mu} = \frac{1}{\mu}||W||^2_2$}
+%   \Initialize{$x \in Q_p, \mu=0.9||W^T x_0||_{\infty}$,
+%   $L_{\mu} = \frac{1}{\mu}||W||^2_2$}
 %     %   $x^{k+1} = x^{k}$\\
@@
 %   \frac{L_{\mu}}{2}||x - x_k||_2^2 + \langle \nabla f(x_k),~ x\rangle$\\
-%         $\displaystyle {z_k = \text{arg } \min_{x\in Q_p} \frac{L_{\mu}}{2}||x-x_0||_2^2 +
+%   $\displaystyle {z_k = \text{arg } \min_{x\in Q_p}
+%   \frac{L_{\mu}}{2}||x-x_0||_2^2 +
 %   \langle \sum_{i=0}^k \alpha_i \nabla f(x_i), ~x \rangle}$\\
@@
 %   $\mu = \gamma \mu$\\
-%       $L_{\mu} = (1/\mu)||W||^2_2$
-%     }
-%   \Output{Reconstruction $x_k$}
+%   $L_{\mu} = (1/\mu)||W||^2_2$ } \Output{Reconstruction $x_k$}
 %   \caption{NESTA algorithm}
@@
 % \end{algorithm}
-%   \todo{seems like a waste of space to reprint the algo, since its really no different than the reference}
-
-% In the termination condition for the inner loop, $\Delta f_{\mu} = |f_{\mu}(x_k) - \bar{f}_{\mu}(x_k)|/\bar{f}_{\mu}(x_k)$ where
+% \todo{seems like a waste of space to reprint the algo, since its
+% really no different than the reference}
+
+% In the termination condition for the inner loop,
+% $\Delta f_{\mu} = |f_{\mu}(x_k) -
+% \bar{f}_{\mu}(x_k)|/\bar{f}_{\mu}(x_k)$ where
 % \begin{equation}
@@
 % \end{equation}
-% When $RR^T=I$, the sub-problems in lines 6 and 7 have a closed-form solution. Details can be found in~\cite{becker_nesta_2011}.
+% When $RR^T=I$, the sub-problems in lines 6 and 7 have a closed-form
+% solution. Details can be found in~\cite{becker_nesta_2011}.
 
@@
 % % \begin{equation}
-% %   p = \textrm{arg } \min_{x\in Q_p} \frac{L}{2}||x - r|| + \langle g,~x - r\rangle
+% %   p = \textrm{arg } \min_{x\in Q_p} \frac{L}{2}||x - r|| + \langle
+% %   g,~x - r\rangle
 % % \end{equation}
-% % for some vectors $g$ and $r$ and, as shown in~\cite{becker_nesta_2011}, have a closed-form solution given by
+% % for some vectors $g$ and $r$ and, as shown
+% % in~\cite{becker_nesta_2011}, have a closed-form solution given by
 % % \begin{align}
-% %   \lambda & = \textrm{max}(0, \sigma^{-1}\left| b - Rq\right| - L\\
+% %   \lambda & = \textrm{max}(0, \sigma^{-1}\left| b -
+% %     Rq\right| - L\\
 % %   q &= r - L^{-1}g\\
-% %   p &= \left(I - \frac{\lambda}{\lambda + L} R^TR\right)\left( \frac{\lambda}{L}R^Tb + q\right).
+% %   p &= \left(I - \frac{\lambda}{\lambda + L}
+% %     R^TR\right)\left( \frac{\lambda}{L}R^Tb + q\right).
 % % \end{align}
@@
 A simulation comparison between BPDN and BPVV is shown in
-Fig.~\ref{fig:BPTV_demonstration}.
-The first column shows two raster scans: the top is 512 by 512 pixel image of a CS20NG grating acquired with an Agilent 5400 AFM and the bottom is a 256 by 256 pixel image of DNA acquired with an Agilent 5500 AFM.
-For the CS20NG grating, we sampled 15\% of the pixels with 50 pixel $\mu$-paths.
-We sampled 25\% of the DNA image with 25 pixel long $\mu$-paths.
-The second columns shows the full frame reconstructions using BPDN and the third columns shows the result using BPVV.
-The fourth column zooms in on the region indicated by the red box in column one.
-Similarly, the fifth and six columns show the detail of the reconstructions.
-The reconstruction results show the artifacts apparent in the BPDN reconstruction are largely
-mitigated using BPVV.
-Thus, in the remainder of the paper, we focus exclusively on BPVV.
-As for reconstruction time, it took about 1.5 seconds to reconstruct the DNA image and about 7 seconds for the CS20NG.
+Fig.~\ref{fig:BPTV_demonstration}. The first column shows two raster
+scans: the top is 512 by 512 pixel image of a CS20NG grating acquired
+with an Agilent 5400 AFM and the bottom is a 256 by 256 pixel image of
+DNA acquired with an Agilent 5500 AFM. For the CS20NG grating, we
+sampled 15\% of the pixels with 50 pixel $\mu$-paths. We sampled 25\%
+of the DNA image with 25 pixel long $\mu$-paths. The second columns
+shows the full frame reconstructions using BPDN and the third columns
+shows the result using BPVV. The fourth column zooms in on the region
+indicated by the red box in column one. Similarly, the fifth and six
+columns show the detail of the reconstructions. The reconstruction
+results show the artifacts apparent in the BPDN reconstruction are
+largely mitigated using BPVV. Thus, in the remainder of the paper, we
+focus exclusively on BPVV. As for reconstruction time, it took about
+1.5 seconds to reconstruct the DNA image and about 7 seconds for the
+CS20NG.
 
@@
 
-Through a breakout box, the Agilent 5400 provides access to the $Z$-axis deflection signal.
-When the Agilent software is set to open-loop mode, a $\pm10$~volt input on the standard control box allows control of the $Z$-axis of the N9524a piezo scanner, which has a total range of 7 $\mu$m.
-Initial (course) engagement of the tip to the
-sample is performed using the PicoView software before control is handed over to
-the custom controllers.
-
-All control logic is programmed using LabVIEW 2019 and compiled to a Xilinx
-Spartan-6 LX150 Field Programmable Gate Array (FPGA) inside the cRIO-9082. The
-cRIO includes a 16-Bit, 100 kHz NI-9215 analog-to-digital input module and a
-16-Bit, 100 kHz NI-9263 digital-to-analog output module. All control loops are
-implemented using a 25 kHz sampling rate.
+Through a breakout box, the Agilent 5400 provides access to the
+$Z$-axis deflection signal. When the Agilent software is set to
+open-loop mode, a $\pm10$~volt input on the standard control box
+allows control of the $Z$-axis of the N9524a piezo scanner, which has
+a total range of 7 $\mu$m. Initial (course) engagement of the tip to
+the sample is performed using the PicoView software before control is
+handed over to the custom controllers.
+
+All control logic is programmed using LabVIEW 2019 and compiled to a
+Xilinx Spartan-6 LX150 Field Programmable Gate Array (FPGA) inside the
+cRIO-9082. The cRIO includes a 16-Bit, 100 kHz NI-9215
+analog-to-digital input module and a 16-Bit, 100 kHz NI-9263
+digital-to-analog output module. All control loops are implemented
+using a 25 kHz sampling rate.
 
@@
 
-Implementing the $\mu$-path scheme involves operating the AFM in several
-distinct stages. In the $XY$-direction, the system must transition from tracking
-a step command (in the transition to a new measurement location) to tracking a
-scan pattern. For our simple integral controller, this only involves changing
-the reference signals $X_{ref}$ and $Y_{ref}$.
-In the $Z$-direction, the system
-must transition between tip descent, surface scanning, tip retraction, and
-maintaining a $Z$-axis position.
-
-Transition between, and operation in, these different stages is implemented as a
-simple state machine, summarized in Table~\ref{tab:cs_tasks}. 
-In the following, $r_X$ and $r_Y$ refer to the references for the $X$ and $Y$ axes while $r_{Z,s}$ and $\rzup$ refer to the $Z$-axis setpoints during scanning and retraction, respectively.
+Implementing the $\mu$-path scheme involves operating the AFM in
+several distinct stages. In the $XY$-direction, the system transitions
+from tracking a step command in the transition to a new
+measurement location to tracking a short ramp during the actual $\mu$-path scan.
+For our simple integral controller, this only involves changing the reference signals
+$X_{ref}$ and $Y_{ref}$. In the $Z$-direction, the system must
+transition between tip descent, surface scanning, and tip retraction. F
+
+Transition between, and operation in, these different stages is
+implemented as a simple state machine, summarized in
+Table~\ref{tab:cs_tasks}. In the following, $r_X$ and $r_Y$ refer to
+the references for the $X$ and $Y$ axes while $r_{Z,s}$ and $\rzup$
+refer to the $Z$-axis setpoints during scanning and retraction,
+respectively.
 
@@
   \begin{tabular}{lccc}
-    state & $X$,$Y$ & $Z$ & next-state\\
+    state & $r_X$,$r_Y$ & $r_Z$ & next-state\\
     \toprule
@@
 \end{table}
-Two cycles of this sequential process are illustrated by the time series in
-Fig.~\ref{fig:mupathsignaltrajectory}. The following subsections describe in
-more detail several features of the CS scanning process.
+Two cycles of this sequential process are illustrated by the time
+series in Fig.~\ref{fig:cs_cycle}. The following
+subsections describe in more detail several features of the CS
+scanning process.
+
+\subsection{Cantilever does not need to fully disengage.}
+\todo{Not clear to me yet that friction is useful if I scan parallel
+  to cantilever. Also not clear to me that the normal force and shear
+  force are orthogonal concepts. Maybe the macroscopic analogy breaks
+  down, but thinking of a knife pushed into a surface and then
+  dragged...}
+In our initial implementation \cite{braker_hardware_2018}, we insisted that the during
+tip-retraction (state-5), the cantilever tip should fully break
+contact with the surface. Here, we impose no such requirement. Rather,
+we change the $Z$-setpoint during tip-retraction to only pull away far
+enough that the deflection signal stays low (i.e., below the scanning
+setpoint), even while we run across the surface. We choose \rzup so
+that the interaction between the tip and sample becomes purely
+adhesive. In general, stable imaging in is not possible at \rzup and
+complete dis-engagement occasionally occurs. This can be seen in bottom pane of
+Fig.~\ref{fig:cs_cycle} during the second $XY$-move (black portion) where the tip detaches partway through the move.
+%Fig.~\ref{fig:afm_bd_dinv} which selects either the scanning setpoint $r_{Z,s}$ or the retraction setpoint $r_{Z,\textrm{up}}$ based the current state.
+When dis-engagement does occur, the $Z$-axis control loop implements an anti-windup scheme to prevent the control from saturating.
+
+Only moving the tip into the adhesive region during the $XY$ move saves considerable time
+compared to completely detaching the tip between each $\mu$-path.
+By eliminating the normal force into the sample, we are able to take dozens of images with a single probe without a noticeable degradation in image quality.
+However, completely characterizing the damage done to the tip and sample with this scheme compared complete detachment (which can also damage the probe \cite{meyer_atomic_1992}), remains an outstanding goal.
 
 \begin{figure}[t!]
-  \centering
-  \includesvg[width=1\columnwidth]{figures/cs_cycle.svg}
+  \centering \includesvg[width=1\columnwidth]{figures/cs_cycle.svg}
   \caption{Several CS cycles. Each state is indicated by color.}
-  \label{fig:mupathsignaltrajectory}
+  \label{fig:cs_cycle}
 \end{figure}
 
-\subsection{Cantilever does not need to fully disengage.}
-\todo{Not clear to me yet that friction is useful if I scan parallel to cantilever.
-  Also not clear to me that the normal force and shear force are orthogonal concepts.
-  Maybe the macroscopic analogy breaks down, but thinking of a knife pushed into a surface and then dragged...}
-In our initial implementation \cite{braker_hardware_2018}, we insisted that the during tip-retraction
-(state-5), the cantilever tip should fully break contact with the surface. Here,
-we impose no such requirement. Rather, we change the $Z$-setpoint during
-tip-retraction to only pull away far enough that the deflection signal stays low
-(i.e., below the scanning setpoint), even while we run across the surface.
-We choose \rzup so that the interaction between the tip and sample becomes purely adhesive.
-In general, stable imaging in is not possible at \rzup and complete dis-engagement occasionally occurs.
-
-The change in setpoints is achieved via the multiplexer in Fig.~\ref{fig:afm_bd_dinv}
-which selects either the scanning setpoint $r_{Z,s}$ or the retraction setpoint
-$r_{Z,\textrm{up}}$ based the current state.
-When dis-engagement does occur, the $Z$-axis control loop implements an anti-windup scheme.
-
-% Ultimately the concern is damage to the sample and tip,
-% which is caused by the force imparted by the cantilever probe
-% \cite{clayton_review_2009}. The deflection signal, though un-calibrated (meaning
-% it does not directly lead to a value in $kN$), is proportional to that force,
-% because it is proportional to how much the cantilever is bent. I.e., a large
-% (towards $+\infty$) deflection implies the spring force of the cantilever is
-% pushing hard into the sample, thereby inducing damage. In a typical imaging
-% scenario, we choose a deflection setpoint, (say $0.15$~[v], as in
-% Fig.~\ref{fig:z_drift}), and have in some way decided that this is sufficient,
-% all else being equal, to not damage things too much.
-
 \begin{figure*}[ht!]
@@
   \includegraphics[width=1\textwidth]{figures/AFM_loop_xyz.pdf}
-  \caption{Block diagram of the $Z$-axis control loop. The anti-windup is active
-    for decision index $i\in\{0,1,5\}$, which correspond to states such that
-    $r_Z=\rzup$.}
+  \caption{Block diagram of the $Z$-axis control loop. The anti-windup
+    is active for decision index $i\in\{0,1,5\}$, which correspond to
+    states such that $r_Z=\rzup$.}
   \label{fig:afm_bd_dinv}
@@
 \subsection{The pre-scan}
-% \begin{figure*}
-%   \begin{subfigure}{.33\textwidth}
-%     \includesvg[width=1\textwidth]{figures/zbounce_uz_example.svg}
-%     \caption{ }
-%     % \label{fig: }
-%   \end{subfigure}
-%   \begin{subfigure}{.33\textwidth}
-%     \includesvg[width=1\textwidth]{figures/prescan_uz_example.svg}
-%     \caption{ }
-%     \label{fig:uz_prescan}
-%   \end{subfigure}
-%   \begin{subfigure}{.33\textwidth}
-%     \includesvg[width=1\textwidth]{figures/prescan_zbounce_PSD.svg}
-%     \caption{ }
-%     % \label{fig: }
-%   \end{subfigure}
-%   \caption{(a) A ``$Z$-bounce'' experiment where the $XY$-stage is motionless
-%     and the cantilever is repeatedly engaged and disengaged. (b) One cycle of a
-%     tightly packed set of CS-cycles where the movement between each measurement
-%     location is 0. (c) PSDs from the portions of the trajectories which are
-%     colored blue and turquoise, averaged over many such cycles, demonstrating
-%     that the scan process itself reduces vibration in the $Z$-axis.}
-%   \label{fig:prescan_difference}
-% \end{figure*}
-After the tip-descent, we begin scanning in a ``pre-scan'' phase (state (3)).
-During this phase,
-
-To motivate, this consider Fig.~\ref{fig:prescan_difference}. The left panel
-represents what we call a ``$Z$''-bounce experiment, where the $XY$-stage stays
-motionless, but we repeatedly retract and re-engage the tip with specimen,
-exactly as we would in a CS scan. The right panel represents a single cycle from
-specialized CS pattern, where the $\mu$-paths are still 500 nm long, but the
-paths are separated by 0 pixels.
-In this case, the specimen is freshly cleaved
-mica.
-The goal here is to eliminate (i) any oscillations which arise from the
-$XY$-move and (ii) to have a perfectly flat surface to scan over so that
-there are as few disturbances as possible entering the control loop. Finally,
-the left panel of Fig.~\ref{fig:prescan_difference} shows the PSDs of the left
-and right panels (but averaged over many similar cycles). Note that the PSD is
-only computed from the combination of the blue and turquoise signals.
-
-What we see then, is that, for some unknown (to me) reason, scanning reduces the
-amount of energy that shows up near 215 Hz. The idea behind the pre-scan is to
-take advantage of this. The pre-scan phase is relatively long (150 samples),
-especially for the faster scan rates. However, the pre-scan also allows us to
-eliminate the over-scan at the end of the $\mu$-path, because by the time we are
-ready to start taking data, the $X$-axis is already in quasi-steady-state. For
-the current control design, the required over-scan is about 90 samples (which
-can be computed from the steady-state error of the closed-loop system to a
-ramp), which means the pre-scan incurs an effective overhead of about 60 samples
-per $\mu$-path.
-
-% The tip settling (pre-scan) period could likely be much shorter if we a had a
-% $Z$-axis position sensor. Part of the reason it is so long is that, despite not
-% pulling the cantilever completely away from the sample, there is still a small
-% drift transient, as can be seen Fig.~\ref{fig:uz_prescan}. We would like to at
-% least give the major part of that drift transient time to die out. With a
-% position sensor, we would not care about the drift transient: the control signal
-% drifts to keep the $Z$-position constant.
+After the tip-descent, we begin scanning in a ``pre-scan'' phase
+(state (3)), which is the turquoise portion of the trajectories in Fig.~\ref{fig:cs_cycle}.
+There are two reasons for this.
+First, we have observed that there is less noise in the deflection signal while the $XY$-stage is in motion compared to sitting still.
+More importantly, it lets us bring the $X$-axis to its scanning velocity at the same time the transients from the $Z$-axis die out.
+Without this, we must extend the $\mu$-path by a distance equal to the steady-state error following a ramp.
+For an arbitrary scan speed, this means the $\mu$-path scan would need an extra
+\begin{equation}
+  N = \left\lceil\lim_{z\rightarrow 1} \frac{1-H_x}{z-1}\right\rceil
+\end{equation}
+time steps, where $H_x$ is closed-loop transfer function for the $x$-axis, including $F_X$.
+For our system $N=111$. By initiating the scan while the $Z$-axis settles, we eliminate much of
+this overhead.
 
 \subsection{Control}\label{sec:control}
-\begin{figure}
-  \centering
-  \includesvg[width=1\columnwidth]{figures/z_control_design.svg}
-  \caption{FRFs of the $Z$-axis. The blue curve is the open loop response from $u_Z$ to deflection. By inverting the bending mode at 215~Hz, we achieve the black curve in closed-loop.}
-  \label{fig:z_control}
-\end{figure}
-The control structure for each axis, shown in the block diagram in Fig.~\ref{fig:afm_bd_dinv}, is similar and essentially consists of a set of filters in series with a PI controller.
-The open-loop frequency response for the $Z$-axis is shown in Fig.~\ref{fig:z_control} and in Fig.~\ref{fig:mimo_frf_uxuy} for the $X$ and $Y$ axes as the black curves.
-The first resonance of each axis is the bending mode, which appears at 215~Hz for the $Z$ axis and about 350~Hz for the $X$ and $Y$ axes.
-
-The filter portion of the $Z$-axis controller $D_Z$ is second-order and simply inverts the complex-conjugate pole-zero pair at 215~Hz.
-This allows the gain of the PI controller to be increased substantially.
-The closed-loop achieves a bandwidth of about 450~Hz, as shown by the black curve in Fig.~\ref{fig:z_control}.
-Without this inversion, the bandwidth is limited to about 50~Hz.
-
-We take a similar approach for the $X$ and $Y$ axes.
-The filters $D_x$ and $D_y$ invert the bending modes at 350~Hz and add notch filters at the main resonant peaks near 650~Hz.
-The resulting closed-loop transfer functions are shown as the red curves in Fig.~\ref{fig:mimo_frf_uxuy}.
-
-In general, the $X$-axis positioning requirements are more stringent for both CS and raster scanning.
-BLA BLAH hysteresis and creep.
-Thus, the $X$-axis compensator also includes an inverse creep and hysteresis model.
-The hysteresis model is a modified Prandtl-Ishlinki type model and is based on the work of \cite{kuhnen_modeling_2003}, while the drift compensation models the piezo creep as a simple second order transfer function with real poles and zeros.
-In Fig.~\ref{fig:afm_bd_dinv}, the hysteresis inversion is indicated by $\mathcal{H}^{-1}[\cdot]$.
-We have found that the inclusion of these extra compensators limits the overshoot of the $X$-axis during larger moves between different $\mu$-paths.
-More details on fitting the creep and hysteresis models can be found in our other work \cite{braker_afmmpc_2019}.
-
-% There are multiple advantages to this method: first,
-% an inverse compensator still makes sense as a feedforward, open-loop compensator
-% if the feedback path is broken. This situation can and does occur during parts
-% of the CS cycle. Second, the inverse compensator
-% requires no tuning as it is defined only by a fit to the measured FRF.
+% \begin{figure}
+%   \centering
+%   \includesvg[width=1\columnwidth]{figures/z_control_design.svg}
+%   \caption{FRFs of the $Z$-axis. The blue curve is the open loop
+%   response from $u_Z$ to deflection. By inverting the bending mode
+%   at 215~Hz, we achieve the black curve in closed-loop.}
+%   \label{fig:z_control}
+% \end{figure}
+The control structure for each axis, shown in the block diagram in
+Fig.~\ref{fig:afm_bd_dinv}, is similar and essentially consists of a
+set of filters in series with a PI controller. The open-loop frequency
+response for the $X$ and $Y$ axes is shown as the black curves in Fig.~\ref{fig:mimo_frf_uxuy} and for the $Z$-axis in Fig.~\ref{fig:z_control}.
+The first resonance of each axis is the bending mode, which
+appears at 215~Hz for the $Z$ axis and about 350~Hz for the $X$ and
+$Y$ axes.
+
+The filter portion of the $Z$-axis controller $D_Z$ is second-order
+and simply inverts the complex-conjugate pole-zero pair at 215~Hz.
+This allows the gain of the PI controller to be increased
+substantially. The closed-loop achieves a bandwidth of about 450~Hz,
+as shown by the red curve in Fig.~\ref{fig:z_control}. Without this
+inversion, the bandwidth is limited to about 50~Hz.
+
+We take a similar approach for the $X$ and $Y$ axes. The filters $D_x$
+and $D_y$ invert the bending modes at 350~Hz and add notch filters at
+the main resonant peaks near 650~Hz. The resulting closed-loop
+transfer functions are shown as the red curves in
+Fig.~\ref{fig:mimo_frf_uxuy}.
+
+In general, the $X$-axis positioning requirements are more stringent
+for both CS and raster scanning. Due to the step inputs the $X$-axis must track, we have found that
+compensating hysteresis and creep to be particular helpful during $\mu$-path scanning. Thus,
+the $X$-axis compensator also includes an inverse creep and hysteresis
+model. The hysteresis model is a modified Prandtl-Ishlinki type model
+and is based on the work of \cite{kuhnen_modeling_2003}, while the
+drift compensation models the piezo creep as a simple second order
+transfer function with real poles and zeros. In
+Fig.~\ref{fig:afm_bd_dinv}, the hysteresis inversion is indicated by
+$\mathcal{H}^{-1}[\cdot]$. We have found that the inclusion of these
+extra compensators limits the overshoot of the $X$-axis during larger
+moves between different $\mu$-paths (e.g., without them, the $X$-axis trajectory in Fig.~\ref{fig:with_ff} would show noticeable overshoot). More details on fitting the creep
+and hysteresis models can be found in our other work \cite{braker_afmmpc_2019}.
 
@@
   \centering
+  \begin{subfigure}[b]{.65\textwidth}
     \includesvg[width=1\textwidth]{figures/MIMO_CL_uxuy.svg}
-  \caption{MIMO closed and open loop FRFs, showing the dramatic affect on $G_{Z,u_X}$ and $G_{Z,u_Y}$ when the feedforward compensators are used for the $X$ and $Y$ axes.}
-  \label{fig:mimo_frf_uxuy}
+    \caption{}\label{fig:mimo_frf_uxuy}
+  \end{subfigure}\hfill
+  \begin{subfigure}[b]{.34\textwidth}
+    \includesvg[width=1\textwidth]{figures/with_wo_ff.svg}
+    \caption{}\label{fig:with_ff}
+    \vspace{2ex}
+    \includesvg[width=1\textwidth]{figures/z_control_design.svg}
+    \caption{}\label{fig:z_control}
+  \end{subfigure}
+  \caption{(a) MIMO closed and open-loop FRFs, showing the dramatic
+    affect on $G_{Z,u_X}$ and $G_{Z,u_Y}$ when the feedforward
+    compensators are used for the $X$ and $Y$ axes.
+(b) The vertical control $u_Z$ (top) after a large move in the $X$-direction (bottom) without (left column) and with (right column) the feedforward compensation.
+(c) Frequency response of the $Z$-axis in open-loop (black) and closed-loop (red).
+}
 \end{figure*}
 
-% As illustrated in Fig.~\ref{fig:zMultiplex_anderssonLab}, the voltage applied to
-% the $z$-piezo is adjusted by switching the feedback signal between the $z$-axis
-% position sensor (when the tip is off the surface) and the deflection signal
-% (when the tip is engaged). The difference equation associated with
-% \eqref{eqn:dzI} for the $z$-axis is
-% \begin{equation}
-%   u_z(k) = K_Ie(k) + u_z(k-1).
-%   \label{eqn:intdiff}
-% \end{equation}
-
-% In the $z$-axis position control mode, the $z$-axis position is controlled to a
-% fixed value $z_{ref}$ which, in general, is slightly above the sample surface.
-% The difference between the measured $z$-axis position and $z_{ref}$,
-% ${e(k) = z_{ref} - z(k)}$, is used as the error signal. In the deflection
-% control mode, when the tip is in contact with the sample, the deflection signal
-% is controlled to a fixed value $l_{ref}$ to ensure a constant tip-sample force.
-% The sample surface acts as a disturbance to the control loop. Therefore, the
-% $z$-axis position measurements can be taken to represent the surface topography
-% of the sample. In this case, the difference between the measured deflection and
-% $l_{ref}$ is the error, $e(k) = l_{ref} - l(k)$.
-
-% We note that the $z$-axis control described here operates the AFM in constant
-% force mode during imaging. It is straightforward to perform scanning under
-% different AFM modes, such as tapping mode, simply by adjusting the signals and
-% control involved in the vertical loop.
+% We note that the $z$-axis control described here operates the AFM in
+% constant force mode during imaging. It is straightforward to perform
+% scanning under different AFM modes, such as tapping mode, simply by
+% adjusting the signals and control involved in the vertical loop.
 
 \subsection{Feedforward Control}\label{sec:ff_control}
-% In our AFM, there is a strong coupling between the horizontal axes and vertical deflection.
-Fig.~\ref{fig:mimo_frf_uxuy} shows a MIMO FRF for $u_X$ and $u_Y$ to the outputs in each axis.
-The dotted black curves are the open loop responses and the dashed red curves are the nominal closed-loop responses.
-Though the $Z$-direction inputs are not shown, the closed loop responses include the $Z$-axis controller.
-Note that, especially for $H_{z,u_X}$, the closed-loop response is barely improved over the open loop response and in particular, there is a sharp resonance at 215~Hz and 505~Hz.
-To deal with this, we employ two different strategies for CS and raster scanning.
-Unfortunately, as the bottom panel of Fig.~\ref{fig:mimo_frf_uxuy} makes clear, there is a strong cross-coupling from the horizontal plane to the $Z$ axis (the coupling from $u_Z$ to the $X$ and $Y$ axes is very weak, and so is not shown).
-Our SISO control scheme does little to attenuate the resonances of $G_{Z,u_X}$ and $G_{Z,u_Y}$.
-In particular, there are modes in both these transfer functions at 215 and 505 Hz that do not appear in a SISO model of $G_{X,u_X}$ or $G_{Y,u_Y}$.
-
-For raster scans, the frequency content of the $X$-axis reference (which is a triangle wave) decays like $1/n^2$ with a gain proportional to the raster frequency.
-In contrast, the $X$-axis reference for a $\mu$-path scan is composed of a sequence of steps and ramps.
-The inclusion of the (discontinuous) steps means we should expect the $\mu$-path $X$ reference to decay like $1/n$.
-Thus,  while the cross-coupling can induce $Z$-axis vibrations for faster raster scans, it is especially problematic for $\mu$-path scanning.
-This is illustrated in the left column of Fig.~\ref{fig:with_ff}, which shows a CS cycle during which the $X$-axis makes a 5 micron move, which induces excessively large vibrations in the vertical control.
-
-In principle, one could mitigate these issues with a full MIMO control design. In this work, we opt for a much simpler feedforward scheme.
-For CS scanning, we insert feed-forward filters ($F_X$ and $F_Y$ in Fig.~\ref{fig:afm_bd_dinv}) with three notches: one at 215~Hz, one at 350~Hz and one at 505~Hz.
-We design a similar feed-forward filter for the $Y$-axis.
-Both filters are shown in Fig.~\ref{fig:mimo_frf_uxuy} as the solid pink curves and the resulting overall FRF is shown as the solid blue curves, which show a dramatic reduction in the cross coupling.
-A similar affect could be achieve by using a simple low-pass filter.
-However, to achieve the same 40~dB of attenuation of the mode at 215 Hz, would require, e.g., that a two-pole low-pass filter have its cut-off frequency at about 20~Hz.
-Thus, while our feedforward scheme slows the $X$-axis down, we achieve better bandwidth than we would with a simple low-pass filter.
-
-For raster scanning, we set $F_X=F_Y=1$ and instead take advantage of the periodicity of the $X$-axis reference, which is a triangle wave.
-We modify the triangle wave to a truncated Fourier series, where each Fourier coefficient is scaled by the inverse of the closed-loop FRF at the corresponding frequency.
-See, e.g., \cite{clayton_review_2009} for more details on this strategy.
-We truncate this series such that the highest frequency is smaller than 200 Hz, which implies that we should never excite the problematic $G_{Z,u_X}$ modes.
-This scheme implies that the effective bandwidth of the $X$-axis controller is higher while raster scanning than while CS-scanning.
-On the other hand, it also implies that the for faster scan rates, fewer Fourier coefficients are used, and so the approximation to a triangle wave is worse.
-\begin{figure}
-  \includesvg[width=1\columnwidth]{figures/with_wo_ff.svg}
-  \caption{Scans over mica. (left) Without feedforward. (right) with feedforward.}
-  \label{fig:with_ff}
-\end{figure}
+Unfortunately, as the bottom row of plots in Fig.~\ref{fig:mimo_frf_uxuy}
+makes clear, there is a strong cross-coupling from the horizontal
+plane to the $Z$ axis (the coupling from $u_Z$ to the $X$ and $Y$ axes
+is very weak, and so is not shown). Our SISO control scheme does
+little to attenuate the resonances of $G_{Z,u_X}$ and $G_{Z,u_Y}$. In
+particular, there are modes in both these transfer functions at 215
+and 505 Hz that do not appear in a SISO model of $G_{X,u_X}$ or
+$G_{Y,u_Y}$.
+
+For raster scans, the frequency content of the $X$-axis reference
+(which is a triangle wave) decays like $1/n^2$ with a gain
+proportional to the raster frequency. In contrast, the $X$-axis
+reference for a $\mu$-path scan is composed of a sequence of steps and
+ramps. The inclusion of the (discontinuous) steps means we should
+expect the $\mu$-path $X$ reference to decay like $1/n$. Thus, while
+the cross-coupling can induce $Z$-axis vibrations for faster raster
+scans, it is especially problematic for $\mu$-path scanning. This is
+illustrated in the left column of Fig.~\ref{fig:with_ff}, which shows
+a CS cycle during which the $X$-axis makes a 5 micron move, which
+induces excessively large vibrations in the vertical control.
+
+In principle, one could mitigate these issues with a full MIMO control
+design. In this work, we opt for a much simpler feedforward scheme.
+For CS scanning, we insert feed-forward filters ($F_X$ and $F_Y$ in
+Fig.~\ref{fig:afm_bd_dinv}) with three notches: one at 215~Hz, one at
+350~Hz and one at 505~Hz. Both filters are shown in Fig.~\ref{fig:mimo_frf_uxuy}
+as the dashed-pink curves and the resulting overall FRF is shown as the
+dotted-blue curves, which show a dramatic reduction in the cross
+coupling. A similar affect could be achieve by using a simple low-pass
+filter. However, to achieve the same 40~dB of attenuation of the mode
+at 215 Hz, would require, e.g., that a two-pole low-pass filter have
+its cut-off frequency at about 20~Hz. Thus, while our feedforward
+scheme slows the $X$-axis down, we achieve better bandwidth than we
+would with a simple low-pass filter.
+
+For raster scanning, we set $F_X=F_Y=1$ and instead take advantage of
+the periodicity of the $X$-axis reference, which is a triangle wave.
+We modify the triangle wave to a truncated Fourier series, where each
+Fourier coefficient is scaled by the inverse of the closed-loop FRF at
+the corresponding frequency. See, e.g., \cite{clayton_review_2009} for
+more details on this strategy. We truncate this series such that the
+highest frequency is smaller than 200 Hz, which means that we should
+never excite the problematic $G_{Z,u_X}$ modes. This scheme implies
+that the effective bandwidth of the $X$-axis controller is higher
+while raster scanning than while CS-scanning. On the other hand, it
+also implies that the for faster scan rates, fewer Fourier
+coefficients are used, and so the approximation to a triangle wave is
+worse.
 
 \section{Metrics}\label{sec:rdi}
-In section~\ref{sec:results} we use three metrics to asses our results.
-The first two seek to quantify image quality of two images. 
-Define a master image as $X$ and a reconstruction or corrupted version as $Y$, with each having $s\times h=m$ pixels.
-Let $x=\textrm{vec}(X)$ and $y=\textrm{vec}(Y)$. Let $L$ be the dynamic range of the master image $x$.
-Then the peak signal to noise ratio (PSNR) is given by
+In section~\ref{sec:results} we use three metrics to asses our
+results. The first two seek to quantify image quality of two images.
+Define a master image as $X$ and a reconstruction or corrupted version
+as $Y$, with each having $s\times h=m$ pixels. Let $x=\textrm{vec}(X)$
+and $y=\textrm{vec}(Y)$. Let $L$ be the dynamic range of the master
+image $x$. Then the peak signal to noise ratio (PSNR) is given by
 \begin{equation*}
@@
 
-The goal of the SSIM is to compare two image's structure, luminescence, and contrast and is built up from the means ($\mu_x$ and $\mu_y$), standard deviations ($\sigma_x$ and $\sigma_y$), and covariance ($\sigma_{xy}$) of the image vectors $x$ and $y$.
-The variation of the SSIM used in this paper is defined as
+The goal of the SSIM is to compare two image's structure,
+luminescence, and contrast and is built up from the means ($\mu_x$ and
+$\mu_y$), standard deviations ($\sigma_x$ and $\sigma_y$), and
+covariance ($\sigma_{xy}$) of the image vectors $x$ and $y$. The
+variation of the SSIM used in this paper is defined as
 \begin{equation*}
@@
 \end{equation*}
-where the constants $C_1$ and $C_2$ are regularizing constants to prevent singularity if, e.g., $\mu_x=\mu_y=0$.
-We use the default values suggested in \cite{wang_image_2004} of $C_1=(0.01L)^2$ and ${C_2=(0.03L)^2}$, where again, $L$ is the dynamic range.
-In general two images which are identical will yield an infinite PSNR and an SSIM of 1.
+where the constants $C_1$ and $C_2$ are regularizing constants to
+prevent singularity if, e.g., $\mu_x=\mu_y=0$. We use the default
+values suggested in \cite{wang_image_2004} of $C_1=(0.01L)^2$ and
+${C_2=(0.03L)^2}$, where again, $L$ is the dynamic range. In general
+two images which are identical will yield an infinite PSNR and an SSIM
+of 1.
 
 \subsection{Limitations of SSIM and PSNR}\label{sec:limits}
-The SSIM and PSNR have become reasonably popular in studies comparing simulated AFM image reconstructions \cite{oxvig_structure_2017, han_optimal_2018, Luo_nano_2015}.
-However, it remains somewhat of an open question how to best compare experimental AFM images.
-While we use the SSIM and PSNR in Section~\ref{sec:results}, we believe those numbers should be interpreted with some caution.
-In our experimental setup, actuation in the $XY$-plane happens via the nPoint piezo stage and the $XY$-direction of the original piezo scanner is uncontrolled.
-This leads to substantial drift between images.
-To illustrate this, we took a sequence of 6 raster scans of a sample grating, each at a 1~Hz scan rate over a 5 micron by 5 micron area.
-The top row of Fig.~\ref{fig:baseline_errors} shows the error between the first and second image and the first and 6th image.
-The PSNR and SSIM between images one and six are \baseline{one2twoNoAlgnPsnr} and \baseline{one2twoNoAlgnSsim}; between images one and six they are \baseline{one2sixNoAlgnPsnr} and \baseline{one2sixNoAlgnSsim}, respectively, even though on their own each image has good quality.
-
-To mitigate this affect, we use an image alignment technique based on the 2D cross-correlation between each image.
-Essentially, this takes a sub-slice of image 1 (here, a 25 pixel inset on each edge), and finds the offset in the other image that produces the smallest error.
-The result of this procedure are shown in the bottom row of Fig.~\ref{fig:baseline_errors}.
+The SSIM and PSNR have become reasonably popular in studies comparing
+simulated AFM image reconstructions \cite{oxvig_structure_2017,
+  han_optimal_2018, Luo_nano_2015}. However, it remains somewhat of an
+open question how to best compare experimental AFM images. While we
+use the SSIM and PSNR in Section~\ref{sec:results}, we believe those
+numbers should be interpreted with some caution. In our experimental
+setup, actuation in the $XY$-plane happens via the nPoint piezo stage
+and the $XY$-direction of the original piezo scanner is uncontrolled.
+This leads to substantial drift between images. To illustrate this, we
+took a sequence of 6 raster scans of a sample grating, each at a 1~Hz
+scan rate over a 5 micron by 5 micron area. The top row of
+Fig.~\ref{fig:baseline_errors} shows the error between the first and
+second image and the first and 6th image. The PSNR and SSIM between
+images one and six are \baseline{one2twoNoAlgnPsnr} and
+\baseline{one2twoNoAlgnSsim}; between images one and six they are
+\baseline{one2sixNoAlgnPsnr} and \baseline{one2sixNoAlgnSsim},
+respectively, even though on their own each image has good quality.
+
+To mitigate this affect, we use an image alignment technique based on
+the 2D cross-correlation between each image. Essentially, this takes a
+sub-slice of image 1 (here, a 25 pixel inset on each edge), and finds
+the offset in the other image that produces the smallest error. The
+result of this procedure are shown in the bottom row of
+Fig.~\ref{fig:baseline_errors}.
 % Taking the first scan as the master, we compute the PSNR and SSIM
-% metrics. The best PSNR here is 16.57 and the worst is 9.02.
-% The best SSIM is 0.54 and the worst is 0.28.
-Although the situation is improved compared to the un-aligned images, there is still noticeable stretching,
-particularly in the $Y$-direction.
-Notably, with the alignment technique,
-the SSIM is \baseline{one2twoAlgnSsim} for images one and two, and \baseline{one2sixAlgnSsim} for images one and six; the PSNR is \baseline{one2twoAlgnPsnr} and \baseline{one2sixAlgnPsnr} respectively.
+% metrics. The best PSNR here is 16.57 and the worst is 9.02. The best
+% SSIM is 0.54 and the worst is 0.28.
+Although the situation is improved compared to the un-aligned images,
+there is still noticeable stretching, particularly in the
+$Y$-direction. Notably, with the alignment technique, the SSIM is
+\baseline{one2twoAlgnSsim} for images one and two, and
+\baseline{one2sixAlgnSsim} for images one and six; the PSNR is
+\baseline{one2twoAlgnPsnr} and \baseline{one2sixAlgnPsnr}
+respectively.
 
 \begin{figure}[t!]
-  \includesvg[width=1\columnwidth]{figures/baseline_errors_aligned_1Hz.svg}
-  \caption{Errors between the first and second (left column) and first and sixth (right column) raster scans in a sequence of six 1.0~Hz raster scans. (top) Errors without alignment (bottom)
-    The same data but aligned via cross correlation.}
+  \centering
+  % \includesvg[width=0.7\columnwidth]{figures/baseline_errors_aligned_1Hz.svg}
+  \includesvg[width=0.7\columnwidth]{figures/baseline_errors_1and6.svg}
+  \caption{Errors between the first and second (left column) and first
+    and sixth (right column) raster scans in a sequence of six 1.0~Hz
+    raster scans. (top) Errors without alignment (bottom) The same
+    data but aligned via cross correlation.}
   \label{fig:baseline_errors}
@@
 %   \includesvg[width=1\columnwidth]{figures/damage_illustration.svg}
-%   \caption{The RDI metric defined in \eqref{eqn:RDI} penalizes everything in the
-%     red shaded region and does not penalize anything in the un-shaded region.}
+%   \caption{The RDI metric defined in \eqref{eqn:RDI} penalizes
+%   everything in the red shaded region and does not penalize anything
+%   in the un-shaded region.}
 %   \label{fig:damage_illustrate}
@@
 % Th PSNR and SSIM metrics only assess the similarity of two images.
-% However, in AFM imaging, pure image quality is not the
-% only concern, particularly for delicate samples. What is needed is a figure of
-% merit for how much damage was done to specimen during the imaging process. While
-% this is not really a concern while imaging a hard calibration grating, it plays
-% a prominent role biological samples~\cite{ando_highspeed_2008}. In general,
-% damage occurs while scanning into an uphill region, which results in a positive
-% deflection signal. The actual damage done by a given $Z_d$ will depend on the
-% spring constant of the cantilever and the softness of the specimen. Nonetheless,
-% we can use the positive deviations of $Z_d$ as a relative measure of damage
-% between different scan speeds or scanning methods, for a given cantilever and
-% specimen. This motivates a metric we term the relative damage index (RDI), which
-% we define as
+% However, in AFM imaging, pure image quality is not the only concern,
+% particularly for delicate samples. What is needed is a figure of
+% merit for how much damage was done to specimen during the imaging
+% process. While this is not really a concern while imaging a hard
+% calibration grating, it plays a prominent role biological
+% samples~\cite{ando_highspeed_2008}. In general, damage occurs while
+% scanning into an uphill region, which results in a positive
+% deflection signal. The actual damage done by a given $Z_d$ will
+% depend on the spring constant of the cantilever and the softness of
+% the specimen. Nonetheless, we can use the positive deviations of
+% $Z_d$ as a relative measure of damage between different scan speeds
+% or scanning methods, for a given cantilever and specimen. This
+% motivates a metric we term the relative damage index (RDI), which we
+% define as
 % \begin{align}
@@
 % \end{align}
-% where $N$ is the total number of samples in a given scan, $Z_{d,k}$ is the
-% deflection signal at sample $k$ and $r_{Z,\textrm{s}}$ is the scanning setpoint.
-% The RDI is basically the power in positive deflection. By excluding negative
-% values of the deflection, we do not penalize the CS algorithm while it is
-% re-engaging with the specimen \emph{unless} it overshoots the scanning setpoint,
-% which we do want to penalize. This is illustrated in
-% Fig.~\ref{fig:damage_illustrate}, which shows several CS cycles with a poorly
-% tuned controller. Only deflection signals in the red-shaded region will be
-% penalized by the RDI.
+% where $N$ is the total number of samples in a given scan, $Z_{d,k}$
+% is the deflection signal at sample $k$ and $r_{Z,\textrm{s}}$ is the
+% scanning setpoint. The RDI is basically the power in positive
+% deflection. By excluding negative values of the deflection, we do
+% not penalize the CS algorithm while it is re-engaging with the
+% specimen \emph{unless} it overshoots the scanning setpoint, which we
+% do want to penalize. This is illustrated in
+% Fig.~\ref{fig:damage_illustrate}, which shows several CS cycles with
+% a poorly tuned controller. Only deflection signals in the red-shaded
+% region will be penalized by the RDI.
 
 \section{Experimental Results}\label{sec:results}
-We compared $\mu$-path scanning to two scenarios. First, we compare it to full resolution raster scans at several scan rates. Second we compare to course raster scans.
+We compared $\mu$-path scanning to two scenarios. First, we compare it
+to full resolution raster scans at several scan rates. Second we
+compare to course raster scans.
 % For both comparisons, we use the same set of $\mu$-path scans.
@@
 \subsection{Comparison to full raster}
-We took scans of a Ted Pella CS-20NG sample grating over an area with holes on a 500 nm
-pitch.
-The holes are 20 nm deep.
-We scanned 5 micron by 5 micron images using standard raster scans with 512 lines.
-For the raster scans, we took scans at 1.0~Hz, 2.5~Hz, 5.0~Hz, 8.0~Hz and 10~Hz.
-We also took $\mu$-path scans with densities at 12.5\%, 15\% and 25\% and reconstructed 512 by 512 pixel images. 
-The CS scans we taken with scan velocities equivalent to raster scan rates of 1.0~Hz,
-2.0~Hz, 5.0~Hz and 8.0~Hz. 
-For all CS scans, the $\mu$-paths are $\scanD{muLenNM}$ nm long, which translates to $\scanD{muLenPix}$ pixels.
-
-The free value of the deflections signal was approximately -0.6 volts and we set
-the scanning reference to ${\rzs=\scanD{spScan}}$~volts and the withdraw reference to
-${\rzup=\scanD{spMv}}$ volts. We set the $XY$-settle boundary to $\pm \scanD{xyBoundaryMic}$
-microns and required $\scanD{xySetSamps}$ samples within this boundary before moving to the
-$Z$-engage state. The pre-scan length was $\scanD{preScanSamples}$ time steps.
-The cantilever was an Budget Sensors ContAI-G, with a nominal
-length of 450 microns and spring constant of $k=0.2$~N/m.
+We took scans of a Ted Pella CS-20NG sample grating over an area with
+holes on a 500 nm pitch. The holes are 20 nm deep. We scanned 5 micron
+by 5 micron images using standard raster scans with 512 lines. For the
+raster scans, we took scans at 1.0~Hz, 2.5~Hz, 5.0~Hz, 8.0~Hz and
+10~Hz. We also took $\mu$-path scans with densities at 12.5\%, 15\%
+and 25\% and reconstructed 512 by 512 pixel images. The CS scans we
+taken with scan velocities equivalent to raster scan rates of 1.0~Hz,
+2.0~Hz, 5.0~Hz and 8.0~Hz. For all CS scans, the $\mu$-paths are
+$\scanD{muLenNM}$ nm long, which translates to $\scanD{muLenPix}$
+pixels.
+
+The free value of the deflections signal was approximately -0.6 volts
+and we set the scanning reference to ${\rzs=\scanD{spScan}}$~volts and
+the withdraw reference to ${\rzup=\scanD{spMv}}$ volts. We set the
+$XY$-settle boundary to $\pm \scanD{xyBoundaryMic}$ microns and
+required $\scanD{xySetSamps}$ samples within this boundary before
+moving to the $Z$-engage state. The pre-scan length was
+$\scanD{preScanSamples}$ time steps. The cantilever was an Budget
+Sensors ContAI-G, with a nominal length of 450 microns and spring
+constant of $k=0.2$~N/m.
 
@@
 The CS scans were reconstructed with BPVV. We set
-${\sigma = \scanD{sigma}}$, ${\mu_f=\scanD{muf}}$, ${\alpha_v=\scanD{alpv}}$ and ${\alpha_h=\scanD{alph}}$. The data remained scaled in terms of volts.
-
-For the raster scans, we discard data from the re-trace and divided the
-remaining data for each scan line into 512 bins based on the \xc sensor
-measurements. We then average the data in each bin to obtain the value of one
-pixel. To remove the affects of piezo creep and sample tilt, we then de-trend
-each individual line.
-De-trending each line causes the flat portion between the holes in the horizontal direction to appear at a different height than the flat portion between holes in the vertical direction.
-To remove this effect, we select a column of
-pixels on the left and right side of each image that does not cross any holes
-(i.e., a vertical line through the flat area), register each scan line to a
-common height along these columns. This step eases comparison with the CS scans
-and was inspired by a feature in \texttt{SPIW} \cite{spiw}.
-
-As a final step, we subtract the mean from each CS and raster image, so that
-they can all be mapped to the same color intensity in the images. The color maps
-represent a range of $\pm$20 nm.
-
-The resulting images are shown in Fig.~\ref{fig:resultsF1_images}. The rows of
-pixels indicated by the red lines are shown as cross sections Fig.~\ref{fig:pixel_rows}.
-
-For each raster scan and each CS scan, we computed the SSIM, PSNR (both with
-default parameters) using the 1~Hz scan as the master and also computed the RDI
-metric. These are collected in table ~\ref{tab:rast_vs_cs_v1}.
+${\sigma = \scanD{sigma}}$, ${\mu_f=\scanD{muf}}$,
+${\alpha_v=\scanD{alpv}}$ and ${\alpha_h=\scanD{alph}}$. The data
+remained scaled in terms of volts.
+
+For the raster scans, we discard data from the re-trace and divided
+the remaining data for each scan line into 512 bins based on the \xc
+sensor measurements. We then average the data in each bin to obtain
+the value of one pixel. To remove the affects of piezo creep and
+sample tilt, we then de-trend each individual line. De-trending each
+line causes the flat portion between the holes in the horizontal
+direction to appear at a different height than the flat portion
+between holes in the vertical direction. To remove this effect, we
+select a column of pixels on the left and right side of each image
+that does not cross any holes (i.e., a vertical line through the flat
+area), register each scan line to a common height along these columns.
+This step eases comparison with the CS scans and was inspired by a
+feature in \texttt{SPIW} \cite{spiw}.
+
+As a final step, we subtract the mean from each CS and raster image,
+so that they can all be mapped to the same color intensity in the
+images. The color maps represent a range of $\pm$20 nm.
+
+The resulting images are shown in Fig.~\ref{fig:resultsF1_images}. The
+rows of pixels indicated by the red lines are shown as cross sections
+Fig.~\ref{fig:pixel_rows}.
+
+For each raster scan and each CS scan, we computed the SSIM, PSNR
+(both with default parameters) using the 1~Hz scan as the master and
+also computed the RDI metric. These are collected in table
+~\ref{tab:rast_vs_cs_v1}.
 
@@
   \includesvg[scale=.98]{figures/cs_raster_images_6-5-2019.svg}
-  \caption{Raster and compressed sensing images of a 5 micron square area of the
-     CS-20NG grating. All images are 512$\times$512 pixels: the raster images marked as 64 and 128 lines have been interpolated. The rows of pixels
-     indicated by the red line are shown in Fig.~\ref{fig:pixel_rows}.}
+  \caption{Raster and compressed sensing images of a 5 micron square
+    area of the CS-20NG grating. All images are 512$\times$512 pixels:
+    the raster images marked as 64 and 128 lines have been
+    interpolated. The rows of pixels indicated by the red line are
+    shown in Fig.~\ref{fig:pixel_rows}.}
   \label{fig:resultsF1_images}
@@
   \centering
-  \caption{Breakdown of state times for the CS scans listed in
-    Table~\ref{tab:rast_vs_cs_v1}. All times are in seconds.}
+  \caption{Breakdown of state times for the CS scans shown in
+    Fig.~\ref{fig:resultsF1_images}. All times are in seconds.}
   \label{tab:final_state_times}
   \begin{tabular}{ccccccc}
-    \input{tables/cs_state_times_table_4-26-2019_muInf_dct2.tex}
+    \input{tables/cs_state_times_table_6-5-2019_muInf_dct2.tex}
   \end{tabular}
@@
 
-\begin{figure}[t!]
+\begin{figure}
   \includesvg[width=1\columnwidth]{figures/cs_raster_pixel_rows_6-5-2019.svg}
   \caption{Rows of pixels, as indicated by the red lines in
-    Fig.~\ref{fig:resultsF1_images}. For clarity, not all images are included.}
+    Fig.~\ref{fig:resultsF1_images}. For clarity, not all images are
+    included.}
   \label{fig:pixel_rows}
@@
 
-Unfortunately, the SSIM and PSNR metrics are not particularly illuminating. It
-is easiest to see this by plotting PSNR and SSIM against total acquisition time,
-which is shown in Fig.~\ref{fig:time_ssim} and ~\ref{fig:time_psnr}. There are several
-inconsistencies. First, the 4~Hz raster scan has the lowest PSNR of all the
-raster scans, while the 8~Hz scan has the highest. Second, all of the 15\% CS
-scans except the 8~Hz version have as good or better SSIM numbers than the
-raster scans. It makes no sense for a CS scan at a 5~Hz rate to have better
-quality than a raster scan at a 5~Hz rate.
-
-Fig.~\ref{fig:improve_512} shows amount of improvement of the different sub-sampling techniques over full raster scans with 512 lines as a function of scan rate.
-As far as pure speed goes, the CS scan at 12.5\% is the fastest for a rate of 1~Hz, though the 64 line raster scan is close.
-At the same time, the image quality of the 1~Hz, 12.5\% CS scan is better than the the 1~Hz 64 line raster scan.
+Unfortunately, the SSIM and PSNR metrics are not particularly
+illuminating. It is easiest to see this by plotting PSNR and SSIM
+against total acquisition time, which is shown in
+Fig.~\ref{fig:time_ssim} and ~\ref{fig:time_psnr}. There are several
+inconsistencies. First, the 4~Hz raster scan has the lowest PSNR of
+all the raster scans, while the 8~Hz scan has the highest. Second, all
+of the 15\% CS scans except the 8~Hz version have as good or better
+SSIM numbers than the raster scans. It makes no sense for a CS scan at
+a 5~Hz rate to have better quality than a raster scan at a 5~Hz rate.
+
+Fig.~\ref{fig:improve_512} shows amount of improvement of the
+different sub-sampling techniques over full raster scans with 512
+lines as a function of scan rate. As far as pure speed goes, the CS
+scan at 12.5\% is the fastest for a rate of 1~Hz, though the 64 line
+raster scan is close. At the same time, the image quality of the 1~Hz,
+12.5\% CS scan is better than the the 1~Hz 64 line raster scan.
 However, this advantage quickly evaporates for faster scan rates.
-Indeed, for rates beyond about 5~Hz, the raster scan with 128 lines is not only faster than the 12.5\% CS scan, it also has (arguably) better image quality.
-
-Thus, we conclude that $\mu$-path based sub-sampling is only beneficial when there is an exigent reason to scan slowly.
-This may be the case for delicate specimens.
-We can roughly quantify this by computing the power in the deflection signal during scanning
+Indeed, for rates beyond about 5~Hz, the raster scan with 128 lines is
+not only faster than the 12.5\% CS scan, it also has (arguably) better
+image quality.
+
+Thus, we conclude that $\mu$-path based sub-sampling is only
+beneficial when there is an exigent reason to scan slowly. This may be
+the case for delicate specimens. We can roughly quantify this by
+computing the power in the deflection signal during scanning
 \begin{align}
@@
 \end{align}
-The idea behind the idea is that increased scan rates lead to larger deflection signals (and thereby increased force into the specimen) at each surface feature, which the RDI accumulates.
-
-The values of the RDI for each of the $\mu$-path and raster scans are shown in Fig.~\ref{fig:time_damage} as a function of total imaging time.
-As one would expect, as imaging time decreases, the RDI for each scan type increases.
-
-% More importantly though, 
-\subsection{Comparison to Sub-line Sampling}
-Perhaps the simplest alternative to $\mu$-path sampling is to simply take a standard raster scan with fewer lines.
-This is the technique we consider in this subsection.
-Many of sub-line sampling papers assume that the lines to sample are selected randomly \cite{han_optimal_2018, Luo_nano_2015}.
-In contrast, we take an even simpler approach scan every 4th and every 8th line.
-This yields images with 128 and 64 lines respectively.
-For each of these scenarios, we first divide the data for each line into 512 bins.
-This gives an image that is 128 (resp., 64) pixels by 512 pixels.
-We then linearly interpolate along each column to produce a 512 by 512 pixel image.
-Again, we take these courser raster scans at 1.0, 5.0, 8.0 and 10.0 Hz.
-The resulting images are shown in Fig.
-XX.
-
-\begin{figure}
-  \includesvg[width=1\columnwidth]{figures/improvements.svg}
-  \caption{Fraction of improvement in total scan time over a scan with 512 lines vs scan rate for the three sets of CS scans (at 25\%, 15\% and 12.5\%) and courser raster scans at 128 and 64 lines.}
-  \label{fig:improve_512}
-\end{figure}
-
-\begin{figure}[ht!]
-  \centering
-  \begin{subfigure}{1\columnwidth}
+The idea behind the idea is that increased scan rates lead to larger
+deflection signals (and thereby increased force into the specimen) at
+each surface feature, which the RDI accumulates.
+
+The values of the RDI for each of the $\mu$-path and raster scans are
+shown in Fig.~\ref{fig:time_damage} as a function of total imaging
+time. As one would expect, as imaging time decreases, the RDI for each
+scan type increases.
+
+\begin{figure*}[t!]
+  \centering
+  \begin{subfigure}{0.329\linewidth}
     \centering
@@
   \end{subfigure}
-  \begin{subfigure}{1\columnwidth}
+  \begin{subfigure}{0.329\linewidth}
     \centering
@@
   \end{subfigure}
-\caption{Metrics for raster scan and $\mu$-path scans at 10\% and 15\% sampling.
-(a) SSIM as a function of total acquisition time.
-(b) PSNR  as a function of total acquisition time.
-(c) RDI as a function of total acquisition time.
-The scan rate is indicated by color while the scan style is indicated by marker style.}
+  \caption{Metrics for raster scan at 512, 128 and 64 lines and
+    $\mu$-path scans at 12.5\% and 25\% sampling. The scan rate is
+    indicated by color while the scan style is indicated by marker
+    style. (a) SSIM as a function of total acquisition time. (b) PSNR
+    as a function of total acquisition time. (c) RDI as a function of
+    total acquisition time.}
   % \label{fig:time_vs_metrics}
+\end{figure*}
+
+Where CS seems to really shine is if we look at the RDI for a given
+time or scan rate. This is plotted in Fig.~\ref{fig:time_damage}. For
+example, the 10~Hz raster scan, which takes about 51 seconds, gives an
+RDI of 23.7. All of the CS scans, except for the 15\% scan at 1~Hz
+(which is only 0.9 seconds longer) are faster than the 10~Hz raster
+scan, yet have much lower RDI values, ranging from 1.21 to 13.13.
+Unsurprisingly, the relationship between scan speed and RDI is quite
+linear. For the raster scans, the left panel of
+Fig.~\ref{fig:time_damage} just plots the inverse relationship of the
+right panel, since scan time is inversely proportional to raster
+frequency. This is not quite the case for the CS scans due to the
+sub-sampling and the fixed overhead which does not scale with scan
+rate (e.g., the amount of time for the $XY$-move etc remains
+essentially constant for a given scan density).
+
+From the left panel of Fig.~\ref{fig:time_damage}, we see that for a
+fixed RDI, CS has a faster imaging acquisition rate. The amount of
+improvement is best if we need a very low RDI: for example, if we want
+to hold the RDI below 2, then we have to take the 1~Hz raster scan
+(512 seconds) while we can achieve the same RDI via CS in about 52
+seconds with the 15\% sampling, which is a speed improvement of nearly
+10. The higher of an RDI we are willing to tolerate, the advantage of
+CS over raster narrows. For example, the 4~Hz raster scan and 5~Hz,
+15\% CS scan have comparable RDI, but now CS is only about 6 times
+faster. This is a result of the constant overhead imposed by the
+engage/disengage and $XY$-move states in CS.
+
+% More importantly though,
+\subsection{Comparison to Sub-line Sampling}
+Perhaps the simplest alternative to $\mu$-path sampling is to simply
+take a standard raster scan with fewer lines. This is the technique we
+consider in this subsection. Many of sub-line sampling papers assume
+that the lines to sample are selected randomly \cite{han_optimal_2018,
+  Luo_nano_2015}. In contrast, we take an even simpler approach scan
+every 4th and every 8th line. This yields images with 128 and 64 lines
+respectively. For each of these scenarios, we first divide the data
+for each line into 512 bins. This gives an image that is 128 (resp.,
+64) pixels by 512 pixels. We then linearly interpolate along each
+column to produce a 512 by 512 pixel image. Again, we take these
+courser raster scans at 1.0, 5.0, 8.0 and 10.0 Hz. The resulting
+images are shown in Fig.~\ref{fig:results_subline_images}.
+
+Note the defect on the hole located in the second column, sixth row
+from the top. The CS-scans do a poor job detecting this, while both
+course raster scans do so. However, the other artifacts in 64 line
+scan obscure the defect.
+
+\begin{figure*}
+  \centering
+  \includesvg[scale=.98]{figures/cs_raster_images_subl_6-5-2019.svg}
+  \caption{Raster scans at 128 (top) and 64 (bottom) which have been
+    interpolated along each column to 512 lines.}
+  \label{fig:results_subline_images}
+\end{figure*}
+
+\begin{figure}
+  \includesvg[width=1\columnwidth]{figures/improvements.svg}
+  \caption{Fraction of improvement in total scan time over a scan with
+    512 lines vs scan rate for the three sets of CS scans (at 25\%,
+    15\% and 12.5\%) and courser raster scans at 128 and 64 lines.}
+  \label{fig:improve_512}
 \end{figure}
-
-Where CS seems to really shine is if we look at the RDI for a given time or scan
-rate. This is plotted in Fig.~\ref{fig:time_damage}. For example, the 10~Hz
-raster scan, which takes about 51 seconds, gives an RDI of 23.7. All of the CS
-scans, except for the 15\% scan at 1~Hz (which is only 0.9 seconds longer) are
-faster than the 10~Hz raster scan, yet have much lower RDI values, ranging from
-1.21 to 13.13. Unsurprisingly, the relationship between scan speed and RDI is
-quite linear. For the raster scans, the left panel of Fig.~\ref{fig:time_damage}
-just plots the inverse relationship of the right panel, since scan time is
-inversely proportional to raster frequency. This is not quite the case for the
-CS scans due to the sub-sampling and the fixed overhead which does not scale
-with scan rate (e.g., the amount of time for the $XY$-move etc remains
-essentially constant for a given scan density).
-
-What is surprising is that for the same scan rate, the CS scans have a lower RDI
-than a raster scan at the same rate. One possibility is that the probability
-that a given $\mu$-path will start on the flat portion of the grating, scan
-\textit{into} a hole and then the tip withdraws before exiting the hole is
-higher than the probability that a scan starts in a hole and exits the hole.
-This would result in a lower RDI, because scanning \textit{out} of hole is what
-the RDI penalizes.
-
-From the left panel of Fig.~\ref{fig:time_damage}, we see that for a fixed RDI,
-CS has a faster imaging acquisition rate. The amount of improvement is best if
-we need a very low RDI: for example, if we want to hold the RDI below 2, then we
-have to take the 1~Hz raster scan (512 seconds) while we can achieve the same
-RDI via CS in about 52 seconds with the 15\% sampling, which is a speed
-improvement of nearly 10. The higher of an RDI we are willing to tolerate, the
-advantage of CS over raster narrows. For example, the 4~Hz raster scan and 5~Hz,
-15\% CS scan have comparable RDI, but now CS is only about 6 times faster. This
-is a result of the constant overhead imposed by the engage/disengage and
-$XY$-move states in CS.
 
@@
 %   \includesvg[width=1\columnwidth]{figures/subline_vs_cs.svg}
-%   \caption{(left) A 128 line raster scan interpolated onto 512 lines. (right) The CS scan with the nearest time.}
+%   \caption{(left) A 128 line raster scan interpolated onto 512
+%   lines. (right) The CS scan with the nearest time.}
 %   \label{fig:subline}
@@
 \section{Conclusions}\label{sec:conclusions}
-The main conclusion of this chapter is that with CS, it seems that we can
-acquire images faster yet (putatively) with less specimen damage than is
-possible with raster scanning, which we showed by introducing a new metric, the
-RDI. Of course, a natural criticism is that we did not validate the RDI against
-delicate specimens. We leave this as an area for future work.
+The main conclusion of this chapter is that with CS, it seems that we
+can acquire images faster yet (putatively) with less specimen damage
+than is possible with raster scanning, which we showed by introducing
+a new metric, the RDI. Of course, a natural criticism is that we did
+not validate the RDI against delicate specimens. We leave this as an
+area for future work.
 

### 2019-06-17 plot_baseline_raster_analysis_1Hz.m

@@ -86,6 +86,11 @@ modes = [false, true];
 F = mkfig(3000, 3.5, 3.5); clf
 [ha, pos] = tight_subplot(2, 2, [.02, .01 ], [.027, 0.055], .005);
 ha = reshape(ha', 2, [])';
+
+F6 = mkfig(3002, 3.5, 3.5/2); clf
+[ha6, pos] = tight_subplot(1, 2, [.02, .01 ], [.027, 0.055], .005);
+
+
 clc
 suffix = {'NoAlgn', 'Algn'}
 names = {'one2two', 'one2six'};
@@ -122,23 +127,28 @@ for j=1:2
 %     fprintf("%s: 'PSNR=%.2f, SSIM=%.2f'\n", stit, psn_1k, ssm_1k);
     ime=imk_slice - im1_ontok_fit; %, 'parent', h(k), 'Scaling', 'joint')
     ime = ime-mean(ime(:));
-    imagesc(ha(j, k), ime, [-2*thresh, thresh*2]); %, [-0.5*thresh, 0.5*thresh]);
+    imagesc(ha(j, k), ime, [-thresh, thresh]); %, [-0.5*thresh, 0.5*thresh]);
     colormap('gray')
     
     set(ha(j, k), 'YTick', [], 'XTick', [])
     if j == 1
         title(ha(j, k), stit)
     end
+    
+    if k==2
+        imagesc(ha6(j), ime, [-thresh, thresh]);
+        colormap('gray')
+        set(ha6(j), 'YTick', [], 'XTick', [])
+    end
   end
 
-  set(ha(end), 'Visible', 'off');
+%   set(ha(end), 'Visible', 'off');
 
 end
-%%
-data_writer({ST}, 'latex/baseline_errors.txt', '%.2g')
 
-%%
+data_writer({ST}, 'latex/baseline_errors.txt', '%.2g')
 save_fig(F, 'latex/figures/baseline_errors_aligned_1Hz', false)
+save_fig(F6, 'latex/figures/baseline_errors_1and6', false)
 
 
 %%

### 2019-06-17 plot_cs_cycle.m

@@ -62,9 +62,9 @@ Fig = mkfig(100, 3.5, 4); clf
 ha = tight_subplot(4, 1, [.05, .05], [0.075, .03], [.15, .03], false);
 
 
-tstart = 7.4;
+tstart = 7.25;
 CS_idx1 = cs_exps{1}.find_cycle_idx(tstart);
-CS_idx2 = CS_idx1 + 1;
+CS_idx2 = CS_idx1 + 2;
 
 %
 % The Bad Case
@@ -73,11 +73,11 @@ state_names = {'move', 'tdown', 'tsettle', 'scan', 'tup'};
 
 % The Good Case
 traj_names = {'y', 'x', 'uz', 'ze'};
-names = {'$Y$ [$\mu$m]', '$X$ [$\mu$m]', '$u_Z [nm]$', 'deflection [v]'};
+names = {'$Y$ [$\mu$m]', '$X$ [$\mu$m]', '$u_Z$ [nm]', 'deflection [v]'};
 
 
 
-xlm1 = [7.362, 7.5];
+xlm1 = [7.286, 7.434];
 hands = gobjects(length(state_names), 1);
 for j=1:length(traj_names)
   h_j = ha(j);
@@ -106,8 +106,6 @@ ylim(ha(2), [0, 5]);
 ylim(ha(3), [-20, 90])
 
 
-leg = legend(hands, 'NumColumns', 2, 'Position', [0.4071 0.6322 0.5624 0.1030]);
+leg = legend(hands, 'NumColumns', 1, 'Position', [0.6709 0.5861 0.2993 0.1656]);
 %%
-
-
 save_fig(Fig, 'latex/figures/cs_cycle', false)

### 2019-06-17 plot_with_without_FF_loop_cs20ngflat.m

@@ -56,7 +56,7 @@ if 0
 end
 
 width = 3.5;
-height = 3.8;
+height = 2.5;
 F5 = mkfig(25, width, height); clf
 margh = [0.1, 0.02];
 margw = [0.105, 0.05];

### 2019-06-17 plot_z_axis_control_design.m

@@ -35,13 +35,13 @@ Hyr_old = feedback(D_ki_old*G_frf, 1);
 Hyr_noinv = feedback(D_ki*dat.K*G_frf, 1);
 
 
-F2 = mkfig(2, 3.48, 2); clf
-[ha, pos] = tight_subplot(1, 1, [.02, .01 ], [.165, 0.03], [.12, .02]);
+F2 = mkfig(2, 3.48, 1.8); clf
+[ha, pos] = tight_subplot(1, 1, [.02, .01 ], [.165, 0.03], [.1, .02]);
 
 
-h1 = frf_bode_mag(Loop, ss_data.freq_s, ha, 'Hz', 'Color', [0.35, 0.75, 0.93], 'LineWidth', 1.2);
-h2 = frf_bode_mag(G_frf, ss_data.freq_s, ha, 'Hz', '-k', 'LineWidth', 1.2);
-h4 = frf_bode_mag(Hyr, ss_data.freq_s, ha, 'Hz', '-r', 'LineWidth', 1.2);
+h1 = frf_bode_mag(Loop, ss_data.freq_s, ha, 'Hz', ':b');
+h2 = frf_bode_mag(G_frf, ss_data.freq_s, ha, 'Hz', '-k'); %, 'LineWidth', 1.1);
+h4 = frf_bode_mag(Hyr, ss_data.freq_s, ha, 'Hz', '-.r'); % 'LineWidth', 1.1);
 
 ylim(ha(1), [-40, 20]);
 
@@ -49,8 +49,8 @@ h1.DisplayName = 'Loop gain';
 h2.DisplayName = '$G_{Z_d,u_Z}$';
 h4.DisplayName = '$H_{Z_d, r_{Z}}$ ';
 leg = legend([h1, h2, h4]);
-
-set(leg, 'Location', 'southwest', 'FontSize', 10);
+set(ha, 'FontSize', 8)
+set(leg, 'Location', 'southwest', 'FontSize', 8);
 
 % [pm, gm] = margin(Loop)
 save_fig(F2, fullfile(PATHS.tmech_fig(), 'z_control_design'), false);

### 2019-06-19 plot_baseline_raster_analysis_1Hz.m
Adjust saved precision.

@@ -146,7 +146,7 @@ for j=1:2
 
 end
 
-data_writer({ST}, 'latex/baseline_errors.txt', '%.2g')
+data_writer({ST}, 'latex/baseline_errors.txt', '%.2f')
 save_fig(F, 'latex/figures/baseline_errors_aligned_1Hz', false)
 save_fig(F6, 'latex/figures/baseline_errors_1and6', false)
 

### 2019-06-19 process_data_6_5_2019.m
Need to put the union of rates in the metrics fig pseudo legend.

@@ -43,62 +43,64 @@ for k=1:length(raster_files)
 end
 fprintf('finished loading raster data\n')
 
-if 1
-    target_pix = 512;
-    use_ze = false;
-    % last image is 128 pixels
-    x1s = [36,   27,  27,  27,  27, 27, 6*4];
-    x2s = [493, 493, 493, 495, 494, 494, 122*4];
-    figbase = 10;
-    for k=1:length(rast_exps)
-        rast_exps{k}.uz = log_creep_detrend(rast_exps{k}.uz, []);
+%%
+target_pix = 512;
+use_ze = false;
+% last image is 128 pixels
+x1s = [36,   27,  27,  27,  27, 27, 6*4];
+x2s = [493, 493, 493, 495, 494, 494, 122*4];
+figbase = 10;
+for k=1:length(rast_exps)
+    rast_exps{k}.uz = log_creep_detrend(rast_exps{k}.uz, []);
+    
+    if rast_exps{k}.npix_y_og ~= target_pix
+        rast_exps{k}.bin_raster_really_slow([], use_ze, target_pix);
+        rast_exps{k}.bin_raster_really_slow([], true, target_pix);
+        rast_exps{k}.interp_y(target_pix, true);
+        stit = sprintf('(raster %.1f sec) interpolated from %d pix %.2f Hz',...
+            length(rast_exps{k}.ze)*AFM.Ts, rast_exps{k}.npix_y_og,...
+            rast_exps{k}.meta_in.raster_freq);
         
-        if rast_exps{k}.npix_y_og ~= target_pix
-            rast_exps{k}.bin_raster_really_slow([], use_ze, target_pix);
-            rast_exps{k}.bin_raster_really_slow([], true, target_pix);
-            rast_exps{k}.interp_y(target_pix, true);
-            stit = sprintf('(raster %.1f sec) interpolated from %d pix %.2f Hz',...
-                length(rast_exps{k}.ze)*AFM.Ts, rast_exps{k}.npix_y_og,...
-                rast_exps{k}.meta_in.raster_freq);
-            
-        else
-            rast_exps{k}.bin_raster_really_slow([], use_ze);
-            rast_exps{k}.bin_raster_really_slow([], true);
[…]

### 2019-06-19 latex/afm-cs-main.tex
Update plots; edit documents.

@@
 reconstruction with continuous scanning to reduce the number of tip
-engagements. %Though the pattern is motivated from CS, it also works well in practice for inpainting reconstruction \cite{luo2015comparison}.
-\todo{Would be beneficial to shrink intro, if possible}
-
+engagements.
+
+\textbf{Contributions}
 Our previous work on the $\mu$-path pattern using theoretical
@@
 
-\textbf{Contributions} Much of the prior work on undersampled AFM
+Much of the prior work on undersampled AFM
 images is based purely on simulations \cite{han_optimal_2018,
   Luo_nano_2015, oxvig_structure_2017, jensen_reconstruction_2013,
-  maxwell_acc_2014, Chen_2012jx}.
-
+  maxwell_acc_2014, Chen_2012jx} and consequently, there is little discussion of the physical practicality of the proposed methods.
+For example, most estimates of the potential time savings of sub-sampling techniques are not informed by experiments.
+Often, a discussion of the harmonic content of the proposed reference signals is typically neglected \cite{luo_continuous_2019, Chen_2012jx,han_optimal_2018}, even though this is a critical concern in AFM.
+As we show in Section~\ref{sec:control}, the discontinuous nature of the $\mu$-path pattern essentially requires that the control system be to filter the higher frequency content of the step inputs between $\mu$-paths.
+
+Despite this, we show in Section~\ref{sec:results} that $\mu$-path scanning provides a non-trivial speed increase compared to a full quality raster scan. 
 % % ------------------ TKTKTKT ------------------
@@
 took a sequence of 6 raster scans of a sample grating, each at a 1~Hz
-scan rate over a 5 micron by 5 micron area. The top row of
+scan rate over a 5 micron by 5 micron area. The left image of
 Fig.~\ref{fig:baseline_errors} shows the error between the first and
-second image and the first and 6th image. The PSNR and SSIM between
-images one and six are \baseline{one2twoNoAlgnPsnr} and
-\baseline{one2twoNoAlgnSsim}; between images one and six they are
+ sixth image. The PSNR and SSIM between
+images the first and second images are \baseline{one2twoNoAlgnPsnr} and
+\baseline{one2twoNoAlgnSsim}; between the first and sixth are
 \baseline{one2sixNoAlgnPsnr} and \baseline{one2sixNoAlgnSsim},
@@
 the offset in the other image that produces the smallest error. The
-result of this procedure are shown in the bottom row of
+result of this procedure are shown in the right image of
 Fig.~\ref{fig:baseline_errors}.
-% Taking the first scan as the master, we compute the PSNR and SSIM
-% metrics. The best PSNR here is 16.57 and the worst is 9.02. The best
-% SSIM is 0.54 and the worst is 0.28.
 Although the situation is improved compared to the un-aligned images,
-there is still noticeable stretching, particularly in the
-$Y$-direction. Notably, with the alignment technique, the SSIM is
-\baseline{one2twoAlgnSsim} for images one and two, and
-\baseline{one2sixAlgnSsim} for images one and six; the PSNR is
-\baseline{one2twoAlgnPsnr} and \baseline{one2sixAlgnPsnr}
+there is still noticeable stretching (the upper and lower portions appear considerably worse than the middle). Notably however, with the alignment technique, the SSIM is
+\baseline{one2twoAlgnSsim} for both sets of images and
+while the PSNR is increases to \baseline{one2twoAlgnPsnr} and \baseline{one2sixAlgnPsnr}
 respectively.
@@
   \includesvg[width=0.7\columnwidth]{figures/baseline_errors_1and6.svg}
-  \caption{Errors between the first and second (left column) and first
-    and sixth (right column) raster scans in a sequence of six 1.0~Hz
-    raster scans. (top) Errors without alignment (bottom) The same
+  \caption{Errors between the first and sixth raster scans in a sequence of six 1.0~Hz
+    raster scans. (left) Errors without alignment (right) The same
     data but aligned via cross correlation.}
@@
 \subsection{A new metric}
-% \begin{figure}[t!]
-%   \centering
-%   \includesvg[width=1\columnwidth]{figures/damage_illustration.svg}
-%   \caption{The RDI metric defined in \eqref{eqn:RDI} penalizes
-%   everything in the red shaded region and does not penalize anything
-%   in the un-shaded region.}
-%   \label{fig:damage_illustrate}
-% \end{figure}
-
-% Th PSNR and SSIM metrics only assess the similarity of two images.
-% However, in AFM imaging, pure image quality is not the only concern,
-% particularly for delicate samples. What is needed is a figure of
-% merit for how much damage was done to specimen during the imaging
-% process. While this is not really a concern while imaging a hard
-% calibration grating, it plays a prominent role biological
-% samples~\cite{ando_highspeed_2008}. In general, damage occurs while
-% scanning into an uphill region, which results in a positive
-% deflection signal. The actual damage done by a given $Z_d$ will
-% depend on the spring constant of the cantilever and the softness of
-% the specimen. Nonetheless, we can use the positive deviations of
-% $Z_d$ as a relative measure of damage between different scan speeds
-% or scanning methods, for a given cantilever and specimen. This
-% motivates a metric we term the relative damage index (RDI), which we
-% define as
-% \begin{align}
-%   \text{RDI} &= \frac{1}{T_s}\sum_{k\in I} \frac{1}{k} \left(Z_{d,k} - r_{Z,s}\right)^2 \label{eqn:RDI}\\
-%   I &= \{k: k\in[0,~N-1],~ Z_{d,k}-r_{Z,s} > 0 \} \nonumber
-% \end{align}
-% where $N$ is the total number of samples in a given scan, $Z_{d,k}$
-% is the deflection signal at sample $k$ and $r_{Z,\textrm{s}}$ is the
-% scanning setpoint. The RDI is basically the power in positive
-% deflection. By excluding negative values of the deflection, we do
-% not penalize the CS algorithm while it is re-engaging with the
-% specimen \emph{unless} it overshoots the scanning setpoint, which we
-% do want to penalize. This is illustrated in
-% Fig.~\ref{fig:damage_illustrate}, which shows several CS cycles with
-% a poorly tuned controller. Only deflection signals in the red-shaded
-% region will be penalized by the RDI.
+Th PSNR and SSIM metrics only assess the similarity of two images.
+However, in AFM imaging, pure image quality is not the only concern,
+particularly for delicate samples. What is needed is a figure of
+merit for how much damage was done to specimen during the imaging
+process. While damage to the specimen is not really a concern while imaging a hard
+calibration grating, it plays a prominent role for biological
+samples~\cite{ando_highspeed_2008}, though damage to the probe itself is still a concern.
+In general, the faster the scan rate,
+the more difficulty the $Z$-axis control
+will have following the sample surface,
+which results in a larger $Z_d$ over more time. 
+The actual damage done by a given $Z_d$ will
+depend on the spring constant of the cantilever and the softness of
+the specimen. Nonetheless, we propose a metric, which we call the Relative Damage Index (RDI)
+which computes the power in the deflection signal for a given scan. That is,
+
+\begin{align}
+  \text{RDI} &= \frac{1}{T_s}\sum_{k=0}^N \frac{1}{k} \left(Z_{d,k} - r_{Z,s}\right)^2 \label{eqn:RDI}\\
+\end{align}
+The idea behind the RDI is that increased scan rates lead to larger
+deflection signals (and thereby increased force into the specimen) at
+each surface feature, which the RDI accumulates.
 
@@
 We compared $\mu$-path scanning to two scenarios. First, we compare it
-to full resolution raster scans at several scan rates. Second we
-compare to course raster scans.
-% For both comparisons, we use the same set of $\mu$-path scans.
-
-\subsection{Comparison to full raster}
+to full resolution raster scans at several scan rates in Section~\ref{sec:cp_full}.
+Second we compare to course raster scans in Section \ref{sec:cp_subline}.
+
+\subsection{Comparison to full raster}\label{sec:cp_full}
 We took scans of a Ted Pella CS-20NG sample grating over an area with
@@
 raster scans, we took scans at 1.0~Hz, 2.5~Hz, 5.0~Hz, 8.0~Hz and
-10~Hz. We also took $\mu$-path scans with densities at 12.5\%, 15\%
-and 25\% and reconstructed 512 by 512 pixel images. The CS scans we
+10~Hz. We also took $\mu$-path scans with densities at 12.5\%,
+and 25\% and reconstructed 512 by 512 pixel images. The CS scans were
 taken with scan velocities equivalent to raster scan rates of 1.0~Hz,
@@
 The free value of the deflections signal was approximately -0.6 volts
-and we set the scanning reference to ${\rzs=\scanD{spScan}}$~volts and
-the withdraw reference to ${\rzup=\scanD{spMv}}$ volts. We set the
+and we set the scanning reference to ${\rzs=\scanD{spScan}}$~volts (for both raster and CS)
+and the withdraw reference to ${\rzup=\scanD{spMv}}$ volts. We set the
 $XY$-settle boundary to $\pm \scanD{xyBoundaryMic}$ microns and
@@
 moving to the $Z$-engage state. The pre-scan length was
-$\scanD{preScanSamples}$ time steps. The cantilever was an Budget
+$\scanD{preScanSamples}$ time steps. The cantilever was a Budget
 Sensors ContAI-G, with a nominal length of 450 microns and spring
@@
 The CS scans were reconstructed with BPVV. We set
-${\sigma = \scanD{sigma}}$, ${\mu_f=\scanD{muf}}$,
-${\alpha_v=\scanD{alpv}}$ and ${\alpha_h=\scanD{alph}}$. The data
-remained scaled in terms of volts.
-
+${\alpha_v=\scanD{alpv}}$ and ${\alpha_h=\scanD{alph}}$. 
 For the raster scans, we discard data from the re-trace and divided
@@
 This step eases comparison with the CS scans and was inspired by a
-feature in \texttt{SPIW} \cite{spiw}.
-
-As a final step, we subtract the mean from each CS and raster image,
-so that they can all be mapped to the same color intensity in the
-images. The color maps represent a range of $\pm$20 nm.
-
-The resulting images are shown in Fig.~\ref{fig:resultsF1_images}. The
+feature in the AFM image processing toolbox \texttt{SPIW} \cite{spiw}.
+The resulting images are shown in Fig.~\ref{fig:resultsF1_images}.
+The color maps represent a range of $\pm$20 nm. The
 rows of pixels indicated by the red lines are shown as cross sections
 Fig.~\ref{fig:pixel_rows}.
-
-For each raster scan and each CS scan, we computed the SSIM, PSNR
-(both with default parameters) using the 1~Hz scan as the master and
-also computed the RDI metric. These are collected in table
-~\ref{tab:rast_vs_cs_v1}.
 
@@
 %   \begin{tabular}{cccccc}
-%     \input{tables/cs_raster_table_4-26-2019_muInf_dct2.tex}
+%     \input{tables/cs_raster_table_6-5-2019_muInf_dct2.tex}
 %   \end{tabular}
@@
 \end{figure}
-
+For each raster scan and each CS scan, we computed the SSIM and PSNR
+ using the 1~Hz scan as the master and
+also computed the RDI metric. These are plotted against total acquisition time
+in Fig.~\ref{fig:time_ssim} and ~\ref{fig:time_psnr}.
 Unfortunately, the SSIM and PSNR metrics are not particularly
-illuminating. It is easiest to see this by plotting PSNR and SSIM
-against total acquisition time, which is shown in
-Fig.~\ref{fig:time_ssim} and ~\ref{fig:time_psnr}. There are several
-inconsistencies. First, the 4~Hz raster scan has the lowest PSNR of
-all the raster scans, while the 8~Hz scan has the highest. Second, all
-of the 15\% CS scans except the 8~Hz version have as good or better
-SSIM numbers than the raster scans. It makes no sense for a CS scan at
-a 5~Hz rate to have better quality than a raster scan at a 5~Hz rate.
-
-Fig.~\ref{fig:improve_512} shows amount of improvement of the
-different sub-sampling techniques over full raster scans with 512
-lines as a function of scan rate. As far as pure speed goes, the CS
-scan at 12.5\% is the fastest for a rate of 1~Hz, though the 64 line
-raster scan is close. At the same time, the image quality of the 1~Hz,
-12.5\% CS scan is better than the the 1~Hz 64 line raster scan.
-However, this advantage quickly evaporates for faster scan rates.
-Indeed, for rates beyond about 5~Hz, the raster scan with 128 lines is
-not only faster than the 12.5\% CS scan, it also has (arguably) better
-image quality.
-
-Thus, we conclude that $\mu$-path based sub-sampling is only
-beneficial when there is an exigent reason to scan slowly. This may be
-the case for delicate specimens. We can roughly quantify this by
-computing the power in the deflection signal during scanning
-\begin{align}
-  \text{RDI} &= \frac{1}{T_s}\sum_{k=0}^N \frac{1}{k} \left(Z_{d,k} - r_{Z,s}\right)^2 \label{eqn:RDI}\\
-\end{align}
-The idea behind the idea is that increased scan rates lead to larger
-deflection signals (and thereby increased force into the specimen) at
-each surface feature, which the RDI accumulates.
-
-The values of the RDI for each of the $\mu$-path and raster scans are
-shown in Fig.~\ref{fig:time_damage} as a function of total imaging
-time. As one would expect, as imaging time decreases, the RDI for each
-scan type increases.
+illuminating. There are several inconsistencies. For example, it makes no sense
+the 1 Hz CS scan at 25\% has a \emph{worse} PSNR and SSIM than 5 Hz version;
+nor does it make sense that the 8~Hz full raster scan has a worse SSIM and PSNR than
+the 10~Hz full raster scan.
 
@@
     total acquisition time.}
-  % \label{fig:time_vs_metrics}
+  \label{fig:time_vs_metrics}
 \end{figure*}
 
-Where CS seems to really shine is if we look at the RDI for a given
-time or scan rate. This is plotted in Fig.~\ref{fig:time_damage}. For
-example, the 10~Hz raster scan, which takes about 51 seconds, gives an
-RDI of 23.7. All of the CS scans, except for the 15\% scan at 1~Hz
-(which is only 0.9 seconds longer) are faster than the 10~Hz raster
-scan, yet have much lower RDI values, ranging from 1.21 to 13.13.
-Unsurprisingly, the relationship between scan speed and RDI is quite
-linear. For the raster scans, the left panel of
-Fig.~\ref{fig:time_damage} just plots the inverse relationship of the
-right panel, since scan time is inversely proportional to raster
-frequency. This is not quite the case for the CS scans due to the
-sub-sampling and the fixed overhead which does not scale with scan
-rate (e.g., the amount of time for the $XY$-move etc remains
-essentially constant for a given scan density).
-
-From the left panel of Fig.~\ref{fig:time_damage}, we see that for a
+Things are clearer if we plot the RDI for each scan against total acquisition time, which is
+shown inf Fig.~\ref{fig:time_damage} and 
+this is where CS seems to shine.
+This is plotted in Fig.~\ref{fig:time_damage}.
+As one would expect, as imaging time decreases, the RDI for each
+scan type increases. 
+From Fig.~\ref{fig:time_damage}, we see that for a
 fixed RDI, CS has a faster imaging acquisition rate. The amount of
@@
 
-% More importantly though,
-\subsection{Comparison to Sub-line Sampling}
-Perhaps the simplest alternative to $\mu$-path sampling is to simply
+\subsection{Comparison to Sub-line Sampling} \label{sec:cp_subline}
+ Many of sub-line sampling papers assume
+that the lines to sample are selected randomly \cite{han_optimal_2018,
+  Luo_nano_2015}. An even simpler alternative to
+$\mu$-path sampling is to simply 
 take a standard raster scan with fewer lines. This is the technique we
-consider in this subsection. Many of sub-line sampling papers assume
-that the lines to sample are selected randomly \cite{han_optimal_2018,
-  Luo_nano_2015}. In contrast, we take an even simpler approach scan
-every 4th and every 8th line. This yields images with 128 and 64 lines
-respectively. For each of these scenarios, we first divide the data
+consider in this subsection, by scanning images with 
+ 128 and 64 lines. For each of these scenarios, we first divide the data
 for each line into 512 bins. This gives an image that is 128 (resp.,
@@
 scan obscure the defect.
+
+Fig.~\ref{fig:improve_512} shows the amount of improvement of the
+different sub-sampling techniques over full raster scans with 512
+lines as a function of scan rate. As far as pure speed goes, the CS
+scan at 12.5\% is the fastest for a rate of 1~Hz, though the 64 line
+raster scan is close. At the same time, the image quality of the 1~Hz,
+12.5\% CS scan is better than the the 1~Hz 64 line raster scan.
+However, this advantage quickly evaporates for faster scan rates.
+Indeed, for rates beyond about 5~Hz, the raster scan with 128 lines is
+not only faster than the 12.5\% CS scan, it also has (arguably) better
+image quality.
 
@@
 can acquire images faster yet (putatively) with less specimen damage
-than is possible with raster scanning, which we showed by introducing
-a new metric, the RDI. Of course, a natural criticism is that we did
-not validate the RDI against delicate specimens. We leave this as an
-area for future work.
+than is possible while raster scanning a full image.
+On the other hand, it appears that reconstructing a course raster scan makes more sense for faster scan rates.
+This is notable, since a course raster scan only requires an additional step in post-processing.
+It remains to be seen if this conclusion holds for a wide range of instruments.
 

### 2019-06-19 latex/afm-cs-main.tex
Final touches before sean and lucy see it.

@@
 \title{Improving the Image Acquisition Rate of an Atomic Force
-  Microscope Through Compressive Sampling}
+  Microscope Through Sub-sampling and Reconstruction}
 
@@
 and materials science
-\cite{Dufrene:2017gm,Yang:2017im,Payton:2016hj,Altman:2015ic,Haase:2015eh}
+\cite{Dufrene:2017gm,Yang:2017im,Payton:2016hj,Altman:2015ic,Haase:2015eh}.
 
@@
 engaged with the surface to collect a measurement, lifted and moved to
-the new location, and engaged again. Because the re-engagement process
+the new location, and engaged again.
+Because the re-engagement process
 is typically slow, this can lead to excessively long image acquisition
 times and negate the gains from undersampling \cite{andersson2012non}.
-One discrete undersampling scheme, called a $\mu$-path pattern, was
-proposed in \cite{maxwell2014compressed} to improve sampling
-efficiency. The $\mu$-path pattern consists of randomly placed short,
-horizontal scans (see Fig.~\ref{fig:mu_mask} for one such pattern) and
-is designed to balance the randomness needed to ensure good
-reconstruction with continuous scanning to reduce the number of tip
-engagements.
-
-\textbf{Contributions}
+In \cite{maxwell2014compressed}, we introduced a discrete undersampling scheme,
+called a $\mu$-path pattern, which consists of short randomly placed,
+horizontal scans (see Fig.~\ref{fig:mu_mask} for one such pattern). It
+is designed to balance the randomness needed (to ensure good
+reconstruction) with continuous scanning (to reduce the number of tip
+engagements).
+
 Our previous work on the $\mu$-path pattern using theoretical
 calculations, simulations, and a preliminary implementation,
-demonstrates that the approach can achieve significant scanning time
+demonstrates that the approach can achieve scanning time
 reduction while maintaining faithful image reconstruction
-\cite{maxwell2014compressed,Luo:2015tu, braker_hardware_2018}. This
-paper builds upon that earlier work in several significant ways.
-
-Much of the prior work on undersampled AFM
-images is based purely on simulations \cite{han_optimal_2018,
-  Luo_nano_2015, oxvig_structure_2017, jensen_reconstruction_2013,
-  maxwell_acc_2014, Chen_2012jx} and consequently, there is little discussion of the physical practicality of the proposed methods.
-For example, most estimates of the potential time savings of sub-sampling techniques are not informed by experiments.
-Often, a discussion of the harmonic content of the proposed reference signals is typically neglected \cite{luo_continuous_2019, Chen_2012jx,han_optimal_2018}, even though this is a critical concern in AFM.
-As we show in Section~\ref{sec:control}, the discontinuous nature of the $\mu$-path pattern essentially requires that the control system be to filter the higher frequency content of the step inputs between $\mu$-paths.
-
-Despite this, we show in Section~\ref{sec:results} that $\mu$-path scanning provides a non-trivial speed increase compared to a full quality raster scan. 
-% % ------------------ TKTKTKT ------------------
-% \todo{Strike this?} First, we demonstrate performance using both
-% randomly-placed $\mu-$paths and designed $\mu-$paths that are
-% optimized to minimize the expected reconstruction error given some
-% initial estimate of the frequency structure of the sample. These
-% schemes are described in Sec. \ref{sec:samplingScheme}.
-% % --------------------------
-We also introduce a new reconstruction algorithm which is designed to
+\cite{maxwell2014compressed,Luo:2015tu, braker_hardware_2018}. 
+The main contributions of this paper relative to that past work are:
+\begin{itemize}
+\item We introduce a new reconstruction algorithm which is designed to
 minimize the artifacts arising from the structure of the $\mu$-path
 scanning pattern. This algorithm is described and compared to existing
-reconstruction methods through simulations in Sec.
-\ref{sec:reconstructionMethods}. Section \ref{sec:control} describes
-improvements to the control algorithms compared to our preliminary
-implementation in ~\cite{braker_hardware_2018}. We then demonstrate
-the entire scheme from sampling through reconstruction using
-experiments on a commercial AFM (Agilent 5500). The experimental setup
-and implementation details are described in Secs.
-\ref{sec:experimentalSetup} and \ref{sec:implementation}\footnote{The
-  software portion of the implementation and image reconstruction
-  described in this paper can be found at
-  \url{https://github.com/rabraker/AFM_CS}}. Experimental results are
-provided in Sec. \ref{sec:results}. Finally, we provide a few
-concluding remarks in Sec. \ref{sec:conclusions}.
+reconstruction methods through simulations in Sec. \ref{sec:reconstructionMethods}.
+\item In our prior experimental prototype, \cite{braker_hardware_2018} we used very basic integral controllers for all three axes for both raster and $\mu$-path scans.
+Here, we design compensators for each axis using standard loop-shaping techniques (Sec.~\ref{sec:control}), which result in a substantial increase in closed-loop bandwidth (e.g., 50 Hz to 450~Hz for the $Z$-axis).
+We show in Sec.~\ref{sec:ff_control} that one of the limitations of $\mu$-path scanning is the discontinuous $X$-axis reference (e.g., in moving between $\mu$-paths) which excites the cross-coupling modes between the $X$ and $Z$ axes, an affect which neither our prior experimental work nor the numerous simulation studies have accounted for.
+We mitigate the cross coupling with a feed-forward design.
+\item We experimentally compare (Sec.
+\ref{sec:results}) $\mu$-path scanning to not only full density raster scans but also to course raster scans which are interpolated to a full image.
+This is in contrast to typical sub-line sampling which takes scan lines at random.
+The clear advantage to a course raster scan is that it requires no modification to the instrument, only to the post-processing.
+\item The bulk of this work is based on experiment, not simulation, in contrast to prior work by ourselves \cite{Luo_nano_2015,maxwell_acc_2014} and others \cite{han_optimal_2018,jensen_reconstruction_2013,oxvig_structure_2017}.
+Our main focus here is on delineating the practical issues which must be addressed to effectively realize $\mu$-path scanning, which has only seen limited attention in the past.
+\end{itemize}
 
@@
   \centering
-  \includegraphics[width=0.7\columnwidth]{figures-SBA/random_mask.pdf}
+  \includegraphics[width=0.65\columnwidth]{figures-SBA/random_mask.pdf}
   \caption{An example of the horizontal $\mu$-path sampling pattern
@@
 % =========================================================================
-\subsection{Reconstruction methods}
+\section{Reconstruction methods}
 \label{sec:reconstructionMethods}
@@
 \noindent where $y\in\mathbb{R}^m$ is the observation vector, $R$ is
-an $n\times m$ matrix defining the measurements, $U$ is an $m\times m$
+an $m\times n$ matrix defining the measurements, $U$ is an $n\times n$
 sparsity basis and $\eta$ is the sparse representation of $x$ in the
-domain of $U$. In general, $n\ll m$. In an imaging application, where
+domain of $U$. In general, $m\ll n$. In an imaging application, where
 the underlying signal is a matrix $X\in\mathbb{R}^{h\times s}$, we
@@
 
-In the AFM application, the probe can only measure a single pixel at a
-time. Thus the rows of $R$ are a subset of the rows of an $m$ by $m$
-identity matrix. Ideally, the sparsity basis and the measurement
-matrix $R$ will have a low \textit{mutual coherence}, a measure that
-describes how each of the rows of $R$ (the measurements) ``spreads
-out'' in the domain of $U$ \cite{candes2007sparsity}. In the
-following, we assume that $U^TU=I$, though in the simulation and
-experimental results, we take $U^T$ as the Discrete Cosine Transform
-(DCT). The DCT basis generally keeps a good balance between achieving
-a low mutual coherence between $U$ and the $\mu$-path sensing matrices
-$R$ and providing a high sparsity for typical AFM sample images.
-
-Basis pursuit with denoising (BPDN) is one common realization of the
-CS-based reconstruction problem, and is given by the optimization
-\begin{equation}
-  \min_{x} \left \| U^Tx \right \|_1 \quad
-  \text{s.t.}\quad x\in Q_p = \{x:~\|Rx - y\|_2 < \sigma\} \label{op:bp}
-\end{equation}
-where $\sigma$ represents uncertainty in the measurements. BPDN
-essentially searches for the sparsest signal from all the candidates
-that match the measurements.
-
-Although BPDN is effective in the general setting, using it for
-reconstruction from horizontal $\mu$-path samples often yields
-artifacts in the vertical direction (that is, the direction orthogonal
-to the $\mu$-path scans) leading to strong discontinuities in the
-image. These artifacts grow more prominent as the length of the
-$\mu$-paths is increased \cite{maxwell2014compressed}, because these
-longer paths lead to increased mutual coherence between the
-measurement matrix $R$ and the sparsity basis $U$. However, longer
-$\mu$-paths means fewer $\mu$-paths and thus shorter scan times.
 \noindent
@@
 
+In the AFM application, the probe can only measure a single pixel at a
+time. Thus the rows of $R$ are a subset of the rows of an $n$ by $n$
+identity matrix. Ideally, the sparsity basis and the measurement
+matrix $R$ will have a low \textit{mutual coherence}, a measure of
+how each of the rows of $R$ (the measurements) ``spreads
+out'' in the domain of $U$ \cite{candes2007sparsity}. In the
+following, we assume that $U^TU=I$, though in the simulation and
+experimental results, we take $U^T$ as the Discrete Cosine Transform
+(DCT). The DCT basis generally keeps a good balance between achieving
+a low mutual coherence between $U$ and the $\mu$-path sensing matrices
+$R$ and providing a high sparsity for typical AFM sample images.
+
+Basis pursuit with denoising (BPDN) is one common realization of the
+CS-based reconstruction problem, and is given by the optimization
+\begin{equation}
+  \min_{x} \left \| U^Tx \right \|_1 \quad
+  \text{s.t.}\quad x\in Q_p = \{x:~\|Rx - y\|_2 < \sigma\} \label{op:bp}
+\end{equation}
+where $\sigma$ represents uncertainty in the measurements. BPDN
+essentially searches for the sparsest signal from all the candidates
+that match the measurements.
+
+Although BPDN is effective in the general setting, using it for
+reconstruction from horizontal $\mu$-path samples often yields
+artifacts in the vertical direction (that is, the direction orthogonal
+to the $\mu$-path scans) leading to strong discontinuities in the
+image. These artifacts grow more prominent as the length of the
+$\mu$-paths is increased \cite{maxwell2014compressed}, because these
+longer paths lead to increased mutual coherence between the
+measurement matrix $R$ and the sparsity basis $U$. However, longer
+$\mu$-paths means fewer $\mu$-paths and thus shorter scan times.
+
 To mitigate these affects, we propose a new variant of BPDN that we
@@
 a matrix in the vertical (resp., horizontal) direction (see, e.g.,
-\cite[Section 6.1,]{becker_nesta_2011}).
+\cite[Sec. 6.1,]{becker_nesta_2011}).
 % and
@@
 measurement location to tracking a short ramp during the actual $\mu$-path scan.
-For our simple integral controller, this only involves changing the reference signals
-$X_{ref}$ and $Y_{ref}$. In the $Z$-direction, the system must
-transition between tip descent, surface scanning, and tip retraction. F
+In the $Z$-direction, the system must
+transition between tip descent, surface scanning, and tip retraction.
+Two cycles of this sequential process are illustrated by the time
+series in Fig.~\ref{fig:cs_cycle}. The following
+subsections describe in more detail several features of the CS
+scanning process.
 
@@
 implemented as a simple state machine, summarized in
-Table~\ref{tab:cs_tasks}. In the following, $r_X$ and $r_Y$ refer to
+Table~\ref{tab:cs_tasks}. The main job of the state machine is to
+adjust the reference signals to accomplish each task.
+In the following, $r_X$ and $r_Y$ and $r_Z$ refer to
 the references for the $X$ and $Y$ axes while $r_{Z,s}$ and $\rzup$
@@
 
-\begin{table}
+\begin{table}[h!]
   \centering
@@
 \end{table}
-Two cycles of this sequential process are illustrated by the time
-series in Fig.~\ref{fig:cs_cycle}. The following
-subsections describe in more detail several features of the CS
-scanning process.
 
@@
 \end{equation}
-time steps, where $H_x$ is closed-loop transfer function for the $x$-axis, including $F_X$.
+time steps, where $H_x$ is closed-loop transfer function for the $x$-axis.
 For our system $N=111$. By initiating the scan while the $Z$-axis settles, we eliminate much of
@@
 open question how to best compare experimental AFM images. While we
-use the SSIM and PSNR in Section~\ref{sec:results}, we believe those
+use the SSIM and PSNR in Sec.~\ref{sec:results}, we believe those
 numbers should be interpreted with some caution. In our experimental
@@
  sixth image. The PSNR and SSIM between
-images the first and second images are \baseline{one2twoNoAlgnPsnr} and
+the first and second images are \baseline{one2twoNoAlgnPsnr} and
 \baseline{one2twoNoAlgnSsim}; between the first and sixth are
 \baseline{one2sixNoAlgnPsnr} and \baseline{one2sixNoAlgnSsim},
-respectively, even though on their own each image has good quality.
+respectively, even though on their own each image appears to have good quality.
 
@@
 the 2D cross-correlation between each image. Essentially, this takes a
-sub-slice of image 1 (here, a 25 pixel inset on each edge), and finds
+sub-slice of the master (first) image (here, a 25 pixel inset on each edge), and finds
 the offset in the other image that produces the smallest error. The
@@
 there is still noticeable stretching (the upper and lower portions appear considerably worse than the middle). Notably however, with the alignment technique, the SSIM is
-\baseline{one2twoAlgnSsim} for both sets of images and
-while the PSNR is increases to \baseline{one2twoAlgnPsnr} and \baseline{one2sixAlgnPsnr}
+\baseline{one2twoAlgnSsim} for both the second and sixth image images and
+the PSNR is increases to \baseline{one2twoAlgnPsnr} and \baseline{one2sixAlgnPsnr}
 respectively.
@@
 We compared $\mu$-path scanning to two scenarios. First, we compare it
-to full resolution raster scans at several scan rates in Section~\ref{sec:cp_full}.
-Second we compare to course raster scans in Section \ref{sec:cp_subline}.
+to full resolution raster scans at several scan rates in Sec.~\ref{sec:cp_full}.
+Second, we compare to course raster scans in Sec.~\ref{sec:cp_subline}.
 
@@
 For each raster scan and each CS scan, we computed the SSIM and PSNR
- using the 1~Hz scan as the master and
+ using the 1~Hz raster scan as the master and
 also computed the RDI metric. These are plotted against total acquisition time
@@
 illuminating. There are several inconsistencies. For example, it makes no sense
-the 1 Hz CS scan at 25\% has a \emph{worse} PSNR and SSIM than 5 Hz version;
+the 1~Hz CS scan at 25\% has a \emph{worse} PSNR and SSIM than 5~Hz version;
 nor does it make sense that the 8~Hz full raster scan has a worse SSIM and PSNR than
@@
 Things are clearer if we plot the RDI for each scan against total acquisition time, which is
-shown inf Fig.~\ref{fig:time_damage} and 
+shown in Fig.~\ref{fig:time_damage} and 
 this is where CS seems to shine.
-This is plotted in Fig.~\ref{fig:time_damage}.
 As one would expect, as imaging time decreases, the RDI for each
@@
 to hold the RDI below 2, then we have to take the 1~Hz raster scan
-(512 seconds) while we can achieve the same RDI via CS in about 52
-seconds with the 15\% sampling, which is a speed improvement of nearly
+(512 seconds) while we can achieve the same RDI via CS in about 42
+seconds with the 12.5\% sampling, which is a speed improvement of over
 10. The higher of an RDI we are willing to tolerate, the advantage of
-CS over raster narrows. For example, the 4~Hz raster scan and 5~Hz,
-15\% CS scan have comparable RDI, but now CS is only about 6 times
+CS over raster narrows. For example, the 8~Hz raster scan and 8~Hz,
+12.5\% CS scan have comparable RDIs, but now CS is only about 5 times
 faster. This is a result of the constant overhead imposed by the
-engage/disengage and $XY$-move states in CS.
+engage/disengage and $XY$-move states in CS which remains constant for
+different scan rates.
 
@@
 column to produce a 512 by 512 pixel image. Again, we take these
-courser raster scans at 1.0, 5.0, 8.0 and 10.0 Hz. The resulting
+courser raster scans at 1.0, 2.5, 5.0, 8.0 and 10.0 Hz. The resulting
 images are shown in Fig.~\ref{fig:results_subline_images}.
 
+Both visually and from the metrics show in
+From both From the metrics in Figs.Figs.~\ref{fig:time_ssim} and \ref{fig:time_psnr}, the 64 line scan
+performs the worst of the all the sub-sampling methods and is slower than 12.5\% CS for slow scan rates.
+However, the 128 line scans appear to have as good or better image quality than either CS scans.
+
 Note the defect on the hole located in the second column, sixth row
-from the top. The CS-scans do a poor job detecting this, while both
-course raster scans do so. However, the other artifacts in 64 line
+from the top (of the grating holes). The CS-scans do a poor job detecting this,
+while both course raster scans do so. However, the other artifacts in 64 line
 scan obscure the defect.
 
-Fig.~\ref{fig:improve_512} shows the amount of improvement of the
-different sub-sampling techniques over full raster scans with 512
+Fig.~\ref{fig:improve_512} compares the amount of speed improvement of the different sub-sampling scheme over a full raster scans with 512
 lines as a function of scan rate. As far as pure speed goes, the CS
@@
 
-% \begin{figure}
-%   \includesvg[width=1\columnwidth]{figures/subline_vs_cs.svg}
-%   \caption{(left) A 128 line raster scan interpolated onto 512
-%   lines. (right) The CS scan with the nearest time.}
-%   \label{fig:subline}
-% \end{figure}
-
 \section{Conclusions}\label{sec:conclusions}
-The main conclusion of this chapter is that with CS, it seems that we
-can acquire images faster yet (putatively) with less specimen damage
+The main conclusion of this paper is that with CS, it seems that we
+can acquire images faster yet with less specimen damage
 than is possible while raster scanning a full image.
-On the other hand, it appears that reconstructing a course raster scan makes more sense for faster scan rates.
-This is notable, since a course raster scan only requires an additional step in post-processing.
-It remains to be seen if this conclusion holds for a wide range of instruments.
+On the other hand, it appears that reconstructing a course raster scan makes
+more sense for faster scan rates. This is notable, since a course raster scan only
+requires an additional step in post-processing. It remains to be seen if this conclusion
+holds for a wide range of instruments.
 

### 2019-06-24 latex/afm-cs-main.tex
Update on Overleaf.

@@
-\documentclass[twocolumn,oneside]{IEEEtran/IEEEtran}
+\documentclass[journal]{IEEEtran}
+% \documentclass[twocolumn,oneside]{IEEEtran/IEEEtran}
 % \documentclass[defaultstyle,11pt]{IEEETran}
 
-\usepackage{showframe}
+% \usepackage{showframe}
 \usepackage{amssymb}		% to get all AMS symbols
@@
 \begin{document}
-\title{Improving the Image Acquisition Rate of an Atomic Force
-  Microscope Through Sub-sampling and Reconstruction}
+\title{Improving the Image Acquisition Rate \\ of an Atomic Force Microscope \\
+Through Sub-sampling and Reconstruction}
 
@@
     roger.braker@colorado.edu) is a graduate student and L.Y. Pao
-    (pao@colorado.edu) is the Richard \& Joy Dorf Professor.}
+    (pao@colorado.edu) is the Palmer  Professor.}
   \thanks{This work was supported in part by the US National Science
-    Foundation (NSF Grant CMMI-1234980) and Agilent Technologies,
-    Inc.} }
+    Foundation (NSF Grant CMMI-1234980)  Agilent Technologies,
+    Inc., and the Hanse-Wissenschaftskolleg Institute for Advanced Study in Delmenhorst, Germany.} }
 
@@
 resolution, and ability to image in vacuum, air, and liquid, AFM is
-widely used in a variety of disciplines, including physics, biology
+widely used in a variety of disciplines, including physics, biology,
 and materials science
@@
 modifications to the physical components. These have included the use
-of small, fast cantilevers \cite{viani1999fast,
+of small, fast cantilevers \cite{Viani:1999tp,
   braunsmann2010high,Adams:2016hg}, the development of faster
@@
 
-Our previous work on the $\mu$-path pattern using theoretical
+Our previous work on the $\mu$-path pattern, using theoretical
 calculations, simulations, and a preliminary implementation,
@@
 reconstruction methods through simulations in Sec. \ref{sec:reconstructionMethods}.
-\item In our prior experimental prototype, \cite{braker_hardware_2018} we used very basic integral controllers for all three axes for both raster and $\mu$-path scans.
+\item In our prior experimental prototype \cite{braker_hardware_2018}, we used very basic integral controllers for all three axes for both raster and $\mu$-path scans.
 Here, we design compensators for each axis using standard loop-shaping techniques (Sec.~\ref{sec:control}), which result in a substantial increase in closed-loop bandwidth (e.g., 50 Hz to 450~Hz for the $Z$-axis).
@@
 \item We experimentally compare (Sec.
-\ref{sec:results}) $\mu$-path scanning to not only full density raster scans but also to course raster scans which are interpolated to a full image.
+\ref{sec:results}) $\mu$-path scanning to not only full density raster scans but also to coarse raster scans which are interpolated to a full image.
 This is in contrast to typical sub-line sampling which takes scan lines at random.
-The clear advantage to a course raster scan is that it requires no modification to the instrument, only to the post-processing.
+The clear advantage to a coarse raster scan is that it requires no modification to the instrument, only to the post-processing.
 \item The bulk of this work is based on experiment, not simulation, in contrast to prior work by ourselves \cite{Luo_nano_2015,maxwell_acc_2014} and others \cite{han_optimal_2018,jensen_reconstruction_2013,oxvig_structure_2017}.
@@
 
+\begin{IEEEbiography}{Roger A. Braker} is so happy that all this is almost done.
+
+\end{IEEEbiography}
+
+\begin{IEEEbiography}[{\includegraphics[width=1 in,height=1.25in,clip,keepaspectratio]{yufan.JPG}}]{Yufan Luo}
+received dual B.S.
+degrees in automation and in management science from Zhejiang University, Zhejiang, China, in 2011, an M.S.
+degree in industrial and operations engineering from the University of Michigan, Ann Arbor, MI, USA, in 2012, and a Ph.D.
+degree in systems engineering from Boston University in 2019.
+He is currently with Juniper Networks, Sunnyvale, CA.
+
+\end{IEEEbiography}
+
+\begin{IEEEbiography}{Lucy Y. Pao} is probably not so happy that Arnold's almost done.
+
+\end{IEEEbiography}
+
+\begin{IEEEbiography}[{\includegraphics[width=1 in,height=1.25in,clip,keepaspectratio]{SeanAndersson_IEEE.jpg}}]{Sean B. Andersson}
+received the B.S.
+degree in engineering and applied physics from Cornell University, Ithaca, NY, USA, in 1994, the M.S.
+degree in mechanical engineering from Stanford University, Stanford, CA, USA, in 1995, and the Ph.D.
+degree in electrical and computer engineering from the University of Maryland, College Park, MD, USA, in 2003.
+He has worked at AlliedSignal Aerospace and Aerovironment, Inc.
+and is currently an Associate Professor of mechanical engineering and of systems engineering with Boston University, Boston, MA, USA.
+His research interests include systems and control theory with applications in scanning probe microscopy, dynamics in molecular systems, and robotics.
+He received an NSF CAREER award in 2009, is a senior member of the IEEE, and was an associate editor for the IEEE Transactions on Automatic Control (2014-2018) and for the SIAM Journal on Control and Optimization (2013-2018).
+\end{IEEEbiography}
+
 %%%%%%%%% then the Bibliography, if any %%%%%%%%%

### 2019-06-24 latex/afm-cs-main.tex
Edits that should have gone in last week.

--- 2019-06-19 latex/afm-cs-main.tex
@@
 engaged with the surface to collect a measurement, lifted and moved to
-the new location, and engaged again.
-Because the re-engagement process
+the new location, and engaged again. Because the re-engagement process
 is typically slow, this can lead to excessively long image acquisition
 times and negate the gains from undersampling \cite{andersson2012non}.
-In \cite{maxwell2014compressed}, we introduced a discrete undersampling scheme,
-called a $\mu$-path pattern, which consists of short randomly placed,
-horizontal scans (see Fig.~\ref{fig:mu_mask} for one such pattern). It
-is designed to balance the randomness needed (to ensure good
-reconstruction) with continuous scanning (to reduce the number of tip
-engagements).
+In \cite{maxwell2014compressed}, we introduced a discrete
+undersampling scheme, called a $\mu$-path pattern, which consists of
+short randomly placed, horizontal scans (see Fig.~\ref{fig:mu_mask}
+for one such pattern). It is designed to balance the randomness needed
+(to ensure good reconstruction) with continuous scanning (to reduce
+the number of tip engagements).
 
@@
 calculations, simulations, and a preliminary implementation,
-demonstrates that the approach can achieve scanning time
-reduction while maintaining faithful image reconstruction
-\cite{maxwell2014compressed,Luo:2015tu, braker_hardware_2018}. 
-The main contributions of this paper relative to that past work are:
+demonstrates that the approach can achieve scanning time reduction
+while maintaining faithful image reconstruction
+\cite{maxwell2014compressed,Luo:2015tu, braker_hardware_2018}. The
+main contributions of this paper relative to that past work are:
 \begin{itemize}
@@
   minimize the artifacts arising from the structure of the $\mu$-path
-scanning pattern. This algorithm is described and compared to existing
-reconstruction methods through simulations in Sec. \ref{sec:reconstructionMethods}.
-\item In our prior experimental prototype, \cite{braker_hardware_2018} we used very basic integral controllers for all three axes for both raster and $\mu$-path scans.
-Here, we design compensators for each axis using standard loop-shaping techniques (Sec.~\ref{sec:control}), which result in a substantial increase in closed-loop bandwidth (e.g., 50 Hz to 450~Hz for the $Z$-axis).
-We show in Sec.~\ref{sec:ff_control} that one of the limitations of $\mu$-path scanning is the discontinuous $X$-axis reference (e.g., in moving between $\mu$-paths) which excites the cross-coupling modes between the $X$ and $Z$ axes, an affect which neither our prior experimental work nor the numerous simulation studies have accounted for.
-We mitigate the cross coupling with a feed-forward design.
-\item We experimentally compare (Sec.
-\ref{sec:results}) $\mu$-path scanning to not only full density raster scans but also to course raster scans which are interpolated to a full image.
-This is in contrast to typical sub-line sampling which takes scan lines at random.
-The clear advantage to a course raster scan is that it requires no modification to the instrument, only to the post-processing.
-\item The bulk of this work is based on experiment, not simulation, in contrast to prior work by ourselves \cite{Luo_nano_2015,maxwell_acc_2014} and others \cite{han_optimal_2018,jensen_reconstruction_2013,oxvig_structure_2017}.
-Our main focus here is on delineating the practical issues which must be addressed to effectively realize $\mu$-path scanning, which has only seen limited attention in the past.
+  scanning pattern. This algorithm is described and compared to
+  existing reconstruction methods through simulations in Sec.
+  \ref{sec:reconstructionMethods}.
+\item In our prior experimental prototype, \cite{braker_hardware_2018}
+  we used very basic integral controllers for all three axes for both
+  raster and $\mu$-path scans. Here, we design compensators for each
+  axis using standard loop-shaping techniques
+  (Sec.~\ref{sec:control}), which result in a substantial increase in
+  closed-loop bandwidth (e.g., 50 Hz to 450~Hz for the $Z$-axis). We
+  show in Sec.~\ref{sec:ff_control} that one of the limitations of
+  $\mu$-path scanning is the discontinuous $X$-axis reference (e.g.,
+  in moving between $\mu$-paths) which excites the cross-coupling
+  modes between the $X$ and $Z$ axes, an affect which neither our
+  prior experimental work nor the numerous simulation studies have
+  accounted for. We mitigate the cross coupling with a feed-forward
+  design.
+\item We experimentally compare (Sec. \ref{sec:results}) $\mu$-path
+  scanning to not only full density raster scans but also to course
+  raster scans which are interpolated to a full image. This is in
+  contrast to typical sub-line sampling which takes scan lines at
+  random. The clear advantage to a course raster scan is that it
+  requires no modification to the instrument.
 \end{itemize}
+In general, our main focus here is on delineating the practical issues which
+must be addressed to effectively realize $\mu$-path scanning, which
+has only seen limited attention in the past, as most of the prior 
+investigation of CS in AFM  have been based purely on simulation
+\cite{Luo_nano_2015,maxwell_acc_2014, han_optimal_2018,jensen_reconstruction_2013,oxvig_structure_2017}.
 
@@
 identity matrix. Ideally, the sparsity basis and the measurement
-matrix $R$ will have a low \textit{mutual coherence}, a measure of
-how each of the rows of $R$ (the measurements) ``spreads
-out'' in the domain of $U$ \cite{candes2007sparsity}. In the
-following, we assume that $U^TU=I$, though in the simulation and
-experimental results, we take $U^T$ as the Discrete Cosine Transform
-(DCT). The DCT basis generally keeps a good balance between achieving
-a low mutual coherence between $U$ and the $\mu$-path sensing matrices
-$R$ and providing a high sparsity for typical AFM sample images.
+matrix $R$ will have a low \textit{mutual coherence}, a measure of how
+each of the rows of $R$ (the measurements) ``spreads out'' in the
+domain of $U$ \cite{candes2007sparsity}. In the following, we assume
+that $U^TU=I$, though in the simulation and experimental results, we
+take $U^T$ as the Discrete Cosine Transform (DCT). The DCT basis
+generally keeps a good balance between achieving a low mutual
+coherence between $U$ and the $\mu$-path sensing matrices $R$ and
+providing a high sparsity for typical AFM sample images.
 
@@
 % %   \lambda & = \textrm{max}(0, \sigma^{-1}\left| b -
-% %     Rq\right| - L\\
+% %     Rq\right| -
+% %   L\\
 % %   q &= r - L^{-1}g\\
 % %   p &= \left(I - \frac{\lambda}{\lambda + L}
-% %     R^TR\right)\left( \frac{\lambda}{L}R^Tb + q\right).
+% %     R^TR\right)\left(
+% %     \frac{\lambda}{L}R^Tb +
+% %     q\right).
 % % \end{align}
@@
 several distinct stages. In the $XY$-direction, the system transitions
-from tracking a step command in the transition to a new
-measurement location to tracking a short ramp during the actual $\mu$-path scan.
-In the $Z$-direction, the system must
-transition between tip descent, surface scanning, and tip retraction.
-Two cycles of this sequential process are illustrated by the time
-series in Fig.~\ref{fig:cs_cycle}. The following
-subsections describe in more detail several features of the CS
-scanning process.
+from tracking a step command in the transition to a new measurement
+location to tracking a short ramp during the actual $\mu$-path scan.
+In the $Z$-direction, the system must transition between tip descent,
+surface scanning, and tip retraction. Two cycles of this sequential
+process are illustrated by the time series in Fig.~\ref{fig:cs_cycle}.
+The following subsections describe in more detail several features of
+the CS scanning process.
 
@@
 Table~\ref{tab:cs_tasks}. The main job of the state machine is to
-adjust the reference signals to accomplish each task.
-In the following, $r_X$ and $r_Y$ and $r_Z$ refer to
-the references for the $X$ and $Y$ axes while $r_{Z,s}$ and $\rzup$
-refer to the $Z$-axis setpoints during scanning and retraction,
-respectively.
+adjust the reference signals to accomplish each task. In the
+following, $r_X$ and $r_Y$ and $r_Z$ refer to the references for the
+$X$ and $Y$ axes while $r_{Z,s}$ and $\rzup$ refer to the $Z$-axis
+setpoints during scanning and retraction, respectively.
 
@@
   down, but thinking of a knife pushed into a surface and then
-  dragged...}
-In our initial implementation \cite{braker_hardware_2018}, we insisted that the during
+  dragged...} In our initial implementation
+\cite{braker_hardware_2018}, we insisted that the during
 tip-retraction (state-5), the cantilever tip should fully break
@@
 adhesive. In general, stable imaging in is not possible at \rzup and
-complete dis-engagement occasionally occurs. This can be seen in bottom pane of
-Fig.~\ref{fig:cs_cycle} during the second $XY$-move (black portion) where the tip detaches partway through the move.
-%Fig.~\ref{fig:afm_bd_dinv} which selects either the scanning setpoint $r_{Z,s}$ or the retraction setpoint $r_{Z,\textrm{up}}$ based the current state.
-When dis-engagement does occur, the $Z$-axis control loop implements an anti-windup scheme to prevent the control from saturating.
-
-Only moving the tip into the adhesive region during the $XY$ move saves considerable time
-compared to completely detaching the tip between each $\mu$-path.
-By eliminating the normal force into the sample, we are able to take dozens of images with a single probe without a noticeable degradation in image quality.
-However, completely characterizing the damage done to the tip and sample with this scheme compared complete detachment (which can also damage the probe \cite{meyer_atomic_1992}), remains an outstanding goal.
+complete dis-engagement occasionally occurs. This can be seen in
+bottom pane of Fig.~\ref{fig:cs_cycle} during the second $XY$-move
+(black portion) where the tip detaches partway through the move.
+% Fig.~\ref{fig:afm_bd_dinv} which selects either the scanning
+% setpoint $r_{Z,s}$ or the retraction setpoint $r_{Z,\textrm{up}}$
+% based the current state.
+When dis-engagement does occur, the $Z$-axis control loop implements
+an anti-windup scheme to prevent the control from saturating.
+
+Only moving the tip into the adhesive region during the $XY$ move
+saves considerable time compared to completely detaching the tip
+between each $\mu$-path. By eliminating the normal force into the
+sample, we are able to take dozens of images with a single probe
+without a noticeable degradation in image quality. However, completely
+characterizing the damage done to the tip and sample with this scheme
+compared complete detachment (which can also damage the probe
+\cite{meyer_atomic_1992}), remains an outstanding goal.
 
@@
 After the tip-descent, we begin scanning in a ``pre-scan'' phase
-(state (3)), which is the turquoise portion of the trajectories in Fig.~\ref{fig:cs_cycle}.
-There are two reasons for this.
-First, we have observed that there is less noise in the deflection signal while the $XY$-stage is in motion compared to sitting still.
-More importantly, it lets us bring the $X$-axis to its scanning velocity at the same time the transients from the $Z$-axis die out.
-Without this, we must extend the $\mu$-path by a distance equal to the steady-state error following a ramp.
-For an arbitrary scan speed, this means the $\mu$-path scan would need an extra
+(state (3)), which is the turquoise portion of the trajectories in
+Fig.~\ref{fig:cs_cycle}. There are two reasons for this. First, we
+have observed that there is less noise in the deflection signal while
+the $XY$-stage is in motion compared to sitting still. More
+importantly, it lets us bring the $X$-axis to its scanning velocity at
+the same time the transients from the $Z$-axis die out. Without this,
+we must extend the $\mu$-path by a distance equal to the steady-state
+error following a ramp. For an arbitrary scan speed, this means the
+$\mu$-path scan would need an extra
 \begin{equation}
@@
 \end{equation}
-time steps, where $H_x$ is closed-loop transfer function for the $x$-axis.
-For our system $N=111$. By initiating the scan while the $Z$-axis settles, we eliminate much of
-this overhead.
+time steps, where $H_x$ is closed-loop transfer function for the
+$x$-axis. For our system $N=111$. By initiating the scan while the
+$Z$-axis settles, we eliminate much of this overhead.
 
@@
 set of filters in series with a PI controller. The open-loop frequency
-response for the $X$ and $Y$ axes is shown as the black curves in Fig.~\ref{fig:mimo_frf_uxuy} and for the $Z$-axis in Fig.~\ref{fig:z_control}.
-The first resonance of each axis is the bending mode, which
-appears at 215~Hz for the $Z$ axis and about 350~Hz for the $X$ and
-$Y$ axes.
+response for the $X$ and $Y$ axes is shown as the black curves in
+Fig.~\ref{fig:mimo_frf_uxuy} and for the $Z$-axis in
+Fig.~\ref{fig:z_control}. The first resonance of each axis is the
+bending mode, which appears at 215~Hz for the $Z$ axis and about
+350~Hz for the $X$ and $Y$ axes.
 
@@
 In general, the $X$-axis positioning requirements are more stringent
-for both CS and raster scanning. Due to the step inputs the $X$-axis must track, we have found that
-compensating hysteresis and creep to be particular helpful during $\mu$-path scanning. Thus,
-the $X$-axis compensator also includes an inverse creep and hysteresis
-model. The hysteresis model is a modified Prandtl-Ishlinki type model
-and is based on the work of \cite{kuhnen_modeling_2003}, while the
-drift compensation models the piezo creep as a simple second order
-transfer function with real poles and zeros. In
-Fig.~\ref{fig:afm_bd_dinv}, the hysteresis inversion is indicated by
-$\mathcal{H}^{-1}[\cdot]$. We have found that the inclusion of these
-extra compensators limits the overshoot of the $X$-axis during larger
-moves between different $\mu$-paths (e.g., without them, the $X$-axis trajectory in Fig.~\ref{fig:with_ff} would show noticeable overshoot). More details on fitting the creep
-and hysteresis models can be found in our other work \cite{braker_afmmpc_2019}.
+for both CS and raster scanning. Due to the step inputs the $X$-axis
+must track, we have found that compensating hysteresis and creep to be
+particular helpful during $\mu$-path scanning. Thus, the $X$-axis
+compensator also includes an inverse creep and hysteresis model. The
+hysteresis model is a modified Prandtl-Ishlinki type model and is
+based on the work of \cite{kuhnen_modeling_2003}, while the drift
+compensation models the piezo creep as a simple second order transfer
+function with real poles and zeros. In Fig.~\ref{fig:afm_bd_dinv}, the
+hysteresis inversion is indicated by $\mathcal{H}^{-1}[\cdot]$. We
+have found that the inclusion of these extra compensators limits the
+overshoot of the $X$-axis during larger moves between different
+$\mu$-paths (e.g., without them, the $X$-axis trajectory in
+Fig.~\ref{fig:with_ff} would show noticeable overshoot). More details
+on fitting the creep and hysteresis models can be found in our other
+work \cite{braker_afmmpc_2019}.
 
@@
     affect on $G_{Z,u_X}$ and $G_{Z,u_Y}$ when the feedforward
-    compensators are used for the $X$ and $Y$ axes.
-(b) The vertical control $u_Z$ (top) after a large move in the $X$-direction (bottom) without (left column) and with (right column) the feedforward compensation.
-(c) Frequency response of the $Z$-axis in open-loop (black) and closed-loop (red).
-}
+    compensators are used for the $X$ and $Y$ axes. (b) The vertical
+    control $u_Z$ (top) after a large move in the $X$-direction
+    (bottom) without (left column) and with (right column) the
+    feedforward compensation. (c) Frequency response of the $Z$-axis
+    in open-loop (black) and closed-loop (red). }
 \end{figure*}
@@
 \subsection{Feedforward Control}\label{sec:ff_control}
-Unfortunately, as the bottom row of plots in Fig.~\ref{fig:mimo_frf_uxuy}
-makes clear, there is a strong cross-coupling from the horizontal
-plane to the $Z$ axis (the coupling from $u_Z$ to the $X$ and $Y$ axes
-is very weak, and so is not shown). Our SISO control scheme does
-little to attenuate the resonances of $G_{Z,u_X}$ and $G_{Z,u_Y}$. In
-particular, there are modes in both these transfer functions at 215
-and 505 Hz that do not appear in a SISO model of $G_{X,u_X}$ or
-$G_{Y,u_Y}$.
+Unfortunately, as the bottom row of plots in
+Fig.~\ref{fig:mimo_frf_uxuy} makes clear, there is a strong
+cross-coupling from the horizontal plane to the $Z$ axis (the coupling
+from $u_Z$ to the $X$ and $Y$ axes is very weak, and so is not shown).
+Our SISO control scheme does little to attenuate the resonances of
+$G_{Z,u_X}$ and $G_{Z,u_Y}$. In particular, there are modes in both
+these transfer functions at 215 and 505 Hz that do not appear in a
+SISO model of $G_{X,u_X}$ or $G_{Y,u_Y}$.
 
@@
 Fig.~\ref{fig:afm_bd_dinv}) with three notches: one at 215~Hz, one at
-350~Hz and one at 505~Hz. Both filters are shown in Fig.~\ref{fig:mimo_frf_uxuy}
-as the dashed-pink curves and the resulting overall FRF is shown as the
-dotted-blue curves, which show a dramatic reduction in the cross
-coupling. A similar affect could be achieve by using a simple low-pass
-filter. However, to achieve the same 40~dB of attenuation of the mode
-at 215 Hz, would require, e.g., that a two-pole low-pass filter have
-its cut-off frequency at about 20~Hz. Thus, while our feedforward
-scheme slows the $X$-axis down, we achieve better bandwidth than we
-would with a simple low-pass filter.
+350~Hz and one at 505~Hz. Both filters are shown in
+Fig.~\ref{fig:mimo_frf_uxuy} as the dashed-pink curves and the
+resulting overall FRF is shown as the dotted-blue curves, which show a
+dramatic reduction in the cross coupling. A similar affect could be
+achieve by using a simple low-pass filter. However, to achieve the
+same 40~dB of attenuation of the mode at 215 Hz, would require, e.g.,
+that a two-pole low-pass filter have its cut-off frequency at about
+20~Hz. Thus, while our feedforward scheme slows the $X$-axis down, we
+achieve better bandwidth than we would with a simple low-pass filter.
 
@@
 Fig.~\ref{fig:baseline_errors} shows the error between the first and
- sixth image. The PSNR and SSIM between
-the first and second images are \baseline{one2twoNoAlgnPsnr} and
-\baseline{one2twoNoAlgnSsim}; between the first and sixth are
-\baseline{one2sixNoAlgnPsnr} and \baseline{one2sixNoAlgnSsim},
-respectively, even though on their own each image appears to have good quality.
+sixth image. The PSNR and SSIM between the first and second images are
+\baseline{one2twoNoAlgnPsnr} and \baseline{one2twoNoAlgnSsim}; between
+the first and sixth are \baseline{one2sixNoAlgnPsnr} and
+\baseline{one2sixNoAlgnSsim}, respectively, even though on their own
+each image appears to have good quality.
 
@@
 the 2D cross-correlation between each image. Essentially, this takes a
-sub-slice of the master (first) image (here, a 25 pixel inset on each edge), and finds
-the offset in the other image that produces the smallest error. The
-result of this procedure are shown in the right image of
-Fig.~\ref{fig:baseline_errors}.
-Although the situation is improved compared to the un-aligned images,
-there is still noticeable stretching (the upper and lower portions appear considerably worse than the middle). Notably however, with the alignment technique, the SSIM is
-\baseline{one2twoAlgnSsim} for both the second and sixth image images and
-the PSNR is increases to \baseline{one2twoAlgnPsnr} and \baseline{one2sixAlgnPsnr}
-respectively.
+sub-slice of the master (first) image (here, a 25 pixel inset on each
+edge), and finds the offset in the other image that produces the
+smallest error. The result of this procedure are shown in the right
+image of Fig.~\ref{fig:baseline_errors}. Although the situation is
+improved compared to the un-aligned images, there is still noticeable
+stretching (the upper and lower portions appear considerably worse
+than the middle). Notably however, with the alignment technique, the
+SSIM is \baseline{one2twoAlgnSsim} for both the second and sixth image
+images and the PSNR is increases to \baseline{one2twoAlgnPsnr} and
+\baseline{one2sixAlgnPsnr} respectively.
 
@@
   \includesvg[width=0.7\columnwidth]{figures/baseline_errors_1and6.svg}
-  \caption{Errors between the first and sixth raster scans in a sequence of six 1.0~Hz
-    raster scans. (left) Errors without alignment (right) The same
-    data but aligned via cross correlation.}
+  \caption{Errors between the first and sixth raster scans in a
+    sequence of six 1.0~Hz raster scans. (left) Errors without
+    alignment (right) The same data but aligned via cross
+    correlation.}
   \label{fig:baseline_errors}
@@
 However, in AFM imaging, pure image quality is not the only concern,
-particularly for delicate samples. What is needed is a figure of
-merit for how much damage was done to specimen during the imaging
-process. While damage to the specimen is not really a concern while imaging a hard
-calibration grating, it plays a prominent role for biological
-samples~\cite{ando_highspeed_2008}, though damage to the probe itself is still a concern.
-In general, the faster the scan rate,
-the more difficulty the $Z$-axis control
-will have following the sample surface,
-which results in a larger $Z_d$ over more time. 
-The actual damage done by a given $Z_d$ will
-depend on the spring constant of the cantilever and the softness of
-the specimen. Nonetheless, we propose a metric, which we call the Relative Damage Index (RDI)
-which computes the power in the deflection signal for a given scan. That is,
+particularly for delicate samples. What is needed is a figure of merit
+for how much damage was done to specimen during the imaging process.
+While damage to the specimen is not really a concern while imaging a
+hard calibration grating, it plays a prominent role for biological
+samples~\cite{ando_highspeed_2008}, though damage to the probe itself
+is still a concern. In general, the faster the scan rate, the more
+difficulty the $Z$-axis control will have following the sample
+surface, which results in a larger $Z_d$ over more time. The actual
+damage done by a given $Z_d$ will depend on the spring constant of the
+cantilever and the softness of the specimen. Nonetheless, we propose a
+metric, which we call the Relative Damage Index (RDI) which computes
+the power in the deflection signal for a given scan. That is,
 
@@
 We compared $\mu$-path scanning to two scenarios. First, we compare it
-to full resolution raster scans at several scan rates in Sec.~\ref{sec:cp_full}.
-Second, we compare to course raster scans in Sec.~\ref{sec:cp_subline}.
+to full resolution raster scans at several scan rates in
+Sec.~\ref{sec:cp_full}. Second, we compare to course raster scans in
+Sec.~\ref{sec:cp_subline}.
 
@@
 raster scans, we took scans at 1.0~Hz, 2.5~Hz, 5.0~Hz, 8.0~Hz and
-10~Hz. We also took $\mu$-path scans with densities at 12.5\%,
-and 25\% and reconstructed 512 by 512 pixel images. The CS scans were
+10~Hz. We also took $\mu$-path scans with densities at 12.5\%, and
+25\% and reconstructed 512 by 512 pixel images. The CS scans were
 taken with scan velocities equivalent to raster scan rates of 1.0~Hz,
@@
 The free value of the deflections signal was approximately -0.6 volts
-and we set the scanning reference to ${\rzs=\scanD{spScan}}$~volts (for both raster and CS)
-and the withdraw reference to ${\rzup=\scanD{spMv}}$ volts. We set the
-$XY$-settle boundary to $\pm \scanD{xyBoundaryMic}$ microns and
-required $\scanD{xySetSamps}$ samples within this boundary before
-moving to the $Z$-engage state. The pre-scan length was
-$\scanD{preScanSamples}$ time steps. The cantilever was a Budget
-Sensors ContAI-G, with a nominal length of 450 microns and spring
-constant of $k=0.2$~N/m.
+and we set the scanning reference to ${\rzs=\scanD{spScan}}$~volts
+(for both raster and CS) and the withdraw reference to
+${\rzup=\scanD{spMv}}$ volts. We set the $XY$-settle boundary to
+$\pm \scanD{xyBoundaryMic}$ microns and required $\scanD{xySetSamps}$
+samples within this boundary before moving to the $Z$-engage state.
+The pre-scan length was $\scanD{preScanSamples}$ time steps. The
+cantilever was a Budget Sensors ContAI-G, with a nominal length of 450
+microns and spring constant of $k=0.2$~N/m.
 
@@
 The CS scans were reconstructed with BPVV. We set
-${\alpha_v=\scanD{alpv}}$ and ${\alpha_h=\scanD{alph}}$. 
-For the raster scans, we discard data from the re-trace and divided
-the remaining data for each scan line into 512 bins based on the \xc
+${\alpha_v=\scanD{alpv}}$ and ${\alpha_h=\scanD{alph}}$. For the
+raster scans, we discard data from the re-trace and divided the
+remaining data for each scan line into 512 bins based on the \xc
 sensor measurements. We then average the data in each bin to obtain
@@
 feature in the AFM image processing toolbox \texttt{SPIW} \cite{spiw}.
-The resulting images are shown in Fig.~\ref{fig:resultsF1_images}.
-The color maps represent a range of $\pm$20 nm. The
-rows of pixels indicated by the red lines are shown as cross sections
+The resulting images are shown in Fig.~\ref{fig:resultsF1_images}. The
+color maps represent a range of $\pm$20 nm. The rows of pixels
+indicated by the red lines are shown as cross sections
 Fig.~\ref{fig:pixel_rows}.
@@
 For each raster scan and each CS scan, we computed the SSIM and PSNR
- using the 1~Hz raster scan as the master and
-also computed the RDI metric. These are plotted against total acquisition time
-in Fig.~\ref{fig:time_ssim} and ~\ref{fig:time_psnr}.
-Unfortunately, the SSIM and PSNR metrics are not particularly
-illuminating. There are several inconsistencies. For example, it makes no sense
-the 1~Hz CS scan at 25\% has a \emph{worse} PSNR and SSIM than 5~Hz version;
-nor does it make sense that the 8~Hz full raster scan has a worse SSIM and PSNR than
-the 10~Hz full raster scan.
+using the 1~Hz raster scan as the master and also computed the RDI
+metric. These are plotted against total acquisition time in
+Fig.~\ref{fig:time_ssim} and ~\ref{fig:time_psnr}. Unfortunately, the
+SSIM and PSNR metrics are not particularly illuminating. There are
+several inconsistencies. For example, it makes no sense the 1~Hz CS
+scan at 25\% has a \emph{worse} PSNR and SSIM than 5~Hz version; nor
+does it make sense that the 8~Hz full raster scan has a worse SSIM and
+PSNR than the 10~Hz full raster scan.
 
@@
 
-Things are clearer if we plot the RDI for each scan against total acquisition time, which is
-shown in Fig.~\ref{fig:time_damage} and 
-this is where CS seems to shine.
-As one would expect, as imaging time decreases, the RDI for each
-scan type increases. 
-From Fig.~\ref{fig:time_damage}, we see that for a
-fixed RDI, CS has a faster imaging acquisition rate. The amount of
-improvement is best if we need a very low RDI: for example, if we want
-to hold the RDI below 2, then we have to take the 1~Hz raster scan
-(512 seconds) while we can achieve the same RDI via CS in about 42
-seconds with the 12.5\% sampling, which is a speed improvement of over
-10. The higher of an RDI we are willing to tolerate, the advantage of
-CS over raster narrows. For example, the 8~Hz raster scan and 8~Hz,
-12.5\% CS scan have comparable RDIs, but now CS is only about 5 times
-faster. This is a result of the constant overhead imposed by the
-engage/disengage and $XY$-move states in CS which remains constant for
-different scan rates.
+Things are clearer if we plot the RDI for each scan against total
+acquisition time, which is shown in Fig.~\ref{fig:time_damage} and
+this is where CS seems to shine. As one would expect, as imaging time
+decreases, the RDI for each scan type increases. From
+Fig.~\ref{fig:time_damage}, we see that for a fixed RDI, CS has a
+faster imaging acquisition rate. The amount of improvement is best if
+we need a very low RDI: for example, if we want to hold the RDI below
+2, then we have to take the 1~Hz raster scan (512 seconds) while we
+can achieve the same RDI via CS in about 42 seconds with the 12.5\%
+sampling, which is a speed improvement of over 10. The higher of an
+RDI we are willing to tolerate, the advantage of CS over raster
+narrows. For example, the 8~Hz raster scan and 8~Hz, 12.5\% CS scan
+have comparable RDIs, but now CS is only about 5 times faster. This is
+a result of the constant overhead imposed by the engage/disengage and
+$XY$-move states in CS which remains constant for different scan
+rates.
 
 \subsection{Comparison to Sub-line Sampling} \label{sec:cp_subline}
- Many of sub-line sampling papers assume
-that the lines to sample are selected randomly \cite{han_optimal_2018,
-  Luo_nano_2015}. An even simpler alternative to
-$\mu$-path sampling is to simply 
-take a standard raster scan with fewer lines. This is the technique we
-consider in this subsection, by scanning images with 
- 128 and 64 lines. For each of these scenarios, we first divide the data
-for each line into 512 bins. This gives an image that is 128 (resp.,
-64) pixels by 512 pixels. We then linearly interpolate along each
-column to produce a 512 by 512 pixel image. Again, we take these
-courser raster scans at 1.0, 2.5, 5.0, 8.0 and 10.0 Hz. The resulting
-images are shown in Fig.~\ref{fig:results_subline_images}.
-
-Both visually and from the metrics show in
-From both From the metrics in Figs.Figs.~\ref{fig:time_ssim} and \ref{fig:time_psnr}, the 64 line scan
-performs the worst of the all the sub-sampling methods and is slower than 12.5\% CS for slow scan rates.
-However, the 128 line scans appear to have as good or better image quality than either CS scans.
+Many of sub-line sampling papers assume that the lines to sample are
+selected randomly \cite{han_optimal_2018, Luo_nano_2015}. An even
+simpler alternative to $\mu$-path sampling is to simply take a
+standard raster scan with fewer lines. This is the technique we
+consider in this subsection, by scanning images with 128 and 64 lines.
+For each of these scenarios, we first divide the data for each line
+into 512 bins. This gives an image that is 128 (resp., 64) pixels by
+512 pixels. We then linearly interpolate along each column to produce
+a 512 by 512 pixel image. Again, we take these courser raster scans at
+1.0, 2.5, 5.0, 8.0 and 10.0 Hz. The resulting images are shown in
+Fig.~\ref{fig:results_subline_images}.
+
+Both visually and from the metrics show in From both From the metrics
+in Figs.Figs.~\ref{fig:time_ssim} and \ref{fig:time_psnr}, the 64 line
+scan performs the worst of the all the sub-sampling methods and is
+slower than 12.5\% CS for slow scan rates. However, the 128 line scans
+appear to have as good or better image quality than either CS scans.
 
 Note the defect on the hole located in the second column, sixth row
-from the top (of the grating holes). The CS-scans do a poor job detecting this,
-while both course raster scans do so. However, the other artifacts in 64 line
-scan obscure the defect.
-
-Fig.~\ref{fig:improve_512} compares the amount of speed improvement of the different sub-sampling scheme over a full raster scans with 512
+from the top (of the grating holes). The CS-scans do a poor job
+detecting this, while both course raster scans do so. However, the
+other artifacts in 64 line scan obscure the defect.
+
+Fig.~\ref{fig:improve_512} compares the amount of speed improvement of
+the different sub-sampling scheme over a full raster scans with 512
 lines as a function of scan rate. As far as pure speed goes, the CS
@@
 The main conclusion of this paper is that with CS, it seems that we
-can acquire images faster yet with less specimen damage
-than is possible while raster scanning a full image.
-On the other hand, it appears that reconstructing a course raster scan makes
-more sense for faster scan rates. This is notable, since a course raster scan only
-requires an additional step in post-processing. It remains to be seen if this conclusion
-holds for a wide range of instruments.
+can acquire images faster yet with less specimen damage than is
+possible while raster scanning a full image. On the other hand, it
+appears that reconstructing a course raster scan makes more sense for
+faster scan rates. This is notable, since a course raster scan only
+requires an additional step in post-processing. It remains to be seen
+if this conclusion holds for a wide range of instruments.
 

### 2019-06-24 latex/afm-cs-main.tex
Add headshots.

@@
 
-\begin{IEEEbiography}{Roger A. Braker} is so happy that all this is almost done.
+\begin{IEEEbiography}
+  [{\includegraphics[width=1 in,height=1.25in,clip,keepaspectratio]{figures/braker_headshot.jpg}}]
+  {Roger A. Braker} is so happy that all this is almost done.
 
@@
 
-\begin{IEEEbiography}[{\includegraphics[width=1 in,height=1.25in,clip,keepaspectratio]{yufan.JPG}}]{Yufan Luo}
+\begin{IEEEbiography}
+  [{\includegraphics[width=1 in,height=1.25in,clip,keepaspectratio]{figures/yufan.JPG}}]
+  {Yufan Luo}
 received dual B.S.
@@
 
-\begin{IEEEbiography}{Lucy Y. Pao} is probably not so happy that Arnold's almost done.
+\begin{IEEEbiography}
+  [{\includegraphics[width=1 in,height=1.25in,clip,keepaspectratio]{figures/pao_headshot.jpg}}]
+  {Lucy Y. Pao} is probably not so happy that Arnold's almost done.
 
@@
 
-\begin{IEEEbiography}[{\includegraphics[width=1 in,height=1.25in,clip,keepaspectratio]{SeanAndersson_IEEE.jpg}}]{Sean B. Andersson}
+\begin{IEEEbiography}
+  [{\includegraphics[width=1 in,height=1.25in,clip,keepaspectratio]{figures/SeanAndersson_IEEE.jpg}}]
+  {Sean B. Andersson}
 received the B.S.

### 2019-06-25 latex/afm-cs-main.tex
Update on Overleaf.

@@
 
-\author{Roger A. Braker, Yufan Luo, Lucy Y. Pao and Sean B. Andersson
-  \thanks{The authors are with the Dept. of Electrical, Computer, and
+\author{Roger A.
+Braker, \textit{Student Member, IEEE}, Yufan Luo, \textit{Student Member, IEEE} , Lucy Y.
+Pao, \textit{Fellow, IEEE} and Sean B.
+Andersson, \textit{Senior Member, IEEE, and Member, ASME}
+  \thanks{Braker and Pao are with the Dept. of Electrical, Computer, and
     Energy Engineering at the University of Colorado, 425 UCB,
-    Boulder, CO 80309, United States. Phone: +1 (303) 492-2360. Fax:
-    +1 (303) 492-2758. R. A. Braker (corresponding author
-    roger.braker@colorado.edu) is a graduate student and L.Y. Pao
-    (pao@colorado.edu) is the Palmer  Professor.}
+    Boulder, CO 80309, USA. %Phone: +1 (303) 492-2360. Fax:
+    +1 (303) 492-2758.}%R. A. Braker (corresponding author
+    %roger.braker@colorado.edu) is a graduate student and L.Y. Pao
+    %(pao@colorado.edu) is the Palmer  Professor.}
+    \thanks{Luo is with the Division of Systems Engineering and Andersson is with the Division of Systems Engineering and the Department of Mechanical Engineering, Boston University, Boston, MA 02215, USA.}
   \thanks{This work was supported in part by the US National Science
-    Foundation (NSF Grant CMMI-1234980)  Agilent Technologies,
+    Foundation (NSF Grants CMMI-1234980, CMMI-1234845, CMMI-1562031, and DBI-1352729)  Agilent Technologies,
     Inc., and the Hanse-Wissenschaftskolleg Institute for Advanced Study in Delmenhorst, Germany.} }
@@
   to reduce the time to acquire an image by reducing the number of
-  measurements needed while still maintaining image quality. In this
-  paper, we describe a hardware implementation and demonstration of
-  one such approach based on the use of collections of short scans
+  measurements needed while still maintaining image quality.
+The approach consists of two components: data acquisition and image reconstruction.
+While the underlying idea is straightforward, practical implementation of a working scheme involves solving a variety of non-trivial problems.
+In this
+  paper, we describe one such hardware implementation and demonstration based on the use of collections of short scans
   known as $\mu$--paths. Using a commercial AFM, we acquire data on a
@@
   a new variant of basis pursuit, Basis Pursuit with Vertical
-  Variation (BPVV), that is designed to reduce artifacts arising from
+  Variation, that is designed to reduce artifacts arising from
   the sampling pattern. The quality of the resulting images is
@@
   and the structured similarity index metric and a new metric we call
-  the relative damage index. \todo{Re-write abstract, especially
-    conclusions} These experiments demonstrate that at slow scan
+  the relative damage index.
+These images are compared both to standard raster scans as well as to simple subline sampling where only a subset of the rows of the image are acquired (followed by reconstruction).
+\textcolor{red}{These experiments demonstrate that at slow scan
   rates, the $\mu-$path scheme produces similar image quality with
@@
   and that at high rates, the undersampling scheme produces higher
-  quality images than raster scanning.
+  quality images than raster scanning.}
 \end{abstract}
@@
   braunsmann2010high,Adams:2016hg}, the development of faster
-actuators \cite{Maroufi:2015gt,Yong:2012kd,Kenton:2012cm}, as well as
+actuators \cite{Maroufi:2015gt,Yong:2012kd,Kenton:2012cm}, and
 the application of advanced controllers
@@
 trajectories like spirals, cycloids, and Lissajous figures, have been
-used in place of the standard raster scan. These trajectories are
+used in place of the standard raster pattern. While these trajectories are
 easier for the actuators to follow, allowing the tip to be moved more
@@
 unmodified instrument
-\cite{Bazaei:2017dm,Wu:2015dt,Rana:2014bj,Tuma:2012hv,Yong:2010gm}.
-Such approaches are ultimately limited by the vertical bandwidth of
+\cite{Bazaei:2017dm,Wu:2015dt,Rana:2014bj,Tuma:2012hv,Yong:2010gm}, they are ultimately limited by the vertical bandwidth of
 the instrument for regulating the deflection signal \cite{Teo:2016ev}.
-Related to these are local scanning methods that use the measurements
-in real-time to steer the tip to focus the scan on features of
-interest, reducing imaging time by reducing the amount of sampling
-needed \cite{Hartman:2018ja,Wen:2018fl,Zhang:2015cf,Huang:2014dw}.
+
+A different use of non-raster scan patterns are those that seek to improve imaging rate by reducing sampling rather than increasing speed.
+This class includes local scanning methods that use the measurements in real-time to steer the tip to focus the scan on features of
+interest \cite{Hartman:2018ja,Wen:2018fl,Zhang:2015cf,Huang:2014dw}.
 While these have been shown to yield an order of magnitude or better
 improvement in imaging rate, they are limited in the class of samples
-that can be imaged.
+that can be imaged and do not produce a full image with all the corresponding context.
 
@@
 CS make clear that \textit{randomness} in the sampling pattern is
-essential for creating good reconstructions in the general case. The
-smooth nature of these patterns reduces their randomness and thus
-leads to less accurate reconstructions than a completely random
-sampling of the pixels for the same sampling fraction.
+essential for creating good reconstructions in the general case.
+%The smooth nature of these patterns reduces their randomness and thus leads to less accurate reconstructions than a completely random sampling of the pixels for the same sampling fraction.
 
@@
 times and negate the gains from undersampling \cite{andersson2012non}.
-In \cite{maxwell2014compressed}, we introduced a discrete undersampling scheme,
+In \cite{maxwell2014compressed}, we introduced an undersampling scheme,
 called a $\mu$-path pattern, which consists of short randomly placed,
-horizontal scans (see Fig.~\ref{fig:mu_mask} for one such pattern). It
-is designed to balance the randomness needed (to ensure good
+horizontal scans (illustrated in Fig.~\ref{fig:mu_mask}). It
+is designed to balance randomness (to ensure good
 reconstruction) with continuous scanning (to reduce the number of tip
@@
 \cite{maxwell2014compressed,Luo:2015tu, braker_hardware_2018}. 
-The main contributions of this paper relative to that past work are:
+The main contributions of this paper relative to that past work are as follows.
 \begin{itemize}
@@
 Here, we design compensators for each axis using standard loop-shaping techniques (Sec.~\ref{sec:control}), which result in a substantial increase in closed-loop bandwidth (e.g., 50 Hz to 450~Hz for the $Z$-axis).
-We show in Sec.~\ref{sec:ff_control} that one of the limitations of $\mu$-path scanning is the discontinuous $X$-axis reference (e.g., in moving between $\mu$-paths) which excites the cross-coupling modes between the $X$ and $Z$ axes, an affect which neither our prior experimental work nor the numerous simulation studies have accounted for.
+We show in Sec.~\ref{sec:ff_control} that one of the limitations of $\mu$-path scanning is the discontinuous $X$-axis reference (e.g., in moving between $\mu$-paths) which excites the cross-coupling modes between the $X$ and $Z$ axes, an effect which neither our prior experimental work nor simulation studies accounted for.
 We mitigate the cross coupling with a feed-forward design.
@@
 The clear advantage to a coarse raster scan is that it requires no modification to the instrument, only to the post-processing.
-\item The bulk of this work is based on experiment, not simulation, in contrast to prior work by ourselves \cite{Luo_nano_2015,maxwell_acc_2014} and others \cite{han_optimal_2018,jensen_reconstruction_2013,oxvig_structure_2017}.
+\item The bulk of this work is based on experiment, not simulation, in contrast to prior work by ourselves \cite{luo2015comparison,maxwell2014compressed} and others \cite{han_optimal_2018,jensen_reconstruction_2013,oxvig_structure_2017}.
 Our main focus here is on delineating the practical issues which must be addressed to effectively realize $\mu$-path scanning, which has only seen limited attention in the past.
@@
     column) Original raster-scanned image. (second column) BPDN
-    reconstruction from random, 40 pixel long $\mu$-paths with 25\%
-    sampling. (third column) BPVV reconstruction from the same
+    reconstruction from random, \textcolor{red}{40 pixel long $\mu$-paths with 25\%
+    sampling}. (third column) BPVV reconstruction from the same
     sub-sampled data. (remaining columns) Corresponding details from
@@
 In the AFM application, the probe can only measure a single pixel at a
-time. Thus the rows of $R$ are a subset of the rows of an $n$ by $n$
+time. Thus the rows of $R$ are a subset of those of an $n$ by $n$
 identity matrix. Ideally, the sparsity basis and the measurement
@@
 domain of $U$ \cite{candes2007sparsity}. In the following, we assume
-that $U^TU=I$, though in the simulation and experimental results, we
-take $U^T$ as the Discrete Cosine Transform (DCT). The DCT basis
+that $U^TU=I$, and in the simulation and experimental results we make the specific choice of $U^T$ as the Discrete Cosine Transform (DCT). The DCT basis
 generally keeps a good balance between achieving a low mutual
@@
   \min_{x} \left \| U^Tx \right \|_1 \quad
-  \text{s.t.}\quad x\in Q_p = \{x:~\|Rx - y\|_2 < \sigma\} \label{op:bp}
+  \text{subj. to}\quad %x\in Q_p = \{x:~\|Rx - y\|_2 < \sigma\} 
+  \|Rx-y\|_2 < \sigma \label{op:bp}
 \end{equation}
 where $\sigma$ represents uncertainty in the measurements. BPDN
-essentially searches for the sparsest signal from all the candidates
-that match the measurements.
+essentially searches for the sparsest signal among the candidates
+that match the measurements to within the tolerance $\sigma$.
 
@@
 \begin{equation*}
-  W = \begin{bmatrix}U^T&\alpha D_h&\beta D_v \end{bmatrix}
+  W = \begin{bmatrix}U^T&\alpha D_v&\beta D_h \end{bmatrix}
 \end{equation*}
 with ${D_v x=\text{vec}(\nabla_v X)}$ (resp.,
-${D_v x=\text{vec}(\nabla_v X)}$) representing a discrete gradient of
+${D_h x=\text{vec}(\nabla_h X)}$) representing a discrete gradient of
 a matrix in the vertical (resp., horizontal) direction (see, e.g.,
@@
 NESTA~\cite{becker_nesta_2011}.
+Note that the BPVV designation technically holds only for $\beta=0$; our experience, however, shows that including a small but nonzero $\beta$ (relative to $\alpha$) improves reconstruction.
 
@@
 Fig.~\ref{fig:BPTV_demonstration}. The first column shows two raster
-scans: the top is 512 by 512 pixel image of a CS20NG grating acquired
+scans: the top is a 512 by 512 pixel image of a CS20NG grating (Ted Pella, USA) acquired
 with an Agilent 5400 AFM and the bottom is a 256 by 256 pixel image of
 DNA acquired with an Agilent 5500 AFM. For the CS20NG grating, we
-sampled 15\% of the pixels with 50 pixel $\mu$-paths. We sampled 25\%
+sampled 15\% of the pixels with 50 pixel $\mu$-paths and 25\%
 of the DNA image with 25 pixel long $\mu$-paths. The second columns
 shows the full frame reconstructions using BPDN and the third columns
-shows the result using BPVV. The fourth column zooms in on the region
+shows the result using BPVV (\textcolor{red}{with $\alpha = ??$ and $\beta = ??$}). The fourth column zooms in on the region
 indicated by the red box in column one. Similarly, the fifth and six
@@
 largely mitigated using BPVV. Thus, in the remainder of the paper, we
-focus exclusively on BPVV. As for reconstruction time, it took about
-1.5 seconds to reconstruct the DNA image and about 7 seconds for the
-CS20NG.
+focus exclusively on BPVV. These reconstructions wth BPVV took about
+1.5 seconds for the DNA image and about 7 seconds for the
+CS20NG (on a typical laptop computer).
 
@@
 allows control of the $Z$-axis of the N9524a piezo scanner, which has
-a total range of 7 $\mu$m. Initial (course) engagement of the tip to
+a total range of 7 $\mu$m. Initial (coarse) engagement of the tip to
 the sample is performed using the PicoView software before control is
@@
 Xilinx Spartan-6 LX150 Field Programmable Gate Array (FPGA) inside the
-cRIO-9082. The cRIO includes a 16-Bit, 100 kHz NI-9215
-analog-to-digital input module and a 16-Bit, 100 kHz NI-9263
-digital-to-analog output module. All control loops are implemented
+cRIO-9082. The cRIO includes 16-bit, 100 kHz analog-to-digital input (NI-9215)) and digital-to-analog output (NI-9263) modules.
+%a 16-Bit, 100 kHz NI-9215analog-to-digital input module and a 16-Bit, 100 kHz NI-9263 digital-to-analog output module. 
+All control loops are implemented
 using a 25 kHz sampling rate.
@@
 adjust the reference signals to accomplish each task. In the
-following, $r_X$ and $r_Y$ and $r_Z$ refer to the references for the
+following, $r_X$ and $r_Y$ refer to the references for the
 $X$ and $Y$ axes while $r_{Z,s}$ and $\rzup$ refer to the $Z$-axis
@@
   down, but thinking of a knife pushed into a surface and then
-  dragged...} In our initial implementation
+  dragged...}
+
+In order to minimize the scanning time, tip tip should be moved as fast as possible when trainsitioning between $\mu$-path locations (state (1)).
+Since such speeds can be beyond the bandwidth of the $z-$axis controller, it is important to reduce the tip-sample interaction force to prevent tip sear and sample damage.
+In our initial implementation, this was achieved by
+%In our initial implementation
 \cite{braker_hardware_2018}, we insisted that the during
-tip-retraction (state-5), the cantilever tip should fully break
+tip-retraction (state (5)), the cantilever tip should fully break
 contact with the surface. Here, we impose no such requirement. Rather,
@@
 that the interaction between the tip and sample becomes purely
-adhesive. In general, stable imaging in is not possible at \rzup and
+adhesive. In general, stable imaging is not possible at \rzup and
 complete dis-engagement occasionally occurs. This can be seen in bottom pane of
@@
 After the tip-descent, we begin scanning in a ``pre-scan'' phase
-(state (3)), which is the turquoise portion of the trajectories in
+(state (3)), which is the turquoise ``tip settle'' portion of the trajectories in
 Fig.~\ref{fig:cs_cycle}. There are two reasons for this. First, we
@@
 set of filters in series with a PI controller. The open-loop frequency
-response for the $X$ and $Y$ axes is shown as the black curves in
+responses for the $X$ and $Y$ axes are shown as the black curves in
 Fig.~\ref{fig:mimo_frf_uxuy} and for the $Z$-axis in
@@
 
-We take a similar approach for the $X$ and $Y$ axes. The filters $D_x$
-and $D_y$ invert the bending modes at 350~Hz and add notch filters at
+We take a similar approach for the $X$ and $Y$ axes. The filters $D_X$
+and $D_Y$ invert the bending modes at 350~Hz and add notch filters at
 the main resonant peaks near 650~Hz. The resulting closed-loop
@@
 compensator also includes an inverse creep and hysteresis model. The
-hysteresis model is a modified Prandtl-Ishlinki type model and is
+hysteresis model is a modified Prandtl-Ishlinskii type model and is
 based on the work of \cite{kuhnen_modeling_2003}, while the drift
-compensation models the piezo creep as a simple second order transfer
+compensation models the piezo creep as a simple second-order transfer
 function with real poles and zeros. In Fig.~\ref{fig:afm_bd_dinv}, the
@@
   \end{subfigure}
-  \caption{(a) MIMO closed and open-loop FRFs, showing the dramatic
+  \caption{(a) MIMO closed and open-loop frequency-response functions (FRFs), showing the dramatic
     affect on $G_{Z,u_X}$ and $G_{Z,u_Y}$ when the feedforward
@@
 For CS scanning, we insert feed-forward filters ($F_X$ and $F_Y$ in
-Fig.~\ref{fig:afm_bd_dinv}) with three notches: one at 215~Hz, one at
-350~Hz and one at 505~Hz. Both filters are shown in
-Fig.~\ref{fig:mimo_frf_uxuy} as the dashed-pink curves and the
-resulting overall FRF is shown as the dotted-blue curves, which show a
-dramatic reduction in the cross coupling. A similar affect could be
+Fig.~\ref{fig:afm_bd_dinv}) with three notches: at 215~Hz, 350~Hz, and 505~Hz. Both filters are shown in Fig.~\ref{fig:mimo_frf_uxuy} as the dashed-pink curves and the
+resulting overall FRF is shown as the blue curves, which show a
+dramatic reduction in the cross coupling. A similar effect could be
 achieve by using a simple low-pass filter. However, to achieve the
-same 40~dB of attenuation of the mode at 215 Hz, would require, e.g.,
+same 40~dB of attenuation of the mode at 215~Hz, would require, e.g.,
 that a two-pole low-pass filter have its cut-off frequency at about
@@
 while raster scanning than while CS-scanning. On the other hand, it
-also implies that the for faster scan rates, fewer Fourier
+also implies that for faster scan rates, fewer Fourier
 coefficients are used, and so the approximation to a triangle wave is
@@
 \section{Metrics}\label{sec:rdi}
-In section~\ref{sec:results} we use three metrics to asses our
-results. The first two seek to quantify image quality of two images.
+In section~\ref{sec:results} we use three metrics to assess our
+results. The first two seek to quantify image quality between two images.
 Define a master image as $X$ and a reconstruction or corrupted version
@@
 $\mu_y$), standard deviations ($\sigma_x$ and $\sigma_y$), and
-covariance ($\sigma_{xy}$) of the image vectors $x$ and $y$. The
-variation of the SSIM used in this paper is defined as
+covariance ($\sigma_{xy}$) of the image vectors $x$ and $y$. The SSIM definition used in this paper is
 \begin{equation*}
@@
 edge), and finds the offset in the other image that produces the
-smallest error. The result of this procedure are shown in the right
+smallest error. The result of this procedure is shown in the right
 image of Fig.~\ref{fig:baseline_errors}. Although the situation is
@@
 SSIM is \baseline{one2twoAlgnSsim} for both the second and sixth image
-images and the PSNR is increases to \baseline{one2twoAlgnPsnr} and
+images and the PSNR increases to \baseline{one2twoAlgnPsnr} and
 \baseline{one2sixAlgnPsnr} respectively.
@@
 \subsection{A new metric}
-Th PSNR and SSIM metrics only assess the similarity of two images.
+The PSNR and SSIM metrics only assess the similarity of two images.
 However, in AFM imaging, pure image quality is not the only concern,
 particularly for delicate samples. What is needed is a figure of merit
-for how much damage was done to specimen during the imaging process.
+for how much damage was done to a specimen during the imaging process.
 While damage to the specimen is not really a concern while imaging a
@@
 is still a concern. In general, the faster the scan rate, the more
-difficulty the $Z$-axis control will have following the sample
+difficulty the $Z$-axis control will have in following the sample
 surface, which results in a larger $Z_d$ over more time. The actual
@@
 to full resolution raster scans at several scan rates in
-Sec.~\ref{sec:cp_full}. Second, we compare to course raster scans in
+Sec.~\ref{sec:cp_full}. Second, we compare to coarse raster scans in
 Sec.~\ref{sec:cp_subline}.
@@
 \subsection{Comparison to full raster}\label{sec:cp_full}
-We took scans of a Ted Pella CS-20NG sample grating over an area with
+We took scans of a Ted Pella CS20NG sample grating over an area with
 holes on a 500 nm pitch. The holes are 20 nm deep. We scanned 5 micron
@@
 raster scans, we took scans at 1.0~Hz, 2.5~Hz, 5.0~Hz, 8.0~Hz and
-10~Hz. We also took $\mu$-path scans with densities at 12.5\%, and
+10~Hz. We also took $\mu$-path scans with densities at 12.5\% and
 25\% and reconstructed 512 by 512 pixel images. The CS scans were
@@
 
-The free value of the deflections signal was approximately -0.6 volts
+The free value of the deflection signal was approximately $-0.6$ volts
 and we set the scanning reference to ${\rzs=\scanD{spScan}}$~volts
@@
 that does not cross any holes (i.e., a vertical line through the flat
-area), register each scan line to a common height along these columns.
+area), and register each scan line to a common height along these columns.
 This step eases comparison with the CS scans and was inspired by a
@@
 metric. These are plotted against total acquisition time in
-Fig.~\ref{fig:time_ssim} and ~\ref{fig:time_psnr}. Unfortunately, the
+Fig.~\ref{fig:time_vs_metrics}. Unfortunately, the
 SSIM and PSNR metrics are not particularly illuminating. There are
-several inconsistencies. For example, it makes no sense the 1~Hz CS
-scan at 25\% has a \emph{worse} PSNR and SSIM than 5~Hz version; nor
+several inconsistencies. For example, it makes no sense that the 1~Hz CS
+scan at 25\% has a \emph{worse} PSNR and SSIM than the 5~Hz scan; nor
 does it make sense that the 8~Hz full raster scan has a worse SSIM and
@@
 Things are clearer if we plot the RDI for each scan against total
-acquisition time, which is shown in Fig.~\ref{fig:time_damage} and
+acquisition time, which is shown in Fig.~\ref{fig:time_damage}, and
 this is where CS seems to shine. As one would expect, as imaging time
@@
 faster imaging acquisition rate. The amount of improvement is best if
-we need a very low RDI: for example, if we want to hold the RDI below
-2, then we have to take the 1~Hz raster scan (512 seconds) while we
+we need a very low RDI: for example, if we want to hold the RDI below~2, then we have to take the 1~Hz raster scan (512 seconds) while we
 can achieve the same RDI via CS in about 42 seconds with the 12.5\%
-sampling, which is a speed improvement of over 10. The higher of an
+sampling, which is a speed improvement of over a factor of 10. The higher of an
 RDI we are willing to tolerate, the advantage of CS over raster
@@
 \subsection{Comparison to Sub-line Sampling} \label{sec:cp_subline}
-Many of sub-line sampling papers assume that the lines to sample are
+Many sub-line sampling papers assume that the lines to sample are
 selected randomly \cite{han_optimal_2018, Luo_nano_2015}. An even
@@
 512 pixels. We then linearly interpolate along each column to produce
-a 512 by 512 pixel image. Again, we take these courser raster scans at
+a 512 by 512 pixel image. Again, we take these coarser raster scans at
 1.0, 2.5, 5.0, 8.0 and 10.0 Hz. The resulting images are shown in
@@
 
-Both visually and from the metrics show in From both From the metrics
-in Figs.Figs.~\ref{fig:time_ssim} and \ref{fig:time_psnr}, the 64 line
+Both visually from Fig.~\ref{fig:results_subline_images} and from the SSIM and PSNR metrics shown in 
+Figs.~\ref{fig:time_ssim} and \ref{fig:time_psnr}, the 64 line
 scan performs the worst of the all the sub-sampling methods and is
@@
 from the top (of the grating holes). The CS-scans do a poor job
-detecting this, while both course raster scans do so. However, the
-other artifacts in 64 line scan obscure the defect.
+detecting this, while both coarse raster scans do so. However, the
+other artifacts in the 64 line scan obscure the defect.
 
 Fig.~\ref{fig:improve_512} compares the amount of speed improvement of
-the different sub-sampling scheme over a full raster scans with 512
+the different sub-sampling schemes over a full raster scan with 512
 lines as a function of scan rate. As far as pure speed goes, the CS
@@
     512 lines vs scan rate for the three sets of CS scans (at 25\%,
-    15\% and 12.5\%) and courser raster scans at 128 and 64 lines.}
+    15\%, and 12.5\%) and coarser raster scans at 128 and 64 lines.}
   \label{fig:improve_512}
@@
 possible while raster scanning a full image. On the other hand, it
-appears that reconstructing a course raster scan makes more sense for
-faster scan rates. This is notable, since a course raster scan only
+appears that reconstructing a coarse raster scan makes more sense for
+faster scan rates. This is notable, since a coarse raster scan only
 requires an additional step in post-processing. It remains to be seen
@@
   [{\includegraphics[width=1 in,height=1.25in,clip,keepaspectratio]{figures/pao_headshot.jpg}}]
-  {Lucy Y. Pao} is probably not so happy that Arnold's almost done.
+  {Lucy Y. Pao} 
+  is the Palmer Endowed Chair Professor in the Electrical, Computer, and Energy Engineering Department at the University of Colorado Boulder.
+She earned B.S., M.S., and Ph.D.
+degrees in Electrical Engineering from Stanford University.
+Her research has primarily focused on engineering control systems, with applications ranging from atomic force microscopes to multi-megawatt wind energy systems.
+She is a Fellow of the IEEE and the International Federation of Automatic Control (IFAC).
+Selected recent awards include the 2012 IEEE Control Systems Magazine Outstanding Paper Award, the 2015 Society for Industrial and Applied Mathematics (SIAM) Journal on Control and Optimization Best Paper Prize, the 2017 Control Engineering Practice Award from the American Automatic Control Council, and the Scientific Award 2017 from the European Academy of Wind Energy.
+Selected recent and current professional society activities include being a Fellow of the Renewable and Sustainable Energy Institute (2009-present),
+  General Chair of the 2013 American Control Conference, member of the IEEE Control Systems Society (CSS) Board of Governors (2011-2013 and 2015), IEEE CSS Fellow Nominations Chair (2016-2018), and member of the IFAC Executive Board (2017-2020).
 

### 2019-06-25 process_data_6_5_2019.m
Fix the double blue curves x-direction pixel figure.

@@ -346,7 +346,7 @@ ha_subl = reshape(ha_subl', 3, [])';
 
 Fig_rows = mkfig(3002, 7, 4.5); clf
 ha_row = tight_subplot(2, 1, [0.1, 0.015], [.1, .05], [.085, .02], false);
-xlabel(ha_row(2), 'x-direction pixel', 'FontSize', 14)
+xlabel(ha_row(2), '$X$-direction pixel', 'FontSize', 14)
 ylabel(ha_row(1), 'height [nm]', 'FontSize', 14)
 title(ha_row(1), 'raster', 'FontSize', 14)
 title(ha_row(2), 'CS', 'FontSize', 14)
@@ -388,11 +388,17 @@ for k=1:length(rast_exps)
                 rast_exps{k}.meta_in.raster_freq)
             continue
     end
+
+    rate_k = rast_exps{k}.meta_in.raster_freq;
+    
+    if abs(rate_k - 1.0)<0.1 && k~=1
+        continue
+    end
+    
     ax_im = ax_im(fig_col);
     
     imk = rast_exps{k}.pix_mat_pinned;% - mean(rast_exps{k}.pix_mat_pinned(:));
     
-    rate_k = rast_exps{k}.meta_in.raster_freq;
     imagesc(ax_im, imk, clr_range);
     colormap(ax_im, 'gray');
     stit = sprintf('raster %d (%.1f Hz)', rast_exps{k}.npix_y_og, rate_k);
@@ -404,12 +410,13 @@ for k=1:length(rast_exps)
         hold(ha_row(1), 'on')
         ha_row(1).ColorOrderIndex = fig_col;
         plot(ha1(fig_row, fig_col), [1, 512], [row_idx, row_idx], 'r');
+        
         row_hands(fig_col) = plot(ha_row(1), imk(row_idx, :)*AFM.volts2nm_z());
         row_hands(fig_col).DisplayName = sprintf('%.1f Hz', rate_k);
         hold(ha_row(1), 'on')
         
     end
-    
+%     pause
 
 end
 remove_ticks(ha1)

### 2019-06-25 plot_bptv_vs_bp.m
Update for new NESTA_mine calling signature.

@@ -5,7 +5,7 @@ clc
 % ------------ Row 1, CS20NG -------------------------
 im_og = double(imread('cs20ng.png'));
 % im_og = im_og(1:2:512, 1:2:512);
-mu_len = 20;
+mu_len = 50;
 samp_frac = 0.15;
 n = size(im_og, 1);
 
@@ -72,11 +72,12 @@ function [ssm, X_bptv] = fun(im_og, b, E_fun, Et_fun, opts, alpv, alph)
 
     opts.alpha_v = alpv;
     opts.alpha_h = alph;
-    
-    mu = 1e-5;
-    delta = 0.01;
+    opts.mu = 1e-5;
+    opts.sigma = 0.01;
+%     mu = 1e-5;
+%     delta = 0.01;
 
-    x_bptv = NESTA_mine(E_fun, Et_fun, b, mu, delta, opts);
+    x_bptv = NESTA_mine(E_fun, Et_fun, b, opts);
 
     X_bptv = CsTools.pixvec2mat(x_bptv, n);
     figure(7)
@@ -103,15 +104,13 @@ function t_recon = cp_bptv_bp(im_og, pix_idx, prefix, figbase)
     
     
     opts = NESTA_opts('U', U_fun, 'Ut', Ut_fun, 'alpha_v', 0.0705, 'alpha_h', .4037,...
-        'verbose', 5, 'TolVar', 1e-5);
+        'verbose', 5, 'TolVar', 1e-5, 'mu', 1e-3, 'sigma', 0.001);
     
     b = CsTools.pixmat2vec(im_og);
     b = b(pix_idx);
     
-    mu = 1e-3;
-    delta = .001
     tic 
-    x_bptv = NESTA_mine(E_fun, Et_fun, b, mu, delta, opts);
+    x_bptv = NESTA_mine(E_fun, Et_fun, b, opts);
     t_recon = toc;
     X_bptv = CsTools.pixvec2mat(x_bptv, n);
     
@@ -120,7 +119,7 @@ function t_recon = cp_bptv_bp(im_og, pix_idx, prefix, figbase)
         'verbose', 5, 'TolVar', 1e-5);
     
     
-    x_bp = NESTA_mine(E_fun, Et_fun, b, mu, delta, opts);
+    x_bp = NESTA_mine(E_fun, Et_fun, b, opts);
     X_bp = CsTools.pixvec2mat(x_bp, n);
     
     

### 2019-06-25 latex/afm-cs-main.tex
Add bio info for myself.

@@
   [{\includegraphics[width=1 in,height=1.25in,clip,keepaspectratio]{figures/braker_headshot.jpg}}]
-  {Roger A. Braker} is so happy that all this is almost done.
+  {Roger A. Braker} earned the B.A. degree in physics from the University of Oklahoma in 2005 and the M.S. degree in electrical engineering from the University of Colorado in 2017.
+  Since 2014, he has been a graduate student in the Electrical, Computer, and Energy Engineering
+  Department at the University of Colorado Boulder.
 

### 2019-06-25 latex/afm-cs-main.tex
Minor text tweaks.
Change CS20NG to CS-20NG.
fix alha beta.

@@
 Fig.~\ref{fig:BPTV_demonstration}. The first column shows two raster
-scans: the top is a 512 by 512 pixel image of a CS20NG grating (Ted Pella, USA) acquired
+scans: the top is a 512 by 512 pixel image of a CS-20NG grating (Ted Pella, USA) acquired
 with an Agilent 5400 AFM and the bottom is a 256 by 256 pixel image of
-DNA acquired with an Agilent 5500 AFM. For the CS20NG grating, we
+DNA acquired with an Agilent 5500 AFM. For the CS-20NG grating, we
 sampled 15\% of the pixels with 50 pixel $\mu$-paths and 25\%
@@
 1.5 seconds for the DNA image and about 7 seconds for the
-CS20NG (on a typical laptop computer).
+CS-20NG (on a typical laptop computer).
 
@@
   \text{PSNR}(x,y) = 10\log_{10}\frac{L^2}
-  {\sqrt{\frac{1}{p^2} \sum_{i=1}^{m}( x_{i} - y_{i})^2 }}.
+  {\sqrt{\frac{1}{m} \sum_{i=1}^{m}( x_{i} - y_{i})^2 }}.
 \end{equation*}
@@
 \subsection{Comparison to full raster}\label{sec:cp_full}
-We took scans of a Ted Pella CS20NG sample grating over an area with
+We took scans of a Ted Pella CS-20NG sample grating over an area with
 holes on a 500 nm pitch. The holes are 20 nm deep. We scanned 5 micron
@@
 taken with scan velocities equivalent to raster scan rates of 1.0~Hz,
-2.0~Hz, 5.0~Hz and 8.0~Hz. For all CS scans, the $\mu$-paths are
+2.0~Hz, 4.0~Hz, 5.0~Hz and 8.0~Hz. For all CS scans, the $\mu$-paths are
 $\scanD{muLenNM}$ nm long, which translates to $\scanD{muLenPix}$
@@
 cantilever was a Budget Sensors ContAI-G, with a nominal length of 450
-microns and spring constant of $k=0.2$~N/m.
+microns and spring constant of $0.2$~N/m.
 
@@
 The CS scans were reconstructed with BPVV. We set
-${\alpha_v=\scanD{alpv}}$ and ${\alpha_h=\scanD{alph}}$. For the
+${\alpha=\scanD{alph}}$ and ${\beta=\scanD{alpv}}$. For the
 raster scans, we discard data from the re-trace and divided the

### 2019-06-25 latex/afm-cs-main.tex
Fix fig 5 caption.

@@
   \includegraphics[width=1\textwidth]{figures/AFM_loop_xyz.pdf}
-  \caption{Block diagram of the $Z$-axis control loop. The anti-windup
-    is active for decision index $i\in\{0,1,5\}$, which correspond to
-    states such that $r_Z=\rzup$.}
+  \caption{Block diagram of the AFM control loop for all three axes.
+    Not shown is anti-windup for the $Z$-axis integrator, which is active
+    when $r_Z=\rzup$ (states 1 and 5) where sensor saturation is possible.}
   \label{fig:afm_bd_dinv}

### 2019-06-25 latex/afm-cs-main.tex
setpoints.

@@
 adjust the reference signals to accomplish each task. In the
-following, $r_X$ and $r_Y$ refer to the references for the
-$X$ and $Y$ axes while $r_{Z,s}$ and $\rzup$ refer to the $Z$-axis
-setpoints during scanning and retraction, respectively.
+following, $r_X$ and $r_Y$, $r_Z$ refer to the references for the
+$X$, $Y$, and $Z$ axes, respectively. The $Z$-axis setpoint $r_Z$
+takes on values $r_{Z,s}$ (the scanning setpoint) and $\rzup$ (the
+retraction setpoint).
 

### 2019-06-25 process_data_6_5_2019.m
Use actual percentage in table II.

@@ -860,8 +860,8 @@ function S = state_times_table(cs_exps, hz_skip, frac_skip)
     for k=1:length(cs_exps)
         cst = cs_exps{k}.get_state_times();
         rate = cs_exps{k}.equiv_raster_rate();
-        frac = cs_exps{k}.meta_in.actual_sub_samble_perc;
-        
+%         frac = cs_exps{k}.meta_in.actual_sub_samble_perc;
+        frac = cs_exps{k}.sub_sample_frac()*100;
         if any(abs(frac_skip - frac) < 0.5)
             continue
         end

### 2019-06-25 latex/afm-cs-main.tex
Fix fig 8 caption.

@@
   \includesvg[scale=.98]{figures/cs_raster_images_6-5-2019.svg}
-  \caption{Raster and compressed sensing images of a 5 micron square
-    area of the CS-20NG grating. All images are 512$\times$512 pixels:
-    the raster images marked as 64 and 128 lines have been
-    interpolated. The rows of pixels indicated by the red line are
+  \caption{Raster and compressed sensing images of a 5 micron by 5 micron 
+    area of the CS-20NG grating. All images are 512$\times$512 pixels.
+    The rows of pixels indicated by the red lines are
     shown in Fig.~\ref{fig:pixel_rows}.}

### 2019-06-25 latex/afm-cs-main.tex
Add colorbar.

@@
 \begin{align}
-  \text{RDI} &= \frac{1}{T_s}\sum_{k=0}^N \frac{1}{k} \left(Z_{d,k} - r_{Z,s}\right)^2 \label{eqn:RDI}\\
+  \text{RDI} &= \frac{1}{T_s}\sum_{k=1}^N \frac{1}{k} \left(Z_{d,k} - r_{Z,s}\right)^2 \label{eqn:RDI}\\
 \end{align}
@@
 color maps represent a range of $\pm$20 nm. The rows of pixels
-indicated by the red lines are shown as cross sections
+indicated by the red lines are shown as cross sections in
 Fig.~\ref{fig:pixel_rows}.
 
+% \begin{figure}
+%   \begin{subfigure}{.48\textwidth}
+%     \includesvg[width=1\textwidth]{figures/ }
+%     \caption{ }
+%     \label{fig: }
+%   \end{subfigure}
+%   \begin{subfigure}{.48\textwidth}
+%     \includegraphics[width=1\textwidth]{figures/ }
+%     \caption{ }
+%     \label{fig: }
+%   \end{subfigure}
+%   \caption{}
+%   \label{fig: }
+% \end{figure}
 \begin{figure*}
-  \centering
-  \includesvg[scale=.98]{figures/cs_raster_images_6-5-2019.svg}
+  % \begin{center}
+  \parbox{.1\textwidth}{\phantom{p}}
+  \begin{subfigure}{.8\textwidth}
+  \includesvg[width=1\textwidth]{figures/cs_raster_images_6-5-2019.svg}
+\end{subfigure}
+\begin{subfigure}[t]{.09\textwidth}
+  \vspace{-18.2em}
+    \includesvg[width=1\textwidth]{figures/colorbar.svg}
+  \end{subfigure}
+  % \hfill
+% \end{center}
   \caption{Raster and compressed sensing images of a 5 micron by 5 micron 
@@
 \end{figure*}
+
+% \begin{figure*}
+%   % \centering
+%   \includesvg[scale=.98]{figures/cs_raster_images_6-5-2019.svg}
+%   \caption{Raster and compressed sensing images of a 5 micron by 5 micron 
+%     area of the CS-20NG grating. All images are 512$\times$512 pixels.
+%     The rows of pixels indicated by the red lines are
+%     shown in Fig.~\ref{fig:pixel_rows}.}
+%   \label{fig:resultsF1_images}
+% \end{figure*}
 
@@
 
+%%%%%%%%% then the Bibliography, if any %%%%%%%%%
+% \bibliographystyle{plain} % or "siam", or "alpha", etc.
+\bibliographystyle{IEEEtran} % or "siam", or "alpha", etc.
+\bibliography{braker_bibs,Andersson_bibs,Yufans_bibs} % Bib database in "refs.bib"
+
 \begin{IEEEbiography}
@@
 
-%%%%%%%%% then the Bibliography, if any %%%%%%%%%
-% \bibliographystyle{plain} % or "siam", or "alpha", etc.
-\bibliographystyle{IEEEtran} % or "siam", or "alpha", etc.
-% \nocite{*} % list all refs in database, cited or not
-\bibliography{braker_bibs,Andersson_bibs,Yufans_bibs} % Bib database in "refs.bib"
-
 %%%%%%%%% then the Appendices, if any %%%%%%%%%

### 2019-06-25 latex/afm-cs-main.tex
Update on Overleaf.

@@
 In order to minimize the scanning time, tip tip should be moved as fast as possible when trainsitioning between $\mu$-path locations (state (1)).
-Since such speeds can be beyond the bandwidth of the $z-$axis controller, it is important to reduce the tip-sample interaction force to prevent tip sear and sample damage.
-In our initial implementation, this was achieved by
-%In our initial implementation
-\cite{braker_hardware_2018}, we insisted that the during
+Since such speeds can be beyond the bandwidth of the $z-$axis controller, it is important to reduce the tip-sample interaction force to prevent tip wear and sample damage.
+In our initial implementation \cite{braker_hardware_2018},
+%we insisted that the during
+this was achieved by insisting that during the
 tip-retraction (state (5)), the cantilever tip should fully break
@@
 that the interaction between the tip and sample becomes purely
-adhesive. In general, stable imaging is not possible at \rzup and
-complete dis-engagement occasionally occurs. This can be seen in bottom pane of
+adhesive. In general, stable imaging is not possible with the setpoint at \rzup and
+complete dis-engagement occasionally occurs. This can be seen in the bottom pane of
 Fig.~\ref{fig:cs_cycle} during the second $XY$-move (black portion) where the tip detaches partway through the move.
@@
 compared to completely detaching the tip between each $\mu$-path.
-By eliminating the normal force into the sample, we are able to take dozens of images with a single probe without a noticeable degradation in image quality.
+By essentially eliminating the normal force into the sample, we are able to take dozens of images with a single probe without a noticeable degradation in image quality and is a key component to the new quality metric we introduce in Sec.~\ref{sec:rdi}.
 However, completely characterizing the damage done to the tip and sample with this scheme compared complete detachment (which can also damage the probe \cite{meyer_atomic_1992}), remains an outstanding goal.
@@
 have observed that there is less noise in the deflection signal while
-the $XY$-stage is in motion compared to sitting still. More
+the $XY$-stage is in motion compared to sitting still. Second, and more
 importantly, it lets us bring the $X$-axis to its scanning velocity at

### 2019-06-25 plot_cs_cycle.m
Adjust legend of fig 4.

@@ -105,7 +105,8 @@ end
 ylim(ha(2), [0, 5]);
 ylim(ha(3), [-20, 90])
 
+hands(3).DisplayName = 'tip settle/pre-scan';
 
-leg = legend(hands, 'NumColumns', 1, 'Position', [0.6709 0.5861 0.2993 0.1656]);
+leg = legend(hands, 'NumColumns', 1, 'Position', [0.6064 0.6017 0.3808 0.1656]);
 %%
 save_fig(Fig, 'latex/figures/cs_cycle', false)

### 2019-06-25 build_controllers_with_xyFF_DxDy.m
Do not use anything from afm-cs/matlab-code/functions.

@@ -8,7 +8,7 @@ clear all
 % Options
 figbase  = 50;
 verbose = 0;
-
+rmpath('/home/arnold/matlab/afm-cs/matlab-code/functions/')
 addpath('functions');
 addpath(fullfile('functions', 'state_space_x'));
 

### 2019-06-25 functions/close_three_axis.m

@@ -1,0 +1,77 @@
+% [HH] = close_three_axis(Gxyz_frf, xdir_cntrl, Dy, Dzki, Dinv)  
+%
+% Construct the entire closed transfer function for all three afm axes.
+% 
+% Arguments
+% ----------
+%   Gxyz_frf:  An FRD object of the full MIMO frequency response;
+%   xdir_cntrl: a struct of the x-direction state-space stuff, obtain this from 
+%               get_xdir_standard_control();
+%   Dy:         This should be a simple PI compensator (for now, the code works
+%               fine with a more general TF, but labview doesnt implement that yet.
+%   Dzki:      Z-direction PI controller
+%   Dinv:      Z-direction bending mode inversion
+%
+%  The resulting compensator will have the form (all blocks are transfer
+%  matrices):
+% 
+%    R-->[ M ]--->O---->[ D2 ]-->[ G ]--+---> y
+%                 |                     |
+%                 +-----[ D1 ]<---------+
+%
+% y =        G*D1
+%      --------------- * M * R
+%      I + D2*G*G1
+%
+%            R-prime
+%              ^  (Mss is sort of fictitious with state-space, and this is what
+%              |   we usually want from r-prime)
+%              |
+%    R-->[ M ]--> [M_ss ]--->O---->[Dki*D ]-->[ G ]----+---> y
+%                            |                      |
+%                            +-----[ Dss ]<---------+
+
+function [HH] = close_three_axis(Gxyz_frf, xdir_cntrl, ydir_cntrl, Dzki, Dinv)
+  
+  % State-space parts
+  Dssx = xdir_cntrl.Dss; % The feedback
+  Mssx = xdir_cntrl.Mss; % The feedforward
+  % TF parts
+  Dx_ff = xdir_cntrl.M;
+  Dx = xdir_cntrl.D;       % The transfer-function feedback (if any)
+  Dki_x = xdir_cntrl.Dki;
+  
+  Dssy = ydir_cntrl.Dss; % The state-space feedback (if any)
+  Mssy = ydir_cntrl.Mss; % The state-space feedforward (if any)
+  Dy_ff = ydir_cntrl.M; % the real feedforward. (if any)
+  Dy = ydir_cntrl.D;       % The transfer-function feedback (if any)
[…]

### 2019-06-25 functions/get_xdir_loop_shaped_control.m

@@ -4,8 +4,6 @@ function xdirControl = get_xdir_loop_shaped_control(verbose)
         verbose = true;
     end
 
-    addpath(fullfile(getCsRoot(), 'matlab-code', 'functions'));
-    
     % ------- Load Plants -----
     [plants, frf_data] = CanonPlants.plants_ns14(9, '5micron');
     

### 2019-06-25 functions/get_xdir_standard_control.m

@@ -1,10 +1,7 @@
 function xdirControl = get_xdir_standard_control(type, gam)
-addpath(fullfile(getCsRoot(), 'matlab-code', 'functions'));
-addpath(fullfile(getCsRoot(), 'matlab-code', 'functions', 'state_space_x'));
+
 
 md = 1;
-
-
 
 % ------- Load Plants -----
 [plants, frf_data] = CanonPlants.plants_ns14(9);

### 2019-06-25 functions/impulse2ss.m

@@ -1,0 +1,86 @@
+% [Ad, Bd, Cd] = impulse2ss(yy_exp, r, s)
+%
+% Performs the eigensystem realization algorithm from the paper,
+%   "Multivariable Model Identification from Frequency Response Data", by
+%   Robert N. Jacques and David W. Miller, CDC, 1993.
+%
+% Inputs:
+%   YY_imp: the impulse response data. This should be a 3d array with No
+%   rows, Ni columns and length(t) pages.
+%
+%   r, s are integers, of rows and columns of hankel. Or something. Go look
+% this up.
+
+
+
+
+function [Ad, Bd, Cd, sigmas] = impulse2ss(yy_IMP, r, s, Ns)
+
+no = size(yy_IMP, 1);
+ni = size(yy_IMP, 2);
+fprintf('Assuming number of outputs = %d, number inputs = %d\n', no, ni) 
+% Form Hankel matrices and start the Eigen system Realization
+k = 1;
+H0 = impulse2hankel(yy_IMP, k, r, s,ni, no);
+k = 2;
+Hmag1 = impulse2hankel(yy_IMP, k, r, s, ni,no);
+
+fprintf('size of Hankel is %d x %d \n', size(Hmag1,1), size(Hmag1,2));
+[P, D, Q] = svd(H0, 'econ');
+% % H = P*D*Q'
+% keyboard
+I_no = eye(no);
+I_ni = eye(ni);
+Z_no = zeros(no,no);
+Z_ni = zeros(ni, ni);
+
+
+Ep = repmat(Z_no, r,1);
+Ep(1:no,1:no) = I_no;
+
+Em = repmat(Z_ni, s, 1);
+Em(1:ni,1:ni) = I_ni;
+
+% SISO case:
+% Ep    = zeros(r,1);
+% Ep(1) = 1;
+% Em    = zeros(r,1);
+% Em(1) = 1;
+
+if exist('Ns', 'var')
+   Dp = zeros(size(D));
+   D_neg_sqrt = Dp;
+   D_sqrt     = Dp;
+   
+   D_neg_sqrt(1:Ns, 1:Ns) = (D(1:Ns, 1:Ns))^-0.5;
+   D_sqrt(1:Ns,1:Ns)      = sqrt(D(1:Ns, 1:Ns));
+else
+    D_neg_sqrt = D^-0.5;
[…]

### 2019-06-25 functions/pole_zero_freq.m

@@ -1,0 +1,18 @@
+function [pl_ws, zr_ws, pl_zet, zr_zet] = pole_zero_freq(G)
+   pls = pole(G);
+   zrs = tzero(G);
+   
+   
+   if ~(G.Ts > 0)
+       error('This function only works with discrete time models');
+   end
+   
+   Ts = G.Ts;
+   sloc_pl = -log(pls)/Ts;
+   sloc_zr = -log(zrs)/Ts;
+   pl_ws = abs(sloc_pl)/2/pi;
+   zr_ws = abs(sloc_zr)/2/pi;
+   
+   pl_zet = real(pls)./pl_ws;
+   zr_zet = real(zrs)./zr_ws;
+end

### 2019-06-25 latex/afm-cs-main.tex
Fix typos.
Minor tweaks to text.

@@
 \begin{equation}
-  N = \left\lceil\lim_{z\rightarrow 1} \frac{1-H_x}{z-1}\right\rceil
+  N = \left\lceil\lim_{z\rightarrow 1} \frac{1-H_X}{z-1}\right\rceil
 \end{equation}
-time steps, where $H_x$ is closed-loop transfer function for the
-$x$-axis. For our system $N=111$. By initiating the scan while the
+time steps, where $H_X$ is closed-loop transfer function for the
+$X$-axis. For our system $N=111$. By initiating the scan while the
 $Z$-axis settles, we eliminate much of this overhead.
@@
 function with real poles and zeros. In Fig.~\ref{fig:afm_bd_dinv}, the
-hysteresis inversion is indicated by $\mathcal{H}^{-1}[\cdot]$. We
+hysteresis inversion is indicated by $\mathcal{H}_X^{-1}[\cdot]$. We
 have found that the inclusion of these extra compensators limits the
@@
 For CS scanning, we insert feed-forward filters ($F_X$ and $F_Y$ in
-Fig.~\ref{fig:afm_bd_dinv}) with three notches: at 215~Hz, 350~Hz, and 505~Hz. Both filters are shown in Fig.~\ref{fig:mimo_frf_uxuy} as the dashed-pink curves and the
+Fig.~\ref{fig:afm_bd_dinv}) with three notches: at 215~Hz, 350~Hz, and
+505~Hz. Both filters are shown in Fig.~\ref{fig:mimo_frf_uxuy} as the
+dashed-pink curves and the
 resulting overall FRF is shown as the blue curves, which show a
@@
 achieve by using a simple low-pass filter. However, to achieve the
-same 40~dB of attenuation of the mode at 215~Hz, would require, e.g.,
+same 40~dB of attenuation of the mode at 215~Hz would require, e.g.,
 that a two-pole low-pass filter have its cut-off frequency at about
@@
 \begin{align}
-  \text{RDI} &= \frac{1}{T_s}\sum_{k=1}^N \frac{1}{k} \left(Z_{d,k} - r_{Z,s}\right)^2 \label{eqn:RDI}\\
+  \text{RDI} &= \frac{1}{T_s}\sum_{k=1}^N \frac{1}{k} \left(Z_{d,k} - r_{Z,s}\right)^2 \label{eqn:RDI}
 \end{align}

### 2019-06-26 latex/afm-cs-main.tex
Use the same alpha and beta for sim as for experiment.

@@
 the application of advanced controllers
-\cite{Rana:2018es,Yong:2015gr,butterworth2010adaptive,salapaka2002high}.
+\cite{Rana:2018es,Yong:2015gr,butterworth_discrete_2012,salapaka2002high}.
 By combining different techniques, there are current generation,
@@
     column) Original raster-scanned image. (second column) BPDN
-    reconstruction from random, \textcolor{red}{40 pixel long $\mu$-paths with 25\%
-    sampling}. (third column) BPVV reconstruction from the same
+    reconstruction from random, $\mu$-path sampling.
+    (third column) BPVV reconstruction from the same
     sub-sampled data. (remaining columns) Corresponding details from
-    the red boxes indicated in the raster image. The results show that
-    BPVV reduces the artifacts arising from the horizontal scans of
-    the $\mu$-path pattern that appear in BPDN reconstructions.}
+    the red boxes indicated in the raster image.
+    The top row uses 15\% sampling with 50 pixel $\mu$-paths and the
+    bottom row uses 25\% sampling with 25 pixel $\mu$-paths.
+    The results show that BPVV reduces the artifacts arising from the
+    horizontal scans of the $\mu$-path pattern that appear in BPDN
+    reconstructions.}
   \label{fig:BPTV_demonstration}
@@
 shows the full frame reconstructions using BPDN and the third columns
-shows the result using BPVV (\textcolor{red}{with $\alpha = ??$ and $\beta = ??$}). The fourth column zooms in on the region
+shows the result using BPVV (with $\alpha = 0.75$ and $\beta = 0.1$). The fourth column zooms in on the region
 indicated by the red box in column one. Similarly, the fifth and six

### 2019-06-26 plot_bptv_vs_bp.m

@@ -58,39 +58,6 @@ fprintf('CS20NG reconstruction time: %.2f\n', t_recon_cs20ng);
 fprintf('DNA reconstruction time: %.2f\n', t_recon_dna);
 
 
-function [ssm, X_bptv] = fun(im_og, b, E_fun, Et_fun, opts, alpv, alph)
-    n = size(im_og, 1);
-    
-%     U_fun = @(x) idct(x);
-%     Ut_fun = @(x) dct(x);
-%     
-%     E_fun = @(x) CsTools.E_fun1(x, pix_idx);
-%     Et_fun = @(x) CsTools.Et_fun1(x, pix_idx, n, n);
-%         
-%     opts = NESTA_opts('U', U_fun, 'Ut', Ut_fun, 'alpha_v', alpv, 'alpha_h', alph,...
-%         'verbose', 5, 'TolVar', 1e-5);
-
-    opts.alpha_v = alpv;
-    opts.alpha_h = alph;
-    opts.mu = 1e-5;
-    opts.sigma = 0.01;
-%     mu = 1e-5;
-%     delta = 0.01;
-
-    x_bptv = NESTA_mine(E_fun, Et_fun, b, opts);
-
-    X_bptv = CsTools.pixvec2mat(x_bptv, n);
-    figure(7)
-    imagesc(X_bptv, [0, 1])
-    colormap('gray')
-    
-    ssm = -psnr(im_og, X_bptv, 1);
-    s= sprintf('alph = %f, alpv = %f, ssm = %f\n', alph, alpv, ssm);
-    title(s)
-    fprintf('%s', s);
-end
-
-
 function t_recon = cp_bptv_bp(im_og, pix_idx, prefix, figbase)
     
     im_og = im_og / max(im_og(:));
@@ -103,7 +70,7 @@ function t_recon = cp_bptv_bp(im_og, pix_idx, prefix, figbase)
     Et_fun = @(x) CsTools.Et_fun1(x, pix_idx, n, n);
     
     
-    opts = NESTA_opts('U', U_fun, 'Ut', Ut_fun, 'alpha_v', 0.0705, 'alpha_h', .4037,...
+    opts = NESTA_opts('U', U_fun, 'Ut', Ut_fun, 'alpha_v', 0.1, 'alpha_h', .75,...
         'verbose', 5, 'TolVar', 1e-5, 'mu', 1e-3, 'sigma', 0.001);
     
[…]

### 2019-06-26 process_data_6_5_2019.m
Make the text in the metrics color legend white.

@@ -541,7 +541,7 @@ wo = 7;
 yo = 35;
 h = 3;
 fac = (xs(1) + wo)/xs(1);
-
+text_color = [0.97, 0.97, 0.97];
 for k=1:7
 % rate_k = rastm_512.rate(k);
 rate_k = color_ord_map(1, k);
@@ -550,7 +550,7 @@ clr = ha.ColorOrder;
 x1 = xs(k);
 
 x2 = x1*fac;
-w = (xs(k+1) - xs(k))*.9;
+w = (xs(k+1) - xs(k))*.92;
 
 X = [x1, x1+w, x1+w, x1];
 Y = [yo, yo, yo+h, yo+h];
@@ -558,8 +558,8 @@ C= clr(k,:);
 pt = patch(ha, X, Y, C);
 
 st = sprintf('%.1f Hz', rate_k);
-tx = text(ha, mean(X(1:2))-1, mean(Y([1,3])), st, 'VerticalAlignment', 'middle',...
-    'HorizontalAlignment', 'center');
+tx = text(ha, mean(X(1:2))-0.5*x1/wo, mean(Y([1,3])), st, 'VerticalAlignment', 'middle',...
+    'HorizontalAlignment', 'center', 'Color', text_color);
 
 end
 ylim(ha, [0, 38])
@@ -629,8 +629,8 @@ C= clr(k,:);
 pt = patch(ha_ssm, X, Y, C);
 
 st = sprintf('%.1f Hz', rate_k);
-tx = text(ha_ssm, mean(X(1:2)), mean(Y([1,3])), st,...
-    'VerticalAlignment', 'middle', 'HorizontalAlignment', 'center');
+tx = text(ha_ssm, mean(X(1:2))-0.25*x1/wo, mean(Y([1,3])), st,...
+    'VerticalAlignment', 'middle', 'HorizontalAlignment', 'center', 'Color', text_color);
 
 end
 xlim(ha_ssm, [6, 230])
@@ -692,7 +692,8 @@ C= clr(k,:);
 pt = patch(ha_psn, X, Y, C);
 
 st = sprintf('%.1f Hz', rate_k);
-tx = text(ha_psn, mean(X(1:2)), mean(Y([1,3])), st, 'VerticalAlignment', 'middle', 'HorizontalAlignment', 'center');
+tx = text(ha_psn, mean(X(1:2))-0.25*x1/wo, mean(Y([1,3])), st,...
[…]

### 2019-06-27 latex/coverletter.tex
Start coverletter

\documentclass[a4paper,twoside]{article}
\usepackage[margin=1in]{geometry}
\begin{document}
\hspace*{0.45\linewidth}
\begin{minipage}{0.52\linewidth}
Roger A. Braker\par
University of Colorado, Boulder\par
Dept of Electrical, Computer and Energy Engineering \par
425 UCB\par
Boulder, CO 80305\par
United States\par
roger.braker@colorado.edu\par
\today
\end{minipage}
\par\bigskip

Dear Prof. Qingze Zou,\par\bigskip
% check this is correct

It is our pleasure to submit this manuscript entitled ``Improving the Image Acquisition Rate of an Atomic Force Microscope Through Sub-sampling and Reconstruction'' (authored by Roger A. Braker Yufan Luo, Lucy Y. Pao and Sean Andersson) for consideration to be published in the Transactions on Mechatronics. This paper is submitted for possible publication in the Focused Section on Nano/Micro 
Motion  Systems:  Design,  Sensing  and  Control(NMMS).

\par\bigskip
\noindent Sincerely,
\par\bigskip
\noindent R.A. Braker\par
\noindent Y. Luo\par
\noindent L.Y. Pao
\noindent S. Andersson

\end{document}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2019-06-27 latex/coverletter.tex
Add sponsors to coverletter.

@@
 \documentclass[a4paper,twoside]{article}
-\usepackage[margin=1in]{geometry}
+\usepackage[margin=1.5in]{geometry}
 \begin{document}
@@
 
-It is our pleasure to submit this manuscript entitled ``Improving the Image Acquisition Rate of an Atomic Force Microscope Through Sub-sampling and Reconstruction'' (authored by Roger A.
+It is our pleasure to submit this manuscript entitled \textit{Improving the Image Acquisition Rate of an Atomic Force Microscope Through Sub-sampling and Reconstruction} (authored by Roger A.
 Braker Yufan Luo, Lucy Y.
@@
 Motion  Systems:  Design,  Sensing  and  Control(NMMS).
+
+While sub-sampling schemes have seen increased attention recently, many of the existing studies are based purely on simulation.
+In contrast, this manuscript largely focuses on the experimental challenges which must be overcome to realize a sub-sampling scheme.
+
+The manuscript has not been published nor is it under review elsewhere.
+All four authors agree to submit the manuscript in its present form to the IEEE/ASME Transactions Mechatronics focused section NMMS.
+This work was supported in part by Agilent Technologies, Inc, The US National Science Foundation (under Grants CMMI-1234980, CMMI-1234845, CMMI-1562031, and DBI-1352729), and the Hanse Wissenschaftskolleg in Delmenhorst, Germany.
+Thank you for the consideration and we look forward to hearing from you.
 

### 2019-06-28 latex/afm-cs-main.tex
Make the text in the metrics color legend white.
Update on Overleaf.

@@
 \subsection{Feedforward Control}\label{sec:ff_control}
-Unfortunately, as the bottom row of plots in
+As the bottom row of plots in
 Fig.~\ref{fig:mimo_frf_uxuy} makes clear, there is a strong
@@
 dashed-pink curves and the
-resulting overall FRF is shown as the blue curves, which show a
+resulting overall FRF is shown as the
+blue curves, which show a
 dramatic reduction in the cross coupling. A similar effect could be
@@
 coefficients are used, and so the approximation to a triangle wave is
-worse.
+worse, leading to scans which do not cover the entire intended range..
 
 \section{Metrics}\label{sec:rdi}
-In section~\ref{sec:results} we use three metrics to assess our
-results. The first two seek to quantify image quality between two images.
-Define a master image as $X$ and a reconstruction or corrupted version
+In this section we introduce the three metrics used to assess our
+results in Sec.~\ref{sec:results}. The first two seek to quantify image quality between two images.
+To that end, define a master image as $X$ and a reconstruction or corrupted version
 as $Y$, with each having $s\times h=m$ pixels. Let $x=\textrm{vec}(X)$
 and $y=\textrm{vec}(Y)$. Let $L$ be the dynamic range of the master
-image $x$. Then the peak signal to noise ratio (PSNR) is given by
+image $x$. The first metric is the peak signal to noise ratio (PSNR), given by
 \begin{equation*}
@@
 
+The second metric is the Structured Similarity Index Metrix (SSIM).
 The goal of the SSIM is to compare two image's structure,
@@
   % \includesvg[width=0.7\columnwidth]{figures/baseline_errors_aligned_1Hz.svg}
-  \includesvg[width=0.7\columnwidth]{figures/baseline_errors_1and6.svg}
+  \includesvg[width=0.9\columnwidth]{figures/baseline_errors_1and6.svg}
   \caption{Errors between the first and sixth raster scans in a
@@
 However, in AFM imaging, pure image quality is not the only concern,
-particularly for delicate samples. What is needed is a figure of merit
-for how much damage was done to a specimen during the imaging process.
-While damage to the specimen is not really a concern while imaging a
+particularly for delicate samples. While damage to the specimen is not really a concern while imaging a
 hard calibration grating, it plays a prominent role for biological
 samples~\cite{ando_highspeed_2008}, though damage to the probe itself
-is still a concern. In general, the faster the scan rate, the more
+is still a concern even with hard samples. In general, the faster the scan rate, the more
 difficulty the $Z$-axis control will have in following the sample
@@
 damage done by a given $Z_d$ will depend on the spring constant of the
-cantilever and the softness of the specimen. Nonetheless, we propose a
-metric, which we call the Relative Damage Index (RDI) which computes
-the power in the deflection signal for a given scan. That is,
+cantilever and the softness of the specimen. To capture these concerns, we propose a
+metric, which we call the Relative Damage Index (RDI) that computes
+the power in the deflection signal for a given scan. The RDI,given by
 
 \begin{align}
-  \text{RDI} &= \frac{1}{T_s}\sum_{k=1}^N \frac{1}{k} \left(Z_{d,k} - r_{Z,s}\right)^2 \label{eqn:RDI}
+  \text{RDI} &= \frac{1}{T_s}\sum_{k=1}^N \frac{1}{k} \left(Z_{d,k} - r_{Z,s}\right)^2, \label{eqn:RDI}
 \end{align}
-The idea behind the RDI is that increased scan rates lead to larger
-deflection signals (and thereby increased force into the specimen) at
-each surface feature, which the RDI accumulates.
+accumulates the deflection signal as a measure of the net force applied to the specimen  over time.
 
 \section{Experimental Results}\label{sec:results}
-We compared $\mu$-path scanning to two scenarios. First, we compare it
-to full resolution raster scans at several scan rates in
-Sec.~\ref{sec:cp_full}. Second, we compare to coarse raster scans in
+We compared $\mu$-path scanning to two scenarios: first to full resolution raster scans at several scan rates in
+Sec.~\ref{sec:cp_full}, and second, to coarse raster scans in
 Sec.~\ref{sec:cp_subline}.
@@
 raster scans, we took scans at 1.0~Hz, 2.5~Hz, 5.0~Hz, 8.0~Hz and
-10~Hz. We also took $\mu$-path scans with densities at 12.5\% and
+10~Hz. We also took $\mu$-path scans with densities at approximately 12.5\% and
 25\% and reconstructed 512 by 512 pixel images. The CS scans were

### 2019-06-28 latex/afm-cs-main.tex
Update abstract and conclusion.

@@
   grating sample. Reconstructions are made from these data using
-  % three approaches: (1) inpainting, an interpolation technique that
-  % diffuses information from sampled locations into unsampled
-  % regions, (2)
-  % basis-pursuit, a compressive sensing-based algorithm that seeks to
-  % minimize a
-  % measure of sparsity in the underlying image, and (3)
   a new variant of basis pursuit, Basis Pursuit with Vertical
@@
   and the structured similarity index metric and a new metric we call
-  the relative damage index.
-These images are compared both to standard raster scans as well as to simple subline sampling where only a subset of the rows of the image are acquired (followed by reconstruction).
-\textcolor{red}{These experiments demonstrate that at slow scan
-  rates, the $\mu-$path scheme produces similar image quality with
-  significantly less sampling (and thus less tip-sample interaction)
-  and that at high rates, the undersampling scheme produces higher
-  quality images than raster scanning.}
+  the relative damage index. These images are compared (across a range of scan speeds)
+  to both standard raster
+  scans as well as to simple subline sampling where only a subset of the
+  rows of the image are acquired (followed by reconstruction).
+  These experiments show that at low sampling densities and slow scan rates,
+  $\mu$-path scanning achieves better image quality than subline sampling.
+  Conversely, for faster scan rates, subline sampling achieves better image quality
+  in less time.
+  % These experiments demonstrate that at slow scan
+  % rates, the $\mu-$path scheme produces similar image quality with
+  % significantly less sampling (and thus less tip-sample interaction)
+  % and that at high rates, the undersampling scheme produces higher
+  % quality images than raster scanning.
 \end{abstract}
@@
 unmodified instrument
-\cite{Bazaei:2017dm,Wu:2015dt,Rana:2014bj,Tuma:2012hv,Yong:2010gm}, they are ultimately limited by the vertical bandwidth of
+\cite{Bazaei:2017dm,Wu:2015dt,Rana:2014bj,Tuma:2012hv,Yong:2010gm}, they
+are ultimately limited by the vertical bandwidth of
 the instrument for regulating the deflection signal \cite{Teo:2016ev}.
 
-A different use of non-raster scan patterns are those that seek to improve imaging rate by reducing sampling rather than increasing speed.
-This class includes local scanning methods that use the measurements in real-time to steer the tip to focus the scan on features of
+A different use of non-raster scan patterns are those that seek to improve
+imaging rate by reducing sampling rather than increasing speed. This class
+includes local scanning methods that use the measurements in real-time to
+steer the tip to focus the scan on features of
 interest \cite{Hartman:2018ja,Wen:2018fl,Zhang:2015cf,Huang:2014dw}.
@@
 The main contributions of this paper relative to that past work are as follows.
+% \begin{enumerate}[wide, labelwidth=!, labelindent=0pt]
 \begin{itemize}
@@
 Our main focus here is on delineating the practical issues which must be addressed to effectively realize $\mu$-path scanning, which has only seen limited attention in the past.
+% \end{enumerate}
 \end{itemize}
@@
 
-% \begin{figure*}
-%   % \centering
-%   \includesvg[scale=.98]{figures/cs_raster_images_6-5-2019.svg}
-%   \caption{Raster and compressed sensing images of a 5 micron by 5 micron 
-%     area of the CS-20NG grating. All images are 512$\times$512 pixels.
-%     The rows of pixels indicated by the red lines are
-%     shown in Fig.~\ref{fig:pixel_rows}.}
-%   \label{fig:resultsF1_images}
-% \end{figure*}
-
-% \begin{table}[t!]
-%   \centering
-%   \caption{Performance metrics for raster and CS scans.}
-%   \begin{tabular}{cccccc}
-%     \input{tables/cs_raster_table_6-5-2019_muInf_dct2.tex}
-%   \end{tabular}
-%   \label{tab:rast_vs_cs_v1}
-% \end{table}
-
 \begin{table}[t!]
@@
 metric. These are plotted against total acquisition time in
-Fig.~\ref{fig:time_vs_metrics}. Unfortunately, the
-SSIM and PSNR metrics are not particularly illuminating. There are
-several inconsistencies. For example, it makes no sense that the 1~Hz CS
-scan at 25\% has a \emph{worse} PSNR and SSIM than the 5~Hz scan; nor
-does it make sense that the 8~Hz full raster scan has a worse SSIM and
+Fig.~\ref{fig:time_vs_metrics}. Roughly speaking, image quality improves as
+acquisition time increase. However, the metrics are quite noisy, leading to 
+several inconsistencies. For example, it makes no sense that the 1~Hz, 25\% CS
+scan has a \emph{worse} PSNR and SSIM than the 5~Hz, 25\% CS~scan;
+nor does it make sense that the 8~Hz full raster scan has a worse SSIM and
 PSNR than the 10~Hz full raster scan.
@@
   \caption{Fraction of improvement in total scan time over a scan with
-    512 lines vs scan rate for the three sets of CS scans (at 25\%,
-    15\%, and 12.5\%) and coarser raster scans at 128 and 64 lines.}
+    512 lines vs scan rate for the two sets of CS scans (at 25\%
+    and 12.5\%) and coarse raster scans at 128 and 64 lines.}
   \label{fig:improve_512}
@@
 \section{Conclusions}\label{sec:conclusions}
-The main conclusion of this paper is that with CS, it seems that we
+In this paper, we introduced a new reconstruction method designed to reduce $\mu$-path
+sampling artifacts. We then addressed several practical implementation issues.
+Chief among these is the need to more aggressively mitigate coupling between the
+horizontal plane and the $Z$-axis than is required for raster scanning. Here, we applied
+a feedforward control scheme which attenuates the problematic modes by approximately 40 dB.
+
+We then experimentally demonstrated $\mu$-path sub-sampling
+and compared the resulting images to both full raster scans
+and course raster scans paired with reconstruction.
+The main conclusion of this comparison is that with $\mu$-paths, we
 can acquire images faster yet with less specimen damage than is
-possible while raster scanning a full image. On the other hand, it
-appears that reconstructing a coarse raster scan makes more sense for
-faster scan rates. This is notable, since a coarse raster scan only
-requires an additional step in post-processing. It remains to be seen
-if this conclusion holds for a wide range of instruments.
+possible while raster scanning a full image and that for slow scan rates,
+$\mu$-path scanning achieves better images in less time than subline sampling.
+On the other hand, for faster scan rates, reconstructing a coarse raster scan makes more sense.
+This is notable, since a coarse raster scan with reconstruction is considerably
+easier to implement, both on the hardware side as well as the post-processing side. 
+It remains to be seen if this conclusion holds for a wide range of instruments.
 
@@
 \bibliography{braker_bibs,Andersson_bibs,Yufans_bibs} % Bib database in "refs.bib"
-
+\vspace{-2em}
 \begin{IEEEbiography}
@@
   Department at the University of Colorado Boulder.
-
 \end{IEEEbiography}
-
 \begin{IEEEbiography}
@@
 He is currently with Juniper Networks, Sunnyvale, CA.
-
 \end{IEEEbiography}
-
 \begin{IEEEbiography}
@@
   General Chair of the 2013 American Control Conference, member of the IEEE Control Systems Society (CSS) Board of Governors (2011-2013 and 2015), IEEE CSS Fellow Nominations Chair (2016-2018), and member of the IFAC Executive Board (2017-2020).
-
 \end{IEEEbiography}
-
 \begin{IEEEbiography}

### 2019-06-28 latex/afm-cs-main.tex
Double period.

@@
 coefficients are used, and so the approximation to a triangle wave is
-worse, leading to scans which do not cover the entire intended range..
+worse, leading to scans which do not cover the entire intended range.
 

### 2019-06-28 latex/coverletter.tex
Update coverletter

@@
 It is our pleasure to submit this manuscript entitled \textit{Improving the Image Acquisition Rate of an Atomic Force Microscope Through Sub-sampling and Reconstruction} (authored by Roger A.
-Braker Yufan Luo, Lucy Y.
+Braker, Yufan Luo, Lucy Y.
 Pao and Sean Andersson) for consideration to be published in the Transactions on Mechatronics.
-This paper is submitted for possible publication in the Focused Section on Nano/Micro
-Motion  Systems:  Design,  Sensing  and  Control(NMMS).
+This paper is submitted for possible publication in the Focused Section on Nano/Micro Motion  Systems:  Design,  Sensing  and  Control(NMMS).
 
+The main goal of this manuscript is to show that the native imaging speed of an atomic force microscope (AFM) can be improved by under-sampling  the specimen (i.e., only acquiring a subset of the total pixels for a target image size).
 While sub-sampling schemes have seen increased attention recently, many of the existing studies are based purely on simulation.
-In contrast, this manuscript largely focuses on the experimental challenges which must be overcome to realize a sub-sampling scheme.
+However, the AFM is fundamentally a mechanical device and most of these sub-sampling studies provide little insight
+into how the instrument will respond to the proposed sampling patterns nor into how the patterns might be implemented.
+Our manuscript seeks to partially fill this gap, as it largely focuses on the practical challenges which must be overcome to realize a sub-sampling scheme.
 
@@
 \noindent Y. Luo\par
-\noindent L.Y. Pao
+\noindent L.Y. Pao\par
 \noindent S. Andersson

### 2019-06-28 latex/afm-cs-main.tex
Fix final typos, adjust RDI definition.

@@
 This is in contrast to typical sub-line sampling which takes scan lines at random.
-The clear advantage to a coarse raster scan is that it requires no modification to the instrument, only to the post-processing.
+The clear advantage to a coarse raster scan is that its implementation only requires adjustments to the data collection and post-processing.
+  % it requires no modification to the instrument, only to the post-processing.
 \item The bulk of this work is based on experiment, not simulation, in contrast to prior work by ourselves \cite{luo2015comparison,maxwell2014compressed} and others \cite{han_optimal_2018,jensen_reconstruction_2013,oxvig_structure_2017}.
@@
 1.5 seconds for the DNA image and about 7 seconds for the
-CS-20NG (on a typical laptop computer).
+CS-20NG (on a typical desktop computer).
 
@@
 adjust the reference signals to accomplish each task. In the
-following, $r_X$ and $r_Y$, $r_Z$ refer to the references for the
+following, $r_X$, $r_Y$, and $r_Z$ refer to the references for the
 $X$, $Y$, and $Z$ axes, respectively. The $Z$-axis setpoint $r_Z$
@@
 
-In order to minimize the scanning time, tip tip should be moved as fast as possible when trainsitioning between $\mu$-path locations (state (1)).
+In order to minimize the scanning time, the tip should be moved as fast as possible when trainsitioning between $\mu$-path locations (state (1)).
 Since such speeds can be beyond the bandwidth of the $z-$axis controller, it is important to reduce the tip-sample interaction force to prevent tip wear and sample damage.
@@
 By essentially eliminating the normal force into the sample, we are able to take dozens of images with a single probe without a noticeable degradation in image quality and is a key component to the new quality metric we introduce in Sec.~\ref{sec:rdi}.
-However, completely characterizing the damage done to the tip and sample with this scheme compared complete detachment (which can also damage the probe \cite{meyer_atomic_1992}), remains an outstanding goal.
+However, completely characterizing the damage done to the tip and sample with this scheme compared to complete detachment (which can also damage the probe \cite{meyer_atomic_1992}), remains an outstanding goal.
 
@@
 setup, actuation in the $XY$-plane happens via the nPoint piezo stage
-and the $XY$-direction of the original piezo scanner is uncontrolled.
+and the $XY$-direction of the original piezo tube scanner is uncontrolled.
 This leads to substantial drift between images. To illustrate this, we
@@
 difficulty the $Z$-axis control will have in following the sample
-surface, which results in a larger $Z_d$ over more time. The actual
+surface, which results in a larger deflection signal $Z_d$ over more time. The actual
 damage done by a given $Z_d$ will depend on the spring constant of the
@@
 metric, which we call the Relative Damage Index (RDI) that computes
-the power in the deflection signal for a given scan. The RDI,given by
+the power in the deflection signal for a given scan. The RDI, given by
 
 \begin{align}
-  \text{RDI} &= \frac{1}{T_s}\sum_{k=1}^N \frac{1}{k} \left(Z_{d,k} - r_{Z,s}\right)^2, \label{eqn:RDI}
+  \text{RDI} &= \frac{1}{T_s}\sum_{k\in I} \frac{1}{k} \left(Z_{d,k} - r_{Z,s}\right)^2, \label{eqn:RDI}\\
+  I & = \{k : r_{Z,k} = r_{z,s}\}
 \end{align}
-accumulates the deflection signal as a measure of the net force applied to the specimen  over time.
+accumulates the deflection signal while scanning as a measure of the net force applied to the specimen  over time.
 

### 2019-06-28 latex/afm-cs-main.tex
Adjust RDI definition.
Update on Overleaf.

@@
   \text{RDI} &= \frac{1}{T_s}\sum_{k\in I} \frac{1}{k} \left(Z_{d,k} - r_{Z,s}\right)^2, \label{eqn:RDI}\\
-  I & = \{k : r_{Z,k} = r_{z,s}\}
+  I & = \{k : r_{Z,k} = r_{z,s}\} \nonumber
 \end{align}
@@
 sensor measurements. We then average the data in each bin to obtain
-the value of one pixel. To remove the affects of piezo creep and
-sample tilt, we then de-trend each individual line. De-trending each
+the value of one pixel. To remove the effects of piezo creep and
+sample tilt, we de-trend each individual line. De-trending each
 line causes the flat portion between the holes in the horizontal
@@
 Fig.~\ref{fig:time_vs_metrics}. Roughly speaking, image quality improves as
-acquisition time increase. However, the metrics are quite noisy, leading to 
-several inconsistencies. For example, it makes no sense that the 1~Hz, 25\% CS
-scan has a \emph{worse} PSNR and SSIM than the 5~Hz, 25\% CS~scan;
-nor does it make sense that the 8~Hz full raster scan has a worse SSIM and
-PSNR than the 10~Hz full raster scan.
+acquisition time increase. However, the metrics are quite noisy and the results of the different methods are overlapping, making it difficult to extract a general result on the scanning approaches.
+
+%leading to several inconsistencies.
+For example, it makes no sense that the 1~Hz, 25\% CS scan has a \emph{worse} PSNR and SSIM than the 5~Hz, 25\% CS~scan; nor does it make sense that the 8~Hz full raster scan has a worse SSIM and PSNR than the 10~Hz full raster scan.
 
@@
 Things are clearer if we plot the RDI for each scan against total
-acquisition time, which is shown in Fig.~\ref{fig:time_damage}, and
-this is where CS seems to shine. As one would expect, as imaging time
-decreases, the RDI for each scan type increases. From
+acquisition time, shown in Fig.~\ref{fig:time_damage}.
+%, and this is where CS seems to shine. 
+As one would expect, as imaging time
+decreases, the RDI for each scan type increases. Note that the CS curves are always better than that of the full raster scan. From
 Fig.~\ref{fig:time_damage}, we see that for a fixed RDI, CS has a
@@
 selected randomly \cite{han_optimal_2018, Luo_nano_2015}. An even
-simpler alternative to $\mu$-path sampling is to simply take a
+simpler alternative to $\mu$-path sampling is simply to take a
 standard raster scan with fewer lines. This is the technique we
@@
 other artifacts in the 64 line scan obscure the defect.
+It is important to note, however, that the appearance (or lack thereof) of such small features in the image is in large part a random occurrence.
+In our scans, the line scanner happened to pass through this region and capture the appropriate data while the $\mu$-path pattern used did not.
 
@@
 not only faster than the 12.5\% CS scan, it also has (arguably) better
-image quality.
+image quality, at least on the sample used.
 

### 2019-06-28 latex/coverletter.tex
Add differences from work to coverletter.

@@
 into how the instrument will respond to the proposed sampling patterns nor into how the patterns might be implemented.
-Our manuscript seeks to partially fill this gap, as it largely focuses on the practical challenges which must be overcome to realize a sub-sampling scheme.
+Our manuscript seeks to partially fill this gap, as it largely focuses on the practical (yet non-trivial) challenges which must be overcome to realize a sub-sampling scheme.
+
+The manuscript is an extension of two prior conference papers (ACC 2014 and ACC 2018).
+That first paper (ACC 2014) introduced a sub-sampling technique we called $\mu$-path scanning, which consists of short, randomly placed scans.
+However, we only evaluated its effectiveness via simulation.
+In the second conference paper (ACC 2018), we described our initial efforts at experimental implementation of $\mu$-path scanning, which used only primitive integral control.
+Here, we design and implement higher bandwidth feedback controllers.
+Further, we identify coupling between the horizontal plane and the $Z$-axis as one of the primary limiting factors in $\mu$-path scanning, which we mitigate with a feedforward control scheme.
+A second significant difference between this manuscript and our prior work is that we compare $\mu$-path scanning to a much simpler sub-sampling technique, where we scan every fourth or every eighth line, followed by an interpolation.
+Finally, we also introduce a new reconstruction method designed to mitigate artifacts arising from the $\mu$-path pattern.
 

### 2019-06-28 latex/afm-cs-main.tex
Update on Overleaf.

@@
   Conversely, for faster scan rates, subline sampling achieves better image quality
-  in less time.
+  in less time, though at a penalty in the damage index.
   % These experiments demonstrate that at slow scan
@@
 into 512 bins. This gives an image that is 128 (resp., 64) pixels by
-512 pixels. We then linearly interpolate along each column to produce
+512 pixels, corresponding to 25\% (resp., 12.5\% sampling). We then linearly interpolate along each column to produce
 a 512 by 512 pixel image. Again, we take these coarser raster scans at
@@
 not only faster than the 12.5\% CS scan, it also has (arguably) better
-image quality, at least on the sample used.
+image quality, at least on the sample used. However, as seen in Fig.~\ref{fig:time_damage}, the 12.5\% CS scan has better RDI performance that the 128 line scan.
 

### 2019-06-29 latex/afm-cs-main.tex
Fix an error in the code which produces fig 12. Re-write to account for this.

@@
 Fig.~\ref{fig:cs_cycle} during the second $XY$-move (black portion) where the tip detaches partway through the move.
-%Fig.~\ref{fig:afm_bd_dinv} which selects either the scanning setpoint $r_{Z,s}$ or the retraction setpoint $r_{Z,\textrm{up}}$ based the current state.
 When dis-engagement does occur, the $Z$-axis control loop implements an anti-windup scheme to prevent the control from saturating.
@@
 compared to completely detaching the tip between each $\mu$-path.
-By essentially eliminating the normal force into the sample, we are able to take dozens of images with a single probe without a noticeable degradation in image quality and is a key component to the new quality metric we introduce in Sec.~\ref{sec:rdi}.
+By essentially eliminating the normal force into the sample, we are able to take dozens of images with a single probe without a noticeable degradation in image quality.
+% RAB: I don't see this. Whether we disengage completely or not, RDI should remain the same.
+% and is a key component to the new quality metric we introduce in Sec.~\ref{sec:rdi}.
 However, completely characterizing the damage done to the tip and sample with this scheme compared to complete detachment (which can also damage the probe \cite{meyer_atomic_1992}), remains an outstanding goal.
@@
 \subsection{Control}\label{sec:control}
-% \begin{figure}
-%   \centering
-%   \includesvg[width=1\columnwidth]{figures/z_control_design.svg}
-%   \caption{FRFs of the $Z$-axis. The blue curve is the open loop
-%   response from $u_Z$ to deflection. By inverting the bending mode
-%   at 215~Hz, we achieve the black curve in closed-loop.}
-%   \label{fig:z_control}
-% \end{figure}
 The control structure for each axis, shown in the block diagram in
@@
 
-% We note that the $z$-axis control described here operates the AFM in
-% constant force mode during imaging. It is straightforward to perform
-% scanning under different AFM modes, such as tapping mode, simply by
-% adjusting the signals and control involved in the vertical loop.
-
 \subsection{Feedforward Control}\label{sec:ff_control}
@@
 \begin{align}
-  \text{RDI} &= \frac{1}{T_s}\sum_{k\in I} \frac{1}{k} \left(Z_{d,k} - r_{Z,s}\right)^2, \label{eqn:RDI}\\
-  I & = \{k : r_{Z,k} = r_{z,s}\} \nonumber
+  \text{RDI} &= \frac{1}{T_s}\sum_{k\in I} \frac{1}{k} \left(Z_{d,k} - r_{Z,s}\right)^2, \label{eqn:RDI}
 \end{align}
-accumulates the deflection signal while scanning as a measure of the net force applied to the specimen  over time.
+with ${I = \{k : r_{Z,k} = r_{z,s}\}}$, accumulates the deflection signal while scanning as a measure of the net force applied to the specimen  over time.
 
@@
 raster scans, we took scans at 1.0~Hz, 2.5~Hz, 5.0~Hz, 8.0~Hz and
-10~Hz. We also took $\mu$-path scans with densities at approximately 12.5\% and
+10~Hz. We also took $\mu$-path scans with nominal densities of 12.5\% and
 25\% and reconstructed 512 by 512 pixel images. The CS scans were
@@
 % \SSData{G2}$& $g_6 = \SSData{G6}
-The CS scans were reconstructed with BPVV. We set
+The CS scans were reconstructed with BPVV using
 ${\alpha=\scanD{alph}}$ and ${\beta=\scanD{alpv}}$. For the
@@
 feature in the AFM image processing toolbox \texttt{SPIW} \cite{spiw}.
-The resulting images are shown in Fig.~\ref{fig:resultsF1_images}. The
-color maps represent a range of $\pm$20 nm. The rows of pixels
-indicated by the red lines are shown as cross sections in
-Fig.~\ref{fig:pixel_rows}.
-
-% \begin{figure}
-%   \begin{subfigure}{.48\textwidth}
-%     \includesvg[width=1\textwidth]{figures/ }
-%     \caption{ }
-%     \label{fig: }
-%   \end{subfigure}
-%   \begin{subfigure}{.48\textwidth}
-%     \includegraphics[width=1\textwidth]{figures/ }
-%     \caption{ }
-%     \label{fig: }
-%   \end{subfigure}
-%   \caption{}
-%   \label{fig: }
-% \end{figure}
+A subset of the resulting images are shown in Fig.~\ref{fig:resultsF1_images}. The
+rows of pixels indicated by the red lines are shown as cross sections in
+Fig.~\ref{fig:pixel_rows}. For the CS scans shown in Fig.~\ref{fig:resultsF1_images}, Table~\ref{tab:final_state_times} breaks down the amount of time spent on each task.
+
 \begin{figure*}
@@
 a 512 by 512 pixel image. Again, we take these coarser raster scans at
-1.0, 2.5, 5.0, 8.0 and 10.0 Hz. The resulting images are shown in
+1.0, 2.5, 5.0, 8.0 and 10.0 Hz. A subset of the resulting images are shown in
 Fig.~\ref{fig:results_subline_images}.
@@
 
-Note the defect on the hole located in the second column, sixth row
-from the top (of the grating holes). The CS-scans do a poor job
-detecting this, while both coarse raster scans do so. However, the
-other artifacts in the 64 line scan obscure the defect.
+% Note the defect on the hole located in the second column, sixth row
+% from the top (of the grating holes). The CS-scans do a poor job
+% detecting this, while both coarse raster scans do so. However, the
+% other artifacts in the 64 line scan obscure the defect.
 It is important to note, however, that the appearance (or lack thereof) of such small features in the image is in large part a random occurrence.
 In our scans, the line scanner happened to pass through this region and capture the appropriate data while the $\mu$-path pattern used did not.
+% Except that it passed through this region for all of the sub-line scans, which did not scan exactly the same area...
 
@@
 12.5\% CS scan is better than the the 1~Hz 64 line raster scan.
-However, this advantage quickly evaporates for faster scan rates.
-Indeed, for rates beyond about 5~Hz, the raster scan with 128 lines is
-not only faster than the 12.5\% CS scan, it also has (arguably) better
-image quality, at least on the sample used. However, as seen in Fig.~\ref{fig:time_damage}, the 12.5\% CS scan has better RDI performance that the 128 line scan.
+This speed advantage quickly evaporates for faster scan rates.
+Indeed, for rates beyond about 3~Hz, the 64 line scan is faster than the 12.5\% CS scan and
+the 128 line scan is faster than the 25\% CS scan. 
+In general, the artifacts of the CS reconstructions are different than the interpolated raster scans.
+CS appears to preserve the edges of the holes better than sub-line sampling while sub-line sampling has less noise in the flat areas of the specimen.
 
@@
   \centering
-  \includesvg[scale=.98]{figures/cs_raster_images_subl_6-5-2019.svg}
+  \includesvg[scale=.95]{figures/cs_raster_images_subl_6-5-2019.svg}
   \caption{Raster scans at 128 (top) and 64 (bottom) which have been
@@
 \begin{figure}
-  \includesvg[width=1\columnwidth]{figures/improvements.svg}
+  \centering
+  \includesvg[width=0.85\columnwidth]{figures/improvements.svg}
   \caption{Fraction of improvement in total scan time over a scan with
@@
 \vspace{-2em}
+\parbox[][][t]{1\columnwidth}{
 \begin{IEEEbiography}
@@
   Department at the University of Colorado Boulder.
-\end{IEEEbiography}
+\end{IEEEbiography}\vspace{-2em}
+\baselineskip=1pt
 \begin{IEEEbiography}
@@
 He is currently with Juniper Networks, Sunnyvale, CA.
-\end{IEEEbiography}
+\end{IEEEbiography}\vspace{-2em}
 \begin{IEEEbiography}
@@
   General Chair of the 2013 American Control Conference, member of the IEEE Control Systems Society (CSS) Board of Governors (2011-2013 and 2015), IEEE CSS Fellow Nominations Chair (2016-2018), and member of the IFAC Executive Board (2017-2020).
-\end{IEEEbiography}
+\end{IEEEbiography}\vspace{-2em}
 \begin{IEEEbiography}
@@
 \end{IEEEbiography}
+}
 

### 2019-06-29 process_data_6_5_2019.m

@@ -50,7 +50,7 @@ use_ze = false;
 x1s = [36,   27,  27,  27,  27, 27, 6*4];
 x2s = [493, 493, 493, 495, 494, 494, 122*4];
 figbase = 10;
-for k=1:length(rast_exps)
+for k=1:1 %length(rast_exps)
     rast_exps{k}.uz = log_creep_detrend(rast_exps{k}.uz, []);
     
     if rast_exps{k}.npix_y_og ~= target_pix
@@ -85,6 +85,7 @@ for k=1:length(rast_exps)
         plot(ax1, [idx_right, idx_right], [1, 512], 'r')
     end
 end
+
 fprintf('Finished processing raster data\n');
 if false
     save the first image so we can simulate reconstruction in plot_bptv_vs_bp.m
@@ -405,16 +406,18 @@ for k=1:length(rast_exps)
 
 
 
-    if fig_row == 1 && ~(abs(rate_k - 1.0)<0.1 && k~=1)
+    if fig_row == 1
         hold(ha1(fig_row, fig_col), 'on')
         hold(ha_row(1), 'on')
         ha_row(1).ColorOrderIndex = fig_col;
         plot(ha1(fig_row, fig_col), [1, 512], [row_idx, row_idx], 'r');
-        
+        if abs(rate_k - 1.0)<0.1 && k~=1
+            continue
+        end
         row_hands(fig_col) = plot(ha_row(1), imk(row_idx, :)*AFM.volts2nm_z());
         row_hands(fig_col).DisplayName = sprintf('%.1f Hz', rate_k);
         hold(ha_row(1), 'on')
-        
+        %keyboard
     end
 %     pause
 
@@ -464,7 +467,7 @@ for k=1:length(cs_exps)
     imk = cs_exps{k}.pix_mat_uz;
     imagesc(ha1(fig_row, fig_col), imk, clr_range);
     colormap(ha1(fig_row, fig_col), 'gray');
-    stit = sprintf('CS (%.1f Hz, %.1f \\%%)',...
+    stit = sprintf('CS (%.1f \\%%, %.1f Hz)',...
         cs_exps{k}.sub_sample_frac()*100, cs_exps{k}.equiv_raster_rate());
[…]

### 2019-06-30 latex/afm-cs-main.tex
typo.
Update abstract. Change fig 8 to show 8hz for raster.

@@
   These experiments show that at low sampling densities and slow scan rates,
-  $\mu$-path scanning achieves better image quality than subline sampling.
-  Conversely, for faster scan rates, subline sampling achieves better image quality
-  in less time, though at a penalty in the damage index.
+  $\mu$-path scanning achieves better image quality in less time than subline sampling.
+  Conversely, for faster scan rates and higher densities, subline sampling
+  achieves better image quality in less time.
   % These experiments demonstrate that at slow scan
@@
 raster scan is close. At the same time, the image quality of the 1~Hz,
-12.5\% CS scan is better than the the 1~Hz 64 line raster scan.
+12.5\% CS scan is better than the 1~Hz 64 line raster scan.
 This speed advantage quickly evaporates for faster scan rates.
@@
 $\mu$-path scanning achieves better images in less time than subline sampling.
-On the other hand, for faster scan rates, reconstructing a coarse raster scan makes more sense.
+On the other hand, for faster scan rates (and especially with higher sampling densities), reconstructing a coarse raster scan makes more sense.
 This is notable, since a coarse raster scan with reconstruction is considerably
 easier to implement, both on the hardware side as well as the post-processing side. 
-It remains to be seen if this conclusion holds for a wide range of instruments.
+It remains to be seen if this conclusion holds for a wide range of instruments and specimens.
 

### 2019-06-30 process_data_6_5_2019.m

@@ -103,7 +103,7 @@ for k=1:length(rast_exps)
 end
 
 
-
+%%
 cs_exps = cell(length(cs_files), 1);
 for k=1:length(cs_files)
     [dat_root, dat_name, ext] = fileparts(cs_files{k});
@@ -380,7 +380,7 @@ for k=1:length(rast_exps)
             fig_col = 1;
         case 5.0 
             fig_col = 2;
-        case 10
+        case 8
             fig_col = 3;
         case 15 
             fig_col = 4;

### 2019-06-30 latex/afm-cs-main.tex
tweak abstract.
Update on Overleaf.

@@
     Energy Engineering at the University of Colorado, 425 UCB,
-    Boulder, CO 80309, USA. %Phone: +1 (303) 492-2360. Fax:
-    +1 (303) 492-2758.}%R. A. Braker (corresponding author
+    Boulder, CO 80309 USA. %Phone: 
+    +1 (303) 492-2360.} 
+    %Fax:
+    %+1 (303) 492-2758.}%R. A. Braker (corresponding author
     %roger.braker@colorado.edu) is a graduate student and L.Y. Pao
     %(pao@colorado.edu) is the Palmer  Professor.}
-    \thanks{Luo is with the Division of Systems Engineering and Andersson is with the Division of Systems Engineering and the Department of Mechanical Engineering, Boston University, Boston, MA 02215, USA.}
+    \thanks{Luo and Andersson are with the Division of Systems Engineering and Andersson is also with the Department of Mechanical Engineering, Boston University, Boston, MA 02215 USA.}
   \thanks{This work was supported in part by the US National Science
-    Foundation (NSF Grants CMMI-1234980, CMMI-1234845, CMMI-1562031, and DBI-1352729)  Agilent Technologies,
-    Inc., and the Hanse-Wissenschaftskolleg Institute for Advanced Study in Delmenhorst, Germany.} }
+    Foundation (NSF Grants CMMI-1234980, CMMI-1234845, CMMI-1562031, and DBI-1352729), Agilent Technologies,
+    Inc., a Palmer Endowed Chair Professorship, and the Hanse-Wissenschaftskolleg Institute for Advanced Study in Delmenhorst, Germany.} }
 
@@
   $\mu$-path scanning achieves better image quality in less time than subline sampling.
-  Conversely, for faster scan rates and higher densities, subline sampling
-  achieves better image quality in less time.
+  Conversely, for faster scan rates subline sampling is faster and, for higher sampling
+  densities, achieves comparable image quality.
   % These experiments demonstrate that at slow scan
@@
     Not shown is anti-windup for the $Z$-axis integrator, which is active
-    when $r_Z=\rzup$ (states 1 and 5) where sensor saturation is possible.}
+    when $r_Z=\rzup$ (states (1) and (5)) where sensor saturation is possible.}
   \label{fig:afm_bd_dinv}

### 2019-06-30 latex/coverletter.tex
Update on Overleaf.

@@
 Pao and Sean Andersson) for consideration to be published in the Transactions on Mechatronics.
-This paper is submitted for possible publication in the Focused Section on Nano/Micro Motion  Systems:  Design,  Sensing  and  Control(NMMS).
+This paper is submitted for possible publication in the Focused Section on Nano/Micro Motion  Systems:  Design,  Sensing  and  Control (NMMS).
 
@@
 The manuscript has not been published nor is it under review elsewhere.
-All four authors agree to submit the manuscript in its present form to the IEEE/ASME Transactions Mechatronics focused section NMMS.
-This work was supported in part by Agilent Technologies, Inc, The US National Science Foundation (under Grants CMMI-1234980, CMMI-1234845, CMMI-1562031, and DBI-1352729), and the Hanse Wissenschaftskolleg in Delmenhorst, Germany.
-Thank you for the consideration and we look forward to hearing from you.
+All four authors agree to submit the manuscript in its present form to the IEEE/ASME Transactions on Mechatronics focused section on NMMS.
+This work was supported in part by Agilent Technologies, Inc., the US National Science Foundation (under Grants CMMI-1234980, CMMI-1234845, CMMI-1562031, and DBI-1352729),
+a Palmer Endowed Chair Professorship,
+and the Hanse Wissenschaftskolleg in Delmenhorst, Germany. Thank you for the consideration and we look forward to hearing from you.
 

### 2019-06-30 latex/afm-cs-main.tex
Final editing tweaks.

@@
 
-\newcommand{\rzup}{\ensuremath{r_{z,\textrm{up}}}\xspace}
-\newcommand{\rzs}{\ensuremath{r_{z,\textrm{s}}}\xspace}
+\newcommand{\rzup}{\ensuremath{r_{Z,\textrm{up}}}\xspace}
+\newcommand{\rzs}{\ensuremath{r_{Z,\textrm{s}}}\xspace}
 
@@
 
-\author{Roger A.
-Braker, \textit{Student Member, IEEE}, Yufan Luo, \textit{Student Member, IEEE} , Lucy Y.
-Pao, \textit{Fellow, IEEE} and Sean B.
-Andersson, \textit{Senior Member, IEEE, and Member, ASME}
+\author{Roger A. Braker, Yufan Luo, \textit{Student Member, IEEE}, Lucy Y. Pao, \textit{Fellow, IEEE}\\ and Sean B. Andersson, \textit{Senior Member, IEEE, and Member, ASME}
   \thanks{Braker and Pao are with the Dept. of Electrical, Computer, and
@@
     column) Original raster-scanned image. (second column) BPDN
-    reconstruction from random, $\mu$-path sampling.
+    reconstruction from random $\mu$-path sampling.
     (third column) BPVV reconstruction from the same
@@
 largely mitigated using BPVV. Thus, in the remainder of the paper, we
-focus exclusively on BPVV. These reconstructions wth BPVV took about
+focus exclusively on BPVV. These reconstructions with BPVV took about
 1.5 seconds for the DNA image and about 7 seconds for the
@@
 In order to minimize the scanning time, the tip should be moved as fast as possible when trainsitioning between $\mu$-path locations (state (1)).
-Since such speeds can be beyond the bandwidth of the $z-$axis controller, it is important to reduce the tip-sample interaction force to prevent tip wear and sample damage.
+Since such speeds can be beyond the bandwidth of the $Z-$axis controller, it is important to reduce the tip-sample interaction force to prevent tip wear and sample damage.
 In our initial implementation \cite{braker_hardware_2018},
@@
 compensation models the piezo creep as a simple second-order transfer
-function with real poles and zeros. In Fig.~\ref{fig:afm_bd_dinv}, the
-hysteresis inversion is indicated by $\mathcal{H}_X^{-1}[\cdot]$. We
+function with real poles and zeros whose inverse is part of $D_X$.
+In Fig.~\ref{fig:afm_bd_dinv}, the hysteresis inversion is indicated
+by $\mathcal{H}_X^{-1}[\cdot]$. We
 have found that the inclusion of these extra compensators limits the
@@
 coefficients are used, and so the approximation to a triangle wave is
-worse, leading to scans which do not cover the entire intended range.
+worse, leading to scans which cover slightly less than the intended range.
 
@@
 As one would expect, as imaging time
-decreases, the RDI for each scan type increases. Note that the CS curves are always better than that of the full raster scan. From
-Fig.~\ref{fig:time_damage}, we see that for a fixed RDI, CS has a
-faster imaging acquisition rate. The amount of improvement is best if
-we need a very low RDI: for example, if we want to hold the RDI below~2, then we have to take the 1~Hz raster scan (512 seconds) while we
-can achieve the same RDI via CS in about 42 seconds with the 12.5\%
+decreases, the RDI for each scan type increases.
+From Fig.~\ref{fig:time_damage}, we see that for a fixed RDI, CS has a
+faster imaging acquisition rate. Conversely, for an acquisition time below
+a given threshold, CS offers a smaller RDI than a full raster scan.
+% This is not the case: e.g., compare 8Hz cs and 1 hz raster.
+% Note that the CS curves are always better than that of the full raster scan.
+% From Fig.~\ref{fig:time_damage}, we see that for a fixed RDI, CS has a
+% faster imaging acquisition rate.
+The amount of improvement is best if we need a very low RDI: for example,
+if we want to hold the RDI below~2, then we have to take the 1~Hz raster scan
+(512 seconds) while we can achieve the same RDI via CS in about 42 seconds with the 12.5\%
 sampling, which is a speed improvement of over a factor of 10. The higher of an
@@
 raster scan is close. At the same time, the image quality of the 1~Hz,
-12.5\% CS scan is better than the 1~Hz 64 line raster scan.
+12.5\% CS scan is better than the 1~Hz, 64 line raster scan.
 This speed advantage quickly evaporates for faster scan rates.
@@
 In general, the artifacts of the CS reconstructions are different than the interpolated raster scans.
-CS appears to preserve the edges of the holes better than sub-line sampling while sub-line sampling has less noise in the flat areas of the specimen.
+CS appears to preserve the edges of the holes better than sub-line sampling,
+while sub-line sampling has less noise in the flat areas of the specimen.
 

### 2019-06-30 process_data_6_5_2019.m
Swap CS percenage and rate titles.

@@ -467,8 +467,8 @@ for k=1:length(cs_exps)
     imk = cs_exps{k}.pix_mat_uz;
     imagesc(ha1(fig_row, fig_col), imk, clr_range);
     colormap(ha1(fig_row, fig_col), 'gray');
-    stit = sprintf('CS (%.1f \\%%, %.1f Hz)',...
-        cs_exps{k}.sub_sample_frac()*100, cs_exps{k}.equiv_raster_rate());
+    stit = sprintf('CS (%.1f Hz, %.1f \\%%)',...
+        cs_exps{k}.equiv_raster_rate(), cs_exps{k}.sub_sample_frac()*100);
     title(ha1(fig_row, fig_col), stit, 'FontSize', 7.5);
     
     if abs(cs_exps{k}.equiv_raster_rate()-2)< .1 ||...
@@ -705,6 +705,7 @@ xlim(ha_psn, [6, 230])
 % set(ha1(end), 'Visible', 'off')
 % set(ha_err(end), 'Visible', 'off')
 save_fig(Fig1, fullfile(PATHS.tmech_fig(), 'cs_raster_images_6-5-2019'), false)
+%%
 save_fig(Fig_subl, fullfile(PATHS.tmech_fig(), 'cs_raster_images_subl_6-5-2019'),false)
 save_fig(Fig_rows, fullfile(PATHS.tmech_fig(), 'cs_raster_pixel_rows_6-5-2019'), false)
 

### 2019-07-01 latex/afm-cs-main.tex
Final commit at submission.

@@
 \ref{sec:results}) $\mu$-path scanning to not only full density raster scans but also to coarse raster scans which are interpolated to a full image.
-This is in contrast to typical sub-line sampling which takes scan lines at random.
+This is in contrast to typical subline sampling which takes scan lines at random.
 The clear advantage to a coarse raster scan is that its implementation only requires adjustments to the data collection and post-processing.
@@
   \centering \includesvg[width=1\columnwidth]{figures/cs_cycle.svg}
-  \caption{Several CS cycles. Each state is indicated by color.}
+  \caption{Several CS cycles. Each state is indicated by color. The deflection is shifted so its free value is zero.}
   \label{fig:cs_cycle}
@@
 hysteresis model is a modified Prandtl-Ishlinskii type model and is
-based on the work of \cite{kuhnen_modeling_2003}, while the drift
+based on the work of \cite{kuhnen_modeling_2003}. The drift
 compensation models the piezo creep as a simple second-order transfer
@@
 
-\subsection{Comparison to Sub-line Sampling} \label{sec:cp_subline}
-Many sub-line sampling papers assume that the lines to sample are
+\subsection{Comparison to subline Sampling} \label{sec:cp_subline}
+Many subline sampling papers assume that the lines to sample are
 selected randomly \cite{han_optimal_2018, Luo_nano_2015}. An even
@@
 In our scans, the line scanner happened to pass through this region and capture the appropriate data while the $\mu$-path pattern used did not.
-% Except that it passed through this region for all of the sub-line scans, which did not scan exactly the same area...
+% Except that it passed through this region for all of the subline scans, which did not scan exactly the same area...
 
@@
 In general, the artifacts of the CS reconstructions are different than the interpolated raster scans.
-CS appears to preserve the edges of the holes better than sub-line sampling,
-while sub-line sampling has less noise in the flat areas of the specimen.
+CS appears to preserve the edges of the holes better than subline sampling,
+while subline sampling has less noise in the flat areas of the specimen.
 

### 2019-10-07 functions/@CsExp/CsExp.m
Updates from Overleaf

@@ -1,0 +1,745 @@
+classdef CsExp < handle
+  properties
+    x;
+    x_positive;
+    y;
+    y_positive;
+    uz;
+    ze;
+    z_friction;
+    t;
+    Ts;
+    met_ind;
+    idx_state_s;
+    npix;
+    width;
+    channel_map;
+   
+    Gz;
+    meta_exp;
+    meta_in;
+    state_times;
+    time_total;
+    feature_height
+    gg;
+    cs_paths;
+
+    pix_mat_raw_uz;
+    pix_mat_uz;
+    pix_mask_uz;
+
+    pix_mat_raw_ze;
+    pix_mask_ze;
+    pix_mat_ze;
+    
+    UserData = [];
+  end
+
+  methods
+    function self = CsExp(cs_paths, varargin)
+    % channel_map, Ts, feature_height_nm, gg)
+    % Obtain cs_paths (which is a struct) from, e.g.,
+    % cs_exp_paths(data_root, data_name)
+      default_chan_map = ChannelMap([1:6]);
+      optP = inputParser();
+      optP.addParameter('reload_raw', false, @(s)islogical(s));
+      optP.addParameter('channel_map', default_chan_map);
+      optP.addParameter('feature_height', Inf);
+      optP.addParameter('gg', []);
+      optP.addParameter('Ts', AFM.Ts);
+      optP.addParameter('load_full', false, @(s)islogical(s));
+      optP.parse(varargin{:});
+      opts = optP.Results;
+      % Check to see if an already processed mat file exists.
+      mat_exists = exist(cs_paths.data_path_mat, 'file');
+
+      if ~opts.reload_raw && mat_exists == 2
+        fprintf('loading from mat file...\n')
+        self = self.load_mat(cs_paths.data_path_mat, opts.load_full);
+        fprintf('\bdone\n')
+      else
+        fprintf('loading from raw data...\n')
+        self = self.load_raw_data(cs_paths, opts);
+        fprintf('\bdone\n')
+      end
+
+      self.time_total = length(self.x)*self.Ts;
+    end
+    function rate = equiv_raster_rate(self)
+       rate = self.meta_in.tip_velocity * 0.5 / self.meta_in.width; 
+    end
+    function N = N_scans(self)
+        N = length(self.idx_state_s.scan);
+    end
+    
+    function [tmu_overhead_avg, tscan_avg] = get_mean_mu_overhead(self)
[…]

### 2019-10-07 functions/@CsExp/get_idx_by_state_in_time_range.m

@@ -1,0 +1,48 @@
+%[idx_cell, N_min]= get_idx_by_state_in_time_range(self, state_name, t_start, t_end)
+% Given a start time, t_start and end time t_end, this function
+% will extract all indeces of state_name within that time range.
+%
+% For example: suppose t_start = 1.2, and t_end = 5 
+% and state_name = 'scan'. Then the function returns a matrix of
+% indeces idx_mat such that 
+% self.uz(idx_mat{k} returns the control signal for the kth
+% scan in the range t_start to t_end.
+%
+% Inputs
+% ------
+% state_name:  string = ('scan' | 'move' | 'tdown' | 'tsettle' |'tup')
+%              Note that these correspond to the field names in idx_state_s
+% 
+% t_start   :  Time at which the search begins.
+% 
+% t_end     :  Time at which the search ends.
+%
+% Outputs
+% ------
+% idx_cell  : A cell array. Each cell contains a set of indeces
+%             such indexing the raw data on the kth index set returns
+%             the data for the kth scan in range t_start to t_end.
+% 
+% N_min    :  Integer. The length of the smallest index set.
+%
+% See Also : psd_from_intervals
+function [idx_cell, N_min]= get_idx_by_state_in_time_range(self, state_name, t_start, t_end)
+
+  CS_idx1 = self.find_cycle_idx(t_start);
+  CS_idx2 = self.find_cycle_idx(t_end);
+  
+  N_min = Inf;
+  idx_cell = {};
+  j = 1;
+  for k = CS_idx1:CS_idx2
+    state_idx = self.idx_state_s.(state_name){k};
+    % uz_scan = self.uz(state_idx);
+    % uz_scan = self.ze(state_idx);
+    % uz_scan = uz_scan - mean(uz_scan);
+    N_min = min(N_min, length(state_idx));
+    
+    idx_cell{j} = state_idx;
+    j = j+1;
+  end
+
+end

### 2019-10-07 functions/@CsExp/load_raw_data.m

@@ -1,0 +1,131 @@
+function self = load_raw_data(self, cs_paths, opts)
+% Loads the raw cs data from the paths defined in cs_paths. This is
+% a helper function for the main constructor.
+% 
+%Arguments
+%---------
+%  cs_paths :  struct of paths
+%              Generate with the function get_cs_paths(). This 
+%              function expects that cs-paths will minimally contain 
+% 
+%  cs_paths.meta_path : (string) 
+%                        Path to the matfile saved by laview and contains meta
+%                        data generated in the experiment, like
+%                        control parameters and settings.
+% 
+%  cs_paths.parent_meta_path : (string)
+%                              This is the .mat file containing the parents
+%                              meta data, saved, e.g., by get_cs_paths.m.
+%   
+%  cs_paths.data_path :        This is the csv file of the actual raw data, saved
+%                              by labview.
+% 
+%  opts :  struct
+%          an options structure (typically from name-value pairs
+%          passed to the constructor). We exect the following
+%          properties.
+%  opts.channel_map integer vector
+%                   Construct with ChannelMap
+%  opts.Ts : double
+%            If empty, will use the value in AFM.Ts
+%  opts.feature_height: double
+%                       Expected feature height of the sample. Used
+%                       for visualizing when verbose=true in
+%                       process_cs_data().
+%  opts.gg :  lti model
+%             If this is non-empty, the uz control data will be
+%             filtered through this transfer function. Useful for
+%             removing drift etc.
+% 
+% 
+%Returns
+%-------
+%  self : CsExp
+%         The current instance with data loaded into the proper
+%         properties.    
+% 
+%See Also
+%--------
+%  get_cs_paths.m, CsExp.load_mat()
+% 
+  
+  channel_map = opts.channel_map;
+  self.channel_map = opts.channel_map;
+  self.cs_paths = cs_paths;
+  
+  dat_meas = csvread(cs_paths.data_path);
+  tmp = loadjson(cs_paths.meta_path);  % Provides ExpMetaData
[…]

### 2019-10-07 functions/@CsExp/process_cs_data.m

@@ -1,0 +1,94 @@
+function process_cs_data(self, use_ze, register_uzk)
+  %  process_cs_data(self, verbose, figs, use_ze, register_uzk)
+  %
+  %  Process the raw CS data. This will populate self.Img_raw and 
+  %  self.pix_mask.
+  %
+  %  Arguments
+  %  -----------
+  %     verbose: integer. Plot some stuff if greater than 0 (broken at the moment).
+  %     figs: only used with verbose
+  %     use_ze: [true|false] if true, process deflection data, rather than
+  %     control data.
+  %     register_uzk: [true|false] Only used if use_ze==false. If true, subtract
+  %     the max value of each mu-path off.
+  %
+  if isempty(self.x) || isempty(self.y) || isempty(self.uz) || isempty(self.ze)
+    warning(['You have empty raw data fields. Reload with ',...
+      '"load_full=true".', 'Skipping']);
+    return
+  end
+  if ~exist('use_ze', 'var') || isempty(use_ze)
+      use_ze = false;
+  end
+  if ~exist('register_uzk', 'var') || isempty(register_uzk)
+      register_uzk = true;
+  end
+  
+  
+  pix_mask = zeros(self.npix, self.npix);
+  pix_mat_raw = zeros(self.npix, self.npix);
+  
+  % bin all the data into pixels.
+
+  microns_per_volt = AFM.volts2mic_xy;
+  pix_per_volt = (self.npix/self.width)*microns_per_volt;
+  if isempty(self.x_positive) || isempty(self.y_positive)
+    self.xy_positive();
+  end
+
+  
+  for k = 1:length(self.idx_state_s.scan)
+    
+    % Get the data for the current mu-path.
+    if use_ze
+        [X_raw, Y_raw, ~, U_scan] = self.get_scan_k(k, true);
+    else
+        [X_raw, Y_raw, U_scan] = self.get_scan_k(k, true);
+    end
+    Y_raw = Y_raw*pix_per_volt;
+    X_raw = X_raw*pix_per_volt;
+%     figure(1)
+%     subplot(2,1,1);
+%     cla
+%     plot(detrend(X_raw))
+%     hold on
+%     plot([0, length(X_raw)], [0.5, 0.5], 'r')
+%     plot([0, length(X_raw)], -[0.5, 0.5], 'r')
+%     subplot(2,1,2)
+%     plot(Y_raw)
[…]

### 2019-10-07 functions/@CsTools/CsTools.m

@@ -13,7 +13,7 @@ classdef CsTools
     
     Mpix = pixvec2mat(vpix, nrows, ncol);
     
-    [pix_mask, pix_idx] = mu_path_mask(mupath_len, n, m, samplingRatio, repeat_sampling);
+    [pix_mask, pix_idx, npaths] = mu_path_mask(mupath_len, n, m, samplingRatio, repeat_sampling);
     
     [Ir] = bregman_split_delxy(I,E,epsy, epsx, mu, lam,gam,maxiter,tol)
     
@@ -90,7 +90,18 @@ classdef CsTools
       b = b(pix_idx);
 
     end
+    function [ x ] = Utfun_dct2(z, N)
+      Z_mat = CsTools.pixvec2mat(z, N);
+      X_mat = dct2(Z_mat);
+      x = CsTools.pixmat2vec(X_mat);
+    end
+    
+    function [z] = Ufun_dct2(x, N)
+      X_mat = CsTools.pixvec2mat(x, N);
+      Z_mat = idct2(X_mat);
+      z = CsTools.pixmat2vec(Z_mat);
 
+    end
   end
   
 end

### 2019-10-07 functions/@RasterExp/bin_raster_really_slow.m

@@ -1,0 +1,122 @@
+% [ self] = bin_raster_really_slow(self, line_detrender)
+% 
+% Bins the raw raster data based on x,y, and uz. The data is binned
+% and averaged according to the actual values x, converted to
+% pixels. This means that it is possible, due to noise, for the
+% data to be binned non-contiguously.
+%
+% This method will populate the properties of a RasterExp
+% instance of self.pix_mat and self.pix_mask.
+% The pix_mask is a mask, similar to the CS mask, which will have
+% ones where we actually have data and zeros elsewhere. This may be
+% usefull for detrending the image.
+%
+% If you wish to detrend each line, provide a handle to function to
+% do so. The prototype for such a function is 
+% [x] = line_detrender_local(x)
+
+function [ self] = bin_raster_really_slow(self, line_detrender, use_error, npix_x)
+  if isempty(self.x) || isempty(self.y) || isempty(self.ze) || isempty(self.uz)
+    warning(['Raw dat properties are empty. To process raw data, load',...
+      'the raw data with the load_full flag. Skipping'])
+    return
+  end
+  % nperiods, samps_per_period, volt2pix,
+  % if size(xyu_dat, 1) ~= nperiods*samps_per_period
+  %   s = sprintf('Expected length(xyu_dat) == nperiods*samps_per_period')
+  %   s = sprintf('%s \n but have length(xyu_dat)=%d, nperiods*samps_per_period = %d',...
+  %     s, length(xyu_dat), nperiods*samps_per_period)
+  %   error(s)
+  % end
+  if ~exist('line_detrender', 'var') || isempty(line_detrender)
+    line_detrender = @(x) line_detrender_local(x);
+  end
+  
+  if ~exist('use_error', 'var') || isempty(use_error)
+      use_error = false;
+  end
+  if ~exist('npix_x', 'var') || isempty(npix_x)
+      npix_x = self.npix_x;
+  else
+      micron2pix_x = npix_x/self.width;
+      volts2pix_x = AFM.volts2mic_xy  * micron2pix_x;
+      
+      % Update the instance properties
+      self.npix_x = npix_x;
+      self.volts2pix_x = volts2pix_x;
+      self.micron2pix_x = micron2pix_x;
+  end
+  
+  xpix = self.npix_x; 
[…]

### 2019-10-07 functions/ChannelMap.m

@@ -1,0 +1,23 @@
+classdef ChannelMap
+  properties
+    names;
+    x;
+    y;
+    ze;
+    uz;
+    met;
+    friction;
+  end
+    methods
+      function self = ChannelMap(idx_s)
+        self.names = {'x', 'y', 'ze', 'uz', 'met', 'friction'};
+        for k=1:min(length(self.names), length(idx_s))
+          self.(self.names{k}) = idx_s(k);
+        end
+      end
+    end
+      
+  
+end
+  
+  

### 2019-10-07 functions/ScanMetrics.m

@@ -1,0 +1,45 @@
+classdef ScanMetrics < handle
+  properties
+    damage;
+    quality;
+    psnr;
+    ssim;
+    time;
+    rate;
+    coverage;
+    type;
+    ypix;
+  end
+  
+  methods
+    function self = ScanMetrics(varargin)
+        self.type = {};
+    end
+    function append_metrics(self, varargin)
+      p = inputParser();
+      p.addParameter('damage', Inf);
+      p.addParameter('quality', Inf);
+      p.addParameter('psnr', 0);
+      p.addParameter('ssim', 0);
+      p.addParameter('rate', 0);
+      p.addParameter('time', 0);
+      p.addParameter('type', 'na');
+      p.addParameter('coverage', 0);
+      p.addParameter('ypix', 0);
+      
+      p.parse(varargin{:});
+      
+      self.damage(end+1) = p.Results.damage;
+      self.quality(end+1) = p.Results.quality;
+      self.psnr(end+1) = p.Results.psnr;
+      self.ssim(end+1) = p.Results.ssim;
+      self.rate(end+1) = p.Results.rate;
+      self.time(end+1) = p.Results.time;
+      self.coverage(end+1) = p.Results.coverage;
+      self.type{end+1} = p.Results.type;
+      self.ypix(end+1) = p.Results.ypix;
+      
+    end
+  end
+
+end

### 2019-10-07 functions/frf2ss.m

@@ -1,0 +1,105 @@
+classdef frf2ss
+
+    properties
+       frf;
+       freqs_rad;
+       frf_even
+       freqs_rad_even;
+       impulse_experimental;
+       Nd; 
+       opts;
+       sigmas;
+       ss_full;
+       ni;
+       no;
+    end
+    
+    methods
+        function self = frf2ss(frf, freqs_rad, Nd, opts)
+        % self = frf2ss(frf, freqs_rad, Nd, opts)
+        % This should be a 3d array with No
+        %  rows, Ni columns and length(t) pages.
+            sz = size(frf);
+            if length(sz) == 2
+              frf = reshape(frf, 1, 1, []);
+              ni = 1;
+              no = 1;
+            else
+              ni = sz(2); % ni cols
+              no = sz(1); % no rows
+              
+            end
+            self.ni = ni;
+            self.no = no;
+            
+            self.opts = opts;
+            self.freqs_rad = freqs_rad;
+            self.frf = frf;
+            
+            self.Nd = Nd;
+            t = [0:opts.Ts:opts.impulse_length_sec]';
+            N = length(t);
+
+            % For the fourier transform, N we need evenly spaced frequencies, where N
+            % is length of impulse response.
+            freqs_even = [0:(1/(N*opts.Ts)):floor((1/opts.Ts)*0.5)]'; %Frequencies up to nyquist.
+            ws_even    = freqs_even*2*pi;
+            self.freqs_rad_even = ws_even;
+            
+            self.impulse_experimental = []; %zeros(ni, no, length(ws_even));
+            self.frf_even = zeros(ni, no, length(ws_even));
+            % Interpolate the FRF we have onto the evenly spaced frequencies.
+            K_freq_max = find(ws_even <= freqs_rad(end), 1, 'last');
+            K_freq_min = find(ws_even <= freqs_rad(1), 1, 'last');
+            gdelay = (exp(j*ws_even*opts.Ts)).^Nd;
+            
+            for k_in = 1:ni  % no cols
+              for j_out = 1:no % ni rows
+                frf_iter = squeeze(frf(j_out, k_in, :));
+                [frf_iter, freqs_rad] = monotonicFRF(frf_iter, freqs_rad);
+                frf_iter = interp1(freqs_rad, frf_iter, ws_even(1:K_freq_max), 'spline');
+                frf_iter = frf_iter.*gdelay(1:K_freq_max);
+                
[…]

### 2019-10-07 functions/get_cs_paths.m

@@ -1,0 +1,25 @@
+
+
+function [cs_paths] = get_cs_paths(data_root, data_name, parent_folder)
+  if nargin < 3
+      parent_folder = 'parents';
+  end
+  parent_root = get_parent_root(data_root, parent_folder);
+  parent_name = get_parent_name(data_name, '_out_');
+  parent_meta_name = strrep(parent_name, '.csv', '.json');
+  
+  cs_exp_meta_name = strrep(data_name, '.csv', '-meta.json');
+  
+  % Location of the raw, experimental data.
+  cs_paths.data_path = fullfile(data_root, data_name);
+  cs_paths.parent_path = []; %fullfile(parent_root, parent_name);
+
+  % Location of the post-experiment meta-data.
+  cs_paths.meta_path = fullfile(data_root, cs_exp_meta_name);
+
+  % Where the input file is
+  cs_paths.parent_meta_path = fullfile(parent_root, parent_meta_name);
+  
+  % Where to save the post-processed data.
+  cs_paths.data_path_mat = strrep(cs_paths.data_path, '.csv', '.mat');
+end

### 2019-10-07 functions/get_parent_root.m

@@ -1,0 +1,23 @@
+% parent_root = get_parent_root(data_root)
+%  
+% Given a path data_root, e.g.,
+% /media/labserver/afm-cs/imaging/cs-imaging/5microns/11-13-2018
+%
+% produces the location of the parent data
+%
+% /media/labserver/afm-cs/imaging/cs-imaging/5microns/parents
+
+function parent_root = get_parent_root(data_root, parent_folder)
+  if nargin < 2
+      parent_folder = 'parents';
+  end    
+  % remove trailing slash
+  data_root = strip(data_root, 'right', filesep);
+  
+  % break path apart and drop the final term
+  fparts = strsplit(data_root, filesep);
+  
+  fparts = {fparts{1:end-1}, parent_folder};
+  parent_root = strjoin(fparts, filesep);
+  
+end

### 2019-10-07 functions/get_xdir_standard_control.m

@@ -1,0 +1,75 @@
+function xdirControl = get_xdir_standard_control(type, gam)
+
+
+md = 1;
+
+% ------- Load Plants -----
+[plants, frf_data] = CanonPlants.plants_ns14(9);
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%                                                                         %
+% Design control/estimator gains. This gains are what we actually         %
+% use in both the simulation and experimentant system.                    %
+%                                                                         %
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% 3). LQR generation gain.
+% -------------------------------------------------------------------------
+if strcmp(type, 'const-sig')
+  cmplx_rad = 0.9;
+  [Q1, R0, S1] = build_control_constsigma(plants.sys_recyc, cmplx_rad);
+    gam_rob = 46.4;
+elseif strcmp(type, 'choose-zeta')
+  can_cntrl = CanonCntrlParamsChoozeZeta();
+  [Q1, R0, S1] = build_control_choosezeta(plants.sys_recyc, can_cntrl);
+  gam_rob = 25;
+else
+    error('unrecognized control type.');
+end
+
+if exist('gam', 'var')
+    gam_rob = gam;
+end
+
+
+% ------------------------- Observer Gain ---------------------------------
+can_obs_params = CanonObsParams_01();
+can_obs_params.beta = 50;
+[sys_obsDist, L_dist] = build_obs(plants.SYS, can_obs_params);
+
+% 2). Design FeedForward gains.
+K_lqr = dlqr(plants.sys_recyc.a, plants.sys_recyc.b, Q1, R0+gam_rob, S1);
+
+if 0
+  verbose = 0;
+  analyze_margins(plants, sys_obsDist, K_lqr, L_dist, verbose);
+end
+
+[Sens, Hyd, Hyr, Hyeta, Loop, D1, D2] = ss_loops_delta_dist(plants.SYS, plants.sys_recyc,...
+    sys_obsDist, K_lqr, L_dist);
+
+
+
[…]

### 2019-10-07 functions/norm_align.m

@@ -1,0 +1,13 @@
+
+
+function Im_fit = norm_align(Im_sub, Im)
+  
+  D = normxcorr2(Im_sub, Im);
+
+  [~, idx] = max(abs(D(:)));
+  
+  [i, j] = ind2sub(size(D), idx);
+  
+  Im_fit = Im(i-size(Im_sub,1)+1:i, j-size(Im_sub,1)+1:j);
+  
+end

### 2019-10-07 functions/remove_ticks.m

@@ -1,7 +1,9 @@
 function remove_ticks(ax)
    % Remove the x and y axis ticks labels.
-   for k=1:length(ax)
-       set(ax(k), 'XTickLabel', [])
-       set(ax(k), 'yTickLabel', [])
+   for k=1:size(ax, 1)
+       for j=1:size(ax, 2)
+           set(ax(k, j), 'XTickLabel', [])
+           set(ax(k, j), 'yTickLabel', [])
+       end
    end
 end

### 2019-10-07 functions/ssim_psnr_norm.m

@@ -1,0 +1,32 @@
+function [psn, ssm] = ssim_psnr_norm(Im_master, Im_compare, varargin)
+%   Im_master = detrend_lines_local(Im_master);
+%   Im_compare = detrend_lines_local(Im_compare);
+  
+  if length(varargin) > 1
+    DRng = varargin{1};
+  else
+    Im_master = Im_master - mean(Im_master(:));
+    Im_compare = Im_compare - mean(Im_compare(:));
+    
+    mx1 = max((Im_master(:)));
+    mx2 = max((Im_compare(:)));
+    
+    mn1 = min((Im_master(:)));
+    mn2 = min((Im_compare(:)));
+    
+    mx = max(mx1, mx2);
+    mn = min(mn1, mn2);
+    DRng = mx - mn;
+  end
+  psn = psnr(Im_master, Im_compare, DRng);
+  ssm = ssim(Im_master, Im_compare, 'DynamicRange', DRng);
+  
+end
+
+function X=detrend_lines_local(X)
+  
+  for k=1:size(X,1)
+    X(k,:) = detrend(X(k,:));
+  end
+  
+end

### 2019-10-07 functions/state_space_x/StageParams.m

@@ -1,0 +1,30 @@
+classdef StageParams
+%     This is a class of static parameters that define different aspects of our
+%     stage and the sensors I have built, like the current measurement, and the
+%     associated du_max derived from the TF bound.
+% 
+%     du_max
+%     opamp2powI 
+%     Vdiv2Vhigh 
+%     Imax 
+%     Rsense
+  
+  properties (Constant)
+    du_max_1nm = 0.140;     % See publish_plotting/compute_du_1norm_bounds.m
+    du_max_1nm_vib = 0.1007; % See publish_plotting/compute_du_1norm_bounds.m
+    du_max = 0.198;
+    opamp2powI = 1/15.15;
+%     R1 = 29.7e6;
+%     R2 = 1.732e6;
+%     Vdiv_gain = R2/(R1 + R2);
+    Vdiv2Vhigh = 1/(29.7e6/(1.732e6 + 29.7e6));
+    Imax = 0.100;
+    Rsense = 0.1;
+    Ts = 40e-6;
+  end
+
+  methods
+  end
+  
+end
+

### 2019-10-07 functions/state_space_x/build_control_choosezeta.m

@@ -1,0 +1,93 @@
+function [Q, R0, S, P_x] = build_control_choosezeta(sys_recyc, can_cntrl, tol)
+% [Q, R0, S] = build_control(sys_recyc, can_cntrl)
+% Construct the quadratic cost matrices using the root-locus
+% technique (fictitious zeros). 
+% 
+% Inputs
+% ------
+%  sys_recyc : the deltaUk ss system
+%  can_control : an instance of CanonControlParams_XX.m
+%
+% tol : tolerance for ctrbf, which will be used if pole placment fails.
+% Unfortunately, the default tolerance is often not sufficient to promote a
+% decomposition for all cases where pole placement fails.
+  
+  if ~exist('tol', 'var')
+      tol = 1e-8;
+  end
+  
+  if sys_recyc.InputDelay ~= 0 || sys_recyc.IOdelay ~=0
+    error(['All Delays of sys_obs must be part of the states, not ' ...
+           'included as a property']);
+  end
+  
+  
+  P_x  = getCharDes(sys_recyc, can_cntrl.gam_s, can_cntrl.pint,...
+      can_cntrl.zeta_s, can_cntrl.rho_s, can_cntrl.rad);
+
+  try
+      [Chat, Dhat] = place_zeros(sys_recyc, P_x);
+  catch
+      [Chat, Dhat] = place_zeros_kalman_decomp_local(sys_recyc, P_x, tol);
+  end
+
+  
+  Q = Chat'*Chat;
+  S = Chat'*Dhat;
+  R0 = Dhat'*Dhat;
+  
+
+end
+
+
+function [Chat, Dhat] = place_zeros_kalman_decomp_local(sys, P_x, tol)
+% The trouble with controllability is that the recycled system (delta Uk
+% puts a zero at z=0, but we also have delay poles there, so pole-zero
+% cancellation. This function tries to decompose the controllable and
+% uncontrollable subspaces.
+
+    ns = size(sys.b, 1);
+    for i=1:100
+        % We dont care about Cc.
+        [ab, bb, cb, T, L] = ctrbf(sys.a, sys.b, sys.c, tol);
+        nc = sum(L);
+        if nc < ns
+            fprintf(['Controllable/uncontrollable decomposition succeeded ',...
+                'with tol=%f\n'], tol)
+            break
+        end
+        tol = tol * 10;
+    end
[…]

### 2019-10-07 functions/state_space_x/ss_loops_delta_dist.m

@@ -1,0 +1,56 @@
+
+function [Sens, Hyd, Hyr, Hyeta, Loop, D1, D2] =ss_loops_delta_dist(sys, sys_recyc, sys_obs, KxKu, LxLd)
+% [Sens, Hyd, Hyr, Hyeta, Loop, D1, D2] =ss_loops_delta_dist(sys, sys_recyc, sys_obs, KxKu, LxLd)
+% 
+% D1 is in the loop,
+% D2 is feedforward.
+%
+% For the closed loop s.s. system with deltaU augmentation and disturbance
+% estimation (input disturbance only), constructs the closed loop transfer
+% functions:
+%
+% Sens = 1/(1 + Loop)
+% Loop = G(z)* K_c(zI - A_tilde)^-1 * LL_
+%
+% Hyr = G(z)[Nbar - K_c(zI - A_tilde)^-1 BB_ ]
+%       --------------------------------------
+%        1 + G(z) * K_c(zI - A_tilde)^-1 * LL_
+%
+% Hyd =                 G(z)
+%       --------------------------------------
+%        1 + G(z) * K_c(zI - A_tilde)^-1 * LL_
+%
+  Ts = sys.Ts;
+  
+  Kx = KxKu(1:end-1);
+  Ku = KxKu(end);
+  Nbar = SSTools.getNbar(sys_recyc, KxKu);
+
+  Ld = LxLd(end);
+  Lx = LxLd(1:end-1);
+  Cd = sys_obs.c(end);
+
+  A_tilde = sys.a - sys.b*Kx - Lx*sys.c;
+
+  AA_ = [A_tilde, sys.b-sys.b*Ku, -(sys.b*Nbar+Lx*Cd);
+       -Kx,     1-Ku,             -Nbar;
+       -Ld*sys.c,    0,              1-Ld*Cd];
+
+  BB_ = [sys.b*Nbar; Nbar; 0];
+  LL_ = [Lx; 0; Ld];
+
+  K_c = [KxKu, Nbar];
+  K_c(end-1) = K_c(end-1)-1;
+  D1 = ss(AA_, LL_, K_c, 0, Ts);
+  D2 = ss(AA_, BB_, -K_c, Nbar, Ts);
+
+  % % Estimated state feedback loop gain:
+  Loop = sys*D1;
+  Sens = 1/(1+Loop);
+
+  Hyr = ((sys*D2*Sens));
+  Hyd = minreal( sys*Sens);
[…]

### 2019-10-07 plot_baseline_raster_analysis_1Hz.m

@@ -1,0 +1,187 @@
+% This file compares 8 slow raster scans all taken back to back at 0.5 Hz overa
+% 5 micron area. The goal is to establish a baseline of what we should expect
+% for the performance metrics.
+
+clc
+clear
+close all
+addpath functions
+addpath ~/matlab/dependencies/l1c/
+addpath ~/matlab/dependencies/l1c/lib
+
+% initialize paths.
+
+figbase = 20;
+
+size_dir = '5microns';
+fname = fullfile(PATHS.sysid, 'x-axis_sines_info_intsamps_zaxisFourierCoef_10-29-2018-01.mat');
+models = load(fname);
+G = -models.modelFit.G_zdir;
+p = pole(G);
+z = zero(G);
+gg = zpk(z(end-1:end), p(1:2), 1, G.Ts);
+hole_depth = (20);
+
+chan_map = ChannelMap([1:5]);
+exp_date = '3-21-2019'
+% ----------------------- Load and Process CS-data -----------------------------
+dat_root = PATHS.raster_image_data(size_dir, exp_date);
+
+% ----------------------- Load and Process raster-data -------------------------
+raster_files = {...
+'raster_scan_512pix_5mic_01Hz_out_3-21-2019-01.csv',...
+'raster_scan_512pix_5mic_01Hz_out_3-21-2019-02.csv',...
+'raster_scan_512pix_5mic_01Hz_out_3-21-2019-06.csv',...
+};
+% 'raster_scan_512pix_5mic_01Hz_out_3-21-2019-03.csv',...
+% 'raster_scan_512pix_5mic_01Hz_out_3-21-2019-04.csv',...
+% 'raster_scan_512pix_5mic_01Hz_out_3-21-2019-05.csv',...
+
+
+pixmaps = cell(length(raster_files), 1);
+for k=1:length(raster_files)
+  raster_paths = get_raster_paths(dat_root, raster_files{k});
+  rast_exps{k} = RasterExp(raster_paths, 'reload_raw', false);
+end
+
+%%
+% npix = rast_exps{1}.npix_x;
+% Ts = rast_exps{1}.Ts;
+% width = rast_exps{1}.width;
+% stit = sprintf('Scan %d', k)
+
+%%
[…]

### 2019-10-07 plot_bptv_vs_bp.m

@@ -2,81 +2,132 @@ clear
 addpath('functions/')
 clc
 
+% ------------ Row 1, CS20NG -------------------------
+im_og = double(imread('cs20ng.png'));
+% im_og = im_og(1:2:512, 1:2:512);
+mu_len = 50;
+samp_frac = 0.15;
+n = size(im_og, 1);
 
+[mask, pix_idx] = CsTools.mu_path_mask(mu_len, n, n, samp_frac);
+
+figbase = 1;
+t_recon_cs20ng = cp_bptv_bp(im_og, pix_idx, 'cs20ng', figbase);
+
+U_fun = @(x) idct(x);
+Ut_fun = @(x) dct(x);
+    
+E_fun = @(x) CsTools.E_fun1(x, pix_idx);
+Et_fun = @(x) CsTools.Et_fun1(x, pix_idx, n, n);
+%        
+% clc
+% im_og = im_og / max(im_og(:));
+% b = CsTools.pixmat2vec(im_og);
+% b = b(pix_idx);
+% alpv = .01;
+% alph = .91;
+% opts = NESTA_opts('U', U_fun, 'Ut', Ut_fun, 'verbose', 0, 'TolVar', 1e-5);
+
+% [ssm, X] = fun(im_og, b, E_fun, Et_fun, opts, alpv, alph);
+% alps_0 = [alpv; alph];
+% %%
+% 
+% 
+% f = @(alps) fun(im_og, b, E_fun, Et_fun, opts, alps(1), alps(2));
+% 
+% fmopts = optimoptions('fmincon', 'MaxIterations', 10, 'Disp', 'iter');
+% alps = fmincon(f, alps_0, [], [], [], [], [0;0], [], [], fmopts)
+
+%
+
+% ------------ Row 2, DNA -------------------------
 im_og = double(rgb2gray(imread('dnn_dna_gt.png')));
-im_og = im_og / max(im_og(:));
+
 n = 256;
 im_og = im_og(1:n, 1:n);
 
 mu_len = 25;
 samp_frac = 0.25;
+figbase = 100;
 
-[mask, pix_idx] = CsTools.mu_path_mask(mu_len, n, n, samp_frac);
+[mask, pix_idx] = CsTools.mu_path_mask(mu_len, n, n, samp_frac, figbase);
 
-U_fun = @(x) idct(x);
-Ut_fun = @(x) dct(x);
[…]

### 2019-10-07 plot_colorbar.m

@@ -1,0 +1,22 @@
+
+F1 = mkfig(1, 0.75, 1.5, false);clf
+
+ax4 = tight_subplot(1, 1, 0.05, 0.01, 0.01, false);
+
+
+h = colorbar(ax4, 'Location', 'EastOutside', 'Position', [0.03194 0.05 0.241 0.9]);
+set(h, 'YAxisLocation','right')
+
+colormap gray
+% convert the threshold to nanometers
+
+thresh_color = thresh*(7/20)*(1000/1)*1.005; %should give 22
+caxis([-thresh_color, thresh_color])
+% set(h, 'Ticks', [-20, -10, 0, 10, 20])
+
+text(.75, .3, '$Z$ [nm]', 'rot', 90, 'interpreter', 'latex',...
+    'Units', 'normalized', 'FontSize', 12)
+
+ax4.Visible = 'off';
+
+save_fig(F1, 'latex/figures/colorbar', false)

### 2019-10-07 plot_cs_cycle.m

@@ -1,0 +1,112 @@
+clc
+clear
+%%
+% close all
+clear
+clc
+addpath functions/scanning_v1/
+addpath ~/matlab/dependencies/l1c/
+
+% initialize paths.
+
+figbase = 20;
+
+size_dir = '5microns';
+hole_depth = (20);
+
+chan_map = ChannelMap([1:5]);
+exp_date = '6-5-2019'
+% ----------------------- Load and Process CS-data -----------------------------
+dat_root = PATHS.raster_image_data(size_dir, exp_date);
+
+% ----------------------- Load and Process raster-data -------------------------
+cs_files = {...
+'cs-traj-512pix-12perc-500nm-5mic-01Hz-150prescan-notconnect_out_6-5-2019-01.csv',...
+};
+
+
+data_root = PATHS.cs_image_data(size_dir, exp_date);
+cs_exps = {};
+for k=1:length(cs_files)
+  cs_paths = get_cs_paths(data_root, cs_files{k});
+  gg = @(u, idx_state_s) log_creep_detrend(u, idx_state_s);
+  cs_exps{k} = CsExp(cs_paths, 'feature_height', hole_depth, 'gg', gg, 'load_full', true);
+
+  cs_exps{k}.print_state_times();
+  cs_exps{k}.sub_sample_frac()
+  cs_exps{k}.t = (0:length(cs_exps{k}.x)-1)'*AFM.Ts;
+end
+
+% taken from cycle 3, where tip detaches.
+cs_exp1 = cs_exps{1};
+zdfl_free = -0.637-.05;
+cs_exp1.ze = cs_exp1.ze - zdfl_free;
+
+
+cs_exp1.x = cs_exp1.x*AFM.volts2mic_xy;
+cs_exp1.y = cs_exp1.y*AFM.volts2mic_xy;
+cs_exp1.uz = cs_exp1.uz*AFM.volts2nm_z;
+
+%%
+[~, axs] = make_cs_traj_figs(figbase, 4);
+cs_exps{1}.plot_all_cycles(axs{1:4});
+
+
+
+%%
+
+indc = {   'k',        'r',   [0, .75, .75],       'b',        [.93 .69 .13], 'm';
+          'xy-move', 'tip down', 'tip settle',  '$\mu$-path scan', 'tip up', 'connect'};
+        
+Fig = mkfig(100, 3.5, 4); clf
[…]

### 2019-10-07 plot_z_axis_control_design.m

@@ -1,0 +1,62 @@
+addpath functions
+clear
+% close all
+root = fullfile(PATHS.sysid, 'z_axis_evolution', 'batch-1');
+file = 'first_res_fit-3-17-2019-1.json';
+
+dat = loadjson(fullfile(root, file));
+
+gz_k = dat.SOS_frf_data.resp_real + dat.SOS_frf_data.resp_imag*1i;
+
+ss_fname = fullfile(root, 'ALL-axis_sines_info_intsamps_quickFourierCoef_3-17-2019-01.json');
+ss_data = SweptSinesOnline(ss_fname);
+
+G_frf = frd(ss_data.FC_s(:,2)./ss_data.FC_s(:,1), ss_data.freq_s, AFM.Ts, 'FrequencyUnit', 'Hz');
+
+
+KI = -0.06;
+D_inv = dat.K*frd(tf(dat.Dinv_Num, dat.Dinv_den, AFM.Ts),  ss_data.freq_s,  'FrequencyUnit', 'Hz');
+
+KI_norm = KI;
+
+D_ki = zpk([], [1], KI, AFM.Ts);
+D_ki_old = zpk([], [1], 0.005, AFM.Ts);
+
+DD = D_ki * D_inv;
+
+Loop = DD * G_frf;
+Loop_noinv = D_ki * G_frf;
+
+Huz_d = feedback(D_ki, D_inv*G_frf);
+H2 = D_ki/(1+Loop);
+
+Hyr = feedback(D_ki*D_inv*G_frf, 1);
+Hyr_old = feedback(D_ki_old*G_frf, 1);
+Hyr_noinv = feedback(D_ki*dat.K*G_frf, 1);
+
+
+F2 = mkfig(2, 3.48, 2); clf
+[ha, pos] = tight_subplot(1, 1, [.02, .01 ], [.15, 0.08], [.1, .02]);
+
+
+h1 = frf_bode_mag(Loop, ss_data.freq_s, ha, 'Hz', ':b');
+h2 = frf_bode_mag(G_frf, ss_data.freq_s, ha, 'Hz', '-k'); %, 'LineWidth', 1.1);
+h4 = frf_bode_mag(Hyr, ss_data.freq_s, ha, 'Hz', '-.r'); % 'LineWidth', 1.1);
+
+ylim(ha(1), [-40, 20]);
+
+h1.DisplayName = 'Loop gain';
+h2.DisplayName = '$G_{Z_d,u_Z}$';
[…]

### 2019-10-07 q_vs_density.m

@@ -1,0 +1,257 @@
+% ------------ Row 1, CS20NG -------------------------
+
+addpath functions
+im_og = double(imread('cs20ng.png'));
+% im_og = double(imread('cameraman.tif'));
+im_og = im_og - min(im_og(:));
+im_og = (im_og / max(im_og(:)))*256;
+% im_og = im_og(1:2:512, 1:2:512);
+
+samp_frac = 0.15;
+npix = size(im_og, 1);
+
+mx = max(im_og(:)) - min(im_og(:))
+skip = 4;
+h = skip:skip:npix;
+im_128_sub = im_og(h, :);
+im_128 = interp_y(im_128_sub, npix);
+ssm_128 = ssim(im_128, im_og, 'DynamicRange', mx);
+psn_128 = psnr(im_128, im_og, mx);
+
+skip = 8;
+h = skip:skip:npix;
+im_64_sub = im_og(h, :);
+im_64 = interp_y(im_64_sub, npix);
+ssm_64 = ssim(im_64, im_og, 'DynamicRange', mx);
+psn_64 = psnr(im_64, im_og, mx);
+
+
+U_fun = @(x) idct(x);
+Ut_fun = @(x) dct(x);
+
+mu = 1e-7;
+delta = 0.01;
+alpv = 0.01;
+alph = 0.75;
+opts = NESTA_opts('U', U_fun, 'Ut', Ut_fun, 'verbose', 0, 'TolVar', 1e-5,...
+    'alpha_v', alpv, 'alpha_h', alph);
+
+%%
+qs = [(1:2:10), (15:5:50), (50:15:512)];
+fracs = (5:2:50)/100;
+% fracs = 50/100;
+dat128 = zeros(length(qs), 7);
+dat64 = zeros(length(qs), 7);
+map_ssm = zeros(length(qs), length(fracs));
+map_psn = zeros(length(qs), length(fracs));
+
+Y = map_ssm;
+X = map_ssm;
+gam = npix/50;
+fprintf('128: ssm: %.3f, psn: %.3f\n', ssm_128, psn_128);
+fprintf('64: ssm: %.3f, psn: %.3f\n', ssm_64, psn_64);
+fprintf('===============================================\n');
+figure(11); clf
+subplot(1,3,1),
+imagesc(im_128, [1, 255]), colormap('gray')
+title('128 lines')
+subplot(1,3,2)
+imagesc(im_128, [1, 255]), colormap('gray')
[…]

### 2019-10-07 latex/review-response-1.tex
Start rebuttal

\documentclass[11pt]{article} % use larger type; default would be 10pt
\usepackage{xr} % allow crossref to root.tex of all references
\externaldocument{jpaper}
\usepackage{xcite} % allow crossref to root.tex to all citations therein.
\externalcitedocument[A-]{jpaper}
%%% PACKAGES

% \usepackage[resetlabels,labeled]{multibib}
% \newcites{A}{review_response}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bbold}
\usepackage{mathtools}	
\usepackage{epstopdf}
\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{url}
\usepackage[margin=1in]{geometry}		%%DSZ: changed the margins 
\usepackage{appendix}
\usepackage{calc}
\usepackage{xspace}

\newcommand{\pic}[2]{\includegraphics[width={#2}]{#1}}
%% Try this out

\usepackage{enumitem}

\usepackage[normalem]{ulem}
\usepackage{soul}
\usepackage{framed}
\usepackage{environ}
\usepackage{xcolor}

\newcommand{\sgn}{\ensuremath{\text{sgn}}\xspace}
\newcommand{\sat}{\ensuremath{\text{sat}}\xspace}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% The following two macros allow us to use citations in this document which are
% not in the primary manuscript and add a prepended letter ('R' in this case)
% to disambugate from the citations refered to by xcite from the main manuscript.
% In order to use this must include a bibliography and style file at the end. 
\makeatletter
\renewcommand\@biblabel[1]{[R#1]}
\makeatother

\setlist{  
  listparindent=\parindent,
  parsep=0pt,
}
% \let\svbibcite\bibcite
% \def\bibcite#1#2{\svbibcite{#1}{#2}}
% \makeatletter
% \let\svbiblabel\@biblabel
% \def\@biblabel#1{\svbiblabel{R#1}}
% \makeatother
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newtheorem{prlm}{Problem}

\renewenvironment{leftbar}[1]
{%\begin{leftbar}%
    \def\FrameCommand
    {%
        {\color{#1}\vrule width 3pt}%
        \hspace{0pt}%must no space.
        \fboxsep=\FrameSep\colorbox{lightgray}%
    }%
    \MakeFramed{\hsize \hsize\advance\hsize-\width\FrameRestore}%
}
{\endMakeFramed}

% ---------------------------------------------------------------- %
% use this command as \listintertext{text here} to insert a rebuttal text
% between list items.
\makeatletter
\newcommand{\listintertext}{\@ifstar\listintertext@\listintertext@}

\newcommand{\listintertext@}[1]{% \listintertext*{#1}
  \hspace*{-\@totalleftmargin}
  % \begin{minipage}{\textwidth}
  \parbox{\textwidth}{
    \setlength{\parindent}{24pt}
    #1
    }}
  % \end{minipage}}

% \newcommand{\listintertext}{\@ifstar\listintertext@\listintertext@@}

% \newcommand{\listintertext@}[1]{% \listintertext*{#1}
%   \hspace*{-\@totalleftmargin}\parbox{\textwidth}{#1}}

% \newcommand{\listintertext@@}[1]{% \listintertext{#1}
%   \hspace{-\leftmargin}\mbox{#1}}
\makeatother

\newcommand{\inttext}[1]{\end{enumerate} #1\begin{enumerate}[resume]}
\newcommand{\itemaddr}[2]{\begin{leftbar}{#1} \item{#2}\end{leftbar}}

\title{Response to Reviews}
\author{Roger A. Braker and Lucy Y. Pao}

\date{\parbox{\linewidth}{\centering%
  %\today
\endgraf\bigskip
  }}

%\date{} % Activate to display a given date or no date (if empty),
         % otherwise the current date is prined

\begin{document}
\maketitle
\noindent
Dear Reviewers and Prof. Editors,

We thank the reviewers for their helpful comments. 
We have revised the paper based on these suggestions, with full details described below. The original review comments appear with a vertical bar on the left. References to equations use the numbers as they appear in the revised manuscript. 
%Citations specifically used in this rebuttal document are pre-pended with the letter 'R', e.g., [R1].

\section{Review 1}
\begin{leftbar}{black}
  A Comparison of 
\end{leftbar}

\begin{enumerate}

    \itemaddr{black}{Objection}

    \inttext{Response}
  \end{enumerate}
  While interesting, this paper assumes full state feedback.
  That is not a realistic assumption for many systems,
  including the one under consideration here.

\section{Review 2}

  \listintertext{Response. }

% \bibliographystyle{IEEEtran}
% \bibliography{review_response, prefixnumbers=A}

\bibliographystyle{IEEEtran}
% \bibliography{/home/arnold/bib_pdf/main_bibliography,review_response}
%\bibliography{afm_mpc_tcst.bib,review_response}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:

### 2019-10-07 build_controllers_with_xyFF_DxDy.m

@@ -1,0 +1,310 @@
+% Implement augmented state space integral control with shift register to
+% 'estimate' the delay states.
+
+
+clear all
+%%
+% clc
+% Options
+figbase  = 50;
+verbose = 0;
+rmpath('/home/arnold/matlab/afm-cs/matlab-code/functions/')
+addpath('functions');
+addpath(fullfile('functions', 'state_space_x'));
+
+
+% ---- Paths for shuffling data to labview and back. ------
+
+
+TOL = 14/512; % max volts by pixels
+% TOL = .01;
+tol_mode = 'abs';
+% which simulations to run
+
+do_sim_hyst = false;
+do_inv_hyst = false;
+do_drift = false;
+do_invdrift = false;
+
+plotstate = false;
+plotpoles = false;
+plotdriftpoles = false;
+plotdriftbode = false;
+saveon = true;
+
+cntrl_type = 'const-sig';
+
+
+% ------- Load Plants -----
+[plants, frf_dataX] = CanonPlants.plants_ns14(9, '5micron');
+Gxyz_frd = get_H();
+
+Ts  = plants.SYS.Ts;
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%                                                                         %
+%                  Design reference "trajectory"                          %
+%                                                                         %
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% Get a ref trajectory to track.
+N  = 800;
+r1 =1.37;
+
+step_ref = StepRef([r1], N);
+yref = step_ref.yref;
+yref.Data = yref.Data*1;
+step_descr = 'single_step';
+
+dist_traj = yref;
+dist_traj.Data = dist_traj.Data*0;
+thenoise = dist_traj;
+
+
+F_yudu = figure(60); clf
+subplot(3,1,1)
+hold on, grid on;
+step_ref.plot(F_yudu, '-k', 'LineWidth', 0.5);
+
+F_y = figure(61); clf
[…]

### 2019-10-07 functions/@CsExp/dataview_callback.m

@@ -1,0 +1,53 @@
+
+function output_txt = dataview_callback(self, event_obj, ax1, ax2)
+% output_txt = dataview_callback(self, event_obj, ax1, ax2)
+%
+% use as: fun = @(event_obj)(dataview_callback(self, event_obj, ax1, ax2)
+% where you have provided ax1 and ax2.
+% 
+% This should be used as the callback function when Using
+% ImshowDataView.imshow().
+%
+% It will plot, in dashed red, the original, unconstructed CS data.
+%
+%
+  pos = get(event_obj,'Position');
+  
+  ind = get(event_obj, 'DataIndex');
+  
+  yidx = pos(2);
+  xidx = pos(1);
+  
+  dat = event_obj.Target.CData(yidx, :);
+  height = dat(xidx);
+  
+  npix = size(self.pix_mask_uz,1);
+  dat_og = self.pix_mat_uz(yidx, :);
+  mask_row = self.pix_mask_uz(yidx, :);
+  dat_og(mask_row~=1) = NaN; % matlab wont plot this.
+  
+  zmin = min(event_obj.Target.CData(:));
+  zmax = max(event_obj.Target.CData(:));
+  cla(ax2);
+  plot(ax2, dat);
+  hold(ax2, 'on')
+  plot(ax2, xidx, dat(xidx), 'xk')
+  plot(ax2, dat_og, '--r')
+  grid(ax2, 'on');
+  ylim(ax2, [zmin, zmax]);
+  hold(ax1, 'on')
+  
+  dims = size(event_obj.Target.CData);
+  h_line = plot(ax1, [1, dims(1)], [yidx, yidx], '-r');
+  if ~isempty(event_obj.Target.UserData.line) ...
+      && isa(event_obj.Target.UserData.line, 'matlab.graphics.chart.primitive.Line')
+    delete(event_obj.Target.UserData.line)
+  end
+  event_obj.Target.UserData.line = h_line;
+  
+  output_txt = {['x-pix: ',num2str(pos(1),4)],...
+    ['y-pix: ',num2str(pos(2),4)],...
+    ['Index: ', num2str(ind)],...
+    ['value:  ', num2str(height)]};
+  
+end

### 2019-10-07 functions/@CsExp/plot_all_cycles.m

@@ -1,0 +1,181 @@
+function [hands, legs] = plot_all_cycles(self, ax1, ax2, ax3, ax4, bounds, xy_scl)
+%   [hands] = plot_all_cycles(self, ax1, ax2, ax3, ax4, bounds, xy_scl)
+% Plot the color-ized cs cycles to the provided axes.
+%
+% Usage
+% -----
+% You can call this method in several ways
+%
+%  hands = plot_all_cycles(ax1) : plot uz to ax1
+%  hands =  plot_all_cycles(..., ax2) : also plot ze to ax2
+%  hands = plot_all_cycles(..., ax3) : also plot x to ax3
+%  hands = plot_all_cycles(..., ax4) : also plot y to ax4
+%
+% Alternatively,
+%   hands = plot_all_cycles('all') : plot uz, ze, x, and y to the figures
+%                                    generated by repeated
+%                                    calls to figure();
+%  bounds = [upper, lower] for z_error
+% TODO: Implement what follows
+%   hands = plot_all_cycles(spec) : Plot the data specified by
+%                                   spec to created figures.
+%                                   Spec should be a string
+%                                   such as 'xyz' or 'ux' which
+%                                   would result in plots of x,
+%                                   y, and ze, or u_z and x, respectivily.
+%
+  
+  if ~exist('xy_scl', 'var')
+    xy_scl=1;
+  end
+  
+% First, parse the input. 
+  if isa(ax1, 'char') && strcmp(ax1, 'all')
+    plotx=true;
+    ploty=true;
+    plotuz=true;
+    plotze=true;
+    
+    figure()
+    ax1 = gca();
+    figure();
+    ax2 = gca();
+    figure();
+    ax3 = gca();
+    figure();
+    ax4 = gca();
+
+  else % assume first arg is ax1
+      if ~isempty(ax1)
+          plotuz = true;
+      else
+          plotuz = false;
+      end
+  end
+  % The case, unless we find out otherwise.
+  plotze = false;
+  plotx = false;
+  ploty = false;
+  
+  if exist('ax2', 'var') && ~isempty(ax2)
+    plotze = true;
+  end
[…]

### 2019-10-07 functions/@CsTools/mu_path_mask.m

@@ -16,14 +16,14 @@
 %                  mu-path areas, and zeros elsewhere.
 
 
-function [pix_mask, pix_idx] = mu_path_mask(mupath_len, n, m, samplingRatio, repeat_sampling)
+function [pix_mask, pix_idx, npaths] = mu_path_mask(mupath_len, n, m, samplingRatio, repeat_sampling)
    
     if nargin < 5
         repeat_sampling = false;
     end
 
     pix_mask = zeros(n,m);
-
+    npaths = 0;
     while (sum(sum(pix_mask))<samplingRatio*n*m)
         
         if repeat_sampling
@@ -37,6 +37,7 @@ function [pix_mask, pix_idx] = mu_path_mask(mupath_len, n, m, samplingRatio, rep
             rand_j = randi(m-mupath_len+1);
             if sum(pix_mask(rand_i,rand_j:rand_j+mupath_len-1)) < 0.5
                 pix_mask(rand_i,rand_j:rand_j+mupath_len-1) = 1;
+                npaths = npaths + 1;
             end            
         end
     end

### 2019-10-07 functions/@RasterExp/RasterExp.m

@@ -1,0 +1,259 @@
+classdef RasterExp <matlab.mixin.Copyable
+% rast_exp = RasterExp(raster_paths, varargin)
+% 
+% 'rel
+  properties
+    raster_paths;
+    channel_map;
+    % parent_data;
+    xref;
+    yref;
+%     meta_data;
+    Ts;
+    met_ind;
+    npix_x;
+    npix_y;
+    npix_y_og;
+    width;
+    volts2pix_y;
+    volts2pix_x;
+    micron2pix_y;
+    micron2pix_x;
+
+    samps_per_period;
+    samps_per_line;
+    gg;
+    meta_exp;
+    meta_in;
+    time_total;
+    uz;
+    ze;
+    z_friction;
+    x;
+    y;
+    pix_mat;
+    pix_mat_pinned;
+    pin_idx_s;
+    pix_mask;
+    
+    pix_mask_ze;
+    pix_mat_ze;
+%     UserData;
+  end
+  
+  methods
+    function self= RasterExp(raster_paths, varargin)
+    % self= RasterExp(raster_paths, varargin)
+    
+    % [datmat, samps_period, samps_line] 
+      self.raster_paths = raster_paths;
+      default_chan_map = ChannelMap([1:6]);
+      optP = inputParser();
+      optP.addParameter('reload_raw', false, @(s)islogical(s));
+      optP.addParameter('channel_map', default_chan_map);
+      optP.addParameter('gg', []);
+      optP.addParameter('load_full', false, @(s)islogical(s));
+      
+      optP.parse(varargin{:});
+      opts = optP.Results;
+      
+      % Check to see if an already processed mat file exists.
+      mat_exists = exist(raster_paths.data_path_mat, 'file');
+      if ~opts.reload_raw && mat_exists
+        fprintf('loading from mat file...\n')
+        self = self.load_mat(raster_paths.data_path_mat, opts.load_full);
+        fprintf('\bdone\n')
+      else
+        fprintf('loading from raw data...\n')
+        self = self.load_raw_data(raster_paths, opts);
+        self.npix_y_og = self.npix_y;
+        fprintf('\bdone\n')
+      end      
+      self.time_total = length(self.x)*self.Ts;
+      
+    end
+    
+    % Methods defined in other files
+    self = load_raw_data(self, raster_paths, npix, width, opts)
+    [ self] = bin_raster_really_slow(self, line_detrender, use_error, npix_x)
+    trace_inds = get_trace_indeces(self)
+    
[…]

### 2019-10-07 functions/@RasterExp/bin_raster_slow.m

@@ -1,0 +1,53 @@
+
+function [ pixmat, pixelifsampled] = bin_raster_slow(xyu_dat, nperiods, samps_per_period, volt2pix)
+if size(xyu_dat, 1) ~= nperiods*samps_per_period
+   s = sprintf('Expected length(xyu_dat) == nperiods*samps_per_period')
+   s = sprintf('%s \n but have length(xyu_dat)=%d, nperiods*samps_per_period = %d',...
+       s, length(xyu_dat), nperiods*samps_per_period)
+    error(s)
+end
+xpix = nperiods;
+ypix = nperiods; % TODO: make this work with rectangular image. 
+
+% Get the indeces corresponding to trace data only.
+trace_inds = get_trace_indeces(nperiods, samps_per_period);                        
+                        
+
+xdat_trace = xyu_dat(trace_inds, 1);
+ydat_trace = xyu_dat(trace_inds, 2);
+udat_trace = xyu_dat(trace_inds, 3);
+
+% Make the image be at (0,0, 0).
+xdat_trace = (xdat_trace - min(xdat_trace))*volt2pix;
+ydat_trace = (ydat_trace - min(ydat_trace))*volt2pix;
+
+% make 
+udat_trace = (udat_trace - min(udat_trace));
+udat_trace = udat_trace/max(udat_trace);
+% xbins = linspace(0, xpix-1, xpix)';
+% ybins = linspace(0, ypix-1, ypix)';
+
+pixelifsampled = zeros(xpix, ypix);
+pixmat = zeros(xpix,ypix)*mean(udat_trace);
+for j_row = 0:ypix-1
+%     ind_y = find(ydat_trace >= j_row & ydat_trace < j_row+1);
+    ind_y = j_row*(samps_per_period/2)+1:(j_row+1)*(samps_per_period/2);
+    x_dat_j = xdat_trace(ind_y)';
+    U_dat_j = udat_trace(ind_y)';
+    
+    for i_col = 0:xpix-1
+        ind_x = find(x_dat_j >= i_col & x_dat_j < i_col+1);
+        
+        u_mean_ij = mean(U_dat_j(ind_x));
+        if ~isnan(u_mean_ij)
+             pixmat(j_row+1, i_col+1) = u_mean_ij;
+             pixelifsampled(j_row+1, i_col+1) = 1;
+        else
+%             keyboard
+        end
+       
+    end
+end
+
+end
+

### 2019-10-07 functions/@RasterExp/find_raster_extents.m

@@ -1,0 +1,42 @@
+% [kmin, kmax] = find_raster_extents(rdat)
+%
+% Find the x-axis extent of the raster data. kmin and kmax are the indeces
+% where the raster data actually exists. 
+
+function [kmin, kmax] = find_raster_extents(rdat)
+
+
+    kmin = 1;
+    kmax = size(rdat.pixelifsampled, 2);
+
+    kstarts = zeros(kmax,1);
+    kends = zeros(kmax,1);
+    
+    for i_row=1:rdat.npix
+       inds_not = find(rdat.pixelifsampled(i_row,:) ~= 0);
+       kstarts(i_row) = inds_not(1);
+       kends(i_row) = inds_not(end);
+    end
+    
+    kmin = max(kstarts);
+    kmax = min(kends);
+%     for i=1:rdat.npix
+%        if mean(rdat.pixelifsampled(:,i)) < 0.5
+%            kmin = i+1;
+%        else
+%            break
+%        end
+%     end
+% 
+%     for i = kmin+1:rdat.npix
+%        if mean(rdat.pixelifsampled(:,i)) < 0.5
+%            kmax = i-1;
+%            break
+%        end
+%     end
+
+
+
+
+end
+

### 2019-10-07 functions/@RasterExp/get_retrace_indeces.m

@@ -1,0 +1,20 @@
+% [ retrace_ind ] = get_retrace_indeces(nperiods, samps_per_period)
+
+% Returns a set of indeces corresponding only to the trace data, so that we
+% can discard the retrace.
+%
+% use like 
+% [ trace_ind ] = get_trace_indeces(nperiods, samps_per_period)
+% xdat_trace = xdat(trace_ind)
+function [ retrace_ind ] = get_retrace_indeces(nperiods, samps_per_period)
+
+
+samps_per_line = samps_per_period/2;
+retrace_ind = [];
+for i=0:nperiods-1
+    ind = [i*samps_per_period+1:(i*samps_per_period+samps_per_line)]'+samps_per_line;
+    retrace_ind = [retrace_ind; ind];
+end
+
+end
+

### 2019-10-07 functions/AFM.m

@@ -1,0 +1,79 @@
+classdef AFM
+  % Static methods that provide constants associated with the nPoint stage and
+  % z-axis parameters.
+  
+  methods (Static)
+    function ts = Ts()
+    % Ts = Ts() 
+    % Standard sample time.
+          
+      ts = 40e-6;
+    end
+    
+    function mic = volts2mic_xy()
+    % mic = volts2mic_xy()
+    % 
+    % Unit conversion of volts 2 microns for xy-stage
+      mic = 5;
+    end
+    
+    function volt = mic2volt_xy()
+    % volt = mic2volt_xy()
+    % 
+    % Unit conversion of microns to volts for xy-stage
+        
+      volt = 1/AFM.volts2mic_xy();
+      
+    end
+
+    function mic = volts2mic_z()
+    % mic = volts2mic_z()
+    % 
+    % Unit conversion of volts 2 microns for z-axis
+        
+      mic = 7/20; % 7 micron range in +-20 volts
+    end
+
+    function volts = mic2volts_z()
+    % volts = mic2volts_z()
+    % 
+    % Unit conversion of volts 2 microns for z-axis
+        
+      volts = 1/AFM.volts2mic_z(); 
+    end
+
+    function nm = volts2nm_z()
+    % nm = volts2nm_z()
+    % 
+    % Unit conversion of volts 2 nanometers for z-axis
+        
+      nm= AFM.volts2mic_z()*1000; 
+      
+    end
+
+    function volts = nm2volts_z()
+    % volts = nm2volts_z()
+    % 
+    % Unit conversion of volts 2 microns for z-axis
+        
+      volts = 1/AFM.volts2nm_z(); 
+      
+    end
+    
+    function map = nametrans()
+    % map = nametrans()
+    % 
+    % A translation map between x, y, z corridinates to the ADC/DAC
+    % number they are hooked up to.
+        
+      keySet ={ 'AI-0', 'AI-1', 'AI-2', 'AI-3',...
+        'Input-0', 'Input-1', 'Input-2', 'Input-3',...
+        'DAC control', 'Reference'};
+      valSet = {'y_X', 'y_Y', 'y_Z', 'null',...
+        'X', 'Y', 'Z', 'null', 'u_', 'ref_'};
+      map = containers.Map(keySet, valSet);
+    end
+    
+  end % Static Methods
+  
+end

### 2019-10-07 functions/AfmSisoController.m

@@ -1,0 +1,67 @@
+classdef AfmSisoController
+% This class is just a container for the siso axis controllers, to enforce
+% consistent naming, rather than a struct.
+% 
+%            R-prime
+%              ^  (Mss is sort of fictitious with state-space, and this is what
+%              |   we usually want from r-prime)
+%              |
+%    R-->[ M ]--> [M_ss ]--->O---->[Dki*D ]-->[ G ]----+---> y
+%                            |                      |
+%                            +-----[ Dss ]<---------+
+% 
+% -- For transfer function designs, Dss=Mss=1. Dki is an integrator and D is likely
+%    a notch etc.
+% -- For state space designs, D=1.
+% 
+
+   properties
+    G;  % System plant
+    Sens; % Sensitivity function
+    Hyr; 
+    Hy_rprime;
+    Loop;
+    plants; % All the plants
+    Ki;     % Integrator gain.
+    Dki;   % Integrator.
+    D;
+    M;
+    Dss;
+    Mss;
+   end
+   
+   methods
+       function self = AfmSisoController(G, varargin)
+          p = inputParser();
+          g_static = zpk([], [], 1, AFM.Ts);
+          
+          p.addParameter('plants', []);
+          p.addParameter('Ki', 0);
+          p.addParameter('Dki', g_static);
+          p.addParameter('D', g_static);
+          p.addParameter('M', g_static);
+          p.addParameter('Dss', g_static);
+          p.addParameter('Mss', g_static);
+          
+          p.parse(varargin{:});
+          self.plants = p.Results.plants;
+          self.Ki = p.Results.Ki;
+          self.Dki = p.Results.Dki;
+          self.D = p.Results.D;
+          self.M = p.Results.M;
+          self.Dss = p.Results.Dss;
+          self.Mss = p.Results.Mss;
+
+          self.G = absorbDelay(ss(G));
+          
+          self.Loop = self.Dki * self.D * self.G *self.Dss;
+%           self.Sens = balreal(minreal(1/(1+self.Loop)));
+          self.Sens = feedback(1, self.Loop);
+%           self.Hy_rprime = minreal(self.Mss * (self.Dki * self.D * self.G) * self.Sens);
+          self.Hy_rprime = minreal(self.Mss * feedback(self.Dki*self.D*self.G, self.Dss));
+          
+          self.Hyr = minreal(self.M * self.Hy_rprime);
+          
+       end
+   end
+end

### 2019-10-07 functions/AfmSisoSSController.m

@@ -1,0 +1,71 @@
+classdef AfmSisoSSController < AfmSisoController
+% This class is just a container for the siso axis controllers, to enforce
+% consistent naming, rather than a struct.
+% 
+%            R-prime
+%              ^  (Mss is sort of fictitious with state-space, and this is what
+%              |   we usually want from r-prime)
+%              |
+%    R-->[ M ]--> [M_ss ]--->O---->[Dki*D ]-->[ G ]----+---> y
+%                            |                      |
+%                            +-----[ Dss ]<---------+
+% 
+% -- For transfer function designs, Dss=Mss=1. Dki is an integrator and D is likely
+%    a notch etc.
+% -- For state space designs, D=1.
+% 
+
+   properties
+%     G;  % System plant
+%     Sens; % Sensitivity function
+%     Hyr; 
+%     Hy_rprime;
+%     Loop;
+%     plants; % All the plants
+%     Ki;     % Integrator gain.
+%     Dki;   % Integrator.
+%     D;
+%     M;
+%     Dss;
+%     Mss;
+      K_lqr;
+      L_dist;
+      Nx;
+      Nu;
+      sys_recyc;
+      sys_obsDist;
+      
+   end
+   
+   methods
+       function self = AfmSisoSSController(G, G_recyc, G_obsdist, L_dist, K_lqr, varargin)
+           self = self@AfmSisoController(G, varargin{:});
+          
+          [Sens, ~, Hy_rprime, ~, Loop, Dss, Mss] = ss_loops_delta_dist(G, G_recyc,...
+              G_obsdist, K_lqr, L_dist);
+          
+          self.G = balreal(absorbDelay(ss(G)));
+          self.sys_recyc = G_recyc;
+          self.sys_obsDist = G_obsdist;
+          self.Sens = Sens;
+          self.Hy_rprime = Hy_rprime;
+          
+          self.Dss = Dss;
+          self.Mss = Mss;
+          self.K_lqr = K_lqr;
+          self.L_dist = L_dist;
+          
+          [Nx, Nu] = SSTools.getNxNu(G_recyc);
+          self.Nx = Nx;
+          self.Nu = Nu;
+          
+          g_static = zpk([], [], 1, AFM.Ts);
+          self.Ki = 0;
+          self.Dki = g_static;
+          self.D = g_static;
+          
+          self.Hyr = minreal(self.M * self.Hy_rprime);
+          
+       end
+   end
+end

### 2019-10-07 functions/Core_Nesterov_mine.m

@@ -70,7 +70,7 @@ function [xk,niter] = Core_Nesterov_mine(...
     
     if opts.alpha_v > 0
         alp_v = opts.alpha_v;
-        Lmu = Lmu + alp_v^2 * 4;
+        Lmu = Lmu + (alp_v^2 * 4)/mu;
 
         Dv = alp_v*spdiags([reshape([-ones(n-1,n); zeros(1,n)],N,1) ...
             reshape([zeros(1,n); ones(n-1,n)],N,1)], [0 1], N, N);
@@ -80,7 +80,7 @@ function [xk,niter] = Core_Nesterov_mine(...
     
     if opts.alpha_h > 0
         alp_h = opts.alpha_h;%.125;
-        Lmu = Lmu + alp_h^2 * 4;
+        Lmu = Lmu + (alp_h^2 * 4)/mu;
         Dh = alp_h*spdiags([reshape([-ones(n,n-1) zeros(n,1)],N,1) ...
             reshape([zeros(n,1) ones(n,n-1)],N,1)], [0 n], N, N);
     else
@@ -88,9 +88,10 @@ function [xk,niter] = Core_Nesterov_mine(...
     end
     
     residuals = zeros(maxiter, 2);
-    st = sprintf('Iter |     fmu     |  Rel. Vartn fmu |  Residual  |');
-    fprintf('%s\n%s\n', st, repmat('-', 1, length(st)));
-
+    if opts.Verbose > 0
+        st = sprintf('Iter |     fmu     |  Rel. Vartn fmu |  Residual  |');
+        fprintf('%s\n%s\n', st, repmat('-', 1, length(st)));
+    end
     % ---------------------------- MAIN ITERATION -------------------------- %
     max_means = 10;
     fmu_s = zeros(max_means+1, 1);

### 2019-10-07 functions/NESTA_opts.m

@@ -3,27 +3,33 @@
 %               The fieldnames are case insensitive.  Below
 %               are the possible fieldnames:
 %               
-%               opts.U and opts.Ut - Analysis/Synthesis operators as function
+%           .U and opts.Ut - Analysis/Synthesis operators as function
 %               handles.
-%               opts.normU - if opts.U is provided, this should be norm(U)
+%           .normU - if opts.U is provided, this should be norm(U)
 % 
-%               opts.alpha_v - weight for vertical TV (default 0)
-%               opts.alpha_h - weight for horizontal TV (default 0)
+%           .alpha_v - weight for vertical TV (default 0)
+%           .alpha_h - weight for horizontal TV (default 0)
 % 
-%               opts.MaxIntIter - number of continuation steps.
+%           .MaxIntIter - number of continuation steps.
 %                 default is 5
-%               opts.maxiter - max number of iterations in an inner loop.
+%           .maxiter - max number of iterations in an inner loop.
 %                 default is 10,000
-% 
+%           .muf - The desired value of mu at the last continuation step.
+%                 A smaller mu leads to higher accuracy.
+%           .sigma - l2 error bound.  This enforces how close the variable
+%               must fit the observations b, i.e. || y - Ax ||_2 <= delta
+%               If delta = 0, enforces y = Ax
+%               Common heuristic: delta = sqrt(m + 2*sqrt(2*m))*sigma;
+%               where sigma=std(noise).
 %               opts.TolVar - tolerance for the stopping criteria, i.e.,
 %                             when the relative change in the objective 
 %                             function is less than TolVar.
-%               opts.Verbose - if this is 0 or false, then very
+%           .opts.Verbose - if this is 0 or false, then very
 %                   little output is displayed.  If this is 1 or true,
 %                   then output every iteration is displayed.
 %                   If this is a number p greater than 1, then
 %                   output is displayed every pth iteration.
-%               opts.errFcn - if this is a function handle,
+%            .opts.errFcn - if this is a function handle,
 %                   then the program will evaluate opts.errFcn(xk)
 %                   at every iteration and display the result.
 %                   ex.  opts.errFcn = @(x) norm( x - x_true )
@@ -49,6 +55,8 @@ function opts = NESTA_opts(varargin)
    
    p.addParameter('alpha_v', 0);
    p.addParameter('alpha_h', 0);
+   p.addParameter('mu', 1e-5);
+   p.addParameter('sigma', 0.01);
    
    p.parse(varargin{:});
    

### 2019-10-07 functions/PATHS.m

@@ -15,10 +15,10 @@ classdef PATHS
       end
     end
     function path = tmech_fig()
-       path = '/home/arnold/gradschool/publications/afm-cs-tmech/latex/figures/'; 
+       path = '/home/arnold/gradschool/publications/tmech-afm-cs/latex/figures/'; 
     end
     function path = tmech_table()
-      path = '/home/arnold/gradschool/publications/afm-cs-tmech/latex/tables';
+      path = '/home/arnold/gradschool/publications/tmech-afm-cs/latex/tables';
     end
     
     function path = cs_final_fig()

### 2019-10-07 functions/data_writer.m

@@ -1,0 +1,55 @@
+
+function data_writer(data, fname, numeric_fmt)
+    if nargin < 3
+        numeric_fmt = '%.3g';
+    end
+   assert(isa(data, 'cell')); 
+   fid = fopen(fname, 'w+');
+   
+   
+   for k=1:length(data)
+      dat_k = data{k};
+      assert(isstruct(dat_k));
+      write_struct(dat_k, fid, numeric_fmt)
+   end
+    
+end
+
+
+function write_struct(data, fid, fmt)
+    
+   flds = fieldnames(data);
+   
+   for k=1:length(flds)
+      fld = flds{k};
+      dat_k =  data.(fld);
+      if isnumeric(dat_k) || islogical(dat_k)
+          write_number(dat_k, fld, fid, fmt)
+      elseif ischar(dat_k)
+          write_string(dat_k, fld, fid);
+      elseif isstruct(dat_k)
+          write_struct(dat_k, fid, fmt)
+      else
+          error(['I dont know what to do with type %s, in field %s. ',...
+              'Expected numeric or struct.'], class(dat_k), fld)
+      end
+   end
+    
+end
+
+function write_string(data, name, fid)
+    
+   fprintf(fid, '%%<*%s>\n', name);
+   fprintf(fid, '%s\n', data);
+   fprintf(fid, '%%</%s>\n', name);
+    
+end
+
+function write_number(data, name, fid, fmt)
+    
+    fmt_str = sprintf('%s\n', fmt);
+   fprintf(fid, '%%<*%s>\n', name);
+   fprintf(fid, fmt_str, data);
+   fprintf(fid, '%%</%s>\n', name);
+    
+end

### 2019-10-07 functions/frf2ss_opts.m

@@ -1,0 +1,44 @@
+classdef frf2ss_opts
+  %   opts = frf2ss_opts(name1, value1,...)
+  % Builds an options structure for for frf2ss via name-value pairs. Options
+  % are:
+  % 'Ts', sampling_time
+  % 'nd', integer number of delay. This does not appear to get used in frf2ss. 
+  %       This should be fixed.
+  % 'impulse_length_sec', default = 0.1
+  % 'r', integer
+  % 's', integer
+  %
+  % r and s and the width and hieght of the hankel matrix. Defaults to 500x500.
+  % 
+   properties
+       Ts;
+       nd;
+       impulse_length_sec;
+       r;
+       s;
+       
+   end
+    
+   methods
+       function self = frf2ss_opts(varargin)
+          p = inputParser;
+          p.addParameter('Ts', 40e-6);
+          p.addParameter('nd', 0);
+          p.addParameter('impulse_length_sec', 0.1);
+          p.addParameter('r', 500);
+          p.addParameter('s', 500);
+          
+          parse(p, varargin{:});
+          
+          self.Ts = p.Results.Ts;
+          self.nd = p.Results.nd;
+          self.impulse_length_sec = p.Results.impulse_length_sec;
+          self.r = p.Results.r;
+          self.s = p.Results.s;
+          
+       end
+   end
+    
+    
+end

### 2019-10-07 functions/get_raster_paths.m

@@ -1,0 +1,27 @@
+% [raster_paths] = get_raster_paths(data_root, data_name,  parent_folder)
+%
+% Given data_root and data_name, returns a struct raster_paths with the 
+% following fields:
+% 
+% raster_paths.data_path
+% raster_paths.meta_path
+% raster_paths.parent_path
+% raster_paths.data_path_mat
+
+function [raster_paths] = get_raster_paths(data_root, data_name, parent_folder)
+  if nargin < 3
+      parent_folder = 'parents';
+  end
+  parent_root = get_parent_root(data_root, parent_folder);
+  parent_name = get_parent_name(data_name, '_out_', '.json');
+  
+  raster_exp_meta_name = strrep(data_name, '.csv', '-meta.json');
+  % Location of the raw, experimental data.
+  raster_paths.data_path = fullfile(data_root, data_name);
+  % Location of the post-experiment meta-data.
+  raster_paths.meta_path = fullfile(data_root, raster_exp_meta_name);
+  % Where the input file is
+  raster_paths.parent_path = fullfile(parent_root, parent_name);
+  % Where to save the post-processed data.
+  raster_paths.data_path_mat = strrep(raster_paths.data_path, '.csv', '.mat');
+end

### 2019-10-07 functions/get_xdir_loop_shaped_control.m

@@ -1,0 +1,118 @@
+
+function xdirControl = get_xdir_loop_shaped_control(verbose)
+    if nargin < 1
+        verbose = true;
+    end
+
+    % ------- Load Plants -----
+    [plants, frf_data] = CanonPlants.plants_ns14(9, '5micron');
+    
+    % It is important to id the mode with a very small (0.1 volt) amplitude.
+    newest_xfrf_path = fullfile(PATHS.sysid, 'x-axis_sines_info_first_resFourierCoef_6-1-2019-01.json');
+    sysx_new = SweptSinesOnline(newest_xfrf_path);
+    
+    
+    [z, p, k] = zpkdata(plants.Gvib, 'v');
+    p1 = p(end-1:end);
+    z1 = z(end-3:end-2);
+    p(end-1:end) = [];
+    z(end-3:end-2) = [];
+    
+    g_tmp = zpk(z, p, k, plants.Gvib.Ts)*plants.gdrift;
+    g_tmp = g_tmp*dcgain(plants.Gvib*plants.gdrift)/dcgain(g_tmp);
+    
+    Gx_bend_ = sysx_new.FRF_from_FC(1, [2]);
+    Gx_bend_frd = Gx_bend_/g_tmp;
+    
+    % Initial guess.
+    gx_bend0 = zpk(z1, p1, 1, plants.Gvib.Ts);
+    
+    sos_fos_xbend = SosFos(gx_bend0, 'iodelay', 9);
+    lg = LogCostZPK(squeeze(Gx_bend_frd.Response), Gx_bend_frd.Frequency*2*pi, sos_fos_xbend);
+    lg.solve_lsq(1);
+    gx_bend_lg = lg.sos_fos.realize();
+    
+    if verbose
+        figure(100)
+        opts = bodeoptions();
+        opts.FreqUnits = 'Hz';
+        bodeplot(Gx_bend_frd, opts)
+        grid
+        hold on
+        bodeplot(gx_bend_lg, Gx_bend_frd.Frequency*2*pi);
+    end
+
+    Dinv = 1 / gx_bend_lg;
+    Dinv = Dinv / dcgain(Dinv);
+    
+    D_notch= zpk([0.979 + 1i*0.163, 0.979  - 1i*0.163], [0.8, 0.8], 1, AFM.Ts);
+    D_notch = D_notch/dcgain(D_notch);
+    
+
+   
+    Ki = 0.035;
+    Dki = zpk(0, 1, Ki, AFM.Ts);
[…]

### 2019-10-07 functions/mimo_bode_mag.m

@@ -1,0 +1,39 @@
+
+
+function hands = mimo_bode_mag(HH, freq_s, ha, varargin)
+    nu = size(HH, 2);
+    no = size(HH, 1);
+    
+    if isempty(ha)
+        [ha] = tight_subplot(no, nu, .01, [.061, 0.03], [.065, .02]);
+        ha = reshape(ha', [], no)';
+    end
+    
+    hands = gobjects(no, nu);
+    ylm = [-95, 30];
+    coords = {'X', 'Y', 'Z'};
+    for ny = 1:size(HH, 1)
+        for nu=1:size(HH, 2)
+            try
+                hands(ny, nu) = frf_bode_mag(HH(ny,nu), freq_s, ha(ny,nu), 'Hz', varargin{:});
+            catch
+                keyboard
+            end
+            set(ha(ny,nu), 'YLim', ylm);
+            if nu >1
+                set(ha(ny,nu), 'YLabel', [], 'YTickLabel', []);
+            else
+                ylabel(ha(ny,nu), sprintf('Output %s (Mag [dB])', coords{ny}));
+            end
+            if ny ==1
+                title(ha(ny,nu), sprintf('Input %s', coords{nu}));
+            end
+            if ny <3
+                set(ha(ny,nu),  'XLabel', [], 'XTickLabel', []);
+            end
+            set(ha(ny,nu), 'XTick', [10,100,1000,10000]);
+            
+        end
+    end
+  
+end

### 2019-10-07 functions/pin_along_column.m

@@ -1,0 +1,20 @@
+% pixmat = pin_along_column(pixmat, x1, x2)
+function pixmat = pin_along_column(pixmat, x1, x2)
+
+  xs = 1:size(pixmat,2);
+  for k=1:size(pixmat,1)
+      row = detrend(pixmat(k, :));
+      y1 = row(x1);
+      y2 = row(x2);
+%     y1 = pixmat(k, x1);
+%     y2 = pixmat(k, x2);
+    
+    m = (y2-y1)/(x2-x1);
+    b = y1 - m*x1;
+    line = m*xs + b;
+%     pixmat(k,:) = pixmat(k,:) - line;
+    pixmat(k, :) = row - line;
+  end
+  
+
+end

### 2019-10-07 functions/state_space_x/CanonCntrlParamsChoozeZeta.m

@@ -1,0 +1,51 @@
+classdef CanonCntrlParamsChoozeZeta
+% Constructs the standard pole-placement data for the AFM.
+% zeta_s = [.8, .7, .4, .4 .542];
+% gams = [1., 1., 1., 1., 1];
+% rad = 0.25
+% pint = 0.8
+% rhos = [1.02, 1,1]
+  
+  properties
+    rho_s;
+    gam_s;
+    zeta_s;
+    rad;
+    pint;
+    
+  end
+
+  methods
+    
+    function self = CanonCntrlParamsChoozeZeta(sys)
+      
+    % if we make the last one 0.4, the high freq poles with
+    % zeta ~=0.5 actually lose damping.
+      self.zeta_s = [.85, 0.85, .7, .4, .4 .4];
+      self.gam_s = [1., 1., 1., 1., 1., 1.]; % puts it at the extant zero
+      self.rad = 0.25;
+      self.pint = 0.8;
+      
+      %[wp_real_x, wz_real_x] = w_zp_real(sys);
+%       rho_1 = wz_real_x(1)/wp_real_x(1);
+      % self.rho_s = [rho_1, 1., 1];
+      self.rho_s = [1.2, 1., 1];
+      
+    end
+    
+    function self = aggressive_params(self)
+      self.zeta_s = [.7, 0.7, .6, .4, .4 .4];
+      self.gam_s = [1.25, 1.2, 1.3, 1., 1., 1.]; % puts it at the extant zero
+      self.rad = 0.25;
+      self.pint = 0.8;
+      self.rho_s = [2.0, 1., 1];
+    end
+    
+  end
+  
+        
+        
+end
+
+    
+    

### 2019-10-07 functions/state_space_x/CanonPlants.m

@@ -1,0 +1,81 @@
+classdef CanonPlants
+  
+  properties
+    path = fullfile(PATHS.sysid, 'FRF_data_current_stage2.mat');
+    plants;
+  end
+  
+  
+  methods (Static)
+    function [plants, frf_data, modelFit] = plants_ns14(nd, version)
+    % [plants, frf_data] = plants_ns14(nd)
+      
+    %       load(fullfile(PATHS.sysid, ['hysteresis/steps_hyst_model.mat']));
+    %       hyst.rp = rp;
+    %       hyst.wp = wp;
+    %       hyst.r = r;
+    %       hyst.w = w;
+    %
+    %       modelFit_file = fullfile(cs_root,'xy-stage', 'x-axis_sines_infoFourierCoef_9-11-2018-01.mat');
+    if ~exist('version', 'var')
+      version = 1;
+    end
+      
+      if version == 1
+        modelFit_file = fullfile(PATHS.sysid,'xy-stage', 'x-axis_sines_infoFourierCoef_9-11-2018-01.mat');
+      elseif version == '5micron'
+        modelFit_file = fullfile(PATHS.sysid,'xy-stage', 'x-axis_sines_infoFourierCoef_9-11-2018-01_5michyst.mat');
+      else
+        error('version number $d not recocnized');
+      end
+      
+      load(modelFit_file, 'modelFit')
+      if exist('nd', 'var') && ~isempty(nd)
+        modelFit.models.Gvib.IOdelay = 0;
+        modelFit.models.G_uz2stage.IOdelay = 0;
+        modelFit.models.Gvib.InputDelay = nd;
+        modelFit.models.G_uz2stage.InputDelay = nd;
+      else
+        modelFit.models.Gvib.IOdelay = 0;
+        modelFit.models.G_uz2stage.IOdelay = 0;
+        modelFit.models.Gvib.InputDelay = 9;
+        modelFit.models.G_uz2stage.InputDelay = 9;
+      end
+      plants = modelFit.models;
+      SYS = ss(modelFit.models.Gvib);
+      
+      %plants.gdrift = modelFit.models.gdrift;
+      plants.gdrift_inv = 1/plants.gdrift;
+      
+      SYS = balreal(SYS);
+      Nx = SSTools.getNxNu(SYS);
+      T = diag(1./Nx)/10;
+      SYS = ss2ss(SYS, T);
+      PLANT = SYS;
+      
[…]

### 2019-10-07 functions/state_space_x/build_control_constsigma.m

@@ -1,0 +1,107 @@
+function [Q, R0, S, Px] = build_control_constsigma(G_recyc, cmplx_rad, tol)
+% [Q, R0, S] = build_control(sys_recyc, can_cntrl)
+% Construct the quadratic cost matrices using the root-locus
+% technique (fictitious zeros). 
+% 
+% Inputs
+% ------
+%  sys_recyc : the deltaUk ss system
+%  can_control : an instance of CanonControlParams_XX.m
+% tol : tolerance for ctrbf, which will be used if pole placment fails.
+% Unfortunately, the default tolerance is often not sufficient to promote a
+% decomposition for all cases where pole placement fails.
+  
+
+  if ~exist('tol', 'var')
+      tol = 1e-8;
+  end
+  
+
+  p_int = 0.8;  rho_s = [1., 1]; rad = 0.25;
+  Px = getCharDes_const_sig(G_recyc, p_int, cmplx_rad, rho_s, rad).';
+  
+  z = tzero(G_recyc);
+  z = sort_by_w(z(imag(z)~=0));
+  %Px(2:3) = z(1:2);
+  Px(4:5) = z(3:4);
+  % Px(5:6) = z(3:4);
+  
+  try
+      [Chat, Dhat] = place_zeros(G_recyc, Px);
+  catch
+      [Chat, Dhat] = place_zeros_kalman_decomp_local(G_recyc, Px, tol);
+  end
+
+  Q = Chat'*Chat;
+  
+  S = Chat'*Dhat;
+  R0 = Dhat'*Dhat;
+  
+%   if sys_recyc.InputDelay ~= 0 || sys_recyc.IOdelay ~=0
+%     error(['All Delays of sys_obs must be part of the states, not ' ...
+%            'included as a property']);
+%   end
+%   
+%   
+%   P_x  = getCharDes(sys_recyc, can_cntrl.gam_s, can_cntrl.pint,...
+%                                can_cntrl.zeta_s, can_cntrl.rho_s, can_cntrl.rad);
+%   [Chat, Dhat] = place_zeros(sys_recyc, P_x);
+%   
+%   Q = Chat'*Chat;
+%   S = Chat'*Dhat;
+%   R0 = Dhat'*Dhat;
+  
+
+end
+
+function [Chat, Dhat] = place_zeros_kalman_decomp_local(sys, P_x, tol)
+% The trouble with controllability is that the recycled system (delta Uk
+% puts a zero at z=0, but we also have delay poles there, so pole-zero
[…]

### 2019-10-07 functions/state_space_x/build_obs.m

@@ -1,0 +1,20 @@
+function [sys_obsDist, L_dist] = build_obs(sys_obs, can_params)
+ %  [sys_obsDist, L_dist] = build_obs(sys_obs, can_params)
+  if sys_obs.InputDelay ~= 0 || sys_obs.IOdelay ~=0
+    error(['All Delays of sys_obs must be part of the states, not ' ...
+           'included as a property']);
+  end
+  
+  
+  p_int_d = can_params.p_int;
+  
+  Qw = sys_obs.b*sys_obs.b'*can_params.beta;
+  
+  Lx = dlqr(sys_obs.a', sys_obs.c', Qw, 1)';
+  Ad = 1;
+  Cd = 1;
+  [L_dist, sys_obsDist, IDENT_obs, eNs_12] = DistEst.output_dist_est(sys_obs,...
+                                                    Lx, p_int_d, Ad, Cd);
+  [Nx_r, Nx_d, Nu_r, Nu_d] = DistEst.steady_state_gains(sys_obs, sys_obs.b*0, 1);
+  
+end

### 2019-10-07 functions/state_space_x/ss_loops_delta_dist_frf.m

@@ -1,0 +1,54 @@
+
+function [Sens, Hyd, Hyr, Loop] =ss_loops_delta_dist_frf(G_frf, omegas, sys, sys_recyc, sys_obs, KxKu, LxLd)
+% [Sens, Hyd, Hyr] = ss_loops_delta_dist_frf(G_frf, omegas, sys, sys_recyc, sys_obs, KxKu, LxLd)
+% 
+% For the closed loop s.s. system with deltaU augmentation and disturbance
+% estimation (input disturbance only), constructs the closed loop transfer
+% functions:
+%
+% Sens = 1/(1 + Loop)
+% Loop = G(z)* K_c(zI - A_tilde)^-1 * LL_
+%
+% Hyr = G(z)[Nbar - K_c(zI - A_tilde)^-1 BB_ ]
+%       --------------------------------------
+%        1 + G(z) * K_c(zI - A_tilde)^-1 * LL_
+%
+% Hyd =                 G(z)
+%       --------------------------------------
+%        1 + G(z) * K_c(zI - A_tilde)^-1 * LL_
+%
+  Ts = sys.Ts;
+  
+  Kx = KxKu(1:end-1);
+  Ku = KxKu(end);
+  Nbar = SSTools.getNbar(sys_recyc, KxKu);
+
+  Ld = LxLd(end);
+  Lx = LxLd(1:end-1);
+  Cd = sys_obs.c(end);
+
+  A_tilde = sys.a - sys.b*Kx - Lx*sys.c;
+
+  AA_ = [A_tilde, sys.b-sys.b*Ku, -(sys.b*Nbar+Lx*Cd);
+       -Kx,     1-Ku,             -Nbar;
+       -Ld*sys.c,    0,              1-Ld*Cd];
+
+  BB_ = [sys.b*Nbar; Nbar; 0];
+  LL_ = [Lx; 0; Ld];
+
+  K_c = [KxKu, Nbar];
+  K_c(end-1) = K_c(end-1)-1;
+  D1 = ss(AA_, LL_, K_c, 0, Ts);
+  D2 = ss(AA_, BB_, -K_c, Nbar, Ts);
+
+  D1_frf = squeeze(freqresp(D1, omegas));
+  D2_frf = squeeze(freqresp(D2, omegas));
+  
+  % % Estimated state feedback loop gain:
+  Loop = G_frf.*D1_frf;
+  Sens = 1./(1+Loop);
+
[…]

### 2019-10-07 plot_with_without_FF_loop_cs20ngflat.m

@@ -1,0 +1,179 @@
+% 
+% This script plots the z-bounce like experiment over a flat portion of the
+% CS20ng grating. Both controllers are based on the loop-shaping transfer
+% function control. The -03 experiment has the feedforward filter, the 02 does
+% not.
+
+% close all
+clear PATHS
+addpath functions
+addpath ~/matlab/dependencies/l1c/
+addpath ~/matlab/dependencies/l1c/lib
+
+addpath ~/matlab/afm-cs/matlab-code/functions/
+% initialize paths.
+
+figbase = 20;
+
+
+size_dir = '5microns';
+hole_depth = (20);
+
+chan_map = ChannelMap([1:5]);
+% exp_date = '3-20-2019'
+% ----------------------- Load and Process CS-data -----------------------------
+
+
+data_root = '/media/labserver/afm-cs/z-bounce/6-12-2019/';
+% ----------------------- Load and Process raster-data -------------------------
+cs_files = {...
+'cs-traj-512pix-3perc-500nm-5mic-01Hz-150prescan-notconnect_out_6-12-2019-03.csv',...
+'cs-traj-512pix-3perc-500nm-5mic-01Hz-150prescan-notconnect_out_6-12-2019-02.csv',...
+};
+
+cs_exps = {};
+for k=1:length(cs_files)
+  cs_paths = get_cs_paths(data_root, cs_files{k});
+  gg = @(u, idx_state_s) log_creep_detrend(u, idx_state_s);
+  cs_exps{k} = CsExp(cs_paths, 'feature_height', hole_depth, 'gg', gg, 'load_full', true);
+  cs_exps{k}.print_state_times();
+end
+
+name_s = {'CR w/o notch', 'CR-w/notch', 'CZ w/o notch', 'CZ w/ notch'};
+for k=1:length(cs_exps)
+   cs_exps{k}.uz  = cs_exps{k}.uz*AFM.volts2nm_z;
+end
+
+%%
+if 0
+    [~, axs1] = make_cs_traj_figs(figbase+100, 3);
+    cs_exps{1}.plot_all_cycles(axs1{1:3}, [], [], 512);
+    
+    [~, axs2] = make_cs_traj_figs(figbase+200, 3);
+    cs_exps{2}.plot_all_cycles(axs2{1:3}, [], [], 512);
+    
[…]

### 2019-10-07 process_data_5_29_2019.m

@@ -1,0 +1,660 @@
+clc
+clear
+%%
+close all
+addpath functions
+
+% initialize paths.
+% init_paths();
+figbase = 20;
+
+
+size_dir = '5microns';
+fname = fullfile(PATHS.sysid, 'x-axis_sines_info_intsamps_zaxisFourierCoef_10-29-2018-01.mat');
+models = load(fname);
+G = -models.modelFit.G_zdir;
+p = pole(G);
+z = zero(G);
+gg = zpk(z(end-1:end), p(1:2), 1, G.Ts);
+hole_depth = (20);
+
+chan_map = ChannelMap([1:5]);
+exp_date = '5-30-2019'
+% ----------------------- Load and Process CS-data -----------------------------
+dat_root = PATHS.raster_image_data(size_dir, exp_date);
+
+% ----------------------- Load and Process raster-data -------------------------
+raster_files = {...
+'raster_scan_512pix_5mic_1.00e+00Hz_fourier_out_5-30-2019-01.csv',...
+'raster_scan_512pix_5mic_4.00e+00Hz_fourier_out_5-30-2019-01.csv',...
+'raster_scan_512pix_5mic_05Hz_fourier_out_5-30-2019-01.csv',...
+'raster_scan_512pix_5mic_8.00e+00Hz_fourier_out_5-30-2019-01.csv',...
+'raster_scan_512pix_5mic_10Hz_fourier_out_5-30-2019-01.csv',...
+'raster_scan_512pix_5mic_1.50e+01Hz_fourier_out_5-30-2019-01.csv',...
+'raster_scan_128pix_5mic_05Hz_fourier_out_5-30-2019-01.csv',...
+};
+
+cs_files = {...
+'cs-traj-512pix-10perc-500nm-5mic-01Hz-150prescan-notconnect_out_5-30-2019-01.csv',...
+'cs-traj-512pix-10perc-500nm-5mic-02Hz-150prescan-notconnect_out_5-30-2019-01.csv',...
+'cs-traj-512pix-10perc-500nm-5mic-04Hz-150prescan-notconnect_out_5-30-2019-01.csv',...
+'cs-traj-512pix-10perc-500nm-5mic-05Hz-150prescan-notconnect_out_5-30-2019-01.csv',...
+'cs-traj-512pix-10perc-500nm-5mic-08Hz-150prescan-notconnect_out_5-30-2019-01.csv',...
[…]

### 2019-10-07 process_data_6_5_2019.m

@@ -1,0 +1,927 @@
+clc
+clear
+%%
+close all
+addpath functions
+
+% initialize paths.
+
+size_dir = '5microns';
+fname = fullfile(PATHS.sysid, 'x-axis_sines_info_intsamps_zaxisFourierCoef_10-29-2018-01.mat');
+models = load(fname);
+G = -models.modelFit.G_zdir;
+p = pole(G);
+z = zero(G);
+gg = zpk(z(end-1:end), p(1:2), 1, G.Ts);
+hole_depth = (20);
+
+chan_map = ChannelMap(1:5);
+
+% ----------------------- Load and Process raster-data -------------------------
+fls = ls('/media/labserver/afm-cs/imaging/raster/5microns/6-5-2019/*.csv', '-t');
+raster_files = strsplit(fls);
+% The last element is always an empty string.
+raster_files = flipud(raster_files(1:end-1)')
+
+
+fls = ls('/media/labserver/afm-cs/imaging/cs-imaging/5microns/6-5-2019/*.csv', '-t');
+cs_files = strsplit(fls);
+% The last element is always an empty string.
+cs_files = flipud(cs_files(1:end-1)')
+
+
+
+rast_exps = cell(length(raster_files), 1);
+for k=1:length(raster_files)
+    [dat_root, dat_name, ext] = fileparts(raster_files{k});
+    
+    raster_paths = get_raster_paths(dat_root, [dat_name, ext], 'parents-loop');
+    rast_exps{k} = RasterExp(raster_paths, 'load_full', true, 'reload_raw', false);
+    if rast_exps{k}.time_total == 0
+        rast_exps{k}.time_total = rast_exps{k}.samps_per_period*rast_exps{k}.npix*AFM.Ts;
+    end
+end
+fprintf('finished loading raster data\n')
+
+
+target_pix = 512;
+use_ze = false;
+% last image is 128 pixels
+x1s = [36,   27,  27,  27,  27, 27, 6*4];
+x2s = [493, 493, 493, 495, 494, 494, 122*4];
+figbase = 10;
+for k=1:1 %length(rast_exps)
+    rast_exps{k}.uz = log_creep_detrend(rast_exps{k}.uz, []);
+    
+    if rast_exps{k}.npix_y_og ~= target_pix
[…]

### 2019-10-07 latex/review-response-1.tex
Start response letter.

@@
 
+\textbf{WHAT ARE THE CONTRIBUTIONS OF THIS PAPER:} Please see the section "Comments to the Author".
+
+\textbf{WHAT ARE SOME WAYS IN WHICH THE PAPER COULD BE IMPROVED:} Please see the section "Comments to the Author".
+
+Comments to the Author
+
+Authors extended their own previous work related to $\mu$-path pattern for AFM imaging.
+Bulk of this work is to experimentally demonstrate potential advantages of $\mu$-path pattern namely: (a) reduction in scanning time, and (b) sampling artifacts.
+
 \begin{enumerate}
+\itemaddr{red}{Writing could be improved. Certain sentences are too long and may benefit by decomposing into two sentences.}
 
-    \itemaddr{black}{Objection}
+\itemaddr{red}{For BPVV technique, what can be the minimum value of $\beta$ instead of zero?
+The value of $\beta$ was chosen to be 0.1.
+Does the reconstruction improve by having $\beta$ to be 0.05, 0.01, 0.001 or less?}
 
-    \inttext{Response}
+\itemaddr{red}{In section IV A, authors have mentioned that the cantilever does not need to fully disengage.
+This may be lead to damage of delicate biological samples.
+Hence, is this approach viable for biological samples?}
+
+\itemaddr{red}{Why was PID controller not chosen over PI controller (section IV C)? Please explain in detail.}
+
+\itemaddr{red}{Instead of using SSIM and PSNR to compare two images, did authors work on quantifying the error by overlapping/comparing the obtained images with master image?
+Please explain.
+Further, does $\mu$-path provide high accuracy when compared to other techniques e.g.
+raster scan?}
+
+\itemaddr{red}{Did authors experimentally evaluate the tip as well as sample damage and correlate that to the RDI number? Please explain in detail.}
+
+\itemaddr{red}{CS or $\mu$-method is dependent on frequency e.g.
+at 8 Hz (Fig 11), raster 128 images look comparable or may be better than CS (12.7\% and 24.8\%).
+In addition, the time taken by raster 128 is approximately half of CS 25\% and close to CS 12.5\%.
+Hence, the method mentioned in this paper may not be applied to all frequencies.
+Please comment.}
+
+\itemaddr{red}{In Fig 12, what is the significance or value of showing 10 Hz data only for raster scans (128 and 64 lines)?
+Suggestion is to add 10 Hz data also for CS 12.5\% and CS 25\%.
+Alternatively, 10 Hz data for raster scans can be removed.}
+
 \end{enumerate}
-  While interesting, this paper assumes full state feedback.
-  That is not a realistic assumption for many systems,
-  including the one under consideration here.
+\section{Review 2}
+\textbf{WHAT ARE THE CONTRIBUTIONS OF THIS PAPER:} This paper, building on substantial prior work of the authors [31,33,35-37], demonstrates AFM imaging based on sub-sampling and reconstruction.
+The paper summarizes compressive sensing approaches, the experimental implementation of the method, image quality metrics and presents experimental results.
+The main contributions are a new reconstruction algorithm (BPVV) and experimental comparison of AFM images using standard raster scanning and the proposed method.
 
-\section{Review 2}
+\textbf{WHAT ARE SOME WAYS IN WHICH THE PAPER COULD BE IMPROVED:} The paper is well written and easy to follow.
+The presentation of the results in general is good.
+However, a lot of content is based on prior work by the authors [31,33,35-37] and therefore is only revisited.
+Given that the paper is already on the long side and the limited novel content, the authors could consider to focus on the main contribution.
+The authors mention the control scheme as a new contribution however the use of notches and pre-filters is a standard approach in such tracking control applications.
 
-  \listintertext{Response. }
+Some section headings should be revisited, e.g.
+better headings found for IV A), V B).
+Particularly, the experimental results sections A) and B) are quite wordy and it would benefit the readability to focus on concise statements and summarized results.
+Maybe, the results on subline sampling can be included in the overall comparison (Fig.
+10) for conciseness.
+
+Further Comments:
+\begin{itemize}
+\itemaddr{red}{No clear trend can be seen in Fig. 10 a) and b) compared to c). Can the authors comment on the origin of this observation and how it relates to the definition of the metrics used? }
+
+\itemaddr{black}{The deflection signal should be stated in real-word units instead of volts. In contact mode AFM, the setpoint is a contact force and not a voltage.}
+
+\listintertext{This is not true. In PicoView, the setpoint is either a voltage or a unitless number.}
+
+\itemaddr{red}{The authors mention difficulties with leveling the images. Could facet leveling be used instead however this will depend on the z-noise level?}
+
+\listintertext{What is facet leveling?}
+\end{itemize}
+
+Comments to the Author
+please see above
+
+\section{Review 3}
+
+WHAT ARE THE CONTRIBUTIONS OF THIS PAPER: Please see comments to the author.
+
+WHAT ARE SOME WAYS IN WHICH THE PAPER COULD BE IMPROVED: Please see comments to the author.
+
+Comments to the Author
+The article presents an undersampling-based approach ($\mu$-path) for reducing the imaging time in atomic force microscopy, with the aim of retaining the imaging quality of a slower raster scan.
+The approach is based on sampling random lines and reconstructing the image from the gathered data.
+The experimental results are convincing, indicating that the approach taken can substantially increase the imaging speed under certain conditions.
+The article is well written and easy to follow.
+
+The introduction provides a well-founded motivation for the work, and gives a comprehensive overview of related research.
+The authors combine their previous preliminary work on the topic into a more comprehensive work.
+Together with the new contributions, this work is suitable for publication.
+
+Please consider some additional comments in the following.
+
+The meaning of undersampling in this case could be made more clear at an earlier point, as it may be confused with the term used in signal processing, that is, signal sampling rate below the Nyquist limit.
+"Reducing sampling" is ambiguous in this sense.
+
+For the reconstruction method, do the values of alpha and beta need to be tuned for different samples, or do the values used in the article apply generally?
+
+The implementation details are generally well described.
+However, some description of the mechanical setup of the AFM would help interpret the results, ie.
+later in the article it is clarified that it is based on a piezo tube scanner.
+This explains some of the coupling between the xy-axes and the z-axis.
+Furthermore, this leads to the question of whether or not the results are independent of the mechanical setup, that is, would the results be comparable on a scanner with more independent axes?
+
+It would be interesting to see a plot of the triangle-like wave of the raster scanning reference trajectory, and possibly compared to a trajectory generated by the CS approach.
+
+The experimental results: How is 'nominal density' defined?
+
+Figure 8 and 11 should have the total imaging time indicated.
+In general, comparison in terms of imaging time is the more interesting result in this reviewers opinon, rather than the scanning frequency.
+
+Figure 10 is not easy to read.
+Perhaps it would be easier if the scan types (ie.
+raster 512, CS 25%, …) are colored, and solid lines used to connect the scans.
+Furthermore, perhaps numbers [Hz] to indicate scanning speed.
+
+The images produced by the CS approach seems to be quite blurry near the edges. Is there an explanation for this observation?
+
+In general, while this approach provides good contrast and quality for some scanning speeds, it seems that it could potentially miss smaller details in the sample entirely, due the random sampling.
+Is it possible to say something about what kind of samples would be more suitable for the approach in this regard?
+
+\section{Review 4}
+\textbf{WHAT ARE SOME WAYS IN WHICH THE PAPER COULD BE IMPROVED:} The paper can be improved in the following aspects:
+1) The title and the abstract need to be changed to make the paper clearly distinct from the authors' previous work.
+2) A few technical questions are required to be answered.
+
+\textbf{WHAT ARE THE CONTRIBUTIONS OF THIS PAPER:} The paper presents the implementation of a data acquisition approach, which drives AFM to scan over a $\mu$ path.
+It also suggests a data reconstruction method Basis Pursuit Vertical Variation (BPVV) Compressive Sensing (CS) method.
+As a result, the AFM scanning time is faster than typical raster scans.
+The damage to the tip and delicate specimens is reduced.
+The work is of high quality and very valuable for the research area.
+The paper is recommended for publishing after a few further clarifications are added.
+
+Comments to the Author
+
+To authors,
+
+The paper presents a data acquisition approach based on $\mu$ scanning path.
+The measured data is suggested to be reconstructed via a Basis Pursuit Vertical Variation (BPVV) Compressive Sensing (CS) method.
+Practical control method has been designed and implemented for the $\mu$ path scans.
+Experimental results have shown the advantages of the proposed data acquisition method.
+The paper is in high quality and is important.
+
+The paper can be improved as follows, for higher quality.
+\begin{enumerate}[label=\alph*]
+\itemaddr{red}{It would be better to change the tile to make it easy to differentiate the paper from the authors’ previous work.  Please rephrase the abstract also to make it more concise.}
+
+\itemaddr{red}{I assume the AFM works in contact mode based on the article itself. Please make it clearer.}
+
+\itemaddr{red}{Do we have a constant $\mu$ path for each scanning configurations in terms of size, resolution and speed? }
+
+\itemaddr{red}{The signal $x$ needs to satisfy sparsity, in order to satisfy Equation (1).
+In AFM, can we make sure that the sparsity-property is true?
+Please clarify assumptions, if signal $x$ in Equation (1) and the following requires sparsity.}
+
+\itemaddr{red}{The scanning path is designed as parts of raster patterns. Do the transitions between scanning patterns follow any order?}
+
+\itemaddr{red}{What is the used anti-windup design? Is it only a saturation of sensing signals as mentioned in the caption of Fig 5?}
+
+\itemaddr{red}{The error between the first and sixth raster scans in Fig 7 seems to be a result of drifting.
+Is it possible to correct the signals by measuring the drift instead of the used computational method?
+When the specimen is alive, the proposed computational method may ignore the moving of the specimen.}
+
+\itemaddr{red}{There is no unit in Table II.}
+\end{enumerate}
 
